### 2014-07-24 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Add RFC for data analysis extensions and LaTeX RFC class
Former-commit-id: e82513630e4c2b091a59db685e8c601209f84007

\documentclass[letterpaper,hyper]{THG_RFC}

% Fonts
\usepackage{ifluatex}
\ifluatex
  % Font
  \usepackage{luatextra, xunicode, unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont[
    UprightFont={*},
    BoldFont={* Bold},
    ItalicFont={* Italic},
    BoldItalicFont={* Bold Italic}
  ]{STIX}
  \setsansfont[
    UprightFont={*},
    BoldFont={* Bold},
    ItalicFont={* Italic},
    BoldItalicFont={* Bold Italic}
  ]{Source Sans Pro}
  \setmathfont[math-style=ISO, bold-style=ISO]{Latin Modern Math}
  \setmonofont[
    UprightFont={*},
    BoldFont={* Bold},
    ItalicFont={* Oblique},
    BoldItalicFont={* Bold Oblique}
  ]{DejaVu Sans Mono}
\else
  \usepackage{lmodern} % times / lmodern / mathpazo / palatino
  \usepackage[scaled=.95]{helvet}
  \usepackage{courier}
\fi

% Path to figures, plots
\graphicspath{{./pics/}{./plots/}}

%% TikZ
\usepackage{tikz}
\usetikzlibrary{patterns, shapes, shadows}

% Code snippets
\usepackage{listings}
\def\lstsetc{\lstset{language=C,
  numbers=left,
  xleftmargin=20pt,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  showspaces=false, 
  showstringspaces=false,
  breaklines=true,
  basicstyle=\footnotesize\ttfamily,
  stringstyle=\itshape,
  commentstyle=\itshape\bfseries,
  morekeywords={main, size_t, malloc, free,
    hsize_t, hid_t, herr_t, H5X_class_t, H5X_type_t,
    H5Fcreate, H5Fclose,
    H5Dcreate, H5Dopen, H5Dclose, H5Dwrite, H5Dread, H5Dquery,
    H5Qcreate, H5Qclose,
    H5Screate_simple, H5Sclose, H5Sget_select_npoints,
    H5Xcreate
    }
  }
}

% Title, author, etc
\title{Data Analysis Extensions}
\author{Jerome Soumagne}
\author{Quincey Koziol}
\date{July 17, 2014}
\rfcversion{2014-07-17.v1}
\revision{July 17, 2014}{Version 1 circulated for comment within The HDF Group.}

%% Start the document
\begin{document}

%% Title
\maketitle

%% Abstract
\begin{abstract}
Accessing and retrieving data from an HDF5 container can be a time consuming
process, particularly so when the data is very large. To enable,
ease and accelerate the process of querying data, we introduce in this RFC data
analysis extensions to query, select and index data.
\end{abstract}

\section{Introduction}
Data Analysis Extensions to the HDF5 API and data model can enable application
developers to create complex and high-performance queries on both metadata and
data elements within an HDF5 container and retrieve the results of applying
those query operations to an HDF5 container.
Support for data analysis operations on HDF5 containers can be defined via:
\begin{itemize}
\item New \textit{query} object\footnote{Query and view objects are
\textit{in-memory} objects, which therefore do not modify the content of the
container.\label{fn:object}} and API routines, enabling the construction of
query requests for execution on HDF5 containers;
\item New \textit{view} object\footref{fn:object} and API routines, which apply a query to an HDF5
container and return a set of references into the container that fulfills
the query criteria;
\item New \textit{index} object and API routines, which allows the creation of
indices on the contents of HDF5 containers, to improve query performance.
\end{itemize}

\section{Query Objects}
Query objects are the foundation of the data analysis operations in HDF5 and
can be built up from simple components in a programmatic way to create complex
operations using \textit{Boolean} operations. The core query API is composed of
two routines: \texttt{H5Qcreate} and \texttt{H5Qcombine}. \texttt{H5Qcreate}
creates new queries, by specifying an aspect of an HDF5 container, such as
data elements, link names, attribute names, etc., a match operator, such as
$=$, $\neq$, $\leq$, $\geq$, and a value for the match operator.
\texttt{H5Qcombine} combines two query objects into a
new query object, using Boolean operators such as $AND(\land)$ and $OR(\lor)$.
Queries created with \texttt{H5Qcombine} can be used as input to further
calls to \texttt{H5Qcombine}, creating more complex queries.

For example, a single call to \texttt{H5Qcreate} could create a query object
that would match data elements in any dataset within the container that are
equal to the value $17$. Another call to \texttt{H5Qcreate} could create a
query object that would match link names equal to $Pressure$.
Calling \texttt{H5Qcombine} with the $\land$ operator and those two query
objects would create a new query object that matched elements equal to $17$
in HDF5 datasets with link names equal to $Pressure$.
Creating the data analysis extensions to HDF5 using a \textit{programmatic
interface} for defining queries avoids defining a text-based query language
as a core component of the data analysis interface, and is more in keeping with
the design and level of abstraction of the HDF5 API.
The HDF5 data model is more complex than traditional database tables and a
simpler query model would likely not be able to express the kinds of queries
needed to extract the full set of components of an HDF5 container. A text-based
query language (or GUI) could certainly be built on top of the query API
defined here to provide a more user-friendly (as opposed to
\textit{developer-friendly}) query syntax like $Pressure = 17$. However, we
regard this as out-of-scope for now.

\todo{Add something about parallel queries / multi dataset serial}

\section{View Objects}
Applying a query to an HDF5 container creates an HDF5 view object. HDF5 view
objects are runtime, in-memory objects (i.e., not stored in a container) that
consist of read-only references into the contents of the HDF5 container that
the query was applied to. View objects are created with \texttt{H5Vcreate},
which applies a query to an HDF5 container, group hierarchy, or individual
object and produces the view object as a result. The attributes, objects,
and/or data elements referenced within a view can be retrieved by further API
calls.

For example, starting with the HDF5 container described in
\FigureRef{fig:HDF5File-Checkpoint}:

\begin{figure}
\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint}
\caption{HDF5 container example.}
\label{fig:HDF5File-Checkpoint}
\end{figure}

Applying the $link\_name = Pressure$ query (described above) would result
in the view shown in \FigureRef{fig:HDF5File-Checkpoint-View1}, with the
underlying container grayed out and the view highlighted in green.

\begin{figure}
\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint-View1}
\caption{HDF5 container example with query $link\_name = Pressure$ applied.}
\label{fig:HDF5File-Checkpoint-View1}
\end{figure}

Alternatively, applying the $data\_element = 17$ query (described above) would
result in the view shown in \FigureRef{fig:HDF5File-Checkpoint-View2}, with the
underlying container greyed out and the view highlighted in green.

\begin{figure}
\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint-View2}
\caption{HDF5 container example with query $data\_element = 17$ applied.}
\label{fig:HDF5File-Checkpoint-View2}
\end{figure}

Finally, applying the combined $(link\_name = Pressure)\land(data\_element = 17)$
query (described above) would result in the view shown in
\FigureRef{fig:HDF5File-Checkpoint-View3}, with the underlying container
greyed out and the view highlighted in green.

\begin{figure}
\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint-View3}
\caption{HDF5 container example with query $(link\_name = Pressure)\land(data\_element = 17)$ applied.}
\label{fig:HDF5File-Checkpoint-View3}
\end{figure}

Views can be thought of as containing a set of HDF5 references (object,
dataset region or attribute references) to components of the underlying
container, retaining the context of the original container. For example, the
view containing the results of the $(link\_name = Pressure)\land(data\_element = 17)$
query will contain three dataset region references, which
can be retrieved from the view object and probed for the dataset and selection
containing the elements that match the query with the existing \texttt{H5Rdereference}
and \texttt{H5Rget\_region} API calls. Note that selections returned from a region
reference retain the underlying dataset's dimensionality and coordinates---they
are not \textit{flattened} into a 1-D series of elements. The selection returned
from a region reference can also be applied to a different dataset in the container,
allowing a query on pressure values to be used to extract temperature values,
for example.

\section{Index Objects}
The final component of the data analysis extensions to HDF5 is the index object.
Index objects are designed to accelerate creation of view objects from
frequently occurring query operations.
For example, if the $(link\_name = Pressure)\land(data\_element = 17)$ query
(described above) is going to be frequently executed on the container, indices
could be created in that container, which would speed up the creation of views
when querying for link names and for data element values. Indices created for
accelerating the $link\_name = Pressure$ or $data\_element = 17$ queries
would also improve view creation for the more complex
$(link\_name = Pressure)\land(data\_element = 17)$ query.

Although creating indices for metadata components of queries, such as link or
attribute names, is possible, we focus on index creation for
dataset elements, as they represent the largest volume of data in typical HPC
application usage of HDF5. Queries with metadata components execute properly,
\todo{Must write about metadata indexing} but are not able to be accelerated
with an index currently.

The indexing API works in conjunction with the view API. When an \texttt{H5Vcreate}
call is made for a group or dataset, an index attached to any dataset queried
for element value ranges will be used to speed up the query process and return
a dataspace selection to the library for later use.

There are different techniques for creating data element indices, and the most
efficient method will vary depending on the type of the data that is to be
indexed, its layout, etc. We therefore define a new interface for the HDF5
library that uses a plugin mechanism.

\subsection{Indexing Interface and Plugins}

A new HDF5 interface is defined for adding third-party indexing plugins,
such as FastBit~\cite{Wu05}, ALACRITY~\cite{alacrity13}, etc.
The interface provides indexing plugins with efficient access to the contents of
the container for both the creation and the maintenance of indices. In addition,
the interface allows third-party plugins to create private data structures
within the container for storing the contents of the index.

Index objects are stored in the HDF5 container that they apply to, but are not
visible in the container's group hierarchy\footnote{Plugin developers, note that
the HDF5 library's existing anonymous dataset and group creation calls can be
used to create objects in HDF5 files that are not visible in the container's
group hierarchy.}.
Instead, index objects are part of the metadata for the file itself. New index
objects are created by passing an H5 container to be indexed and the index
plugin ID to the \texttt{H5Xcreate} call.
Index information (such as plugin id and index metadata) is stored at index
creation time\footnote{This therefore introduces a file format change},
and when the user later calls \texttt{H5Dopen}, the plugin open
callback will retrieve this stored information and make use of the corresponding
index plugin for all subsequent operations. Similarly, calling \texttt{H5Dclose}
will call the plugin index close callback and close the objects used to store
the index data.

\begin{figure}
\input{pics/hdf5filestruc}
\caption{HDF5 stores multidimensional arrays (datasets)
  along with metadata in a file. In this case, a dataset is contiguously mapped
  from the application memory to a file, its data structure being described in
  the metadata cache.}
\label{fig:hdf5filestruc}
\end{figure}

When a call to \texttt{H5Dwrite} is made, the index plugin \texttt{pre\_update} and
\texttt{post\_update} callbacks will be triggered, allowing efficient index
update by first telling the index plugin the region that is going to be updated
with new data, and then realizing the actual index update, after the dataset
write has completed. This allows various optimization to be made, depending on
the data selection passed and the index plugin used. For example, a plugin could
store the region and defer the actual index update until the dataset is closed,
hence saving repeated index computation/update calls.

When a call to \texttt{H5Vcreate} is made, the index plugin query callback will be
invoked to create a selection of elements in the dataset that match the query
parameters. Applications can also use the new \texttt{H5Dquery} routine to directly
execute a query on a dataset (accelerated by any index defined on the dataset),
retrieving the selection within that dataset that matches the query.

Because the amount of space taken by the index cannot be directly retrieved by
the user since the datasets storing the indices should be \textit{anonymous}
and not visible from the file hierarchy, we also plan on adding callbacks to
query from a specified dataset the amount of space the index that is attached
to it takes.

\subsubsection{Interface}

{\lstsetc
\begin{lstlisting}
typedef struct {
    unsigned version;     /* Version number of the index plugin class struct */
                          /* (Should always be set to H5X_CLASS_VERSION, which
                           *  may vary between releases of HDF5 library) */
    unsigned id;          /* Index ID (assigned by The HDF Group, for now) */
    const char *idx_name; /* Index name (for debugging only, currently) */
    H5X_type_t type;      /* Type of data indexed by this plugin */

    /* Callbacks, described above */
    void *(*create)(hid_t file_id, hid_t dataset_id, hid_t xcpl_id,
        hid_t xapl_id, size_t *metadata_size, void **metadata);
    herr_t (*remove)(hid_t file_id, hid_t dataset_id, size_t metadata_size,
        void *metadata);
    void *(*open)(hid_t file_id, hid_t dataset_id, hid_t xapl_id,
        size_t metadata_size, void *metadata);
    herr_t (*close)(void *idx_handle);
    herr_t (*pre_update)(void *idx_handle, hid_t dataspace_id, hid_t xxpl_id);
    herr_t (*post_update)(void *idx_handle, const void *buf, hid_t dataspace_id,
            hid_t xxpl_id);
    herr_t (*query)(void *idx_handle, hid_t query_id, hid_t xxpl_id,
        hid_t *dataspace_id);
    herr_t (*refresh)(void *idx_handle, size_t *metadata_size, void **metadata);
} H5X_class_t;
\end{lstlisting}
}

\subsubsection{Current and future plugins}

Current implementations for FastBit and ALACRITY index packages are already
present, as well as a brute force indexing plugin. In the future more plugins
will be added, with and without external dependency.
To satisfy that need, dynamic plugin loading and registration will be supported,
allowing external libraries to plug to the current interface.
\todo{pytable indexing?}

\subsection{Limitations}

There are some existing limitations in the use of indices in the current
implementation: FastBit and
ALACRITY do not support incremental updates, an index is a shared resource for
a dataset. Taken together, these conspire to put limits on application updates
to datasets with indices.
Additionally, because FastBit and Alacrity don't allow incremental updates to
an index, each modification to an existing index forces the index to be entirely
rebuilt. The limitation in FastBit and Alacrity will need to be addressed in
the base packages' implementation, so that they can make incremental updates
to their index information.

\subsubsection*{Questions}
Some questions are still open regarding the handling on indices:
\begin{itemize}
\item How could an index be built in parallel for a dataset that already exists?
\item How to handle index updates when the specified index plugin is not available?
(In traditional databases, stored procedures are saved with the data and
therefore available at any time, but that is not the case here)
\item How to handle index queries when the specified index plugin is not
available?
\end{itemize}

\section{HDF5 and tools}

Existing HDF5 tools must be compatible and take into account the existence of
indices in the file if there are any. For reference, the following behavior for
the tools is given:

\begin{itemize}
\item h5dump: report index information
\item h5ls: report index information
\item h5diff: ignore index information?
\item h5repack: copy index information
\item h5edit: ignore index information?
\item h5toh4: ignore index information?
\item h5import: copy index information
\end{itemize}

\section{Usage Example}

In the following example, we show how one can make use of the query and
indexing interface to get a dataspace selection within a dataset,
for simplicity we first create a dataset within the file, then open it to
create and attach a new index, to finally query data from it.

{\lstsetc
\begin{lstlisting}
#define NTUPLES 256

int
main(int argc, char *argv[])
{
    float data[NTUPLES];
    hsize_t dims[1] = {NTUPLES};
    hid_t t file_id, dataspace_id, dataset_id;
    hid_t query_id, result_space_id;
    size_t result_npoints;
    float *result;
    int i;

    /* Initialize data. */
    for(i = 0; i < NTUPLES; i++) data[i] = (float) i;

    /* Create file. */
    file_id = H5Fcreate(file_name, H5F_ACC_TRUNC, H5P_DEFAULT, H5P_DEFAULT);

    /* Create the data space for the dataset. */
    dataspace_id = H5Screate_simple(rank, dims, NULL);

    /* Create dataset. */
    dataset_id = H5Dcreate(file_id, "Pressure", H5T_NATIVE_FLOAT, dataspace_id,
        H5P_DEFAULT, H5P_DEFAULT, H5P_DEFAULT);

    /* Write dataset. */
    H5Dwrite(dataset_id, H5T_NATIVE_FLOAT, H5S_ALL, H5S_ALL, H5P_DEFAULT, data);

    /* Close the dataset. */
    H5Dclose(dataset_id);

    /* Close dataspace. */
    H5Sclose(dataspace_id);

    /* Open dataset. */
    dataset_id = H5Dopen(file_id, "Pressure", H5P_DEFAULT);

    /* Create index using FastBit. */
    H5Xcreate(file_id, H5X_PLUGIN_FASTBIT, dataset_id, H5P_DEFAULT);

    /* Close the dataset. */
    H5Dclose(dataset_id);

    /* Create a simple query */
    query_id = H5Qcreate(H5Q_TYPE_DATA_ELEM, H5Q_MATCH_EQUAL, H5T_NATIVE_FLOAT,
        &query_value);

    /* Open dataset. */
    dataset_id = H5Dopen(file_id, "Pressure", H5P_DEFAULT);

    /* Use query to select elements in the dataset. */
    result_space_id = H5Dquery(dataset_id, query_id);

    /* Allocate space to read data. */ 
    result_npoints = (size_t) H5Sget_select_npoints(result_space_id);
    result = malloc(result_npoints * sizeof(float));

    /* Read data using result_space_id. */
    H5Dread(dataset_id, H5T_NATIVE_FLOAT, H5S_ALL, result_space_id,
        H5P_DEFAULT, result);

    /* Use result. */

    /* Free result. */
    free(result);

    /* Close the dataset. */
    H5Dclose(dataset_id);

    /* Close dataspace. */
    H5Sclose(result_space_id);

    /* Close query. */
    H5Qclose(query_id);

    /* Close the file. */
    H5Fclose(file_id);
}
\end{lstlisting}
}

\section{Conclusion}

%% Close
\section*{Revision History}
\makerevisions

%% References
\bibliographystyle{ieeetr}
\bibliography{analysis_ext}

\end{document}

### 2014-07-24 RFCs/HDF5_Library/AnalysisExt/pics/hdf5filestruc.tex
Add RFC for data analysis extensions and LaTeX RFC class
Former-commit-id: e82513630e4c2b091a59db685e8c601209f84007

\tikzstyle{textBox}    = [rectangle, text centered, font=\small \bfseries]
\tikzstyle{appBox}     = [draw, rectangle, rounded corners, fill=white, dashed, very thick]
\tikzstyle{fileBox}    = [draw, rectangle, fill=white, drop shadow={opacity=0.25}]
\tikzstyle{headerBox}  = [draw, rectangle, fill=rulecolor, font=\footnotesize]
\tikzstyle{dataBox}    = [draw, rectangle, thick, fill=white, pattern color=rulecolor, pattern=dots, font=\small]
\tikzstyle{cacheBox}   = [draw, rectangle, thick, fill=black!10, drop shadow={opacity=0.25}]
\tikzstyle{cacheBoxes} = [draw, tape, tape bend top=none, fill=rulecolor, double copy shadow]

%\tikzstyle{trans} = [->, >=stealth, thick, text centered, font=\footnotesize]
\tikzstyle{message} = [draw=blue, ->, very thick, shorten <=2pt, shorten >=2pt, 
  text centered, text width=2.5cm, font=\footnotesize]

\begin{tikzpicture}

\node[appBox, minimum height=4cm, minimum width=14cm] (app) {};
\node[textBox, minimum height=1cm, minimum width=2cm, below left=2mm of app.north east] (apptitle) {Application memory};
\node[cacheBox, minimum height=3.6cm, minimum width=6.4cm, right=2mm of app.west] (cache) {};
\node[rectangle, minimum height=3.6cm, minimum width=2.9cm, right=2mm of cache.west] (cachecol1) {};
\node[rectangle, minimum height=3.6cm, minimum width=2.9cm, right=2mm of cachecol1.east] (cachecol2) {};
\node[headerBox, minimum width=2.5cm, minimum height=0.7cm, below=1.7mm of cachecol1.north] (cache1) {Dataset header};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache1] (cache2) {\dots};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache2] (cache3) {Datatype};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache3] (cache4) {Dataspace};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache4] (cache5) {\dots};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache5] (cache6) {Attributes};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache6] (cache7) {\dots};

\node[textBox, minimum height=1cm, minimum width=2cm, below=1mm of cachecol2.north] (cachetitle) {Metadata cache};
\node[cacheBoxes, below=1.5cm of cachecol2.north, minimum width=2cm, minimum height=1cm] () {};

\node[fileBox, minimum height=1cm, minimum width=14cm, below=5mm of app] (file) {};
\node[textBox, minimum height=1cm, minimum width=2cm, right=4mm of file.west] (filetitle) {File};
\node[headerBox, thick, minimum height=1cm, minimum width=1cm, right=1.5cm of filetitle] (fileheader) {};
\node[dataBox, minimum height=1cm, minimum width=5cm, right=3cm of fileheader] (filedata) {Dataset data};

\node[rectangle, fill=white, minimum height=1cm, minimum width=5cm, above=2cm of filedata, drop shadow={opacity=0.25}] () {};
\node[dataBox, minimum height=1cm, minimum width=5cm, above=2cm of filedata] (appdata) {Dataset data};

\draw[message] (cache7.east) -| (fileheader.north);
\draw[message] (appdata.south west) -- (filedata.north west);
\draw[message] (appdata.south east) -- (filedata.north east);

\end{tikzpicture}

### 2014-07-29 RFCs/HDF5_Library/tex_template/rfc_template.tex
add an RFC template based on the RFC that Jerome generated for Analysis shipping.
Former-commit-id: 28e2890b0ff925e94771f8df87261608ae6b4028

--- 2014-07-24 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
@@
   commentstyle=\itshape\bfseries,
-  morekeywords={main, size_t, malloc, free,
-    hsize_t, hid_t, herr_t, H5X_class_t, H5X_type_t,
-    H5Fcreate, H5Fclose,
-    H5Dcreate, H5Dopen, H5Dclose, H5Dwrite, H5Dread, H5Dquery,
-    H5Qcreate, H5Qclose,
-    H5Screate_simple, H5Sclose, H5Sget_select_npoints,
-    H5Xcreate
-    }
+  morekeywords={RFC, template}
   }
@@
 % Title, author, etc
-\title{Data Analysis Extensions}
-\author{Jerome Soumagne}
-\author{Quincey Koziol}
-\date{July 17, 2014}
-\rfcversion{2014-07-17.v1}
-\revision{July 17, 2014}{Version 1 circulated for comment within The HDF Group.}
+\title{Title}
+\author{Author1}
+\author{Author2}
+\date{July 29, 2014}
+\rfcversion{2014-07-29.v1}
+\revision{July 29, 2014}{Version 1 circulated for comment within The HDF Group.}
 
@@
 \begin{abstract}
-Accessing and retrieving data from an HDF5 container can be a time consuming
-process, particularly so when the data is very large. To enable,
-ease and accelerate the process of querying data, we introduce in this RFC data
-analysis extensions to query, select and index data.
+First, have an abstract.
+Briefly describe the reason for the RFC and the recommendation it makes.
+Provide just enough information to let the reader decide if they should keep reading, or if RFC is of no interest to them.
 \end{abstract}
@@
 \section{Introduction}
-Data Analysis Extensions to the HDF5 API and data model can enable application
-developers to create complex and high-performance queries on both metadata and
-data elements within an HDF5 container and retrieve the results of applying
-those query operations to an HDF5 container.
-Support for data analysis operations on HDF5 containers can be defined via:
-\begin{itemize}
-\item New \textit{query} object\footnote{Query and view objects are
-\textit{in-memory} objects, which therefore do not modify the content of the
-container.\label{fn:object}} and API routines, enabling the construction of
-query requests for execution on HDF5 containers;
-\item New \textit{view} object\footref{fn:object} and API routines, which apply a query to an HDF5
-container and return a set of references into the container that fulfills
-the query criteria;
-\item New \textit{index} object and API routines, which allows the creation of
-indices on the contents of HDF5 containers, to improve query performance.
-\end{itemize}
+Every RFC should have an introduction.
+Tell the reader about the problem this RFC is designed to address, or the enhancement it will provide.
+The introduction should give the reader enough background that they can decide if they want to keep reading.
 
-\section{Query Objects}
-Query objects are the foundation of the data analysis operations in HDF5 and
-can be built up from simple components in a programmatic way to create complex
-operations using \textit{Boolean} operations. The core query API is composed of
-two routines: \texttt{H5Qcreate} and \texttt{H5Qcombine}. \texttt{H5Qcreate}
-creates new queries, by specifying an aspect of an HDF5 container, such as
-data elements, link names, attribute names, etc., a match operator, such as
-$=$, $\neq$, $\leq$, $\geq$, and a value for the match operator.
-\texttt{H5Qcombine} combines two query objects into a
-new query object, using Boolean operators such as $AND(\land)$ and $OR(\lor)$.
-Queries created with \texttt{H5Qcombine} can be used as input to further
-calls to \texttt{H5Qcombine}, creating more complex queries.
+\section{Approach / Motivation / Etc.}
+Typically the first section after the Introduction will go into motivation in more depth, talk about approach or whatever you want.
+There is no requirement for the actual Section name.
+It may have subsections.
+Do what makes sense for your RFC.
 
-For example, a single call to \texttt{H5Qcreate} could create a query object
-that would match data elements in any dataset within the container that are
-equal to the value $17$. Another call to \texttt{H5Qcreate} could create a
-query object that would match link names equal to $Pressure$.
-Calling \texttt{H5Qcombine} with the $\land$ operator and those two query
-objects would create a new query object that matched elements equal to $17$
-in HDF5 datasets with link names equal to $Pressure$.
-Creating the data analysis extensions to HDF5 using a \textit{programmatic
-interface} for defining queries avoids defining a text-based query language
-as a core component of the data analysis interface, and is more in keeping with
-the design and level of abstraction of the HDF5 API.
-The HDF5 data model is more complex than traditional database tables and a
-simpler query model would likely not be able to express the kinds of queries
-needed to extract the full set of components of an HDF5 container. A text-based
-query language (or GUI) could certainly be built on top of the query API
-defined here to provide a more user-friendly (as opposed to
-\textit{developer-friendly}) query syntax like $Pressure = 17$. However, we
-regard this as out-of-scope for now.
+\section{Standard Parts of the Template}
 
-\todo{Add something about parallel queries / multi dataset serial}
-
-\section{View Objects}
-Applying a query to an HDF5 container creates an HDF5 view object. HDF5 view
-objects are runtime, in-memory objects (i.e., not stored in a container) that
-consist of read-only references into the contents of the HDF5 container that
-the query was applied to. View objects are created with \texttt{H5Vcreate},
-which applies a query to an HDF5 container, group hierarchy, or individual
-object and produces the view object as a result. The attributes, objects,
-and/or data elements referenced within a view can be retrieved by further API
-calls.
-
-For example, starting with the HDF5 container described in
-\FigureRef{fig:HDF5File-Checkpoint}:
-
-\begin{figure}
-\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint}
-\caption{HDF5 container example.}
-\label{fig:HDF5File-Checkpoint}
-\end{figure}
-
-Applying the $link\_name = Pressure$ query (described above) would result
-in the view shown in \FigureRef{fig:HDF5File-Checkpoint-View1}, with the
-underlying container grayed out and the view highlighted in green.
-
-\begin{figure}
-\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint-View1}
-\caption{HDF5 container example with query $link\_name = Pressure$ applied.}
-\label{fig:HDF5File-Checkpoint-View1}
-\end{figure}
-
-Alternatively, applying the $data\_element = 17$ query (described above) would
-result in the view shown in \FigureRef{fig:HDF5File-Checkpoint-View2}, with the
-underlying container greyed out and the view highlighted in green.
-
-\begin{figure}
-\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint-View2}
-\caption{HDF5 container example with query $data\_element = 17$ applied.}
-\label{fig:HDF5File-Checkpoint-View2}
-\end{figure}
-
-Finally, applying the combined $(link\_name = Pressure)\land(data\_element = 17)$
-query (described above) would result in the view shown in
-\FigureRef{fig:HDF5File-Checkpoint-View3}, with the underlying container
-greyed out and the view highlighted in green.
-
-\begin{figure}
-\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint-View3}
-\caption{HDF5 container example with query $(link\_name = Pressure)\land(data\_element = 17)$ applied.}
-\label{fig:HDF5File-Checkpoint-View3}
-\end{figure}
-
-Views can be thought of as containing a set of HDF5 references (object,
-dataset region or attribute references) to components of the underlying
-container, retaining the context of the original container. For example, the
-view containing the results of the $(link\_name = Pressure)\land(data\_element = 17)$
-query will contain three dataset region references, which
-can be retrieved from the view object and probed for the dataset and selection
-containing the elements that match the query with the existing \texttt{H5Rdereference}
-and \texttt{H5Rget\_region} API calls. Note that selections returned from a region
-reference retain the underlying dataset's dimensionality and coordinates---they
-are not \textit{flattened} into a 1-D series of elements. The selection returned
-from a region reference can also be applied to a different dataset in the container,
-allowing a query on pressure values to be used to extract temperature values,
-for example.
-
-\section{Index Objects}
-The final component of the data analysis extensions to HDF5 is the index object.
-Index objects are designed to accelerate creation of view objects from
-frequently occurring query operations.
-For example, if the $(link\_name = Pressure)\land(data\_element = 17)$ query
-(described above) is going to be frequently executed on the container, indices
-could be created in that container, which would speed up the creation of views
-when querying for link names and for data element values. Indices created for
-accelerating the $link\_name = Pressure$ or $data\_element = 17$ queries
-would also improve view creation for the more complex
-$(link\_name = Pressure)\land(data\_element = 17)$ query.
-
-Although creating indices for metadata components of queries, such as link or
-attribute names, is possible, we focus on index creation for
-dataset elements, as they represent the largest volume of data in typical HPC
-application usage of HDF5. Queries with metadata components execute properly,
-\todo{Must write about metadata indexing} but are not able to be accelerated
-with an index currently.
-
-The indexing API works in conjunction with the view API. When an \texttt{H5Vcreate}
-call is made for a group or dataset, an index attached to any dataset queried
-for element value ranges will be used to speed up the query process and return
-a dataspace selection to the library for later use.
-
-There are different techniques for creating data element indices, and the most
-efficient method will vary depending on the type of the data that is to be
-indexed, its layout, etc. We therefore define a new interface for the HDF5
-library that uses a plugin mechanism.
-
-\subsection{Indexing Interface and Plugins}
-
-A new HDF5 interface is defined for adding third-party indexing plugins,
-such as FastBit~\cite{Wu05}, ALACRITY~\cite{alacrity13}, etc.
-The interface provides indexing plugins with efficient access to the contents of
-the container for both the creation and the maintenance of indices. In addition,
-the interface allows third-party plugins to create private data structures
-within the container for storing the contents of the index.
-
-Index objects are stored in the HDF5 container that they apply to, but are not
-visible in the container's group hierarchy\footnote{Plugin developers, note that
-the HDF5 library's existing anonymous dataset and group creation calls can be
-used to create objects in HDF5 files that are not visible in the container's
-group hierarchy.}.
-Instead, index objects are part of the metadata for the file itself. New index
-objects are created by passing an H5 container to be indexed and the index
-plugin ID to the \texttt{H5Xcreate} call.
-Index information (such as plugin id and index metadata) is stored at index
-creation time\footnote{This therefore introduces a file format change},
-and when the user later calls \texttt{H5Dopen}, the plugin open
-callback will retrieve this stored information and make use of the corresponding
-index plugin for all subsequent operations. Similarly, calling \texttt{H5Dclose}
-will call the plugin index close callback and close the objects used to store
-the index data.
-
-\begin{figure}
-\input{pics/hdf5filestruc}
-\caption{HDF5 stores multidimensional arrays (datasets)
-  along with metadata in a file. In this case, a dataset is contiguously mapped
-  from the application memory to a file, its data structure being described in
-  the metadata cache.}
-\label{fig:hdf5filestruc}
-\end{figure}
-
-When a call to \texttt{H5Dwrite} is made, the index plugin \texttt{pre\_update} and
-\texttt{post\_update} callbacks will be triggered, allowing efficient index
-update by first telling the index plugin the region that is going to be updated
-with new data, and then realizing the actual index update, after the dataset
-write has completed. This allows various optimization to be made, depending on
-the data selection passed and the index plugin used. For example, a plugin could
-store the region and defer the actual index update until the dataset is closed,
-hence saving repeated index computation/update calls.
-
-When a call to \texttt{H5Vcreate} is made, the index plugin query callback will be
-invoked to create a selection of elements in the dataset that match the query
-parameters. Applications can also use the new \texttt{H5Dquery} routine to directly
-execute a query on a dataset (accelerated by any index defined on the dataset),
-retrieving the selection within that dataset that matches the query.
-
-Because the amount of space taken by the index cannot be directly retrieved by
-the user since the datasets storing the indices should be \textit{anonymous}
-and not visible from the file hierarchy, we also plan on adding callbacks to
-query from a specified dataset the amount of space the index that is attached
-to it takes.
-
-\subsubsection{Interface}
-
-{\lstsetc
-\begin{lstlisting}
-typedef struct {
-    unsigned version;     /* Version number of the index plugin class struct */
-                          /* (Should always be set to H5X_CLASS_VERSION, which
-                           *  may vary between releases of HDF5 library) */
-    unsigned id;          /* Index ID (assigned by The HDF Group, for now) */
-    const char *idx_name; /* Index name (for debugging only, currently) */
-    H5X_type_t type;      /* Type of data indexed by this plugin */
-
-    /* Callbacks, described above */
-    void *(*create)(hid_t file_id, hid_t dataset_id, hid_t xcpl_id,
-        hid_t xapl_id, size_t *metadata_size, void **metadata);
-    herr_t (*remove)(hid_t file_id, hid_t dataset_id, size_t metadata_size,
-        void *metadata);
-    void *(*open)(hid_t file_id, hid_t dataset_id, hid_t xapl_id,
-        size_t metadata_size, void *metadata);
-    herr_t (*close)(void *idx_handle);
-    herr_t (*pre_update)(void *idx_handle, hid_t dataspace_id, hid_t xxpl_id);
-    herr_t (*post_update)(void *idx_handle, const void *buf, hid_t dataspace_id,
-            hid_t xxpl_id);
-    herr_t (*query)(void *idx_handle, hid_t query_id, hid_t xxpl_id,
-        hid_t *dataspace_id);
-    herr_t (*refresh)(void *idx_handle, size_t *metadata_size, void **metadata);
-} H5X_class_t;
-\end{lstlisting}
-}
-
-\subsubsection{Current and future plugins}
-
-Current implementations for FastBit and ALACRITY index packages are already
-present, as well as a brute force indexing plugin. In the future more plugins
-will be added, with and without external dependency.
-To satisfy that need, dynamic plugin loading and registration will be supported,
-allowing external libraries to plug to the current interface.
-\todo{pytable indexing?}
-
-\subsection{Limitations}
-
-There are some existing limitations in the use of indices in the current
-implementation: FastBit and
-ALACRITY do not support incremental updates, an index is a shared resource for
-a dataset. Taken together, these conspire to put limits on application updates
-to datasets with indices.
-Additionally, because FastBit and Alacrity don't allow incremental updates to
-an index, each modification to an existing index forces the index to be entirely
-rebuilt. The limitation in FastBit and Alacrity will need to be addressed in
-the base packages' implementation, so that they can make incremental updates
-to their index information.
-
-\subsubsection*{Questions}
-Some questions are still open regarding the handling on indices:
-\begin{itemize}
-\item How could an index be built in parallel for a dataset that already exists?
-\item How to handle index updates when the specified index plugin is not available?
-(In traditional databases, stored procedures are saved with the data and
-therefore available at any time, but that is not the case here)
-\item How to handle index queries when the specified index plugin is not
-available?
-\end{itemize}
-
-\section{HDF5 and tools}
-
-Existing HDF5 tools must be compatible and take into account the existence of
-indices in the file if there are any. For reference, the following behavior for
-the tools is given:
-
-\begin{itemize}
-\item h5dump: report index information
-\item h5ls: report index information
-\item h5diff: ignore index information?
-\item h5repack: copy index information
-\item h5edit: ignore index information?
-\item h5toh4: ignore index information?
-\item h5import: copy index information
-\end{itemize}
-
-\section{Usage Example}
-
-In the following example, we show how one can make use of the query and
-indexing interface to get a dataspace selection within a dataset,
-for simplicity we first create a dataset within the file, then open it to
-create and attach a new index, to finally query data from it.
-
-{\lstsetc
-\begin{lstlisting}
-#define NTUPLES 256
-
-int
-main(int argc, char *argv[])
-{
-    float data[NTUPLES];
-    hsize_t dims[1] = {NTUPLES};
-    hid_t t file_id, dataspace_id, dataset_id;
-    hid_t query_id, result_space_id;
-    size_t result_npoints;
-    float *result;
-    int i;
-
-    /* Initialize data. */
-    for(i = 0; i < NTUPLES; i++) data[i] = (float) i;
-
-    /* Create file. */
-    file_id = H5Fcreate(file_name, H5F_ACC_TRUNC, H5P_DEFAULT, H5P_DEFAULT);
-
-    /* Create the data space for the dataset. */
-    dataspace_id = H5Screate_simple(rank, dims, NULL);
-
-    /* Create dataset. */
-    dataset_id = H5Dcreate(file_id, "Pressure", H5T_NATIVE_FLOAT, dataspace_id,
-        H5P_DEFAULT, H5P_DEFAULT, H5P_DEFAULT);
-
-    /* Write dataset. */
-    H5Dwrite(dataset_id, H5T_NATIVE_FLOAT, H5S_ALL, H5S_ALL, H5P_DEFAULT, data);
-
-    /* Close the dataset. */
-    H5Dclose(dataset_id);
-
-    /* Close dataspace. */
-    H5Sclose(dataspace_id);
-
-    /* Open dataset. */
-    dataset_id = H5Dopen(file_id, "Pressure", H5P_DEFAULT);
-
-    /* Create index using FastBit. */
-    H5Xcreate(file_id, H5X_PLUGIN_FASTBIT, dataset_id, H5P_DEFAULT);
-
-    /* Close the dataset. */
-    H5Dclose(dataset_id);
-
-    /* Create a simple query */
-    query_id = H5Qcreate(H5Q_TYPE_DATA_ELEM, H5Q_MATCH_EQUAL, H5T_NATIVE_FLOAT,
-        &query_value);
-
-    /* Open dataset. */
-    dataset_id = H5Dopen(file_id, "Pressure", H5P_DEFAULT);
-
-    /* Use query to select elements in the dataset. */
-    result_space_id = H5Dquery(dataset_id, query_id);
-
-    /* Allocate space to read data. */ 
-    result_npoints = (size_t) H5Sget_select_npoints(result_space_id);
-    result = malloc(result_npoints * sizeof(float));
-
-    /* Read data using result_space_id. */
-    H5Dread(dataset_id, H5T_NATIVE_FLOAT, H5S_ALL, result_space_id,
-        H5P_DEFAULT, result);
-
-    /* Use result. */
-
-    /* Free result. */
-    free(result);
-
-    /* Close the dataset. */
-    H5Dclose(dataset_id);
-
-    /* Close dataspace. */
-    H5Sclose(result_space_id);
-
-    /* Close query. */
-    H5Qclose(query_id);
-
-    /* Close the file. */
-    H5Fclose(file_id);
-}
-\end{lstlisting}
-}
-
-\section{Conclusion}
+\section{Recommendation}
 
@@
 %% References
-\bibliographystyle{ieeetr}
-\bibliography{analysis_ext}
+%\bibliographystyle{ieeetr}
+%\bibliography{}
 

### 2014-07-29 RFCs/HDF5_Library/tex_template/rfc_template.tex
Cleanup rfc_template.tex
Former-commit-id: cbe04f14c895dfee9bfeffc8e618575760d91d09

@@
 % Fonts
-\usepackage{ifluatex}
-\ifluatex
-  % Font
-  \usepackage{luatextra, xunicode, unicode-math}
-  \defaultfontfeatures{Ligatures=TeX}
-  \setmainfont[
-    UprightFont={*},
-    BoldFont={* Bold},
-    ItalicFont={* Italic},
-    BoldItalicFont={* Bold Italic}
-  ]{STIX}
-  \setsansfont[
-    UprightFont={*},
-    BoldFont={* Bold},
-    ItalicFont={* Italic},
-    BoldItalicFont={* Bold Italic}
-  ]{Source Sans Pro}
-  \setmathfont[math-style=ISO, bold-style=ISO]{Latin Modern Math}
-  \setmonofont[
-    UprightFont={*},
-    BoldFont={* Bold},
-    ItalicFont={* Oblique},
-    BoldItalicFont={* Bold Oblique}
-  ]{DejaVu Sans Mono}
-\else
 \usepackage{lmodern} % times / lmodern / mathpazo / palatino
@@
 \usepackage{courier}
-\fi
 
@@
 \graphicspath{{./pics/}{./plots/}}
-
-%% TikZ
-\usepackage{tikz}
-\usetikzlibrary{patterns, shapes, shadows}
 

### 2014-07-29 RFCs/HDF5_Library/H5Fis_accessible/h5fis_accessible.tex
Add RFC for H5Fis_accessible
Former-commit-id: 9650e7e29699abbd5eb87f2d6e663ee633145a21

\documentclass[letterpaper,hyper]{THG_RFC}

% Fonts
\usepackage{ifluatex}
\ifluatex
  % Font
  \usepackage{luatextra, xunicode, unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont[
    UprightFont={*},
    BoldFont={* Bold},
    ItalicFont={* Italic},
    BoldItalicFont={* Bold Italic}
  ]{STIX}
  \setsansfont[
    UprightFont={*},
    BoldFont={* Bold},
    ItalicFont={* Italic},
    BoldItalicFont={* Bold Italic}
  ]{Source Sans Pro}
  \setmathfont[math-style=ISO, bold-style=ISO]{Latin Modern Math}
  \setmonofont[
    UprightFont={*},
    BoldFont={* Bold},
    ItalicFont={* Oblique},
    BoldItalicFont={* Bold Oblique}
  ]{DejaVu Sans Mono}
\else
  \usepackage{lmodern} % times / lmodern / mathpazo / palatino
  \usepackage[scaled=.95]{helvet}
  \usepackage{courier}
\fi

% Path to figures, plots
\graphicspath{{./pics/}{./plots/}}

%% TikZ
\usepackage{tikz}
\usetikzlibrary{patterns, shapes, shadows}

% Code snippets
\usepackage{listings}
\def\lstsetc{\lstset{language=C,
  numbers=left,
  xleftmargin=20pt,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  showspaces=false, 
  showstringspaces=false,
  breaklines=true,
  basicstyle=\footnotesize\ttfamily,
  stringstyle=\itshape,
  commentstyle=\itshape\bfseries,
  morekeywords={H5Fis_accessible, H5Fis_HDF5}
  }
}

% Title, author, etc
\title{Replacing {\tt H5Fis\_hdf5()} with {\tt H5Fis\_accessible()}}
\author{Mohamad Chaarawi}
\author{Quincey Koziol}
\date{July 29, 2014}
\rfcversion{2014-07-29.v1}
\revision{July 29, 2014}{Version 1 circulated for comment within The HDF Group.}

%% Start the document
\begin{document}

%% Title
\maketitle

%% Abstract
\begin{abstract}
The HDF5 library provides a routine ({\tt H5Fis\_hdf5()}) to determine whether a given file is in the HDF5 format or not given the file name. This API routine is not robust however, and can be considered a bug in the API, because it only uses the default file driver when attempting to open the file. Furthermore, with the introduction of the HDF5 Virtual Object Layer (VOL), all HDF5 files that have not been created through the native HDF5 VOL plugin will not be in the HDF5 file format, but they are still accessible from the HDF5 library. We propose to address the two concerns outlined above by adding a new routine, {\tt H5Fis\_accessible()}, to eventually replace {\tt H5Fis\_hdf5()} in the HDF5 library.
\end{abstract}

\section{Introduction and Motivation}
The HDF5 library provides users with a routine to check whethere a given file is in the HDF5 file format, and the HDF5 library is capable of opening it. This routine is defined as:
\begin{lstlisting}
htri_t H5Fis_hdf5(const char *name);
\end{lstlisting}
When successful, this routines returns a positive value, for TRUE, or 0 (zero), for FALSE. On any error, including the case that the file does not exist, it returns a negative value.

This routine is not robust enough to check HDF5 files created by a driver different than the HDF5 default SEC2 virtual file driver (VFD). If an HDF5 file is created with a family file driver for example, the routine will incorrectly return false when invoked with the file name, even though the file is in the HDF5 file format.

A new feature that will make it into the HDF5 1.10 series is the ability to created HDF5 files that are accessible through the HDF5 API but with a different file format than the native file format. Another problem with the {\tt H5Fis\_hdf5()} function as it stands is that it would not handle such files/containers in non-native HDF5 format. The API currently does not provide an alternative for such a routine to work on files created by the non-native VOL plugin.

\section{Approach}
We propose to add a new routine to address the concerns detailed in the earlier section. The new routine will be defined as:
\begin{lstlisting}
htri_t H5Fis_accessible(const char *name, hid_t fapl_id);
\end{lstlisting}
This routine checks whether a given file can be opened with the given file access property list ({\tt fapl\_id}). When successful, this routines returns a positive value, for TRUE, or 0 (zero), for FALSE. On any error, including the case that the file does not exist, it returns a negative value.

The additional {\tt fapl\_id} argument would be used to tell the library what VFD or VOL plugin to use to try and open the file to see if it is accessible. For example, the user could call {\tt H5Pset\_fapl\_family()} on the {\tt fapl\_id} to check if a given file can be accessed with the family file driver.

We decided to change the name of the function rather than fix the old function by adding the {\tt fapl\_id} argument for bacward compatibilty issues and the better representation of what the function does with the new name.

\section{Implementation and Recommendation}
A protoype implementation for {\tt H5Fis\_accessible()} is done and available for testing in the VOL branch located here:
{\url http://svn.hdfgroup.uiuc.edu/hdf5/features/vol}.
New tests have been added to verify that the routine works with the different VFDs that ship with the HDF5 library.

We recommend to add this new routine to the trunk and the 1.8 branch and deprecate {\tt H5Fis\_hdf5()} since the former is a more robust version of the latter.

%% Close
\section*{Revision History}
\makerevisions

%% References
%\bibliographystyle{ieeetr}
%\bibliography{}

\end{document}

### 2014-07-30 RFCs/HDF5_Library/H5Fis_accessible/h5fis_accessible.tex
Former-commit-id: 11d6d77d1f8010905bbf9b2de2536b3266a3bd43

@@
 This API routine is not robust however, and can be considered a bug in the API, because it only uses the default file driver when attempting to open the file.
-Furthermore, with the introduction of the HDF5 Virtual Object Layer (VOL), all HDF5 files that have not been created through the native HDF5 VOL plugin will not be in the HDF5 file format, but they are still accessible from the HDF5 library.
+Furthermore, with the introduction of the HDF5 Virtual Object Layer (VOL)~\cite{vol-rfc}, all HDF5 files that have not been created through the native HDF5 VOL plugin will not be in the HDF5 file format, but they are still accessible from the HDF5 library.
 We propose to address the two concerns outlined above by adding a new routine, {\tt H5Fis\_accessible()}, to eventually replace {\tt H5Fis\_hdf5()} in the HDF5 library.
@@
 
-We decided to change the name of the function rather than fix the old function by adding the {\tt fapl\_id} argument for bacward compatibilty issues and the better representation of what the function does with the new name.
+We decided to change the name of the function rather than fix the old function by adding the {\tt fapl\_id} argument for backward compatibilty issues and the better representation of what the function does with the new name.
 
@@
 %% References
-%\bibliographystyle{ieeetr}
-%\bibliography{}
+\bibliographystyle{ieeetr}
+\bibliography{h5fis_accessible}
 

### 2014-08-18 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Updates to analysis RFC
Former-commit-id: 6fb57a85f099a15da82e1a2b3d94ecf88385f5c0

@@
     ItalicFont={* Italic},
-    BoldItalicFont={* Bold Italic}
-  ]{STIX}
+    BoldItalicFont={* Bold Italic},
+    SlantedFont={* Italic},
+    BoldSlantedFont={* Bold Italic}
+  ]{Calibri}
   \setsansfont[
@@
     BoldItalicFont={* Bold Italic}
-  ]{Source Sans Pro}
-  \setmathfont[math-style=ISO, bold-style=ISO]{Latin Modern Math}
+  ]{Calibri}
+  \setmathfont[math-style=ISO, bold-style=ISO]{Asana Math}
   \setmonofont[
@@
     BoldFont={* Bold},
-    ItalicFont={* Oblique},
-    BoldItalicFont={* Bold Oblique}
-  ]{DejaVu Sans Mono}
+    ItalicFont={* Italic},
+    BoldItalicFont={* Bold Italic}
+  ]{Courier New}
 \else
@@
 \usepackage{tikz}
-\usetikzlibrary{patterns, shapes, shadows}
+\usetikzlibrary{patterns, shapes, decorations.pathreplacing}
+\usepackage{gnuplot-lua-tikz}
+
+% SI units
+%\usepackage{textcomp}
+\usepackage[binary-units]{siunitx}
+\sisetup{per-mode = symbol}
+\providecommand{\gbps}[1]{\SI{#1}{\giga\byte\per\second}}
+\providecommand{\mbps}[1]{\SI{#1}{\mega\byte\per\second}}
+\providecommand{\gb}[1]{\SI{#1}{\giga\byte}}
+\providecommand{\mb}[1]{\SI{#1}{\mega\byte}}
+\providecommand{\kb}[1]{\SI{#1}{\kilo\byte}}
 
@@
   morekeywords={main, size_t, malloc, free,
-    hsize_t, hid_t, herr_t, H5X_class_t, H5X_type_t,
+    hsize_t, hid_t, herr_t, H5X_class_t, H5X_type_t, H5Q_combine_op_t,
+    H5Q_type_t, H5Q_match_op_t,
     H5Fcreate, H5Fclose,
     H5Dcreate, H5Dopen, H5Dclose, H5Dwrite, H5Dread, H5Dquery,
-    H5Qcreate, H5Qclose,
+    H5Qcreate, H5Qclose, H5Qcombine, H5Qget_type, H5Qget_match_op,
+    H5Qget_components, H5Qget_combine_op, H5Qencode, H5Qdecode,
     H5Screate_simple, H5Sclose, H5Sget_select_npoints,
-    H5Xcreate
+    H5Xregister, H5Xunregister, H5Xcreate, H5Xremove, H5Xget_count
     }
@@
 
+%% Add Attribute reference RFC
+
 %% Title
@@
 Accessing and retrieving data from an HDF5 container can be a time consuming
-process, particularly so when the data is very large. To enable,
+process, particularly so when data is very large. To enable,
 ease and accelerate the process of querying data, we introduce in this RFC data
@@
 can be built up from simple components in a programmatic way to create complex
-operations using \textit{Boolean} operations. The core query API is composed of
+operations using \textit{Boolean} operations. The current API is presented
+below:
+
+{\lstsetc
+\begin{lstlisting}
+hid_t  H5Qcreate(H5Q_type_t query_type, H5Q_match_op_t match_op, ...);
+herr_t H5Qclose(hid_t query_id);
+
+hid_t  H5Qcombine(hid_t query1_id, H5Q_combine_op_t combine_op, hid_t query2_id);
+
+herr_t H5Qget_type(hid_t query_id, H5Q_type_t *query_type);
+herr_t H5Qget_match_op(hid_t query_id, H5Q_match_op_t *match_op);
+herr_t H5Qget_components(hid_t query_id, hid_t *subquery1_id, hid_t *subquery2_id);
+herr_t H5Qget_combine_op(hid_t query_id, H5Q_combine_op_t *op_type);
+
+herr_t H5Qencode(hid_t query_id, void *buf, size_t *nalloc);
+hid_t  H5Qdecode(const void *buf);
+\end{lstlisting}
+}
+
+The core query API is composed of
 two routines: \texttt{H5Qcreate} and \texttt{H5Qcombine}. \texttt{H5Qcreate}
@@
 $=$, $\neq$, $\leq$, $\geq$, and a value for the match operator.
+Created query objects can be serialized and deserialized using \texttt{H5Qencode}
+and \texttt{H5Qdecode} routines\footnote{Useful if the query needs to be sent
+through the network}, and their content can be retrieved using the corresponding
+accessor routines.
 \texttt{H5Qcombine} combines two query objects into a
@@
 
-\todo{Add something about parallel queries / multi dataset serial}
+\TableRef{tab:querycomb} describes the result types for atomic queries and
+combining queries of different types. Query results of $None$ type are rejected
+when \texttt{H5Qcombine} is called, causing it to return failure\footnote{Query
+results of $None$ type may be implemented with another result type in the
+future, once experience with the query framework is acquired and a meaningful
+grammar for those results are defined.}.
+
+\begin{table}[ht]\footnotesize
+\caption{Query combinations and associated result type.}
+\label{tab:querycomb}
+\begin{tabular}{ll} \toprule
+Query &
+Result Type\\ \midrule
+\texttt{H5Q\_TYPE\_DATA\_ELEM} & $Dataset~Element$ \\
+\texttt{H5Q\_TYPE\_ATTR\_VALUE} & $Attribute$ \\
+\texttt{H5Q\_TYPE\_ATTR\_NAME} & $Object$ \\
+\texttt{H5Q\_TYPE\_LINK\_NAME} & $Object$ \\
+$Dataset~Element \land Dataset~Element$ & $Dataset~Element$ \\
+$Dataset~Element \land Attribute$ & $None$ \\
+$Dataset~Element \land Object$ & $Dataset~Element$ \\
+$Attribute \land Attribute$ & $Attribute$ \\
+$Attribute \land Object$ & $Attribute$ \\
+$Object \land Object$ & $Object$ \\
+$Dataset~Element \lor Dataset~Element$ & $Dataset~Element$ \\
+$Dataset~Element \lor Attribute$ & $Combination$ \\
+$Dataset~Element \lor Object$ & $Combination$ \\
+$Dataset~Element \lor Combination$ & $Combination$ \\
+$Attribute \lor Attribute$ & $Attribute$ \\
+$Attribute \lor Object$ & $Combination$ \\
+$Attribute \lor Combination$ & $Combination$ \\
+$Object \lor Object$ & $Object$ \\
+$Object \lor Combination$ & $Combination$ \\
+$Combination \lor Combination$ & $Combination$ \\
+$Combination \land Dataset~Element$ & $None$ \\
+$Combination \land Attribute$ & $None$ \\
+$Combination \land Object$ & $None$ \\
+$Combination \land Combination$ & $None$ \\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 consist of read-only references into the contents of the HDF5 container that
-the query was applied to. View objects are created with \texttt{H5Vcreate},
-which applies a query to an HDF5 container, group hierarchy, or individual
-object and produces the view object as a result. The attributes, objects,
-and/or data elements referenced within a view can be retrieved by further API
-calls.
+the query was applied to. The current API is presented below:
 
-For example, starting with the HDF5 container described in
-\FigureRef{fig:HDF5File-Checkpoint}:
+{\lstsetc
+\begin{lstlisting}
+hid_t H5Vcreate(hid_t loc_id, hid_t query_id, hid_t vcpl_id);
+herr_t H5Vclose(hid_t view_id);
+herr_t H5Vget_location(hid_t view_id, hid_t *loc_id);
+herr_t H5Vget_query(hid_t view_id, hid_t *query_id);
+herr_t H5Vget_counts(hid_t view_id, hsize_t *attr_count, hsize_t *obj_count,
+  hsize_t *elem_region_count);
+herr_t H5Vget_attrs(hid_t view_id, hsize_t start, hsize_t count, hid_t attr_id[]);
+herr_t H5Vget_objs(hid_t view_id, hsize_t start, hsize_t count, hid_t obj_id[]);
+herr_t H5Vget_elem_regions(hid_t view_id, hsize_t start, hsize_t count,
+  hid_t dataset_id[], hid_t dataspace_id[]);
+\end{lstlisting}
+}
+
+View objects are created with \texttt{H5Vcreate}, which applies a query to an
+HDF5 container, group hierarchy, or individual object and produces the view
+object as a result. The attributes, objects, and/or data elements referenced
+within a view can be retrieved by further API calls. Note that currently,
+attribute references are not available, this feature will be added in order to
+support views that contain attribute references\footnote{See RFC XXXX for attribute references.}.
 
 \begin{figure}
-\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint}
+\input{pics/hdf5_view1}
 \caption{HDF5 container example.}
-\label{fig:HDF5File-Checkpoint}
+\label{fig:hdf5_view1}
 \end{figure}
 
-Applying the $link\_name = Pressure$ query (described above) would result
-in the view shown in \FigureRef{fig:HDF5File-Checkpoint-View1}, with the
-underlying container grayed out and the view highlighted in green.
+For example, starting with the HDF5 container described in \FigureRef{fig:hdf5_view1},
+applying the $link\_name = Pressure$ query (described above) would result
+in the view shown in \FigureRef{fig:hdf5_view2}, with the
+underlying container grayed out and the view highlighted in blue.
 
 \begin{figure}
-\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint-View1}
+\input{pics/hdf5_view2}
 \caption{HDF5 container example with query $link\_name = Pressure$ applied.}
-\label{fig:HDF5File-Checkpoint-View1}
+\label{fig:hdf5_view2}
 \end{figure}
@@
 Alternatively, applying the $data\_element = 17$ query (described above) would
-result in the view shown in \FigureRef{fig:HDF5File-Checkpoint-View2}, with the
-underlying container greyed out and the view highlighted in green.
+result in the view shown in \FigureRef{fig:hdf5_view3}, with the
+underlying container greyed out and the view highlighted in blue.
 
 \begin{figure}
-\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint-View2}
+\input{pics/hdf5_view3}
 \caption{HDF5 container example with query $data\_element = 17$ applied.}
-\label{fig:HDF5File-Checkpoint-View2}
+\label{fig:hdf5_view3}
 \end{figure}
@@
 query (described above) would result in the view shown in
-\FigureRef{fig:HDF5File-Checkpoint-View3}, with the underlying container
-greyed out and the view highlighted in green.
+\FigureRef{fig:hdf5_view4}, with the underlying container
+greyed out and the view highlighted in blue.
 
 \begin{figure}
-\includegraphics[width=\mediumfigwidth]{HDF5File-Checkpoint-View3}
+\input{pics/hdf5_view4}
 \caption{HDF5 container example with query $(link\_name = Pressure)\land(data\_element = 17)$ applied.}
-\label{fig:HDF5File-Checkpoint-View3}
+\label{fig:hdf5_view4}
 \end{figure}
@@
 Although creating indices for metadata components of queries, such as link or
-attribute names, is possible, we focus on index creation for
-dataset elements, as they represent the largest volume of data in typical HPC
-application usage of HDF5. Queries with metadata components execute properly,
+attribute names, is possible, we focus on index creation for dataset elements,
+as they represent the largest volume of data in typical HPC application usage of
+HDF5. Queries with metadata components execute properly,
 \todo{Must write about metadata indexing} but are not able to be accelerated
@@
 within the container for storing the contents of the index.
+The current API as well as the plugin interface are presented below:
+
+{\lstsetc
+\begin{lstlisting}
+herr_t H5Xregister(const H5X_class_t *idx_class);
+herr_t H5Xunregister(unsigned plugin_id);
+
+herr_t H5Xcreate(hid_t file_id, unsigned plugin_id, hid_t scope_id,
+        hid_t xcpl_id);
+herr_t H5Xremove(hid_t file_id, unsigned plugin_id, hid_t scope_id);
+herr_t H5Xget_count(hid_t scope_id, hsize_t *idx_count);
+
+typedef struct {
+    unsigned version;     /* Version number of the index plugin class struct */
+                          /* (Should always be set to H5X_CLASS_VERSION, which
+                           *  may vary between releases of HDF5 library) */
+    unsigned id;          /* Index ID (assigned by The HDF Group, for now) */
+    const char *idx_name; /* Index name (for debugging only, currently) */
+    H5X_type_t type;      /* Type of data indexed by this plugin */
+
+    /* Callbacks, described above */
+    void *(*create)(hid_t file_id, hid_t dataset_id, hid_t xcpl_id,
+        hid_t xapl_id, size_t *metadata_size, void **metadata);
+    herr_t (*remove)(hid_t file_id, hid_t dataset_id, size_t metadata_size,
+        void *metadata);
+    herr_t (*copy)(hid_t file1_id, hid_t file2_id, hid_t dataset1_id,
+        hid_t dataset2_id, hid_t xcpl_id, hid_t xapl_id,
+        size_t metadata_size, void *metadata);
+    void *(*open)(hid_t file_id, hid_t dataset_id, hid_t xapl_id,
+        size_t metadata_size, void *metadata);
+    herr_t (*close)(void *idx_handle);
+    herr_t (*pre_update)(void *idx_handle, hid_t dataspace_id, hid_t xxpl_id);
+    herr_t (*post_update)(void *idx_handle, const void *buf, hid_t dataspace_id,
+            hid_t xxpl_id);
+    herr_t (*query)(void *idx_handle, hid_t query_id, hid_t xxpl_id,
+        hid_t *dataspace_id);
+    herr_t (*refresh)(void *idx_handle, size_t *metadata_size, void **metadata);
+    herr_t (*get_size)(void *idx_handle, size_t *idx_size);
+} H5X_class_t;
+\end{lstlisting}
+}
 
@@
 plugin ID to the \texttt{H5Xcreate} call.
-Index information (such as plugin id and index metadata) is stored at index
+Alternatively an index may be created at the same time as a dataset gets created
+by passing a property to the dataset creation property list.
+Index information (such as plugin ID and index metadata) is stored at index
 creation time\footnote{This therefore introduces a file format change},
@@
 \begin{figure}
-\input{pics/hdf5filestruc}
-\caption{HDF5 stores multidimensional arrays (datasets)
-  along with metadata in a file. In this case, a dataset is contiguously mapped
-  from the application memory to a file, its data structure being described in
-  the metadata cache.}
-\label{fig:hdf5filestruc}
+\input{pics/hdf5_index}
+\caption{Index information (plugin ID and metadata) is stored along the object header.}
+\label{fig:hdf5_index}
 \end{figure}
@@
 Because the amount of space taken by the index cannot be directly retrieved by
-the user since the datasets storing the indices should be \textit{anonymous}
-and not visible from the file hierarchy, we also plan on adding callbacks to
-query from a specified dataset the amount of space the index that is attached
-to it takes.
+the user since the datasets storing the indices are known only by the plugin
+itself, the \texttt{get\_size} callback can query the amount of space that
+the index takes in the file.
 
-\subsubsection{Interface}
-
-{\lstsetc
-\begin{lstlisting}
-typedef struct {
-    unsigned version;     /* Version number of the index plugin class struct */
-                          /* (Should always be set to H5X_CLASS_VERSION, which
-                           *  may vary between releases of HDF5 library) */
-    unsigned id;          /* Index ID (assigned by The HDF Group, for now) */
-    const char *idx_name; /* Index name (for debugging only, currently) */
-    H5X_type_t type;      /* Type of data indexed by this plugin */
-
-    /* Callbacks, described above */
-    void *(*create)(hid_t file_id, hid_t dataset_id, hid_t xcpl_id,
-        hid_t xapl_id, size_t *metadata_size, void **metadata);
-    herr_t (*remove)(hid_t file_id, hid_t dataset_id, size_t metadata_size,
-        void *metadata);
-    void *(*open)(hid_t file_id, hid_t dataset_id, hid_t xapl_id,
-        size_t metadata_size, void *metadata);
-    herr_t (*close)(void *idx_handle);
-    herr_t (*pre_update)(void *idx_handle, hid_t dataspace_id, hid_t xxpl_id);
-    herr_t (*post_update)(void *idx_handle, const void *buf, hid_t dataspace_id,
-            hid_t xxpl_id);
-    herr_t (*query)(void *idx_handle, hid_t query_id, hid_t xxpl_id,
-        hid_t *dataspace_id);
-    herr_t (*refresh)(void *idx_handle, size_t *metadata_size, void **metadata);
-} H5X_class_t;
-\end{lstlisting}
-}
+\todo{Add something about parallel queries / multi dataset serial / multiquery paragraph}
 
@@
 Current implementations for FastBit and ALACRITY index packages are already
-present, as well as a brute force indexing plugin. In the future more plugins
-will be added, with and without external dependency.
+present, as well as a brute force indexing plugin. Early performance results
+are presented in \FigureRef{fig:indexing_perf}.
+
+\begin{figure}
+\input{plots/indexing_perf}
+\caption{Indexing performance.}
+\label{fig:indexing_perf}
+\end{figure}
+
+In the future more plugins
+will be added, with and without external dependency (e.g., pytable indexing,
+bitmap indexing).
 To satisfy that need, dynamic plugin loading and registration will be supported,
 allowing external libraries to plug to the current interface.
-\todo{pytable indexing?}
 
@@
 There are some existing limitations in the use of indices in the current
-implementation: FastBit and
-ALACRITY do not support incremental updates, an index is a shared resource for
-a dataset. Taken together, these conspire to put limits on application updates
-to datasets with indices.
+implementation: FastBit and ALACRITY do not support incremental updates,
+an index is a shared resource for a dataset. Taken together, these conspire to
+put limits on application updates to datasets with indices.
 Additionally, because FastBit and Alacrity don't allow incremental updates to
 an index, each modification to an existing index forces the index to be entirely
-rebuilt. The limitation in FastBit and Alacrity will need to be addressed in
+rebuilt. The limitation in FastBit and ALACRITY will need to be addressed in
 the base packages' implementation, so that they can make incremental updates
@@
 \begin{itemize}
-\item How could an index be built in parallel for a dataset that already exists?
+\item How could an index be built and queried in parallel for a dataset that already exists?
 \item How to handle index updates when the specified index plugin is not available?
@@
 therefore available at any time, but that is not the case here)
+We could mark the index as out of date and rebuild the index when the plugin is
+available again.
 \item How to handle index queries when the specified index plugin is not
-available?
+available? We could fallback to another plugin and do a brute force query on the data.
 \end{itemize}
@@
 \begin{itemize}
+\item h5copy: copy
 \item h5dump: report index information
@@
 \item h5diff: ignore index information?
-\item h5repack: copy index information
+\item h5repack: copy index information / or generate index
 \item h5edit: ignore index information?
 \item h5toh4: ignore index information?
-\item h5import: copy index information
+\item h5import: ignore index information
 \end{itemize}
+
+Additional tools for indexing data and answering queries will also be added
+in the future.
 
@@
 create and attach a new index, to finally query data from it.
+Note that some of the calls may be moved to the higher level API, in order to
+directly read data that corresponds to the result of the index query.
 
@@
 
-%% Close
 \section*{Revision History}

### 2014-08-18 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_index.tex
Updates to analysis RFC
Former-commit-id: 6fb57a85f099a15da82e1a2b3d94ecf88385f5c0

\tikzstyle{textBox}    = [rectangle, text centered, font=\sffamily\footnotesize\bfseries]
\tikzstyle{fileBox}    = [draw, rectangle, fill=white]
\tikzstyle{headerBox}  = [draw, rectangle, fill=white, font=\sffamily\footnotesize]
\tikzstyle{dataBox}    = [draw, rectangle, thick, fill=white, pattern color=rulecolor, pattern=dots, font=\sffamily\small]
\tikzstyle{indexBox}   = [draw, rectangle, thick, fill=white, pattern color=rulecolor, pattern=north west lines, font=\sffamily\small]

\tikzstyle{cacheBox}   = [draw, rectangle, thick, fill=black!10, drop shadow={opacity=0.25}]

\tikzstyle{message} = [draw=rulecolor, very thick, shorten <=2pt, shorten >=2pt, 
  text centered, text width=2.5cm, font=\footnotesize]
\tikzstyle{capt} = [text centered, font=\sffamily\footnotesize\bfseries, above=3mm]

\begin{tikzpicture}

\node[rectangle, minimum height=4cm, minimum width=14cm] (app) {};
\node[rectangle, minimum height=3.6cm, minimum width=6.4cm, right=2mm of app.west] (cache) {};
\node[rectangle, draw=rulecolor, very thick, minimum height=3.1cm, minimum width=2.9cm, right=2mm of cache.west] (cachecol1) {};
\node[rectangle, minimum height=3.6cm, minimum width=2.9cm, right=2mm of cachecol1.east] (cachecol2) {};
\node[textBox, minimum width=2.5cm, minimum height=0.7cm, below=2mm of cachecol1.north] (cache1) {Dataset header};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache1] (cache2) {\dots};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache2] (cache3) {Plugin ID};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache3] (cache4) {Metadata Size};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache4] (cache5) {Metadata};
\node[headerBox, minimum width=2.5cm, below=-1pt of cache5] (cache6) {\dots};

\node[fileBox, minimum height=1cm, minimum width=14cm, below=5mm of app] (file) {};
\node[textBox, minimum height=1cm, minimum width=2cm, right=4mm of file.west] (filetitle) {File};
\node[headerBox, fill=rulecolor, thick, minimum height=1cm, minimum width=1cm, right=1.5cm of filetitle] (fileheader) {};
\node[indexBox, minimum height=1cm, minimum width=2cm, right=1cm of fileheader] (index) {};
\node[dataBox, minimum height=1cm, minimum width=4cm, right=1cm of index] (dataset) {};

%\matrix (A) [matrix of math nodes, column sep=0 mm] 
%{ a_{11} & a_{12} & a_{13}  \\
%  a_{21} & a_{22} & a_{23}  \\
%  a_{31} & a_{32} & a_{33}  \\
%  a_{11} & a_{12} & a_{13} \\
%  a_{21} & a_{22} & a_{13}\\
%};

\draw[message, ->] (cachecol1.east) -| (fileheader.north);
\draw[decorate, decoration={brace, raise=2mm}, draw=rulecolor, very thick] (index.north west) to
  node [capt] {Index} (index.north east);
\draw[decorate, decoration={brace, raise=2mm}, draw=rulecolor, very thick] (dataset.north west) to
  node [capt] {Dataset} (dataset.north east);

\end{tikzpicture}

### 2014-08-18 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view1.tex
Updates to analysis RFC
Former-commit-id: 6fb57a85f099a15da82e1a2b3d94ecf88385f5c0

\tikzstyle{groupBox} = [draw, ellipse, fill=white, minimum size=20pt,
  text centered, font=\footnotesize\sffamily, text width=20pt, inner sep=0]

\tikzstyle{textBox} = [fill=white, inner sep=2pt, text centered, font=\footnotesize\sffamily]

\tikzstyle{link} = [->, thick, >=stealth', shorten <=1pt, shorten >=1pt]

\pgfmathsetseed{1}

\def\drawdataset#1{%
\begin{scope}[#1]
  \foreach \y in {-1.5,-0.5,0.5} {
      \foreach \x in {-2.5,-1.5,-0.5,0.5,1.5} {
          \path[fill=white, draw] (\x,\y) rectangle ++(1,1);
      }
  }
\end{scope}
}

\begin{tikzpicture}

% Root
\node[groupBox] (root) {root};

% Groups
\node[below=50pt of root, inner sep=0] (rootgroup) {};
\node[groupBox, left=80pt of rootgroup] (group0) {};
\node[groupBox, below=100pt of root] (group1) {};
\node[groupBox, right=80pt of rootgroup] (group2) {};

% Datasets
% G0
\node[below=30pt of group0, inner sep=0] (datasetg0) {};
\node[rectangle, text height=25pt, left=40pt of datasetg0, inner sep=0] (tempg0) {};
\drawdataset{shift=(tempg0.south), scale=0.3}
\node[rectangle, text height=25pt, right=40pt of datasetg0, inner sep=0] (presg0) {};
\drawdataset{shift=(presg0.south), scale=0.3}

% G1
\node[below=30pt of group1, inner sep=0] (datasetg1) {};
\node[rectangle, text height=25pt, left=40pt of datasetg1, inner sep=0] (tempg1) {};
\drawdataset{shift=(tempg1.south), scale=0.3}
\node[rectangle, text height=25pt, right=40pt of datasetg1, inner sep=0] (presg1) {};
\drawdataset{shift=(presg1.south), scale=0.3}

% G2
\node[below=30pt of group2, inner sep=0] (datasetg2) {};
\node[rectangle, text height=25pt, left=40pt of datasetg2, inner sep=0] (tempg2) {};
\drawdataset{shift=(tempg2.south), scale=0.3}
\node[rectangle, text height=25pt, right=40pt of datasetg2, inner sep=0] (presg2) {};
\drawdataset{shift=(presg2.south), scale=0.3}

% Links
\draw[link] (root) -- node [textBox] {Timestep1} (group0);
\draw[link] (root) -- node [textBox] {Timestep2} (group1);
\draw[link] (root) -- node [textBox] {Timestep3} (group2);

\draw[link] (group0) -- node [textBox] {Temperature} (tempg0);
\draw[link] (group0) -- node [textBox] {Pressure} (presg0);

\draw[link] (group1) -- node [textBox] {Temperature} (tempg1);
\draw[link] (group1) -- node [textBox] {Pressure} (presg1);

\draw[link] (group2) -- node [textBox] {Temperature} (tempg2);
\draw[link] (group2) -- node [textBox] {Pressure} (presg2);

%node distance=100pt,

%\pgfmathsetseed{1}
%\foreach \col in {black,red,green,blue}
%{
%\begin{tikzpicture}[x=10pt,y=10pt,ultra thick,baseline,line cap=round]
%\coordinate (current point) at (0,0);
%\coordinate (old velocity) at (0,0);
%\coordinate (new velocity) at (rand,rand);
%\foreach \i in {0,1,...,100}
%{
%\draw[\col!\i] (current point)
%.. controls ++([scale=-1]old velocity) and
%++(new velocity) .. ++(rand,rand)
%coordinate (current point);
%\coordinate (old velocity) at (new velocity);
%\coordinate (new velocity) at (rand,rand);
%}
%\end{tikzpicture}
%}

\end{tikzpicture}

### 2014-08-18 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view2.tex
Updates to analysis RFC
Former-commit-id: 6fb57a85f099a15da82e1a2b3d94ecf88385f5c0

--- 2014-08-18 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view1.tex
@@
 \draw[link] (group0) -- node [textBox] {Temperature} (tempg0);
-\draw[link] (group0) -- node [textBox] {Pressure} (presg0);
+\draw[link, draw=rulecolor, text=rulecolor] (group0) -- node [textBox] {Pressure} (presg0);
 
 \draw[link] (group1) -- node [textBox] {Temperature} (tempg1);
-\draw[link] (group1) -- node [textBox] {Pressure} (presg1);
+\draw[link, draw=rulecolor, text=rulecolor] (group1) -- node [textBox] {Pressure} (presg1);
 
 \draw[link] (group2) -- node [textBox] {Temperature} (tempg2);
-\draw[link] (group2) -- node [textBox] {Pressure} (presg2);
+\draw[link, draw=rulecolor, text=rulecolor] (group2) -- node [textBox] {Pressure} (presg2);
 

### 2014-08-18 RFCs/HDF5_Library/AnalysisExt/plots/gen.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+for i in `ls *.gpi`
+do
+    echo $i
+    gnuplot $i
+done
+

### 2014-08-20 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Updates to analysis RFC
Former-commit-id: e7997e97497dd95c73c42f13018a101f09568ab3

@@
     BoldSlantedFont={* Bold Italic}
-  ]{Calibri}
+  ]{Verdana}
   \setsansfont[
@@
     BoldItalicFont={* Bold Italic}
-  ]{Calibri}
-  \setmathfont[math-style=ISO, bold-style=ISO]{Asana Math}
+  ]{Verdana}
+%  \setmathfont[math-style=ISO, bold-style=ISO]{Latin Modern Math}
   \setmonofont[
@@
     H5Screate_simple, H5Sclose, H5Sget_select_npoints,
-    H5Xregister, H5Xunregister, H5Xcreate, H5Xremove, H5Xget_count
+    H5Xregister, H5Xunregister, H5Xcreate, H5Xremove, H5Xget_count,
+    H5Vcreate, H5Vclose, H5Vget_location, H5Vget_query, H5Vget_counts,
+    H5Vget_attrs, H5Vget_objs, H5Vget_elem_regions
     }
@@
     /* Callbacks, described above */
-    void *(*create)(hid_t file_id, hid_t dataset_id, hid_t xcpl_id,
-        hid_t xapl_id, size_t *metadata_size, void **metadata);
-    herr_t (*remove)(hid_t file_id, hid_t dataset_id, size_t metadata_size,
+    void *(*create)(hid_t dataset_id, hid_t xcpl_id, hid_t xapl_id,
+        size_t *metadata_size, void **metadata);
+    herr_t (*remove)(hid_t dataset_id, size_t metadata_size, void *metadata);
+    herr_t (*copy)(hid_t src_dataset_id, hid_t dest_dataset_id, hid_t xcpl_id,
+        hid_t xapl_id, size_t src_metadata_size, void *src_metadata,
+        size_t *dest_metadata_size, void **dest_metadata);
+    void *(*open)(hid_t dataset_id, hid_t xapl_id, size_t metadata_size,
         void *metadata);
-    herr_t (*copy)(hid_t file1_id, hid_t file2_id, hid_t dataset1_id,
-        hid_t dataset2_id, hid_t xcpl_id, hid_t xapl_id,
-        size_t metadata_size, void *metadata);
-    void *(*open)(hid_t file_id, hid_t dataset_id, hid_t xapl_id,
-        size_t metadata_size, void *metadata);
     herr_t (*close)(void *idx_handle);
@@
     herr_t (*refresh)(void *idx_handle, size_t *metadata_size, void **metadata);
-    herr_t (*get_size)(void *idx_handle, size_t *idx_size);
+    herr_t (*get_size)(void *idx_handle, hsize_t *idx_size);
 } H5X_class_t;

### 2014-08-21 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Updates to analysis RFC
Former-commit-id: bbfe76e0e54d6dcac1822e3583baa798a4ffd6fe

@@
   \setmainfont[
-    UprightFont={*},
+    UprightFont={* Regular},
     BoldFont={* Bold},
@@
     BoldSlantedFont={* Bold Italic}
-  ]{Verdana}
+  ]{Minion Pro}
   \setsansfont[
@@
     BoldItalicFont={* Bold Italic}
-  ]{Verdana}
-%  \setmathfont[math-style=ISO, bold-style=ISO]{Latin Modern Math}
+  ]{Optima LT Std}
+  \setmathfont[math-style=ISO, bold-style=ISO]{Latin Modern Math}
   \setmonofont[
@@
     BoldFont={* Bold},
-    ItalicFont={* Italic},
-    BoldItalicFont={* Bold Italic}
-  ]{Courier New}
+    ItalicFont={* Oblique},
+    BoldItalicFont={* Bold Oblique}
+  ]{Courier Std}
 \else
@@
 \author{Quincey Koziol}
-\date{July 17, 2014}
-\rfcversion{2014-07-17.v1}
+\date{August 20, 2014}
+\rfcversion{2014-07-17.v2}
 \revision{July 17, 2014}{Version 1 circulated for comment within The HDF Group.}
+\revision{August 20, 2014}{Version 2 circulated for comment within The HDF Group.}
 

### 2014-08-28 RFCs/HDF5/VOL/user_guide/intro.tex
Updates to User guide and RFC document.
Former-commit-id: 283e0ce257e84c90e0e132ff6707d8ca1780c327

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

\section{Introduction}
The Virtual Object Layer (VOL) is an abstraction layer in the HDF5
library that intercepts all API calls that could potentially access
objects in an HDF5 container and forwards those calls to plugin
''object drivers''. The plugins could store the objects in variety of
ways. A plugin could, for example, have objects be distributed
remotely over different platforms, provide a raw mapping of the model
to the file system, or even store the data in other file formats (like
native netCDF or HDF4 format). The user still gets the same data model
where access is done to a single HDF5 “container”; however the plugin
object driver translates from what the user sees to how the data is
actually stored. Having this abstraction layer maintains the object
model of HDF5 and would allow HDF5 developers or users to write their
own plugins for accessing HDF5 data.

This user guide is for developers interested in developing a VOL
plugin for the HDF5 library. The document is meant to be used in
conjunction with the HDF5 reference manual. It is assumed that the
reader has good knowledge of the VOL architecture obtained by reading
the VOL architectural design document ~\ref{HERE} MSC-ref. The
document will cover the steps needed to create external and internal
VOL plugins. Both ways have a lot of common steps and rules that will
be covered first.

### 2014-08-28 RFCs/HDF5/VOL/user_guide/plugin.tex
Updates to User guide and RFC document.
Former-commit-id: 283e0ce257e84c90e0e132ff6707d8ca1780c327

\section{Creating a VOL Plugin}
\label{sec:vol}
Each VOL plugin should be of type {\tt H5VL\_class\_t} that is defined
as:

\begin{lstlisting}
/* Class information for each VOL driver */
typedef struct H5VL_class_t {
    H5VL_class_value_t value;
    const char *name;
    herr_t  (*initialize)(hid_t vipl_id);
    herr_t  (*terminate)(hid_t vtpl_id);
    size_t  fapl_size;
    void *  (*fapl_copy)(const void *info);
    herr_t  (*fapl_free)(void *info);

    /* Data Model */
    H5VL_attr_class_t          attr_cls;
    H5VL_dataset_class_t       dataset_cls;
    H5VL_datatype_class_t      datatype_cls;
    H5VL_file_class_t          file_cls;
    H5VL_group_class_t         group_cls;
    H5VL_link_class_t          link_cls;
    H5VL_object_class_t        object_cls;

    /* Services */
    H5VL_async_class_t         async_cls;
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
} H5VL_class_t;
\end{lstlisting}

The {\tt value} field is a unique integer enum identifier that should be
greater than 128 for external plugins and smaller than 128 for
internal plugins. Setting it in the VOL structure is required.

The {\tt name} field is a string that uniquely identifies the VOL plugin
name. Setting it in the VOL structure is required. No two plugins with the same name can be registered with the library at the same time.

The {\tt initialize} field is a function pointer to a routine that a plugin implements to set up or intialize access to the plugin. Implementing this function by the plugin is not required, since some plugins do not require any set up to start accessing the plugin. In that case, the value of the function pointer should be set to NULL. Plugin specific variables that are required to be passed from users should be passed through the VOL initialize property list. Generic properties can be added to this property class for user-defined plugins that can not modify the HDF5 library to add internal properties. For more information consult the property list reference manual pages.

The {\tt terminate} field is a function pointer to a routine that a plugin implements to terminate or finalize access to the plugin. Implementing this function by the plugin is not required, since some plugins do not require any termination phase to the plugin. In that case, the value of the function pointer should be set to NULL. Plugin specific variables that are required to be passed from users should be passed through the VOL terminate property list. Generic properties can be added to this property class for user-defined plugins that can not modify the HDF5 library to add internal properties. For more information consult the property list reference manual pages.

The {\tt fapl\_size} field indicates the size required to store the
info data that the plugin needs. That info data is passed when the
plugin is selected for usage with the file access property list (fapl)
function. It might be that the plugin defined does not require any
information from the user, which means the size in this field will be
zero. More information about the info data and the fapl selection
routines follow later.

The {\tt fapl\_copy} field is a function pointer that is called when
the plugin is selected with the fapl function. It allows the plugin to
make a copy if the info data since the user might free it when closing
the fapl. It is required if there is info data needed by the plugin.

The {\tt fapl\_free} field is a function pointer that is called to
free the info data when the fapl close routine is called. It is
required if there is info data needed by the plugin.

The rest of the fields in the {\tt H5VL\_class\_t} struct are "subclasses'' that define all the VOL function callbacks that
are mapped to from the HDF5 API layer. Those subclasses are categorized into two categories, Data Model and Services. Data Model classes are those that provide functionality for accessing an HDF5 container and objects in that container as defined by the HDF5 data model.  Service classes are those that provide services for users that are not related to the data model specifically. Asynchronous operations, for example, are a service that most plugins can implement, so we add a class for it in the VOL structure. If a service becomes generic enough and common between many plugins, a class for it should be added in the VOL structure. However, many plugins can/will provide services that are not shared by other plugins. A good way to support these services is through an optional callback in the VOL structure which can be a hook from the API to the plugin that provides those services, passing any necessary arguments needed without the HDF5 library having to worry about supporting that service. A similar API operation to allow users to use that service will be added. This API call would be similar to an “ioctl” call where any kind of operation can be supported and passed down to the plugin that has enough knowledge from the user to interpret the type of the operation. All classes and their defined callbacks will be detailed in the following sub-sections.

\subsection{Mapping the API to the Callbacks}
\label{sec:map}

The callback interface defined for the VOL has to be general enough to
handle all the HDF5 API operations that would access the
file. Furthermore it has to capture future additions to the HDF5
library with little to no changes to the callback interface. Changing
the interface often whenever new features are added would be
discouraging to plugin developers since that would mean reworking
their VOL plugin structure. To remedy this issue, every callback will
contain two parameters:
\begin{itemize}
\item A data transfer property list (DXPL) which allows that API to
  put some properties on for the plugins to retrieve if they have to
  for particular operations, without having to add arguments to the
  VOL callback function.
\item A pointer to a request ({\tt void **req}) to handle asynchronous
  operations if the HDF5 library adds support for them in future
  releases (beyond the 1.8 series). That pointer is set by the VOL
  plugin to a request object it creates to manage progress on that
  asynchronous operation. If the {\tt req} is {\tt NULL}, that means
  that the API operation is blocking and so the plugin would not
  execute the operation asynchronously. If the plugin does not support
  asynchronous operations, it needs not to worry about this field and
  leaves it unset.
\end{itemize}

In order to keep the number of the VOL object classes and callbacks
concise and readable, it was decided to not have a one-to-one mapping
between API operation and callbacks. Furthermore, to keep the
callbacks themselves short and not cluttered with a lot of parameters,
some of the parameters are passed in as properties in property lists
included with the callback. The value of those properties can be
retrieved by calling the public routine (or its private version if
this is an internal plugin): 
\begin{lstlisting}
herr_t H5Pget(hid_t plist_id, const char *property_name, void *value);
\end{lstlisting}
The property names and value types will be detailed when describing
each callback in their respective sections.

The HDF5 library provides several routines to access an object in the
container. For example to open an attribute on a group object, the
user could use {\tt H5Aopen()} and pass the group identifier directly
where the attribute needs to be opened. Alternatively, the user could
use {\tt H5Aopen\_by\_name()} or {\tt H5Aopen\_by\_idx()} to open the
attribute, which provides a more flexible way of locating the
attribute, whether by a starting object location and a path or an
index type and traversal order. All those types of accesses usually
map to one VOL callback with a parameter that indicates the access
type. In the example of opening an attribute, the three API open
routine will map to the same VOL open callback but with a different
location parameter. The same applies to all types of routines that
have multiple types of accesses.  The location parameter is a
structure defined as follows:

\begin{lstlisting}
/* 
 * Structure to hold parameters for object locations.
 * either: BY_SELF, BY_NAME, BY_IDX, BY_ADDR, BY_REF 
 */

typedef struct H5VL_loc_params_t {
    H5I_type_t obj_type; /* The object type of the location object */
    H5VL_loc_type_t type; /* The location type */
    union { /* parameters of the location */
        struct H5VL_loc_by_name loc_by_name;
        struct H5VL_loc_by_idx  loc_by_idx;
        struct H5VL_loc_by_addr loc_by_addr;
        struct H5VL_loc_by_ref  loc_by_ref;
    }loc_data;
} H5VL_loc_params_t

/* 
 * Types for different ways that objects are located in an 
 * HDF5 container.
 */
typedef enum H5VL_loc_type_t {
    /* starting location is the target object*/
    H5VL_OBJECT_BY_SELF,

    /* location defined by object and path in H5VL_loc_by_name */
    H5VL_OBJECT_BY_NAME,

    /* location defined by object, path, and index in H5VL_loc_by_idx */
    H5VL_OBJECT_BY_IDX,

    /* location defined by physical address in H5VL_loc_by_addr */
    H5VL_OBJECT_BY_ADDR,

    /* NOT USED */
    H5VL_OBJECT_BY_REF
} H5VL_loc_type_t;

struct H5VL_loc_by_name {
    const char *name; /* The path relative to the starting location */
    hid_t plist_id; /* The link access property list */
};

struct H5VL_loc_by_idx {
    const char *name; /* The path relative to the starting location */
    H5_index_t idx_type; /* Type of index */
    H5_iter_order_t order; /* Index traversal order */
    hsize_t n; /* position in index */
    hid_t plist_id; /* The link access property list */
};

struct H5VL_loc_by_addr {
    haddr_t addr; /* physical address of location */
};

/* Not used for now */
struct H5VL_loc_by_ref {
    H5R_type_t ref_type;
    const void *_ref;
    hid_t plist_id;
};
\end{lstlisting}

Other API routines that would make a one-to-one mapping difficult are:
\begin{itemize} 
\item the {\tt Get} operations that retrieve something from an object; for example a property list or a datatype of a dataset, etc... 
\item API routines specific to each class of callbacks(attributes, files, etc...). Having a callback for each one would clutter the VOL callback structure and reduce user friendliness. 
\item API routines that make sense to only implement in the native HDF5 file format and would not be possible to implement in other plugins. Adding a callback for those routines would be confusing to plugin developers. 
\end{itemize}

To handle that large set of API routines, each class in the Data Model category has three generic callbacks, {\tt get}, {\tt specific}, and {\tt optional} to handle the three set of API operations outline above respectively. The callbacks will have a {\tt va\_list} argument to handle the different set of parameters that could be passed in.  The {\tt get} and {\tt specific} callbacks also have an {\tt op\_type} that contain an {\tt enum} of the type of operation that is requested to be performed. Using that type, the {\tt va\_list} argument can be parsed. The {\tt optional} callback is a free for all callback where anything from the API layer is passed in directly. This callback is used to support plugin specific operations in the API that other plugins should or would not know about. More information about types and the arguments for each type will be detailed in the corresponding class arguments.

\subsection{The File Function Callbacks}
The file API routines (H5F) allow HDF5 users to create and manage HDF5
containers. All the H5F API routines that modify the HDF5 container
map to one of the file callback routines in this class that the plugin
needs to implement:

\begin{lstlisting}
typedef struct H5VL_file_class_t {
    void *(*create)(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
    void *(*open)(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
    herr_t (*get)(void *obj, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*specific)(void *obj, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*close) (void *file, hid_t dxpl_id, void **req);
} H5VL_file_class_t;
\end{lstlisting}

The {\tt create} callback in the file class should create a container
and returns a pointer to the file structure created by the plugin containing information to
access the container in future calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*create)(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt name} & (IN): The name of the container to be created.\\
  {\tt flags} & (IN): The creation flags of the container.\\
  {\tt fcpl\_id} & (IN): The file creation property list.\\
  {\tt fapl\_id} & (IN): The file access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt open} callback in the file class should open a container and
returns a pointer to the file structure created by the plugin containing information to
access the container in future calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*open)(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt name} & (IN): The name of the container to open.\\
  {\tt flags} & (IN): The open flags of the container.\\
  {\tt fapl\_id} & (IN): The file access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt get} callback in the file class should retrieve
information about the container as specified in the {\tt get\_type}
parameter. It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*get)(void *obj, H5VL_file_get_t get_type, hid_t dxpl_id, 
        void **req, va_list arguments);
\end{lstlisting}

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all file get API routines */
typedef enum H5VL_file_get_t {
    H5VL_FILE_GET_FAPL,      /* file access property list   */
    H5VL_FILE_GET_FCPL,      /* file creation property list */
    H5VL_FILE_GET_INTENT,    /* file intent                 */
    H5VL_FILE_GET_NAME,      /* file name                   */
    H5VL_FILE_GET_OBJ_COUNT, /* object count in file        */
    H5VL_FILE_GET_OBJ_IDS,   /* object ids in file          */
    H5VL_OBJECT_GET_FILE     /* retrieve or resurrect file of object */
} H5VL_file_get_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The container or object where information needs to be
  retrieved from.\\
  {\tt get\_type} & (IN): The type of the information to retrieve.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt get\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_FILE\_GET\_FCPL}, to retrieve the file creation
  property list:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    file creation property list.
  \end{enumerate}

\item {\tt H5VL\_FILE\_GET\_FAPL}, to retrieve the file access
  property list:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    file access property list.
  \end{enumerate}

\item {\tt H5VL\_FILE\_GET\_OBJ\_COUNT:}, to retrieve the object count
  in the container:
  \begin{enumerate}
  \item {\tt unsigned types} (IN): type of objects to look for.
  \item {\tt ssize\_t *ret} (OUT): buffer for the object count.
  \end{enumerate}

\item {\tt H5VL\_FILE\_GET\_OBJ\_IDS:}, to retrieve object identifiers
  in the container:
  \begin{enumerate}
  \item {\tt unsigned types} (IN): type of objects to look for.
  \item {\tt size\_t max\_objs} (IN): maximum number of objects to
    open.
  \item {\tt hid\_t *oid\_list} (OUT): buffer for the object identifiers.
  \item {\tt ssize\_t *ret} (OUT): buffer for the object count.
  \end{enumerate}

\item {\tt H5VL\_FILE\_GET\_INTENT}, get access intent of the
  container:
  \begin{enumerate}
  \item {\tt unsigned *ret} (OUT): buffer for the intent value.
  \end{enumerate}

\item {\tt H5VL\_FILE\_GET\_NAME}, get container name an object
  belongs to:
  \begin{enumerate}
  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
  \item {\tt size\_t size} (IN): size of the buffer for the file name.
  \item {\tt char *name} (OUT): buffer for the file name.
  \item {\tt ssize\_t *ret} (OUT): buffer for the entire size of the
    file name.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_GET\_FILE}, get the container that the object
  belongs to:
  \begin{enumerate}
  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
  \item {\tt void **ret} (OUT): pointer to the file structure returned
    by the plugin.
  \end{enumerate}
\end{itemize}

The {\tt specific} callback in the file class implements specific operations on HDF5 files as specified in the {\tt
  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*specific)(void *obj, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

The {\tt specific\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for file SPECIFIC callback */
typedef enum H5VL_file_specific_t {
    H5VL_FILE_FLUSH,                  /* Flush file */
    H5VL_FILE_IS_ACCESSIBLE,          /* Check if a file is accessible */
    H5VL_FILE_MOUNT,                  /* Mount a file */
    H5VL_FILE_UNMOUNT                 /* Un-Mount a file */
} H5VL_file_specific_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The container or object where the operation needs
  to happen.\\
  {\tt specific\_type} & (IN): The type of the operation.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt specific\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_FILE\_FLUSH}, flushes all buffers associated with the container to disk:
  \begin{enumerate}
  \item {\tt H5I\_type\_t obj\_type} (IN): The object type of {\tt obj} on which the flush operation was called.
  \item {\tt H5F\_scope\_t scope} (IN): The scope of the flushing action.
  \end{enumerate}

\item {\tt H5VL\_FILE\_IS\_ACCESSIBLE}, checks if a container is
  accessible using a specific file access property list:
  \begin{enumerate}
  \item {\tt hid\_t *fapl\_id} (IN): file access property list.
  \item {\tt char *name} (IN): name of the container to check.
  \item {\tt htri\_t *result} (OUT): buffer for the result; 0 if no, 1
    if yes.
  \end{enumerate}

\item {\tt H5VL\_FILE\_MOUNT}, Mounts a file on the location object:
  \begin{enumerate}
  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
  \item {\tt char *name} (IN): name of the group onto which the file
    specified by {\tt file} is to be mounted.
  \item {\tt void *file} (IN): child file to be mounted.
  \item {\tt hid\_t *fmpl\_id} (IN): file mount property list.
  \end{enumerate}

\item {\tt H5VL\_FILE\_UNMOUNT}, un-mounts a file from the location object:
  \begin{enumerate}
  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
  \item {\tt char *name} (IN): name of the mount point.
  \end{enumerate}
\end{itemize}

The {\tt optional} callback in the file class implements plugin specific operations on an HDF5 container. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
\end{tabular}

Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema. For example, in the native plugin, the first argument in the {\tt va\_list} is the optional argument type enum defined as follows:

\begin{lstlisting}
/* types for all file optional operations */
typedef enum H5VL_file_optional_t {
    H5VL_FILE_CLEAR_ELINK_CACHE,  /* Clear external link cache         */
    H5VL_FILE_GET_FILE_IMAGE,     /* file image                        */
    H5VL_FILE_GET_FREE_SECTIONS,  /* file free selections              */
    H5VL_FILE_GET_FREE_SPACE,     /* file freespace                    */
    H5VL_FILE_GET_INFO,           /* file info                         */
    H5VL_FILE_GET_MDC_CONF,       /* file metadata cache configuration */
    H5VL_FILE_GET_MDC_HR,         /* file metadata cache hit rate      */
    H5VL_FILE_GET_MDC_SIZE,       /* file metadata cache size          */
    H5VL_FILE_GET_SIZE,           /* file size                         */
    H5VL_FILE_GET_VFD_HANDLE,     /* file VFD handle                   */
    H5VL_FILE_REOPEN,             /* reopen the file                   */
    H5VL_FILE_RESET_MDC_HIT_RATE, /* get metadata cache hit rate       */
    H5VL_FILE_SET_MDC_CONFIG      /* set metadata cache configuration  */
} H5VL_file_optional_t;
\end{lstlisting}

The remaining arguments are parsed depending on the optional operation type.

%\begin{itemize}
%
%\item {\tt H5VL\_FILE\_GET\_SIZE}, retrieve the size of the container
%  in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt hsize\_t *ret} (OUT): file size.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_GET\_FILE\_IMAGE}, retrieve file image from the
%  container in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt void *buf\_ptr} (OUT): buffer to return the file image.
%  \item {\tt ssize\_t *ret} (OUT): buffer for the total size needed for
%    the file image.
%  \item {\tt size\_t buf\_len} (IN): size of the buffer passed in.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_GET\_FREE\_SPACE}, retrieve amount of free
%  space in the container in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt hssize\_t *ret} (OUT): buffer for the free space.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_GET\_FREE\_SECTIONS}, retrieve free sections from the
%  container in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt H5F\_sect\_info\_t *sinfo} (OUT): pointer to the section
%    info structure to fill.
%  \item {\tt ssize\_t *ret} (OUT): buffer for the total number of free
%    sections.
%  \item {\tt H5F\_mem\_t type} (IN): type of the memory space to check
%    for.
%  \item {\tt size\_t nsects} (IN): number of section allocate in {\tt sinfo}.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_GET\_INFO}, retrieve file info from the
%  object in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
%  \item {\tt H5F\_info2\_t *finfo} (OUT): pointer to info structure to fill.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_GET\_MDC\_CONF}, retrieve the meta data cache
%  configuration from the container in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
%  \item {\tt H5AC\_cache\_config\_t *conf} (OUT): pointer to
%    configuration structure to fill.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_GET\_MDC\_HR}, retrieve the meta data cache
%  hit rate from the container in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt double *ret} (OUT): buffer for the hit rate.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_GET\_MDC\_SIZE}, retrieve the meta data cache
%  size information from the container in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt size\_t max\_size\_ptr} (OUT): buffer for maximum size.
%  \item {\tt size\_t min\_clean\_size\_ptr} (OUT): buffer for minimum
%    clean size.
%  \item {\tt size\_t cur\_size\_ptr} (OUT): buffer for current size.
%  \item {\tt int cur\_num\_entries\_ptr} (OUT): buffer for number of
%    current cache entries.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_GET\_VFD\_HANDLE}, retrieve the virtual file
%  driver handle from the container in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt void **handle} (OUT): pointer to a buffer the plugin sets
%    to the VFD handle.
%  \item {\tt hid\_t fapl} (IN): File access property list.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_CLEAR\_ELINK\_CACHE}, clears the external link
%  file cache. Takes no extra arguments.
%
%\item {\tt H5VL\_FILE\_REOPEN}, reopen the container in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt void **ret} (OUT): pointer to be set to the opened file
%    structure.
%  \end{enumerate}
%
%\item {\tt H5VL\_FILE\_RESET\_MDC\_HIT\_RATE}, resets the hit rate
%  statistics for the metadata cache on the container in {\tt
%    obj}. Takes no extra arguments.
%
%\item {\tt H5VL\_FILE\_SET\_MDC\_CONFIG}, sets the meta data cache
%  configuration for the container in {\tt obj}:
%  \begin{enumerate}
%  \item {\tt H5AC\_cache\_config\_t *conf} (IN): pointer to
%    configuration structure to use.
%  \end{enumerate}
%
%\end{itemize}

The {\tt close} callback in the file class should terminate access to
the file object and free all resources it was consuming, and returns
an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*close)(void *file, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt file} & (IN): Pointer to the file.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

\subsection{The Group Function Callbacks}
The group API routines (H5G) allow HDF5 users to create and manage
HDF5 groups. All the H5G API routines that modify the HDF5 container
map to one of the group callback routines in this class that the
plugin needs to implement:

\begin{lstlisting}
typedef struct H5VL_group_class_t {
    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
    herr_t (*get)(void *obj, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*specific)(void *obj, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*close) (void *grp, hid_t dxpl_id, void **req);
} H5VL_group_class_t;
\end{lstlisting}

The {\tt create} callback in the group class should create a group
object in the container of the location object and returns a pointer
to the group structure containing information to access the group in
future calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the group needs
  to be created or where the look-up of the target object needs to
  start.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_SELF} in this callback. \\
  {\tt name} & (IN): The name of the group to be created.\\
  {\tt dcpl\_id} & (IN): The group creation property list. It contains
  all the group creation properties in addition to the link creation
  property list of the create operation (an {\tt hid\_t}) that can be
  retrieved with the property {\tt H5VL\_GRP\_LCPL\_ID}.\\
  {\tt gapl\_id} & (IN): The group access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt open} callback in the group class should open a group object
in the container of the location object and returns a pointer to the
group structure containing information to access the group in future
calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
        const char*name, hid_t gapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the group needs to be
  opened or where the look-up of the target object needs to start.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_SELF} in this callback. \\
  {\tt name} & (IN): The name of the group to be opened.\\
  {\tt dapl\_id} & (IN): The group access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt get} callback in the group class should retrieve information
about the group as specified in the {\tt get\_type} parameter. It
returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*get)(void *obj, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all group get API routines */
typedef enum H5VL_group_get_t {
    H5VL_GROUP_GET_GCPL,      /*group creation property list */
    H5VL_GROUP_GET_INFO       /*group info                   */
} H5VL_group_get_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The group object where information needs to be
  retrieved from.\\
  {\tt get\_type} & (IN): The type of the information to retrieve.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt get\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_GROUP\_GET\_GCPL}, to retrieve the group creation
  property list of the group specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    group creation property list.
  \end{enumerate}

\item {\tt H5VL\_GROUP\_GET\_INFO}, to retrieve the attribute info:
  \begin{enumerate}
  \item {\tt H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
    explained in section~\ref{sec:map}. 
  \item {\tt H5G\_info\_t *ginfo} (OUT): info structure to fill the
    group info in.
  \end{enumerate}
\end{itemize}

The {\tt specific} callback in the group class currently does not require any functionality to be implemented and should be left as {\tt NULL}.

The {\tt optional} callback in the group class implements plugin specific operations on an HDF5 group. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
\end{tabular}

Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.

The {\tt close} callback in the group class should terminate access to
the group object and free all resources it was consuming, and returns
an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*close)(void *group, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt group} & (IN): Pointer to the group object.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

\subsection{The Dataset Function Callbacks}
The dataset API routines (H5D) allow HDF5 users to create and manage
HDF5 datasets. All the H5D API routines that modify the HDF5 container
map to one of the dataset callback routines in this class that the
plugin needs to implement:

\begin{lstlisting}
typedef struct H5VL_dataset_class_t {
    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
    herr_t (*read)(void *dset, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t xfer_plist_id, void * buf, void **req);
    herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t xfer_plist_id, const void * buf, void **req);
    herr_t (*get)(void *obj, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*specific)(void *obj, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*close) (void *dset, hid_t dxpl_id, void **req);
} H5VL_dataset_class_t;
\end{lstlisting}

The {\tt create} callback in the dataset class should create a dataset
object in the container of the location object and returns a pointer
to the dataset structure containing information to access the dataset
in future calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the dataset needs
  to be created or where the look-up of the target object needs to
  start.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_SELF} in this callback. \\
  {\tt name} & (IN): The name of the dataset to be created.\\
  {\tt dcpl\_id} & (IN): The dataset creation property list. It contains
  all the dataset creation properties in addition to the dataset
  datatype (an {\tt hid\_t}), dataspace (an {\tt hid\_t}), and the
  link creation property list of the create operation (an {\tt
    hid\_t}) that can be retrieved with the properties, {\tt
    H5VL\_DSET\_TYPE\_ID}, {\tt H5VL\_DSET\_SPACE\_ID},  and {\tt
    H5VL\_DSET\_LCPL\_ID} respectively.\\
  {\tt dapl\_id} & (IN): The dataset access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt open} callback in the dataset class should open a dataset
object in the container of the location object and returns a pointer
to the dataset structure containing information to access the dataset
in future calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the dataset needs to be
  opened or where the look-up of the target object needs to start.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_SELF} in this callback. \\
  {\tt name} & (IN): The name of the dataset to be opened.\\
  {\tt dapl\_id} & (IN): The dataset access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt read} callback in the dataset class should read data from
the dataset object and returns an {\tt herr\_t} indicating success or
failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*read)(void *dset, hid_t mem_type_id, hid_t mem_space_id, 
        hid_t file_space_id, hid_t dxpl_id, void *buf, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt dset} & (IN): Pointer to the dataset object.\\
  {\tt mem\_type\_id} & (IN): The memory datatype of the data.\\
  {\tt mem\_space\_id} & (IN): The memory dataspace selection.\\
  {\tt file\_space\_id} & (IN): The file dataspace selection.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt buf} & (OUT): Data buffer to be read into.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt write} callback in the dataset class should write data to
the dataset object and returns an {\tt herr\_t} indicating success or
failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, 
        hid_t file_space_id, hid_t dxpl_id, const void * buf, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt dset} & (IN): Pointer to the dataset object.\\
  {\tt mem\_type\_id} & (IN): The memory datatype of the data.\\
  {\tt mem\_space\_id} & (IN): The memory dataspace selection.\\
  {\tt file\_space\_id} & (IN): The file dataspace selection.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt buf} & (IN): Data buffer to be written from.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt set\_extent} callback in the dataset class should extend the
dataset dimensions and returns an {\tt herr\_t} indicating success or
failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*set_extent)(void *dset, const hsize_t size[], 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt dset} & (IN): Pointer to the dataset object.\\
  {\tt size} & (IN): new dimensions of the dataset.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt get} callback in the dataset class should retrieve
information about the dataset as specified in the {\tt get\_type}
parameter.It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*get)(void *dset, H5VL_dataset_get_t get_type, 
        hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for dataset GET callback */
typedef enum H5VL_dataset_get_t {
    H5VL_DATASET_GET_DAPL,                  /* access property list */
    H5VL_DATASET_GET_DCPL,                  /* creation property list */
    H5VL_DATASET_GET_OFFSET,                /* offset */
    H5VL_DATASET_GET_SPACE,                 /* dataspace */
    H5VL_DATASET_GET_SPACE_STATUS,          /* space  status */
    H5VL_DATASET_GET_STORAGE_SIZE,          /* storage size */
    H5VL_DATASET_GET_TYPE                   /* datatype */
} H5VL_dataset_get_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt dset} & (IN): The dataset object where information needs to be
  retrieved from.\\
  {\tt get\_type} & (IN): The type of the information to retrieve.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt get\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_DATASET\_GET\_DAPL}, to retrieve the dataset access
  property list of the dataset specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    dataset access property list.
  \end{enumerate}

\item {\tt H5VL\_DATASET\_GET\_DCPL}, to retrieve the dataset creation
  property list of the dataset specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    dataset creation property list.
  \end{enumerate}

\item {\tt H5VL\_DATASET\_GET\_OFFSET}, to retrieve the offset of the
  dataset specified in {\tt obj} in the container:
  \begin{enumerate}
  \item {\tt haddr\_t *ret} (OUT): buffer for the offset of the
    dataset in the container.
  \end{enumerate}

\item {\tt H5VL\_DATASET\_GET\_SPACE}, to retrieve the dataspace of the
  dataset specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    dataset dataspace.
  \end{enumerate}

\item {\tt H5VL\_DATASET\_GET\_SPACE\_STATUS}, to retrieve the
  information whether space has been allocated for the dataset:
  \begin{enumerate}
  \item {\tt H5D\_space\_status\_t *allocation} (OUT): buffer for the
    space status.
  \end{enumerate}

\item {\tt H5VL\_DATASET\_GET\_STORAGE\_SIZE}, to retrieve the storage
  size of the dataset specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hsize\_t *ret} (OUT): buffer for the storage size of
    the dataset in the container.
  \end{enumerate}

\item {\tt H5VL\_DATASET\_GET\_TYPE}, to retrieve the datatype of the
  dataset specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    dataset datatype.
  \end{enumerate}
\end{itemize}

The {\tt specific} callback in the dataset class implements specific operations on HDF5 datasets as specified in the {\tt
  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*specific)(void *obj, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

The {\tt specific\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for dataset SPECFIC callback */
typedef enum H5VL_dataset_specific_t {
    H5VL_DATASET_SET_EXTENT           /* H5Dset_extent */
} H5VL_dataset_specific_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The dset  where the operation needs
  to happen.\\
  {\tt specific\_type} & (IN): The type of the operation.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt specific\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_DATASET\_SET\_EXTENT}, changes the extent of the dataset dimensions:
  \begin{enumerate}
  \item {\tt hsize\_t size} (IN): Array containing the new magnitude of each dimension of the dataset. 
  \end{enumerate}
\end{itemize}

The {\tt optional} callback in the dataset class implements plugin specific operations on an HDF5 dataset. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
\end{tabular}

Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.

The {\tt close} callback in the dataset class should terminate access
to the dataset object and free all resources it was consuming, and
returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*close)(void *dset, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt dset} & (IN): Pointer to the dataset object.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

\subsection{The Attribute Function Callbacks}
The attribute API routines (H5A) allow HDF5 users to create and manage
HDF5 attributes. All the H5A API routines that modify the HDF5
container map to one of the attribute callback routines in this
class that the plugin needs to implement:

\begin{lstlisting}
typedef struct H5VL_attr_class_t {
    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *attr_name, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char *attr_name, hid_t aapl_id, hid_t dxpl_id, void **req);
    herr_t (*read)(void *attr, hid_t mem_type_id, void *buf, hid_t dxpl_id, void **req);
    herr_t (*write)(void *attr, hid_t mem_type_id, const void *buf, hid_t dxpl_id, void **req);
    herr_t (*get)(void *obj, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
    herr_t (*close) (void *attr, hid_t dxpl_id, void **req);
} H5VL_attr_class_t;
\end{lstlisting}

The {\tt create} callback in the attribute class should create an
attribute object in the container of the location object and
returns a pointer to the attribute structure containing information to
access the attribute in future calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*create)(void *obj, H5VL_loc_params_t loc_params, 
        const char *attr_name, hid_t acpl_id, hid_t aapl_id, 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the attribute needs
  to be created or where the look-up of the target object needs to
  start.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map}.\\
  {\tt attr\_name} & (IN): The name of the attribute to be created.\\
  {\tt acpl\_id} & (IN): The attribute creation property list. It contains
  all the attribute creation properties in addition to the attribute
  datatype (an {\tt hid\_t}) and dataspace (an {\tt hid\_t}) that can
  be retrieved with the properties, {\tt H5VL\_ATTR\_TYPE\_ID} and
  {\tt H5VL\_ATTR\_SPACE\_ID}.\\
  {\tt aapl\_id} & (IN): The attribute access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt open} callback in the attribute class should open an
attribute object in the container of the location object and returns a
pointer to the attribute structure containing information to access
the attribute in future calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
        const char *attr_name, hid_t aapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the attribute needs to be
  opened or where the look-up of the target object needs to start.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map}.\\
  {\tt attr\_name} & (IN): The name of the attribute to be opened.\\
  {\tt aapl\_id} & (IN): The attribute access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt read} callback in the attribute class should read data from
the attribute object and returns an {\tt herr\_t} indicating success or
failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*read)(void *attr, hid_t mem_type_id, void *buf, 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt attr} & (IN): Pointer to the attribute object.\\
  {\tt mem\_type\_id} & (IN): The memory datatype of the attribute.\\
  {\tt buf} & (OUT): Data buffer to be read into.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt write} callback in the attribute class should write data to
the attribute object and returns an {\tt herr\_t} indicating success or
failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*write)(void *attr, hid_t mem_type_id, const void *buf, 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt attr} & (IN): Pointer to the attribute object.\\
  {\tt mem\_type\_id} & (IN): The memory datatype of the attribute.\\
  {\tt buf} & (IN): Data buffer to be written.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt get} callback in the attribute class should retrieve
information about the attribute as specified in the {\tt get\_type}
parameter.It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*get)(void *obj, H5VL_attr_get_t get_type, hid_t dxpl_id, 
        void **req, va_list arguments);
\end{lstlisting}

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for attribute GET callback */
typedef enum H5VL_attr_get_t {
    H5VL_ATTR_GET_ACPL,               /* creation property list */
    H5VL_ATTR_GET_INFO,               /* info */
    H5VL_ATTR_GET_NAME,               /* access property list */
    H5VL_ATTR_GET_SPACE,              /* dataspace */
    H5VL_ATTR_GET_STORAGE_SIZE,       /* storage size */
    H5VL_ATTR_GET_TYPE                 /* datatype */
} H5VL_attr_get_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt attr} & (IN): An attribute or location object where information
  needs to be retrieved from.\\
  {\tt get\_type} & (IN): The type of the information to retrieve.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt get\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}

\item {\tt H5VL\_ATTR\_GET\_ACPL}, to retrieve the attribute creation
  property list of the attribute specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    attribute creation property list.
  \end{enumerate}

\item {\tt H5VL\_ATTR\_GET\_INFO}, to retrieve the attribute info:
  \begin{enumerate}
  \item {\tt H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
    explained in section~\ref{sec:map}. 
  \item {\tt H5A\_info\_t *ainfo} (OUT): info structure to fill the
    attribute info in.
  \end{enumerate}

\item {\tt H5VL\_ATTR\_GET\_NAME}, to retrieve an attribute name on a
  particular object specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
    explained in section~\ref{sec:map}. The type could be either
    {\tt H5VL\_OBJECT\_BY\_SELF} meaning {\tt obj} is the attribute,
    or {\tt H5VL\_OBJECT\_BY\_IDX} meaning the attribute to retrieve
    the name for should be looked up using the index information on
    the object in {\tt obj} and the index information in {\tt loc\_params}.
  \item {\tt size\_t buf\_size} (IN): the size of the buffer to store
    the name in.
  \item {\tt void *buf} (OUT): Buffer to store the name in.
  \item {\tt ssize\_t *ret\_val} (OUT): return the actual size needed
    to store the fill attribute name.
  \end{enumerate}

\item {\tt H5VL\_ATTR\_GET\_SPACE}, to retrieve the dataspace of the
  attribute specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    attribute dataspace.
  \end{enumerate}

\item {\tt H5VL\_ATTR\_GET\_STORAGE\_SIZE}, to retrieve the storage
  size of the attribute specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hsize\_t *ret} (OUT): buffer for the storage size of
    the attribute in the container.
  \end{enumerate}

\item {\tt H5VL\_ATTR\_GET\_TYPE}, to retrieve the datatype of the
  attribute specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    attribute datatype.
  \end{enumerate}

\end{itemize}

The {\tt specific} callback in the attribute class implements specific operations on HDF5 attributes as specified in the {\tt
  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

The {\tt specific\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for attribute SPECFIC callback */
typedef enum H5VL_attr_specific_t {
    H5VL_ATTR_DELETE,                 /* H5Adelete(_by_name/idx) */
    H5VL_ATTR_EXISTS,                 /* H5Aexists(_by_name) */
    H5VL_ATTR_ITER,                   /* H5Aiterate(_by_name) */
    H5VL_ATTR_RENAME                  /* H5Arename(_by_name) */
} H5VL_attr_specific_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The location object  where the operation needs to happen.\\
  {\tt loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
  {\tt specific\_type} & (IN): The type of the operation.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt specific\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_ATTR\_DELETE}, to delete an attribute on an object:
  \begin{enumerate}
  \item {\tt char *attr\_name} (IN): the name of the attribute to delete.
  \end{enumerate}

\item {\tt H5VL\_ATTR\_EXISTS}, to check if an attribute exists on a
  particular object specified in {\tt obj}:
  \begin{enumerate}
  \item {\tt H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
    explained in section~\ref{sec:map}.
  \item {\tt char *attr\_name} (IN): the attribute name to check.
  \item {\tt htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
  \end{enumerate}

\item {\tt H5VL\_ATTR\_ITER}, to iterate over all attributes of an object and call a user specified callback on each one:
  \begin{enumerate}
  \item {\tt H5\_index\_t idx\_type} (IN): Type of index.\\
  \item {\tt H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
  \item {\tt hsize\_t *idx} (IN/OUT): Initial and return offset within index.\\
  \item {\tt H5A\_operator2\_t op} (IN): User-defined function to pass each attribute to. \\
  \item {\tt void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
  \end{enumerate}

\item {\tt H5VL\_ATTR\_RENAME}, to rename an attribute on an object:
  \begin{enumerate}
  \item {\tt char *old\_name} (IN): the original name of the attribute.
  \item {\tt char *new\_name} (IN): the new name to assign for the attribute.
  \end{enumerate}

\end{itemize}

The {\tt optional} callback in the attribute class implements plugin specific operations on an HDF5 attribute. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
\end{tabular}

Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.

The {\tt close} callback in the attribute class should terminate
access to the attribute object and free all resources it was
consuming, and returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*close)(void *attr, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt attr} & (IN): Pointer to the attribute object.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

\subsection{The Named Datatype Function Callbacks}
The HDF5 datatype routines (H5T) allow users to create and manage HDF5
datatypes. Those routines are divided into two categories. One that
operates on all types of datatypes but do not modify the contents of
the container (all in memory), and others that operate on named
datatypes by accessing the container. When a user creates an HDF5
datatype, it is still an object in memory space (transient datatype)
that has not been added to the HDF5 containers. Only when a user
commits the HDF5 datatype, it becomes persistent in the
container. Those are called named/committed datatypes. The transient
H5T routines should work on named datatypes nevertheless.

All the H5T API routines that modify the HDF5 container map to one of
the named datatype callback routines in this class that the plugin needs to
implement:

\begin{lstlisting}
typedef struct H5VL_datatype_class_t {
    void *(*commit)(void *obj, H5VL_loc_params_t loc_params, 
        const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, 
        hid_t tapl_id, hid_t dxpl_id, void **req);

    void *(*open) (void *obj, H5VL_loc_params_t loc_params, 
        const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);

    ssize_t (*get_binary)(void *obj, unsigned char *buf, size_t size, 
        hid_t dxpl_id, void **req);

    herr_t (*get) (void *obj, H5VL_datatype_get_t get_type, 
        hid_t dxpl_id, void **req, va_list arguments);

    herr_t (*close) (void *dt, hid_t dxpl_id, void **req);
} H5VL_datatype_class_t;
\end{lstlisting}

The {\tt commit} callback in the named datatype class should create a datatype object in the container of the location object and
returns a pointer to the datatype structure containing information to
access the datatype in future calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*commit)(void *obj, H5VL_loc_params_t loc_params, 
        const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, 
        hid_t tapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the datatype needs
  to be committed or where the look-up of the target object needs to
  start.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map}. In this call, the location type is always {\tt
    H5VL\_OBJECT\_BY\_SELF}. \\
  {\tt name} & (IN): The name of the datatype to be created.\\
  {\tt type\_id} & (IN): The transient datatype identifier to be
  committed. \\
  {\tt lcpl\_id} & (IN): The link creation property list. \\
  {\tt tcpl\_id} & (IN): The datatype creation property list.\\
  {\tt tapl\_id} & (IN): The datatype access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt open} callback in the named datatype class should open a
previously committed datatype object in the container of the location
object and returns a pointer to the datatype structure containing
information to access the datatype in future calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*open) (void *obj, H5VL_loc_params_t loc_params, 
        const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the datatype needs
  to be opened or where the look-up of the target object needs to
  start.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map}. In this call, the location type is always {\tt
    H5VL\_OBJECT\_BY\_SELF}. \\
  {\tt name} & (IN): The name of the datatype to be opened.\\
  {\tt tapl\_id} & (IN): The datatype access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt get\_binary} callback in the named datatype class should
serialize the original transient HDF5 datatype that was committed, or
return the size that is required for it be serialized if the passed in
buffer is {\tt NULL}. The HDF5 library provides two functions to
encode and decode datatypes in their transient form, {\tt H5Tencode()}
and {\tt H5Tdecode()}. When a datatype is committed, the plugin is
required to keep the serialized form of the transient datatype stored
somewhere in the container (which is usually the case anyway when
committing a named datatype), so it can be retrieved with this
call. This is needed to generate the higher level HDF5 datatype
identifier that allows all the H5T ``transient'' routines to work
properly on the named datatype.

\textbf{Signature:}
\begin{lstlisting}
    ssize_t (*get_binary)(void *obj, unsigned char *buf, size_t size, 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to the named datatype object.\\
  {\tt buf} & (OUT): Buffer to out the binary form of the datatype in.\\
  {\tt size} & (IN): The size of the buffer passed in (0 if NULL).\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt get} callback in the named datatype class should retrieve
information about the named datatype as specified in the {\tt get\_type}
parameter.It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*get) (void *obj, H5VL_datatype_get_t get_type, 
        hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all datatype get API routines */
typedef enum H5VL_datatype_get_t {
    H5VL_DATATYPE_GET_TCPL   /*datatype creation property list */
} H5VL_datatype_get_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The named datatype to retrieve information from.\\
  {\tt get\_type} & (IN): The type of the information to retrieve.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt get\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_DATATYPE\_GET\_TCPL}, to retrieve the datatype
  creation property list:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
    type creation property list.
  \end{enumerate}
\end{itemize}

The {\tt optional} callback in the datatype class implements plugin specific operations on an HDF5 datatype. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
\end{tabular}

Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.

The {\tt close} callback in the named datatype class should terminate
access to the datatype object and free all resources it was
consuming, and returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*close) (void *dt, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt dt} & (IN): Pointer to the datatype object.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

\subsection{The Object Function Callbacks}
The object API routines (H5O) allow HDF5 users to manage HDF5 group,
dataset, and named datatype objects. All the H5O API routines that
modify the HDF5 container map to one of the object callback routines
in this class that the plugin needs to implement:

\begin{lstlisting}
typedef struct H5VL_object_class_t {
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
        H5I_type_t *opened_type, hid_t dxpl_id, void **req);

    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, 
        const char *src_name, void *dst_obj, 
        H5VL_loc_params_t loc_params2, const char *dst_name,
        hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);

    herr_t (*visit)(void *obj, H5VL_loc_params_t loc_params, 
        H5_index_t idx_type, H5_iter_order_t order, 
        H5O_iterate_t op, void *op_data, hid_t dxpl_id, void **req);

    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_object_get_t get_type, hid_t dxpl_id, 
        void **req, va_list arguments);

    herr_t (*misc)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_object_misc_t misc_type, hid_t dxpl_id, 
        void **req, va_list arguments);

    MSC - NOT USED
    herr_t (*optional)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_object_optional_t op_type, hid_t dxpl_id, 
        void **req, va_list arguments);

    MSC - NOT USED
    herr_t (*close) (void *obj, H5VL_loc_params_t loc_params, 
        hid_t dxpl_id, void **req);
} H5VL_object_class_t;
\end{lstlisting}

The {\tt open} callback in the object class should open the object in
the container of the location object and returns a pointer to the
object structure containing information to access the object in future
calls.

\textbf{Signature:}
\begin{lstlisting}
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
        H5I_type_t *opened_type, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to a file or group where the objecy needs to be
  opened or where the look-up of the target object needs to start.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map}.\\
  {\tt opened\_type} & (OUT): buffer to return the type of the object
  opened ({\tt H5I\_GROUP} or {\tt H5I\_DATASET} or {\tt H5I\_DATATYPE}).\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt copy} callback in the object class should copy the object
from the source object to the destination object. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, 
        const char *src_name, void *dst_obj, 
        H5VL_loc_params_t loc_params2, const char *dst_name,
        hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt src\_obj} & (IN): Pointer to location of the source object to
  be copied.\\
  {\tt loc\_params1} & (IN): The location parameters as explained in
  section~\ref{sec:map}. The type should only be {\tt
    H5VL\_OBJECT\_BY\_SELF} for this callback.\\
  {\tt src\_name} & (IN): Name of the source object to
  be copied.\\
  {\tt dst\_obj} & (IN): Pointer to location of the destination
  object.\\
  {\tt loc\_params2} & (IN): The location parameters as explained in
  section~\ref{sec:map}. The type should only be {\tt
    H5VL\_OBJECT\_BY\_SELF} for this callback.\\
  {\tt dst\_name} & (IN): Name to be assigned to the new copy.\\
  {\tt ocpypl\_id} & (IN): The object copy property list.\\
  {\tt lcpl\_id} & (IN): The link creation property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt visit} callback in the object class should recursively visit
all objects accessible from a specified object and call the
user defined function on each one. It returns an {\tt herr\_t}
indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*visit)(void *obj, H5VL_loc_params_t loc_params, 
        H5_index_t idx_type, H5_iter_order_t order, 
        H5O_iterate_t op, void *op_data, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): Pointer to an object where the iteration needs
  to happen or where the look-up of the target object needs to
  start.\\
  {\tt loc\_params} & (IN): The location parameters as
  explained in section~\ref{sec:map}. The type could be {\tt
    H5VL\_OBJECT\_BY\_SELF} or {\tt
    H5VL\_OBJECT\_BY\_NAME} for this callback.\\
  {\tt idx\_type} & (IN): Type of index.\\
  {\tt order} & (IN): Order in which to iterate over index.\\
  {\tt op} & (IN): User-defined function to pass each object to.\\
  {\tt op\_data} & (IN/OUT): User data to pass through to and to be
  returned by iterator operator function. \\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt get} callback in the object class should retrieve information
about the object as specified in the {\tt get\_type} parameter.It
returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_object_get_t get_type, hid_t dxpl_id, 
        void **req, va_list arguments);
\end{lstlisting}

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all object get API routines */
typedef enum H5VL_object_get_t {
    H5VL_OBJECT_EXISTS,      /* Object exists?       */
    H5VL_OBJECT_GET_INFO,    /* object info          */
    H5VL_OBJECT_GET_COMMENT, /* object comment       */
    H5VL_REF_GET_REGION,     /* dataspace of region  */
    H5VL_REF_GET_TYPE,       /* type of object       */
    H5VL_REF_GET_NAME        /* object name          */
} H5VL_object_get_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): A location object where information needs to be
  retrieved from.\\
  {\tt loc\_params} & (IN): The location parameters as
  explained in section~\ref{sec:map}.\\
  {\tt get\_type} & (IN): The type of the information to retrieve.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt get\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_OBJECT\_EXISTS}, to check if an object with name
  specified in {\tt loc\_params} (type {\tt H5VL\_OBJECT\_BY\_NAME})
  exists:
  \begin{enumerate}
  \item {\tt htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_GET\_INFO}, to retrieve object info:
  \begin{enumerate}
  \item {\tt H5O\_info\_t *oinfo} (OUT): info structure to fill the
    object info in.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_GET\_COMMENT}, to retrieve the comment on the
  object specified with {\tt obj} and {\tt loc\_params} which could
  have types {\tt H5VL\_OBJECT\_BY\_SELF} or {\tt
    H5VL\_OBJECT\_BY\_NAME} here:
  \begin{enumerate}
  \item {\tt void *} (OUT): Buffer to store the comment in.
  \item {\tt size\_t buf\_size} (IN): the size of the buffer passed in.
  \item {\tt ssize\_t *ret} (OUT): return the actual size needed
    to store the comment.
  \end{enumerate}

\item {\tt H5VL\_REF\_GET\_REGION}, to retrieve a region reference
  contained in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the dataspace created
    from the region reference.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference
    (should be {\tt H5R\_DATASET\_REGION}.
  \item {\tt void *ref} (IN): the region reference to open.
  \end{enumerate}

\item {\tt H5VL\_REF\_GET\_TYPE}, to retrieve object type a reference
  points to:
  \begin{enumerate}
  \item {\tt H5O\_type\_t *type} (OUT): buffer to return the object type.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
    query.
  \item {\tt void *ref} (IN): the region reference to query.
  \end{enumerate}

\item {\tt H5VL\_REF\_GET\_NAME}, to retrieve a name for a referenced object:
  \begin{enumerate}
  \item {\tt ssize\_t *ret} (OUT): buffer to return the length of the
    name.
  \item {\tt char* name} (OUT): buffer to copy the name into.
  \item {\tt size\_t size} (IN): size of the buffer name, if 0, return
    only the buffer size needed.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
    query.
  \item {\tt void *ref} (IN): the region reference to query.
  \end{enumerate}
\end{itemize}

The {\tt misc} callback in the object class should execute operations
in the container on objects as specified in the {\tt misc\_type}
parameter.It returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*misc)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_object_misc_t misc_type, hid_t dxpl_id, 
        void **req, va_list arguments);
\end{lstlisting}

The {\tt misc\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all object general operations */
typedef enum H5VL_object_misc_t {
    H5VL_ATTR_RENAME,               /* H5Arename                 */
    H5VL_OBJECT_CHANGE_REF_COUNT,   /* H5Oincr/decr_refcount     */
    H5VL_OBJECT_SET_COMMENT,        /* H5Oset_comment(_by_name)  */
    H5VL_REF_CREATE                 /* H5Rcreate                 */
} H5VL_object_misc_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): A location object for the operation.\\
  {\tt loc\_params} & (IN): The location parameters as
  explained in section~\ref{sec:map}.\\
  {\tt misc\_type} & (IN): The type of the operation.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the misc operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt misc\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_ATTR\_RENAME}, to rename an attribute under the
  location object where the {\tt loc\_params} could have types {\tt
    H5VL\_OBJECT\_BY\_SELF} or {\tt H5VL\_OBJECT\_BY\_NAME}:
  \begin{enumerate}
  \item {\tt char *old\_name} (IN): old name of the attribute to
    rename.
  \item {\tt char *new\_name} (IN): the new attribute name to set for
    the attribute.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_CHANGE\_REF\_COUNT}, to update the reference
  count for the object in {\tt obj}:
  \begin{enumerate}
  \item {\tt int ref\_count} (IN): reference count to set on the object.
  \end{enumerate}

\item {\tt H5VL\_OBJECT\_SET\_COMMENT}, to set a comment on the object
  where the {\tt loc\_params} could have types {\tt
    H5VL\_OBJECT\_BY\_SELF} or {\tt H5VL\_OBJECT\_BY\_NAME}:
  \begin{enumerate}
  \item {\tt char *comment} (IN): comment to set on the object.
  \end{enumerate}

\item {\tt H5VL\_REF\_CREATE}, to create a reference of an object
  under the location object {\tt obj}:
  \begin{enumerate}
  \item {\tt void *ref} (OUT): the region reference created.
  \item {\tt char* name} (IN): Name of the object at the location {\tt
      obj}.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
    create.
  \item {\tt hid\_t* space\_id} (IN): Dataspace identifier with
    selection. Used only for dataset region references; passed as -1 if
    reference is an object reference, i.e., of type {\tt H5R\_OBJECT}.
  \end{enumerate}
\end{itemize}

The {\tt optional} callback in the object class implements plugin specific operations on an HDF5 object. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
\end{tabular}

Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.

\subsection{The Link Function Callbacks}
The link API routines (H5L) allow HDF5 users to create and manage
HDF5 links. All the H5L API routines that modify the HDF5 container
map to one of the link callback routines in this class that the
plugin needs to implement:

\begin{lstlisting}
typedef struct H5VL_link_class_t {
    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj,
        H5VL_loc_params_t loc_params, hid_t lcpl_id, 
        hid_t lapl_id, hid_t dxpl_id, void **req);

    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1,
        void *dst_obj, H5VL_loc_params_t loc_params2,
        hbool_t copy_flag, hid_t lcpl, hid_t lapl, 
        hid_t dxpl_id, void **req);

    herr_t (*iterate)(void *obj, H5VL_loc_params_t loc_params, 
        hbool_t recursive, H5_index_t idx_type, H5_iter_order_t order, 
        hsize_t *idx, H5L_iterate_t op, void *op_data, hid_t dxpl_id, 
        void **req);

    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_link_get_t get_type, hid_t dxpl_id, void **req, 
        va_list arguments);

    herr_t (*remove)(void *obj, H5VL_loc_params_t loc_params, 
        hid_t dxpl_id, void **req);
} H5VL_link_class_t;
\end{lstlisting}

The {\tt create} callback in the group class should create a hard,
soft, external, or user-defined links in the container. It returns an
{\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj,
        H5VL_loc_params_t loc_params, hid_t lcpl_id, 
        hid_t lapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

The {\tt create\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* link create types for VOL */
typedef enum H5VL_link_create_type_t {
    H5VL_LINK_CREATE_HARD,  /* Hard Link          */
    H5VL_LINK_CREATE_SOFT,  /* Soft Link          */
    H5VL_LINK_CREATE_UD     /* External / UD Link */
} H5VL_link_create_type_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt create\_type} & (IN): type of the link to be created.\\
  {\tt obj} & (IN): Pointer to an object where the link needs to be
  created from.\\
  {\tt loc\_params} & (IN): The location parameters as explained in
  section~\ref{sec:map} for the source object. \\
  {\tt lcpl\_id} & (IN): The link creation property list. It contains
  all the link creation properties in addition to other API parameters
  depending on the creation type, which will be detailed next.\\
  {\tt lapl\_id} & (IN): The link access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

As mentioned in the argument list, the {\tt lcpl\_id} contains the
parameters for the link creation operation depending on the creation
type:
\begin{itemize}
\item {\tt H5VL\_LINK\_CREATE\_HARD} contains two properties:
  \begin{enumerate}
  \item {\tt H5VL\_LINK\_TARGET} (with type {\tt void*}): The target
    object where the hard link needs to be created to.
  \item {\tt H5VL\_LINK\_TARGET\_LOC\_PARAMS} (with type {\tt
      H5VL\_loc\_params\_t}): The location parameters as explained in
    section~\ref{sec:map} for the target object.
  \end{enumerate}

\item {\tt H5VL\_LINK\_CREATE\_SOFT} contains one property:
  \begin{enumerate}
  \item {\tt H5VL\_LINK\_TARGET\_NAME} (with type {\tt char*}): The target
    link where the soft link should point to.
  \end{enumerate}

\item {\tt H5VL\_LINK\_CREATE\_UD} contains two properties:
  \begin{enumerate}
  \item {\tt H5VL\_LINK\_TYPE} (with type {\tt H5L\_type\_t}): The
    user defined link class. {\tt H5L\_TYPE\_EXTERNAL} suggests an
    external link is to be created.
  \item {\tt H5VL\_LINK\_UDATA} (with type {\tt void*}): User supplied
    link information (contains the external link buffer for external
    links). 
  \item {\tt H5VL\_LINK\_UDATA\_SIZE} (with type {\tt size\_t}): size
    of the {\tt udata} buffer. 
  \end{enumerate}
\end{itemize}

The {\tt move} callback in the link class should copy or move a link
within the HDF5 container. It returns an {\tt herr\_t} indicating
success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1,
        void *dst_obj, H5VL_loc_params_t loc_params2,
        hbool_t copy_flag, hid_t lcpl, hid_t lapl, 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt src\_obj} & (IN): original/source object or file. \\
  {\tt loc\_params1} & (IN): The location parameters for the source
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  {\tt dst\_obj} & (IN): destination object or file. \\
  {\tt loc\_params1} & (IN): The location parameters for the destination
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  {\tt copy\_flag} & (IN): flag to indicate whether link is to be
  copied (value 1) or moved (value 0).\\
  {\tt lcpl\_id} & (IN): The link creation property list.\\
  {\tt lapl\_id} & (IN): The link access property list.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt iterate} callback in the link class should iterate over links
in a group and apply a user defined routine. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*iterate)(void *obj, H5VL_loc_params_t loc_params, 
        hbool_t recursive, H5_index_t idx_type, H5_iter_order_t order, 
        hsize_t *idx, H5L_iterate_t op, void *op_data, hid_t dxpl_id, 
        void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): object where to start iteration or where the
  lookup for the target object needs to start. \\
  {\tt loc\_params} & (IN): The location parameters for the source
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} or {\tt H5VL\_OBJECT\_BY\_SELF} in this
  callback.\\ 
  {\tt recursive} & (IN): whether to recursively follow links into
  subgroups of the specified group.\\
  {\tt idx\_type} & (IN): Type of index which determines the order.\\
  {\tt idx} & (IN/OUT): iteration position where to start and return
  position where an interrupted iteration may restart.\\
  {\tt op} & (IN): User-defined function for the iterator.\\
  {\tt op\_data} & (IN/OUT): User data to pass through to and to be
  returned by iterator operator function.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt get} callback in the link class should retrieve information
about links as specified in the {\tt get\_type} parameter. It
returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_link_get_t get_type, hid_t dxpl_id, void **req, 
        va_list arguments);
\end{lstlisting}

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* types for all link get API routines */
typedef enum H5VL_link_get_t {
    H5VL_LINK_EXISTS,          /* link existence  */
    H5VL_LINK_GET_INFO,        /* link info       */
    H5VL_LINK_GET_NAME,        /* link name       */
    H5VL_LINK_GET_VAL          /* link value      */
} H5VL_link_get_t;
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The file or group object where information needs to be
  retrieved from.\\
  {\tt loc\_params} & (IN): The location parameters for the source
  object as explained in section~\ref{sec:map}. The type can be only {\tt
    H5VL\_OBJECT\_BY\_NAME} or {\tt H5VL\_OBJECT\_BY\_IDX} in this
  callback.\\ 
  {\tt get\_type} & (IN): The type of the information to retrieve.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}

The {\tt arguments} argument contains a variable list of arguments
depending on the {\tt get\_type} parameter. The following list shows
the argument list, in-order, for each type:

\begin{itemize}
\item {\tt H5VL\_LINK\_EXITS}, to determine whether the link specified
  in the {\tt loc\_params} exits ({\tt loc\_params} is of type {\tt
    H5VL\_OBJECT\_BY\_NAME} only with this type):
  \begin{enumerate}
  \item {\tt htri\_t *ret} (OUT): buffer for the existence of the link
    (0 for no, 1 for yes).
  \end{enumerate}

\item {\tt H5VL\_LINK\_GET\_INFO}, to retrieve the link info from the
  link specified in the {\tt loc\_params}:
  \begin{enumerate}
  \item {\tt H5L\_info\_t linfo} (OUT): pointer to info structure to
    fill.
  \end{enumerate}

\item {\tt H5VL\_LINK\_GET\_NAME}, to retrieve the name of the link
  specified by the index information in {\tt loc\_params} ({\tt
    loc\_params} is of type {\tt H5VL\_OBJECT\_BY\_IDX} only with this
  type):
  \begin{enumerate}
  \item {\tt char* name} (OUT): buffer to copy the name into.
  \item {\tt size\_t size} (IN): size of the buffer name, if 0, return
    only the buffer size needed.
  \item {\tt ssize\_t *ret} (OUT): buffer to return the length of the
    link name.
  \end{enumerate}

\item {\tt H5VL\_LINK\_GET\_VAL}, to retrieve the link value from the
  link specified in the {\tt loc\_params}:
  \begin{enumerate}
  \item {\tt void *buf} (OUT): buffer to put the value into.
  \item {\tt size\_t size} (IN): size of the passed in buffer.
  \end{enumerate}

\end{itemize}

The {\tt remove} callback in the link class should remove a link from
an HDF5 container, and returns an {\tt herr\_t} indicating success or
failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*remove)(void *obj, H5VL_loc_params_t loc_params, 
        hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): group object or file containing the link.\\
  {\tt loc\_params} & (IN): The location parameters for the link to be
  deleted.The type can be only {\tt H5VL\_OBJECT\_BY\_NAME} or {\tt
    H5VL\_OBJECT\_BY\_IDX} in this callback.\\ 
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the plugin.\\
\end{tabular}

The {\tt optional} callback in the link class implements plugin specific operations on an HDF5 link. It returns an {\tt
  herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
  {\tt dxpl\_id} & (IN): The data transfer property list.\\
  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
\end{tabular}

Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.

\subsection{The Asynchronous Function Callbacks}
As of now, the HDF5 library does not provide asynchronous API
operations. An asynchronous class to manage asynchronous operations
was added nevertheless to handle an asynchronous API that might be
added in the future:

\begin{lstlisting}
typedef struct H5VL_async_class_t {
    herr_t (*cancel)(void **, H5ES_status_t *);

    herr_t (*test)  (void **, H5ES_status_t *);

    herr_t (*wait)  (void **, H5ES_status_t *);
} H5VL_async_class_t;
\end{lstlisting}

The {\tt H5ES\_status\_t} argument is an {\tt enum}:
\begin{lstlisting}
/* Asynchronous operation status */
typedef enum H5ES_status_t {
    H5ES_STATUS_IN_PROGRESS, /* Operation has not yet completed */
    H5ES_STATUS_SUCCEED,     /* Operation has completed, successfully */
    H5ES_STATUS_FAIL,        /* Operation has completed, but failed */
    H5ES_STATUS_CANCEL       /* Operation has not completed and has
                                been cancelled */
} H5ES_status_t;
\end{lstlisting}

The {\tt cancel} callback attempts to cancel an asynchronous operation
and returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*cancel)(void **req, H5ES_status_t *status);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt req} & (IN): A pointer to the asynchronous request.\\
  {\tt status} & (OUT): result of the cancel operation.\\
\end{tabular}

The {\tt test} callback tests an asynchronous operation completion
and returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*test)(void **req, H5ES_status_t *status);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt req} & (IN): A pointer to the asynchronous request.\\
  {\tt status} & (OUT): result of the test operation.\\
\end{tabular}

The {\tt wait} callback waits for an asynchronous operation completion
and returns an {\tt herr\_t} indicating success or failure.

\textbf{Signature:}
\begin{lstlisting}
    herr_t (*wait)(void **req, H5ES_status_t *status);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{10cm}}
  {\tt req} & (IN): A pointer to the asynchronous request.\\
  {\tt status} & (OUT): result of the wait operation.\\
\end{tabular}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2014-09-10 RFCs/HDF5/VOL/user_guide/internal.tex
UG updates
Former-commit-id: b80e6f020c627d40056087212ea138ffcacb3d5f

\section{Creating and Using an Internal Plugin}
Internal plugins are developed internally with the HDF5 library and
are required to ship with the entire library to be used. Typically
those plugins need to use internal features and functions of the HDF5
library that are not available publicly from the user application.

\subsection{Implementing an Internal Plugin}
The first step to implement an internal plugin is to implement all the callbacks defined in the VOL class as described in section~\ref{sec:vol}. After implementing the VOL class, the next step would be to allow users to select
this plugin to be used. This is done by creating a new API routine to
set the plugin on the file access property list. For example, if we
create an internal plugin called ``dummy'' that needs an MPI
communicator and info object as information from the user, that
routine signature should look like:

\begin{lstlisting}
herr_t H5Pset_fapl_dummy(hid_t fapl_id, MPI_Comm comm, MPI_Info info);
\end{lstlisting}

The implementation for the above routine should use the internal
function:
\begin{lstlisting}
herr_t H5P_set_vol(H5P_genplist_t *plist, H5VL_class_t *vol_cls, const
void *vol_info);
\end{lstlisting}
that will set the file access using that {\tt fapl\_id} to go through
the ``dummy'' plugin. It will also call the copy callback of the
``dummy'' plugin on the info object ({\tt comm and info}).

A sample implementation for the {\tt H5Pset\_fapl\_dummy()} would look like this:

\begin{lstlisting}
/* DUMMY-specific file access properties */
typedef struct H5VL_dummy_fapl_t {
    MPI_Comm            comm;     /* communicator       */
    MPI_Info            info;     /* MPI information   */
} H5VL_dummy_fapl_t;

herr_t
H5Pset_fapl_dummy(hid_t fapl_id, MPI_Comm comm, MPI_Info info)
{
    H5VL_dummy_fapl_t fa;
    H5P_genplist_t  *plist;      /* Property list pointer */
    herr_t          ret_value;

    FUNC_ENTER_API(FAIL)

    if(fapl_id == H5P_DEFAULT)
        HGOTO_ERROR(H5E_PLIST, H5E_BADVALUE, FAIL, "can't set values in default property list")

    if(NULL == (plist = H5P_object_verify(fapl_id, H5P_FILE_ACCESS)))
        HGOTO_ERROR(H5E_ARGS, H5E_BADTYPE, FAIL, "not a file access property list")

    if(MPI_COMM_NULL == comm)
	HGOTO_ERROR(H5E_PLIST, H5E_BADTYPE, FAIL, "not a valid communicator")

    /* Initialize driver specific properties */
    fa.comm = comm;
    fa.info = info;

    ret_value = H5P_set_vol(plist, &H5VL_dummy_g, &fa);

done:
    FUNC_LEAVE_API(ret_value)
} /* end H5Pset_fapl_dummy() */
\end{lstlisting}

At this point, the internal plugin is ready to be used. For more
information on how to implement an internal plugin, the native plugin
for the HDF5 library is a comprehensive plugin that implements all
features of the library and can be used as a guide.

\subsection{Using an Internal Plugin}
An internal plugin is registered automatically with the HDF5 library when the library gets initialized. Users should not attempt to register an internal plugin. The internal registration operation creates a global identifier for each internal plugin. Applications can query the library for that identifier using the plugin name with {\tt H5VLget\_plugin\_id()}. This identifier is used to initialize the plugin if it requires an initialization phase. A third party library could use that ID to create a plugin that stacks or mirrors on top of an internal plugin using that identifier (refer to section~\ref{sec:stack} for more details on stacking and mirroring).

Some plugins could require an initialization phase before using the plugin with some input parameters from users. For example, a remote plugin would need to setup a connection to a remote machine with a specific hostname that the user knows and the HDF5 library does not know about. This process is done by creating a VOL initialization property list and setting a public property that should be defined by the internal plugin to the hostname of the remote machine. The user then calls the initialize routine ({\tt H5VLintialize()}) with the plugin\_id and the property list to initialize the plugin. Some plugins could create a public API routine that wraps the property list creation, property settings, and plugin initialization into one routine that the user calls to simplify this process for the users. The native HDF5 plugin does not require an initialization phase.

Now that the plugin is initialized, the application can create or open an HDF5 container using the internal plugin by creating a file access property list and calling the corresponding API routine that the internal plugin should define for setting the VOL plugin property and container parameters on the file access property list. That FAPL can be passed to the {\tt H5Fcreate()} or {\tt H5Fopen{}} calls to access the container through the VOL plugin. Subsequently, all other HDF5 calls on the container and objects created or opened in that container will automatically go to the selected VOL plugin.

After closing all objects and containers on that plugin, the application should terminate access to the selected plugin if it requires a termination phase by calling {\tt H5VLterminate()} with the required termination properties (similar to the initialization phase). The native HDF5 plugin does not require a termination phase.

The internal plugin is unregistered automatically by the HDF5 library on library termination, and users should not attempt to unregister it themselves.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2014-09-10 RFCs/HDF5/VOL/user_guide/new_api.tex
UG updates
Former-commit-id: b80e6f020c627d40056087212ea138ffcacb3d5f

\section{New VOL API Routines}
New API routines have been added to the HDF5 library to manage VOL plugins. This section details each new API call and explains their intended usage.

\begin{lstlisting}
  hid_t H5VLobject_register(void *obj, H5I_type_t obj_type, const H5VL_class_t *cls);
\end{lstlisting}
to register an {\tt hid\_t} with an object {\tt obj} associated with
the VOL plugin of class {\tt cls}. This is needed in all iterate and
visit callbacks where the plugins internally need to wrap an {\tt
  hid\_t} around an object to call the user defined operation {\tt op}
on.

\begin{lstlisting}
  herr_t H5VLget_object(hid_t obj_id, void **obj, H5VL_t **vol_plugin);
\end{lstlisting}
to retrieve the VOL object and plugin structure from an HDF5
identifier ({\tt hid\_t}). The plugin structure is defined as:
\begin{lstlisting}
struct H5VL_t {
    const H5VL_class_t *cls;     /* constant class info */
    const char *container_name;  /* name of the underlying storage 
                                    container */
    unsigned long feature_flags; /* VOL Driver feature Flags */
    int nrefs;                   /* number of references by objects
                                    using this struct */
};
\end{lstlisting}

% H5_DLL void *H5Pget_vol_info(hid_t plist_id);
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2014-09-10 RFCs/HDF5/VOL/user_guide/plugin.tex
UG updates
Former-commit-id: b80e6f020c627d40056087212ea138ffcacb3d5f

@@
 
-The {\tt set\_extent} callback in the dataset class should extend the
-dataset dimensions and returns an {\tt herr\_t} indicating success or
-failure.
-
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*set_extent)(void *dset, const hsize_t size[], 
-        hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
-  {\tt dset} & (IN): Pointer to the dataset object.\\
-  {\tt size} & (IN): new dimensions of the dataset.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
 The {\tt get} callback in the dataset class should retrieve
@@
 typedef struct H5VL_datatype_class_t {
-    void *(*commit)(void *obj, H5VL_loc_params_t loc_params, 
-        const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, 
-        hid_t tapl_id, hid_t dxpl_id, void **req);
-
-    void *(*open) (void *obj, H5VL_loc_params_t loc_params, 
-        const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);
-
-    ssize_t (*get_binary)(void *obj, unsigned char *buf, size_t size, 
-        hid_t dxpl_id, void **req);
-
-    herr_t (*get) (void *obj, H5VL_datatype_get_t get_type, 
-        hid_t dxpl_id, void **req, va_list arguments);
-
+    void *(*commit)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
+    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);
+    herr_t (*get)   (void *obj, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*specific)(void *obj, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
     herr_t (*close) (void *dt, hid_t dxpl_id, void **req);
@@
 The {\tt commit} callback in the named datatype class should create a datatype object in the container of the location object and
-returns a pointer to the datatype structure containing information to
-access the datatype in future calls.
+returns a pointer to the datatype structure containing information to access the datatype in future calls.
 
@@
 \begin{lstlisting}
-/* types for all datatype get API routines */
+/* types for datatype GET callback */
 typedef enum H5VL_datatype_get_t {
-    H5VL_DATATYPE_GET_TCPL   /*datatype creation property list */
+    H5VL_DATATYPE_GET_BINARY,               /* get serialized form of transient type */
+    H5VL_DATATYPE_GET_TCPL                  /* datatype creation property list     */
 } H5VL_datatype_get_t;
@@
 \begin{itemize}
+\item {\tt H5VL\_DATATYPE\_GET\_BINARY}, to retrieve the serialized original transient HDF5 datatype that was committed, or
+return the size that is required for it be serialized if the passed in buffer is {\tt NULL}. The HDF5 library provides two functions to
+encode and decode datatypes in their transient form, {\tt H5Tencode()} and {\tt H5Tdecode()}.
+When a datatype is committed, the plugin is required to keep the serialized form of the transient datatype stored somewhere in the container (which is usually the case anyway when committing a named datatype), so it can be retrieved with this call.
+This is needed to generate the higher level HDF5 datatype identifier that allows all the H5T ``transient'' routines to work properly on the named datatype.
+  \begin{enumerate}
+  \item {\tt ssize\_t *nalloc} (OUT): buffer to store the total size of the serialized datatype.
+  \item {\tt void *buf} (OUT): buffer to store the serialized datatype.
+  \item {\tt size\_t size} (IN): size of the passed in buffer.
+  \end{enumerate}
+
 \item {\tt H5VL\_DATATYPE\_GET\_TCPL}, to retrieve the datatype
@@
 \end{itemize}
+
+The {\tt specific} callback in the datatype class currently does not require any functionality to be implemented and should be left as {\tt NULL}.
 
@@
 typedef struct H5VL_object_class_t {
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
-        H5I_type_t *opened_type, hid_t dxpl_id, void **req);
-
-    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, 
-        const char *src_name, void *dst_obj, 
-        H5VL_loc_params_t loc_params2, const char *dst_name,
-        hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
-
-    herr_t (*visit)(void *obj, H5VL_loc_params_t loc_params, 
-        H5_index_t idx_type, H5_iter_order_t order, 
-        H5O_iterate_t op, void *op_data, hid_t dxpl_id, void **req);
-
-    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
-        H5VL_object_get_t get_type, hid_t dxpl_id, 
-        void **req, va_list arguments);
-
-    herr_t (*misc)(void *obj, H5VL_loc_params_t loc_params, 
-        H5VL_object_misc_t misc_type, hid_t dxpl_id, 
-        void **req, va_list arguments);
-
-    MSC - NOT USED
-    herr_t (*optional)(void *obj, H5VL_loc_params_t loc_params, 
-        H5VL_object_optional_t op_type, hid_t dxpl_id, 
-        void **req, va_list arguments);
-
-    MSC - NOT USED
-    herr_t (*close) (void *obj, H5VL_loc_params_t loc_params, 
-        hid_t dxpl_id, void **req);
+    void *(*open)(void *obj, H5VL_loc_params_t loc_params, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
+    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, const char *src_name, void *dst_obj, H5VL_loc_params_t loc_params2, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
+    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
 } H5VL_object_class_t;
@@
 
-The {\tt visit} callback in the object class should recursively visit
-all objects accessible from a specified object and call the
-user defined function on each one. It returns an {\tt herr\_t}
-indicating success or failure.
-
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*visit)(void *obj, H5VL_loc_params_t loc_params, 
-        H5_index_t idx_type, H5_iter_order_t order, 
-        H5O_iterate_t op, void *op_data, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to an object where the iteration needs
-  to happen or where the look-up of the target object needs to
-  start.\\
-  {\tt loc\_params} & (IN): The location parameters as
-  explained in section~\ref{sec:map}. The type could be {\tt
-    H5VL\_OBJECT\_BY\_SELF} or {\tt
-    H5VL\_OBJECT\_BY\_NAME} for this callback.\\
-  {\tt idx\_type} & (IN): Type of index.\\
-  {\tt order} & (IN): Order in which to iterate over index.\\
-  {\tt op} & (IN): User-defined function to pass each object to.\\
-  {\tt op\_data} & (IN/OUT): User data to pass through to and to be
-  returned by iterator operator function. \\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
 The {\tt get} callback in the object class should retrieve information
@@
 \begin{lstlisting}
-/* types for all object get API routines */
+r object GET callback */
 typedef enum H5VL_object_get_t {
-    H5VL_OBJECT_EXISTS,      /* Object exists?       */
-    H5VL_OBJECT_GET_INFO,    /* object info          */
-    H5VL_OBJECT_GET_COMMENT, /* object comment       */
+    H5VL_REF_GET_NAME,                 /* object name                       */
     H5VL_REF_GET_REGION,               /* dataspace of region               */
-    H5VL_REF_GET_TYPE,       /* type of object       */
-    H5VL_REF_GET_NAME        /* object name          */
+    H5VL_REF_GET_TYPE                  /* type of object                    */
 } H5VL_object_get_t;
@@
 \begin{itemize}
-\item {\tt H5VL\_OBJECT\_EXISTS}, to check if an object with name
-  specified in {\tt loc\_params} (type {\tt H5VL\_OBJECT\_BY\_NAME})
-  exists:
-  \begin{enumerate}
-  \item {\tt htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
-  \end{enumerate}
-
-\item {\tt H5VL\_OBJECT\_GET\_INFO}, to retrieve object info:
-  \begin{enumerate}
-  \item {\tt H5O\_info\_t *oinfo} (OUT): info structure to fill the
-    object info in.
-  \end{enumerate}
-
-\item {\tt H5VL\_OBJECT\_GET\_COMMENT}, to retrieve the comment on the
-  object specified with {\tt obj} and {\tt loc\_params} which could
-  have types {\tt H5VL\_OBJECT\_BY\_SELF} or {\tt
-    H5VL\_OBJECT\_BY\_NAME} here:
-  \begin{enumerate}
-  \item {\tt void *} (OUT): Buffer to store the comment in.
-  \item {\tt size\_t buf\_size} (IN): the size of the buffer passed in.
-  \item {\tt ssize\_t *ret} (OUT): return the actual size needed
-    to store the comment.
-  \end{enumerate}
-
-\item {\tt H5VL\_REF\_GET\_REGION}, to retrieve a region reference
-  contained in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the dataspace created
-    from the region reference.
-  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference
-    (should be {\tt H5R\_DATASET\_REGION}.
-  \item {\tt void *ref} (IN): the region reference to open.
-  \end{enumerate}
-
-\item {\tt H5VL\_REF\_GET\_TYPE}, to retrieve object type a reference
-  points to:
-  \begin{enumerate}
-  \item {\tt H5O\_type\_t *type} (OUT): buffer to return the object type.
-  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
-    query.
-  \item {\tt void *ref} (IN): the region reference to query.
-  \end{enumerate}
-
 \item {\tt H5VL\_REF\_GET\_NAME}, to retrieve a name for a referenced object:
@@
   \end{enumerate}
+
+\item {\tt H5VL\_REF\_GET\_REGION}, to retrieve a region reference
+  contained in {\tt obj}:
+  \begin{enumerate}
+  \item {\tt hid\_t *ret\_id} (OUT): buffer for the dataspace created
+    from the region reference.
+  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference
+    (should be {\tt H5R\_DATASET\_REGION}.
+  \item {\tt void *ref} (IN): the region reference to open.
+  \end{enumerate}
+
+\item {\tt H5VL\_REF\_GET\_TYPE}, to retrieve object type a reference
+  points to:
+  \begin{enumerate}
+  \item {\tt H5O\_type\_t *type} (OUT): buffer to return the object type.
+  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
+    query.
+  \item {\tt void *ref} (IN): the region reference to query.
+  \end{enumerate}
 \end{itemize}
 
-The {\tt misc} callback in the object class should execute operations
-in the container on objects as specified in the {\tt misc\_type}
-parameter.It returns an {\tt herr\_t} indicating success or failure.
-
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*misc)(void *obj, H5VL_loc_params_t loc_params, 
-        H5VL_object_misc_t misc_type, hid_t dxpl_id, 
-        void **req, va_list arguments);
-\end{lstlisting}
-
-The {\tt misc\_type} argument is an {\tt enum}:
-\begin{lstlisting}
-/* types for all object general operations */
-typedef enum H5VL_object_misc_t {
-    H5VL_ATTR_RENAME,               /* H5Arename                 */
+The {\tt specific} callback in the object class implements specific operations on HDF5 objects as specified in the {\tt
+  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.
+
+\textbf{Signature:}
+\begin{lstlisting}
+	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+The {\tt specific\_type} argument is an {\tt enum}:
+\begin{lstlisting}
+/* types for object SPECIFIC callback */
+typedef enum H5VL_object_specific_t {
     H5VL_OBJECT_CHANGE_REF_COUNT,      /* H5Oincr/decr_refcount              */
-    H5VL_OBJECT_SET_COMMENT,        /* H5Oset_comment(_by_name)  */
+    H5VL_OBJECT_EXISTS,                /* H5Oexists_by_name                  */
+    H5VL_OBJECT_VISIT,                 /* H5Ovisit(_by_name)                 */
     H5VL_REF_CREATE                    /* H5Rcreate                          */
-} H5VL_object_misc_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): A location object for the operation.\\
-  {\tt loc\_params} & (IN): The location parameters as
-  explained in section~\ref{sec:map}.\\
-  {\tt misc\_type} & (IN): The type of the operation.\\
+} H5VL_object_specific_t;
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt obj} & (IN): The location object  where the operation needs to happen.\\
+  {\tt loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
+  {\tt specific\_type} & (IN): The type of the operation.\\
   {\tt dxpl\_id} & (IN): The data transfer property list.\\
@@
   {\tt arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the misc operation. \\
+  output pointers for the get operation. \\
 \end{tabular}
@@
 The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt misc\_type} parameter. The following list shows
+depending on the {\tt specific\_type} parameter. The following list shows
 the argument list, in-order, for each type:
@@
 \begin{itemize}
-\item {\tt H5VL\_ATTR\_RENAME}, to rename an attribute under the
-  location object where the {\tt loc\_params} could have types {\tt
-    H5VL\_OBJECT\_BY\_SELF} or {\tt H5VL\_OBJECT\_BY\_NAME}:
-  \begin{enumerate}
-  \item {\tt char *old\_name} (IN): old name of the attribute to
-    rename.
-  \item {\tt char *new\_name} (IN): the new attribute name to set for
-    the attribute.
-  \end{enumerate}
-
 \item {\tt H5VL\_OBJECT\_CHANGE\_REF\_COUNT}, to update the reference
@@
 
-\item {\tt H5VL\_OBJECT\_SET\_COMMENT}, to set a comment on the object
-  where the {\tt loc\_params} could have types {\tt
-    H5VL\_OBJECT\_BY\_SELF} or {\tt H5VL\_OBJECT\_BY\_NAME}:
-  \begin{enumerate}
-  \item {\tt char *comment} (IN): comment to set on the object.
+\item {\tt H5VL\_OBJECT\_EXISTS}, to check if an object with name
+  specified in {\tt loc\_params} (type {\tt H5VL\_OBJECT\_BY\_NAME})
+  exists:
+  \begin{enumerate}
+  \item {\tt htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
+  \end{enumerate}
+
+\item {\tt H5VL\_OBJECT\_VISIT}, to iterate over all objects starting at the location provided and call a user specified callback on each one:
+  \begin{enumerate}
+  \item {\tt H5\_index\_t idx\_type} (IN): Type of index.\\
+  \item {\tt H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
+  \item {\tt H5O\_iterate\_t op} (IN): User-defined function to pass each object to. \\
+  \item {\tt void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
   \end{enumerate}
@@
 typedef struct H5VL_link_class_t {
-    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj,
-        H5VL_loc_params_t loc_params, hid_t lcpl_id, 
-        hid_t lapl_id, hid_t dxpl_id, void **req);
-
-    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1,
-        void *dst_obj, H5VL_loc_params_t loc_params2,
-        hbool_t copy_flag, hid_t lcpl, hid_t lapl, 
-        hid_t dxpl_id, void **req);
-
-    herr_t (*iterate)(void *obj, H5VL_loc_params_t loc_params, 
-        hbool_t recursive, H5_index_t idx_type, H5_iter_order_t order, 
-        hsize_t *idx, H5L_iterate_t op, void *op_data, hid_t dxpl_id, 
-        void **req);
-
-    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
-        H5VL_link_get_t get_type, hid_t dxpl_id, void **req, 
-        va_list arguments);
-
-    herr_t (*remove)(void *obj, H5VL_loc_params_t loc_params, 
-        hid_t dxpl_id, void **req);
+    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj, H5VL_loc_params_t loc_params, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
+    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
+    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
 } H5VL_link_class_t;
@@
 
-The {\tt move} callback in the link class should copy or move a link
-within the HDF5 container. It returns an {\tt herr\_t} indicating
-success or failure.
-
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1,
-        void *dst_obj, H5VL_loc_params_t loc_params2,
-        hbool_t copy_flag, hid_t lcpl, hid_t lapl, 
-        hid_t dxpl_id, void **req);
+The {\tt move} callback in the link class should move a link within the HDF5 container. It returns an {\tt herr\_t} indicating success or failure.
+
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
     H5VL\_OBJECT\_BY\_NAME} in this callback. \\
-  {\tt copy\_flag} & (IN): flag to indicate whether link is to be
-  copied (value 1) or moved (value 0).\\
   {\tt lcpl\_id} & (IN): The link creation property list.\\
@@
 
-The {\tt iterate} callback in the link class should iterate over links
-in a group and apply a user defined routine. It returns an {\tt
-  herr\_t} indicating success or failure.
-
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*iterate)(void *obj, H5VL_loc_params_t loc_params, 
-        hbool_t recursive, H5_index_t idx_type, H5_iter_order_t order, 
-        hsize_t *idx, H5L_iterate_t op, void *op_data, hid_t dxpl_id, 
-        void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): object where to start iteration or where the
-  lookup for the target object needs to start. \\
-  {\tt loc\_params} & (IN): The location parameters for the source
+The {\tt copy} callback in the link class should copy a link within the HDF5 container. It returns an {\tt herr\_t} indicating success or failure.
+
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt src\_obj} & (IN): original/source object or file. \\
+  {\tt loc\_params1} & (IN): The location parameters for the source
   object as explained in section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_NAME} or {\tt H5VL\_OBJECT\_BY\_SELF} in this
-  callback.\\ 
-  {\tt recursive} & (IN): whether to recursively follow links into
-  subgroups of the specified group.\\
-  {\tt idx\_type} & (IN): Type of index which determines the order.\\
-  {\tt idx} & (IN/OUT): iteration position where to start and return
-  position where an interrupted iteration may restart.\\
-  {\tt op} & (IN): User-defined function for the iterator.\\
-  {\tt op\_data} & (IN/OUT): User data to pass through to and to be
-  returned by iterator operator function.\\
+    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
+  {\tt dst\_obj} & (IN): destination object or file. \\
+  {\tt loc\_params1} & (IN): The location parameters for the destination
+  object as explained in section~\ref{sec:map}. The type can be only {\tt
+    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
+  {\tt lcpl\_id} & (IN): The link creation property list.\\
+  {\tt lapl\_id} & (IN): The link access property list.\\
   {\tt dxpl\_id} & (IN): The data transfer property list.\\
@@
 typedef enum H5VL_link_get_t {
-    H5VL_LINK_EXISTS,          /* link existence  */
     H5VL_LINK_GET_INFO,        /* link info       */
@@
 \begin{itemize}
-\item {\tt H5VL\_LINK\_EXITS}, to determine whether the link specified
-  in the {\tt loc\_params} exits ({\tt loc\_params} is of type {\tt
-    H5VL\_OBJECT\_BY\_NAME} only with this type):
-  \begin{enumerate}
-  \item {\tt htri\_t *ret} (OUT): buffer for the existence of the link
-    (0 for no, 1 for yes).
-  \end{enumerate}
-
 \item {\tt H5VL\_LINK\_GET\_INFO}, to retrieve the link info from the
@@
   \end{enumerate}
-
 \end{itemize}
 
-The {\tt remove} callback in the link class should remove a link from
-an HDF5 container, and returns an {\tt herr\_t} indicating success or
-failure.
-
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*remove)(void *obj, H5VL_loc_params_t loc_params, 
-        hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): group object or file containing the link.\\
-  {\tt loc\_params} & (IN): The location parameters for the link to be
-  deleted.The type can be only {\tt H5VL\_OBJECT\_BY\_NAME} or {\tt
-    H5VL\_OBJECT\_BY\_IDX} in this callback.\\ 
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
+The {\tt specific} callback in the link class implements specific operations on HDF5 links as specified in the {\tt
+  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.
+
+\textbf{Signature:}
+\begin{lstlisting}
+	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+The {\tt specific\_type} argument is an {\tt enum}:
+\begin{lstlisting}
+/* types for link SPECIFIC callback */
+typedef enum H5VL_link_specific_t {
+    H5VL_LINK_DELETE,          /* H5Ldelete(_by_idx)                */
+    H5VL_LINK_EXISTS,          /* link existence                    */
+    H5VL_LINK_ITER             /* H5Literate/visit(_by_name)              */
+} H5VL_link_specific_t;
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt obj} & (IN): The location object  where the operation needs to happen.\\
+  {\tt loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
+  {\tt specific\_type} & (IN): The type of the operation.\\
+  {\tt dxpl\_id} & (IN): The data transfer property list.\\
+  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+
+The {\tt arguments} argument contains a variable list of arguments
+depending on the {\tt specific\_type} parameter. The following list shows
+the argument list, in-order, for each type:
+
+\begin{itemize}
+\item {\tt H5VL\_LINK\_DELETE}, to remove a link specified in the location parameter from an HDF5 container.
+
+\item {\tt H5VL\_LINK\_EXITS}, to determine whether the link specified
+  in the {\tt loc\_params} exits ({\tt loc\_params} is of type {\tt
+    H5VL\_OBJECT\_BY\_NAME} only with this type):
+  \begin{enumerate}
+  \item {\tt htri\_t *ret} (OUT): buffer for the existence of the link
+    (0 for no, 1 for yes).
+  \end{enumerate}
+
+\item {\tt H5VL\_LINK\_ITER}, to iterate over all links starting at the location provided and call a user specified callback on each one:
+  \begin{enumerate}
+  \item {\tt hbool\_t recursive} (IN): whether to recursively follow links into subgroups of the specified group.\\
+  \item {\tt H5\_index\_t idx\_type} (IN): Type of index.\\
+  \item {\tt H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
+  \item {\tt hsize\_t *idx} (IN/OUT):  iteration position where to start and return position where an interrupted iteration may restart.\\
+  \item {\tt H5L\_iterate\_t op} (IN): User-defined function to pass each link to. \\
+  \item {\tt void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
+  \end{enumerate}
+\end{itemize}
 
@@
     herr_t (*cancel)(void **, H5ES_status_t *);
-
     herr_t (*test)  (void **, H5ES_status_t *);
-
     herr_t (*wait)  (void **, H5ES_status_t *);
@@
     H5ES_STATUS_FAIL,        /* Operation has completed, but failed */
-    H5ES_STATUS_CANCEL       /* Operation has not completed and has
-                                been cancelled */
+    H5ES_STATUS_CANCEL       /* Operation has not completed and has been cancelled */
 } H5ES_status_t;
@@
   {\tt status} & (OUT): result of the wait operation.\\
+\end{tabular}
+
+\subsection{The Optional Generic Callback}
+A generic optional callback is provided for services that are specific to a plugin.
+Asynchronous operations/services could have been implemented through this optional callback, however since we anticipate asynchronous operations to be common across many plugins, they have been promoted to a subclass by themselves as shown in the previous section.
+Other services that are not shared across different plugins might include transactional semantics for managing operations like in~/ref{fastforward}, MSC - add more use cases here.
+
+The {\tt optional} callback has the following definition. It returns an {\tt herr\_t} indicating success or failure.
+
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
+  {\tt dxpl\_id} & (IN): The data transfer property list.\\
+  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
+  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
 \end{tabular}

### 2014-09-10 RFCs/HDF5/VOL/user_guide/stacking.tex
UG updates
Former-commit-id: b80e6f020c627d40056087212ea138ffcacb3d5f

\section{Interchanging and Stacking VOL Plugins}
\label{sec:stack}

Accessing an HDF5 container with a VOL plugin different than the one
it was created with would be a valid approach as long as the
underlying file format is the same. This would be the user’s
responsibility to ensure that the different plugins are
interchangeable.

\subsection{Stacking Plugins on Top of Each Other}
It would be also possible to stack VOL plugins on top of each
other. This notion is similar to the idea of the split VFD, where
underneath the split VFD itself, two file drivers would be used, one
for the file storing the metadata and another for raw data. Some
stackings make sense and others would be erroneous. For example,
stacking the native HDF5 plugin on top of a non-HDF5 backend plugin
does not make sense and is erroneous. Figure~\ref{stack} shows a
stacking of a remote plugin, where data is distributed remotely, on
top of the native h5 plugin, where servers that store the data at
remote locations use the h5 file format.

\begin{figure}[ht!]
\centering
\includegraphics[width=90mm]{stacked.jpg}
\caption{Stacked VOL plugins.}
\label{stack}
\end{figure}

\subsection{Mirroring Plugins}
Another useful design option is to allow a mirroring plugin, where the
HDF5 API calls are forwarded through a mirror plugin to two or more
VOL plugins. This is an extention to the stacking
feature. Figure~\ref{mirror} shows an example of a VOL mirror that
maps HDF5 API calls to an h5 backend plugin and an XML backend plugin.

\begin{figure}[ht!]
\centering
\includegraphics[width=90mm]{mirrored.jpg}
\caption{Mirrored VOL plugins.}
\label{mirror}
\end{figure}

Another possible VOL plugin could be a statistics plugin that just
gathers information on HDF5 API calls and records statistics
associated with the number of calls to a specific API functions and
corresponding parameters. This plugin would be very useful for
profiling purposes. The statistics plugin would be stacked on top of
another VOL plugin that actually performs the required access to the
file.

\subsection{Implementing Stacked and Mirrored Plugins}
A new set of API calls that map directly to the VOL callbacks have
been added to the HDF5 library to make stacking and mirroring easy for
plugin developers. Similarly to the public VFD (H5FD) routines that
call the VFD callbacks directly, we added the following H5VL APIs to
the library:

\begin{lstlisting}
/* ATTRIBUTE OBJECT ROUTINES */
void *H5VLattr_create(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, const char *attr_name, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
void *H5VLattr_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, const char *name, hid_t aapl_id, hid_t dxpl_id, void **req);
herr_t H5VLattr_read(void *attr, H5VL_t *vol_plugin, hid_t dtype_id, void *buf, hid_t dxpl_id, void **req);
herr_t H5VLattr_write(void *attr, H5VL_t *vol_plugin, hid_t dtype_id, const void *buf, hid_t dxpl_id, void **req);
herr_t H5VLattr_iterate(void *obj, H5VL_loc_params_t loc_params,
H5VL_t *vol_plugin, H5_index_t idx_type, H5_iter_order_t order,
hsize_t *n, H5A_operator2_t op, void *op_data, hid_t dxpl_id, void **req);
herr_t H5VLattr_get(void *attr, H5VL_t *vol_plugin, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_remove(void *obj, H5VL_loc_params_t loc_params, H5VL_t
*vol_plugin, const char *attr_name, hid_t dxpl_id, void **req);
herr_t H5VLattr_close(void *attr, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);

/* DATASE OBJECT ROUTINES */
void *H5VLdataset_create(void *obj, H5VL_loc_params_t loc_params,
H5VL_t *vol_plugin, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
void *H5VLdataset_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t
*vol_plugin, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
herr_t H5VLdataset_read(void *dset, H5VL_t *vol_plugin, hid_t
mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, void *buf, void **req);
herr_t H5VLdataset_write(void *dset, H5VL_t *vol_plugin, hid_t
mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
herr_t H5VLdataset_set_extent(void *dset, H5VL_t *vol_plugin, const hsize_t size[], hid_t dxpl_id, void **req);
herr_t H5VLdataset_get(void *dset, H5VL_t *vol_plugin,
H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_close(void *dset, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);

/* DATATYPE OBJECT ROUTINES */
void *H5VLdatatype_commit(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
void *H5VLdatatype_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
ssize_t H5VLdatatype_get_binary(void *obj, H5VL_t *vol_plugin, unsigned char *buf, size_t size, hid_t dxpl_id, void **req);
herr_t H5VLdatatype_get(void *obj, H5VL_t *vol_plugin, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_close(void *dt, H5VL_t *vol_plugin, hid_t dxpl_id,
void **req);

/* FILE OBJECT ROUTINES */
void *H5VLfile_create(H5VL_t **vol_plugin, const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
void *H5VLfile_open(H5VL_t **vol_plugin, const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
herr_t H5VLfile_flush(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, H5F_scope_t scope, hid_t dxpl_id, void **req);
herr_t H5VLfile_misc(void *file, H5VL_t *vol_plugin, H5VL_file_misc_t misc_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_optional(void *file, H5VL_t *vol_plugin,
H5VL_file_optional_t optional_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_get(void *file, H5VL_t *vol_plugin, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_close(void *file, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);

/* GROUP OBJECT ROUTINES */
void *H5VLgroup_create(void *obj, H5VL_loc_params_t loc_params, H5VL_t
*vol_plugin, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
void *H5VLgroup_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t
*vol_plugin, const char *name, hid_t gapl_id, hid_t dxpl_id, void
**req);
herr_t H5VLgroup_get(void *obj, H5VL_t *vol_plugin, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_close(void *grp, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);

/* LINK OBJECT ROUTINES */
herr_t H5VLlink_create(H5VL_link_create_type_t create_type, void *obj,
H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, hid_t lcpl_id, hid_t
lapl_id, hid_t dxpl_id, void **req);
herr_t H5VLlink_move(void *src_obj, H5VL_loc_params_t loc_params1,
void *dst_obj, H5VL_loc_params_t loc_params2, H5VL_t *vol_plugin,
hbool_t copy_flag, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
herr_t H5VLlink_iterate(void *obj, H5VL_loc_params_t loc_params,
H5VL_t *vol_plugin, hbool_t recursive, H5_index_t idx_type,
H5_iter_order_t order, hsize_t *idx, H5L_iterate_t op, void *op_data, hid_t dxpl_id, void **req);
herr_t H5VLlink_get(void *obj, H5VL_loc_params_t loc_params, H5VL_t
*vol_plugin, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_remove(void *obj, H5VL_loc_params_t loc_params, H5VL_t
*vol_plugin, hid_t dxpl_id, void **req);

/* OBJECT ROUTINES */
void *H5VLobject_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
herr_t H5VLobject_copy(void *src_obj, H5VL_loc_params_t loc_params1,
H5VL_t *vol_plugin1, const char *src_name, void *dst_obj,
H5VL_loc_params_t loc_params2, H5VL_t *vol_plugin2, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
herr_t H5VLobject_visit(void *obj, H5VL_loc_params_t loc_params,
H5VL_t *vol_plugin, H5_index_t idx_type, H5_iter_order_t order, H5O_iterate_t op, void *op_data, hid_t dxpl_id, void **req);
herr_t H5VLobject_get(void *obj, H5VL_loc_params_t loc_params, H5VL_t
*vol_plugin, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLobject_misc(void *obj, H5VL_loc_params_t loc_params, H5VL_t
*vol_plugin, H5VL_object_misc_t misc_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLobject_optional(void *obj, H5VL_loc_params_t loc_params,
H5VL_t *vol_plugin, H5VL_object_misc_t optional_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLobject_close(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);

/* ASYNCHRONOUS ROUTINES */
herr_t H5VLrequest_cancel(void **req, H5VL_t *vol_plugin, H5ES_status_t *status);
herr_t H5VLrequest_test(void **req, H5VL_t *vol_plugin, H5ES_status_t *status);
herr_t H5VLrequest_wait(void **req, H5VL_t *vol_plugin, H5ES_status_t *status);
\end{lstlisting}

The above API calls should be used in the stacked or mirror plugin to
call into the lower plugins indicated by the {\tt vol\_plugin}
parameter that is added to all the routines.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2014-09-12 RFCs/HDF5/VOL/user_guide/new_api.tex
more updates
Former-commit-id: 4ede797306f4f397b721fc3f9c1b613c87c74610

@@
 \section{New VOL API Routines}
+\label{sec:api}
 New API routines have been added to the HDF5 library to manage VOL plugins. This section details each new API call and explains their intended usage.
@@
 \begin{lstlisting}
-  hid_t H5VLobject_register(void *obj, H5I_type_t obj_type, const H5VL_class_t *cls);
+hid_t H5VLregister(const H5VL_class_t *cls);
 \end{lstlisting}
-to register an {\tt hid\_t} with an object {\tt obj} associated with
-the VOL plugin of class {\tt cls}. This is needed in all iterate and
-visit callbacks where the plugins internally need to wrap an {\tt
-  hid\_t} around an object to call the user defined operation {\tt op}
-on.
+Registers a user defined VOL plugin with the HDF5 library and returns an identifier for that plugin to be used if successful, otherwise returns a negative value.
+This function is used when the application has direct access to the plugin it wants to use and is able to obtain a pointer for the plugin structure to pass to the HDF5 library.
+The plugin must be unregistered before the application exists with {\tt H5VLunregister()}.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt cls} & (IN): A pointer to the plugin structure to register.\\
+\end{tabular}
 
 \begin{lstlisting}
-  herr_t H5VLget_object(hid_t obj_id, void **obj, H5VL_t **vol_plugin);
+hid_t H5VLregister_by_name(const char *plugin_name);
 \end{lstlisting}
-to retrieve the VOL object and plugin structure from an HDF5
-identifier ({\tt hid\_t}). The plugin structure is defined as:
+Registers a VOL plugin with the HDF5 library given the name of the plugin and returns an identifier for that plugin to be used if successful, otherwise returns a negative value.
+If the plugin is already registered the library will create an identifier for it and returns it to the user; otherwise the library will look for available third party plugins and dynamically load them and registers them for use, then returns an identifier for the plugin.
+Third party plugins must be installed on the system as a shared library or DLL.
+The plugin must be unregistered before the application exists with {\tt H5VLunregister()}.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt name} & (IN): The plugin name to search for an register.\\
+\end{tabular}
+
 \begin{lstlisting}
-struct H5VL_t {
-    const H5VL_class_t *cls;     /* constant class info */
-    const char *container_name;  /* name of the underlying storage 
-                                    container */
-    unsigned long feature_flags; /* VOL Driver feature Flags */
-    int nrefs;                   /* number of references by objects
-                                    using this struct */
-};
+herr_t H5VLunregister(hid_t plugin_id);
+\end{lstlisting}
+Unregisters a plugin from the library and return a positive value on success otherwise return a negative value.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt plugin\_id} & (IN): A valid identifier of the plugin to unregister.\\
+\end{tabular}
+
+\begin{lstlisting}
+htri_t H5VLis_registered(const char *name);
+\end{lstlisting}
+Checks if a VOL plugin is registered with the library given the plugin name and returns TRUE/FALSE on success, otherwise it returns a negative value.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt name} & (IN): The plugin name to check for.\\
+\end{tabular}
+
+\begin{lstlisting}
+ssize_t H5VLget_plugin_name(hid_t obj_id, char *name/*out*/, size_t size);
+\end{lstlisting}
+Retrieves the name of a VOL plugin given and object identifier that was created/opened with it. On success, the name length is returned.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt obj\_id} & (IN): The object identifier to check.\\
+  {\tt name} & (OUT): Buffer pointer to put the plugin name. If NULL, the library just returns the size required to store the plugin name.\\
+  {\tt size} & (IN): the size of the passed in buffer.\\
+\end{tabular}
+
+\begin{lstlisting}
+hid_t H5VLget_plugin_id(const char *name);
+\end{lstlisting}
+Given a plugin name that is registered with the library, this function returns an identifier for the plugin.
+If the plugin is not registered with the library, a negative value is returned.
+The identifier must be released with a call to {\tt H5VLclose()}.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+  {\tt name} & (IN): The plugin name to check for.\\
+\end{tabular}
+
+\begin{lstlisting}
+herr_t H5VLclose(hid_t plugin_id);
+\end{lstlisting}
+Shuts down access to the plugin that the identifier points to and release resources associated with it.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+ {\tt plugin\_id} & (IN): A valid identifier of the plugin to close.\\
+\end{tabular}
+
+\begin{lstlisting}
+  hid_t H5VLobject_register(void *obj, H5I_type_t obj_type, hid_t plugin_id);
+\end{lstlisting}
+Creates an HDF5 identifier for an object given its type and an identifier of the plugin that was used in creating it.
+This function is typically used by external plugins wanting to wrap an {\tt hid\_t} around a plugin specific object to return to a user callback for functions like {\tt H5Literate, H5Lvisit, H5Ovisit, H5Aiterate} etc...
+A Negative value is returned on failure.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+ {\tt obj} & (IN): pointer to the object to register.\\
+ {\tt obj\_type} & (IN): The type of the object ({\tt H5I\_FILE, H5I\_DATASET, H5I\_GROUP, H5I\_ATTRIBUTE, H5I\_DATATYPE}).\\
+ {\tt plugin\_id} & (IN): identifier of the vol plugin the object is associated with.\\
+\end{tabular}
+
+\begin{lstlisting}
+  herr_t H5VLget_object(hid_t obj_id, void **obj); 
+\end{lstlisting}
+Retrieves a pointer to the VOL object from an HDF5 file or object identifier.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+ {\tt obj\_id} & (IN): identifier of the object to dereference.\\
+ {\tt obj} & (OUT): buffer to store the pointer of the VOL object associated with the object identifier.\\
+\end{tabular}
+
+\begin{lstlisting}
+herr_t H5VLinitialize(hid_t plugin_id, hid_t vipl_id);
+\end{lstlisting}
+Initializes access to the VOL plugin represented by {\tt plugin\_id} with initialization parameters set as properties in the the property list {\tt vipl\_id}.
+Some plugins may not require initialization.
+For more information about plugin initialization and what properties are required to be set in the property list refer to the actual plugin documentation.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+ {\tt plugin\_id} & (IN): identifier of VOL plugin to initialize.\\
+ {\tt vipl\_id} & (IN): VOL initialize property list containing properties required for plugin initialization.\\
+\end{tabular}
+
+\begin{lstlisting}
+herr_t H5VLterminate(hid_t plugin_id, hid_t vtpl_id);
 \end{lstlisting}
 
-% H5_DLL void *H5Pget_vol_info(hid_t plist_id);
+Terminates access to the VOL plugin represented by {\tt plugin\_id} with termination parameters set as properties in the the property list {\tt vtpl\_id}.
+Some plugins may not require termination.
+For more information about plugin termination and what properties are required to be set in the property list refer to the actual plugin documentation.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{10cm}}
+ {\tt plugin\_id} & (IN): identifier of VOL plugin to terminate.\\
+ {\tt vtpl\_id} & (IN): VOL terminate property list containing properties required for plugin termination.\\
+\end{tabular}
+
+A set of API calls that map directly to the VOL callbacks themselves have been added to aid in the development of stacked or mirrored plugins.
+For more information on usage refer to Section~\ref{sec:stack}.
+The routines are listed bellow.
+\begin{lstlisting}
+/* ATTRIBUTE OBJECT ROUTINES */
+void *H5VLattr_create(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *attr_name, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
+void *H5VLattr_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t aapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLattr_read(void *attr, hid_t plugin_id, hid_t dtype_id, void *buf, hid_t dxpl_id, void **req);
+herr_t H5VLattr_write(void *attr, hid_t plugin_id, hid_t dtype_id, const void *buf, hid_t dxpl_id, void **req);
+herr_t H5VLattr_get(void *obj, hid_t plugin_id, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLattr_specific(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLattr_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLattr_close(void *attr, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* DATASET OBJECT ROUTINES */
+void *H5VLdataset_create(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
+void *H5VLdataset_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLdataset_read(void *dset, hid_t plugin_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, void *buf, void **req);
+herr_t H5VLdataset_write(void *dset, hid_t plugin_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
+herr_t H5VLdataset_get(void *dset, hid_t plugin_id, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdataset_specific(void *obj, hid_t plugin_id, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdataset_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdataset_close(void *dset, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* DATATYPE OBJECT ROUTINES */
+void *H5VLdatatype_commit(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
+void *H5VLdatatype_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLdatatype_get(void *dt, hid_t plugin_id, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdatatype_specific(void *obj, hid_t plugin_id, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdatatype_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdatatype_close(void *dt, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* FILE OBJECT ROUTINES */
+void *H5VLfile_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
+void *H5VLfile_open(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLfile_get(void *file, hid_t plugin_id, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLfile_specific(void *obj, hid_t plugin_id, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLfile_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLfile_close(void *file, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* GROUP OBJECT ROUTINES */
+void *H5VLgroup_create(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
+void *H5VLgroup_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLgroup_get(void *obj, hid_t plugin_id, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLgroup_specific(void *obj, hid_t plugin_id, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLgroup_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLgroup_close(void *grp, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* LINK OBJECT ROUTINES */
+herr_t H5VLlink_create(H5VL_link_create_type_t create_type, void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLlink_copy(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t plugin_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLlink_move(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t plugin_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLlink_get(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLlink_specific(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLlink_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+
+/* OBJECT ROUTINES */
+void *H5VLobject_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
+herr_t H5VLobject_copy(void *src_obj, H5VL_loc_params_t loc_params1, hid_t plugin_id1, const char *src_name,                      void *dst_obj, H5VL_loc_params_t loc_params2, hid_t plugin_id2, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
+herr_t H5VLobject_get(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLobject_specific(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLobject_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+
+/* ASYNCHRONOUS ROUTINES */
+herr_t H5VLrequest_cancel(void **req, hid_t plugin_id, H5ES_status_t *status);
+herr_t H5VLrequest_test(void **req, hid_t plugin_id, H5ES_status_t *status);
+herr_t H5VLrequest_wait(void **req, hid_t plugin_id, H5ES_status_t *status);
+\end{lstlisting}
+
 %%% Local Variables: 

### 2014-09-12 RFCs/HDF5/VOL/user_guide/stacking.tex
more updates
Former-commit-id: 4ede797306f4f397b721fc3f9c1b613c87c74610

@@
 been added to the HDF5 library to make stacking and mirroring easy for
-plugin developers. Similarly to the public VFD (H5FD) routines that
-call the VFD callbacks directly, we added the following H5VL APIs to
-the library:
+plugin developers. Those APIs are listed at then end of Section~\ref{sec:api}. They are similar to the public VFD (H5FD) routines that call the VFD callbacks directly.
 
+Using those new APIs, A mirror VOL plugin could, for example, implement the create callback in the file class by creating two HDF5 containers each with a different underlying plugin with 2 calls to:
 \begin{lstlisting}
-/* ATTRIBUTE OBJECT ROUTINES */
-void *H5VLattr_create(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, const char *attr_name, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
-void *H5VLattr_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, const char *name, hid_t aapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLattr_read(void *attr, H5VL_t *vol_plugin, hid_t dtype_id, void *buf, hid_t dxpl_id, void **req);
-herr_t H5VLattr_write(void *attr, H5VL_t *vol_plugin, hid_t dtype_id, const void *buf, hid_t dxpl_id, void **req);
-herr_t H5VLattr_iterate(void *obj, H5VL_loc_params_t loc_params,
-H5VL_t *vol_plugin, H5_index_t idx_type, H5_iter_order_t order,
-hsize_t *n, H5A_operator2_t op, void *op_data, hid_t dxpl_id, void **req);
-herr_t H5VLattr_get(void *attr, H5VL_t *vol_plugin, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLattr_remove(void *obj, H5VL_loc_params_t loc_params, H5VL_t
-*vol_plugin, const char *attr_name, hid_t dxpl_id, void **req);
-herr_t H5VLattr_close(void *attr, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);
-
-/* DATASE OBJECT ROUTINES */
-void *H5VLdataset_create(void *obj, H5VL_loc_params_t loc_params,
-H5VL_t *vol_plugin, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
-void *H5VLdataset_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t
-*vol_plugin, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLdataset_read(void *dset, H5VL_t *vol_plugin, hid_t
-mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, void *buf, void **req);
-herr_t H5VLdataset_write(void *dset, H5VL_t *vol_plugin, hid_t
-mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
-herr_t H5VLdataset_set_extent(void *dset, H5VL_t *vol_plugin, const hsize_t size[], hid_t dxpl_id, void **req);
-herr_t H5VLdataset_get(void *dset, H5VL_t *vol_plugin,
-H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLdataset_close(void *dset, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);
-
-/* DATATYPE OBJECT ROUTINES */
-void *H5VLdatatype_commit(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
-void *H5VLdatatype_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
-ssize_t H5VLdatatype_get_binary(void *obj, H5VL_t *vol_plugin, unsigned char *buf, size_t size, hid_t dxpl_id, void **req);
-herr_t H5VLdatatype_get(void *obj, H5VL_t *vol_plugin, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLdatatype_close(void *dt, H5VL_t *vol_plugin, hid_t dxpl_id,
-void **req);
-
-/* FILE OBJECT ROUTINES */
-void *H5VLfile_create(H5VL_t **vol_plugin, const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
-void *H5VLfile_open(H5VL_t **vol_plugin, const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLfile_flush(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, H5F_scope_t scope, hid_t dxpl_id, void **req);
-herr_t H5VLfile_misc(void *file, H5VL_t *vol_plugin, H5VL_file_misc_t misc_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLfile_optional(void *file, H5VL_t *vol_plugin,
-H5VL_file_optional_t optional_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLfile_get(void *file, H5VL_t *vol_plugin, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLfile_close(void *file, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);
-
-/* GROUP OBJECT ROUTINES */
-void *H5VLgroup_create(void *obj, H5VL_loc_params_t loc_params, H5VL_t
-*vol_plugin, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
-void *H5VLgroup_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t
-*vol_plugin, const char *name, hid_t gapl_id, hid_t dxpl_id, void
-**req);
-herr_t H5VLgroup_get(void *obj, H5VL_t *vol_plugin, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLgroup_close(void *grp, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);
-
-/* LINK OBJECT ROUTINES */
-herr_t H5VLlink_create(H5VL_link_create_type_t create_type, void *obj,
-H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, hid_t lcpl_id, hid_t
-lapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLlink_move(void *src_obj, H5VL_loc_params_t loc_params1,
-void *dst_obj, H5VL_loc_params_t loc_params2, H5VL_t *vol_plugin,
-hbool_t copy_flag, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLlink_iterate(void *obj, H5VL_loc_params_t loc_params,
-H5VL_t *vol_plugin, hbool_t recursive, H5_index_t idx_type,
-H5_iter_order_t order, hsize_t *idx, H5L_iterate_t op, void *op_data, hid_t dxpl_id, void **req);
-herr_t H5VLlink_get(void *obj, H5VL_loc_params_t loc_params, H5VL_t
-*vol_plugin, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLlink_remove(void *obj, H5VL_loc_params_t loc_params, H5VL_t
-*vol_plugin, hid_t dxpl_id, void **req);
-
-/* OBJECT ROUTINES */
-void *H5VLobject_open(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
-herr_t H5VLobject_copy(void *src_obj, H5VL_loc_params_t loc_params1,
-H5VL_t *vol_plugin1, const char *src_name, void *dst_obj,
-H5VL_loc_params_t loc_params2, H5VL_t *vol_plugin2, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
-herr_t H5VLobject_visit(void *obj, H5VL_loc_params_t loc_params,
-H5VL_t *vol_plugin, H5_index_t idx_type, H5_iter_order_t order, H5O_iterate_t op, void *op_data, hid_t dxpl_id, void **req);
-herr_t H5VLobject_get(void *obj, H5VL_loc_params_t loc_params, H5VL_t
-*vol_plugin, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLobject_misc(void *obj, H5VL_loc_params_t loc_params, H5VL_t
-*vol_plugin, H5VL_object_misc_t misc_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLobject_optional(void *obj, H5VL_loc_params_t loc_params,
-H5VL_t *vol_plugin, H5VL_object_misc_t optional_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLobject_close(void *obj, H5VL_loc_params_t loc_params, H5VL_t *vol_plugin, hid_t dxpl_id, void **req);
-
-/* ASYNCHRONOUS ROUTINES */
-herr_t H5VLrequest_cancel(void **req, H5VL_t *vol_plugin, H5ES_status_t *status);
-herr_t H5VLrequest_test(void **req, H5VL_t *vol_plugin, H5ES_status_t *status);
-herr_t H5VLrequest_wait(void **req, H5VL_t *vol_plugin, H5ES_status_t *status);
+void *H5VLfile_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
 \end{lstlisting}
-
-The above API calls should be used in the stacked or mirror plugin to
-call into the lower plugins indicated by the {\tt vol\_plugin}
-parameter that is added to all the routines.
+where each call uses a different file access property list, each with the VOL plugin property set to the underlying plugins.
+Then the mirror plugin creates a structure containing the pointers for the containers returned from both underlying plugins and returns a pointer to that structure as the output of the file create callback.
+Subsequent access to the container would again call the the public VOL routines twice for each plugin with its corresponding objects and combine the output as needed.
 

### 2014-09-15 RFCs/HDF5/VOL/user_guide/external.tex
more updates
Former-commit-id: e11d74749afe3f6d492fe7b1ca3eafcae2c1404f

\section{Creating and Using an External Plugin}
External plugins are developed outside of the HDF5 library and do not
use any internal HDF5 private functions. They do not require to be
shipped with the HDF5 library, but can just link to it from userspace
just like an HDF5 application. If an external VOL plugin is installed on system as a shared library or a DLL, the library can search for it and load it dynamically to be used by an application.

\subsection{Creating an External Plugin}
Developing an external plugin is similar to developing an internal plugin. Refer to Section~ref{sec:vol} for details on plugin creation. The important thing to keep in mind is that external plugins cannot use internal HDF5 features. The ``value'' field for an external plugin should be a positive integer greater than 128. The name should be unique across all plugins registered with the library.

In order for the HDF5 library to be able to load an external plugin dynamically, the plugin developer has to define two public routines with the following name and signature:
\begin{lstlisting}
H5PL_type_t H5PLget_plugin_type(void)
const void *H5PLget_plugin_info(void)
\end{lstlisting}
{\tt H5PLget\_plugin\_type} should return the library type which should always be {\tt H5PL\_TYPE\_VOL}. {\tt H5PLget\_plugin\_info} should return a pointer to the plugin structure defining the VOL plugin with all the callbacks. For example, consider an external plugin defined as:
\begin{lstlisting}
static const H5VL_class_t H5VL_log_g = {
    1,	/* version */
    502,	/* value */
    "log",	/* name */
    ...
}
\end{lstlisting}
The plugin would implement the two routines as:
\begin{lstlisting}
H5PL_type_t H5PLget_plugin_type(void) {return H5PL_TYPE_VOL;}
const void *H5PLget_plugin_info(void) {return &H5VL_log_g;}
\end{lstlisting}

Implementing iteration and visit callbacks in external plugins requires the plugin invoking the user defined callback function with an HDF5 identifier ({\tt hid\_t}) on the location object. The current HDF5 H5I API does not allow creating and dereferencing identifiers that point to HDF5 object types. Therefore, two new API routines have been added (see Section~\ref{sec:api} for more details) to get around that. {\tt H5VLobject\_register()} is used to create an HDF5 identifier for a VOL object handle (file, group, dataset, named datatype, or attribute). {\tt H5VLget\_object()} is used to derefernce the HDF5 identifier back to the VOL object handle.

\subsection{Using an External Plugin}
Unlike internal plugins, external plugins cannot create an API routine for applications to use to set the VOL plugin in the file access property list. External plugin developers can however provide a wrapper routine that registers the plugin with {\tt H5VLregister()} instead of having the application call that directly with the pointer to the plugin class structure. Both ways are possible if the external plugin used is in the application's user space. External plugins provided by third pary vendors that are not in the application's user space but are installed on the system with a shared library or DLL can be registered by the application using {\tt H5VLregister\_name()} provided that the application knows the plugin's name in advance.

The registration operation will return a global identifier for the registered plugin. Applications can query the library for that identifier using the plugin name with {\tt H5VLget\_plugin\_id()}. This identifier is used to initialize the plugin if it requires an initialization phase. A third party library could use that ID to create a plugin that stacks or mirrors on top of an internal plugin using that identifier (refer to section~\ref{sec:stack} for more details on stacking and mirroring).

Some plugins could require an initialization phase before using the plugin with some input parameters from users. This process is done by creating a VOL initialization property list and setting a public property that should be defined by the internal plugin to the hostname of the remote machine. The user then calls the initialize routine ({\tt H5VLintialize()}) with the plugin\_id and the property list to initialize the plugin. An external plugin could abstract those operations into a wrapper routine that wraps the property list creation, property settings, and plugin initialization into one call that the user makes to simplify this process.

The application then sets the plugin access property in the file access property list to the external plugin using the plugin identifier with this API routine:
\begin{lstlisting}
  herr_t H5Pset_vol(hid_t fapl_id, hid_t plugin_id, const void *new_vol_info);
\end{lstlisting}
where {\tt new\_vol\_info} is the plugin information needed from the application. Typically it is a plugin defined structure with some fields to setup the plugin access. The external plugin could also provide a wrapper function around this to make it easier for the application to use.

Now that the plugin is initialized, the application can create or open an HDF5 container using the external plugin. After closing all objects and containers on that plugin, the application should terminate access to the selected plugin if it requires a termination phase by calling {\tt H5VLterminate()} with the required termination properties (similar to the initialization phase).

Finally the application is required to un-register the plugin from the library when access to the container(s) is terminated using {\tt H5VLunregister}.

% /* Function prototypes */
% H5_DLL htri_t H5VLis_registered(hid_t id);
% H5_DLL ssize_t H5VLget_plugin_name(hid_t id, char *name/*out*/, size_t size);

% H5_DLL void *H5Pget_vol_info(hid_t plist_id);
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2014-09-15 RFCs/HDF5/VOL/user_guide/stacking.tex
more updates
Former-commit-id: e11d74749afe3f6d492fe7b1ca3eafcae2c1404f

@@
 
-Using those new APIs, A mirror VOL plugin could, for example, implement the create callback in the file class by creating two HDF5 containers each with a different underlying plugin with 2 calls to:
+A mirror VOL plugin could, for example, implement the create callback in the file class by creating two HDF5 containers each with a different underlying plugin with 2 calls to:
 \begin{lstlisting}
@@
 \end{lstlisting}
-where each call uses a different file access property list, each with the VOL plugin property set to the underlying plugins.
+where each call uses a different file access property list, each with the VOL plugin property set to the underlying plugin.
 Then the mirror plugin creates a structure containing the pointers for the containers returned from both underlying plugins and returns a pointer to that structure as the output of the file create callback.
-Subsequent access to the container would again call the the public VOL routines twice for each plugin with its corresponding objects and combine the output as needed.
+Subsequent access to the container created would receive as input the structure with the two files and would again call the the public VOL routines twice for each plugin with its corresponding file object and combine the output as needed.
+
+MSC - refer to an appendix for an example?
 

### 2014-09-16 RFCs/HDF5/VOL/RFC/RFC_VOL.tex
add latex RFC for VOL work.
Former-commit-id: 31c3b06aa40d50021dc43d763d509e88a7b4ba67

\documentclass[letterpaper,hyper]{THG_RFC}

% Fonts
\usepackage{lmodern} % times / lmodern / mathpazo / palatino
\usepackage[scaled=.95]{helvet}
\usepackage{courier}

% Path to figures, plots
\graphicspath{{./pics/}{./plots/}}

% Code snippets
\usepackage{listings}
\def\lstsetc{\lstset{language=C,
  numbers=left,
  xleftmargin=20pt,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  showspaces=false, 
  showstringspaces=false,
  breaklines=true,
  basicstyle=\footnotesize\ttfamily,
  stringstyle=\itshape,
  commentstyle=\itshape\bfseries,
  morekeywords={main, size_t, malloc, free,
    hsize_t, hid_t, herr_t,
    H5VL_class_value_t,
    H5VL_attr_class_t,
    H5VL_dataset_class_t,
    H5VL_datatype_class_t,
    H5VL_file_class_t,
    H5VL_group_class_t,
    H5VL_link_class_t,
    H5VL_object_class_t,
    H5VL_async_class_t,
    H5VL_class_t
    }
  }
}

% Title, author, etc
\title{RFC: Virtual Object Layer}
\author{Mohamad Chaarawi}
\author{Quincey Koziol}
\date{September 16, 2014}
\rfcversion{2014-09-16.v3}
\revision{January 9, 2012}{First Draft circulated internally.}
\revision{March 9, 2012}{Update and circulate internally and externally.}
\revision{August 28, 2014}{Update with new framework changes.}

%% Start the document
\begin{document}

%% Title
\maketitle

%% Abstract
\begin{abstract}
This RFC describes a new abstraction layer within the HDF5 library that enables different methods for accessing data and objects that conforms to the HDF5 data model. This new layer, called Virtual Object Layer (VOL), is similar to the Virtual File Layer (VFL) abstraction where different Virtual File Drivers (VFD) can be plugged in to access data in the file in different ways; however the VOL layer would be at a higher level, to allow abstract operations on objects rather than blocks of bytes. Several plugins developed already will show how the VOL abstraction would work with forms of data storage outside the typical HDF5 file paradigm.
\end{abstract}

\section{Introduction}
The HDF5 data model is composed of two basic objects, groups and datasets. The data model in itself is very powerful and widely used by many applications, including High Performance Computing (HPC) applications. The HDF5 library has an internal abstraction layer called the Virtual File Layer that the library calls after it translates the HDF5 data model and object API calls to operation on blocks of bytes. The operations on those blocks of bytes are abstracted out into drivers so that we do not limit users to one underlying implementation. Several drivers are already implemented and shipped with the HDF5 library such as the POSIX (sec2) driver, MPI-I/O driver, and a memory (core) driver.

The main challenge currently in HDF5 is not in the data model itself, but in the native HDF5 single file format that has performance issues that vary widely over different platforms and has some limitations where all objects actually have to be accessible locally. Furthermore, in parallel applications, file access by several processes has to be coordinated in order to maintain strict consistency semantics to avoid file corruption. In addition, the emergence of new tiered storage architectures and object storage file systems renders the current HDF5 library in need of major implementation changes to leverage such architectures.
To address those concerns, we have been working on a new abstraction layer inside the HDF5 library called the Virtual object layer (VOL). The VOL intercepts all HDF5 API calls that could potentially access objects in the file and forwards those calls to a plugin ``object driver''. The plugins could actually store the objects in variety of ways. A plugin could, for example, have objects be distributed remotely over different platforms, provide a raw mapping of the model to the file system, or even store the data in other file formats (like native netCDF or HDF4 format). The user still gets the same data model where access is done to a single HDF5 ``container''; however the plugin object driver translates from what the user sees to how the data is actually stored. Having this abstraction layer maintains the object model of HDF5 and would allow much better usage of new object storage file systems that are targeted for Exascale systems.

A solid prototype for the VOL has already been implemented and used in several research projects, internally and externally. It was a key component to the FastForward~\cite{ffwd} project. However, all the work that has been done so far on the VOL was research oriented. Production is the next step to integrate this layer into the mainstream HDF5 library. The VOL implementation is in a solid prototype state that is tested daily, but a good amount of work is needed to make the VOL production ready in terms of code reviews, documentation, and support. We expect the production version of the VOL work to be a big step forward for the HDF5 library that will create new partnerships with storage vendors or users that are looking to implement new VOL plugins or users who would use existing plugins.

\section{Design/Architecture}
To implement a VOL interface capable of accepting any plugin a developer wishes to add, a modular design has to be put in place, similar to how the VFL interface in HDF5 is designed to accept different VFDs. The VOL is a higher level abstraction than the VFL abstraction. The following figure shows where the VOL is layered and how the data is accessed in the file:

\begin{figure}[ht!]
\centering
\includegraphics[width=170mm]{pics/vol-arch.jpg}
\caption{Overall VOL architecture.}
\label{fig:vol-arch}
\end{figure}

\subsection{The VOL Callback Structure}
Each VOL plugin is an instance of the following structure:

{\lstsetc
\begin{lstlisting}
/* Class information for each VOL driver */
typedef struct H5VL_class_t {
    H5VL_class_value_t value;
    const char *name;
    herr_t  (*initialize)(hid_t vipl_id);
    herr_t  (*terminate)(hid_t vtpl_id);
    size_t  fapl_size;
    void *  (*fapl_copy)(const void *info);
    herr_t  (*fapl_free)(void *info);

    /* Data Model */
    H5VL_attr_class_t          attr_cls;
    H5VL_dataset_class_t       dataset_cls;
    H5VL_datatype_class_t      datatype_cls;
    H5VL_file_class_t          file_cls;
    H5VL_group_class_t         group_cls;
    H5VL_link_class_t          link_cls;
    H5VL_object_class_t        object_cls;

    /* Services */
    H5VL_async_class_t         async_cls;
    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
} H5VL_class_t;
\end{lstlisting}
}

The VOL public structure separates Data Model operations from Service operations. Data Model operations are those that operate on files, groups, dataset, etc… Those operations are furthermore grouped in their respective ``class'' structure. For example the file class consists of function pointers for plugins to implement operations on the file itself (H5F API operations). Service operations are those that provide services for users that are not related to the data model specifically. Asynchronous operations, for example, are a service that most plugins can implement, so we add a class for it in the VOL structure. If a service becomes generic enough and common between many plugins, a class for it should be added in the VOL structure. However, many plugins can/will provide services that are not shared by other plugins. A good way to support these services is through an optional callback in the VOL structure which can be a hook from the API to the plugin that provides those services, passing any necessary arguments needed without the HDF5 library having to worry about supporting that service. A similar API operation to allow users to use that service will be added. This API call would be similar to an ``ioctl'' call where any kind of operation can be supported and passed down to the plugin that has enough knowledge from the user to interpret the type of the operation. 
The VOL User Guide will discuss the VOL structure in much more detail and provide examples on how to support/implement the classes/callbacks.

\subsection{Calling in the VOL layer}
The VOL intercepts all HDF5 API calls that potentially modify data on disk. Calls to one of these API functions only run sanity checks on the arguments passed in, and then immediately call the associated VOL callback for the API function. Operations, such as creating a group or retrieving a hyperslab from a dataset, will be captured and routed through the selected plugin that knows how the data is actually stored and capable of producing the results needed by the operations. For example, a call to H5Dcreate would be implemented within the HDF5 library as:

{\lstsetc
\begin{lstlisting}
H5Dcreate(hid_t loc_id, const char *name, hid_t type_id, hid_t space_id, hid_t lcpl_id, hid_t dcpl_id, hid_t dapl_id) {
	/* Check arguments */
	check_location (loc_id);
	check_type (type_id);
	check_dataspace (space_id);
	check_property_lists (lcpl_id, dcpl_id, dapl_id);

	/* call the corresponding callback for H5Dcreate */
	result = H5VL_dataset_create (…); /* will route the operation to the plugin at the intermediate VOL layer */
	/* return result to user (yes the dataset is created, or no here is the error */
	return result;
}
\end{lstlisting}
}

The H5Dcreate call will inform the user that a dataset with the returned ID has been created in the HDF5 container being accessed with the chosen VOL plugin. Depending on the plugin selected, the H5Dcreate function might have created a dataset object in an HDF5 file, a netCDF file, a file on a remote machine, or any way a plugin is designed to create a dataset.

\subsection{Plugin Selection}
The user should be able to select the VOL plugin and possibly provide some information to the corresponding plugin. The best way to do that is through a FAPL. For each plugin registered with the HDF5 library, a FAPL routine can be added to set the VOL plugin. If we consider the MDS plugin:
{\lstsetc
\begin{lstlisting}
hid_t fapl = H5Pcreate(H5P_FILE_ACCESS);
H5Pset_fapl_mds_vol(fapl, ...);
hid_t file = H5Fcreate("foo.h5", H5F_ACC_TRUNC, H5P_DEFAULT, fapl);
H5Pclose(fapl);
\end{lstlisting}
}

This would indicate that the MDS object layer plugin is to be used. All accesses to objects within the file opened using that FAPL would be routed through the MDS plugin.
In addition to plugins for the VOL class that will be added in the HDF5 library, any developer may write their own customizable plugin and tell the HDF5 library to use it at runtime. The plugin should be registered using:
{\lstsetc
\begin{lstlisting}
hid_t H5VLregister(H5VOL_class_t *cls)
\end{lstlisting}
}
The {\tt cls} parameter is a structure containing function pointers to the routines that implement all the callback routines the VOL class specifies.

\subsection{Plugin Examples}
\subsubsection{Different File Format Plugins}
We mentioned earlier that a developer could design a plugin such that the file that stores data on disk could be of different format than the H5 format. This is very important to users that would like to use the HDF5 API and data model, but also desire the portability to use their files across different libraries or would like to access data from pre-existing files that are not in the H5 format.

The plugin, which understands the HDF5 data model and how the data is stored, will do the necessary ``translation'' needed for this kind of model. The following figure explains more on how this is achieved:

\begin{figure}[ht!]
\centering
\includegraphics[width=170mm]{pics/plugin-formats.jpg}
\caption{Plugins with different underlying file formats.}
\label{fig:formats}
\end{figure}

\subsubsection{Raw Format Plugin}
The flexibility of the virtual object layer provides developers with the option to abandon the one file, binary format like the native HDF5 implementation. A ``raw'' file format could map HDF5 objects (groups, datasets, etc ...) to file system objects (directories, files, etc ...). The entire set of raw file system objects created would represent one HDF5 container as opposed to one HDF5 file with the native plugin. The actual mapping between all HDF5 objects to file system objects is subject to further research.

This plugin would allow the PLFS package~\cite{plfs} to be applied to applications that use the HDF5 API, where access seems to be done to a single file from the high level, but is mapped by the raw plugin to multiple files/directories for performance benefits that were demonstrated by PLFS.

\subsubsection{Remote Access Plugin}
The current HDF5 implementation requires applications to access a single HDF5 file that is also local on the file system where the application resides. A remote VOL plugin would allow access to files located remotely. The plugin could have an HDF5 server module located where the HDF5 file resides and listens to incoming requests (HDF5 operations that are routed through the VOL) from a remote process.

Remote visualization is an important use case for this plugin. Large, remote datasets are very expensive to migrate to the local virtualization system. It would be faster to just enable in situ virtualization to remotely access the virtualization data using the HDF5 API. This is however not possible at the moment with the native implementation for HDF5 as the file is required to be present locally.

\subsubsection{MDS Plugin}
The MDS plugin uses the proposed strategy in the Independent Metadata RFC~\cite{mds}, which allows processes in HPC applications to call HDF5 operations that modify metadata independently (the current HDF5 semantics require those calls to be collective). The MDS is a set-aside process that manages access to the file's metadata to avoid corruption from simultaneous access by several processes. The design strategy is explained in details in the Independent Metadata RFC.

The MDS strategy puts all HDF5 metadata in a separate file, different than the raw data file. Only the designated MDS process will read/write data to that file. All HDF5 calls made by other processes that potentially need to access the metadata or raw data file must go through the MDS process to serialize access to the metadata and acquire the necessary locks for proper synchronization. Figure~\ref{fig:mds} shows the flow of the operation from the VOL layer to the MDS plugin:

\begin{figure}[ht!]
\centering
\includegraphics[width=170mm]{pics/plugin-mds.jpg}
\caption{Metadata server plugin.}
\label{fig:mds}
\end{figure}

All H5F, H5D, H5A, H5O, H5G, and H5L API calls are mapped to MDS specific implementations. An H5Dopen call, for example, would forward the parameters of the routine to the MDS that actually opens the dataset and returns the ID to the calling process along with some metadata for that dataset. The user gets back the ID of the opened dataset. An H5Dwrite call would ask the MDS process for a shared lock on the dataset being written to, to avoid having another process modify the metadata of the dataset, and then would actually write the data from the API call.
\clearpage
\subsection{Interchanging and Stacking VOL plugins}
Accessing a file created with a different VOL plugin than the one it was created with would be a valid operation as long as the underlying file format is the same. This would be the user’s responsibility to ensure that the different plugins are interchangeable.

It would be also possible to stack VOL plugins on top of each other. This notion is similar to the idea of the split VFD, where underneath the split VFD itself, two file drivers would be used, one for the file storing the metadata and another for raw data. Some stackings make sense and others would be erroneous. For example, stacking the native HDF5 plugin on top of a non-HDF5 backend plugin does not make sense and is erroneous. Figure~\ref{fig:stack} showes a stacking of the remote plugin, where data is distributed remotely, on top of the native h5 plugin, where servers that store the data at remote locations use the h5 file format.

\begin{figure}[h!]
\centering
\includegraphics[width=90mm]{stacked.jpg}
\caption{Stacked VOL plugins.}
\label{fig:stack}
\end{figure}

Another useful design option is to allow a mirroring plugin, where the HDF5 API calls are forwarded through a mirror plugin to two or more VOL plugins. This is an extention to the stacking feature. Figure~\ref{fig:mirror} shows an example of a VOL mirror that maps HDF5 API calls to an h5 backend plugin and an XML backend plugin:

\begin{figure}[h!]
\centering
\includegraphics[width=90mm]{mirrored.jpg}
\caption{Mirrored VOL plugins.}
\label{fig:mirror}
\end{figure}

Another possible VOL plugin could be a statistics plugin that just gathers information on HDF5 API calls and records statistics associated with the number of calls to a specific API functions and corresponding parameters. This plugin would be very useful for profiling purposes. The statistics plugin would be stacked on top of another VOL plugin that actually performs the required access to the file.
\clearpage
\section{Implementation}
The VOL class structure consists of data structure(s) that contain configuration variables that are set by each plugin and a collection of function pointers that maps all HDF5 API operations that access data on disk to the plugin’s corresponding implementations. Internally, each plugin is free to implement the underlying storage of objects in any way desired. The main goal is that the user still gets the same HDF5 API and data access model no matter which plugin is used. This section highlights some implementation details and the preliminary API for the VOL.

\subsection{VOL Callbacks}
A VOL plugin is initialized based on the user selection with a file access property list API call or the default that the library chooses. The plugin is an instance of the VOL class and contains an implementation for the function callbacks specified by the VOL class.

The VOL class includes all the higher level logical callbacks that potentially touch data (metadata or raw data) on disk. All the API routines should map to one of those callbacks. The HDF5 API is too large however to have a 1 to 1 mapping from API routines to VOL callbacks, so we introduce the notion of a generic function call that developers could use to implement certain API routines that do not map to one of the VOL callbacks. This is similar to the UNIX {\tt ioctl()} routine.

The HDF5 library currently does not support nonblocking I/O operations. However, since it is a very desirable feature, future versions of the library most probably will add nonblocking routines. In order to be able to support those API routines and not to double the number of VOL callback routines, we made all VOL callbacks nonblocking compatible, by adding an HDF5 request parameter to all VOL callbacks. If the high level operation issued by the user is nonblocking, then the request would just be forwarded to the VOL plugin and the plugin itself would be responsible to support the nonblocking behavior. If the high level operation is a blocking operation, then a non-active request is forwarded to the plugin which detects that the request is inactive and implements the operation in a blocking behavior.

One could argue that the interface can be simplified by having, for example, a common open routine for all objects (like the {\tt H5Oopen}) routine. We found however that having  a common interface would be detrimental to performance in certain plugin implementations, since it would require querying the VOL plugin twice, once for looking up the object location and once for opening the object. Having an optional callback for every object and a generic one would solve this issue. The VOL layer would check if the specific object callback is implemented in the VOL plugin, and if it is not, it would fall back to the generic object callback routine. This way we don’t sacrifice performance for generality.

Another design issue comes to mind when looking at the large set of functions, and that is whether to lump all the functions together into one data structure as the VOL class, or to have a more object oriented approach, where we can either have a general class that contains all common functions, and then children of that class that contain functions specific to certain HDF5 objects, or for each object have a set of callbacks that are specific to that object. The current design chosen seems to be a good middle ground between generality and readability/maintainability.

\subsection{{\tt H5Ocopy and H5Ocompare}}
The HDF5 API has two routines that will require extra attention to be compatible with the VOL layer, and those are the object copy and compare routines:
{\lstsetc
\begin{lstlisting}
herr_t H5Ocopy( hid_t src_loc_id, const char *src_name, hid_t dst_loc_id, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id );
htri_t H5Ocompare(hid_t loc1_id, const char *name1, hid_t lapl1,  hid_t loc2_id, const char *name2, hid_t lapl2, hid_t cmppl_id, H5O_cmp_cb_t *cb_info);
\end{lstlisting}
}

If the two objects are in containers of the same type, i.e. created using the same VOL plugin, then the VOL layer would be able to detect that and forward those calls to the corresponding implementation using a designated VOL callback. This would allow different sorts of optimizations that a VOL plugin could choose to implement in order to copy or compare two objects. On the other hand, if the objects belong to two different containers, the VOL plugin would not be able to interpret an object created by a different plugin, and so a different approach needs to be considered.

Comparing two objects that belong to different types of HDF5 containers require processing independent of the VOL plugins. One way to accomplish this is to add utility routines to the VOL class to retrieve certain characteristics about an object for comparison. For example, datasets would need utility routines to retrieve the dataset name, dimensions, type, space, and elements. Once those values are retrieved for each object from each VOL plugin, the comparison operation could return the required result. The copy operation would require the same level of processing on the source object. Then using the fetched attributes, the same object is created using a create callback of the destination object’s VOL plugin.

\section{Recommendation}

\section*{Revision History}
\makerevisions

%% References
\bibliographystyle{ieeetr}
\bibliography{RFC_VOL}

\end{document}

### 2014-09-16 RFCs/HDF5/VOL/RFC/RFC_VOL.tex
more updates.
Former-commit-id: f993d3f92b5d8efb931abe1220cba82e90205fa4

@@
 \revision{August 28, 2014}{Update with new framework changes.}
+\revision{September 16, 2014}{Update with new features.}
 
@@
 The VOL public structure separates Data Model operations from Service operations.
-Data Model operations are those that operate on files, groups, dataset, etc… Those operations are furthermore grouped in their respective ``class'' structure.
+Data Model operations are those that operate on files, groups, dataset, etc...
+Those operations are furthermore grouped in their respective ``class'' structure.
 For example the file class consists of function pointers for plugins to implement operations on the file itself (H5F API operations).
@@
 	/* call the corresponding callback for H5Dcreate */
-	result = H5VL_dataset_create (…); /* will route the operation to the plugin at the intermediate VOL layer */
+	result = H5VL_dataset_create (...); /* will route the operation to the plugin at the intermediate VOL layer */
 	/* return result to user (yes the dataset is created, or no here is the error */
@@
 The {\tt cls} parameter is a structure containing function pointers to the routines that implement all the callback routines the VOL class specifies.
+For more information on creating and using VOL plugins, please refer to the VOL user guide.
 
@@
 \section{Implementation}
-The VOL class structure consists of data structure(s) that contain configuration variables that are set by each plugin and a collection of function pointers that maps all HDF5 API operations that access data on disk to the plugin’s corresponding implementations.
+The VOL class structure consists of data structure(s) that contain configuration variables that are set by each plugin and a collection of function pointers that maps all HDF5 API operations that access data on disk to the plugin's corresponding implementations.
 Internally, each plugin is free to implement the underlying storage of objects in any way desired.
 The main goal is that the user still gets the same HDF5 API and data access model no matter which plugin is used.
-This section highlights some implementation details and the preliminary API for the VOL.
+This section highlights some implementation and feature details.
 
@@
 The VOL layer would check if the specific object callback is implemented in the VOL plugin, and if it is not, it would fall back to the generic object callback routine.
-This way we don’t sacrifice performance for generality.
+This way we do not sacrifice performance for generality.
 
@@
 The current design chosen seems to be a good middle ground between generality and readability/maintainability.
+
+\subsection{Internal vs. External Plugins}
+Developers can implement their VOL plugin as a plugin internal to the HDF5 library or an external plugin.
+Internal plugins are ones that rely heavily on internal and private HDF5 functionality like the native and metadata server plugins.
+They are required to ship with the HDF5 library to be used by applications.
+External plugins on the other hand are ones that are implemented outside of the HDF5 library and applications link with to use.
+Those plugins do not require using private HDF5 functionality.
+They can however use public HDF5 features.
+
+External plugins can be provided by the applications themselves or as a third party library, i.e.
+not provided by the HDF5 library nor the application.
+Third party plugins should be installed on the system to be used as a shared library or a DLL.
+HDF5 will attempt to load the plugin if the application requests its use.
+This is similar to Filter plugins~\cite{filters}.
+Refer to the VOL user guide for more detailed information on how to develop and use VOL plugins.
 
@@
 The copy operation would require the same level of processing on the source object.
-Then using the fetched attributes, the same object is created using a create callback of the destination object’s VOL plugin.
+Then using the fetched attributes, the same object is created using a create callback of the destination object's VOL plugin.
 

### 2014-09-18 RFCs/HDF5/VOL/RFC/RFC_VOL.tex
more updates
Former-commit-id: 793677e8e130d49e65815bde32992237ae12c32d

@@
 We expect the production version of the VOL work to be a big step forward for the HDF5 library that will create new partnerships with storage vendors or users that are looking to implement new VOL plugins or users who would use existing plugins.
+
+\section{Requirements}
+The following presents a set of requirements for the VOL framework:
+\begin{enumerate}
+\item All HDF5 API routines that could potentially modify the HDF5 file/container should map to a VOL callback.
+Since the VOL plugins are implementing possible a new file format, all modifications to the container should be handed to the plugins themselves to do.
+\item All HDF5 API routines that do not modify the container, but just provide memory space utilities to the application (like property lists, dataspaces, etc...) should work uniformly across all plugins.
+\item Implementing a VOL plugin should not require any change to the HDF5 library unless the plugin is an internal plugin that modifies the current native file format. 
+\item Current applications, third party libraries, or tools that use the HDF5 library with the native file format should not require any change to work properly with the VOL addition.
+\item Performance of applications without the VOL changes should not change.
+The VOL framework will introduce additional function calls to every HDF5 API call that maps to through the VOL interface, but that should be detrimental to performance.
+\item Applications, third party libraries, and tools that only use the HDF5 public routines and objects should work as expected with any correct and fully implemented plugin.
+Performance may and probably will vary across the different plugins.
+\item The VOL framework should allow plugins to be stackable on top of each other, and should allow implementation of plugins that use 2 or more different plugins.
+It is the plugin developer's  responsibility though to correctly implement such plugins.
+\item Plugin developers should not be required to implement the full VOL functionality for a specific plugin if the intended use of that plugin is a subset of the HDF5 data model and features.
+For example, if a user just intends to access HDF5 datasets, it should be sufficient to develop a plugin that implement container and dataset operations in that container.
+Other advanced functionality of the HDF5 data model should not be required if they will not be used.
+\item The HDF5 library and VOL framework should allow for new functionality or services specific to certain plugins to be added to the library and handed down to the plugin through the HDF5 library from the application.
+\item Applications should be allowed to select a default plugin to use at runtime (with and environment variable possibly) or library configure time so that applications using HDF5 need not be modified to use different plugins than the native plugin.
+\item VOL plugins that can be installed on a system as a shared library should be detected and loaded by the HDF5 library if the application requests their use.
+\end{enumerate}
 

### 2014-09-22 RFCs/HDF5/VOL/developer_guide/body.tex
updates
Former-commit-id: 075132ce087eee5f33c09f6c78cb3bd1c8f6d8c8

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

\section{Introduction}
The Virtual Object Layer (VOL) is an abstraction layer in the HDF5
library that intercepts all API calls that could potentially access
objects in an HDF5 container and forwards those calls to plugin
''object drivers''. The plugins could store the objects in variety of
ways. A plugin could, for example, have objects be distributed
remotely over different platforms, provide a raw mapping of the model
to the file system, or even store the data in other file formats (like
native netCDF or HDF4 format). The user still gets the same data model
where access is done to a single HDF5 “container”; however the plugin
object driver translates from what the user sees to how the data is
actually stored. Having this abstraction layer maintains the object
model of HDF5 and would allow HDF5 developers or users to write their
own plugins for accessing HDF5 data.

This guide is for HDF5 library developers responsible for maintaining the HDF5 C library. It details the changes made to the library to implement the VOL, and the necessary requirements for adding new features to the library to work with the Virtual object layer. Readers of this document are expected to be quite familiar with the VOL high level architecture presented in ~\cite{vol:rfc} and the VOL user's guide\cite{vol:ug}.

\section{New VOL Code}
The VOL captures all API routines that could potentially access the HDF5 file and routes them through the VOL intermediate layer which in-turn calls the plugin callback that implements the API function.

The VOL code additions have been added to the library similar to any new interface introduced. The library's acronym to all VOL related variables and functions is {\tt H5VL}. The public VOL definitions including the VOL class and callbacks are in {\tt H5VLpublic.h}. Private routines are in {H5VLprivate.h}. The actual implementation for public and private routines are in {\tt H5VL.c} and {\tt H5VLint.c} respectively.

\section{The VOL Property in the File Access Property List}
A new property is added for file access property lists (FAPL) that indicates what VOL plugin should be used when accessing a file with the given FAPL. The property {\tt H5F\_ACS\_VOL\_ID\_NAME} maps to the plugin identifier to use. If the plugin selected requires information to be passed down from the application, another property is used, {\tt H5F\_ACS\_VOL\_INFO\_NAME}, which translates to a {\tt void} pointer to the information needed by specific the VOL plugin. The property setting are analogous to the Virtual File Driver properties for selecting and using file drivers with the native HDF5 library. For more information on selecting VOL plugins refer to the VOL user guide.

The default settings for the FAPL properties for the plugin identifier is the global identifier for the native plugin. Since the native plugin does not require any extra information from the application, the info property is set to {\tt NULL} by default. The global identifier for the native plugin is initialized when the HDF5 library is initialized by registering a global identifier with the native plugin structure.

Whenever a plugin is set to be used with a FAPL or when copying a FAPL, the library calls:
\begin{lstlisting}
herr_t H5VL_fapl_open(H5P_genplist_t *plist, hid_t vol_id, const void *vol_info);
\end{lstlisting}
which increments the reference count on the plugin, calls the plugin specific {\tt info\_copy} callback if the {\tt vol\_info} parameter is not {\tt NULL}, and sets the VOL properties for the VOL identifier and info that are described above.

When a FAPL is closed, the library calls:
\begin{lstlisting}
herr_t H5VL_fapl_close(hid_t vol_id, void *vol_info)
\end{lstlisting}
which calls the {\tt info\_free} callback of the VOL plugin with the info if {\tt vol\_info} is not {\tt NULL}, and decrements the reference count on the VOL identifier.

\section{Changes in API Routines Implementation}
The VOL is implemented as an abstraction layer in the HDF5 C library. All API calls have been modified to call into the intermediate VOL layer instead of executing the operation directly with the HDF5 native implementation. For example, the function {\tt H5Fcreate()} was implemented as:

\begin{lstlisting}
    /* Check arguments */
    ...
    /*                                                                                                                                                                                                                                       
     * Create a new file or truncate an existing file.                                                                                                                                                                                       
     */
    if(NULL == (new_file = H5F_open(filename, flags, fcpl_id, fapl_id, H5AC_dxpl_id)))
        HGOTO_ERROR(H5E_FILE, H5E_CANTOPENFILE, FAIL, "unable to create file")
\end{lstlisting}

where {\tt H5F\_open()} is an internal HDF5 function that creates/opens a native HDF5 file. With the VOL changes introduced, the implementation will change to:

\begin{lstlisting}
    /* Check arguments */
    ...
    /* create a new file or truncate an existing file through the VOL */
    if(NULL == (file = H5VL_file_create(vol_cls, filename, flags, fcpl_id, fapl_id, H5AC_dxpl_id, H5_REQUEST_NULL)))
        HGOTO_ERROR(H5E_FILE, H5E_CANTOPENFILE, FAIL, "unable to create file")
\end{lstlisting}

where {\tt H5VL\_file\_create()} is a private function defined in the intermediate VOL layer that calls the the create callback in the file class of the VOL plugin selected in the file access property list.

This change is introduced for all such API routines that could potentially access the file. Multiple API routines could map to the same VOL callback. For example {\tt H5Acreate()}, {\tt H5Acreate\_by\_name()}, and {\tt H5Acreate\_by\_idx()} all map to the attribute create intermediate routine which calls the attribute create callback in the VOL class. For an exact mapping of API routines to VOL intermediate functions and callbacks, please refer to the VOL user guide or the VOL header file in {\tt src/H5VLpublic.h}. All the intermediate routines are implemented in {\tt H5VLint.c}.

\section{Object Identifiers}
All functions that create or open objects in an HDF5 file return an identifier of type {\tt hid\_t} for that object. This identifier could used by the application to access other objects or operate on the object itself. Internally the HDF5 library maintains a mapping of that identifier to the private data structure of the object that it represents. For example, {\tt H5Fcreate()} returns an identifier that internally maps to the private {\tt H5F\_t} structure of that file; {\tt H5Dcreate()} returns an identifier that maps to the {\tt H5D\_t} private structure of the dataset, etc...

With the introduction of the VOL, the current mapping between the identifiers and the private structures is not possible anymore for two main reasons. The first being that the private structures that the identifiers point to now are specific to the native HDF5 implementation. Other plugins will have different structures that they implement. Thus at the API and VOL intermediate layer, those objects are accessible only through a {\tt void} pointer with an unknown structure type to cast it to. The second reason is that the internal structures ({\tt H5F\_t, H5D\_t, H5G\_t,  etc ...}) do not contain a pointer to the plugin class used to create the object. This is problematic because subsequent access on those object through the identifiers would not allow us to determine the VOL class to forward the call to.

To get around the two issues explained above, we introduce a private object structure for all File, Attribute, Dataset, Group, and Named Datatype objects. Those set of objects are the ones currently stored in the HDF5 file. Other object types (dataspace, property lists, etc...) are memory space objects that are not stored or accessed through an HDF5 file. All the API routines that create/open objects will create this ``wrapper'' object around the object pointer returned from the intermediate VOL function.  The new object is defined in {H5VLprivate.h} as:

\begin{lstlisting}
/* The internal vol object structure returned to the API */
typedef struct H5VL_object_t {
    void               *vol_obj;        /* pointer to object created by plugin */
    H5VL_t             *vol_info;       /* pointer to VOL info struct */
} H5VL_object_t;
\end{lstlisting}

where {\tt vol\_obj} is a pointer to the plugin created object. In the native plugin this would be a pointer to the private structures of that object ({\tt H5F\_t, H5D\_t, H5G\_t,  etc ...}). The {\tt vol\_info} contains the information about the plugin that created the object and is defined as:

\begin{lstlisting}
/* Internal struct to track VOL information with objects */
typedef struct H5VL_t {
    const H5VL_class_t *vol_cls;        /* constant plugin class info */
    int                 nrefs;          /* number of references by objects using this struct */
    hid_t               vol_id;         /* identifier for the VOL class */
} H5VL_t;
\end{lstlisting}

{\tt vol\_cls} is a pointer to the plugin class. {\tt nrefs} indicates how many object currently point to the {\tt H5VL\_t} structure. {\tt vol\_id} is the global identifier for the VOL plugin used. Usually this structure is created in {\tt H5Fcreate()} or {\tt H5Fopen()} with {\tt nrefs = 1}, then {\tt nrefs} is incremented by 1 on any subsequent object creation that stored a copy of that pointer and decremented when the object is closed. When {\tt nrefs} becomes zero, the structure is freed.

As a convenience, a new private routines is provided to create the wrapper object for the underlying plugin specific object pointer, manage the VOL info structure, and register an identifier to be returned to the user:

\begin{lstlisting}
H5VL_register_id(H5I_type_t type, void *object, H5VL_t *vol_plugin, hbool_t app_ref);
\end{lstlisting}

This routine is implemented in {\tt H5VLint.c}.Instead of calling {\tt H5I\_register()} to create an identifier, developers should now use the above routine to get back an {\tt hid\_t} for objects stored in HDF5 files.

\section{Using {\tt H5I\_object(), H5I\_object\_verify(), and H5I\_iterate()}}
The change in the mapping of identifiers to the corresponding object pointer and introducing the new wrapper {\tt H5VL\_object\_t} structure, means that any usage in the library of {\tt H5I\_object(), H5I\_object\_verify(), and H5I\_iterate()} expecting to get back a pointer to the native structure of the object is broken, since those routines return a pointer to the object without unwrapping it from the {\tt H5VL\_object\_t} structure. To fix the above problem, we introduced two private convenience functions:
\begin{lstlisting}
void *H5VL_object(hid_t id);
void *H5VL_object_verify(hid_t id, H5I_type_t obj_type);
\end{lstlisting}

which do the same thing as their {\tt H5I} counterpart but return a pointer to the actual VOL specific object ({\tt vol\_obj}) instead of the unwrapped object pointer that the identifier points to. The objects identifiers must be either files, datasets, attributes, named datatypes, or groups; otherwise the function will return {\tt NULL} for erroneous usage. We replaced all usage of {\tt H5I\_object() and H5I\_object\_verify()} in the library as appropriate for the above listed object types. Developers should use the {\tt H5VL} functions above in the native library and tests when expecting to get back the plugin specific objects.

As for {\tt H5I\_iterate()}, we update the implementation of this function internally to unwrap the object being iterated over if it is a file, dataset, group, attribute, or named datatype, and return the plugin specific object to the iterate callback. We saw this as a better approach than requiring a change in all the iteration callbacks to check for the object type and unwrap it accordingly. With the current solution, no code changes are required in the internal usage of {\tt H5I\_iterate()}.

\section{Native Plugin Implementation}
The native HDF5 plugin implements the VOL callbacks with the native HDF5 file format. This is basically all what the library currently does when implementing HDF5 features. The native VOL plugin is implemented in {\tt H5VLnative.c}. The callbacks of the VOL class are implemented here similarly to how the API routines were mapped directly to the internal HDF5 implementation before the VOL was introduced. However, since there isn't a one to one mapping from every API routine to a VOL callback, there is an additional level of processing parameters passed in from the VOL intermediate layer. The protocol for parameter processing is explained in detail in the VOL user guide.

There are places in the library where we need to register an identifier to pass directly to the application (for example, creating a group identifier and calling the user defined link iteration callback). To do that, we need to create the high level object wrapper and attach the native plugin information before registering that ID. This can be done by calling this private and native specific routine:
\begin{lstlisting}
hid_t H5VL_native_register(H5I_type_t type, void *obj, hbool_t app_ref);
\end{lstlisting}
which does all the steps required for creating an identifier for the native object. That identifier has to be freed with:
\begin{lstlisting}
herr_t H5VL_native_unregister(hid_t obj_id);
\end{lstlisting}

\section{The Named Datatype Pickle}

\section{Dynamically Loaded VOL Plugins}

\section{Adding New Features to the Library}

### 2014-09-22 RFCs/HDF5/VOL/user_guide/stacking.tex
updates
Former-commit-id: 075132ce087eee5f33c09f6c78cb3bd1c8f6d8c8

@@
 stacking the native HDF5 plugin on top of a non-HDF5 backend plugin
-does not make sense and is erroneous. Figure~\ref{stack} shows a
+does not make sense and is erroneous. Figure~\ref{fig:stack} shows a
 stacking of a remote plugin, where data is distributed remotely, on
@@
 \caption{Stacked VOL plugins.}
-\label{stack}
+\label{fig:stack}
 \end{figure}
@@
 VOL plugins. This is an extention to the stacking
-feature. Figure~\ref{mirror} shows an example of a VOL mirror that
+feature. Figure~\ref{fig:mirror} shows an example of a VOL mirror that
 maps HDF5 API calls to an h5 backend plugin and an XML backend plugin.
@@
 \caption{Mirrored VOL plugins.}
-\label{mirror}
+\label{fig:mirror}
 \end{figure}
@@
 
+\pagebreak
+
 %%% Local Variables: 

### 2014-09-23 RFCs/HDF5/VOL/developer_guide/body.tex
more updates
Former-commit-id: 71343f270c3f1a4a23269c10a4fd82cf50bcc727

@@
 \section{The Named Datatype Pickle}
+Datatypes in HDF5 exist in two states, transient and committed.
+When a user creates an HDF5 datatype, it is in the transient state, i.e.
+in memory space.
+It does not exist in the file; in fact, an HDF5 program could work with datatypes without even opening or accessing any HDF5 file.
+HDF5 provides a way for users to write (or commit) a datatype to the HDF5 file.
+When a user calls {\tt H5Tcommit()} on a transient type, that datatype is written to the HDF5 file under the location specified in the commit call.
+The datatype then becomes a named/committed datatype.
+Since the datatype is not stored in the file, the use can open that datatype from the file later to retrieve it and work with it in a similar way like other objects that are stored in the file (groups, datasets, and attributes).
 
-\section{Dynamically Loaded VOL Plugins}
+There are a large set of routines that operate on datatypes in general.
+For a complete list, look at the reference manual for the {\tt H5T} interface.
+As far as the user is concerned, it does not matter whether the datatype is committed or not.
+Those routines work the same way for transient or named datatypes.
+With the addition of the VOL, a datatype class is added to handle committing and opening a named datatype, in addition to retrieving some metadata stored with the named datatype.
+However other operations that work with datatypes in both its transient or committed state do not pass through the VOL, since they do not access the datatype in the container.
+At that point the datatype should already by open and loaded into memory space for those operations to work.
+We chose not to handle those operations through the VOL even if that datatype is committed, to relieve VOL plugin developers from implementing a large set of datatype routines that is already available in the HDF5 library and is likely to be the same across all VOL plugins.
+
+The design decision above does have some implications on the internal handling of named datatypes with the VOL changes.
+The higher level datatype APIs expect that the identifier for dataypes (named and transient) to map to the private {\tt H5T\_t} structure.
+However; as we explained earlier in this document, the object that we get back from the VOL plugins when committing a datatype to the file is a {\tt void} pointer that the library just needs to keep track.
+For the native plugin we do know that the pointer is actually pointing to the internal {\tt H5T\_t} structure for the name datatype, but we can not make that assumption for other plugins that will return a pointer to their own implementation of named datatypes.
+Furthermore we need to wrap whatever object returned from the plugin when creating/committing a named datatype with the higher level object structure that contains the VOL plugin information used for creating the datatype.
+This mismatch between what the VOL expects and what the {\tt H5T} API functions expect will require us to do some special handling for committing and opening named datatypes:
+
+\begin{itemize}
+\item Committing a transient datatype: At this point the identifier for the datatype exists and points to the private transient {\tt H5T\_t} structure.
+The difference between other objects and named datatypes is that the identifier for the named datatype should always dereference to the private {\tt H5T\_t} structure, so instead of updating the identifier's underlying object after committing the datatype to the newly created {\tt H5VL\_object\_t} structure for the VOL object of the named datatype, we store that object pointer in a newly added field to the private {\tt H5T\_t} structure and use that field to determine if that datatype is committed or not.
+At this point we satisfied the requirement for the public {\tt H5T} functions that do not care about the state of the datatype and can continue to work with the datatype identifier since it still dereferences to the same {\tt H5T\_t } structure, but with an additional field.
+The additional field contains the VOL object that should be used instead of the {\tt H5T\_t} structure when operating on that datatype through the VOL.
+
+\item Opening a named datatype: The open operation for a named datatype is forwarded to the VOL that returns the VOL specific pointer to the datatype that is opened.
+The open operation for datatypes should return an identifier that dereferences to an {\tt H5T\_t} structure for the reasons we stated earlier.
+However at this point we do not have the {\tt H5T\_t} structure for that datatype.
+For this reason we require all VOL plugins that support named datatypes to store a serialized copy of the HDF5 datatype somewhere in the underlying container when committing a named datatype.
+After opening the datatype through the VOL, we ask the VOL plugin to return the serialized form of the datatype which we can call {\tt H5T\_decode()} on to create the private {H5T\_t} structure which is a transient form of the datatype.
+Then we store the object created from the open operation in the new {\tt vol\_obj} field of the {\tt H5T\_t} structure we just created and atomize it to return to the user.
+\end{itemize}
+
+HDF5 datatypes proved to be quite a challenge with the VOL due to the two states that they exist in unlike any other HDF5 object.
+However we believe the design decisions we made and explained above are a compromise to ease the work for plugin developers and HDF5 library maintainers at the same time.
+
+%\section{Dynamically Loaded VOL Plugins}
+%The VOL supports loading third party VOL plugins that have been installed on a system as shared libraries.
+The implementation for checking and loading those plugins is similar to the HDF5 filter plugin loading.
 
 \section{Adding New Features to the Library}
+It is expected that new features and routines will be added to the HDF5 library after the VOL has been introduced.
+New functionality added that accesses data in the file has to go through the VOL the same way that any other function does.
+There are several ways to handle extensions to the VOL.
+
+\begin{itemize}
+\item Adding a new VOL class for the new feature.
+This usually means that a new object type is added to the HDF5 library or a new service is introduced that is expected to be general in the sense that most plugins should be implemented.
+For example, consider the case when a new HDF5 object is added to the library that allows users to create and use a KV store in the HDF5 container.
+Adding a new class means that all existing plugins have to be modified to cope with the change in the VOL public structure.
+Changing the VOL public structure should be done only in major HDF5 releases, and not in maintenance releases.
+
+\item Adding a new callback to a VOL class.
+This is done when a new API function is added to a particular class of operations (Files, Datasets, Groups, etc...) and is quite important that it can't be ``hidden'' in the {\tt specific} callback of that class.
+This change in the public VOL class also requires all existing plugins to be updated and should be done in major releases only.
+
+\item Adding a new operation type to the {\tt get, specific} or {\tt optional} callbacks of a sub-class in the VOL public structure.
+When a new operation type to retrieve data from a particular object or to execute some new operation on that object, whether that operation is general among all plugins or plugin specific, adding a new type to the {\tt enum} of types for the three callbacks present in every sub-class should be enough to support the new operation.
+For more information on how this works, please consult with the VOL user guide.
+
+\item Adding a new operation type to the {\tt optional} callback in the VOL public class for services.
+New HDF5 functionality that is added specifically for certain plugins and would not make sense to promote to an actual class since it isn't general enough to be implemented by most plugins or would not be used a lot by applications should follow this option.
+
+\end{itemize}

### 2014-09-23 RFCs/HDF5/VOL/user_guide/appendix.tex
add example
Former-commit-id: 06d8b556668e3dd53df67be09620df7dc29f6629

\appendix
\section{VOL Plugin Example}
\label{sec:A}

This appendix shows a simple implementation of a {\tt printf} plugin that stacks on top of the native HDF5 plugin. Note that not all callbacks have been implemented since this is just an example for explaining the general framework of the VOL plugin.

\begin{lstlisting}

#include <stdio.h>
#include <stdlib.h>
#include <assert.h>
#include "hdf5.h"

#define LOG 502

static herr_t H5VL_log_init(hid_t vipl_id);
static herr_t H5VL_log_term(hid_t vtpl_id);

/* Datatype callbacks */
static void *H5VL_log_datatype_commit(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
static void *H5VL_log_datatype_open(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
static herr_t H5VL_log_datatype_get(void *dt, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
static herr_t H5VL_log_datatype_close(void *dt, hid_t dxpl_id, void **req);

/* Dataset callbacks */
static void *H5VL_log_dataset_create(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
static void *H5VL_log_dataset_open(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
static herr_t H5VL_log_dataset_read(void *dset, hid_t mem_type_id, hid_t mem_space_id,
                                    hid_t file_space_id, hid_t plist_id, void *buf, void **req);
static herr_t H5VL_log_dataset_write(void *dset, hid_t mem_type_id, hid_t mem_space_id,
                                     hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
static herr_t H5VL_log_dataset_close(void *dset, hid_t dxpl_id, void **req);

/* File callbacks */
static void *H5VL_log_file_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
static void *H5VL_log_file_open(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
static herr_t H5VL_log_file_get(void *file, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
static herr_t H5VL_log_file_close(void *file, hid_t dxpl_id, void **req);

/* Group callbacks */
static void *H5VL_log_group_create(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
static herr_t H5VL_log_group_close(void *grp, hid_t dxpl_id, void **req);

/* Link callbacks */

/* Object callbacks */
static void *H5VL_log_object_open(void *obj, H5VL_loc_params_t loc_params, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
static herr_t H5VL_log_object_specific(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);

hid_t native_plugin_id = -1;

static const H5VL_class_t H5VL_log_g = {
    0,
    LOG,
    "log",					/* name */
    H5VL_log_init,                              /* initialize */
    H5VL_log_term,                              /* terminate */
    sizeof(hid_t),
    NULL,
    NULL,
    {                                           /* attribute_cls */
        NULL, //H5VL_log_attr_create,                /* create */
        NULL, //H5VL_log_attr_open,                  /* open */
        NULL, //H5VL_log_attr_read,                  /* read */
        NULL, //H5VL_log_attr_write,                 /* write */
        NULL, //H5VL_log_attr_get,                   /* get */
        NULL, //H5VL_log_attr_specific,              /* specific */
        NULL, //H5VL_log_attr_optional,              /* optional */
        NULL  //H5VL_log_attr_close                  /* close */
    },
    {                                           /* dataset_cls */
        H5VL_log_dataset_create,                    /* create */
        H5VL_log_dataset_open,                      /* open */
        H5VL_log_dataset_read,                      /* read */
        H5VL_log_dataset_write,                     /* write */
        NULL, //H5VL_log_dataset_get,               /* get */
        NULL, //H5VL_log_dataset_specific,          /* specific */
        NULL, //H5VL_log_dataset_optional,          /* optional */
        H5VL_log_dataset_close                      /* close */
    },
    {                                               /* datatype_cls */
        H5VL_log_datatype_commit,                   /* commit */
        H5VL_log_datatype_open,                     /* open */
        H5VL_log_datatype_get,                      /* get_size */
        NULL, //H5VL_log_datatype_specific,         /* specific */
        NULL, //H5VL_log_datatype_optional,         /* optional */
        H5VL_log_datatype_close                     /* close */
    },
    {                                           /* file_cls */
        H5VL_log_file_create,                      /* create */
        H5VL_log_file_open,                        /* open */
        H5VL_log_file_get,                         /* get */
        NULL, //H5VL_log_file_specific,            /* specific */
        NULL, //H5VL_log_file_optional,            /* optional */
        H5VL_log_file_close                        /* close */
    },
    {                                           /* group_cls */
        H5VL_log_group_create,                     /* create */
        NULL, //H5VL_log_group_open,               /* open */
        NULL, //H5VL_log_group_get,                /* get */
        NULL, //H5VL_log_group_specific,           /* specific */
        NULL, //H5VL_log_group_optional,           /* optional */
        H5VL_log_group_close                       /* close */
    },
    {                                           /* link_cls */
        NULL, //H5VL_log_link_create,                /* create */
        NULL, //H5VL_log_link_copy,                  /* copy */
        NULL, //H5VL_log_link_move,                  /* move */
        NULL, //H5VL_log_link_get,                   /* get */
        NULL, //H5VL_log_link_specific,              /* specific */
        NULL, //H5VL_log_link_optional,              /* optional */
    },
    {                                           /* object_cls */
        H5VL_log_object_open,                        /* open */
        NULL, //H5VL_log_object_copy,                /* copy */
        NULL, //H5VL_log_object_get,                 /* get */
        H5VL_log_object_specific,                    /* specific */
        NULL, //H5VL_log_object_optional,            /* optional */
    },
    {
        NULL,
        NULL,
        NULL
    },
    NULL
};

typedef struct H5VL_log_t {
    void   *under_object;
} H5VL_log_t;

static herr_t
visit_cb(hid_t oid, const char *name,
         const H5O_info_t *oinfo, void *udata)
{
    ssize_t len;
    char n[25];

    if(H5Iget_type(oid) == H5I_GROUP) {
        len = H5VLget_plugin_name(oid, n, 50);
        printf ("Visiting GROUP VOL name = %s  %d\n", n, len);
    }
    if(H5Iget_type(oid) == H5I_DATASET) 
        printf("visiting dataset\n");
    if(H5Iget_type(oid) == H5I_DATATYPE) 
        printf("visiting datatype\n");

    return 1;
} /* end h5_verify_cached_stabs_cb() */

int main(int argc, char **argv) {
        const char file_name[]="large_dataset.h5";
	const char group_name[]="/Group";
	const char dataset_name[]="Data";
	char fullpath[500];
	hid_t file_id;
	hid_t group_id;
	hid_t dataspaceId;
        hid_t datasetId;
        hid_t acc_tpl;
        hid_t under_fapl;
        hid_t vol_id, vol_id2;
        hid_t int_id;
        hid_t attr;
        hid_t space;
	const unsigned int nelem=60;
	int *data;
	unsigned int i;
	hsize_t dims[1];
        ssize_t len;
        char name[25];
        static hsize_t      ds_size[2] = {10, 20};

        under_fapl = H5Pcreate (H5P_FILE_ACCESS);
        H5Pset_fapl_native(under_fapl);
        assert(H5VLis_registered("native") == 1);

        vol_id = H5VLregister (&H5VL_log_g);
        assert(vol_id > 0);
        assert(H5VLis_registered("log") == 1);

        vol_id2 = H5VLget_plugin_id("log");
        H5VLinitialize(vol_id2, H5P_DEFAULT);
        H5VLclose(vol_id2);

        native_plugin_id = H5VLget_plugin_id("native");
        assert(native_plugin_id > 0);

        acc_tpl = H5Pcreate (H5P_FILE_ACCESS);
        H5Pset_vol(acc_tpl, vol_id, &under_fapl);

	file_id = H5Fcreate(file_name, H5F_ACC_TRUNC, H5P_DEFAULT, acc_tpl);
        len = H5VLget_plugin_name(file_id, name, 25);
        printf ("FILE VOL name = %s  %d\n", name, len);

	group_id = H5Gcreate2(file_id, group_name, H5P_DEFAULT, H5P_DEFAULT, H5P_DEFAULT);
        len = H5VLget_plugin_name(group_id, name, 50);
        printf ("GROUP VOL name = %s  %d\n", name, len);

        int_id = H5Tcopy(H5T_NATIVE_INT);
        H5Tcommit2(file_id, "int", int_id, H5P_DEFAULT, H5P_DEFAULT, H5P_DEFAULT);
        len = H5VLget_plugin_name(int_id, name, 50);
        printf ("DT COMMIT name = %s  %d\n", name, len);
        H5Tclose(int_id);

        int_id = H5Topen2(file_id, "int", H5P_DEFAULT);
        len = H5VLget_plugin_name(int_id, name, 50);
        printf ("DT OPEN name = %s  %d\n", name, len);
        H5Tclose(int_id);

        int_id = H5Oopen(file_id,"int",H5P_DEFAULT);
        len = H5VLget_plugin_name(int_id, name, 50);
        printf ("DT OOPEN name = %s  %d\n", name, len);

        len = H5Fget_name(file_id, name, 50);
        printf("name = %d  %s\n", len, name);

	data = malloc (sizeof(int)*nelem);
	for(i=0;i<nelem;++i)
	  data[i]=i;

	dims [0] = 60;
	dataspaceId = H5Screate_simple(1, dims, NULL); 
        space = H5Screate_simple (2, ds_size, ds_size);

	sprintf(fullpath,"%s/%s",group_name,dataset_name);
	datasetId = H5Dcreate2(file_id, fullpath, H5T_NATIVE_INT, dataspaceId, H5P_DEFAULT, H5P_DEFAULT, H5P_DEFAULT);
	H5Sclose(dataspaceId);

        len = H5VLget_plugin_name(datasetId, name, 50);
        printf ("DSET name = %s  %d\n", name, len);

	H5Dwrite(datasetId, H5T_NATIVE_INT, H5S_ALL, H5S_ALL, H5P_DEFAULT, data);
	H5Dclose(datasetId);

        H5Ovisit(file_id, H5_INDEX_NAME, H5_ITER_NATIVE, visit_cb, NULL);

	free (data);
        H5Oclose(int_id);
        H5Sclose (space);
	H5Gclose(group_id);

	H5Fclose(file_id);
        H5Pclose(acc_tpl);
        H5Pclose(under_fapl);

        H5VLclose(native_plugin_id);
        H5VLterminate(vol_id, H5P_DEFAULT);
        H5VLunregister (vol_id);
        assert(H5VLis_registered("log") == 0);
	return 0;
}

static herr_t H5VL_log_init(hid_t vipl_id)
{
    printf("------- LOG INIT\n");
    return 0;
}

static herr_t H5VL_log_term(hid_t vtpl_id)
{
    printf("------- LOG TERM\n");
    return 0;
}

static void *
H5VL_log_file_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req)
{
    hid_t under_fapl;
    H5VL_log_t *file;

    file = (H5VL_log_t *)calloc(1, sizeof(H5VL_log_t));

    under_fapl = *((hid_t *)H5Pget_vol_info(fapl_id));
    file->under_object = H5VLfile_create(name, flags, fcpl_id, under_fapl, dxpl_id, req);

    printf("------- LOG H5Fcreate\n");
    return (void *)file;
}

static void *
H5VL_log_file_open(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req)
{
    hid_t under_fapl;
    H5VL_log_t *file;

    file = (H5VL_log_t *)calloc(1, sizeof(H5VL_log_t));

    under_fapl = *((hid_t *)H5Pget_vol_info(fapl_id));
    file->under_object = H5VLfile_open(name, flags, under_fapl, dxpl_id, req);

    printf("------- LOG H5Fopen\n");
    return (void *)file;
}

static herr_t 
H5VL_log_file_get(void *file, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments)
{
    H5VL_log_t *f = (H5VL_log_t *)file;

    H5VLfile_get(f->under_object, native_plugin_id, get_type, dxpl_id, req, arguments);

    printf("------- LOG H5Fget %d\n", get_type);
    return 1;
}
static herr_t 
H5VL_log_file_close(void *file, hid_t dxpl_id, void **req)
{
    H5VL_log_t *f = (H5VL_log_t *)file;

    H5VLfile_close(f->under_object, native_plugin_id, dxpl_id, req);
    free(f);

    printf("------- LOG H5Fclose\n");
    return 1;
}

static void *
H5VL_log_group_create(void *obj, H5VL_loc_params_t loc_params, const char *name, 
                      hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req)
{
    H5VL_log_t *group;
    H5VL_log_t *o = (H5VL_log_t *)obj;

    group = (H5VL_log_t *)calloc(1, sizeof(H5VL_log_t));

    group->under_object = H5VLgroup_create(o->under_object, loc_params, native_plugin_id, name, gcpl_id,  gapl_id, dxpl_id, req);

    printf("------- LOG H5Gcreate\n");
    return (void *)group;
}

static herr_t 
H5VL_log_group_close(void *grp, hid_t dxpl_id, void **req)
{
    H5VL_log_t *g = (H5VL_log_t *)grp;

    H5VLgroup_close(g->under_object, native_plugin_id, dxpl_id, req);
    free(g);

    printf("------- LOG H5Gclose\n");
    return 1;
}

static void *
H5VL_log_datatype_commit(void *obj, H5VL_loc_params_t loc_params, const char *name, 
                         hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req)
{
    H5VL_log_t *dt;
    H5VL_log_t *o = (H5VL_log_t *)obj;

    dt = (H5VL_log_t *)calloc(1, sizeof(H5VL_log_t));

    dt->under_object = H5VLdatatype_commit(o->under_object, loc_params, native_plugin_id, name, 
                                           type_id, lcpl_id, tcpl_id, tapl_id, dxpl_id, req);

    printf("------- LOG H5Tcommit\n");
    return dt;
}
static void *
H5VL_log_datatype_open(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req)
{
    H5VL_log_t *dt;
    H5VL_log_t *o = (H5VL_log_t *)obj;

    dt = (H5VL_log_t *)calloc(1, sizeof(H5VL_log_t));

    dt->under_object = H5VLdatatype_open(o->under_object, loc_params, native_plugin_id, name, tapl_id, dxpl_id, req);

    printf("------- LOG H5Topen\n");
    return (void *)dt;
}

static herr_t 
H5VL_log_datatype_get(void *dt, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments)
{
    H5VL_log_t *o = (H5VL_log_t *)dt;
    herr_t ret_value;

    ret_value = H5VLdatatype_get(o->under_object, native_plugin_id, get_type, dxpl_id, req, arguments);

    printf("------- LOG datatype get\n");
    return ret_value;
}

static herr_t 
H5VL_log_datatype_close(void *dt, hid_t dxpl_id, void **req)
{
    H5VL_log_t *type = (H5VL_log_t *)dt;

    assert(type->under_object);

    H5VLdatatype_close(type->under_object, native_plugin_id, dxpl_id, req);
    free(type);

    printf("------- LOG H5Tclose\n");
    return 1;
}

static void *
H5VL_log_object_open(void *obj, H5VL_loc_params_t loc_params, H5I_type_t *opened_type, hid_t dxpl_id, void **req)
{
    H5VL_log_t *new_obj;
    H5VL_log_t *o = (H5VL_log_t *)obj;

    new_obj = (H5VL_log_t *)calloc(1, sizeof(H5VL_log_t));

    new_obj->under_object = H5VLobject_open(o->under_object, loc_params, native_plugin_id, opened_type, dxpl_id, req);

    printf("------- LOG H5Oopen\n");
    return (void *)new_obj;
}

static herr_t 
H5VL_log_object_specific(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, 
                         hid_t dxpl_id, void **req, va_list arguments)
{
    H5VL_log_t *o = (H5VL_log_t *)obj;

    H5VLobject_specific(o->under_object, loc_params, native_plugin_id, specific_type, dxpl_id, req, arguments);

    printf("------- LOG Object specific\n");
    return 1;
}

static void *
H5VL_log_dataset_create(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req) 
{
    H5VL_log_t *dset;
    H5VL_log_t *o = (H5VL_log_t *)obj;

    dset = (H5VL_log_t *)calloc(1, sizeof(H5VL_log_t));

    dset->under_object = H5VLdataset_create(o->under_object, loc_params, native_plugin_id, name, dcpl_id,  dapl_id, dxpl_id, req);

    printf("------- LOG H5Dcreate\n");
    return (void *)dset;
}

static void *
H5VL_log_dataset_open(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req)
{
    H5VL_log_t *dset;
    H5VL_log_t *o = (H5VL_log_t *)obj;

    dset = (H5VL_log_t *)calloc(1, sizeof(H5VL_log_t));

    dset->under_object = H5VLdataset_open(o->under_object, loc_params, native_plugin_id, name, dapl_id, dxpl_id, req);

    printf("------- LOG H5Dopen\n");
    return (void *)dset;
}

static herr_t 
H5VL_log_dataset_read(void *dset, hid_t mem_type_id, hid_t mem_space_id,
                      hid_t file_space_id, hid_t plist_id, void *buf, void **req)
{
    H5VL_log_t *d = (H5VL_log_t *)dset;

    H5VLdataset_read(d->under_object, native_plugin_id, mem_type_id, mem_space_id, file_space_id, 
                     plist_id, buf, req);

    printf("------- LOG H5Dread\n");
    return 1;
}
static herr_t 
H5VL_log_dataset_write(void *dset, hid_t mem_type_id, hid_t mem_space_id,
                       hid_t file_space_id, hid_t plist_id, const void *buf, void **req)
{
    H5VL_log_t *d = (H5VL_log_t *)dset;

    H5VLdataset_write(d->under_object, native_plugin_id, mem_type_id, mem_space_id, file_space_id, 
                     plist_id, buf, req);

    printf("------- LOG H5Dwrite\n");
    return 1;
}
static herr_t 
H5VL_log_dataset_close(void *dset, hid_t dxpl_id, void **req)
{
    H5VL_log_t *d = (H5VL_log_t *)dset;

    H5VLdataset_close(d->under_object, native_plugin_id, dxpl_id, req);
    free(d);

    printf("------- LOG H5Dclose\n");
    return 1;
}
\end{lstlisting}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2014-09-23 RFCs/HDF5/VOL/user_guide/plugin.tex
add example
Former-commit-id: 06d8b556668e3dd53df67be09620df7dc29f6629

@@
 \begin{lstlisting}
-r object GET callback */
+/* type for object GET callback */
 typedef enum H5VL_object_get_t {
@@
   \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference
-    (should be {\tt H5R\_DATASET\_REGION}.
+    (should be {\tt H5R\_DATASET\_REGION}).
   \item {\tt void *ref} (IN): the region reference to open.

### 2014-11-14 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Update analysis extension RFC to revision 3
Former-commit-id: 03d763e94e151b89b3092f5198c962c4dc273817

--- 2014-08-18 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
@@
     UprightFont={*},
-    BoldFont={* Bold},
-    ItalicFont={* Italic},
-    BoldItalicFont={* Bold Italic},
-    SlantedFont={* Italic},
-    BoldSlantedFont={* Bold Italic}
-  ]{Calibri}
+    BoldFont={*-Bold},
+    ItalicFont={*-Italic},
+    BoldItalicFont={*-BoldItalic},
+    SlantedFont={*-Italic},
+    BoldSlantedFont={*-BoldItalic}
+  ]{CMU Serif}
   \setsansfont[
     UprightFont={*},
-    BoldFont={* Bold},
-    ItalicFont={* Italic},
-    BoldItalicFont={* Bold Italic}
-  ]{Calibri}
+    BoldFont={*-Bold},
+    ItalicFont={*-Oblique},
+    BoldItalicFont={*-BoldOblique}
+  ]{CMU Sans Serif}
   \setmathfont[math-style=ISO, bold-style=ISO]{Asana Math}
   \setmonofont[
-    UprightFont={*},
-    BoldFont={* Bold},
-    ItalicFont={* Italic},
-    BoldItalicFont={* Bold Italic}
-  ]{Courier New}
+    UprightFont={*-Regular},
+    BoldFont={*-Bold},
+    ItalicFont={*-Italic},
+    BoldItalicFont={*-BoldItalic}
+  ]{CMU Typewriter}
 \else
@@
   breaklines=true,
-  basicstyle=\footnotesize\ttfamily,
+  basicstyle=\small\ttfamily,
   stringstyle=\itshape,
@@
 \author{Quincey Koziol}
-\date{July 17, 2014}
-\rfcversion{2014-07-17.v1}
+\date{November 14, 2014}
+\rfcversion{2014-07-17.v3}
 \revision{July 17, 2014}{Version 1 circulated for comment within The HDF Group.}
+\revision{August 20, 2014}{Version 2 circulated for comment within The HDF Group.}
+\revision{November 14, 2014}{Version 3 circulated for comment within The HDF Group.}
 
@@
 \begin{abstract}
-Accessing and retrieving data from an HDF5 container can be a time consuming
-process, particularly so when data is very large. To enable,
-ease and accelerate the process of querying data, we introduce in this RFC data
-analysis extensions to query, select and index data.
+Accessing, selecting and retrieving data from an HDF5 container can be a time
+consuming process, particularly so when data is very large. To enable, ease and 
+accelerate this process, we introduce in this RFC extensions to the library
+to efficiently query, select and index data.
 \end{abstract}
@@
 \section{Introduction}
-Data Analysis Extensions to the HDF5 API and data model can enable application
-developers to create complex and high-performance queries on both metadata and
-data elements within an HDF5 container and retrieve the results of applying
-those query operations to an HDF5 container.
-Support for data analysis operations on HDF5 containers can be defined via:
+When working on large datasets, finding and selecting the interesting pieces of
+the data can be a cumbersome process. Currently, the HDF5 library enables the 
+application developer to select, read and write data but does not provide any 
+mechanism
+to select and retrieve pieces without prior knowledge of the content of the data,
+or without the developer to provide the exact data
+coordinates that he is willing to access. To satisfy that need, one must be able
+to issue queries by specifying a data selection criteria. These queries,
+applied to the data, can then generate a selection, which contains the coordinates
+that satisfy the query. This may thus imply accessing the data and selecting it,
+depending on the query condition satisfaction. Furthermore, this process can be 
+accelerated so that the data no longer needs to be directly accessed, by using 
+indexing  techniques, which consist of generating an index and using that index
+to answer the query selection criteria and find the matching elements.
+
+We define in this RFC the components that can enable application developers to
+create complex and high-performance queries on both metadata and data elements
+within an HDF5 container and retrieve the results of applying those query
+operations. Support for these operations on HDF5 containers can be defined via:
 \begin{itemize}
@@
 herr_t H5Qclose(hid_t query_id);
-
 hid_t  H5Qcombine(hid_t query1_id, H5Q_combine_op_t combine_op, hid_t query2_id);
-
 herr_t H5Qget_type(hid_t query_id, H5Q_type_t *query_type);
@@
 herr_t H5Qget_combine_op(hid_t query_id, H5Q_combine_op_t *op_type);
-
 herr_t H5Qencode(hid_t query_id, void *buf, size_t *nalloc);
@@
 \texttt{H5Qcombine} combines two query objects into a
-new query object, using Boolean operators such as $AND(\land)$ and $OR(\lor)$.
+new query object, using boolean operators such as $AND(\land)$ and $OR(\lor)$.
 Queries created with \texttt{H5Qcombine} can be used as input to further
@@
 
-For example, starting with the HDF5 container described in \FigureRef{fig:hdf5_view1},
+For example, starting with the HDF5 container described in~\FigureRef{fig:hdf5_view1},
 applying the $link\_name = Pressure$ query (described above) would result
-in the view shown in \FigureRef{fig:hdf5_view2}, with the
-underlying container grayed out and the view highlighted in blue.
+in the view shown in~\FigureRef{fig:hdf5_view2}, highlighted in blue.
 
@@
 Alternatively, applying the $data\_element = 17$ query (described above) would
-result in the view shown in \FigureRef{fig:hdf5_view3}, with the
-underlying container greyed out and the view highlighted in blue.
+result in the view shown in~\FigureRef{fig:hdf5_view3}, highlighted in blue.
 
@@
 Finally, applying the combined $(link\_name = Pressure)\land(data\_element = 17)$
-query (described above) would result in the view shown in
-\FigureRef{fig:hdf5_view4}, with the underlying container
-greyed out and the view highlighted in blue.
+query (described above) would result in the view shown in~\FigureRef{fig:hdf5_view4},
+highlighted in blue.
 
@@
 \section{Index Objects}
-The final component of the data analysis extensions to HDF5 is the index object.
+The final and core component of the data analysis extensions to HDF5 is the index object.
 Index objects are designed to accelerate creation of view objects from
@@
 For example, if the $(link\_name = Pressure)\land(data\_element = 17)$ query
-(described above) is going to be frequently executed on the container, indices
+(previously described) is going to be frequently executed on the container, indices
 could be created in that container, which would speed up the creation of views
@@
 HDF5. Queries with metadata components execute properly,
-\todo{Must write about metadata indexing} but are not able to be accelerated
+\todo{TBD metadata indexing} but are not able to be accelerated
 with an index currently.
 
-The indexing API works in conjunction with the view API. When an \texttt{H5Vcreate}
+The indexing API can work in conjunction with the view API. When an \texttt{H5Vcreate}
 call is made for a group or dataset, an index attached to any dataset queried
@@
 
-A new HDF5 interface is defined for adding third-party indexing plugins,
+This interface is defined for adding third-party indexing plugins,
 such as FastBit~\cite{Wu05}, ALACRITY~\cite{alacrity13}, etc.
@@
 herr_t  H5Xunregister(unsigned plugin_id);
-
-herr_t H5Xcreate(hid_t file_id, unsigned plugin_id, hid_t scope_id,
-        hid_t xcpl_id);
-herr_t H5Xremove(hid_t file_id, unsigned plugin_id, hid_t scope_id);
+herr_t  H5Xcreate(hid_t scope_id, unsigned plugin_id, hid_t xcpl_id);
+herr_t  H5Xremove(hid_t scope_id, unsigned n /* Index n to be removed */);
 herr_t  H5Xget_count(hid_t scope_id, hsize_t *idx_count);
+herr_t  H5Xget_info(hid_t scope_id, unsigned n, H5X_info_t *info);
+hsize_t H5Xget_size(hid_t scope_id);
 
@@
     /* Callbacks, described above */
-    void *(*create)(hid_t file_id, hid_t dataset_id, hid_t xcpl_id,
-        hid_t xapl_id, size_t *metadata_size, void **metadata);
-    herr_t (*remove)(hid_t file_id, hid_t dataset_id, size_t metadata_size,
+    void *(*create)(hid_t dataset_id, hid_t xcpl_id, hid_t xapl_id,
+        size_t *metadata_size, void **metadata);
+    herr_t (*remove)(hid_t dataset_id, size_t metadata_size, void *metadata);
+    void *(*open)(hid_t dataset_id, hid_t xapl_id, size_t metadata_size,
         void *metadata);
-    herr_t (*copy)(hid_t file1_id, hid_t file2_id, hid_t dataset1_id,
-        hid_t dataset2_id, hid_t xcpl_id, hid_t xapl_id,
-        size_t metadata_size, void *metadata);
-    void *(*open)(hid_t file_id, hid_t dataset_id, hid_t xapl_id,
-        size_t metadata_size, void *metadata);
     herr_t (*close)(void *idx_handle);
+    herr_t (*copy)(hid_t src_dataset_id, hid_t dest_dataset_id, hid_t xcpl_id,
+        hid_t xapl_id, size_t src_metadata_size, void *src_metadata,
+        size_t *dest_metadata_size, void **dest_metadata);
     herr_t (*pre_update)(void *idx_handle, hid_t dataspace_id, hid_t xxpl_id);
@@
 Instead, index objects are part of the metadata for the file itself. New index
-objects are created by passing an H5 container to be indexed and the index
+objects are created by passing an HDF5 container to be indexed and the index
 plugin ID to the \texttt{H5Xcreate} call.
@@
 invoked to create a selection of elements in the dataset that match the query
-parameters. Applications can also use the new \texttt{H5Dquery} routine to directly
-execute a query on a dataset (accelerated by any index defined on the dataset),
-retrieving the selection within that dataset that matches the query.
+parameters. Applications can also use the new \texttt{H5Dquery} routine defined below
+to directly
+execute a query on a particular dataset (accelerated by any index defined on the dataset),
+retrieving the selection that matches the query.
+
+{\lstsetc
+\begin{lstlisting}
+herr_t H5Dquery(hid_t dset_id, hid_t space_id, hid_t query_id, hid_t xapl_id,
+    hid_t *space_id);
+\end{lstlisting}
+}
 
@@
 itself, the \texttt{get\_size} callback can query the amount of space that
-the index takes in the file.
-
-\todo{Add something about parallel queries / multi dataset serial / multiquery paragraph}
+the index takes in the file and users may query that information using the
+corresponding \texttt{H5Xget\_size} routine.
 
@@
 present, as well as a brute force indexing plugin. Early performance results
-are presented in \FigureRef{fig:indexing_perf}.
+are presented in~\FigureRef{fig:indexing_perf}.
 
@@
 
-In the future more plugins
-will be added, with and without external dependency (e.g., pytable indexing,
-bitmap indexing).
+In the future more plugins will be added, with and without external dependency
+(e.g., PyTables indexing, bitmap indexing).
 To satisfy that need, dynamic plugin loading and registration will be supported,
@@
 put limits on application updates to datasets with indices.
-Additionally, because FastBit and Alacrity don't allow incremental updates to
+Additionally, because FastBit and ALACRITY don't allow incremental updates to
 an index, each modification to an existing index forces the index to be entirely
@@
 \subsubsection*{Questions}
-Some questions are still open regarding the handling on indices:
+Some questions are still open regarding the handling of indices:
 \begin{itemize}
-\item How could an index be built and queried in parallel for a dataset that already exists?
+%\item How could an index be built and queried in parallel for a dataset that already exists?
 \item How to handle index updates when the specified index plugin is not available?
@@
 \end{itemize}
+
+\subsection{Support for HDF5 Compound Types}
+
+In a simple scenario, the HDF5 datatype used for creating the dataset can be defined
+as a native and simple type. Therefore, building an index on this dataset implies
+building that index from the entire dataset. However, in more complex scenarios, the
+dataset may have been created by using a compound datatype, hence defining
+multiple fields composed of native and simple datatypes inside that same dataset.
+Consequently, creating an index from that dataset requires the user to select a
+particular field to be indexed, which may lead to having multiple indices per dataset
+depending on the number of fields that it contains. This can be done by passing
+the \texttt{datatype\_id} of the field to be indexed to the \texttt{xcpl\_id},
+the index creation property list, of the \texttt{H5Xcreate} call, which passes
+it down to the plugin \texttt{create} callback. As multiple fields can be defined,
+the field \texttt{datatype\_id} must be stored along with the existing metadata, within the
+\texttt{idx\_info} message (see~\FigureRef{fig:hdf5_index}) so that the index
+for the right field can be retrieved at the time of the query.
+When doing a query, the compound type is passed to the \texttt{H5Qcreate} call.
+The corresponding index is then used and the query is passed to the \texttt{query}
+callback of the plugin.
+
+Consequently, when removing an index, one may choose to remove the index that
+corresponds to a particular field. This can be achieved by calling \texttt{H5Xget\_info},
+compare the datatype returned inside the info structure, and pass the index number
+that needs to be removed.
+
+\subsection{Support for HDF5 Chunking}
+
+To support indexing of HDF5 chunks, we make each chunk a local \textit{sub-dataset}
+of the original dataset. In that sense, handling every chunk can be seen as handling
+a dataset from the indexing plugin point of view. if the dataset is chunked,
+at the time of the index creation, we create a B-tree\footnote{Could also
+be a map object.} (physically
+stored on disk) that maps the coordinates of the chunks to the index plugin metadata.
+When the \texttt{create} callback is called (by representing the chunk as
+a local dataset, i.e. making the dataset layout point to the address of the chunk),
+metadata information is returned and stored.
+In the case of contiguous datasets, the index metadata as well as the index plugin ID is
+stored within the dataset header within the index info message (see~\FigureRef{fig:hdf5_index}).
+In the case of chunked datasets, multiple metadata that correspond to each index created
+from each chunck may be accessed. Therefore, only the address of the B-tree that contains the 
+metadata pieces for each chunk is stored in that header message and the index
+metadata itself is stored in the B-tree.
+
+When the dataset is opened and the index reopened, we can lookup the index
+information in the B-tree that corresponds to each chunk and call the \texttt{open}
+callback using the associated metadata.
+
+%write
+%   if (chunked)
+%     modify I/O loop
+
+Similarly, when a query is issued and needs to be answered, the chunks that
+correspond to the selection passed to the \texttt{H5Dquery} call are selected
+and their index is used to answer that query. The selection returned is then
+added to a global selection, which is then returned to the user.
+
+Finally, when \texttt{H5Xremove} is called, the \texttt{delete} plugin callback is
+invoked for each chunk using the index metadata information stored in the B-tree.
+
+\subsection{Support for Parallel Indexing}
+
+An important design choice to support parallel indexing is to give as much
+freedom as possible to the indexing plugin developer so that in the case when
+the indexing library supports parallel indexing it is still possible to take
+advantage of it. However, three options remain to support parallel indexing
+within the indexing plugin interface:
+\begin{enumerate}
+\item is to let the index creation be collective. This however implies synchronization
+points, which is the main constraint.
+\item is to let the index creation be independent. However, creating datasets to
+store the index data must be done collectively\footnote{An option could be to use
+the metadata server VOL plugin but this option is not easily doable yet.}.
+\item is to let make the index creation in two phases. One that consists of
+building the index in parallel independently and gathering the information (index size, etc)
+at the end. And the other that consists of making the dataset creation by a master
+process, which can then let the other processes write the index data independently.
+There could however be a memory constraint in this case if the index data has to
+be kept in memory between these two phases (note that building the index twice is not
+a good solution either).
+\end{enumerate}
+
+Changes in the plugin interface include passing the parallel context to the
+callback (MPI communicator), which can be done by using the index access property
+list.
+
+Furthermore, in the case of chunked datasets, one may want to operate on several chunks
+at the same time in parallel. This can be done by passing to the callbacks a list of IDs that
+corresponds to each chunk. However this also makes the plugin interface more
+heavy.
 

### 2014-11-24 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Minor edits to RFC
Former-commit-id: 036f2e491d918e31afdbb6a533853248c0c99e12

@@
 
-Current implementations for FastBit and ALACRITY index packages are already
+Implementations for FastBit and ALACRITY index packages are already
 present, as well as a brute force indexing plugin. Early performance results
@@
 
-In the future more plugins will be added, with and without external dependency
+In the future more plugins will be added, with or without external dependency
 (e.g., PyTables indexing, bitmap indexing).
@@
 put limits on application updates to datasets with indices.
-Additionally, because FastBit and ALACRITY don't allow incremental updates to
+Additionally, because FastBit and ALACRITY do not allow incremental updates to
 an index, each modification to an existing index forces the index to be entirely
 rebuilt. The limitation in FastBit and ALACRITY will need to be addressed in
-the base packages' implementation, so that they can make incremental updates
-to their index information.
+the base packages' implementation, so that incremental updates
+to their index information can be made.
 

### 2015-02-06 WhitePapers/revise_chunks/paper-body.tex
Add first version of revise_chunks paper
Former-commit-id: d6849dd1a790ecd5b509ec77c49d4aaf5482a00e

% Say that there are 2 ulimited dimensions for XY extended

\section{Introduction}

The HDF5 library~\cite{Folk2011}\cite{Folk1999} provides users with a high degree of flexibility for data
management---users may define and organize data into different groups and
datasets and build an hierarchical tree of data. Datasets may be contiguously 
mapped from the application memory to a file, or stored in more complex 
patterns to ease further access and analysis of the data. One option that
is commonly used is to create and define a dataset as \textit{extendable},
in order to easily append new values to it.
An HDF5 dataset is extendable when the maximum dimension sizes of its 
dataspace are greater than the current dimension sizes, the maximum dimension 
size being specified as \textit{fixed} size or \textit{unlimited} size.

When defining an extendable dataset, the HDF5 library requires the dataset
to be partitioned into fixed-size multi-dimensional chunks---this operation, 
illustrated in figure~\ref{fig:hdf5_dataset}, is called \textit{chunking}.
Chunking makes it possible to extend datasets efficiently without having to
reorganize contiguous storage excessively. To retrieve elements in the
datasets that are stored in chunked form, the chunk containing those
elements must be located and accessed. Several structures can be used
to achieve that and the locations of chunks for a dataset have originally 
been stored in a B-tree data structure, which maps the index of the chunk to 
the file offset where the chunk's elements are stored. However, depending
on the use case and in particular for extendable datasets, the B-tree
structure used presents some drawbacks, which are addressed in this paper.

This paper is organized as follows. 
Section~\ref{sec:architecture} presents the 
current indexing method used within the library for chunking as well as 
modifications that were made to improve performance when a dataset is 
being extended. Section~\ref{sec:evaluation} presents performance evaluation 
results.
In Section~\ref{sec:related_work} we
first discuss related work before presenting conclusions and 
future research directions in Section~\ref{sec:conclusion}.

\begin{figure}
\begin{subfigure}[b]{.49\linewidth}
\centering
\input{pics/contiguous}
\caption{Contiguous.}
\label{fig:contiguous}
\end{subfigure}%
\hfill
\begin{subfigure}[b]{.49\linewidth}
\centering
\input{pics/chunked}
\vspace{-15pt}
\caption{Chunked.}
\label{fig:chunked}
\end{subfigure}
\caption{HDF5 dataset storage.}
\label{fig:hdf5_dataset}
%\vspace{-14pt}
\end{figure}

\section{Architecture}
\label{sec:architecture}

\begin{figure*}
\centering
\input{pics/btree1}
\caption{Simplified version of original B-tree structure used for indexing 
chunks. In the case of extendable datasets, whenever a new chunk is added to 
the B-tree, its right-most node, if full, is split and a new half empty node 
is created.}
\label{fig:btree1}
\end{figure*}

Chunking is a technique used in the HDF5 library in various cases:
to optimize I/O to disk~\cite{Howison2010}, to compress data~\cite{Folk2011},
to extend datasets.
To retrieve elements in the datasets that are stored in chunked form, the 
chunk containing those elements must be located and accessed. 
The HDF5 library's default data structure for indexing chunks is based on
a B-tree data structure, which maps the index
of the chunk to the file offset where the chunk's elements are stored.

\subsection{B-Trees}

B-trees are generally a good solution that is used for indexing data blocks
and one of the main components of file systems~\cite{Comer1979}~\cite{Folk1992}. 
Insertion of a new entry and lookup is realized in $O(\log_b{n})$, where $n$ is the
number of nodes and $b$ the order of the tree.
In the case of HDF5 datasets and in the original B-tree structure, referred to
as \textit{B-Tree version 1} (BT1), the record for locating the chunk stores the
following information:
\begin{itemize}
\item The coordinates of the chunk in the dataset's dataspace. This is used
as the key for locating chunks in the B-tree.
\item The size of the chunk, in bytes.
\item The address of the chunk in the file.
\item Additional metadata.
\end{itemize}

%One of the first issues is the redundancy of chunk size,
%inserted in every record, as the chunks are fixed size.
As shown in figure~\ref{fig:btree1}, each leaf points to the address of a
chunk. When a dataset is extended, a new entry is added, which may
imply a node split if the node where the record needs to be inserted is full. 
It is worth noting that most chunked datasets are either fixed dimension or
extend in only one dimension. Very few users take advantage of the ability to 
extend multiple dimensions of a dataset.
Because HDF5 datasets only allow their dimensions to be increased or 
decreased at their upper bound, a B-tree used to index chunks for a 1-D 
dataset will only ever insert or remove records from its right-most node.
One of the problems is that inserting/removing only from the right-most
node lets most records half empty, as illustrated in 
figure~\ref{fig:btree1}.

To fix that issue, one of the main improvements made with a new version of
the B-tree structure used, referred to as \textit{B-tree version 2} (BT2), is to
re-balance the entries so that nodes that were half-empty in version 1 are
now full. Additionally, to improve traversal of the tree and easily find the
chunks, the B-tree is counted so that alongside every link to a subtree, the
number of subtree elements is stored.

Some additional modifications are made to the BT2 to improve performance:
\begin{enumerate}
\item
When appending to a dataset, the library will insert a new record to the
B-tree. To determine that the record to be inserted is not in the tree,
the library traverses the corresponding tree nodes and compares the records 
in each node before the insertion.
To accelerate the search, the maximum and minimum records in the tree are 
determined and stored in the B-tree header. The library can then quickly 
determine that the new record to be inserted is not in the tree if it is 
greater than the maximum record or less than the minimum record.
\item
The default B-tree node size is $512$, which leads to a greater tree depth
than version 1 for the append test scenario. This contributes to a lower
performance because the traversal time is increased. The node size for the
tree is therefore modified to $2048$, which will flatten the tree with a tree 
depth that is the same as the BT1.
\end{enumerate}

\subsection{Extensible Arrays}

While the version 2 of the B-tree previously mentioned provides a better
balancing of the records in the tree, using it in the 1-D case (or for
datasets with only one unlimited dimension) still only ever inserts or removes
records from the right-most node.
This negates most of the advantage of using a complicated data structure like a
B-tree to index the chunks.
Additionally, for applications, which wish to rapidly append records to the 
dataset, having to traverse and/or update multiple B-tree nodes for each 
record insertion imposes an additional performance penalty. This is 
especially a drawback when splitting one or more B-tree nodes is required to 
accommodate new record for a chunk.

\begin{figure*}
\centering
\input{pics/ea}
\caption{Simplified version of extensible array structure used for indexing chunks.}
\label{fig:ea}
\end{figure*}

For this particular case, indexing chunks requires a more appropriate data
structure, referred to as \textit{extensible array} (EA), and shown in
figure~\ref{fig:ea}. This structure can be seen as a dynamic array structure.
Brodnik et al's paper~\cite{Brodnik1999} addresses this exact problem,
showing how to implement a dynamic array with $O(1)$ append, shrink and lookup
operations, along with optimal metadata overhead for indexing the array elements.
For indexing chunks in HDF5 datasets, the array elements in the data blocks are
pointers to the chunks on disk.
As mentioned in the paper, the resizable array \textit{super blocks} are not actually 
constructs in the data structure, they are just shown to conceptually group the data 
blocks that the index block points to. The super blocks help show the pattern of 
changes to the data blocks: first the size of the data block doubles, then the 
number of data blocks of that size doubles, then the size doubles again, then the 
number of data blocks of that size doubles, etc.

A couple of things should be noted about the data structure in
figure~\ref{fig:ea}:
\begin{enumerate}
\item The super blocks for the first two data blocks are omitted and the pointers
in the index block point directly to the data blocks.
\item Constant time (i.e., $O(1)$) lookup, append and shrink are still in effect.
The number of I/O accesses to find any chunk address is always $2$ or $3$:
index block $\rightarrow$ super block $\rightarrow$ data block. In
actual operation, the index block will certainly be \textit{hot} enough to stay
in the HDF5 metadata cache, along with many/most of the super blocks,
making the average number of I/O accesses to retrieve a chunk address between
$1$ and $2$, in all likelihood.
\item Super blocks/data blocks which are not yet needed are not allocated and
have a \textit{nil} pointer in the index block/super block (respectively) that refers to them.
\item The height of the index block is constant and its height can be computed
at creation so that resizing it is unnecessary. This can be done by computing
the maximum number of chunks possible for the file's address range
(typically 64-bits) and deriving the maximum number of data/index blocks needed
to index that many blocks. For example, if there are $16$ chunks in the initial
data block, a chunk size of $2048$ (with a single unlimited dimension), and a
4-byte (integer) data element size, maximum height of the index block needed to
store $1.84\times 10^{19}$ bytes of elements (which is the maximum offset possible in a
64-bit file) is $47$.
\end{enumerate}

\subsection{Additional Optimization}
When the dataset is extended and its rank is greater than one, the library scans
and updates each entry in the chunk cache, due to the modified dataspace.
Each entry is hashed based on a chunk index, which varies according to the
dataset dimension sizes. When the dimension sizes are modified, the library
re-calculates each entry's chunk index and updates the cache accordingly.
The re-calculation is expensive and the update time increases as the number of
entries is increased in the cache.

Two modifications are made to the chunk layer to improve performance:
\begin{enumerate}
\item Save the component in the chunk index calculation after
initial computation so that it can be later used when updating the chunk cache.
\item Use a different formula to hash chunk entries into the cache that do not depend
on the chunk index. The new formula is based on the $\log_2$ function
for the faster changing dimension sizes, thus reduces the number of chunk cache
updates due to consecutive dataset extension operations.
\end{enumerate}

\subsection{Summary}

With these data structures in place, when the chunked dataset has only one
unlimited maximum dimension, the extensible array indexing method is used,
allowing chunk access in $O(1)$ time. When it has more than one unlimited
maximum dimension sizes, the B-tree version 2 indexing method is used, allowing
chunk access in $O\log_b{n}$, with $b$ the order of the tree and $n$ the
number of nodes.

\section{Evaluation}
\label{sec:evaluation}

To evaluate the performance of these new methods, we first consider the extension
of datasets so that 1-byte chunks are appended, up to $2,500,000$ bytes.
Note that the default storage for chunked datasets is still the default
B-tree indexing (BT1). In order to retain as much forward compatibility as
possible, all the improvements made are only used when the
\texttt{H5F\_LIBVER\_LATEST} value is used as the \textit{high bound} to the
call to \texttt{H5Pset\_libver\_bounds}.

\subsection{Test Scenarios}

We consider multiple scenarios, which are defined in settings 1, 2 and 3.

\paragraph{Setting 1}
creates a 1-dimensional chunked dataset with the following dataspace:

{\lstsetc
\begin{lstlisting}
curr[0] = 0;
max[0] = H5S_UNLIMITED;
sid = H5Screate_simple(1, curr, max);
\end{lstlisting}
}

This compares the BT1 and EA indexing methods, when appending to the dataset
created with the old and new library format respectively.

\paragraph{Setting 2} creates a 2-dimensional chunked dataset with the following
dataspace, which has one unlimited dimension:

{\lstsetc
\begin{lstlisting}
curr[0] = 0;
curr[1] = 1;
max[0] = H5S_UNLIMITED;
max[1] = 1;
sid = H5Screate_simple(2, curr, max);
\end{lstlisting}
}

This compares the BT1 and EA indexing methods when appending to the dataset
created with the old and the new library format respectively.
Append operations are done along the X or Y directions.

\paragraph{Setting 3} creates 2-dimensional chunked datasets with the following
dataspace, which has two unlimited dimensions:

{\lstsetc
\begin{lstlisting}
curr[0] = 0;
curr[1] = 1;
max[0] = H5S_UNLIMITED;
max[1] = H5S_UNLIMITED;
sid = H5Screate_simple(2, curr, max);
\end{lstlisting}
}

This compares the BT1 and BT2 indexing methods when appending to the
datasets created with the old and new library format respectively.
Append operations are done along the X and/or Y directions.

\subsection{Preliminary Results}

First, measures are realized on the library before optimization.
The quantify tool is used to collect the time in seconds spent in the library
code from the test runs. The result listed in table~\ref{tab:result1} indicates
that the EA indexing method performs better than BT1, while the BT2 indexing
method performs worse than BT1. Note also that the library takes a fair amount
of time for all three indexing methods.

\begin{table}
\centering
\caption{Result for all three test settings before optimization.}
\label{tab:result1}
\begin{tabular}{lrr} \toprule
Indexing Method &
Time (\si{\second}) \\
\midrule
\textit{Along the X-direction} \\
EA & $149.82$\tikzmark{t1x1} \\
BT1 & $156.15$\tikzmark{t1x2} \\
BT2 & $166.56$\tikzmark{t1x3} \\
\midrule
\textit{Along the Y-direction} \\
EA & $150.08$\tikzmark{t1y1} \\
BT1 & $163.82$\tikzmark{t1y2} \\
BT2 & $167.91$\tikzmark{t1y3} \\
\midrule
\textit{Along the XY-direction} \\
EA & $-$ \\
BT1 & $104.08$\tikzmark{t1xy1} \\
BT2 & $114.39$\tikzmark{t1xy2} \\
\bottomrule
\end{tabular}
\tablearrowright{t1x2}{t1x1}{$\simeq -4\%$}{}
\tablearrowleft{t1x2}{t1x3}{$\simeq +7\%$}{}
\tablearrowright{t1y2}{t1y1}{$\simeq -8\%$}{}
\tablearrowleft{t1y2}{t1y3}{$\simeq +2\%$}{}
\tablearrowleft{t1xy1}{t1xy2}{$\simeq +10\%$}{}
\end{table}

\subsection{Results}
Measures are realized after optimization.
The new results shown in table~\ref{tab:result2} indicate that after optimization
BT2 performs better than BT1. General chunk index fixes have made a significant
improvement for all three indexing methods---almost $80\%$.

\begin{table}
\centering
\caption{Result for all three test settings after optimization.}
\label{tab:result2}
\begin{tabular}{lr} \toprule
Indexing Method &
Time (\si{\second}) \\
\midrule
\textit{Along the X-direction} \\
EA & $27.54$\tikzmark{x1}\\
BT1 & $34.01$\tikzmark{x2} \\
BT2 & $31.59$\tikzmark{x3} \\
\midrule
\textit{Along the Y-direction} \\
EA & $29.24$\tikzmark{y1} \\
BT1 & $42.97$\tikzmark{y2} \\
BT2 & $33.72$\tikzmark{y3} \\
\midrule
\textit{Along the XY-direction} \\
EA & $-$ \\
BT1 & $35.46$\tikzmark{xy1} \\
BT2 & $32.92$\tikzmark{xy2} \\
\bottomrule
\end{tabular}
\tablearrowright{x2}{x1}{$\simeq -19\%$}{}
\tablearrowleft{x2}{x3}{$\simeq -7\%$}{fill=paperblue!30}
\tablearrowright{y2}{y1}{$\simeq -32\%$}{}
\tablearrowleft{y2}{y3}{$\simeq -22\%$}{fill=paperblue!30}
\tablearrowleft{xy1}{xy2}{$\simeq -7\%$}{fill=paperblue!30}
\end{table}

As one can see in figure~\ref{fig:chunk_perf}, for significant numbers of chunks,
the BT2 and EA indexing methods perform better than BT1. EA shows good scalability
and a much better performance than BT1/BT2 as the number of chunks increases.
BT2 generally shows better performance than BT1 (it is also worth noting than
even if this is not shown in this result, the amount of space taken by BT2
is reduced). Overall these results confirm the optimization made within the
library and were what we expected given the complexity of the methods used.

\begin{figure*}
\centering
\input{plots/chunk_perf}
\caption{Performance of BT2 and EA chunk indexing methods compared to BT1.
The extensible array method shows good scaling performance, while the B-Tree
version 2 shows improved results compared to BT1.}
\label{fig:chunk_perf}
\end{figure*}

\section{Related Work}
\label{sec:related_work}

Nimako et al.~\cite{Nimako2012} consider another data structure for indexing
chunks, the $O_{2}$-Tree, which performs query operations (searches) in
$O(\log_{2}{n})$ time, where $n$ is the number of internal nodes. They
mention that the conventional arrays and HDF5 incur the cost
of reorganizing  already allocated array elements.
Based on these results and the new optimization made, it would be
interesting to make a new comparison. The $O_{2}$-Tree may perform
better than a B-Tree data structure but the re-sizable array data structure
will still perform better in the 1-unlimited dimension case, as its complexity
is in $O(1)$.

[Other related work?]
%Sub array I/O from ADIOS etc / chunking from other libraries
%Tell what was done for chunking in the past etc

\section{Conclusion and Future Work}
\label{sec:conclusion}

[Conclusion / need to talk about it]

\section*{Acknowledgments}
The work presented in this paper was supported by ???

### 2015-02-06 WhitePapers/revise_chunks/pics/btree1.tex
Add first version of revise_chunks paper
Former-commit-id: d6849dd1a790ecd5b509ec77c49d4aaf5482a00e

\begin{tikzpicture}
\tikzstyle{trans} = [gray,->,thick,>=stealth',shorten <=1pt,shorten >=1pt]
\tikzstyle{node_style} = [rectangle split,rectangle split horizontal,
  rectangle split parts=4,rectangle split empty part width=10.5pt,
  text width=15pt,inner sep=0,thick,draw=black,
  minimum height=15pt,text centered,anchor=center,font=\small]
\tikzstyle{edge_style} = [gray,thick,draw]
\tikzstyle{level 1}=[sibling distance=80pt]
\begin{scope} [local bounding box=scope1,%edge from parent fork down,
  every node/.style=node_style, edge from parent/.style=edge_style]
\node {8 \nodepart{two} 16 \nodepart{three} 24 \nodepart{four} 32}
  child {node (l1_0) {0 \nodepart{two} 4}}
  child {node (l1_1) {8 \nodepart{two} 12}}
   child {node (l1_2) {16 \nodepart{two} 20}}
   child {node (l1_3) {24 \nodepart{two} 28}}
   child {node[fill=paperblue!30] (l1_4) {32 \nodepart{two} 36 \nodepart{three} 40 \nodepart{four} 44}};
\end{scope}

\foreach \i in {0,...,4} {
\node[below=15pt of l1_\i.one south] (c\i) {};
\draw[trans] (l1_\i.one south) -- (c\i);
\node[below=15pt of l1_\i.two south] (c\i_2) {};
\draw[trans] (l1_\i.two south) -- (c\i_2);
}
% Last two arrows
\node[below=15pt of l1_4.three south] (c4_3) {};
\draw[trans] (l1_4.three south) -- (c4_3);
\node[below=15pt of l1_4.four south] (c4_4) {};
\draw[trans] (l1_4.four south) -- (c4_4);

\begin{scope}[shift={($(scope1.south)+(0,-40pt)$)},%edge from parent fork down,
  every node/.style=node_style, edge from parent/.style=edge_style]
\tikzstyle{level 1}=[sibling distance=240pt]
\tikzstyle{level 2}=[sibling distance=80pt]
\node {24}
  child {node {8 \nodepart{two} 16}
    child {node (l2_0) {0 \nodepart{two} 4}}
    child {node (l2_1) {8 \nodepart{two} 12}}
    child {node (l2_2) {16 \nodepart{two} 20}}
  }
  child {node[fill=paperblue!30] (l2_split) {32 \nodepart{two} 40}
    child {node (l2_3) {24 \nodepart{two} 28}}
    child {node[fill=paperblue!30] (l2_4) {32 \nodepart{two} 36}}
    child {node[fill=paperblue!30] (l2_5) {40 \nodepart{two} 44 \nodepart{three} 48}}
  };
\end{scope}

\foreach \i in {0,...,5} {
\node[below=15pt of l2_\i.one south] (c\i) {};
\draw[trans] (l2_\i.one south) -- (c\i);
\node[below=15pt of l2_\i.two south] (c\i_2) {};
\draw[trans] (l2_\i.two south) -- (c\i_2);
}
% Last arrow
\node[below=15pt of l2_5.three south] (c5_3) {};
\draw[trans] (l2_5.three south) -- (c5_3);

\draw[overlay,remember picture,ultra thick,line cap=round,->,
  draw=paperblue!50,shorten <=20pt,shorten >=20pt] (l1_4) to [bend left=30]
  node[right=5pt, font=\small\bfseries] {Node Split} 
  (l2_split);
\end{tikzpicture}

### 2015-02-06 WhitePapers/revise_chunks/pics/ea.tex
Add first version of revise_chunks paper
Former-commit-id: d6849dd1a790ecd5b509ec77c49d4aaf5482a00e

\begin{tikzpicture}
\tikzstyle{sblock} = [rectangle split,rectangle split horizontal,
  rectangle split empty part height=6pt,thick,draw=black,
  minimum width=30pt,text centered,font=\small,
  anchor=center]
\tikzstyle{iblock} = [rectangle split,rectangle split parts=9,
  rectangle split empty part height=6pt,thick,draw=black,
  minimum width=30pt,text centered,font=\small,
  anchor=center]
\tikzstyle{link} = [gray,thick,draw]
\tikzstyle{trans} = [gray,->,thick,>=stealth',shorten <=1pt,shorten >=1pt]
\tikzstyle{annotation} = [font=\small]

\node[iblock] (index) {~\nodepart{two}~\nodepart{three}~\nodepart{four}~\nodepart{five}~\nodepart{six}~\nodepart{seven}~\nodepart{eight}~\nodepart{nine}424};
\node[sblock,rectangle split parts=1,right=20pt of index.nine east] (sblock0) {16/16};
\node[sblock,rectangle split parts=1,right=5pt of sblock0] (sblock1) {32/32};
\node[sblock,rectangle split parts=2,right=5pt of sblock1] (sblock2) {32/32 \nodepart{two} 32/32};
\node[sblock,rectangle split parts=2,right=5pt of sblock2] (sblock3) {64/64 \nodepart{two} 64/64};
\node[sblock,rectangle split parts=4,right=5pt of sblock3] (sblock4) {64/64 \nodepart{two} 64/64 \nodepart{three} 56/64 \nodepart{four} nil};
\node[sblock,rectangle split parts=2,right=102pt of index.six east] (sblock2b) {};
\node[sblock,rectangle split parts=2,right=163pt of index.five east] (sblock3b) {};
\node[sblock,rectangle split parts=4,right=240pt of index.four east] (sblock4b) {};

\draw[link] (index.eight east) -| (sblock0);
\draw[link] (index.seven east) -| (sblock1);
\draw[link] (index.six east) -- (sblock2b);
\draw[link] (index.five east) -- (sblock3b);
\draw[link] (index.four east) -- (sblock4b);

\draw[link] (sblock2b.one south) -- (sblock2.one north);
\draw[link] (sblock2b.two south) -- (sblock2.two north);

\draw[link] (sblock3b.one south) -- (sblock3.one north);
\draw[link] (sblock3b.two south) -- (sblock3.two north);

\draw[link] (sblock4b.one south) -- (sblock4.one north);
\draw[link] (sblock4b.two south) -- (sblock4.two north);
\draw[link] (sblock4b.three south) -- (sblock4.three north);
\draw[link] (sblock4b.four south) -- (sblock4.four north);

\node[annotation,right=15pt of index.one east] (nil0) {nil};
\draw[trans] (index.one east) -- (nil0);
\node[annotation,right=15pt of index.two east] (nil1) {nil};
\draw[trans] (index.two east) -- (nil1);
\node[annotation,right=15pt of index.three east] (nil2) {nil};
\draw[trans] (index.three east) -- (nil2);

\draw[decorate,decoration={brace,mirror,raise=2pt}, thick] (index.eight split west) to node [annotation,text width=40pt,left=5pt] {Number of chunks} (index.south west);
\node[annotation,below=2pt of sblock0] {SB$_0$};
\node[annotation,below=2pt of sblock1] {SB$_1$};
\node[annotation,below=2pt of sblock2] {SB$_2$};
\node[annotation,below=2pt of sblock3] {SB$_3$};
\node[annotation,below=2pt of sblock4] {SB$_4$};
\node[annotation,above=2pt of index] {Index block};

% To help center
%\node[above=100pt of sblock2.one split] (help2) {};
%\draw (help2) -- (sblock2.one split);
%\node[above=100pt of sblock3.one split] (help3) {};
%\draw (help3) -- (sblock3.one split);
%\node[above=100pt of sblock4.two split] (help4) {};
%\draw (help4) -- (sblock4.two split);
\end{tikzpicture}

### 2015-02-25 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Edits and typo fixing for analysis RFC
Former-commit-id: caa2a32fc64547689165612fbbb16cc8ecb279e5

@@
 \author{Quincey Koziol}
-\date{November 14, 2014}
-\rfcversion{2014-07-17.v3}
+\date{February 25, 2015}
+\rfcversion{2014-07-17.v4}
 \revision{July 17, 2014}{Version 1 circulated for comment within The HDF Group.}
@@
 \revision{November 14, 2014}{Version 3 circulated for comment within The HDF Group.}
+\revision{February 25, 2015}{Version 4 edits and typo fixing.}
 
@@
 application developer to select, read and write data but does not provide any 
-mechanism
-to select and retrieve pieces without prior knowledge of the content of the data,
-or without the developer to provide the exact data
-coordinates that he is willing to access. To satisfy that need, one must be able
+mechanism to select and retrieve pieces without prior knowledge of their
+content, or without the developer to provide the exact data coordinates that
+he is willing to access. To satisfy that need, one must be able
 to issue queries by specifying a data selection criteria. These queries,
-applied to the data, can then generate a selection, which contains the coordinates
-that satisfy the query. This may thus imply accessing the data and selecting it,
-depending on the query condition satisfaction. Furthermore, this process can be 
-accelerated so that the data no longer needs to be directly accessed, by using 
-indexing  techniques, which consist of generating an index and using that index
+when applied to the data, can then generate a selection, which contains the coordinates
+that satisfy the query---this may imply accessing the data and selecting it,
+depending on the query condition satisfaction. To accelerate and facilitate this
+process (i.e., so that the data no longer needs to be directly accessed), one can
+use indexing techniques, which consist of generating an index and using that index
 to answer the query selection criteria and find the matching elements.
@@
 operations. Support for these operations on HDF5 containers can be defined via:
-\begin{itemize}
-\item New \textit{query} object\footnote{Query and view objects are
+\begin{enumerate}
+\item New \textit{query} objects\footnote{Query and view objects are
 \textit{in-memory} objects, which therefore do not modify the content of the
@@
 query requests for execution on HDF5 containers;
-\item New \textit{view} object\footref{fn:object} and API routines, which apply a query to an HDF5
+\item New \textit{view} objects\footref{fn:object} and API routines, which apply a query to an HDF5
 container and return a set of references into the container that fulfills
 the query criteria;
-\item New \textit{index} object and API routines, which allows the creation of
+\item New \textit{index} objects and API routines, which allows the creation of
 indices on the contents of HDF5 containers, to improve query performance.
-\end{itemize}
+\end{enumerate}
 
@@
 Created query objects can be serialized and deserialized using \texttt{H5Qencode}
-and \texttt{H5Qdecode} routines\footnote{Useful if the query needs to be sent
-through the network}, and their content can be retrieved using the corresponding
-accessor routines.
+and \texttt{H5Qdecode} routines\footnote{Serialization/deserialization of queries
+were introduced so that queries can be sent through the network.}, and their
+content can be retrieved using the corresponding accessor routines.
 \texttt{H5Qcombine} combines two query objects into a
@@
 Applying a query to an HDF5 container creates an HDF5 view object. HDF5 view
-objects are runtime, in-memory objects (i.e., not stored in a container) that
+objects are run-time, in-memory objects (i.e., not stored in a container) that
 consist of read-only references into the contents of the HDF5 container that
 the query was applied to. The current API is presented below:
+\todo{View API must be revised.}
 
@@
 attribute references are not available, this feature will be added in order to
-support views that contain attribute references\footnote{See RFC XXXX for attribute references.}.
+support views that contain attribute references\footnote{See RFC 201X-XX-XX.vX.}.
 
@@
 \section{Index Objects}
-The final and core component of the data analysis extensions to HDF5 is the index object.
 Index objects are designed to accelerate creation of view objects from
@@
 HDF5. Queries with metadata components execute properly,
-\todo{TBD metadata indexing} but are not able to be accelerated
+\todo{Metadata indexing must be added.} but are not able to be accelerated
 with an index currently.
@@
 efficient method will vary depending on the type of the data that is to be
-indexed, its layout, etc. We therefore define a new interface for the HDF5
-library that uses a plugin mechanism.
+indexed, its layout, etc. A new interface for the HDF5 library that uses a
+plugin mechanism is therefore defined.
 
@@
 Index information (such as plugin ID and index metadata) is stored at index
-creation time\footnote{This therefore introduces a file format change},
+creation time\footnote{Adding index information introduces a file format change.},
 and when the user later calls \texttt{H5Dopen}, the plugin open
@@
 execute a query on a particular dataset (accelerated by any index defined on the dataset),
-retrieving the selection that matches the query.
+and retrieve the selection that matches the query.
 
@@
 Because the amount of space taken by the index cannot be directly retrieved by
-the user since the datasets storing the indices are known only by the plugin
-itself, the \texttt{get\_size} callback can query the amount of space that
+the user (since the datasets storing the indices are known only by the plugin
+itself), the \texttt{get\_size} callback can query the amount of space that
 the index takes in the file and users may query that information using the
@@
 Some questions are still open regarding the handling of indices:
-\begin{itemize}
+\begin{enumerate}
 %\item How could an index be built and queried in parallel for a dataset that already exists?
@@
 available? We could fallback to another plugin and do a brute force query on the data.
-\end{itemize}
+\end{enumerate}
 
@@
 dataset may have been created by using a compound datatype, hence defining
-multiple fields composed of native and simple datatypes inside that same dataset.
+multiple fields composed of native and simple datatypes within that same dataset.
 Consequently, creating an index from that dataset requires the user to select a
@@
 \texttt{idx\_info} message (see~\FigureRef{fig:hdf5_index}) so that the index
-for the right field can be retrieved at the time of the query.
+associated to the field can be retrieved at the time of the query.
 When doing a query, the compound type is passed to the \texttt{H5Qcreate} call.
@@
 corresponds to a particular field. This can be achieved by calling \texttt{H5Xget\_info},
-compare the datatype returned inside the info structure, and pass the index number
+compare the datatype returned within the info structure, and pass the index number
 that needs to be removed.
@@
 of the original dataset. In that sense, handling every chunk can be seen as handling
-a dataset from the indexing plugin point of view. if the dataset is chunked,
-at the time of the index creation, we create a B-tree\footnote{Could also
-be a map object.} (physically
+a dataset from the indexing plugin point of view. If the dataset is chunked,
+at the time of the index creation, we create a B-tree\footnote{The B-tree could also
+be replaced by a map object.} (physically
 stored on disk) that maps the coordinates of the chunks to the index plugin metadata.
 When the \texttt{create} callback is called (by representing the chunk as
-a local dataset, i.e. making the dataset layout point to the address of the chunk),
+a local dataset, i.e., making the dataset layout point to the address of the chunk),
 metadata information is returned and stored.
 In the case of contiguous datasets, the index metadata as well as the index plugin ID is
-stored within the dataset header within the index info message (see~\FigureRef{fig:hdf5_index}).
+stored within the dataset header of the index info message (see~\FigureRef{fig:hdf5_index}).
 In the case of chunked datasets, multiple metadata that correspond to each index created
@@
 and their index is used to answer that query. The selection returned is then
-added to a global selection, which is then returned to the user.
+added to a global selection, which is then in turn returned to the user.
 
 Finally, when \texttt{H5Xremove} is called, the \texttt{delete} plugin callback is
-invoked for each chunk using the index metadata information stored in the B-tree.
+invoked for each chunk, by using the index metadata information stored in the B-tree.
 
@@
 freedom as possible to the indexing plugin developer so that in the case when
-the indexing library supports parallel indexing it is still possible to take
-advantage of it. However, three options remain to support parallel indexing
-within the indexing plugin interface:
+the indexing library supports parallel indexing, it is still possible to take
+advantage of it. Three options are available to support parallel indexing
+from the previous interface:
 \begin{enumerate}
-\item is to let the index creation be collective. This however implies synchronization
+\item Let the index creation be collective. This however implies having synchronization
 points, which is the main constraint.
-\item is to let the index creation be independent. However, creating datasets to
+\item Let the index creation be independent. However, creating datasets to
 store the index data must be done collectively\footnote{An option could be to use
 the metadata server VOL plugin but this option is not easily doable yet.}.
-\item is to let make the index creation in two phases. One that consists of
-building the index in parallel independently and gathering the information (index size, etc)
-at the end. And the other that consists of making the dataset creation by a master
+\item Make the index creation in two phases. One that consists of
+building the index in parallel, independently, and gathering the information (index size, etc)
+at the end. The other that consists of letting the dataset creation be done by a master
 process, which can then let the other processes write the index data independently.
 There could however be a memory constraint in this case if the index data has to
-be kept in memory between these two phases (note that building the index twice is not
+be kept in memory between these two phases (though building the index twice is not
 a good solution either).
@@
 list.
-
-Furthermore, in the case of chunked datasets, one may want to operate on several chunks
-at the same time in parallel. This can be done by passing to the callbacks a list of IDs that
-corresponds to each chunk. However this also makes the plugin interface more
-heavy.
+In the case of chunked datasets, one may also want to operate on several chunks
+at the same time, in parallel. This can be done by passing a list of IDs that
+corresponds to each chunk to the callbacks. However, this also makes the plugin
+interface more heavy.
 
@@
 In the following example, we show how one can make use of the query and
-indexing interface to get a dataspace selection within a dataset,
-for simplicity we first create a dataset within the file, then open it to
-create and attach a new index, to finally query data from it.
-Note that some of the calls may be moved to the higher level API, in order to
-directly read data that corresponds to the result of the index query.
+indexing interface to retrieve a dataspace selection within a dataset.
+For simplicity's sake, we first create a dataset within the file, then open it to
+create and attach a new index, in order to finally query data from it.
+Note that for convenience, calls to directly read data that corresponds to the
+result of the index query may be moved to the high-level API in the future.
 
@@
 \section{Conclusion}
+Document in progress.
 

### 2015-03-16 WhitePapers/revise_chunks/paper-body.tex
Minor updates to paper
Former-commit-id: 79ccdcd6271a12b6751ead4c5386947273d72eee

@@
 being extended. Section~\ref{sec:evaluation} presents performance evaluation 
-results.
-In Section~\ref{sec:related_work} we
-first discuss related work before presenting conclusions and 
-future research directions in Section~\ref{sec:conclusion}.
+results. In Section~\ref{sec:related_work} we discuss related work before
+presenting conclusions and future research directions in Section~\ref{sec:conclusion}.
 
@@
 The HDF5 library's default data structure for indexing chunks is based on
-a B-tree data structure, which maps the index
-of the chunk to the file offset where the chunk's elements are stored.
+a B-tree data structure, which maps the index of the chunk to the file offset
+where the chunk's elements are stored.
 
@@
 
-B-trees are generally a good solution that is used for indexing data blocks
+B-trees are generally used for indexing data blocks
 and one of the main components of file systems~\cite{Comer1979}~\cite{Folk1992}. 
@@
 chunk. When a dataset is extended, a new entry is added, which may
-imply a node split if the node where the record needs to be inserted is full. 
+generate a node split if the node where the record needs to be inserted is full. 
 It is worth noting that most chunked datasets are either fixed dimension or
@@
 pointers to the chunks on disk.
-As mentioned in the paper, the resizable array \textit{super blocks} are not actually 
+As mentioned in~\cite{Brodnik1999}, the resizable array \textit{super blocks} are not actually 
 constructs in the data structure, they are just shown to conceptually group the data 
@@
 
-A couple of things should be noted about the data structure in
-figure~\ref{fig:ea}:
+A couple of things should be noted about the data structure in figure~\ref{fig:ea}:
 \begin{enumerate}
@@
 $1$ and $2$, in all likelihood.
-\item Super blocks/data blocks which are not yet needed are not allocated and
-have a \textit{nil} pointer in the index block/super block (respectively) that refers to them.
+\item Super blocks/data blocks, which are not yet needed, are not allocated and
+have a \textit{nil} pointer in the index block/super block (respectively) that
+refers to them.
 \item The height of the index block is constant and its height can be computed
@@
 data block, a chunk size of $2048$ (with a single unlimited dimension), and a
-4-byte (integer) data element size, maximum height of the index block needed to
-store $1.84\times 10^{19}$ bytes of elements (which is the maximum offset possible in a
-64-bit file) is $47$.
+4-byte (integer) data element size, the maximum height of the index block needed to
+store $1.84\times 10^{19}$ bytes of elements (which is the maximum offset
+possible in a 64-bit file) is $47$.
 \end{enumerate}
@@
 maximum dimension sizes, the B-tree version 2 indexing method is used, allowing
-chunk access in $O\log_b{n}$, with $b$ the order of the tree and $n$ the
+chunk access in $O(\log_b{n})$, with $b$ the order of the tree and $n$ the
 number of nodes.

### 2015-05-21 WhitePapers/revise_chunks/paper-body.tex
Update to chunk index paper
Former-commit-id: ed2f5f90b3f897e3ebbb0e30ca4cc24c6fa84a39

@@
 An HDF5 dataset is extendable when the maximum dimension sizes of its 
-dataspace are greater than the current dimension sizes, the maximum dimension 
+dataspace are greater than the current dimension sizes, with the maximum dimension 
 size being specified as \textit{fixed} size or \textit{unlimited} size.
@@
 to achieve that and the locations of chunks for a dataset have originally 
-been stored in a B-tree data structure, which maps the index of the chunk to 
+been stored in a B-tree data structure. This structure maps the index of the chunk to 
 the file offset where the chunk's elements are stored. However, depending
-on the use case and in particular for extendable datasets, the B-tree
-structure used presents some drawbacks, which are addressed in this paper.
+on the use case and in particular for extendable datasets, it presents some
+drawbacks, which are addressed in this paper.
 
@@
 The HDF5 library's default data structure for indexing chunks is based on
-a B-tree data structure, which maps the index of the chunk to the file offset
-where the chunk's elements are stored.
+a B-tree data structure, which maps the coordinate offset of the chunk to the
+file offset where the chunk's elements are stored.
 
@@
 B-trees are generally used for indexing data blocks
-and one of the main components of file systems~\cite{Comer1979}~\cite{Folk1992}. 
+and are one of the main components of file systems~\cite{Comer1979}~\cite{Folk1992}. 
 Insertion of a new entry and lookup is realized in $O(\log_b{n})$, where $n$ is the
@@
 In the case of HDF5 datasets and in the original B-tree structure, referred to
-as \textit{B-Tree version 1} (BT1), the record for locating the chunk stores the
+as \textit{B-Tree version 1} (BT1), the record for locating a chunk stores the
 following information:
@@
 It is worth noting that most chunked datasets are either fixed dimension or
-extend in only one dimension. Very few users take advantage of the ability to 
+extend in only one dimension---very few users take advantage of the ability to 
 extend multiple dimensions of a dataset.
+
 Because HDF5 datasets only allow their dimensions to be increased or 
@@
 dataset will only ever insert or remove records from its right-most node.
-One of the problems is that inserting/removing only from the right-most
-node lets most records half empty, as illustrated in 
-figure~\ref{fig:btree1}.
-
+One of the problems this causes is that inserting/removing only from the right-most
+node lets most records half empty, as illustrated in figure~\ref{fig:btree1}.
 To fix that issue, one of the main improvements made with a new version of
@@
 re-balance the entries so that nodes that were half-empty in version 1 are
-now full. Additionally, to improve traversal of the tree and easily find the
-chunks, the B-tree is counted so that alongside every link to a subtree, the
-number of subtree elements is stored.
-
-Some additional modifications are made to the BT2 to improve performance:
+now full.
+%Additionally, to improve traversal of the tree and easily find the
+%chunks, the B-tree is counted so that alongside every link to a subtree, the
+%number of subtree elements is stored.
+Some additional modifications have also been made to the BT2 to improve performance:
 \begin{enumerate}
@@
 To accelerate the search, the maximum and minimum records in the tree are 
-determined and stored in the B-tree header. The library can then quickly 
+determined and stored in memory. The library can then quickly 
 determine that the new record to be inserted is not in the tree if it is 
@@
 \item
-The default B-tree node size is $512$, which leads to a greater tree depth
+The default BT2 node size is $512$, which leads to a greater tree depth
 than version 1 for the append test scenario. This contributes to a lower
@@
 \subsection{Extensible Arrays}
-
-While the version 2 of the B-tree previously mentioned provides a better
+While the version 2 B-tree previously mentioned provides a better
 balancing of the records in the tree, using it in the 1-D case (or for
@@
 structure, referred to as \textit{extensible array} (EA), and shown in
-figure~\ref{fig:ea}. This structure can be seen as a dynamic array structure.
-Brodnik et al's paper~\cite{Brodnik1999} addresses this exact problem,
-showing how to implement a dynamic array with $O(1)$ append, shrink and lookup
+figure~\ref{fig:ea}. This structure can be seen as a dynamic array structure,
+which can contain new elements, as needed---insertion, removal and lookup of
+elements are realized in constant time.
+Brodnik et al's paper~\cite{Brodnik1999} shows how to implement a similar
+structure with $O(1)$ append, shrink and lookup
 operations, along with optimal metadata overhead for indexing the array elements.
-For indexing chunks in HDF5 datasets, the array elements in the data blocks are
-pointers to the chunks on disk.
-As mentioned in~\cite{Brodnik1999}, the resizable array \textit{super blocks} are not actually 
-constructs in the data structure, they are just shown to conceptually group the data 
-blocks that the index block points to. The super blocks help show the pattern of 
+In our case and for indexing chunks in HDF5 datasets, the array elements in the
+data blocks are pointers to the chunks on disk.
+To conceptually group the data blocks that the index block points to,
+the extensible array defines \textit{super blocks}.
+Super blocks are not actually constructs in the data structure, but
+as mentioned in~\cite{Brodnik1999}, help to show the pattern of
 changes to the data blocks: first the size of the data block doubles, then the 
@@
 
-A couple of things should be noted about the data structure in figure~\ref{fig:ea}:
+A couple of things should be noted about this data structure (described in
+figure~\ref{fig:ea}):
 \begin{enumerate}
@@
 store $1.84\times 10^{19}$ bytes of elements (which is the maximum offset
-possible in a 64-bit file) is $47$.
+possible in a 64-bit file) is $46$:
+\begin{align*}
+16\times \sum_{i=0}^{n} 2^{i} = \frac{2^{64}}{2048 \times 4}\\
+16\times (2^{n+1}-1) = \frac{2^{64}}{2048 \times 4}\\
+2^{n+1} = \frac{2^{64}}{2048 \times 4 \times 16} + 1\\
+2^{n+1} = 2^{47} + 1\\
+\lceil n \rceil = 46
+\end{align*}
 \end{enumerate}
 
-\subsection{Additional Optimization}
-When the dataset is extended and its rank is greater than one, the library scans
+%Look at H5D_chunk_hashval / H5D_set_extent
+\subsection{Hash Table}
+In the case where chunks are present in cache (i.e., in memory),
+chunks are retrieved from the cache hash table. When a dataset's dimensions are
+extended and the dataset's rank is greater than one, the HDF5 library scans
 and updates each entry in the chunk cache, due to the modified dataspace.
-Each entry is hashed based on a chunk index, which varies according to the
-dataset dimension sizes. When the dimension sizes are modified, the library
-re-calculates each entry's chunk index and updates the cache accordingly.
-The re-calculation is expensive and the update time increases as the number of
-entries is increased in the cache.
+In the original implementation, each entry is hashed based on the chunk index,
+which varies according to the dataset dimension sizes. When the dimension sizes
+are modified, the library re-calculates each entry's chunk index and updates
+the cache accordingly. This is an expensive operation since the update time
+increases as the number of entries is increased in the cache.
 
-Two modifications are made to the chunk layer to improve performance:
+To improve performance of chunk retrieval from the cache, two
+modifications are made to the chunk layer:
 \begin{enumerate}
-\item Save the component in the chunk index calculation after
+\item The fastest changing dimension in the chunk index calculation is saved after
 initial computation so that it can be later used when updating the chunk cache.
-\item Use a different formula to hash chunk entries into the cache that do not depend
-on the chunk index. The new formula is based on the $\log_2$ function
-for the faster changing dimension sizes, thus reduces the number of chunk cache
-updates due to consecutive dataset extension operations.
+\item A different formula to hash chunk entries into the cache is used so that
+it no longer depends on the chunk index. The new formula is based on the
+$\log_2$ function, which reduces the number of chunk cache
+updates due to consecutive dataset extension operations. As shown
+in figure~\ref{fig:scaled}, using scaled coordinates (i.e., relative to the
+dimension sizes), the $\log_2$ function is used to compute
+a binary representation of the coordinates. The number of bits that are necessary
+to encode the coordinates only increases when the new dimension's size crosses
+a power of 2 boundary.
 \end{enumerate}
+
+\begin{figure*}
+\centering
+\input{pics/scaled}
+\caption{Example of hash-value computation that is used to retrieve chunks using
+ scaled coordinates in a 3-dimensional dataset.}
+\label{fig:scaled}
+\end{figure*}
 
@@
 
-With these data structures in place, when the chunked dataset has only one
-unlimited maximum dimension, the extensible array indexing method is used,
+With these data structures in place, when the chunked dataset is on disk and
+has only one unlimited maximum dimension, the extensible array indexing method is used,
 allowing chunk access in $O(1)$ time. When it has more than one unlimited
@@
 chunk access in $O(\log_b{n})$, with $b$ the order of the tree and $n$ the
-number of nodes.
+number of nodes. When it is in cache, the chunk is accessed through the cache
+hash table and the computed hash value .
 
@@
 \texttt{H5F\_LIBVER\_LATEST} value is used as the \textit{high bound} to the
-call to \texttt{H5Pset\_libver\_bounds}.
+call to \texttt{H5Pset\_libver\_bounds}, which can be set by an application
+when the file is opened.
 
@@
 
-[Other related work?]
+%[Other related work?]
 %Sub array I/O from ADIOS etc / chunking from other libraries
@@
 
-[Conclusion / need to talk about it]
-
-\section*{Acknowledgments}
-The work presented in this paper was supported by ???
+%\section*{Acknowledgments}
+%The work presented in this paper was supported by ???

### 2015-05-21 WhitePapers/revise_chunks/pics/ea.tex
Update to chunk index paper
Former-commit-id: ed2f5f90b3f897e3ebbb0e30ca4cc24c6fa84a39

@@
 
-\draw[decorate,decoration={brace,mirror,raise=2pt}, thick] (index.eight split west) to node [annotation,text width=40pt,left=5pt] {Number of chunks} (index.south west);
-\node[annotation,below=2pt of sblock0] {SB$_0$};
-\node[annotation,below=2pt of sblock1] {SB$_1$};
-\node[annotation,below=2pt of sblock2] {SB$_2$};
-\node[annotation,below=2pt of sblock3] {SB$_3$};
-\node[annotation,below=2pt of sblock4] {SB$_4$};
-\node[annotation,above=2pt of index] {Index block};
+\draw[decorate,decoration={brace,mirror,raise=2pt}, thick] (index.eight split west) to node [annotation,text width=40pt,left=5pt,font=\small\bfseries] {Number of chunks} (index.south west);
+\node[annotation,below=2pt of sblock0] {DB$_0$};
+\node[annotation,below=2pt of sblock1] {DB$_1$};
+\node[annotation,below=2pt of sblock2] {DB$_2$};
+\node[annotation,below=2pt of sblock3] {DB$_3$};
+\node[annotation,below=2pt of sblock4] (sblock4_annotation) {DB$_4$};
+\node[annotation,above=2pt of index,font=\small\bfseries] {Index block};
+\node[annotation,right=12pt of sblock4_annotation,font=\small\bfseries] {Data blocks};
+\node[annotation,right=4pt of sblock4b,font=\small\bfseries] {Super blocks};
 

### 2015-05-21 WhitePapers/revise_chunks/pics/scaled.tex
Update to chunk index paper
Former-commit-id: ed2f5f90b3f897e3ebbb0e30ca4cc24c6fa84a39

\tikzstyle{trans} = [>=stealth, thick, text centered, font=\small]
\tikzstyle{computBox} = [draw=black, thick, inner sep=4pt, inner ysep=4pt,
  rectangle, rounded corners]

\newcommand{\drawcuboid}[5]{% width, height, depth, scale, color
\begin{scope}[scale=#4]
\coordinate (O) at (0,0,0);
\coordinate (A) at (0,#2,0);
\coordinate (B) at (0,#2,#3);
\coordinate (C) at (0,0,#3);
\coordinate (D) at (#1,0,0);
\coordinate (E) at (#1,#2,0);
\coordinate (F) at (#1,#2,#3);
\coordinate (G) at (#1,0,#3);

\draw[fill=#5] (O) -- (C) -- (G) -- (D) -- cycle;% Bottom Face
\draw[fill=#5] (O) -- (A) -- (E) -- (D) -- cycle;% Back Face
\draw[fill=#5] (O) -- (A) -- (B) -- (C) -- cycle;% Left Face
\draw[fill=#5] (D) -- (E) -- (F) -- (G) -- cycle;% Right Face
\draw[fill=#5] (C) -- (B) -- (F) -- (G) -- cycle;% Front Face
\draw[fill=#5] (A) -- (B) -- (F) -- (E) -- cycle;% Top Face

\draw[dashed] (O) -- (D);
\draw[dashed] (O) -- (C);
\draw[dashed] (O) -- (A);

\coordinate[left=6pt of A] (A1);
\coordinate[left=6pt of B] (B1);
\coordinate[left=6pt of C] (C1);
\coordinate[below=4pt of C] (C2);
\coordinate[below=4pt of G] (G1);
\draw[<->,trans] (C2) -- node [below] {#1} (G1);
\draw[<->,trans] (C1) -- node [left] {#2} (B1);
\draw[<->,trans] (A1) -- node [above left] {#3} (B1);

\end{scope}
}

%\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\begin{tikzpicture}

\node (cubes) {
\begin{minipage}{0.32\textwidth}
\begin{tikzpicture}
% Origin axes
\draw[->,draw=paperblue,thick] (0,0,0) -- (3.2,0,0);
\draw[->,draw=paperblue,thick] (0,0,0) -- (0,3.8,0);
\draw[->,draw=paperblue,thick] (0,0,0) -- (0,0,4);
\node[font=\itshape] at (3.4,0,0) {x};
\node[font=\itshape] at (0,4,0) {y};
\node[font=\itshape] at (0,0,4.2) {z};

% Cubes
\drawcuboid{60}{75}{75}{0.04}{white}
\drawcuboid{10}{25}{25}{0.04}{paperblue!20}
\end{tikzpicture}
\end{minipage}
};

% Hash value computation
\node [computBox, font=\footnotesize, text width=100pt, right=50pt of cubes] (scaled) {
  \begin{minipage}{\textwidth}
  {
\textbf{Scaled coordinates:}\\
\begin{math}
   X/x = 60/10 = 6\\
   Y/y = 75/25 = 3\\
   Z/z = 75/25 = 3
\end{math}

\smallskip
\textbf{Number of bits to represent\\ coordinates:}\\
\begin{math}
   \lceil \log_2(X/x) \rceil = 3\\
   \lceil \log_2(Y/y) \rceil = 2\\
   \lceil \log_2(Z/z) \rceil = 2
\end{math}
  }
  \end{minipage}
};

\node [right=of scaled,rectangle split,rectangle split horizontal,
  rectangle split parts=2,draw, minimum height=15pt,text centered,anchor=center,font=\small] (zhash) {0 \nodepart{two} 0};
\node [right=14pt of zhash,rectangle split,rectangle split horizontal,
  rectangle split parts=2,draw, minimum height=15pt,text centered,anchor=center,font=\small] (yhash) {0 \nodepart{two} 0};
\node [right=20pt of yhash,rectangle split,rectangle split horizontal,
  rectangle split parts=3,draw, minimum height=15pt,text centered,anchor=center,font=\small] (xhash) {0 \nodepart{two} 0 \nodepart{three} 0};
\node [below=2pt of xhash] {$x$};
\node [below=2pt of yhash] {$y$};
\node [below=2pt of zhash] {$z$};

\draw[very thick, ->] (cubes) -- node[above, text width=4cm, align=center, font=\bfseries]
    {Hash-value} ($ (scaled.west) - (0.5,0) $);

\end{tikzpicture}

### 2015-06-11 RFCs/HDF5_Library/New_Datatypes/new_datatypes.tex
Add RFC for new C99 datatypes
Former-commit-id: 4b0572f26160f8a740ea321c82b9a3cba7b334fb

\documentclass[letterpaper,hyper]{THG_RFC}

% Fonts
\usepackage{ifluatex}
\ifluatex
  % Font
  \usepackage{luatextra, xunicode, unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont[
    UprightFont={*},
    BoldFont={*-Bold},
    ItalicFont={*-Italic},
    BoldItalicFont={*-BoldItalic},
    SlantedFont={*-Italic},
    BoldSlantedFont={*-BoldItalic}
  ]{CMU Serif}
  \setsansfont[
    UprightFont={*},
    BoldFont={*-Bold},
    ItalicFont={*-Oblique},
    BoldItalicFont={*-BoldOblique}
  ]{CMU Sans Serif}
  \setmathfont[math-style=ISO, bold-style=ISO]{Asana Math}
  \setmonofont[
    UprightFont={*-Regular},
    BoldFont={*-Bold},
    ItalicFont={*-Italic},
    BoldItalicFont={*-BoldItalic}
  ]{CMU Typewriter}
\else
  \usepackage{times} % times / lmodern / mathpazo / palatino
  \usepackage[scaled=.95]{helvet}
  \usepackage{courier}
\fi

% Path to figures, plots
\graphicspath{{./pics/}{./plots/}}

%% TikZ
\usepackage{tikz}
\usetikzlibrary{patterns, shapes, decorations.pathreplacing}
\usepackage{gnuplot-lua-tikz}

% SI units
%\usepackage{textcomp}
\usepackage[binary-units]{siunitx}
\sisetup{per-mode = symbol}
\providecommand{\gbps}[1]{\SI{#1}{\giga\byte\per\second}}
\providecommand{\mbps}[1]{\SI{#1}{\mega\byte\per\second}}
\providecommand{\gb}[1]{\SI{#1}{\giga\byte}}
\providecommand{\mb}[1]{\SI{#1}{\mega\byte}}
\providecommand{\kb}[1]{\SI{#1}{\kilo\byte}}

% Code snippets
\usepackage{listings}
\def\lstsetc{\lstset{language=C,
  numbers=left,
  xleftmargin=20pt,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  showspaces=false, 
  showstringspaces=false,
  breaklines=true,
  basicstyle=\small\ttfamily,
  stringstyle=\itshape,
  commentstyle=\itshape\bfseries,
  morekeywords={main, size_t, malloc, free,
    hsize_t, hid_t, herr_t,
    H5Fcreate, H5Fclose,
    H5Dcreate, H5Dopen, H5Dclose, H5Dwrite, H5Dread,
    H5Screate_simple, H5Sclose, H5Sget_select_npoints
    }
  }
}

% Title, author, etc
\title{New Datatypes}
\author{Jerome Soumagne}
\author{Quincey Koziol / Elena Pourmal}
\date{June 11, 2015}
\rfcversion{2015-04-29.v3}
\revision{April 29, 2015}{Version 1 circulated for comment within The HDF Group.}
\revision{June 10, 2015}{Version 2 circulated for comment within The HDF Group.}
\revision{June 11, 2015}{Version 3 circulated for comment within The HDF Group.}

%% Start the document
\begin{document}

%% Add Attribute reference RFC

%% Title
\maketitle

%% Abstract
\begin{abstract}
The C99 standard introduced support for boolean and complex types.
Boolean and complex types are also supported in C++, Fortran, Java, Python.
This RFC describes how support for these types can be added within the HDF5 library.
\end{abstract}

\section{Introduction}
The HDF5 library defines already datatypes for all common types, i.e., char,
short, int, long, etc, as well as their specific encoded variation, for instance
all standard types, as well as little/big endian encoding, etc.
However, new datatypes were requested by HDF5 users (ESDIS, LLNL, etc) who
work with scientific applications to support both \textit{boolean} and
\textit{complex} types. Boolean types should be seen as a distinct conceptual
type, not as another integer type. An important
aspect of having a boolean datatype, despite the convenient mapping that it can
provide between C/C++ codes that use boolean concepts, is to no longer require
the use of integers for storing boolean data and therefore reduce storage needs. 
Regarding complex types, they are already natively defined by the C standard,
therefore not only for convenience but also for performance reasons would it
makes sense for the HDF5 library to provide a native datatype so that users
are no longer forced to either use separate datasets or create a
compound type (which would in this case be composed of real/imaginary fields)
in order to store and retrieve data. As these types were introduced by the
C99 standard, this set of datatypes can be defined as new HDF5 native types.

\section{New Datatypes}

The following types are considered: \texttt{\_Bool}, \texttt{float \_Complex},
\texttt{double \_Complex}, \texttt{long double \_Complex}.
Next sections are a reminder of the rules that the C standard~\cite{c11} defines
for these types.

\subsection{\texttt{\_Bool}}

An object declared as type \texttt{\_Bool} is large enough to store the
values 0 and 1.
While the number of bits in a \texttt{\_Bool} object is at least
\texttt{CHAR\_BIT}, the width (number of sign and value bits) of a
\texttt{\_Bool} may be just 1 bit.

\paragraph{Conversion rules:}
When any scalar value is converted to \texttt{\_Bool}, the result is 0 if the
value compares equal to 0; otherwise, the result is 1.

\subsection{\texttt{\_Complex}}

An object declared as type complex is composed of two parts: real and imaginary,
the real part is always before the imaginary part.
Values of complex types are equal if and only if both their real parts are equal
and also their imaginary parts are equal.
The integer constant 1, \texttt{\_\_STDC\_IEC\_559\_COMPLEX\_\_}, intended to
indicate adherence to the IEC 60559 compatible complex arithmetic specifications.
The integer constant 1, \texttt{\_\_STDC\_NO\_COMPLEX\_\_}, intended to indicate
that the implementation does not support complex types or the \texttt{<complex.h>}
header.

{\lstsetc
\begin{lstlisting}
#include<stdio.h>
#include<complex.h>

union Example
{
  float f[2];
  float complex c;
};

int main()
{
  union Example example;
  example.c = 1.0f + 0.0f*I;
  printf("First element of float: %.4f\n", example.f[0]);
  printf("Second element of float: %.4f\n", example.f[1]);
  printf("Real part of complex: %.4f\n", __real__(example.c));
  printf("Imaginary part of complex: %.4fi\n", __imag__(example.c));
  return 0;
}
\end{lstlisting}
}

As mentioned in~\cite{ibm2014}, on both big endian and little endian, the first
element of f is 1.0000 and the second element of f is 0.0000. The real part of
the complex number c is 1.0000 and the imaginary part is 0.0000i.
\begin{verbatim}
First element of float: 1.0000
Second element of float: 0.0000
Real part of complex: 1.0000
Imaginary part of complex: 0.0000i
\end{verbatim}
The byte order of the elements of a floating-point and a complex number is
different between big endian and little endian, but the element order is the
same.

\paragraph{Conversion rules:}
\begin{table}[ht]\footnotesize
\caption{Conversion to/from \texttt{\_Complex} (\texttt{a+b*i}).}
\label{tab:complex_convert}
\begin{tabular}{lccc} \toprule
Types     & Complex                    & Real             & Imaginary          \\
\midrule
Complex   & \texttt{conv(a)+conv(b)*i} & \texttt{conv(a)} & \texttt{conv(b)*i} \\
Real      & \texttt{conv(a)+0*i}       & -                & \texttt{0*i}       \\
Imaginary & \texttt{0+conv(b)*i}       & \texttt{0}       & -                  \\
\bottomrule
\end{tabular}
\end{table}
As summarized in~\TableRef{tab:complex_convert},
when a value of complex type is converted to another complex type, both the real
and imaginary parts follow the conversion rules for the corresponding real types.
When a value of real type is converted to a complex type, the real part of the
complex result value is determined by the rules of conversion to the
corresponding real type and the imaginary part of the complex result value is a
positive zero or an unsigned zero.
When a value of complex type is converted to a real type, the imaginary part of
the complex value is discarded and the value of the real part is converted
according to the conversion rules for the corresponding real type.
When a value of imaginary type is converted to a real type other than
\texttt{\_Bool}, the result is a positive zero.
When a value of real type is converted to an imaginary type, the result is a
positive imaginary zero.
When a value of imaginary type is converted to a complex type, the real part of
the complex result value is a positive zero and the imaginary part of the
complex result value is determined by the conversion rules for the
corresponding real types.
When a value of complex type is converted to an imaginary type, the real part
of the complex value is discarded and the value of the imaginary part is
converted according to the conversion rules for the corresponding real types.

\section{HDF5 Implementation}

Implementing these new types requires modifications of multiple HDF5 components:
the core library, the high-level library, the Fortran library, the C++ library,
the tools. This implies modification of the corresponding tests that support
these components, as well as of the file format.

\subsection{Core Library Support}
As already described in~\cite{lu2012}, implementation within the HDF5 library
of a new datatype requires the following changes:
\begin{enumerate}
\item Detect the size of the new type in configure/CMake along with other native datatypes. After the configuration, a new macro called \texttt{H5\_SIZEOF\_XXX}
is defined as in \texttt{H5pubconf.h} in the src/ directory under the build
directory. If the compiler does not support this datatype, the value of
\texttt{H5\_SIZEOF\_XXX} would be 0.
\item Add the new type for detection in \texttt{src/H5detect.c}. After compiling
\texttt{H5detect.c} and running \texttt{H5detect}, the properties of the type is
generated in \texttt{H5Tinit.c}. 
\item Declare the variables related to the new type in the top of \texttt{H5T.c}.
\item Release the variable in \texttt{H5T\_term\_interface} of \texttt{H5T.c}.
\item Make the datatype ID public by defining a macro in \texttt{H5Tpublic.h}.
\item Declare the variables for alignments in \texttt{H5Tpkg.h}.
\item Add a printout for the new type in \texttt{H5\_trace} of \texttt{H5trace.c}
along with other types.
\item Add the prototypes of hard conversion functions for this new datatype in
\texttt{H5Tpkg.h}. There should be functions between the new datatype and all
other native integer types and all native floating-point number types.
\item Add the definitions of the hard conversion functions for this new datatype
in \texttt{H5Tconv.c}.
\item Add test cases for the new type in the test suite, especially the data
conversion test \texttt{dt\_arith.c}.
\end{enumerate}

\subsubsection{Boolean Type}
\texttt{H5T\_NATIVE\_BOOL} will be detected and its
size\footnote{By default, when compiling with GCC, \texttt{sizeof(bool)}
is 4 when compiling for Darwin/PowerPC and 1 when compiling for Darwin/x86.}
defined accordingly.
Adding support for the type within the core library should be straightforward.
Conversion routines will follow rules already defined by the C standard.

%\begin{table}[ht]\footnotesize
%\caption{Conversion to/from \texttt{H5T\_NATIVE\_BOOL}.}
%\label{tab:bool_convert}
%\begin{tabular}{lccccccccc} \toprule
%Types & \texttt{\_Bool} &
%\texttt{char} & \texttt{short} & \texttt{int} & \texttt{long} & \texttt{llong}
%& \texttt{float} & \texttt{double} & \texttt{ldouble}\\
%\midrule
%\texttt{\_Bool}  & $2^1 - 1$ & $2^1 - 1$ & $2^1 - 1$ & $2^1 - 1$ & $2^1 - 1$ & $2^1 - 1$ & $2^1 - 1$ & $2^1 - 1$ & $2^1 - 1$ \\
%\texttt{char}    & X & X & X & X & X & X & X & X & X \\
%\texttt{short}   & X & X & X & X & X & X & X & X & X \\
%\texttt{int}     & X & X & X & X & X & X & X & X & X \\
%\texttt{long}    & X & X & X & X & X & X & X & X & X \\
%\texttt{llong}   & X & X & X & X & X & X & X & X & X \\
%\texttt{float}   & X & X & X & X & X & X & X & X & X \\
%\texttt{double}  & X & X & X & X & X & X & X & X & X \\
%\texttt{ldouble} & X & X & X & X & X & X & X & X & X \\
%\bottomrule
%\end{tabular}
%end{table}

\paragraph{HDF5 boolean type:} It is also worth noting that HDF5 used to define
a boolean type, referred to as \texttt{hbool\_t}. This boolean type is
currently defined as an integer, therefore for consistency it will now be
defined as \texttt{\_Bool} when possible.

\subsubsection{Complex Types}
\texttt{H5T\_NATIVE\_FLOAT\_COMPLEX}, \texttt{H5T\_NATIVE\_DOUBLE\_COMPLEX},
and \texttt{H5T\_NATIVE\_LDOUBLE\_COMPLEX} will be detected and their size
defined accordingly.
Adding support for this type may require some more work as one may need to
access real and imaginary parts within the functions that are already defined.
Conversion routines will follow rules already defined by the C standard.

\subsection{High-level Support}
The \texttt{H5LT} API makes minimal use of datatypes and support for these
additional datatypes will be added (straightforward).
High-level read or write make use of datatypes, they will need to be tested
using these new types.

\subsection{Fortran Support}
ISO C bindings are used to provide us with a standard mechanism to pass data
between Fortran and C. Fortran \texttt{LOGICAL} can be mapped to the C
\texttt{\_Bool} type by using a special integer kind (\texttt{C\_BOOL}).

\paragraph{Note.}
We will leave Fortran HL out for now.

\subsection{C++ Support}
C++ supports \texttt{bool} types, as well as complex numbers, which are available
through the standard library.

\subsection{Python Support}
Python supports boolean values \texttt{True} and \texttt{False}, as well as
complex types. Therefore these new datatypes make perfect sense for Python
users.

\subsection{Java Support}
Java provides boolean types. Complex numbers are defined through classes.

\subsection{Tools Support}
The following list of tools must be adapted: \texttt{h5dump}, \texttt{h5ls},
\texttt{h5diff}, \texttt{h5import}, \texttt{h5repack}, \texttt{h5debug}.

\section{Additional Questions}

\section*{Revision History}
\makerevisions

%% References
\bibliographystyle{ieeetr}
\bibliography{new_datatypes}

\end{document}

### 2015-06-11 WhitePapers/revise_chunks/paper-body.tex
Update chunk index paper results
Former-commit-id: 56f2835ea9cecbc020dd71e179bab084f45883b2

@@
 number of nodes. When it is in cache, the chunk is accessed through the cache
-hash table and the computed hash value .
+hash table and the computed hash value.
 
@@
 \textit{Along the X-direction} \\
-EA & $27.54$\tikzmark{x1}\\
-BT1 & $34.01$\tikzmark{x2} \\
-BT2 & $31.59$\tikzmark{x3} \\
+EA & $32.10$\tikzmark{x1}\\
+BT1 & $36.63$\tikzmark{x2} \\
+BT2 & $35.39$\tikzmark{x3} \\
 \midrule
 \textit{Along the Y-direction} \\
-EA & $29.24$\tikzmark{y1} \\
-BT1 & $42.97$\tikzmark{y2} \\
-BT2 & $33.72$\tikzmark{y3} \\
+EA & $32.2$\tikzmark{y1} \\
+BT1 & $39.01$\tikzmark{y2} \\
+BT2 & $34.90$\tikzmark{y3} \\
 \midrule
@@
 EA & $-$ \\
-BT1 & $35.46$\tikzmark{xy1} \\
-BT2 & $32.92$\tikzmark{xy2} \\
+BT1 & $36.11$\tikzmark{xy1} \\
+BT2 & $35.29$\tikzmark{xy2} \\
 \bottomrule
 \end{tabular}
-\tablearrowright{x2}{x1}{$\simeq -19\%$}{}
-\tablearrowleft{x2}{x3}{$\simeq -7\%$}{fill=paperblue!30}
-\tablearrowright{y2}{y1}{$\simeq -32\%$}{}
-\tablearrowleft{y2}{y3}{$\simeq -22\%$}{fill=paperblue!30}
-\tablearrowleft{xy1}{xy2}{$\simeq -7\%$}{fill=paperblue!30}
+\tablearrowright{x2}{x1}{$\simeq -12.4\%$}{}
+\tablearrowleft{x2}{x3}{$\simeq -3.4\%$}{fill=paperblue!30}
+\tablearrowright{y2}{y1}{$\simeq -17.5\%$}{}
+\tablearrowleft{y2}{y3}{$\simeq -10.5\%$}{fill=paperblue!30}
+\tablearrowleft{xy1}{xy2}{$\simeq -2.3\%$}{fill=paperblue!30}
 \end{table}

### 2015-07-20 WhitePapers/revise_chunks/paper-body.tex
Update chunking paper and add seminar slides
Former-commit-id: 0ec8d6529f464ab26accd5af9aef22dc2369e35b

@@
 management---users may define and organize data into different groups and
-datasets and build an hierarchical tree of data. Datasets may be contiguously 
+datasets and build a hierarchical tree of data. Datasets may be contiguously 
 mapped from the application memory to a file, or stored in more complex 
-patterns to ease further access and analysis of the data. One option that
-is commonly used is to create and define a dataset as \textit{extendable},
-in order to easily append new values to it.
+patterns to ease further access and analysis of the data. One
+commonly used option is to define and create a dataset as \textit{extendable},
+which allows new values to be appended to it.
 An HDF5 dataset is extendable when the maximum dimension sizes of its 
 dataspace are greater than the current dimension sizes, with the maximum dimension 
-size being specified as \textit{fixed} size or \textit{unlimited} size.
+size being specified as either \textit{fixed} size or \textit{unlimited} size.
 
@@
 datasets that are stored in chunked form, the chunk containing those
-elements must be located and accessed. Several structures can be used
-to achieve that and the locations of chunks for a dataset have originally 
-been stored in a B-tree data structure. This structure maps the index of the chunk to 
+elements must be located and accessed. Several data structures can be used
+to achieve that and the locations of chunks for a dataset are currently 
+stored in a B-tree data structure. This structure maps the index of the chunk to 
 the file offset where the chunk's elements are stored. However, depending
@@
 to optimize I/O to disk~\cite{Howison2010}, to compress data~\cite{Folk2011},
-to extend datasets.
+and to efficiently extend datasets.
 To retrieve elements in the datasets that are stored in chunked form, the
@@
 B-trees are generally used for indexing data blocks
-and are one of the main components of file systems~\cite{Comer1979}~\cite{Folk1992}. 
+and are one of the main components of many file systems~\cite{Comer1979}\cite{Folk1992}. 
 Insertion of a new entry and lookup is realized in $O(\log_b{n})$, where $n$ is the
@@
 B-tree. To determine that the record to be inserted is not in the tree,
-the library traverses the corresponding tree nodes and compares the records 
+a naive implementation traverses the corresponding tree nodes and compares the records 
 in each node before the insertion.
-To accelerate the search, the maximum and minimum records in the tree are 
+To accelerate the search, because entries are frequently added at the upper bound,
+the maximum and minimum records in the tree are 
 determined and stored in memory. The library can then quickly 
@@
 the extensible array defines \textit{super blocks}.
-Super blocks are not actually constructs in the data structure, but
+Super blocks can be seen as \textit{indirect blocks} in the data structure and,
 as mentioned in~\cite{Brodnik1999}, help to show the pattern of
@@
 curr[1] = 1;
-max[0] = H5S_UNLIMITED;
-max[1] = 1;
+max[0] = H5S_UNLIMITED; /* or 1 if append
+                         * in Y direction */
+max[1] = 1; /* or H5S_UNLIMITED if append
+             * in Y direction */
 sid = H5Screate_simple(2, curr, max);
@@
 First, measures are realized on the library before optimization.
-The quantify tool is used to collect the time in seconds spent in the library
-code from the test runs. The result listed in table~\ref{tab:result1} indicates
+The result listed in table~\ref{tab:result1} indicates
 that the EA indexing method performs better than BT1, while the BT2 indexing
@@
 and a much better performance than BT1/BT2 as the number of chunks increases.
-BT2 generally shows better performance than BT1 (it is also worth noting than
+BT2 generally shows better performance than BT1 (it is also worth noting that
 even if this is not shown in this result, the amount of space taken by BT2
@@
 chunks, the $O_{2}$-Tree, which performs query operations (searches) in
-$O(\log_{2}{n})$ time, where $n$ is the number of internal nodes. They
+$O(\log_{2}{n})$ time, where $n$ is the number of internal nodes. They also
 mention that the conventional arrays and HDF5 incur the cost
@@
 better than a B-Tree data structure but the re-sizable array data structure
-will still perform better in the 1-unlimited dimension case, as its complexity
-is in $O(1)$.
+will still perform better in the single unlimited dimension case, as its
+complexity is in $O(1)$.
 
-%[Other related work?]
-%Sub array I/O from ADIOS etc / chunking from other libraries
-%Tell what was done for chunking in the past etc
+The universal B-tree~\cite{Bayer1997}, which is designed for multidimensional
+data, should also be another alternative to consider. The UB-tree is balanced
+and has all the guaranteed performance characteristics of B-trees, i.e.
+it requires linear space for storage and logarithmic time for insertion, lookup,
+removal of elements. In addition the UB-tree has the fundamental property that
+it preserves clustering of objects with respect to Cartesian distance.
+Therefore, the UB-tree shows its main strengths for multidimensional data.
+It also has very high potential for parallel processing, which makes it a very
+good candidate for further experimentation within the HDF5 library.
 
@@
 
+The various enhancements made to the chunk indexing methods show good performance
+and whereas there is no gain in complexity with the \textit{B-Tree version 2},
+performance and space utilization have been significantly improved. For datasets that are
+extended in a single dimension, the extensible array offers a very good
+improvement compared to the standard B-tree, since elements can be accessed
+in constant time.
+
+One component that is not taken into account in this work is the frequency
+of access of the elements. We should consider this in future work. An idea
+could be to make the \textit{B-Tree version 2} dynamically adjustable by using
+methods such as the Huffman coding~\cite{Huffman1952} already used for data
+compression, and which can represent the frequency of appearance of elements.
+Adding this component could benefit applications that frequently access specific
+regions of chunked data and further reduce the overhead introduced by the chunk
+indexing method.
+
 %\section*{Acknowledgments}

### 2015-07-20 WhitePapers/revise_chunks_seminar/pics/btree1.tex
Update chunking paper and add seminar slides
Former-commit-id: 0ec8d6529f464ab26accd5af9aef22dc2369e35b

--- 2015-02-06 WhitePapers/revise_chunks/pics/btree1.tex
@@
 \tikzstyle{level 1}=[sibling distance=80pt]
+
+\uncover<1->{
 \begin{scope} [local bounding box=scope1,%edge from parent fork down,
@@
 \draw[trans] (l1_4.four south) -- (c4_4);
+}
 
+\uncover<3->{
 \begin{scope}[shift={($(scope1.south)+(0,-40pt)$)},%edge from parent fork down,
@@
 \draw[trans] (l2_5.three south) -- (c5_3);
+}
 
+\uncover<2->{
 \draw[overlay,remember picture,ultra thick,line cap=round,->,
@@
   (l2_split);
+}
 \end{tikzpicture}

### 2015-07-20 WhitePapers/revise_chunks_seminar/pics/chunked.tex
Update chunking paper and add seminar slides
Former-commit-id: 0ec8d6529f464ab26accd5af9aef22dc2369e35b

\input{pics/common}

\begin{tikzpicture}

\node[inner sep=0] (dset) {};
\node[text height=25pt, left=23pt of dset, inner sep=0] (chunk0) {};
\drawdataset{shift=(chunk0.south), scale=0.5}{3}{0}{0}
\node[text height=25pt, right=20pt of dset, inner sep=0] (chunk1) {};
\drawdataset{shift=(chunk1.south), scale=0.5}{3}{-1}{3}
\node[text height=25pt, below=20pt of chunk0, inner sep=0] (chunk2) {};
\drawdataset{shift=(chunk2.south), scale=0.5}{3}{3}{-1}
\node[text height=25pt, below=20pt of chunk1, inner sep=0] (chunk3) {};
\drawdataset{shift=(chunk3.south), scale=0.5}{3}{-1}{-1}

\end{tikzpicture}

### 2015-07-20 WhitePapers/revise_chunks_seminar/pics/ea.tex
Update chunking paper and add seminar slides
Former-commit-id: 0ec8d6529f464ab26accd5af9aef22dc2369e35b

--- 2015-05-21 WhitePapers/revise_chunks/pics/ea.tex
@@
 
+\uncover<3->{
 \draw[decorate,decoration={brace,mirror,raise=2pt}, thick] (index.eight split west) to node [annotation,text width=40pt,left=5pt,font=\small\bfseries] {Number of chunks} (index.south west);
+}
 \node[annotation,below=2pt of sblock0] {DB$_0$};
@@
 \node[annotation,below=2pt of sblock4] (sblock4_annotation) {DB$_4$};
+\uncover<2->{
 \node[annotation,above=2pt of index,font=\small\bfseries] {Index block};
+}
+\uncover<5->{
 \node[annotation,right=12pt of sblock4_annotation,font=\small\bfseries] {Data blocks};
+}
+\uncover<4->{
 \node[annotation,right=4pt of sblock4b,font=\small\bfseries] {Super blocks};
+}
 

### 2015-07-20 WhitePapers/revise_chunks_seminar/pics/scaled.tex
Update chunking paper and add seminar slides
Former-commit-id: 0ec8d6529f464ab26accd5af9aef22dc2369e35b

--- 2015-05-21 WhitePapers/revise_chunks/pics/scaled.tex
@@
 \coordinate[below=4pt of G] (G1);
-\draw[<->,trans] (C2) -- node [below] {#1} (G1);
-\draw[<->,trans] (C1) -- node [left] {#2} (B1);
-\draw[<->,trans] (A1) -- node [above left] {#3} (B1);
+\draw[<->,trans] (C2) -- node [font=\small,below] {#1} (G1);
+\draw[<->,trans] (C1) -- node [font=\small,left] {#2} (B1);
+\draw[<->,trans] (A1) -- node [font=\small,above left] {#3} (B1);
 
@@
 
+\uncover<1->{
 \node (cubes) {
-\begin{minipage}{0.32\textwidth}
+\begin{minipage}{0.52\textwidth}
 \begin{tikzpicture}
@@
 \draw[->,draw=paperblue,thick] (0,0,0) -- (0,0,4);
-\node[font=\itshape] at (3.4,0,0) {x};
-\node[font=\itshape] at (0,4,0) {y};
-\node[font=\itshape] at (0,0,4.2) {z};
+\node[font=\small\itshape] at (3.4,0,0) {x};
+\node[font=\small\itshape] at (0,4,0) {y};
+\node[font=\small\itshape] at (0,0,4.4) {z};
 
@@
 };
+}
 
 % Hash value computation
+\uncover<3->{
 \node [computBox, font=\footnotesize, text width=100pt, right=50pt of cubes] (scaled) {
@@
 \smallskip
-\textbf{Number of bits to represent\\ coordinates:}\\
+\textbf{Number of bits to\\ represent coordinates:}\\
 \begin{math}
@@
 };
+}
 
+\uncover<4->{
 \node [right=of scaled,rectangle split,rectangle split horizontal,
@@
 \node [below=2pt of zhash] {$z$};
+}
 
-\draw[very thick, ->] (cubes) -- node[above, text width=4cm, align=center, font=\bfseries]
+\uncover<2->{
+\draw[very thick, ->] (cubes) -- node[above, text width=4cm, align=center, font=\small\bfseries]
     {Hash-value} ($ (scaled.west) - (0.5,0) $);
+}
 

### 2015-07-20 WhitePapers/revise_chunks_seminar/slides.tex
Update chunking paper and add seminar slides
Former-commit-id: 0ec8d6529f464ab26accd5af9aef22dc2369e35b

\documentclass[10pt,first,firstsupp,handout]{THG_slides}

% Options for beamer:
%
% 9,10,11,12,13,14,17pt  Fontsizes
% 
% compress: navigation bar becomes smaller
% t       : place contents of frames on top (alternative: b,c)
% handout : handoutversion
% notes   : show notes
% notes=onlyslideswithnotes
%

\setbeamertemplate{note page}{\ \\[.3cm]
\textbf{\color{blue}Notes:}\\%[0.1cm]
{\footnotesize %\tiny
\insertnote}}

% URLs
\usepackage{url}

%% Spacing adjustments
\usepackage{textcomp} % Must be loaded to prevent conflict microtype/siunitx
\usepackage{microtype}

% Nicer tabs
\usepackage{booktabs}

%% TikZ
\usepackage{tikz}
\usepackage{gnuplot-lua-tikz}
\usetikzlibrary{tikzmark, calc, patterns, shapes, positioning,arrows,
  decorations.pathmorphing, decorations.pathreplacing, decorations.text,
  math, trees, shadows}

% Tikz macros
\tikzset{%
  highlight/.style={rectangle,rounded corners,draw,thick}
}
\newcommand{\tablearrowright}[4]{%
  \tikz[overlay,remember picture]{
  \draw ($(pic cs:#1) + (5pt,4pt)$) edge[bend right=45,-stealth]
        ($(pic cs:#2) + (5pt,4pt)$)
        node [highlight,right,xshift=5pt,yshift=7pt,#4] {#3};}
}
\newcommand{\tablearrowleft}[4]{%
  \tikz[overlay,remember picture]{
  \draw ($(pic cs:#1) + (5pt,2pt)$) edge[bend left=45,-stealth]
        ($(pic cs:#2) + (5pt,2pt)$)
        node [highlight,right,xshift=5pt,yshift=-7pt,#4] {#3};}
}
\newcommand*{\yellowemph}[1]{%
  \tikz[baseline=(X.base)] \node[rectangle, fill=yellow, rounded corners, inner sep=0.3mm] (X) {#1};%
}
\newcommand{\smiley}{%
  \tikz[baseline=-0.75ex,black]{
    \draw circle (2mm);
    \node[fill,circle,inner sep=0.5pt] (left eye) at (135:0.8mm) {};
    \node[fill,circle,inner sep=0.5pt] (right eye) at (45:0.8mm) {};
    \draw (-145:0.9mm) arc (-120:-60:1.5mm);
  }
}

% Additional colors
\usepackage{xcolor}
\colorlet{paperblue}{-red!75!green!50}

% SI units
\usepackage{siunitx}
\sisetup{per-mode = symbol, binary-units = true}
\providecommand{\gbps}[1]{\SI{#1}{\giga\byte\per\second}}
\providecommand{\mbps}[1]{\SI{#1}{\mega\byte\per\second}}
\providecommand{\gb}[1]{\SI{#1}{\giga\byte}}
\providecommand{\mb}[1]{\SI{#1}{\mega\byte}}
\providecommand{\kb}[1]{\SI{#1}{\kilo\byte}}

%\usepackage[format=hang,labelfont=bf,labelsep=space,font=small]{caption}

% Code snippets
\usepackage{listings}
\def\lstsetc{\lstset{language=C,
%  numbers=left,
%  xleftmargin=2.2em,
  xleftmargin=1.8em,
  framexleftmargin=0.2em,
  numberstyle=\tiny\color{gray},
  stepnumber=1,
  showspaces=false, 
  showstringspaces=false,
  breaklines=true,
  basicstyle=\footnotesize\ttfamily,
  stringstyle=\itshape,
  commentstyle=\itshape\bfseries,
  frame=leftline,
  morekeywords={main, size_t, malloc, free, write, H5Screate_simple},
  morekeywords={[2]H5S_UNLIMITED},
  keywordstyle={[2]\color{gray}\bfseries}
  }
}

% Shows only the navigational symbol for navigating frames.
\setbeamertemplate{navigation symbols}[only frame symbol]

\setlayoutscale{0.5}
\setparametertextfont{\scriptsize}
\setlabelfont{\scriptsize}

\AtBeginSection[]
{
  \frame{
    \frametitle{Outline}
    \tableofcontents[currentsection]
  }
}

\begin{document}

\title{Extending HDF5 Datasets: Enhancements to the Chunk Indexing Methods}
\author{Vailin Choi, Jerome Soumagne, Quincey Koziol}
\institute{The HDF Group}

\begin{frame}
\maketitle
\end{frame}

\input{slides-body}

\end{document}

### 2015-07-24 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/gdata1.js
Added Index and Glossary.
Tested: Firefox
Former-commit-id: 059e3d8b9490556b4d0ad1273d76e0a9434771d6

@@ -1,1 +1,1 @@
-gXMLBuffer ="<?xml version=\"1.0\" encoding=\"utf-8\" ?><data>   <entry name=\"attribute\" value=\"An HDF5 attribute&#160;is a small metadata object describing the nature and/or intended usage of a primary data object. A primary data object may be a dataset, group, or committed datatype.\" />   <entry name=\"Chunked\" value=\"Chunked\" />   <entry name=\"Chunked Storage\" value=\"Chunked Storage\" />   <entry name=\"committed datatype\" value=\"A datatype can be shared by more than one dataset in the file if the datatype is saved to the file with a name. This shareable datatype is known as a committed datatype. In the past, this kind of datatype was called a named datatype.\" />   <entry name=\"Compact\" value=\"Compact\" />   <entry name=\"composite datatype\" value=\"In addition to atomic datatypes, the HDF5 Library supports composite datatypes. A composite datatype is an aggregation of one or more datatypes. Each class of composite datatypes has properties that describe the organization of the composite datatype. See the figure below. Composite datatypes include:\" />   <entry name=\"compound\" value=\"To create and use a compound datatype, you need to create a datatype with class compound (H5T_COM­POUND) and specify the total size of the data element in bytes. A compound datatype consists of zero or more uniquely named members. Members can be defined in any order but must occupy non-overlapping regions within the datum. The table below lists the properties of compound datatype members.\" />   <entry name=\"compound datatype\" value=\"A compound datatype&#160;is a collection of one or more data elements. Each element might be an atomic type, a small array, or another compound datatype.\" />   <entry name=\"Contiguous\" value=\"Contiguous\" />   <entry name=\"Contiguous Storage\" value=\"Contiguous Storage\" />   <entry name=\"dangling link\" value=\"Note that an object’s existence in a file is governed by the presence of at least one hard link to that object. If the last hard link to an object is removed, the object is removed from the file and any remaining soft link becomes a dangling link, a link whose target object does not exist.\" />   <entry name=\"Data Pipeline\" value=\"The Data Pipeline\" />   <entry name=\"Data Pipeline Filters\" value=\"Data Pipeline Filters\" />   <entry name=\"Data Transfer Properties\" value=\"Data Transfer Properties\" />   <entry name=\"dataset header\" value=\"A dataset header consists of one or more header messages containing persistent metadata describing var­ious aspects of the dataset. These records are defined in the HDF5 File Format Specification. The amount of storage required for the metadata depends on the
[…]

### 2015-07-24 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/gdata2.js

@@ -1,1 +1,1 @@
-gXMLBuffer ="<?xml version=\"1.0\" encoding=\"utf-8\" ?><data>   <entry name=\"no-op datatypes\" value=\"At present, the n-bit filter supports all datatypes. For datatypes of class time, string, opaque, reference, ENUM, and variable-length, the n-bit filter acts as a no-op which is short for no operation. For conve­nience, the rest of this section refers to such datatypes as no-op datatypes.\" />   <entry name=\"null dataspace\" value=\"A null dataspace, H5S_NULL, contains no data elements. Note that no selections can be applied to a null dataset as there is nothing to select.\" />   <entry name=\"primary data object\" value=\"An HDF5 attribute&#160;is a small metadata object describing the nature and/or intended usage of a primary data object. A primary data object may be a dataset, group, or committed datatype.\" />   <entry name=\"releasing the object’s identifier\" value=\"An application should close an object such as a datatype, dataspace, or dataset once the object is no lon­ger needed. Since each is an independent object, each must be released (or closed) separately. This action is frequently referred to as releasing the object’s identifier. The code in the example below closes the datatype, dataspace, and dataset that were created in the preceding section.\" />   <entry name=\"scalar dataspace\" value=\"A scalar dataspace, H5S_SCALAR, represents just one element, a scalar. Note that the datatype of this one element may be very complex; example would be a compound structure with members being of any allowed HDF5 datatype, including multidimensional arrays, strings, and nested compound structures. By convention, the rank of a scalar dataspace is always 0 (zero); think of it geometrically as a single, dimen­sionless point, though that point may be complex.\" />   <entry name=\"selections\" value=\"The previous section described writing or reading an entire dataset. HDF5 also supports access to portions of a dataset. These parts of datasets are known as selections.\" />   <entry name=\"self-describing\" value=\"The structure of an HDF5 file is self-describing, meaning that an application can navigate an HDF5 file to discover and understand all the objects it contains. This is an iterative process wherein the structure is tra­versed as a graph, starting at one node and recursively visiting linked nodes. To explore the entire file, the traversal should start at the root group.\" />   <entry name=\"simple dataspace\" value=\"A simple dataspace, H5S_SIMPLE, is a multidimensional array of elements. The dimensionality of the dataspace (or the rank of the array) is fixed and is defined at creation time. The size of each dimension can grow during the life time of the dataspace from the current size&#160;up to the maximum size. Both the current size and the maximum size are specified at creation time. The size
[…]

### 2015-07-24 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/glo.js

@@ -1,1 +1,1 @@
-gXMLBuffer ="<?xml version=\"1.0\" encoding=\"utf-8\" ?><glossary>  <chunkinfo url=\"gdata1.js\" first=\"attribute\" last=\"named datatype\" num=\"38\" />  <chunkinfo url=\"gdata2.js\" first=\"no-op datatypes\" last=\"symbolic links\" num=\"11\" />  </glossary>";
+gXMLBuffer ="<?xml version=\"1.0\" encoding=\"utf-8\" ?><glossary>  <chunkinfo url=\"gdata1.js\" first=\"attribute\" last=\"hard link\" num=\"26\" />  <chunkinfo url=\"gdata2.js\" first=\"hyperslab\" last=\"symbolic link\" num=\"21\" />  </glossary>";

### 2015-07-24 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/idata1.js

@@ -1,1 +1,1 @@
-gXMLBuffer ="<?xml version=\"1.0\" encoding=\"utf-8\" ?><data>  <key name=\"abstract data model\" >    <topic name=\"The HDF5 Data Model and File Structure\" url=\"HDF5_Users_Guide/DataModelAndFileStructure/The_HDF5_Data_Model_and_File_Structure.htm#IX_abstract_data_model\" />  </key>  <key name=\"Access properties\" >    <topic name=\"Properties and Property Lists in HDF5\" url=\"HDF5_Users_Guide/PropertyLists/Properties_and_Property_Lists_in_HDF5.htm#IX_Access_properties\" />  </key>  <key name=\"Array\" >    <topic name=\"HDF5 Datatypes\" url=\"HDF5_Users_Guide/Datatypes/HDF5_Datatypes.htm#IX_Array\" />  </key>  <key name=\"array datatypes\" >    <topic name=\"HDF5 Datasets\" url=\"HDF5_Users_Guide/Datasets/HDF5_Datasets.htm#IX_array_datatypes\" />  </key>  <key name=\"atomic datatypes\" >    <topic name=\"HDF5 Datasets\" url=\"HDF5_Users_Guide/Datasets/HDF5_Datasets.htm#IX_atomic_datatypes\" />  </key>  <key name=\"attr_id\" >    <topic name=\"HDF5 Attributes\" url=\"HDF5_Users_Guide/Attributes/HDF5_Attributes.htm#IX_attr_id_1\" />    <topic name=\"HDF5 Attributes\" url=\"HDF5_Users_Guide/Attributes/HDF5_Attributes.htm#IX_attr_id_2\" />    <topic name=\"HDF5 Attributes\" url=\"HDF5_Users_Guide/Attributes/HDF5_Attributes.htm#IX_attr_id\" />  </key>  <key name=\"backing_store\" >    <topic name=\"The HDF5 File\" url=\"HDF5_Users_Guide/TheFile/The_HDF5_File.htm#IX_backing_store\" />  </key>  <key name=\"big-endian\" >    <topic name=\"HDF5 Datatypes\" url=\"HDF5_Users_Guide/Datatypes/HDF5_Datatypes.htm#IX_big_endian\" />  </key>  <key name=\"block\" >    <topic name=\"HDF5 Dataspaces and Partial I/O\" url=\"HDF5_Users_Guide/Dataspaces/HDF5_Dataspaces_and_Partial
[…]

### 2015-07-24 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/idata24.js

@@ -1,1 +1,1 @@
-gXMLBuffer ="<?xml version=\"1.0\" encoding=\"utf-8\" ?><data>  <key name=\"storage model\" >    <topic name=\"The HDF5 Data Model and File Structure\" url=\"HDF5_Users_Guide/DataModelAndFileStructure/The_HDF5_Data_Model_and_File_Structure.htm#IX_storage_model\" />  </key>  <key name=\"stored data\" >    <topic name=\"The HDF5 Data Model and File Structure\" url=\"HDF5_Users_Guide/DataModelAndFileStructure/The_HDF5_Data_Model_and_File_Structure.htm#IX_stored_data\" />  </key>  <key name=\"stride\" >    <topic name=\"HDF5 Dataspaces and Partial I/O\" url=\"HDF5_Users_Guide/Dataspaces/HDF5_Dataspaces_and_Partial_I_O.htm#IX_stride\" />  </key>  <key name=\"superblock\" >    <topic name=\"The HDF5 File\" url=\"HDF5_Users_Guide/TheFile/The_HDF5_File.htm#IX_superblock\" />  </key>  <key name=\"Transfer properties\" >    <topic name=\"Properties and Property Lists in HDF5\" url=\"HDF5_Users_Guide/PropertyLists/Properties_and_Property_Lists_in_HDF5.htm#IX_Transfer_properties\" />  </key>  <key name=\"transient\" >    <topic name=\"HDF5 Datatypes\" url=\"HDF5_Users_Guide/Datatypes/HDF5_Datatypes.htm#IX_transient\" />    <topic name=\"Properties and Property Lists in HDF5\" url=\"HDF5_Users_Guide/PropertyLists/Properties_and_Property_Lists_in_HDF5.htm#IX_transient_2\" />    <topic name=\"Properties and Property Lists in HDF5\" url=\"HDF5_Users_Guide/PropertyLists/Properties_and_Property_Lists_in_HDF5.htm#IX_transient_1\" />  </key>  <key name=\"userblock\" >    <topic name=\"The HDF5 File\" url=\"HDF5_Users_Guide/TheFile/The_HDF5_File.htm#IX_userblock\" />  </key>  <key name=\"Variable-length\" >    <topic name=\"HDF5 Datatypes\" url=\"HDF5_Users_Guide/Datatypes/HDF5_Data
[…]

### 2015-07-24 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Add view edits to analysis RFC
Former-commit-id: 98d1a68122164b9cb8ee398b06cbff1087faa882

@@
 \else
-  \usepackage{lmodern} % times / lmodern / mathpazo / palatino
+  \usepackage{times} % times / lmodern / mathpazo / palatino
   \usepackage[scaled=.95]{helvet}
@@
 
+\usepackage[margins]{trackchanges}
+\addeditor{JS}
+\addeditor{QK}
+% annote, note, add, remove, change
+
 % Title, author, etc
@@
 \author{Quincey Koziol}
-\date{February 25, 2015}
+\date{July 24, 2015}
 \rfcversion{2014-07-17.v4}
-\revision{July 17, 2014}{Version 1 circulated for comment within The HDF Group.}
-\revision{August 20, 2014}{Version 2 circulated for comment within The HDF Group.}
-\revision{November 14, 2014}{Version 3 circulated for comment within The HDF Group.}
-\revision{February 25, 2015}{Version 4 edits and typo fixing.}
+\revision{Jul. 17, 2014}{Version 1 circulated for comment within The HDF Group.}
+\revision{Aug. 20, 2014}{Version 2 circulated for comment within The HDF Group.}
+\revision{Nov. 14, 2014}{Version 3 circulated for comment within The HDF Group.}
+\revision{Feb. 25, 2015}{Version 4 edits and typo fixing.}
+\revision{Jul. 24, 2015}{Version 5 with edits to view object.}
 
@@
 query requests for execution on HDF5 containers;
-\item New \textit{view} objects\footref{fn:object} and API routines, which apply a query to an HDF5
-container and return a set of references into the container that fulfills
-the query criteria;
+\item New \textit{view} objects\footref{fn:object} and API routines, which
+\change[JS]{apply a query to an HDF5 container and return }{are the result of a query applied
+to an HDF5 container and consist of} a set of references into the
+container that fulfills the query criteria;
 \item New \textit{index} objects and API routines, which allows the creation of
@@
 \section{View Objects}
-Applying a query to an HDF5 container creates an HDF5 view object. HDF5 view
-objects are run-time, in-memory objects (i.e., not stored in a container) that
-consist of read-only references into the contents of the HDF5 container that
-the query was applied to. The current API is presented below:
-\todo{View API must be revised.}
-
+Applying a query to an HDF5 container creates an HDF5 view. HDF5 view
+objects are run-time, in-memory objects (i.e., not stored in a container)
+\add[JS]{but which can be persisted}, that
+consist of read-only references \add[JS]{to attributes, objects and data regions}
+into the contents of the HDF5 container that the query was applied to.
+\add[JS]{The view object can be therefore seen as a virtual container. It is
+defined as an anonymous HDF5 group, which consists of three predefined datasets that
+contain attribute, object and region references. A new view is created by the
+following routine, which applies a query to an HDF5 container, group hierarchy,
+or individual object and returns the object ID of the newly created group:}
 {\lstsetc
 \begin{lstlisting}
-hid_t  H5Vcreate(hid_t loc_id, hid_t query_id, hid_t vcpl_id);
-herr_t H5Vclose(hid_t view_id);
+hid_t H5Qapply(hid_t loc_id, hid_t query_id, hid_t vcpl_id, unsigned *result);
+\end{lstlisting}
+}
+
+\add[JS]{As mentioned, the created view may also need to be persisted. For
+coherency, a time stamp may be attached to it so that its states has a meaning
+compared to the state of the container that the query was applied to (as the
+container may have been modified in the meantime). It may also be useful in
+that case to define different states to the view (\textit{dead} or
+\textit{live}) so that the user knows whether the view is current or not.}
+
+To further ease the retrieval of the results from the view and for convenience,
+an API specific to the view object may be defined:
+
+\note[JS]{Which ones do we really need???}
+{\lstsetc
+\begin{lstlisting}
 herr_t H5Vget_location(hid_t view_id, hid_t *loc_id);
@@
 
-View objects are created with \texttt{H5Vcreate}, which applies a query to an
+\remove[JS]{View objects are created with \texttt{H5Vcreate}, which applies a query to an
 HDF5 container, group hierarchy, or individual object and produces the view
 object as a result. The attributes, objects, and/or data elements referenced
-within a view can be retrieved by further API calls. Note that currently,
+within a view can be retrieved by further API calls.} Note that currently,
 attribute references are not available, this feature will be added in order to

### 2015-08-31 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Updates to analysis RFC
Former-commit-id: 31483f05b44458dca44153eda2d8250b8cff2564

@@
 Applying a query to an HDF5 container creates an HDF5 view. HDF5 view
-objects are run-time, in-memory objects (i.e., not stored in a container)
-\add[JS]{but which can be persisted}, that
+objects are run-time, in-memory objects (i.e., not stored in a container
+\add[JS]{but which can be persisted}), that
 consist of read-only references \add[JS]{to attributes, objects and data regions}
@@
 defined as an anonymous HDF5 group, which consists of three predefined datasets that
-contain attribute, object and region references. A new view is created by the
+contain attribute, object and region references, and stored in-memory, i.e., using
+the existing core driver. A new view is created by the
 following routine, which applies a query to an HDF5 container, group hierarchy,
@@
 \begin{lstlisting}
-hid_t H5Qapply(hid_t loc_id, hid_t query_id, hid_t vcpl_id, unsigned *result);
+hid_t H5Qapply(hid_t loc_id, hid_t query_id, unsigned *result, hid_t vcpl_id);
 \end{lstlisting}
@@
 
-\add[JS]{As mentioned, the created view may also need to be persisted. For
+\add[JS]{As mentioned, the created view may also need to be persisted and this
+can be done by calling \textit{H5Ocopy()} to copy the group (stored in a virtual
+container) to a persistent container. For
 coherency, a time stamp may be attached to it so that its states has a meaning
@@
 
-To further ease the retrieval of the results from the view and for convenience,
-an API specific to the view object may be defined:
+%To further ease the retrieval of the results from the view and for convenience,
+%an API specific to the view object may be defined:
 
-\note[JS]{Which ones do we really need???}
-{\lstsetc
-\begin{lstlisting}
-herr_t H5Vget_location(hid_t view_id, hid_t *loc_id);
-herr_t H5Vget_query(hid_t view_id, hid_t *query_id);
-herr_t H5Vget_counts(hid_t view_id, hsize_t *attr_count, hsize_t *obj_count,
-  hsize_t *elem_region_count);
-herr_t H5Vget_attrs(hid_t view_id, hsize_t start, hsize_t count, hid_t attr_id[]);
-herr_t H5Vget_objs(hid_t view_id, hsize_t start, hsize_t count, hid_t obj_id[]);
-herr_t H5Vget_elem_regions(hid_t view_id, hsize_t start, hsize_t count,
-  hid_t dataset_id[], hid_t dataspace_id[]);
-\end{lstlisting}
-}
+%\note[JS]{Which ones do we really need???}
+%{\lstsetc
+%\begin{lstlisting}
+%herr_t H5Vget_location(hid_t view_id, hid_t *loc_id);
+%herr_t H5Vget_query(hid_t view_id, hid_t *query_id);
+%herr_t H5Vget_counts(hid_t view_id, hsize_t *attr_count, hsize_t *obj_count,
+%  hsize_t *elem_region_count);
+%herr_t H5Vget_attrs(hid_t view_id, hsize_t start, hsize_t count, hid_t attr_id[]);
+%herr_t H5Vget_objs(hid_t view_id, hsize_t start, hsize_t count, hid_t obj_id[]);
+%herr_t H5Vget_elem_regions(hid_t view_id, hsize_t start, hsize_t count,
+%  hid_t dataset_id[], hid_t dataspace_id[]);
+%\end{lstlisting}
+%}
 

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/analysis_ext-body.tex
First bunch of revisions to analysis extensions
Former-commit-id: 6e2f23896444cf11519cdb913e399220ffd38344

--- 2015-08-31 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
@@
-\documentclass[letterpaper,hyper]{THG_RFC}
-
-% Fonts
-\usepackage{ifluatex}
-\ifluatex
-  % Font
-  \usepackage{luatextra, xunicode, unicode-math}
-  \defaultfontfeatures{Ligatures=TeX}
-  \setmainfont[
-    UprightFont={*},
-    BoldFont={*-Bold},
-    ItalicFont={*-Italic},
-    BoldItalicFont={*-BoldItalic},
-    SlantedFont={*-Italic},
-    BoldSlantedFont={*-BoldItalic}
-  ]{CMU Serif}
-  \setsansfont[
-    UprightFont={*},
-    BoldFont={*-Bold},
-    ItalicFont={*-Oblique},
-    BoldItalicFont={*-BoldOblique}
-  ]{CMU Sans Serif}
-  \setmathfont[math-style=ISO, bold-style=ISO]{Asana Math}
-  \setmonofont[
-    UprightFont={*-Regular},
-    BoldFont={*-Bold},
-    ItalicFont={*-Italic},
-    BoldItalicFont={*-BoldItalic}
-  ]{CMU Typewriter}
-\else
-  \usepackage{times} % times / lmodern / mathpazo / palatino
-  \usepackage[scaled=.95]{helvet}
-  \usepackage{courier}
-\fi
-
-% Path to figures, plots
-\graphicspath{{./pics/}{./plots/}}
-
-%% TikZ
-\usepackage{tikz}
-\usetikzlibrary{patterns, shapes, decorations.pathreplacing}
-\usepackage{gnuplot-lua-tikz}
-
-% SI units
-%\usepackage{textcomp}
-\usepackage[binary-units]{siunitx}
-\sisetup{per-mode = symbol}
-\providecommand{\gbps}[1]{\SI{#1}{\giga\byte\per\second}}
-\providecommand{\mbps}[1]{\SI{#1}{\mega\byte\per\second}}
-\providecommand{\gb}[1]{\SI{#1}{\giga\byte}}
-\providecommand{\mb}[1]{\SI{#1}{\mega\byte}}
-\providecommand{\kb}[1]{\SI{#1}{\kilo\byte}}
-
-% Code snippets
-\usepackage{listings}
-\def\lstsetc{\lstset{language=C,
-  numbers=left,
-  xleftmargin=20pt,
-  numberstyle=\tiny\color{gray},
-  stepnumber=1,
-  showspaces=false, 
-  showstringspaces=false,
-  breaklines=true,
-  basicstyle=\small\ttfamily,
-  stringstyle=\itshape,
-  commentstyle=\itshape\bfseries,
-  morekeywords={main, size_t, malloc, free,
-    hsize_t, hid_t, herr_t, H5X_class_t, H5X_type_t, H5Q_combine_op_t,
-    H5Q_type_t, H5Q_match_op_t,
-    H5Fcreate, H5Fclose,
-    H5Dcreate, H5Dopen, H5Dclose, H5Dwrite, H5Dread, H5Dquery,
-    H5Qcreate, H5Qclose, H5Qcombine, H5Qget_type, H5Qget_match_op,
-    H5Qget_components, H5Qget_combine_op, H5Qencode, H5Qdecode,
-    H5Screate_simple, H5Sclose, H5Sget_select_npoints,
-    H5Xregister, H5Xunregister, H5Xcreate, H5Xremove, H5Xget_count,
-    H5Vcreate, H5Vclose, H5Vget_location, H5Vget_query, H5Vget_counts,
-    H5Vget_attrs, H5Vget_objs, H5Vget_elem_regions
-    }
-  }
-}
-
-\usepackage[margins]{trackchanges}
-\addeditor{JS}
-\addeditor{QK}
-% annote, note, add, remove, change
-
-% Title, author, etc
-\title{Data Analysis Extensions}
-\author{Jerome Soumagne}
-\author{Quincey Koziol}
-\date{July 24, 2015}
-\rfcversion{2014-07-17.v4}
-\revision{Jul. 17, 2014}{Version 1 circulated for comment within The HDF Group.}
-\revision{Aug. 20, 2014}{Version 2 circulated for comment within The HDF Group.}
-\revision{Nov. 14, 2014}{Version 3 circulated for comment within The HDF Group.}
-\revision{Feb. 25, 2015}{Version 4 edits and typo fixing.}
-\revision{Jul. 24, 2015}{Version 5 with edits to view object.}
-
-%% Start the document
-\begin{document}
-
-%% Add Attribute reference RFC
-
-%% Title
-\maketitle
-
-%% Abstract
-\begin{abstract}
-Accessing, selecting and retrieving data from an HDF5 container can be a time
-consuming process, particularly so when data is very large. To enable, ease and 
-accelerate this process, we introduce in this RFC extensions to the library
-to efficiently query, select and index data.
-\end{abstract}
-
 \section{Introduction}
@@
 within an HDF5 container and retrieve the results of applying those query
-operations. Support for these operations on HDF5 containers can be defined via:
-\begin{enumerate}
-\item New \textit{query} objects\footnote{Query and view objects are
+operations. Support for these operations can be defined via:
+\begin{itemize}
+\item New \textit{query} objects\footnote{Query objects are
 \textit{in-memory} objects, which therefore do not modify the content of the
@@
 query requests for execution on HDF5 containers;
-\item New \textit{view} objects\footref{fn:object} and API routines, which
-\change[JS]{apply a query to an HDF5 container and return }{are the result of a query applied
-to an HDF5 container and consist of} a set of references into the
-container that fulfills the query criteria;
 \item New \textit{index} objects and API routines, which allows the creation of
 indices on the contents of HDF5 containers, to improve query performance.
-\end{enumerate}
+\end{itemize}
 
@@
 
+\subsection{Query Creation}
+
 The core query API is composed of
 two routines: \texttt{H5Qcreate} and \texttt{H5Qcombine}. \texttt{H5Qcreate}
-creates new queries, by specifying an aspect of an HDF5 container, such as
-data elements, link names, attribute names, etc., a match operator, such as
-$=$, $\neq$, $\leq$, $\geq$, and a value for the match operator.
-Created query objects can be serialized and deserialized using \texttt{H5Qencode}
+creates new queries, by specifying an aspect of an HDF5 container, such as:
+\begin{itemize}
+\item \texttt{H5Q\_TYPE\_DATA\_ELEM} (data element);
+\item \texttt{H5Q\_TYPE\_LINK\_NAME} (link name);
+\item \texttt{H5Q\_TYPE\_ATTR\_NAME} (attribute name);
+\item \texttt{H5Q\_TYPE\_ATTR\_VALUE} (attribute value);
+\end{itemize}
+as well as a match operator, such as:
+\begin{itemize}
+\item \texttt{H5Q\_MATCH\_EQUAL} ($=$);
+\item \texttt{H5Q\_MATCH\_NOT\_EQUAL} ($\neq$);
+\item \texttt{H5Q\_MATCH\_LESS\_THAN} ($\leq$);
+\item \texttt{H5Q\_MATCH\_GREATER\_THAN} ($\geq$);
+\end{itemize}
+and a value for the match operator.
+Created query objects can be serialized and deserialized using the \texttt{H5Qencode}
 and \texttt{H5Qdecode} routines\footnote{Serialization/deserialization of queries
@@
 \texttt{H5Qcombine} combines two query objects into a
-new query object, using boolean operators such as $AND(\land)$ and $OR(\lor)$.
+new query object, using boolean operators such as:
+\begin{itemize}
+\item \texttt{H5Q\_COMBINE\_AND} ($\mathrm{\land}$);
+\item \texttt{H5Q\_COMBINE\_OR} ($\mathrm{\lor}$).
+\end{itemize}
 Queries created with \texttt{H5Qcombine} can be used as input to further
@@
 that would match data elements in any dataset within the container that are
-equal to the value $17$. Another call to \texttt{H5Qcreate} could create a
-query object that would match link names equal to $Pressure$.
-Calling \texttt{H5Qcombine} with the $\land$ operator and those two query
-objects would create a new query object that matched elements equal to $17$
-in HDF5 datasets with link names equal to $Pressure$.
+equal to the value ``$\mathrm{17}$''. Another call to \texttt{H5Qcreate} could create a
+query object that would match link names equal to ``$\mathrm{Pressure}$''.
+Calling \texttt{H5Qcombine} with the $\mathrm{\land}$ operator and those two query
+objects would create a new query object that matched elements equal to ``$\mathrm{17}$''
+in HDF5 datasets with link names equal to ``$\mathrm{Pressure}$''.
 Creating the data analysis extensions to HDF5 using a \textit{programmatic
@@
 defined here to provide a more user-friendly (as opposed to
-\textit{developer-friendly}) query syntax like $Pressure = 17$. However, we
-regard this as out-of-scope for now.
+\textit{developer-friendly}) query syntax like ``$\mathrm{Pressure = 17}$''.
+However, we regard this as out-of-scope for now.
 
-\TableRef{tab:querycomb} describes the result types for atomic queries and
-combining queries of different types. Query results of $None$ type are rejected
-when \texttt{H5Qcombine} is called, causing it to return failure\footnote{Query
-results of $None$ type may be implemented with another result type in the
-future, once experience with the query framework is acquired and a meaningful
-grammar for those results are defined.}.
+\subsection{Query Execution and Views}
+Applying a query to an HDF5 container creates an HDF5 \textit{view}. A view is
+an anonymous HDF5 group in a temporary memory container. A view group contains up to
+three 1-D dataset objects with references into the contents of the HDF5 container
+that the query was applied to:
+one with \textit{object} references, one with \textit{region} references and
+one with \textit{attribute} references.
 
-\begin{table}[ht]\footnotesize
-\caption{Query combinations and associated result type.}
-\label{tab:querycomb}
-\begin{tabular}{ll} \toprule
-Query &
-Result Type\\ \midrule
-\texttt{H5Q\_TYPE\_DATA\_ELEM} & $Dataset~Element$ \\
-\texttt{H5Q\_TYPE\_ATTR\_VALUE} & $Attribute$ \\
-\texttt{H5Q\_TYPE\_ATTR\_NAME} & $Object$ \\
-\texttt{H5Q\_TYPE\_LINK\_NAME} & $Object$ \\
-$Dataset~Element \land Dataset~Element$ & $Dataset~Element$ \\
-$Dataset~Element \land Attribute$ & $None$ \\
-$Dataset~Element \land Object$ & $Dataset~Element$ \\
-$Attribute \land Attribute$ & $Attribute$ \\
-$Attribute \land Object$ & $Attribute$ \\
-$Object \land Object$ & $Object$ \\
-$Dataset~Element \lor Dataset~Element$ & $Dataset~Element$ \\
-$Dataset~Element \lor Attribute$ & $Combination$ \\
-$Dataset~Element \lor Object$ & $Combination$ \\
-$Dataset~Element \lor Combination$ & $Combination$ \\
-$Attribute \lor Attribute$ & $Attribute$ \\
-$Attribute \lor Object$ & $Combination$ \\
-$Attribute \lor Combination$ & $Combination$ \\
-$Object \lor Object$ & $Object$ \\
-$Object \lor Combination$ & $Combination$ \\
-$Combination \lor Combination$ & $Combination$ \\
-$Combination \land Dataset~Element$ & $None$ \\
-$Combination \land Attribute$ & $None$ \\
-$Combination \land Object$ & $None$ \\
-$Combination \land Combination$ & $None$ \\
-\bottomrule
-\end{tabular}
-\end{table}
+\begin{figure}
+\input{pics/hdf5_view}
+\caption{Temporary memory container with datasets containing query results (i.e.,
+HDF5 references).}
+\label{fig:hdf5_view}
+\vspace{-20pt}
+\end{figure}
 
-\section{View Objects}
-Applying a query to an HDF5 container creates an HDF5 view. HDF5 view
-objects are run-time, in-memory objects (i.e., not stored in a container
-\add[JS]{but which can be persisted}), that
-consist of read-only references \add[JS]{to attributes, objects and data regions}
-into the contents of the HDF5 container that the query was applied to.
-\add[JS]{The view object can be therefore seen as a virtual container. It is
-defined as an anonymous HDF5 group, which consists of three predefined datasets that
-contain attribute, object and region references, and stored in-memory, i.e., using
-the existing core driver. A new view is created by the
-following routine, which applies a query to an HDF5 container, group hierarchy,
-or individual object and returns the object ID of the newly created group:}
+A new view is created by the
+following \texttt{H5Qapply} routine, which applies a query to an HDF5 container,
+group hierarchy, or individual object and returns the object ID of the newly created
+group. The attributes, objects, and/or data regions referenced within a view's
+datasets can be retrieved by further HDF5 dataset (H5D*) API calls.
+
 {\lstsetc
@@
 
-\add[JS]{As mentioned, the created view may also need to be persisted and this
-can be done by calling \textit{H5Ocopy()} to copy the group (stored in a virtual
+Although the created view is stored in memory, it can be persisted
+by calling \texttt{H5Ocopy()} to copy the group (stored in a virtual
 container) to a persistent container. For
-coherency, a time stamp may be attached to it so that its states has a meaning
+coherency, a time stamp may also be attached to it so that its states has a meaning
 compared to the state of the container that the query was applied to (as the
-container may have been modified in the meantime). It may also be useful in
+container may have been modified in the meantime). It may be useful in
 that case to define different states to the view (\textit{dead} or
-\textit{live}) so that the user knows whether the view is current or not.}
+\textit{live}) so that the user knows whether the view is current or not.
 
@@
 
-\remove[JS]{View objects are created with \texttt{H5Vcreate}, which applies a query to an
-HDF5 container, group hierarchy, or individual object and produces the view
-object as a result. The attributes, objects, and/or data elements referenced
-within a view can be retrieved by further API calls.} Note that currently,
-attribute references are not available, this feature will be added in order to
-support views that contain attribute references\footnote{See RFC 201X-XX-XX.vX.}.
+%Note that currently, attribute references are not available, this feature will be added in order to
+%support views that contain attribute references\footnote{See RFC 201X-XX-XX.vX.}.
+
+For example, starting with the HDF5 container described in~\FigureRef{fig:hdf5_view1},
+applying a ``$\mathrm{link\_name}$ $\mathrm{=}$ $\mathrm{Pressure}$''
+query would result in the view shown in~\FigureRef{fig:hdf5_view2}, highlighted in blue.
+\begin{figure}
+\begin{subfigure}[b]{.49\linewidth}
+\centering
+\resizebox{\textwidth}{!}{
+  \input{pics/hdf5_view1}
+}
+\caption{HDF5 container example.}
+\label{fig:hdf5_view1}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{.49\linewidth}
+\centering
+\resizebox{\textwidth}{!}{
+  \input{pics/hdf5_view2}
+}
+\caption{HDF5 container with link name query applied.}
+\label{fig:hdf5_view2}
+\end{subfigure}
+\caption{HDF5 view creation example with simple query.}
+\end{figure}
+
+Alternatively, applying a ``$\mathrm{data\_element}$ $\mathrm{=}$ $\mathrm{17}$''
+query would result in the view shown in~\FigureRef{fig:hdf5_view3}, highlighted in blue.
+Finally, applying the combined queries ``$\mathrm{(link\_name = Pressure)}$
+$\mathrm{\land}$ $\mathrm{(data\_element = 17)}$''
+would result in the view shown in~\FigureRef{fig:hdf5_view4}, highlighted in blue.
 
 \begin{figure}
-\input{pics/hdf5_view1}
-\caption{HDF5 container example.}
-\label{fig:hdf5_view1}
+\begin{subfigure}[b]{.49\linewidth}
+\centering
+\resizebox{\textwidth}{!}{
+  \input{pics/hdf5_view3}
+}
+\caption{HDF5 container with data element query applied.}
+\label{fig:hdf5_view3}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{.49\linewidth}
+\centering
+\resizebox{\textwidth}{!}{
+  \input{pics/hdf5_view4}
+}
+\caption{HDF5 container with combined query applied.}
+\label{fig:hdf5_view4}
+\end{subfigure}
+\caption{HDF5 view creation example with combined query.}
+\vspace{-20pt}
 \end{figure}
 
-For example, starting with the HDF5 container described in~\FigureRef{fig:hdf5_view1},
-applying the $link\_name = Pressure$ query (described above) would result
-in the view shown in~\FigureRef{fig:hdf5_view2}, highlighted in blue.
-
-\begin{figure}
-\input{pics/hdf5_view2}
-\caption{HDF5 container example with query $link\_name = Pressure$ applied.}
-\label{fig:hdf5_view2}
-\end{figure}
-
-Alternatively, applying the $data\_element = 17$ query (described above) would
-result in the view shown in~\FigureRef{fig:hdf5_view3}, highlighted in blue.
-
-\begin{figure}
-\input{pics/hdf5_view3}
-\caption{HDF5 container example with query $data\_element = 17$ applied.}
-\label{fig:hdf5_view3}
-\end{figure}
-
-Finally, applying the combined $(link\_name = Pressure)\land(data\_element = 17)$
-query (described above) would result in the view shown in~\FigureRef{fig:hdf5_view4},
-highlighted in blue.
-
-\begin{figure}
-\input{pics/hdf5_view4}
-\caption{HDF5 container example with query $(link\_name = Pressure)\land(data\_element = 17)$ applied.}
-\label{fig:hdf5_view4}
-\end{figure}
-
-Views can be thought of as containing a set of HDF5 references (object,
+Since views contain a set of HDF5 references (object,
 dataset region or attribute references) to components of the underlying
-container, retaining the context of the original container. For example, the
-view containing the results of the $(link\_name = Pressure)\land(data\_element = 17)$
-query will contain three dataset region references, which
+container, they retain the context of the original container. For example, the
+view containing the results in~\FigureRef{fig:hdf5_view4} will contain three
+dataset region references, which
 can be retrieved from the view object and probed for the dataset and selection
@@
 
+\TableRef{tab:querycomb} describes the result types for atomic queries and
+combining queries of different types. Query results of \textit{None} type are rejected
+when \texttt{H5Qcombine} is called, causing it to return failure\footnote{Query
+results of \textit{None} type may be implemented with another result type in the
+future, once experience with the query framework is acquired and a meaningful
+grammar for those results are defined.}.
+
+\begin{table}[ht]\footnotesize
+\caption{Query combinations and associated result reference type.}
+\label{tab:querycomb}
+\begin{tabular}{ll} \toprule
+Query &
+Result Type\\ \midrule
+\texttt{H5Q\_TYPE\_DATA\_ELEM} & Dataset~Region \\
+\texttt{H5Q\_TYPE\_ATTR\_VALUE} & Attribute \\
+\texttt{H5Q\_TYPE\_ATTR\_NAME} & Attribute \\
+\texttt{H5Q\_TYPE\_LINK\_NAME} & Object \\
+Dataset~Element $\mathrm{\land}$ Dataset~Element & Dataset~Region \\
+Dataset~Element $\mathrm{\land}$ Attribute & Dataset~Region \\
+Dataset~Element $\mathrm{\land}$ Object & Dataset~Region \\
+Attribute $\mathrm{\land}$ Attribute & Attribute \\
+Attribute $\mathrm{\land}$ Object & Object \\
+Object $\mathrm{\land}$ Object & Object \\
+Dataset~Element $\mathrm{\lor}$ Dataset~Element & Dataset~Region \\
+Dataset~Element $\mathrm{\lor}$ Attribute & Combination \\
+Dataset~Element $\mathrm{\lor}$ Object & Combination \\
+Dataset~Element $\mathrm{\lor}$ Combination & Combination \\
+Attribute $\mathrm{\lor}$ Attribute & Attribute \\
+Attribute $\mathrm{\lor}$ Object & Combination \\
+Attribute $\mathrm{\lor}$ Combination & Combination \\
+Object $\mathrm{\lor}$ Object & Object \\
+Object $\mathrm{\lor}$ Combination & Combination \\
+Combination $\mathrm{\lor}$ Combination & Combination \\
+Combination $\mathrm{\land}$ Dataset~Element & None \\
+Combination $\mathrm{\land}$ Attribute & None \\
+Combination $\mathrm{\land}$ Object & None \\
+Combination $\mathrm{\land}$ Combination & None \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \section{Index Objects}
-Index objects are designed to accelerate creation of view objects from
-frequently occurring query operations.
-For example, if the $(link\_name = Pressure)\land(data\_element = 17)$ query
-(previously described) is going to be frequently executed on the container, indices
-could be created in that container, which would speed up the creation of views
-when querying for link names and for data element values. Indices created for
-accelerating the $link\_name = Pressure$ or $data\_element = 17$ queries
+Index objects are designed to accelerate creation of views from query operations.
+For example, if the ``$\mathrm{(link\_name = Pressure)}$
+$\mathrm{\land}$ $\mathrm{(data\_element = 17)}$'' query
+(previously described) is going to be either frequently executed or executed
+on a container that contains significantly large datasets, indices
+could be created in that container, which would speed up the
+creation of views when querying for link names and for data element values.
+Indices created for accelerating the $link\_name = Pressure$ or $data\_element = 17$ queries
 would also improve view creation for the more complex
 $(link\_name = Pressure)\land(data\_element = 17)$ query.
-
 Although creating indices for metadata components of queries, such as link or
-attribute names, is possible, we focus on index creation for dataset elements,
+attribute names, is possible, we first focus on index creation for dataset elements,
 as they represent the largest volume of data in typical HPC application usage of
 HDF5. Queries with metadata components execute properly,
-\todo{Metadata indexing must be added.} but are not able to be accelerated
-with an index currently.
+but are not able to be accelerated with an index currently.
 
-The indexing API can work in conjunction with the view API. When an \texttt{H5Vcreate}
-call is made for a group or dataset, an index attached to any dataset queried
+The indexing API can work in conjunction with the view creation. When an \texttt{H5Qapply}
+call is made on a given location, an index attached to any dataset queried
 for element value ranges will be used to speed up the query process and return
 a dataspace selection to the library for later use.
-
 There are different techniques for creating data element indices, and the most
@@
 group hierarchy.}.
-Instead, index objects are part of the metadata for the file itself. New index
-objects are created by passing an HDF5 container to be indexed and the index
-plugin ID to the \texttt{H5Xcreate} call.
+Instead, index objects are part of the metadata for the indexed dataset. New index
+objects are created by passing an HDF5 location (group or dataset) to be indexed
+and the index plugin ID to the \texttt{H5Xcreate} call.
 Alternatively an index may be created at the same time as a dataset gets created
@@
 callback will retrieve this stored information and make use of the corresponding
-index plugin for all subsequent operations. Similarly, calling \texttt{H5Dclose}
+index plugin for all subsequent operations\footnote{Note that the dataset's
+index object is opened only when a query call is made on the dataset.}.
+Similarly, calling \texttt{H5Dclose}
 will call the plugin index close callback and close the objects used to store
@@
 \label{fig:hdf5_index}
+\vspace{-20pt}
 \end{figure}
@@
 
-When a call to \texttt{H5Vcreate} is made, the index plugin query callback will be
+When a call to \texttt{H5Qapply} is made, the index plugin query callback will be
 invoked to create a selection of elements in the dataset that match the query
-parameters. Applications can also use the new \texttt{H5Dquery} routine defined below
-to directly
-execute a query on a particular dataset (accelerated by any index defined on the dataset),
+parameters. Applications can also directly use the internally called
+\texttt{H5Dquery} routine defined below
+to directly execute a query on a particular dataset (accelerated by any index defined on the dataset),
 and retrieve the selection that matches the query.
@@
 itself), the \texttt{get\_size} callback can query the amount of space that
-the index takes in the file and users may query that information using the
-corresponding \texttt{H5Xget\_size} routine.
+the index takes in the file and users may correspondingly query that information using the
+\texttt{H5Xget\_size} routine.
 
@@
 Implementations for FastBit and ALACRITY index packages are already
-present, as well as a brute force indexing plugin. Early performance results
+present, as well as a dummy brute force indexing plugin. Early performance results
 are presented in~\FigureRef{fig:indexing_perf}.
@@
 \label{fig:indexing_perf}
+\vspace{-20pt}
 \end{figure}
@@
 \item How to handle index updates when the specified index plugin is not available?
-(In traditional databases, stored procedures are saved with the data and
-therefore available at any time, but that is not the case here)
+\textit{In traditional databases, stored procedures are saved with the data and
+therefore available at any time, but that is not the case here.
 We could mark the index as out of date and rebuild the index when the plugin is
-available again.
+available again.}
 \item How to handle index queries when the specified index plugin is not
-available? We could fallback to another plugin and do a brute force query on the data.
+available? \textit{We could fallback to another plugin and do a brute force query on the data.}
 \end{enumerate}
@@
 callback using the associated metadata.
-
 %write
@@
 %     modify I/O loop
-
 Similarly, when a query is issued and needs to be answered, the chunks that
@@
 added to a global selection, which is then in turn returned to the user.
-
 Finally, when \texttt{H5Xremove} is called, the \texttt{delete} plugin callback is
@@
 from the previous interface:
-\begin{enumerate}
+\begin{itemize}
 \item Let the index creation be collective. This however implies having synchronization
@@
 a good solution either).
-\end{enumerate}
+\end{itemize}
 
@@
 
-\section{Conclusion}
-Document in progress.
-
-\section*{Revision History}
-\makerevisions
-
-%% References
-\bibliographystyle{ieeetr}
-\bibliography{analysis_ext}
-
-\end{document}
+%\section{Conclusion}
+%Document in progress.

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
First bunch of revisions to analysis extensions
Former-commit-id: 6e2f23896444cf11519cdb913e399220ffd38344

--- 2015-02-25 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
@@
 \documentclass[letterpaper,hyper]{THG_RFC}
-
-% Fonts
-\usepackage{ifluatex}
-\ifluatex
-  % Font
-  \usepackage{luatextra, xunicode, unicode-math}
-  \defaultfontfeatures{Ligatures=TeX}
-  \setmainfont[
-    UprightFont={*},
-    BoldFont={*-Bold},
-    ItalicFont={*-Italic},
-    BoldItalicFont={*-BoldItalic},
-    SlantedFont={*-Italic},
-    BoldSlantedFont={*-BoldItalic}
-  ]{CMU Serif}
-  \setsansfont[
-    UprightFont={*},
-    BoldFont={*-Bold},
-    ItalicFont={*-Oblique},
-    BoldItalicFont={*-BoldOblique}
-  ]{CMU Sans Serif}
-  \setmathfont[math-style=ISO, bold-style=ISO]{Asana Math}
-  \setmonofont[
-    UprightFont={*-Regular},
-    BoldFont={*-Bold},
-    ItalicFont={*-Italic},
-    BoldItalicFont={*-BoldItalic}
-  ]{CMU Typewriter}
-\else
-  \usepackage{lmodern} % times / lmodern / mathpazo / palatino
-  \usepackage[scaled=.95]{helvet}
-  \usepackage{courier}
-\fi
 
@@
 \usepackage{tikz}
-\usetikzlibrary{patterns, shapes, decorations.pathreplacing}
+\usetikzlibrary{patterns, shapes, positioning, decorations.pathreplacing,
+backgrounds, fit}
 \usepackage{gnuplot-lua-tikz}
@@
   numbers=left,
-  xleftmargin=20pt,
+  xleftmargin=1.8em,
+  frame=L,
+  framexleftmargin=0.2em,
+  rulecolor=\color{rulecolor},
   numberstyle=\tiny\color{gray},
@@
   breaklines=true,
-  basicstyle=\small\ttfamily,
+  basicstyle=\footnotesize\ttfamily,
   stringstyle=\itshape,
@@
     H5Qget_components, H5Qget_combine_op, H5Qencode, H5Qdecode,
+    H5Qapply,
     H5Screate_simple, H5Sclose, H5Sget_select_npoints,
-    H5Xregister, H5Xunregister, H5Xcreate, H5Xremove, H5Xget_count,
-    H5Vcreate, H5Vclose, H5Vget_location, H5Vget_query, H5Vget_counts,
-    H5Vget_attrs, H5Vget_objs, H5Vget_elem_regions
+    H5Xregister, H5Xunregister, H5Xcreate, H5Xremove, H5Xget_count, H5Xget_size,
+    H5Xget_info
     }
@@
 \author{Quincey Koziol}
-\date{February 25, 2015}
-\rfcversion{2014-07-17.v4}
-\revision{July 17, 2014}{Version 1 circulated for comment within The HDF Group.}
-\revision{August 20, 2014}{Version 2 circulated for comment within The HDF Group.}
-\revision{November 14, 2014}{Version 3 circulated for comment within The HDF Group.}
-\revision{February 25, 2015}{Version 4 edits and typo fixing.}
+\date{Oct 14, 2015}
+\rfcversion{2014-07-17.v6}
+\revision{Jul. 17, 2014}{Version 1 circulated for comment within The HDF Group.}
+\revision{Aug. 20, 2014}{Version 2 circulated for comment within The HDF Group.}
+\revision{Nov. 14, 2014}{Version 3 circulated for comment within The HDF Group.}
+\revision{Feb. 25, 2015}{Version 4 edits and typo fixing.}
+\revision{Jul. 24, 2015}{Version 5 edits to view object.}
+\revision{Oct. 14, 2015}{Version 6 rework of query/view sections.}
 
@@
 \begin{document}
-
-%% Add Attribute reference RFC
 
@@
 
-\section{Introduction}
-When working on large datasets, finding and selecting the interesting pieces of
-the data can be a cumbersome process. Currently, the HDF5 library enables the 
-application developer to select, read and write data but does not provide any 
-mechanism to select and retrieve pieces without prior knowledge of their
-content, or without the developer to provide the exact data coordinates that
-he is willing to access. To satisfy that need, one must be able
-to issue queries by specifying a data selection criteria. These queries,
-when applied to the data, can then generate a selection, which contains the coordinates
-that satisfy the query---this may imply accessing the data and selecting it,
-depending on the query condition satisfaction. To accelerate and facilitate this
-process (i.e., so that the data no longer needs to be directly accessed), one can
-use indexing techniques, which consist of generating an index and using that index
-to answer the query selection criteria and find the matching elements.
-
-We define in this RFC the components that can enable application developers to
-create complex and high-performance queries on both metadata and data elements
-within an HDF5 container and retrieve the results of applying those query
-operations. Support for these operations on HDF5 containers can be defined via:
-\begin{enumerate}
-\item New \textit{query} objects\footnote{Query and view objects are
-\textit{in-memory} objects, which therefore do not modify the content of the
-container.\label{fn:object}} and API routines, enabling the construction of
-query requests for execution on HDF5 containers;
-\item New \textit{view} objects\footref{fn:object} and API routines, which apply a query to an HDF5
-container and return a set of references into the container that fulfills
-the query criteria;
-\item New \textit{index} objects and API routines, which allows the creation of
-indices on the contents of HDF5 containers, to improve query performance.
-\end{enumerate}
-
-\section{Query Objects}
-Query objects are the foundation of the data analysis operations in HDF5 and
-can be built up from simple components in a programmatic way to create complex
-operations using \textit{Boolean} operations. The current API is presented
-below:
-
-{\lstsetc
-\begin{lstlisting}
-hid_t  H5Qcreate(H5Q_type_t query_type, H5Q_match_op_t match_op, ...);
-herr_t H5Qclose(hid_t query_id);
-hid_t  H5Qcombine(hid_t query1_id, H5Q_combine_op_t combine_op, hid_t query2_id);
-herr_t H5Qget_type(hid_t query_id, H5Q_type_t *query_type);
-herr_t H5Qget_match_op(hid_t query_id, H5Q_match_op_t *match_op);
-herr_t H5Qget_components(hid_t query_id, hid_t *subquery1_id, hid_t *subquery2_id);
-herr_t H5Qget_combine_op(hid_t query_id, H5Q_combine_op_t *op_type);
-herr_t H5Qencode(hid_t query_id, void *buf, size_t *nalloc);
-hid_t  H5Qdecode(const void *buf);
-\end{lstlisting}
-}
-
-The core query API is composed of
-two routines: \texttt{H5Qcreate} and \texttt{H5Qcombine}. \texttt{H5Qcreate}
-creates new queries, by specifying an aspect of an HDF5 container, such as
-data elements, link names, attribute names, etc., a match operator, such as
-$=$, $\neq$, $\leq$, $\geq$, and a value for the match operator.
-Created query objects can be serialized and deserialized using \texttt{H5Qencode}
-and \texttt{H5Qdecode} routines\footnote{Serialization/deserialization of queries
-were introduced so that queries can be sent through the network.}, and their
-content can be retrieved using the corresponding accessor routines.
-\texttt{H5Qcombine} combines two query objects into a
-new query object, using boolean operators such as $AND(\land)$ and $OR(\lor)$.
-Queries created with \texttt{H5Qcombine} can be used as input to further
-calls to \texttt{H5Qcombine}, creating more complex queries.
-
-For example, a single call to \texttt{H5Qcreate} could create a query object
-that would match data elements in any dataset within the container that are
-equal to the value $17$. Another call to \texttt{H5Qcreate} could create a
-query object that would match link names equal to $Pressure$.
-Calling \texttt{H5Qcombine} with the $\land$ operator and those two query
-objects would create a new query object that matched elements equal to $17$
-in HDF5 datasets with link names equal to $Pressure$.
-Creating the data analysis extensions to HDF5 using a \textit{programmatic
-interface} for defining queries avoids defining a text-based query language
-as a core component of the data analysis interface, and is more in keeping with
-the design and level of abstraction of the HDF5 API.
-The HDF5 data model is more complex than traditional database tables and a
-simpler query model would likely not be able to express the kinds of queries
-needed to extract the full set of components of an HDF5 container. A text-based
-query language (or GUI) could certainly be built on top of the query API
-defined here to provide a more user-friendly (as opposed to
-\textit{developer-friendly}) query syntax like $Pressure = 17$. However, we
-regard this as out-of-scope for now.
-
-\TableRef{tab:querycomb} describes the result types for atomic queries and
-combining queries of different types. Query results of $None$ type are rejected
-when \texttt{H5Qcombine} is called, causing it to return failure\footnote{Query
-results of $None$ type may be implemented with another result type in the
-future, once experience with the query framework is acquired and a meaningful
-grammar for those results are defined.}.
-
-\begin{table}[ht]\footnotesize
-\caption{Query combinations and associated result type.}
-\label{tab:querycomb}
-\begin{tabular}{ll} \toprule
-Query &
-Result Type\\ \midrule
-\texttt{H5Q\_TYPE\_DATA\_ELEM} & $Dataset~Element$ \\
-\texttt{H5Q\_TYPE\_ATTR\_VALUE} & $Attribute$ \\
-\texttt{H5Q\_TYPE\_ATTR\_NAME} & $Object$ \\
-\texttt{H5Q\_TYPE\_LINK\_NAME} & $Object$ \\
-$Dataset~Element \land Dataset~Element$ & $Dataset~Element$ \\
-$Dataset~Element \land Attribute$ & $None$ \\
-$Dataset~Element \land Object$ & $Dataset~Element$ \\
-$Attribute \land Attribute$ & $Attribute$ \\
-$Attribute \land Object$ & $Attribute$ \\
-$Object \land Object$ & $Object$ \\
-$Dataset~Element \lor Dataset~Element$ & $Dataset~Element$ \\
-$Dataset~Element \lor Attribute$ & $Combination$ \\
-$Dataset~Element \lor Object$ & $Combination$ \\
-$Dataset~Element \lor Combination$ & $Combination$ \\
-$Attribute \lor Attribute$ & $Attribute$ \\
-$Attribute \lor Object$ & $Combination$ \\
-$Attribute \lor Combination$ & $Combination$ \\
-$Object \lor Object$ & $Object$ \\
-$Object \lor Combination$ & $Combination$ \\
-$Combination \lor Combination$ & $Combination$ \\
-$Combination \land Dataset~Element$ & $None$ \\
-$Combination \land Attribute$ & $None$ \\
-$Combination \land Object$ & $None$ \\
-$Combination \land Combination$ & $None$ \\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\section{View Objects}
-Applying a query to an HDF5 container creates an HDF5 view object. HDF5 view
-objects are run-time, in-memory objects (i.e., not stored in a container) that
-consist of read-only references into the contents of the HDF5 container that
-the query was applied to. The current API is presented below:
-\todo{View API must be revised.}
-
-{\lstsetc
-\begin{lstlisting}
-hid_t  H5Vcreate(hid_t loc_id, hid_t query_id, hid_t vcpl_id);
-herr_t H5Vclose(hid_t view_id);
-herr_t H5Vget_location(hid_t view_id, hid_t *loc_id);
-herr_t H5Vget_query(hid_t view_id, hid_t *query_id);
-herr_t H5Vget_counts(hid_t view_id, hsize_t *attr_count, hsize_t *obj_count,
-  hsize_t *elem_region_count);
-herr_t H5Vget_attrs(hid_t view_id, hsize_t start, hsize_t count, hid_t attr_id[]);
-herr_t H5Vget_objs(hid_t view_id, hsize_t start, hsize_t count, hid_t obj_id[]);
-herr_t H5Vget_elem_regions(hid_t view_id, hsize_t start, hsize_t count,
-  hid_t dataset_id[], hid_t dataspace_id[]);
-\end{lstlisting}
-}
-
-View objects are created with \texttt{H5Vcreate}, which applies a query to an
-HDF5 container, group hierarchy, or individual object and produces the view
-object as a result. The attributes, objects, and/or data elements referenced
-within a view can be retrieved by further API calls. Note that currently,
-attribute references are not available, this feature will be added in order to
-support views that contain attribute references\footnote{See RFC 201X-XX-XX.vX.}.
-
-\begin{figure}
-\input{pics/hdf5_view1}
-\caption{HDF5 container example.}
-\label{fig:hdf5_view1}
-\end{figure}
-
-For example, starting with the HDF5 container described in~\FigureRef{fig:hdf5_view1},
-applying the $link\_name = Pressure$ query (described above) would result
-in the view shown in~\FigureRef{fig:hdf5_view2}, highlighted in blue.
-
-\begin{figure}
-\input{pics/hdf5_view2}
-\caption{HDF5 container example with query $link\_name = Pressure$ applied.}
-\label{fig:hdf5_view2}
-\end{figure}
-
-Alternatively, applying the $data\_element = 17$ query (described above) would
-result in the view shown in~\FigureRef{fig:hdf5_view3}, highlighted in blue.
-
-\begin{figure}
-\input{pics/hdf5_view3}
-\caption{HDF5 container example with query $data\_element = 17$ applied.}
-\label{fig:hdf5_view3}
-\end{figure}
-
-Finally, applying the combined $(link\_name = Pressure)\land(data\_element = 17)$
-query (described above) would result in the view shown in~\FigureRef{fig:hdf5_view4},
-highlighted in blue.
-
-\begin{figure}
-\input{pics/hdf5_view4}
-\caption{HDF5 container example with query $(link\_name = Pressure)\land(data\_element = 17)$ applied.}
-\label{fig:hdf5_view4}
-\end{figure}
-
-Views can be thought of as containing a set of HDF5 references (object,
-dataset region or attribute references) to components of the underlying
-container, retaining the context of the original container. For example, the
-view containing the results of the $(link\_name = Pressure)\land(data\_element = 17)$
-query will contain three dataset region references, which
-can be retrieved from the view object and probed for the dataset and selection
-containing the elements that match the query with the existing \texttt{H5Rdereference}
-and \texttt{H5Rget\_region} API calls. Note that selections returned from a region
-reference retain the underlying dataset's dimensionality and coordinates---they
-are not \textit{flattened} into a 1-D series of elements. The selection returned
-from a region reference can also be applied to a different dataset in the container,
-allowing a query on pressure values to be used to extract temperature values,
-for example.
-
-\section{Index Objects}
-Index objects are designed to accelerate creation of view objects from
-frequently occurring query operations.
-For example, if the $(link\_name = Pressure)\land(data\_element = 17)$ query
-(previously described) is going to be frequently executed on the container, indices
-could be created in that container, which would speed up the creation of views
-when querying for link names and for data element values. Indices created for
-accelerating the $link\_name = Pressure$ or $data\_element = 17$ queries
-would also improve view creation for the more complex
-$(link\_name = Pressure)\land(data\_element = 17)$ query.
-
-Although creating indices for metadata components of queries, such as link or
-attribute names, is possible, we focus on index creation for dataset elements,
-as they represent the largest volume of data in typical HPC application usage of
-HDF5. Queries with metadata components execute properly,
-\todo{Metadata indexing must be added.} but are not able to be accelerated
-with an index currently.
-
-The indexing API can work in conjunction with the view API. When an \texttt{H5Vcreate}
-call is made for a group or dataset, an index attached to any dataset queried
-for element value ranges will be used to speed up the query process and return
-a dataspace selection to the library for later use.
-
-There are different techniques for creating data element indices, and the most
-efficient method will vary depending on the type of the data that is to be
-indexed, its layout, etc. A new interface for the HDF5 library that uses a
-plugin mechanism is therefore defined.
-
-\subsection{Indexing Interface and Plugins}
-
-This interface is defined for adding third-party indexing plugins,
-such as FastBit~\cite{Wu05}, ALACRITY~\cite{alacrity13}, etc.
-The interface provides indexing plugins with efficient access to the contents of
-the container for both the creation and the maintenance of indices. In addition,
-the interface allows third-party plugins to create private data structures
-within the container for storing the contents of the index.
-The current API as well as the plugin interface are presented below:
-
-{\lstsetc
-\begin{lstlisting}
-herr_t  H5Xregister(const H5X_class_t *idx_class);
-herr_t  H5Xunregister(unsigned plugin_id);
-herr_t  H5Xcreate(hid_t scope_id, unsigned plugin_id, hid_t xcpl_id);
-herr_t  H5Xremove(hid_t scope_id, unsigned n /* Index n to be removed */);
-herr_t  H5Xget_count(hid_t scope_id, hsize_t *idx_count);
-herr_t  H5Xget_info(hid_t scope_id, unsigned n, H5X_info_t *info);
-hsize_t H5Xget_size(hid_t scope_id);
-
-typedef struct {
-    unsigned version;     /* Version number of the index plugin class struct */
-                          /* (Should always be set to H5X_CLASS_VERSION, which
-                           *  may vary between releases of HDF5 library) */
-    unsigned id;          /* Index ID (assigned by The HDF Group, for now) */
-    const char *idx_name; /* Index name (for debugging only, currently) */
-    H5X_type_t type;      /* Type of data indexed by this plugin */
-
-    /* Callbacks, described above */
-    void *(*create)(hid_t dataset_id, hid_t xcpl_id, hid_t xapl_id,
-        size_t *metadata_size, void **metadata);
-    herr_t (*remove)(hid_t dataset_id, size_t metadata_size, void *metadata);
-    void *(*open)(hid_t dataset_id, hid_t xapl_id, size_t metadata_size,
-        void *metadata);
-    herr_t (*close)(void *idx_handle);
-    herr_t (*copy)(hid_t src_dataset_id, hid_t dest_dataset_id, hid_t xcpl_id,
-        hid_t xapl_id, size_t src_metadata_size, void *src_metadata,
-        size_t *dest_metadata_size, void **dest_metadata);
-    herr_t (*pre_update)(void *idx_handle, hid_t dataspace_id, hid_t xxpl_id);
-    herr_t (*post_update)(void *idx_handle, const void *buf, hid_t dataspace_id,
-        hid_t xxpl_id);
-    herr_t (*query)(void *idx_handle, hid_t query_id, hid_t xxpl_id,
-        hid_t *dataspace_id);
-    herr_t (*refresh)(void *idx_handle, size_t *metadata_size, void **metadata);
-    herr_t (*get_size)(void *idx_handle, hsize_t *idx_size);
-} H5X_class_t;
-\end{lstlisting}
-}
-
-Index objects are stored in the HDF5 container that they apply to, but are not
-visible in the container's group hierarchy\footnote{Plugin developers, note that
-the HDF5 library's existing anonymous dataset and group creation calls can be
-used to create objects in HDF5 files that are not visible in the container's
-group hierarchy.}.
-Instead, index objects are part of the metadata for the file itself. New index
-objects are created by passing an HDF5 container to be indexed and the index
-plugin ID to the \texttt{H5Xcreate} call.
-Alternatively an index may be created at the same time as a dataset gets created
-by passing a property to the dataset creation property list.
-Index information (such as plugin ID and index metadata) is stored at index
-creation time\footnote{Adding index information introduces a file format change.},
-and when the user later calls \texttt{H5Dopen}, the plugin open
-callback will retrieve this stored information and make use of the corresponding
-index plugin for all subsequent operations. Similarly, calling \texttt{H5Dclose}
-will call the plugin index close callback and close the objects used to store
-the index data.
-
-\begin{figure}
-\input{pics/hdf5_index}
-\caption{Index information (plugin ID and metadata) is stored along the object header.}
-\label{fig:hdf5_index}
-\end{figure}
-
-When a call to \texttt{H5Dwrite} is made, the index plugin \texttt{pre\_update} and
-\texttt{post\_update} callbacks will be triggered, allowing efficient index
-update by first telling the index plugin the region that is going to be updated
-with new data, and then realizing the actual index update, after the dataset
-write has completed. This allows various optimization to be made, depending on
-the data selection passed and the index plugin used. For example, a plugin could
-store the region and defer the actual index update until the dataset is closed,
-hence saving repeated index computation/update calls.
-
-When a call to \texttt{H5Vcreate} is made, the index plugin query callback will be
-invoked to create a selection of elements in the dataset that match the query
-parameters. Applications can also use the new \texttt{H5Dquery} routine defined below
-to directly
-execute a query on a particular dataset (accelerated by any index defined on the dataset),
-and retrieve the selection that matches the query.
-
-{\lstsetc
-\begin{lstlisting}
-herr_t H5Dquery(hid_t dset_id, hid_t space_id, hid_t query_id, hid_t xapl_id,
-    hid_t *space_id);
-\end{lstlisting}
-}
-
-Because the amount of space taken by the index cannot be directly retrieved by
-the user (since the datasets storing the indices are known only by the plugin
-itself), the \texttt{get\_size} callback can query the amount of space that
-the index takes in the file and users may query that information using the
-corresponding \texttt{H5Xget\_size} routine.
-
-\subsubsection{Current and future plugins}
-
-Implementations for FastBit and ALACRITY index packages are already
-present, as well as a brute force indexing plugin. Early performance results
-are presented in~\FigureRef{fig:indexing_perf}.
-
-\begin{figure}
-\input{plots/indexing_perf}
-\caption{Indexing performance.}
-\label{fig:indexing_perf}
-\end{figure}
-
-In the future more plugins will be added, with or without external dependency
-(e.g., PyTables indexing, bitmap indexing).
-To satisfy that need, dynamic plugin loading and registration will be supported,
-allowing external libraries to plug to the current interface.
-
-\subsection{Limitations}
-
-There are some existing limitations in the use of indices in the current
-implementation: FastBit and ALACRITY do not support incremental updates,
-an index is a shared resource for a dataset. Taken together, these conspire to
-put limits on application updates to datasets with indices.
-Additionally, because FastBit and ALACRITY do not allow incremental updates to
-an index, each modification to an existing index forces the index to be entirely
-rebuilt. The limitation in FastBit and ALACRITY will need to be addressed in
-the base packages' implementation, so that incremental updates
-to their index information can be made.
-
-\subsubsection*{Questions}
-Some questions are still open regarding the handling of indices:
-\begin{enumerate}
-%\item How could an index be built and queried in parallel for a dataset that already exists?
-\item How to handle index updates when the specified index plugin is not available?
-(In traditional databases, stored procedures are saved with the data and
-therefore available at any time, but that is not the case here)
-We could mark the index as out of date and rebuild the index when the plugin is
-available again.
-\item How to handle index queries when the specified index plugin is not
-available? We could fallback to another plugin and do a brute force query on the data.
-\end{enumerate}
-
-\subsection{Support for HDF5 Compound Types}
-
-In a simple scenario, the HDF5 datatype used for creating the dataset can be defined
-as a native and simple type. Therefore, building an index on this dataset implies
-building that index from the entire dataset. However, in more complex scenarios, the
-dataset may have been created by using a compound datatype, hence defining
-multiple fields composed of native and simple datatypes within that same dataset.
-Consequently, creating an index from that dataset requires the user to select a
-particular field to be indexed, which may lead to having multiple indices per dataset
-depending on the number of fields that it contains. This can be done by passing
-the \texttt{datatype\_id} of the field to be indexed to the \texttt{xcpl\_id},
-the index creation property list, of the \texttt{H5Xcreate} call, which passes
-it down to the plugin \texttt{create} callback. As multiple fields can be defined,
-the field \texttt{datatype\_id} must be stored along with the existing metadata, within the
-\texttt{idx\_info} message (see~\FigureRef{fig:hdf5_index}) so that the index
-associated to the field can be retrieved at the time of the query.
-When doing a query, the compound type is passed to the \texttt{H5Qcreate} call.
-The corresponding index is then used and the query is passed to the \texttt{query}
-callback of the plugin.
-
-Consequently, when removing an index, one may choose to remove the index that
-corresponds to a particular field. This can be achieved by calling \texttt{H5Xget\_info},
-compare the datatype returned within the info structure, and pass the index number
-that needs to be removed.
-
-\subsection{Support for HDF5 Chunking}
-
-To support indexing of HDF5 chunks, we make each chunk a local \textit{sub-dataset}
-of the original dataset. In that sense, handling every chunk can be seen as handling
-a dataset from the indexing plugin point of view. If the dataset is chunked,
-at the time of the index creation, we create a B-tree\footnote{The B-tree could also
-be replaced by a map object.} (physically
-stored on disk) that maps the coordinates of the chunks to the index plugin metadata.
-When the \texttt{create} callback is called (by representing the chunk as
-a local dataset, i.e., making the dataset layout point to the address of the chunk),
-metadata information is returned and stored.
-In the case of contiguous datasets, the index metadata as well as the index plugin ID is
-stored within the dataset header of the index info message (see~\FigureRef{fig:hdf5_index}).
-In the case of chunked datasets, multiple metadata that correspond to each index created
-from each chunck may be accessed. Therefore, only the address of the B-tree that contains the 
-metadata pieces for each chunk is stored in that header message and the index
-metadata itself is stored in the B-tree.
-
-When the dataset is opened and the index reopened, we can lookup the index
-information in the B-tree that corresponds to each chunk and call the \texttt{open}
-callback using the associated metadata.
-
-%write
-%   if (chunked)
-%     modify I/O loop
-
-Similarly, when a query is issued and needs to be answered, the chunks that
-correspond to the selection passed to the \texttt{H5Dquery} call are selected
-and their index is used to answer that query. The selection returned is then
-added to a global selection, which is then in turn returned to the user.
-
-Finally, when \texttt{H5Xremove} is called, the \texttt{delete} plugin callback is
-invoked for each chunk, by using the index metadata information stored in the B-tree.
-
-\subsection{Support for Parallel Indexing}
-
-An important design choice to support parallel indexing is to give as much
-freedom as possible to the indexing plugin developer so that in the case when
-the indexing library supports parallel indexing, it is still possible to take
-advantage of it. Three options are available to support parallel indexing
-from the previous interface:
-\begin{enumerate}
-\item Let the index creation be collective. This however implies having synchronization
-points, which is the main constraint.
-\item Let the index creation be independent. However, creating datasets to
-store the index data must be done collectively\footnote{An option could be to use
-the metadata server VOL plugin but this option is not easily doable yet.}.
-\item Make the index creation in two phases. One that consists of
-building the index in parallel, independently, and gathering the information (index size, etc)
-at the end. The other that consists of letting the dataset creation be done by a master
-process, which can then let the other processes write the index data independently.
-There could however be a memory constraint in this case if the index data has to
-be kept in memory between these two phases (though building the index twice is not
-a good solution either).
-\end{enumerate}
-
-Changes in the plugin interface include passing the parallel context to the
-callback (MPI communicator), which can be done by using the index access property
-list.
-In the case of chunked datasets, one may also want to operate on several chunks
-at the same time, in parallel. This can be done by passing a list of IDs that
-corresponds to each chunk to the callbacks. However, this also makes the plugin
-interface more heavy.
-
-\section{HDF5 and tools}
-
-Existing HDF5 tools must be compatible and take into account the existence of
-indices in the file if there are any. For reference, the following behavior for
-the tools is given:
-
-\begin{itemize}
-\item h5copy: copy
-\item h5dump: report index information
-\item h5ls: report index information
-\item h5diff: ignore index information?
-\item h5repack: copy index information / or generate index
-\item h5edit: ignore index information?
-\item h5toh4: ignore index information?
-\item h5import: ignore index information
-\end{itemize}
-
-Additional tools for indexing data and answering queries will also be added
-in the future.
-
-\section{Usage Example}
-
-In the following example, we show how one can make use of the query and
-indexing interface to retrieve a dataspace selection within a dataset.
-For simplicity's sake, we first create a dataset within the file, then open it to
-create and attach a new index, in order to finally query data from it.
-Note that for convenience, calls to directly read data that corresponds to the
-result of the index query may be moved to the high-level API in the future.
-
-{\lstsetc
-\begin{lstlisting}
-#define NTUPLES 256
-
-int
-main(int argc, char *argv[])
-{
-    float data[NTUPLES];
-    hsize_t dims[1] = {NTUPLES};
-    hid_t t file_id, dataspace_id, dataset_id;
-    hid_t query_id, result_space_id;
-    size_t result_npoints;
-    float *result;
-    int i;
-
-    /* Initialize data. */
-    for(i = 0; i < NTUPLES; i++) data[i] = (float) i;
-
-    /* Create file. */
-    file_id = H5Fcreate(file_name, H5F_ACC_TRUNC, H5P_DEFAULT, H5P_DEFAULT);
-
-    /* Create the data space for the dataset. */
-    dataspace_id = H5Screate_simple(rank, dims, NULL);
-
-    /* Create dataset. */
-    dataset_id = H5Dcreate(file_id, "Pressure", H5T_NATIVE_FLOAT, dataspace_id,
-        H5P_DEFAULT, H5P_DEFAULT, H5P_DEFAULT);
-
-    /* Write dataset. */
-    H5Dwrite(dataset_id, H5T_NATIVE_FLOAT, H5S_ALL, H5S_ALL, H5P_DEFAULT, data);
-
-    /* Close the dataset. */
-    H5Dclose(dataset_id);
-
-    /* Close dataspace. */
-    H5Sclose(dataspace_id);
-
-    /* Open dataset. */
-    dataset_id = H5Dopen(file_id, "Pressure", H5P_DEFAULT);
-
-    /* Create index using FastBit. */
-    H5Xcreate(file_id, H5X_PLUGIN_FASTBIT, dataset_id, H5P_DEFAULT);
-
-    /* Close the dataset. */
-    H5Dclose(dataset_id);
-
-    /* Create a simple query */
-    query_id = H5Qcreate(H5Q_TYPE_DATA_ELEM, H5Q_MATCH_EQUAL, H5T_NATIVE_FLOAT,
-        &query_value);
-
-    /* Open dataset. */
-    dataset_id = H5Dopen(file_id, "Pressure", H5P_DEFAULT);
-
-    /* Use query to select elements in the dataset. */
-    result_space_id = H5Dquery(dataset_id, query_id);
-
-    /* Allocate space to read data. */ 
-    result_npoints = (size_t) H5Sget_select_npoints(result_space_id);
-    result = malloc(result_npoints * sizeof(float));
-
-    /* Read data using result_space_id. */
-    H5Dread(dataset_id, H5T_NATIVE_FLOAT, H5S_ALL, result_space_id,
-        H5P_DEFAULT, result);
-
-    /* Use result. */
-
-    /* Free result. */
-    free(result);
-
-    /* Close the dataset. */
-    H5Dclose(dataset_id);
-
-    /* Close dataspace. */
-    H5Sclose(result_space_id);
-
-    /* Close query. */
-    H5Qclose(query_id);
-
-    /* Close the file. */
-    H5Fclose(file_id);
-}
-\end{lstlisting}
-}
-
-\section{Conclusion}
-Document in progress.
+\input{analysis_ext-body}
 
@@
 %% References
-\bibliographystyle{ieeetr}
+\bibliographystyle{abbrv}
 \bibliography{analysis_ext}

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_index.tex
Update analysis extension RFC to revision 3
Former-commit-id: 03d763e94e151b89b3092f5198c962c4dc273817
First bunch of revisions to analysis extensions
Former-commit-id: 6e2f23896444cf11519cdb913e399220ffd38344

@@
 
-\node[rectangle, minimum height=4cm, minimum width=14cm] (app) {};
+\node[rectangle, minimum width=14cm] (app) {};
 \node[rectangle, minimum height=3.6cm, minimum width=6.4cm, right=2mm of app.west] (cache) {};
-\node[rectangle, draw=rulecolor, very thick, minimum height=3.1cm, minimum width=2.9cm, right=2mm of cache.west] (cachecol1) {};
-\node[rectangle, minimum height=3.6cm, minimum width=2.9cm, right=2mm of cachecol1.east] (cachecol2) {};
-\node[textBox, minimum width=2.5cm, minimum height=0.7cm, below=2mm of cachecol1.north] (cache1) {Dataset header};
+
+\node[textBox, minimum width=2.5cm, minimum height=0.7cm, right=2mm of cache.west, text width=3cm] (cache1) {Dataset header (\texttt{idx\_info} message)};
 \node[headerBox, minimum width=2.5cm, below=-1pt of cache1] (cache2) {\dots};
@@
 
-\node[fileBox, minimum height=1cm, minimum width=14cm, below=5mm of app] (file) {};
+\node[rectangle, draw=rulecolor, very thick, fit=(cache1) (cache6)] (cachecol1) {};
+
+\node[fileBox, minimum height=1cm, minimum width=14cm, below=80pt of app] (file) {};
 \node[textBox, minimum height=1cm, minimum width=2cm, right=4mm of file.west] (filetitle) {File};

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view.tex
First bunch of revisions to analysis extensions
Former-commit-id: 6e2f23896444cf11519cdb913e399220ffd38344

\tikzstyle{groupBox} = [draw, ellipse, fill=white, minimum size=20pt,
  text centered, font=\footnotesize\sffamily, text width=20pt, inner sep=0]

\tikzstyle{textBox} = [fill=white, inner sep=2pt, text centered, font=\footnotesize\sffamily]

\tikzstyle{link} = [->, thick, >=stealth', shorten <=1pt, shorten >=1pt]

\pgfmathsetseed{1}

\def\drawdataset#1{%
\begin{scope}[#1]
  \foreach \y in {-0.5} {
      \foreach \x in {-2.5,-1.5,-0.5,0.5,1.5} {
          \path[fill=white, draw] (\x,\y) rectangle ++(1,1);
      }
  }
\end{scope}
}

\begin{tikzpicture}

% View
\node[groupBox] (view) {/};

% Refs
\node[below=30pt of view, inner sep=0] (viewgroup) {};

\node[rectangle, text height=7pt, left=70pt of viewgroup, inner sep=0] (obj_ref) {};
\drawdataset{shift=(obj_ref.south), scale=0.3}
\node[rectangle, text height=7pt, below=10pt of viewgroup, inner sep=0] (reg_ref) {};
\drawdataset{shift=(reg_ref), scale=0.3}
\node[rectangle, text height=7pt, right=70pt of viewgroup, inner sep=0] (attr_ref) {};
\drawdataset{shift=(attr_ref.south), scale=0.3}
\node[left=12pt of obj_ref] (g1) {};
\node[right=12pt of attr_ref] (g2) {};

% Links
\draw[link] (view) -- node [textBox] {Obj\_refs} (obj_ref);
\draw[link] (view) -- node [textBox] {Reg\_refs} (reg_ref);
\draw[link] (view) -- node [textBox] {Attr\_refs} (attr_ref);

\begin{scope}[on background layer, shape aspect=.10]
\tikzset{every node/.style={cylinder, shape border rotate=90, draw}}
\node [fit=(view) (obj_ref) (reg_ref) (attr_ref) (g1) (g2)] {};
\end{scope}

%\node [minimum width=1.5cm] at (1.5,0) {B};
\end{tikzpicture}

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view1.tex
First bunch of revisions to analysis extensions
Former-commit-id: 6e2f23896444cf11519cdb913e399220ffd38344

@@
 \tikzstyle{groupBox} = [draw, ellipse, fill=white, minimum size=20pt,
-  text centered, font=\footnotesize\sffamily, text width=20pt, inner sep=0]
+  text centered, font=\sffamily, text width=20pt, inner sep=0]
 
-\tikzstyle{textBox} = [fill=white, inner sep=2pt, text centered, font=\footnotesize\sffamily]
+\tikzstyle{textBox} = [fill=white, inner sep=2pt, text centered, font=\sffamily]
 
@@
 % Root
-\node[groupBox] (root) {root};
+\node[groupBox] (root) {/};
 
@@
 \node[below=30pt of group0, inner sep=0] (datasetg0) {};
-\node[rectangle, text height=25pt, left=40pt of datasetg0, inner sep=0] (tempg0) {};
+\node[rectangle, text height=25pt, left=45pt of datasetg0, inner sep=0] (tempg0) {};
 \drawdataset{shift=(tempg0.south), scale=0.3}
-\node[rectangle, text height=25pt, right=40pt of datasetg0, inner sep=0] (presg0) {};
+\node[rectangle, text height=25pt, right=45pt of datasetg0, inner sep=0] (presg0) {};
 \drawdataset{shift=(presg0.south), scale=0.3}
@@
 \node[below=30pt of group1, inner sep=0] (datasetg1) {};
-\node[rectangle, text height=25pt, left=40pt of datasetg1, inner sep=0] (tempg1) {};
+\node[rectangle, text height=25pt, left=45pt of datasetg1, inner sep=0] (tempg1) {};
 \drawdataset{shift=(tempg1.south), scale=0.3}
-\node[rectangle, text height=25pt, right=40pt of datasetg1, inner sep=0] (presg1) {};
+\node[rectangle, text height=25pt, right=45pt of datasetg1, inner sep=0] (presg1) {};
 \drawdataset{shift=(presg1.south), scale=0.3}
@@
 \node[below=30pt of group2, inner sep=0] (datasetg2) {};
-\node[rectangle, text height=25pt, left=40pt of datasetg2, inner sep=0] (tempg2) {};
+\node[rectangle, text height=25pt, left=45pt of datasetg2, inner sep=0] (tempg2) {};
 \drawdataset{shift=(tempg2.south), scale=0.3}
-\node[rectangle, text height=25pt, right=40pt of datasetg2, inner sep=0] (presg2) {};
+\node[rectangle, text height=25pt, right=45pt of datasetg2, inner sep=0] (presg2) {};
 \drawdataset{shift=(presg2.south), scale=0.3}

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view3.tex
Updates to analysis RFC
Former-commit-id: 6fb57a85f099a15da82e1a2b3d94ecf88385f5c0
First bunch of revisions to analysis extensions
Former-commit-id: 6e2f23896444cf11519cdb913e399220ffd38344

--- 2014-08-18 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view1.tex
@@
       \foreach \x in {-2.5,-1.5,-0.5,0.5,1.5} {
-          \path[fill=white, draw] (\x,\y) rectangle ++(1,1);
+          \pgfmathparse{less(50,rnd*70)*100}
+          \pgfmathtruncatemacro{\fillcolor}{\pgfmathresult}
+          \colorlet{selectcolor}{rulecolor!\fillcolor!white}
+          \path[fill=selectcolor, draw] (\x,\y) rectangle ++(1,1);
       }

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view4.tex
Updates to analysis RFC
Former-commit-id: 6fb57a85f099a15da82e1a2b3d94ecf88385f5c0
First bunch of revisions to analysis extensions
Former-commit-id: 6e2f23896444cf11519cdb913e399220ffd38344

--- 2014-08-18 RFCs/HDF5_Library/AnalysisExt/pics/hdf5_view1.tex
@@
 
-\def\drawdataset#1{%
+\def\drawdataset#1#2{%
 \begin{scope}[#1]
@@
       \foreach \x in {-2.5,-1.5,-0.5,0.5,1.5} {
-          \path[fill=white, draw] (\x,\y) rectangle ++(1,1);
+          \pgfmathparse{less(50,rnd*70)*100}
+          \pgfmathtruncatemacro{\fillcolor}{\pgfmathresult}
+          \colorlet{selectcolor}{#2!\fillcolor!white}
+          \path[fill=selectcolor, draw] (\x,\y) rectangle ++(1,1);
       }
@@
 \node[below=30pt of group0, inner sep=0] (datasetg0) {};
-\node[rectangle, text height=25pt, left=40pt of datasetg0, inner sep=0] (tempg0) {};
-\drawdataset{shift=(tempg0.south), scale=0.3}
-\node[rectangle, text height=25pt, right=40pt of datasetg0, inner sep=0] (presg0) {};
-\drawdataset{shift=(presg0.south), scale=0.3}
+\node[rectangle, text height=25pt, left=45pt of datasetg0, inner sep=0] (tempg0) {};
+\drawdataset{shift=(tempg0.south), scale=0.3}{white}
+\node[rectangle, text height=25pt, right=45pt of datasetg0, inner sep=0] (presg0) {};
+\drawdataset{shift=(presg0.south), scale=0.3}{rulecolor}
 
@@
 \node[below=30pt of group1, inner sep=0] (datasetg1) {};
-\node[rectangle, text height=25pt, left=40pt of datasetg1, inner sep=0] (tempg1) {};
-\drawdataset{shift=(tempg1.south), scale=0.3}
-\node[rectangle, text height=25pt, right=40pt of datasetg1, inner sep=0] (presg1) {};
-\drawdataset{shift=(presg1.south), scale=0.3}
+\node[rectangle, text height=25pt, left=45pt of datasetg1, inner sep=0] (tempg1) {};
+\drawdataset{shift=(tempg1.south), scale=0.3}{white}
+\node[rectangle, text height=25pt, right=45pt of datasetg1, inner sep=0] (presg1) {};
+\drawdataset{shift=(presg1.south), scale=0.3}{rulecolor}
 
@@
 \node[below=30pt of group2, inner sep=0] (datasetg2) {};
-\node[rectangle, text height=25pt, left=40pt of datasetg2, inner sep=0] (tempg2) {};
-\drawdataset{shift=(tempg2.south), scale=0.3}
-\node[rectangle, text height=25pt, right=40pt of datasetg2, inner sep=0] (presg2) {};
-\drawdataset{shift=(presg2.south), scale=0.3}
+\node[rectangle, text height=25pt, left=45pt of datasetg2, inner sep=0] (tempg2) {};
+\drawdataset{shift=(tempg2.south), scale=0.3}{white}
+\node[rectangle, text height=25pt, right=45pt of datasetg2, inner sep=0] (presg2) {};
+\drawdataset{shift=(presg2.south), scale=0.3}{rulecolor}
 

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
A few fixes to previous commit
Former-commit-id: 66a36b3bc72dbb39f4f492b15a12021995ef594e

@@
   morekeywords={main, size_t, malloc, free,
-    hsize_t, hid_t, herr_t, H5X_class_t, H5X_type_t, H5Q_combine_op_t,
-    H5Q_type_t, H5Q_match_op_t,
+    hsize_t, hid_t, herr_t,
+    H5X_class_t, H5X_type_t, H5X_info_t,
+    H5Q_combine_op_t, H5Q_type_t, H5Q_match_op_t,
     H5Fcreate, H5Fclose,

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/analysis_ext-body.tex
A few fixes to previous commit
Former-commit-id: 66a36b3bc72dbb39f4f492b15a12021995ef594e
Update analysis RFC with cross-container queries and add latexdiff support
Former-commit-id: a8e6bf95a7c3ec932a96439f46463b0f574ef90b

@@
 
+\subsection{Cross Container Queries}
+
+In the case where multiple containers (files, locations) need to be queried,
+a single query operation may be used instead of performing individual queries
+on each container. Performing queries across multiple containers with a single
+operation can enable analysis operations to generate an aggregated
+view of query results more easily, as well as enable a silent execution of the
+query in parallel, thereby reducing the time to generate a view from multiple containers.
+
+The first extension to the previously described \texttt{H5Qapply} call is defined
+with the following routine, \texttt{H5Qapply\_multi}:
+
+{\lstsetc
+\begin{lstlisting}
+hid_t H5Qapply_multi(size_t loc_count, hid_t *loc_ids, hid_t query_id,
+  unsigned *result, hid_t vcpl_id);
+\end{lstlisting}
+}
+
+Location IDs specified may be entire containers, groups in a container's hierarchy
+or individual datasets within a container. These locations may reside within the
+same container, or in multiple containers. Additionally, the \texttt{H5Qapply\_str}
+routine allows the user to provide container names instead of HDF5 locations:
+
+{\lstsetc
+\begin{lstlisting}
+hid_t H5Qapply_str(size_t cont_count, const char *cont_name[], hid_t query_id,
+  unsigned *result, hid_t vcpl_id);
+\end{lstlisting}
+}
+
+As a direct consequence, one may want to pass queries that match a particular
+container name. Therefore the \texttt{H5Q\_TYPE\_CONT\_NAME} query type can be
+used to construct a query that matches this new condition. The matching
+condition may be passed in the form of a file name or a regular
+expression.
+
+(Optional?) Apply query on all the containers of a given directory with \texttt{H5Qapply\_dir}
+{\lstsetc
+\begin{lstlisting}
+hid_t H5Qapply_dir(const char *path, hid_t query_id, unsigned *result, hid_t vcpl_id);
+\end{lstlisting}
+}
+
+Applying cross-container queries creates a view that contains references
+to external locations (as opposed to the previous \texttt{H5Qapply} call where
+references were internal). Therefore, the extended HDF5 reference object
+also includes a container identifier so that, when the view result is
+given back to the user, a subsequent call to \texttt{H5Rdereference} can return
+a reference to an object within an externally referenced container\footnote{
+As a result, the HDF5 reference API does not require any changes.}.
+
+Parallel execution of the query optional? \textit{Pass hint for parallel execution
+through property list.}
+
 \section{Index Objects}
@@
 creation of views when querying for link names and for data element values.
-Indices created for accelerating the $link\_name = Pressure$ or $data\_element = 17$ queries
+Indices created for accelerating the  ``$\mathrm{(link\_name = Pressure)}$'' or
+``$\mathrm{(data\_element}$ $\mathrm{= 17)}$'' queries
 would also improve view creation for the more complex
-$(link\_name = Pressure)\land(data\_element = 17)$ query.
+``$\mathrm{(link\_name = Pressure)}$ $\mathrm{\land}$
+$\mathrm{(data\_element = 17)}$'' query.
 Although creating indices for metadata components of queries, such as link or
@@
 \begin{lstlisting}
-herr_t H5Dquery(hid_t dset_id, hid_t space_id, hid_t query_id, hid_t xapl_id,
-    hid_t *space_id);
+hid_t H5Dquery(hid_t dset_id, hid_t space_id, hid_t query_id, hid_t xapl_id);
 \end{lstlisting}
@@
 
-\subsection{Support for HDF5 Compound Types}
+\subsection{Support for HDF5 Compound Types (TBD)}
 
@@
 
-\subsection{Support for HDF5 Chunking}
+\subsection{Support for HDF5 Chunking (TBD)}
 
@@
 
-\subsection{Support for Parallel Indexing}
+\subsection{Support for Parallel Indexing (TBD)}
 
@@
     /* Use query to select elements in the dataset. */
-    result_space_id = H5Dquery(dataset_id, query_id);
+    result_space_id = H5Dquery(dataset_id, H5S_ALL, query_id, H5P_DEFAULT);
 
@@
     /* Use result. */
+    [...]
 

### 2015-10-15 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
Update analysis RFC with cross-container queries and add latexdiff support
Former-commit-id: a8e6bf95a7c3ec932a96439f46463b0f574ef90b

--- 2015-10-15 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
@@
 \def\lstsetc{\lstset{language=C,
-  numbers=left,
+  %numbers=left,
   xleftmargin=1.8em,
@@
     H5Qget_components, H5Qget_combine_op, H5Qencode, H5Qdecode,
-    H5Qapply,
+    H5Qapply, H5Qapply_multi, H5Qapply_str, H5Qapply_dir,
     H5Screate_simple, H5Sclose, H5Sget_select_npoints,
@@
 \author{Quincey Koziol}
-\date{Oct 14, 2015}
-\rfcversion{2014-07-17.v6}
+\date{Oct 15, 2015}
+\rfcversion{2014-07-17.v7}
 \revision{Jul. 17, 2014}{Version 1 circulated for comment within The HDF Group.}
@@
 \revision{Oct. 14, 2015}{Version 6 rework of query/view sections.}
+\revision{Oct. 15, 2015}{Version 7 first draft of cross-container queries.}
 

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/gdata2.js

@@ -1,1 +1,1 @@
-gXMLBuffer ="<?xml version=\"1.0\" encoding=\"utf-8\" ?><data>   <entry name=\"hyperslab\" value=\"The more general case of a hyperslab&#160;can also be a regular pattern of points or blocks within the dataspace. Four parameters are required to describe a general hyperslab: the starting coordinates, the block size, the stride or space between blocks, and the number of blocks. These parameters are each expressed as a one-dimensional array with length equal to the rank of the dataspace and are described in the table below.\" />   <entry name=\"incremental allocation\" value=\"Incremental allocation (chunks only) is done at the time of the first write to the chunk. Chunks that have never been written are not allocated in the file. In a sparsely populated dataset, this option allocates chunks only where data is actually written.\" />   <entry name=\"late allocation\" value=\"Late allocation is done at the time of the first write to dataset. Space for the whole dataset is allocated at the first write.\" />   <entry name=\"link\" value=\"A link is, in effect, a path by which the target object can be accessed; it therefore has a name which func­tions as a single path component. A link can be removed with an H5Ldelete&#160;call, effectively removing the target object from the group that contained the link (assuming, of course, that the removed link was the only link to the target object in the group).\" />   <entry name=\"major message\" value=\"In the example above, we can see that an error record&#160;has a major message and a minor message. A major message&#160;generally indicates where the error happens. The location can be a dataset or a dataspace, for example. A minor message&#160;explains further details of the error. An example is “unable to open file”. Another specific detail about the error can be found at the end of the first line of each error record. This error description&#160;is usually added by the library designer to tell what exactly goes wrong. In the example above, the “predefined datatype” is an error description.\" />   <entry name=\"memory datatype\" value=\"The memory layout of a single data element is specified by the memory datatype. This specifies the size, alignment, and byte order of the element as well as the datatype class. Note that the memory datatype must be the same datatype class as the file, but may have different byte order and other properties. The HDF5 Library automatically transforms data elements between the source and destination layouts. For more information, see &quot;HDF5 Datatypes&quot; on page&#160;173.\" />   <entry name=\"memory space\" value=\"The calling program must allocate sufficient memory to store the data elements to be transferred. For a write (from memory to the file), the memory must be initialized with the data to be written to the file. For a read, the memory must be large enough to store the elements that will be read. The amount of storage needed can be computed from the memory dataty
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_101_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ged\" rd=\"1,0:970|3,0:6344,7815,8020,11538|5,0:27407,41938|6,0:6416,9911,25954|7,0:11596,12277,12482,12620,12901,13255,25630,40482,53083,58925,67931,92010|8,0:94,1425,13025,33010,63036,63066,63137,63241,63255,85902|9,0:10169,10686,16378|10,0:331,16797|11,0:1117|12,0:7525,14816\"/><wd nm=\"gement\" rd=\"3,0:1824,13138|4,0:25792|7,0:19637,19670,19706,19750,28865|8,0:65211|9,0:903,1130|10,0:11874|12,0:20583|13,0:1328\"/><wd nm=\"gency\" rd=\"1,0:2744\"/><wd nm=\"geneous\" rd=\"3,0:7645|8,0:60093,60565,61263,61364\"/><wd nm=\"general\" rd=\"3,0:4301|4,0:5718,5776,8240,8357|5,0:6733,6888|6,0:232|7,0:9547,10248,14088,36656,48048|8,0:146,3135,4886,15805,16581,24076,55888,56040,78739,93166|9,0:28896|12,0:1811,6952,21081,21585,26154,26217\"/><wd nm=\"generally\" rd=\"5,0:3538,24264,36680,38049|7,0:18398,76438|10,0:1917,7276,8997,10474,14198|11,0:4884|12,0:17033\"/><wd nm=\"generate\" rd=\"5,0:38194|8,0:97701,100487,100817\"/><wd nm=\"generated\" rd=\"11,0:5842\"/><wd nm=\"generates\" rd=\"8,0:22892\"/><wd nm=\"generating\" rd=\"5,0:6195|8,0:97038,97106\"/><wd nm=\"generic\" rd=\"3,0:11679|7,0:59710|12,0:1672,2227,20431,20489,20827,20952,21106,23763,26185,26273\"/><wd nm=\"gener­ally\" rd=\"8,0:49472\"/><wd nm=\"gent\" rd=\"5,0:32660\"/><wd nm=\"gents\" rd=\"1,0:2614\"/><wd nm=\"geometrically\" rd=\"9,0:4597\"/><wd nm=\"ger\" rd=\"3,0:10015,18256|4,0:4242,13684,13713,23057,23279
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_105_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"h11231\" rd=\"1,0:2154\"/><wd nm=\"h5\" rd=\"5,0:4351,4457,4647,4695,4994,5595,5724,5913,6346,6366,6497,6766,6921|6,0:11935,11950,12070,12126|7,0:21219,21972,23285,24467,41394,68207,71657,85050,88238|9,0:39738,40948,41230,42504,42804,44104|10,0:15277\"/><wd nm=\"h5_index_t\" rd=\"10,0:11042\"/><wd nm=\"h5_iter_order_t\" rd=\"10,0:11064\"/><wd nm=\"h5_version_ge\" rd=\"5,0:7487\"/><wd nm=\"h5_version_le\" rd=\"5,0:7615\"/><wd nm=\"h5_writ\" rd=\"9,0:39681,41083\"/><wd nm=\"h5_write\" rd=\"9,0:12840,13154,13178,13510\"/><wd nm=\"h5_write_t\" rd=\"9,0:42647\"/><wd nm=\"h5_write_tr\" rd=\"9,0:13536,13852\"/><wd nm=\"h5a\" rd=\"4,0:1682|7,0:2140|10,0:373,1568,3433,3492,3614,16814\"/><wd nm=\"h5a_operator2_t\" rd=\"10,0:11095\"/><wd nm=\"h5a_operator_t\" rd=\"10,0:11600\"/><wd nm=\"h5aclose\" rd=\"4,0:23077,23496,24101|10,0:4074,12647,12663,12686,15655\"/><wd nm=\"h5aclose_f\" rd=\"10,0:4083\"/><wd nm=\"h5acreate\" rd=\"4,0:22853,23261|7,0:2110,2224|8,0:85760,86976|10,0:3658,7128,7157,7384,7400,7822,15491\"/><wd nm=\"h5acreate_by_name\" rd=\"10,0:3807\"/><wd nm=\"h5acreate_by_name_f\" rd=\"10,0:3825\"/><wd nm=\"h5acreate_f\" rd=\"10,0:3668\"/><wd nm=\"h5adelete\" rd=\"7,0:2391|10,0:4124,12050,12067,12105,12195\"/><wd nm=\"h5adelete_by_idx\" rd=\"10,0:4167\"/><wd nm=\"h5adelete_by_idx
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_108_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"h5pset_fapl_mpiposix_f\" rd=\"5,0:14029\"/><wd nm=\"h5pset_fapl_multi\" rd=\"5,0:26679,38986,39158,39451,39801\"/><wd nm=\"h5pset_fapl_sec2\" rd=\"5,0:14291,25443,28836,28968|12,0:10209,11118\"/><wd nm=\"h5pset_fapl_sec2_f\" rd=\"5,0:14308\"/><wd nm=\"h5pset_fapl_split\" rd=\"5,0:14404,26866,40128,40264,40398|12,0:10331,27368\"/><wd nm=\"h5pset_fapl_split_f\" rd=\"5,0:14422\"/><wd nm=\"h5pset_fapl_stdio\" rd=\"5,0:5539,14533,25988,32043,32169\"/><wd nm=\"h5pset_fapl_stdio_f\" rd=\"5,0:14551\"/><wd nm=\"h5pset_fapl_windows\" rd=\"5,0:14609,25824,31461,31591\"/><wd nm=\"h5pset_fclose_degree\" rd=\"4,0:6340\"/><wd nm=\"h5pset_file_image\" rd=\"5,0:10406\"/><wd nm=\"h5pset_file_image_f\" rd=\"5,0:10424\"/><wd nm=\"h5pset_fill_time\" rd=\"7,0:5057\"/><wd nm=\"h5pset_fill_time_f\" rd=\"7,0:5074\"/><wd nm=\"h5pset_fill_value\" rd=\"7,0:4837,15774,86288,89507|8,0:76199,76816\"/><wd nm=\"h5pset_fill_value_f\" rd=\"7,0:4855\"/><wd nm=\"h5pset_filter\" rd=\"4,0:27999|6,0:16317|7,0:5393\"/><wd nm=\"h5pset_filter_callback\" rd=\"7,0:7427\"/><wd nm=\"h5pset_filter_f\" rd=\"6,0:16331|7,0:5407\"/><wd nm=\"h5pset_fletcher32\" rd=\"6,0:16380,16459|7,0:6045|12,0:10586,11570\"/><wd nm=\"h5pset_fletcher32_f\" rd=\"6,0:16398,16477|7,0:6063\"/><wd nm=\"h5pset_gc_references\" rd=\"5,0:23804\"/><wd nm=\"h5pset_hyper_cache\
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_111_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"hase\" rd=\"5,0:11021,11133|10,0:6289,6492|12,0:22355,22668\"/><wd nm=\"hase_change\" rd=\"5,0:10930,11044|6,0:11380,16538,16651|10,0:6211,6419,13273,14579,15355|12,0:22277,22595\"/><wd nm=\"hase_change_f\" rd=\"6,0:16563,16676|10,0:6236,6444|12,0:22302,22620\"/><wd nm=\"hases\" rd=\"7,0:9607,9732,10492\"/><wd nm=\"hasize\" rd=\"9,0:29102\"/><wd nm=\"hat\" rd=\"1,0:535,948,1111,3038|3,0:1720,2335,2405,2654,3699,9699,10409,11326,11402,13621,14483,14553,15097,15690,16247,16356,16516,17332,17700,18013,18334,19693,20478,21008|4,0:244,866,922,1077,1140,1410,1442,1571,2804,2879,4450,4612,4675,4753,5183,5254,6698,6853,9410,9426,9754,9866,9889,10379,10493,10848,10945,11649,11729,11779,11912,14440,15128,15268,16134,17369,17733,20067,20152,20287,20584,20863,22400,22607,22931,23048,25062,26099,26279,27210,27511|5,0:666,2145,3234,4422,4611,5819,5866,6047,6181,6517,7005,12782,13735,16317,17296,17342,17426,17630,17669,17826,17872,19994,20050,21597,22133,23982,24597,24686,24951,26414,27272,28312,29306,30865,32669,32740,34930,35055,38396,39680,42817,44256,44504,44674,44834,44900,45218,45336,45371,45431,45679|6,0:642,4221,4800,4917,5034,5150,5355,5664,6036,6169,6822,8141,8407,10341,10553,11034,11788,11998,12054,12325,12386,12940,15686,18791,18891,18941,18999,19092,19160,19712,19827,19927,20060,20229,20423,21968,22041,22273,22359,22793,22832,23264,24900,26126,26201,26612,26654,26704,26894,26970,27025,28113,28206,28222,28486,29529,29673,30661,31483,31847,31866,31975|7,0:121,672,761,2475,2538,5508,9992,12374,12692,14006,16161,16672,17405,17715,22863,25064,26124,30533,30615,31097,31205,31870,31969,32190,32270,32666
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_113_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"hichever\" rd=\"7,0:45052,45760\"/><wd nm=\"hid_t\" rd=\"4,0:2491,3472,16494,18126|5,0:15161,15205,15219,16078,16120,17110,19060,19075,19772,19819,27998,28017,28985,29553,29643,30351,31611,32187,33054,33140,35593,35624,35674,35706,39176,39221,39327,39372,40282,40331,40377,41807,41871,43131,43528,43547,43905,43924|6,0:19375|7,0:14523,15441,15474,21010,21871,21896,23178,24349,24374,41293,49859,50333,50503,54490,68312,71758,85162,88359|8,0:13221,24138,24359,24372,24544,24557,24693,24704,24762,24947,24976,25147,25226,26668,26829,26957,27239,27514,27641,28031,28146,28508,28627,29165,29527,29647,29957,30409,30505,30626,30740,30841,30865,30964,31062,31177,31195,31293,31439,31570,32227,33464,34002,34126,34778,35307,35678,35808,36074,36201,36751,37114,37231,37309,37444,38032,38422,40472,41276,44421,46748,47521,49702,57873,62356,62375,72058,76121,77588,81664,88709,88807,88889,88973,89019,89047,89129,89258,89271,89612,89641,89909,100602,100915|9,0:7685,7752,8185,8287,8718,8927,15536,39841,39889,41363,41402,41444,42947,42986,43028|10,0:7395,7410,7438,7451,7465,7484,7994,8007,8054,8067,9498,10059,10077,10092,10109,10372,11030,12077,12672,14996|11,0:5625,5979,6623,7099,8965,9771,9784,9798,14352,14597,14616,14871,15016,15177,15272,16350,16584,16822,16883,16895,16909,17051,17184,17306,17416|12,0:17134\"/><wd nm=\"hidden\" rd=\"5,0:45461\"/><wd nm=\"hierarchical\" rd=\"1,0:116,174,268|3,0:84|6,0:57,734,874,1416,6686\"/><wd nm=\"hierarchically\" rd=\"6,0:92\"/><wd nm=\"hierarchy\" rd=\"3,0:5717|6,0:155,3930|7,0:11
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_114_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"however\" rd=\"3,0:4470,18956|5,0:23608,27818,37966|6,0:7135|7,0:53149,67852,76184,77514,81924,83302|8,0:15766,25872,45706,48969,74505|9,0:9592|12,0:14865\" sp=\"1\"/><wd nm=\"hown\" rd=\"3,0:12634|4,0:17500,17668,19585,22880,23656|5,0:4491,27226,30690,45366|7,0:43314|8,0:431,44284,44873,53473,80408|9,0:5242,25687|11,0:6022,9745\"/><wd nm=\"hows\" rd=\"3,0:2185,9770,19974,20022,20067,20149,20305,20473|4,0:7621,12254,16213,16907|5,0:5412,43425,43778,44752,45163,45730|6,0:23609,24393,25427,29295|7,0:10059,12836,14327,15138,16945,20575,21588,22854,27143,32247,32860,39230,42260,43717,43990,49772,50930,51249,51799,52136|8,0:6342,8680,10924,13047,15034,23835,23887,32132,32417,33176,33222,33317,38138,38545,40214,40612,40930,41536,44078,44643,45959,48008,48418,49326,49764,50580,51276,51930,52782,56987,58240,58689,60959,62011,62196,64028,64571,64691,69096,70171,70296,71888,72585,75979,77011,77461,77842,79182,80136,80348,80499,80631,80859,84280,91913,91984,93971,94931,94956,95774,96003,96214|9,0:16686,17245,20553,20841,21175,21502,24001,24191,25362,26951,27682,28492,30235,30557,34133,34519,37477,37923|10,0:2099|11,0:8929,10143,12053,15381,15832,17553,17969\"/><wd nm=\"hrase\" rd=\"11,0:12661\"/><wd nm=\"hread\" rd=\"11,0:1736,1869,3272,4701,5929,12212,12479,17004\"/><wd nm=\"hree\" rd=\"3,0:7094,13771,20002,20310|4,0:10398,10628,10686|5,0:17274,44813,44961,44975|6,0:2591,19207,19359,28947,29333,29379,30157,30339,30840,31627|7,0:9598,9727,35306,44444,51000,51869,64006,65108|8,0:80213,81121|9,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_117_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"id1\" rd=\"4,0:12654,12891,13039|8,0:64266,64323,64339,64344,65736,65851,66052,66057,69342,69383,69619,69769,69774,70758,70790,70887,70982,71074,71169|9,0:26168,26407\"/><wd nm=\"id2\" rd=\"4,0:23227,23312,23462|9,0:31261,31586,36106,36213\"/><wd nm=\"id_f\" rd=\"6,0:15872|7,0:5769|9,0:3168\"/><wd nm=\"id_t\" rd=\"4,0:2491,3472,16494,18126|5,0:15161,15205,15219,16078,16120,17110,19060,19075,19772,19819,27998,28017,28985,29553,29643,30351,31611,32187,33054,33140,35593,35624,35674,35706,39176,39221,39327,39372,40282,40331,40377,41807,41871,43131,43528,43547,43905,43924|6,0:19375|7,0:14523,15441,15474,21010,21871,21896,23178,24349,24374,41293,49859,50333,50503,54490,68312,71758,85162,88359|8,0:13221,24138,24359,24372,24544,24557,24693,24704,24762,24947,24976,25147,25226,26668,26829,26957,27239,27514,27641,28031,28146,28508,28627,29165,29527,29647,29957,30409,30505,30626,30740,30841,30865,30964,31062,31177,31195,31293,31439,31570,32227,33464,34002,34126,34778,35307,35678,35808,36074,36201,36751,37114,37231,37309,37444,38032,38422,40472,41276,44421,46748,47521,49702,57873,62356,62375,72058,76121,77588,81664,88709,88807,88889,88973,89019,89047,89129,89258,89271,89612,89641,89909,100602,100915|9,0:7685,7752,8185,8287,8718,8927,15536,39841,39889,41363,41402,41444,42947,42986,43028|10,0:7395,7410,7438,7451,7465,7484,7994,8007,8054,8067,9498,10059,10077,10092,10109,10372,11030,12077,12672,14996|11,0:5625,5979,6623,7099,8965,9771,9784,9798,14352,14597,14616,14871,15016,15177,15272
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_120_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"igured\" rd=\"7,0:25011\"/><wd nm=\"igures\" rd=\"3,0:17567,19893|5,0:10771|6,0:778,931\"/><wd nm=\"igu­ous\" rd=\"3,0:8130|7,0:43894|9,0:18267\"/><wd nm=\"ig­nificant\" rd=\"8,0:35439\"/><wd nm=\"ig­uous\" rd=\"5,0:35334\"/><wd nm=\"ig­uration\" rd=\"5,0:12417\"/><wd nm=\"ig­ure\" rd=\"3,0:7168\"/><wd nm=\"ii\" rd=\"3,0:18891,19388|5,0:6238|6,0:7060,7580,9579,10940,17726|7,0:6719,11726|8,0:1928,7250,9735,23127,29578,29584,37378,37384,38094,83372,99263,100703|10,0:5950,6715,16984,17356|12,0:390\"/><wd nm=\"ike\" rd=\"3,0:17709|5,0:6465,25293,29282,31939,42102|6,0:5043,6130,12099|7,0:57276,58645,77024,82380|8,0:8998,9323,43720,63588|11,0:205|12,0:17155\"/><wd nm=\"ikely\" rd=\"8,0:74537,97792|11,0:7684\"/><wd nm=\"il\" rd=\"3,0:641,5219|4,0:997,2982,6096,7007|5,0:759,4441,4630,14932,15499,17777,17970,18599,26128,44683,44715,45467|6,0:1818,15634,24030|7,0:5456,9763,10017,10929,11203,20136,42100,42677,42755,53319,68683,68779,68957,69319,69555,69842,69950,70164,70473,70809,70936,71180,73113,73206,73309,73388,73463,73618,73852,74136,74245,74458,74769,75110,75237,75485,85580,85814,86100,86208,86662,87069,87341,87468,87714,88797,89032,89318,89426,89920,90244,90522,90649,90897|8,0:28757,28935,32492,33910,34411,36346,36524,85585,85602,87686|10,0:7891|11,0:3749,5058,6343,7692|12,0:1299,3463,9973\"/><wd nm=\"ilable\" rd=\"1,0:3527|3,0:18170|4,0:7476|5,0:14061,14125,18165,24706,27089,27143,34506,42335,42419|6,0:5512,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_121_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ileid\" rd=\"8,0:72390\"/><wd nm=\"ilename\" rd=\"9,0:41217,41856,42788,43445\"/><wd nm=\"ilenames\" rd=\"5,0:40819\"/><wd nm=\"iler_conv\" rd=\"8,0:18270\"/><wd nm=\"iler_conv_f\" rd=\"8,0:18287\"/><wd nm=\"ilers\" rd=\"8,0:45736\"/><wd nm=\"iles\" rd=\"3,0:1636,1650,1664,4283,5757,15420,15902,16033|4,0:1738|5,0:95,374,1976,3364,3400,3510,3961,11969,13437,13751,13932,14204,14360,14461,14490,14602,14961,14974,15020,24094,24129,24236,24893,26347,26430,26537,26612,27812,28618,31916,32735,32881,33024,34380,34402,34997,35071,35215,35381,37398,37890,37961,38202,38499,38541,38811,38969,39070,39145,39662,40053,40251,40648,42550,44216,44234,44263,44723,44760,45112,45174|6,0:394,457,540,25287,25902,27506|7,0:6451,6531,25775,31369,31462,49481,49529,50269,50297,51458,52029,52982,53070,53243|8,0:87308,87369|12,0:7770,10031,10236,10325|13,0:837,990\"/><wd nm=\"iles_fig3\" rd=\"5,0:45118,45131\"/><wd nm=\"iles_fig4\" rd=\"5,0:45274,45287\"/><wd nm=\"ilesize\" rd=\"5,0:8305\"/><wd nm=\"ilesize_f\" rd=\"5,0:8321\"/><wd nm=\"ile’s\" rd=\"5,0:8746,23449,26281|6,0:19096,27108|7,0:1013\"/><wd nm=\"ile”\" rd=\"11,0:5038|12,0:25151\"/><wd nm=\"iliar\" rd=\"8,0:79788\"/><wd nm=\"iliaze\" rd=\"7,0:85373,88582\"/><wd nm=\"ilies\" rd=\"5,0:13707,37403\"/><wd nm=\"iling\" rd=\"7,0:77398,77455\"/><wd nm=\"ilitate\" rd=\"7,0:27924\"/><wd nm=\"ilities\" rd=\"1,0:158,216,310|5,0:2565
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_128_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"irely\" rd=\"5,0:32540|7,0:36529\"/><wd nm=\"irement\" rd=\"7,0:48055|8,0:63339\"/><wd nm=\"irements\" rd=\"5,0:2349,2902,32643|8,0:46067,47957|10,0:500,11646,11779|12,0:2911,16648\"/><wd nm=\"ires\" rd=\"3,0:16483,20891|4,0:3236,17100,17289,27851|5,0:27463|7,0:63324|8,0:13679,48037,48211,48580,48918,97614|9,0:7343|12,0:18456\"/><wd nm=\"iring\" rd=\"5,0:38625\"/><wd nm=\"irly\" rd=\"12,0:18538\"/><wd nm=\"ironm\" rd=\"12,0:1467\"/><wd nm=\"ironment\" rd=\"3,0:855,1036|4,0:25562|6,0:11463|12,0:640,3268,3296,5372,6049,8120,10999,11059,12054,24937\"/><wd nm=\"ironments\" rd=\"3,0:15950,15993|4,0:25855|5,0:3854,25086,41434|7,0:31793|12,0:11170,11217\"/><wd nm=\"irs\" rd=\"3,0:11737|8,0:7720,71633|10,0:764,6655|12,0:984,6777\"/><wd nm=\"irst\" rd=\"3,0:19963|4,0:9500,9723,10571,10747,12213,12638,13150,15257,15512,17608,18643,19913,19968,20118,21232,21781,22764,23565,24186|5,0:153,4172,5094,19021,19722,36112,36529|6,0:830,6835,20199,20638|7,0:22916,25610,30756,32694,34605,39378,42926,42984,43048,45522,45719,62910,64944,65103,84574|8,0:18929,19002,26033,28765,28943,29012,36354,36532,36601,41822,41887,43819,47339,54232,56970,57033,64011,64554,68044,68178,70154,72769,81076,88584,96039|9,0:8538,9536,10862,11263,11337,11553,11840,14070,14196,14580,23150,23907,26152,27454,27580,27752,27943,28050,28661,29009,34918,34937,35201,35622,37555,38173,38335|10,0:9762,9832,10495|11,0:3396,4273,5100,6866,6928,8371,12878|12,0:12631,14103,14200,18782\
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_12_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"5t_std_ref_obj\" rd=\"8,0:70774,71259,71455\"/><wd nm=\"5t_std_robj\" rd=\"8,0:10571\"/><wd nm=\"5t_std_u16be\" rd=\"8,0:10366,98668\"/><wd nm=\"5t_std_u16le\" rd=\"8,0:98682\"/><wd nm=\"5t_std_u32be\" rd=\"8,0:98697\"/><wd nm=\"5t_std_u32le\" rd=\"8,0:98711\"/><wd nm=\"5t_std_u64be\" rd=\"8,0:98726\"/><wd nm=\"5t_std_u64le\" rd=\"8,0:98740\"/><wd nm=\"5t_std_u8be\" rd=\"8,0:98641\"/><wd nm=\"5t_std_u8le\" rd=\"8,0:98654\"/><wd nm=\"5t_str_nullpad\" rd=\"8,0:29818,37859,99220,100682\"/><wd nm=\"5t_str_nullterm\" rd=\"8,0:29801,37817,83350,99203\"/><wd nm=\"5t_str_spacepad\" rd=\"8,0:29836,37889,99237\"/><wd nm=\"5t_str_t\" rd=\"8,0:29624,37457\"/><wd nm=\"5t_string\" rd=\"8,0:26719,56502,68455,83321,99082,100642\"/><wd nm=\"5t_variable\" rd=\"8,0:69045,69150,69237,69328,69388,99179,100662\"/><wd nm=\"5t_vlen\" rd=\"8,0:26791,56579,99663\"/><wd nm=\"5tarray_create\" rd=\"8,0:21907,32740,61829,62432,82199\"/><wd nm=\"5tarray_create_f\" rd=\"8,0:21923\"/><wd nm=\"5tclose\" rd=\"4,0:4517|7,0:15104,15980,71219,71239,75524,87753,90936|8,0:12111,18089,24753,25724,89434|11,0:4452,4727\"/><wd nm=\"5tclose_f\" rd=\"8,0:18098\"/><wd nm=\"5tcommit\" rd=\"8,0:16788,24937,26050,86398,88736,89602\"/><wd nm=\"5tcommit_anon\" rd=\"8,0:16933\"/><wd nm=\"5tcommit_anon_f\" rd=\"8,0:16
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_133_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"i­nates\" rd=\"5,0:17569\"/><wd nm=\"i­nation\" rd=\"7,0:20259\"/><wd nm=\"i­nition\" rd=\"9,0:7314\"/><wd nm=\"i­ously\" rd=\"6,0:20008|9,0:18784\"/><wd nm=\"i­ple\" rd=\"5,0:26528|8,0:59970\"/><wd nm=\"i­ronment\" rd=\"12,0:11856\"/><wd nm=\"i­sion\" rd=\"8,0:34868,38205,39181\"/><wd nm=\"i­tance\" rd=\"12,0:5278\"/><wd nm=\"i­ties\" rd=\"6,0:810|7,0:44512\"/><wd nm=\"i­tion\" rd=\"4,0:10922|8,0:7042|9,0:23765\"/><wd nm=\"i­tional\" rd=\"8,0:87429\"/><wd nm=\"i­tions\" rd=\"8,0:41869\"/><wd nm=\"j\" rd=\"7,0:21069,21136,21140,21144,21162,21169,21931,23222,68460,69130,69134,69139,69157,85296,85418,85422,85427,85445,88512,88627,88631,88636,88654|8,0:10571,65658,65662,65670,65701,65709,65954,65958,65972,66023,70468,70774,71259,71455,87044|9,0:12974,12978,12983,13012,13022,13360,13374,13377,13698,13712,13718,38986,38990,38995,39022,40017,40066,40070,40075,40104,40114,41632,41667,41681,41684,43218,43252,43266,43272|11,0:10361,10593,10902,13507,13739,14048\"/><wd nm=\"j_count\" rd=\"5,0:9019\"/><wd nm=\"j_count_f\" rd=\"5,0:9036\"/><wd nm=\"j_id\" rd=\"10,0:11035|11,0:15686,15980\"/><wd nm=\"j_ids\" rd=\"5,0:9110\"/><wd nm=\"j_ids_f\" rd=\"5,0:9125\"/><wd nm=\"j_info_idx_f\" rd=\"6,0:13430,13539,13697\"/><wd nm=\"j_io\" rd=\"11,0:17844,18313\"/><wd nm=\"j_num\" rd=\"11,0:9789,9902,10580,13726\"/><wd nm=\"j_
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_137_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"le1\" rd=\"5,0:44793,45203,45268,45773,45910\"/><wd nm=\"le2\" rd=\"5,0:44953,44999,45051,45184,45254,45764,45946,45991\"/><wd nm=\"le32\" rd=\"8,0:92466\"/><wd nm=\"le__\" rd=\"11,0:17813,18282\"/><wd nm=\"le_access\" rd=\"3,0:12878|5,0:4916,5515,19208,19429,43961|10,0:15167|12,0:3863\"/><wd nm=\"le_cache\" rd=\"5,0:7815|6,0:18098\"/><wd nm=\"le_cache_size\" rd=\"5,0:11538|6,0:17958,26046\"/><wd nm=\"le_create\" rd=\"3,0:12814|5,0:4843,19394,43584|12,0:3847\"/><wd nm=\"le_cre­ate\" rd=\"5,0:19161\"/><wd nm=\"le_extent_dims\" rd=\"4,0:10115,13984|9,0:2076,15198,15386,15662,15810,38655\"/><wd nm=\"le_extent_dims_f\" rd=\"9,0:2102,15412\"/><wd nm=\"le_extent_ndims\" rd=\"4,0:10067|9,0:2179,15141,15616,38615\"/><wd nm=\"le_extent_ndims_f\" rd=\"9,0:2206,15168\"/><wd nm=\"le_extent_npoints\" rd=\"9,0:2277\"/><wd nm=\"le_extent_npoints_f\" rd=\"9,0:2306\"/><wd nm=\"le_extent_type\" rd=\"9,0:2381\"/><wd nm=\"le_extent_type_f\" rd=\"9,0:2407\"/><wd nm=\"le_f\" rd=\"7,0:6268|9,0:1549,1629,1856,2587,7481,9081,9114,9229,9305,9408,10397,13442,13784,14960,41925,43514\"/><wd nm=\"le_factor\" rd=\"7,0:81575,81755\"/><wd nm=\"le_fac­tor\" rd=\"7,0:82788\"/><wd nm=\"le_id\" rd=\"4,0:23923,24563|5,0:4323,4966,5569,5805,5870,17115,17213,43552,43634,43715,43929,44077,44179|7,0:21015,21199,21295,21876,21952,22022,23183,23265,23362,24354,24447,24543,41298,41
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_141_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"llbacks\" rd=\"11,0:11182\"/><wd nm=\"llbuf\" rd=\"8,0:78242,78362,78465,78505,78548,78591\"/><wd nm=\"llect\" rd=\"4,0:1191|5,0:7216|9,0:21122\"/><wd nm=\"llect_f\" rd=\"5,0:7234\"/><wd nm=\"llecting\" rd=\"5,0:11844,23838\"/><wd nm=\"llection\" rd=\"3,0:4714,5069,5286,6241,11715|4,0:8198,14097|5,0:2651,23367,23474,23589,23722|7,0:75|11,0:3444|12,0:938,6409,6755,26533\"/><wd nm=\"llections\" rd=\"8,0:78676\"/><wd nm=\"llective\" rd=\"5,0:42381|7,0:8942,9055,19474,33029,42005\"/><wd nm=\"llective_opt\" rd=\"7,0:8957\"/><wd nm=\"llectively\" rd=\"5,0:44062,44155\"/><wd nm=\"llects\" rd=\"5,0:7262\"/><wd nm=\"lled\" rd=\"3,0:10362,15477,17654,20097|4,0:693,11713,19232,22908,23687,24940,27529|5,0:2487,3042,16879,17532,17688,17901,18128,21022,21211,21927,24380,41516,44056,44149|6,0:2661,4327,24429|7,0:2030,22903,23131,29191,30479,36904,37213,39403,39996,41822,44023,44356,46876,47038,64138,64291,64398,67347,67641,77981,82828|8,0:4746,13085,29319,36920,41657,47367,66422,67255,86448,90495,91344,97658|9,0:5035,32768|10,0:11322,12213|11,0:3768,3838,6176,9081,11084,11533|12,0:19102,19319\"/><wd nm=\"llegal\" rd=\"8,0:24858\"/><wd nm=\"llel\" rd=\"3,0:15976,16469|4,0:5914,5949|5,0:2673,3408,13939,18088,18136,24136,26885,26940,27039,41411,41426,41454,41499,41525,41754,42353,42403,42437,43839,43892|7,0:25820,26523,32005,35854,39437,40350,41962,43376,43506|12,0:473,8103,10982,11753,11839\"/><wd nm=\"llenge\" rd=\"8,0:55876\
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_144_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"lus­trates\" rd=\"4,0:21802|9,0:11150\"/><wd nm=\"lute\" rd=\"3,0:19450|4,0:19437,19689,20533,20618,20680,20753,21756,21825,22003|6,0:7649,7925,8200,18811,18918,19297,20126,20273,20598,20884,20959,21248,21382,22146,23324\"/><wd nm=\"lutepathname\" rd=\"3,0:19168,19220|6,0:7349,7401\"/><wd nm=\"lutions\" rd=\"13,0:1387\"/><wd nm=\"lu­ation\" rd=\"12,0:8339\"/><wd nm=\"lval\" rd=\"7,0:15505,15808\"/><wd nm=\"lve\" rd=\"5,0:35134|8,0:49619\"/><wd nm=\"lved\" rd=\"4,0:24843|5,0:22013|9,0:22927,23274\"/><wd nm=\"lves\" rd=\"4,0:25602|5,0:19495\"/><wd nm=\"lvisit\" rd=\"6,0:14350,14431,28019,28333\"/><wd nm=\"lways\" rd=\"3,0:19424|5,0:33358|6,0:4819,6233,6764,7616,19850,21785|7,0:33402,55867,82894|8,0:9500,28433,29058,35999,36647,41711,47873,49910,53418,73814,93208|9,0:4574,5984,12171,12725|12,0:12857,23603,26738,26910\"/><wd nm=\"ly\" rd=\"0,64:231|1,64:1481,1943,2444,3064,3204,3227,3375,3811,4050|2,64:292|3,64:1656,3713,3978,4330,5239,5692,5767,6282,6650,6809,6944,6991,8117,8162,8582,10232,10354,11089,11145,12264,14462,14509,15128,17597,18128,19759,19820,21272|4,64:325,951,1044,1157,2199,3166,4314,4336,4831,5510,6796,8178,8925,9268,9372,11516,14359,14752,15672,15756,15949,16471,17193,17246,17378,18549,19153,19989,20219,20887,21212,25825,26301,26545,27154,27521,28188|5,64:160,278,829,1018,1452,1499,1681,1790,2395,2954,3193,3240,3538,5054,5449,5598,6555,8577,9467,11961,12647,12786,13648,15091,15784,16207,16219,16283,17640,17789,17979,18008,18025,18555,18685,18966
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_146_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"mations\" rd=\"7,0:20061,24857,26343\"/><wd nm=\"mati­cally\" rd=\"5,0:18008|11,0:4078\"/><wd nm=\"matrix\" rd=\"8,0:61455|9,0:39760,40968,41287,42530,42870,44139\"/><wd nm=\"matrix_out\" rd=\"9,0:29889\"/><wd nm=\"mats\" rd=\"6,0:9106,11369|7,0:18416|8,0:1871,5573,7117,16006\"/><wd nm=\"matted\" rd=\"5,0:6249|8,0:42275\"/><wd nm=\"matter\" rd=\"3,0:18017|6,0:5359|7,0:31199,31864|9,0:28996\"/><wd nm=\"mature\" rd=\"5,0:17467\"/><wd nm=\"max\" rd=\"7,0:77322\"/><wd nm=\"max_dims\" rd=\"4,0:14025|9,0:8784,8897,9019,9164,9382,9460,15590,15762,15858\"/><wd nm=\"max_len_f\" rd=\"7,0:3676\"/><wd nm=\"max_rank\" rd=\"8,0:61611\"/><wd nm=\"maxdims\" rd=\"4,0:17884,18013|7,0:12333\"/><wd nm=\"maximize\" rd=\"12,0:864\"/><wd nm=\"maximum\" rd=\"3,0:8713,8731,8831|4,0:9300,13951|5,0:12541,23250,23328,36605|6,0:17012,17104|7,0:11666,12123,12176,12316,12423,32394,40827,75913,79191,79416,80787,80895,91456,92146|8,0:61627|9,0:4900,4935,5110,5481,5560,5740,5815,5920,6222,6448,7404,9745,9964,10080,10297,10364,10607,15365|10,0:14218|12,0:19275,19373\"/><wd nm=\"maxi­mum\" rd=\"7,0:77221|9,0:2165\"/><wd nm=\"max­imum\" rd=\"8,0:42557\"/><wd nm=\"may\" rd=\"1,0:1339|3,0:1917,2020,2802,6766,7580,8280,8320,8738,9277,9836,10128,10607,15713,17048,17852,17880,18288,18293,19041|4,0:3201,19393,26508|5,0:17005,20123,21391,27840,29086,30079,31072,31712,32287,34724,35832,36993,37721,39927
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_150_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"module\" rd=\"3,0:1714,12228|4,0:27813,27904|7,0:25655,27011,30988|9,0:41140,42710\"/><wd nm=\"modules\" rd=\"3,0:2272,3496,15655|4,0:27462,27694|7,0:26979|9,0:41166,42736\"/><wd nm=\"mod­els\" rd=\"3,0:584\"/><wd nm=\"mod­ules\" rd=\"3,0:2212|4,0:26286\"/><wd nm=\"mogeneous\" rd=\"8,0:60565,61263\"/><wd nm=\"mon\" rd=\"3,0:12150|4,0:1398,2032,14339|6,0:183|7,0:56391,91715|8,0:3159,10976,13395,14155,63326,63551,88569|10,0:852|12,0:13717\"/><wd nm=\"mong\" rd=\"3,0:2733|4,0:27484|7,0:72870|10,0:16668\"/><wd nm=\"monitoring\" rd=\"5,0:37573\"/><wd nm=\"monly\" rd=\"5,0:23054|6,0:20377|8,0:1853,5554,8299,9807|10,0:17096\"/><wd nm=\"more\" rd=\"1,0:2241,2497|3,0:3352,3411,4684,5215,5866,6681,10441,10620,15209,16121,16979,18480,19525|4,0:2047,4845,5031,5227,6318,7003,7503,8236,14114,14748|5,0:557,1936,2228,2284,2786,2840,3475,4474,5925,14774,14928,16453,16690,16728,17710,18872,21693,24201,27159,27544,34814,38789,43027,46037|6,0:1814,2177,3002,4411,4677,5810,6376,8763,10158,11956,16190,18854,25080,25988,27567,27600,29859|7,0:1265,6012,9759,17907,26150,29774,30788,30829,36253,36354,37408,38052,38395,38442,38531,39647,44185,47782,48560,48580,49525,50265,57824,58522,70093,74388,78019,79082,80238,82576,84783,86538,89816|8,0:2812,2997,3717,4602,5958,7392,27392,45860,64134,75204,79538,87316,87571,88547,95150|9,0:7892,10048,11823,13135,13491,13833,18439,18568,19275,33291|10,0:1458,6830,13022,13111,13334|11,0:3920,8807,14136|12,0:671,735,1295,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_151_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"mple_extent_dims\" rd=\"4,0:10115,13984|9,0:2076,15198,15386,15662,15810,38655\"/><wd nm=\"mple_extent_dims_f\" rd=\"9,0:2102,15412\"/><wd nm=\"mple_extent_ndims\" rd=\"4,0:10067|9,0:2179,15141,15616,38615\"/><wd nm=\"mple_extent_ndims_f\" rd=\"9,0:2206,15168\"/><wd nm=\"mple_extent_npoints\" rd=\"9,0:2277\"/><wd nm=\"mple_extent_npoints_f\" rd=\"9,0:2306\"/><wd nm=\"mple_extent_type\" rd=\"9,0:2381\"/><wd nm=\"mple_extent_type_f\" rd=\"9,0:2407\"/><wd nm=\"mple_f\" rd=\"9,0:1549,1629,1856,2587,9081,9114,9229,9305,9408,10397,13442,13784,14960,41925,43514\"/><wd nm=\"mplefile\" rd=\"5,0:4341,4447,4685,4984,5585,5714,5903,6336,6356,6487\"/><wd nm=\"mplement\" rd=\"4,0:529,586|6,0:142|7,0:13091,29279|8,0:981,3879,5592,6685,9013,10347,28079,35741,63232|9,0:655,18042,27304,30575,31786,31955,33379\"/><wd nm=\"mplementa\" rd=\"7,0:63991\"/><wd nm=\"mplementatio\" rd=\"6,0:8614\"/><wd nm=\"mplementation\" rd=\"3,0:373,1246,1537|6,0:8656,8724,9006,9521|7,0:83001,83037\"/><wd nm=\"mplementations\" rd=\"3,0:594,671\"/><wd nm=\"mplemented\" rd=\"3,0:6817,11424,15358|4,0:425|6,0:2387,2976|7,0:67669,77012,78103,83254|8,0:63083|9,0:8257,17692|12,0:6724\"/><wd nm=\"mplementing\" rd=\"3,0:1335\"/><wd nm=\"mplements\" rd=\"3,0:111,420,1724,2075,2899,14973|4,0:97,653,25152,25473|7,0:24799,24843,25696,30994,41757|8,0:3404,23604,71605\"/><wd nm=\"mplemen­
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_153_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"n1\" rd=\"7,0:52479\"/><wd nm=\"n2\" rd=\"7,0:52518\"/><wd nm=\"n3\" rd=\"7,0:52557\"/><wd nm=\"n_\" rd=\"10,0:7341\"/><wd nm=\"n_2\" rd=\"8,0:15487,28090,35752\"/><wd nm=\"n_apply_nbit\" rd=\"7,0:64065\"/><wd nm=\"n_buf_size\" rd=\"7,0:48954|8,0:66812\"/><wd nm=\"n_by_idx\" rd=\"4,0:24357,24548|10,0:5373,8878,8981\"/><wd nm=\"n_by_idx_f\" rd=\"10,0:5388\"/><wd nm=\"n_by_name\" rd=\"4,0:23591,23907|10,0:5482,8649,8672\"/><wd nm=\"n_by_name_f\" rd=\"10,0:5498\"/><wd nm=\"n_colors\" rd=\"8,0:72063,72137,72187,72239,72290,72342,72409\"/><wd nm=\"n_create\" rd=\"8,0:22332,32761,63965,64271\"/><wd nm=\"n_create_f\" rd=\"8,0:22347\"/><wd nm=\"n_f\" rd=\"5,0:6978,7314,7376,9385,9429,11172|6,0:12780,12865|7,0:2802,2888,3676|8,0:16698,16948,18740,18816,19199,19264|9,0:41781,43370|10,0:5290\"/><wd nm=\"n_ge\" rd=\"5,0:7487\"/><wd nm=\"n_get_buf_size\" rd=\"7,0:3655,24174\"/><wd nm=\"n_get_max_len_f\" rd=\"7,0:3676\"/><wd nm=\"n_id\" rd=\"11,0:15771,16002\"/><wd nm=\"n_idx\" rd=\"7,0:2296\"/><wd nm=\"n_le\" rd=\"5,0:7615\"/><wd nm=\"n_mem_manager\" rd=\"7,0:8277,8410,49095|8,0:65260,66631\"/><wd nm=\"n_members_f\" rd=\"6,0:13517,13564,13641\"/><wd nm=\"n_name\" rd=\"7,0:2283\"/><wd nm=\"n_none\" rd=\"8,0:15445,28111,32320,35773\"/><wd nm=\"n_nu
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_156_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"nd_1\" rd=\"8,0:101023\"/><wd nm=\"nd_2\" rd=\"8,0:101055\"/><wd nm=\"nd_f\" rd=\"8,0:45181,54510,55150,55283,55414\"/><wd nm=\"nd_type\" rd=\"8,0:98369,99480,100299\"/><wd nm=\"nda\" rd=\"4,0:16698\"/><wd nm=\"ndable\" rd=\"3,0:8661|4,0:16719,17136,17272,18979|10,0:17748\"/><wd nm=\"ndants\" rd=\"3,0:5507\"/><wd nm=\"ndard\" rd=\"3,0:9955,13499|4,0:1505|5,0:3336,3372,24066,24101,25895,26915,26980,37543,41569|7,0:13059,25177,25707,29159,29234,58116|8,0:749,3030,8334,8892,8981,16356,65131,66257,68868,74146,74276|9,0:6091|10,0:262,817|11,0:4059,4527,7022,8337|12,0:10179\"/><wd nm=\"ndards\" rd=\"3,0:9640\"/><wd nm=\"ndaries\" rd=\"8,0:95022|9,0:21957\"/><wd nm=\"ndary\" rd=\"5,0:29988|8,0:48199,48499\"/><wd nm=\"ndation\" rd=\"1,0:3247\"/><wd nm=\"ndatory\" rd=\"10,0:12558\"/><wd nm=\"nddo\" rd=\"8,0:53977|9,0:13388,13394,13726,13732,41695,41701,43280,43286\"/><wd nm=\"nded\" rd=\"4,0:16938,16989,17390|5,0:6208,18709|6,0:11819|7,0:11651,40317,40414,40812,41897,42871,43242,43359,43408,52762,52891,72799,82351,91366,91808|8,0:38305,83966,90555,99943|9,0:9555,9627,19953|10,0:107,12372|11,0:718|12,0:21521\"/><wd nm=\"ndefined\" rd=\"5,0:17248|7,0:44073,44329,44829,44971,45169,45201,46223,46351\"/><wd nm=\"ndence\" rd=\"3,0:3733\"/><wd nm=\"ndencies\" rd=\"3,0:2193\"/><wd nm=\"ndent\" rd=\"1,0:1907|3,0:816|4,0:3135,4268,7566,25713|5,0
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_160_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"notable\" rd=\"6,0:11048\"/><wd nm=\"notably\" rd=\"6,0:24930\"/><wd nm=\"notates\" rd=\"7,0:776\"/><wd nm=\"notation\" rd=\"6,0:8449,8465\"/><wd nm=\"note\" rd=\"3,0:3693,11322,17328,17540,17696,20286,20454,20618,20789|4,0:2778,3961,6694,7854,17678,20063,20859,26275|5,0:4393,5815,6513,17486,18075,24682,27268,34331,36562,45304,45855|6,0:4913,5030,8403,26087,26122,29525|7,0:9988,16668,17711,31093,35810,43334,51300,54765,55126,57040,57404,58263,58775,71058,71361,75359,75641,87590,87870,90771,91053|8,0:33269,38256,40648,41114,41586,43220,45394,47141,49570,62115,69229,70482,75820,77913,86151,87218,87879,88217,92528,95827,97589|9,0:4342,5169,5664,5872,6331,9682,14281,19682,22609,27063,34411,37574|10,0:13878,16446|11,0:10998|12,0:4843,5920,24053,24237,24434,24676,24780\"/><wd nm=\"noted\" rd=\"3,0:19500|6,0:7124,7765\"/><wd nm=\"notes\" rd=\"5,0:5035,24552,27642|8,0:6665|12,0:26547\"/><wd nm=\"nother\" rd=\"3,0:506,1429,2531,6412,17937,20171,20640,20811|4,0:5890,14175,19411,25582|5,0:5152,44560,44588,45586|6,0:4868,5279,31759|7,0:62711|8,0:5039,47421,62807,69894,91110|9,0:20898,26704,32546|10,0:3711,13524,14083|11,0:3681,5043,16548,16646,18051|12,0:2769,18208|13,0:322,424\"/><wd nm=\"nothing\" rd=\"7,0:91905|9,0:5224\"/><wd nm=\"notice\" rd=\"1,0:42,84,624,736|4,0:10842|7,0:57502|8,0:48507,58799|9,0:25715\"/><wd nm=\"noticeably\" rd=\"5,0:23211\"/><wd nm=\"notices\" rd=\"1,0:934\"/><wd nm=\"noting\" rd=\"9,0:5425,55
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_161_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"nsidered\" rd=\"4,0:5398|7,0:83338,83946|8,0:25982\"/><wd nm=\"nsidering\" rd=\"12,0:13544\"/><wd nm=\"nsid­ered\" rd=\"8,0:73233\"/><wd nm=\"nsient\" rd=\"3,0:5112,12101|8,0:16819,16974,17142,24401,24495,24883,25032,25183,25243,85676,86064,86210,86365,86683,86890,87745,87839,88173,88243,88415,88441,88721,89691,89972|12,0:10711,11280,11345,27033\"/><wd nm=\"nsigned\" rd=\"5,0:15191,16106,30383|7,0:62368,91507|8,0:6767,7766,9032,10054,10401,11136,11194,11247,11298,11359,11589,11649,11710,11771,15932,28102,30520,30639,30753,30878,31579,32176,35764,39153,39265,39552,64072,64248,65622,65677,65999,74818|11,0:9672,9812,10266,13412,16870\"/><wd nm=\"nsigned”\" rd=\"8,0:3926\"/><wd nm=\"nsignificant\" rd=\"7,0:81102,81958\"/><wd nm=\"nsion\" rd=\"3,0:7470,8685|4,0:9156,9241,12218,13958,17738,18648|5,0:40316,40363,40686,40712,40751,40783|7,0:12067,12130,12164,12183,12259,12430,40798,41060,41110,41527,52946|8,0:7928,31130,53827,53853,53890,61218,61293,61898,63123|9,0:274,2149,4828,5465,5589,5724,5757,5784,5944,7411,8543,8616,9541,9582,10817,10847,10874,11268,11349,11393,11419,11558,11845,13258,13619,14336,14495,14585,14614,20228,20422,23155,24148,41501,43085|12,0:15745,19292,19390\"/><wd nm=\"nsional\" rd=\"3,0:4761,4868,7357,8561|4,0:7401,8498,9661,10404,10453,10634,10692,11697,11848,11981|7,0:298,317,25304,25939,33713,34396,39250,39516,40616,50965,51834,52214|8,0:6151,6206,8047,60583,61593,62049,62330,62604,62729,63055,64110,67526,67632,67771,67910,80275|9,0:288,4476,4699,8473,12378,20623,21261,21550,21578,25151,25215,25273,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_165_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"o2_t\" rd=\"11,0:7517\"/><wd nm=\"o_actual_chunk_opt_mode\" rd=\"12,0:11963\"/><wd nm=\"o_bluegreen_txt\" rd=\"0,0:81,102\"/><wd nm=\"o_by_idx\" rd=\"6,0:13223,14944|10,0:4509\"/><wd nm=\"o_by_idx_f\" rd=\"6,0:13242|10,0:4528\"/><wd nm=\"o_by_name\" rd=\"6,0:13340,15087|10,0:4605\"/><wd nm=\"o_by_name_f\" rd=\"6,0:13360,15107|10,0:4625\"/><wd nm=\"o_chunk_opt\" rd=\"7,0:8667|12,0:11869\"/><wd nm=\"o_chunk_opt_num\" rd=\"7,0:8769|12,0:11896\"/><wd nm=\"o_chunk_opt_ratio\" rd=\"7,0:8864|12,0:11927\"/><wd nm=\"o_collective_opt\" rd=\"7,0:8957\"/><wd nm=\"o_dtype\" rd=\"8,0:22772,97474,97673,98129,100468,100624,100798,100937\"/><wd nm=\"o_f\" rd=\"5,0:13902,14551|6,0:13148,14610,16786,16887|7,0:8560,8619|10,0:4442|11,0:2101,2967\"/><wd nm=\"o_float_dscale\" rd=\"7,0:89879\"/><wd nm=\"o_idx_f\" rd=\"6,0:13430,13539,13697\"/><wd nm=\"o_info_t\" rd=\"6,0:27867|10,0:10387\"/><wd nm=\"o_int\" rd=\"7,0:86601\"/><wd nm=\"o_int_minimumbits_default\" rd=\"7,0:86613\"/><wd nm=\"o_is_v2\" rd=\"11,0:1615\"/><wd nm=\"o_null\" rd=\"5,0:44024\"/><wd nm=\"o_t\" rd=\"6,0:27855,27867|7,0:48669,48862|10,0:10387|11,0:6640,7116\"/><wd nm=\"o_target\" rd=\"6,0:25525,25607\"/><wd nm=\"o_text\" rd=\"8,0:22851,97527,97769,98149\"/><wd nm=\"oach\" rd=\"6,0:
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_169_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ompound_1\" rd=\"8,0:101023\"/><wd nm=\"ompound_2\" rd=\"8,0:101055\"/><wd nm=\"ompound_f\" rd=\"8,0:45181,54510,55150,55283,55414\"/><wd nm=\"ompound_type\" rd=\"8,0:98369,99480,100299\"/><wd nm=\"ompo­sition\" rd=\"7,0:35866\"/><wd nm=\"omprehensive\" rd=\"5,0:5929|12,0:20770\"/><wd nm=\"ompress\" rd=\"7,0:59962,60123,60161,60201,60242,60324,60697,61346,61779,67396,67407\"/><wd nm=\"ompressed\" rd=\"3,0:8291|4,0:25902,26003,26340,26786,26944|7,0:35677,60403,60443,60463,61264,61287,69715,74009,77244,78933,79964,83467,83539,85973,89191,91768|10,0:14140,16308|12,0:9347\"/><wd nm=\"ompressed_data\" rd=\"4,0:20714,21137,21477,21620,21855,22035,22095,22261,22317\"/><wd nm=\"ompresses\" rd=\"7,0:55873,55886,60947,75985\"/><wd nm=\"ompressing\" rd=\"7,0:55262\"/><wd nm=\"ompression\" rd=\"1,0:3547,3633|3,0:1960,3509,7985,13027|4,0:20816,20834,20867,25423,25682,26354,26806,27048,27744,27893|5,0:27366|6,0:16279,16299|7,0:4799,4819,6360,13100,14026,25151,29288,29660,29677,29703,29720,29818,29835,29904,29921,29985,34886,56319,56343,57311,57710,58680,59907,59937,60599,62172,62194,62236,62285,62386,62509,62887,63894,63907,64238,64252,65221,66111,67258,67272,67303,67317,67575,67589,67653,67745,67833,67906,67955,68105,70007,71063,71576,74302,75364,76468,76778,76837,77592,77824,78544,78559,78597,78677,78696,78818,78837,78950,78971,79001,79023,79772,79800,79887,79929,80268,80382,80407,80472,80569,81196,81690,81704,81830,82407,83721,83853,83867,84199,84217,84230,84401,84414,84492,84958,86446,87595,88130,89667,90776,91308,9
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_170_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"on_f\" rd=\"5,0:6978,7314,11172|6,0:12780|7,0:2802|8,0:16948,18740,18816\"/><wd nm=\"on_ge\" rd=\"5,0:7487\"/><wd nm=\"on_le\" rd=\"5,0:7615\"/><wd nm=\"on_obj\" rd=\"8,0:70468\"/><wd nm=\"on_order\" rd=\"6,0:10684,17136,17247|10,0:6091,6312|12,0:22157,22489\"/><wd nm=\"on_order_f\" rd=\"6,0:17163,17274|10,0:6118,6339|12,0:22184,22516\"/><wd nm=\"on_t\" rd=\"11,0:8980\"/><wd nm=\"onable\" rd=\"4,0:14555|5,0:32492|12,0:6939\"/><wd nm=\"onably\" rd=\"4,0:325\"/><wd nm=\"onal\" rd=\"0,192:0,238,355|1,192:0,1150,1783,2066,2250,2506,4057,4174|2,192:0,299,416|3,64:4761,4868,7357,8561,9983,12506,21279|4,64:265,7401,8498,9661,10404,10453,10634,10692,11697,11848,11981,28195|5,64:5365,18220,25961,29066,29136,30059,31052,31692,31762,31984,32267,32337,34704,36973,39907,41240,41312,42457,46260|6,64:22526,32171|7,64:298,317,10199,12963,13148,13546,13731,13747,13965,14129,19202,19388,20286,20440,22543,22706,25130,25304,25939,26468,29176,29262,29408,31310,32172,32757,33713,34396,35311,37705,39250,39516,40616,50965,51834,52214,53956,92424|8,64:6151,6206,8047,29086,36675,45817,59787,60583,61593,62049,62330,62604,62729,63055,64110,67526,67632,67771,67910,80275,87429,101216|9,64:288,4476,4699,8473,10386,12378,20623,21261,21550,21578,25151,25215,25273,25295,25398,25806,25828,30304,30348,34190,34232,44362|10,64:2782,3284,16698,16741,17871|11,64:18724|12,64:530,1738,2721,14882,15700,17599,24871,26090,27745|13,192:0,21,62,134,1541,1658\"/><wd nm=\"onality\" rd=\"5,0:31284|7,0:842|8,0:9
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_172_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"operations\" rd=\"0,128:17,372|1,128:17,4191|2,128:17,433|3,0:14983,15680|4,0:740,910,22668,26074,26146|5,0:34781,34918|6,0:2856,2937,3157,18325|7,0:1417,9818,9890,10082,10182,10919,11079,11193,11255,11386,16275,16381,24938,26135,26242,26721,26856,26908,31175,33053,34154,36287,59782|8,0:5337,13464,16596,24083|9,0:437,627,6675,6955,15947,25643,31941,31983,32460|11,0:280,514,1196,1254,3380,3960,11662,11710,11751,11881|12,0:1826,2242,12750,17621,17648,17729,20842,26173|13,0:799,968\"/><wd nm=\"operator2_t\" rd=\"10,0:11095\"/><wd nm=\"operator_t\" rd=\"10,0:11600\"/><wd nm=\"operator’s\" rd=\"10,0:11670\"/><wd nm=\"opera­tion\" rd=\"7,0:27351,49377\"/><wd nm=\"opera­tions\" rd=\"12,0:26491\"/><wd nm=\"operly\" rd=\"11,0:11347|12,0:27169,27261\"/><wd nm=\"opers\" rd=\"5,0:19998|11,0:11008\"/><wd nm=\"opert\" rd=\"12,0:13930\"/><wd nm=\"operti\" rd=\"5,0:1877|12,0:23562\"/><wd nm=\"opertie\" rd=\"12,0:12221\"/><wd nm=\"operties\" rd=\"3,0:5946,6100,6163,6266,6329,7862,7919,7958,8228,9508,11782,12026,12831,12895,12984,13070,13166|4,0:2629,2662,3949,6604,14871,14938,15301,15395,17434,18192,18440|5,0:2123,2259,2321,2527,2815,2874,4592,4883,4954,11423,15530,15762,18391,18653,18891,19003,19485,19585,19690,20550,20911,21094,21283,21546,21587,21956,28869,29027,29746,29803,30266,30566,31497,31653,32077,32228,32949,33059,33145,33299,35493,35556,35629,35712,36178,36235,36273,36746,36809,39044,39124,39485,39541,39782,40174,40233,40287,40336,40382,40432,40488,41150,41225,41680,41772,41928,42692,43119,43219,43253|7,0:
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_175_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ose_degree\" rd=\"4,0:6340|5,0:11685\"/><wd nm=\"ose_degree_f\" rd=\"5,0:11710\"/><wd nm=\"ose_f\" rd=\"5,0:7052,7917|6,0:13014|7,0:2986|8,0:18098|9,0:1310,42263,42329,42380,42438,43852,43918,43969,44027|10,0:4083|12,0:21939\"/><wd nm=\"ose_msg\" rd=\"11,0:1877,15164,15967,15989\"/><wd nm=\"ose_stack\" rd=\"11,0:1945,17401\"/><wd nm=\"ose_strong\" rd=\"4,0:6235\"/><wd nm=\"osed\" rd=\"1,0:3016|3,0:9897|4,0:1006,1023,2269,4307,4799,4825,5201,5291,5370,5408,5517,5559,5844,6140,6164,6297|5,0:288,16025,17801,17989,18032,18068,26142,33538,33652,33967,34083,44731|6,0:10926,22300|7,0:64,10039,10946,11220,11306,11355,48231|8,0:46448,82364,85594,85709,88325,88359|9,0:12184,23012|10,0:11658,12503,12575|11,0:11629,12395,16742|12,0:17318\"/><wd nm=\"osely\" rd=\"8,0:97848\"/><wd nm=\"osen\" rd=\"6,0:19782\"/><wd nm=\"oses\" rd=\"1,0:518,3511|3,0:3126|4,0:4412,6263|5,0:7084,7929,16797,17279,17553,24564|6,0:11714,13026,24810|7,0:2998|8,0:3171,97274|9,0:11527,11796,39218|10,0:4095,11887,12694|11,0:1913,1983,15203,15853,17446|12,0:21951\"/><wd nm=\"oset_comment\" rd=\"6,0:15210\"/><wd nm=\"osh\" rd=\"5,0:35947|6,0:410\"/><wd nm=\"osing\" rd=\"3,0:6353|4,0:2472,4142,4730,4911,5565|5,0:367,3950,5630,5665,5770,16767,17182,42543|6,0:21691|8,0:80093|10,0:1826,12393,12602|11,0:15916\"/><wd nm=\"osite\" rd=\"3,0:9876|4,0:11569|7,0:71039,75340,80442,87571,90752|8,0:2952,5900,5919,5982,60
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_176_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"oun\" rd=\"4,0:14059\"/><wd nm=\"ound\" rd=\"4,0:14078,14182,14220,14284,14401,14470,14597,14647,14656,14716,14883,14916,15042,15283,15326,15377,15435,15453,15530,15593,15706,15919,16235,16340,16520|5,0:45512|6,0:3239,10207|7,0:430,7009,32437,37154,37820,54260,55329,55386,55422,55459,59876,60224,61310,61373,61597,62029,62995,63034,63093,63518,64801,64888,65022,65586,65607,66622,66643,66728,66786,66843,67160,67181,76169|8,0:217,6107,8104,8730,15742,20828,20920,21021,21077,21209,21306,21390,21491,21603,21743,21817,24285,26755,30425,30456,30541,30568,30660,30695,30772,30823,30899,32548,32671,42000,42057,42100,42125,42143,42216,42320,42414,42440,42486,43368,43461,43690,43781,43842,43906,44046,44104,44306,44447,44675,44896,45402,45970,46096,46213,46278,46326,46432,46501,46556,46581,46656,46681,46813,47004,47193,47428,47453,47544,47852,48560,48663,48898,49038,49117,49359,49449,49681,49809,49838,49869,49896,50102,50220,50258,50382,50462,50627,50687,50884,51128,51387,51412,51475,51715,52358,52465,53009,53072,53331,53390,53539,54088,54212,54918,55086,55816,55853,56151,56191,56258,56323,56540,56609,56674,56950,57277,57519,57926,58275,58337,58420,58538,58727,58930,59025,59211,60001,60667,61341,75587,75684,76426,76523,77041,77874,78219,78820,78862,78934,78998,79221,79340,79473,79611,79697,79890,79992,80032,80153,80193,80233,80727,80779,80830,80982,81101,81244,81537,81749,82004,82348,82543,82991,83095,83121,83135,83225,83468,83538,83894,84002,84031,84166,84328,84544,84631,84653,84867,94737,94939,94980,95317,9
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_179_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"pace1_dim1\" rd=\"8,0:65817,65900,69584,69668,71394\"/><wd nm=\"pace1_rank\" rd=\"4,0:12676|9,0:26190\"/><wd nm=\"pace_f\" rd=\"5,0:8385|7,0:3038|10,0:4841\"/><wd nm=\"pace_fig10\" rd=\"9,0:23860,23875\"/><wd nm=\"pace_fig14\" rd=\"9,0:25312,25327\"/><wd nm=\"pace_fig16a\" rd=\"9,0:26830,26846\"/><wd nm=\"pace_fig16b\" rd=\"9,0:26865,26881\"/><wd nm=\"pace_fig16c\" rd=\"9,0:26900,26916\"/><wd nm=\"pace_fig19a\" rd=\"9,0:30946,30962\"/><wd nm=\"pace_fig19b\" rd=\"9,0:30981,30997\"/><wd nm=\"pace_fig19c\" rd=\"9,0:31016,31032\"/><wd nm=\"pace_fig1new\" rd=\"9,0:5626,5643\"/><wd nm=\"pace_fig21\" rd=\"9,0:33707,33722\"/><wd nm=\"pace_fig22\" rd=\"9,0:33790,33805\"/><wd nm=\"pace_fig23\" rd=\"9,0:34377,34392\"/><wd nm=\"pace_fig2a\" rd=\"9,0:13947,13962\"/><wd nm=\"pace_fig2b\" rd=\"9,0:14032,14047\"/><wd nm=\"pace_fig2c\" rd=\"9,0:14158,14173\"/><wd nm=\"pace_fig2d\" rd=\"9,0:14247,14262\"/><wd nm=\"pace_fig4\" rd=\"9,0:17018,17032\"/><wd nm=\"pace_fig5\" rd=\"9,0:17087,17101\"/><wd nm=\"pace_fig6\" rd=\"9,0:20724,20738\"/><wd nm=\"pace_fig7\" rd=\"9,0:21064,21078\"/><wd nm=\"pace_fig8\" rd=\"9,0:21325,21339\"/><wd nm=\"pace_fig9\" rd=\"9,0:21662,21676\"/><wd nm=\"pace_id\" rd=\"7,0:24379,24573|8,0:13297,51150,54980,76342,92228,92242|9,0:7690,7701,7760,7799,8190
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_181_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"pecial\" rd=\"3,0:6752,18817|5,0:2342,2895,26654,27472|6,0:4121,6890,6950|7,0:84344|8,0:67180,68980|9,0:33003|10,0:346,1076,1347,1477,1845,12784,17470,17650\"/><wd nm=\"pecialized\" rd=\"7,0:29862|8,0:40333|12,0:11159\"/><wd nm=\"pecially\" rd=\"7,0:42372\"/><wd nm=\"pecific\" rd=\"1,0:1404,3106|3,0:2092,4351,4915,9495,11769|4,0:753,870,27269|5,0:21904|6,0:21127,22475|7,0:25876,35826|8,0:869,911,1244,2331,2598,2667,4113,9106,16183,26448,31795,32369,33237,33325,56789|9,0:22965|11,0:5050|12,0:623,797,6459,21276|13,0:103\"/><wd nm=\"pecifically\" rd=\"5,0:19951\"/><wd nm=\"pecification\" rd=\"3,0:959,3395,3828,13296,13327,13745,14099,14674,14834|5,0:28427|7,0:25348,38176,52277|8,0:75286,95747|9,0:7354,10934\"/><wd nm=\"pecifications\" rd=\"8,0:116\"/><wd nm=\"pecifica­tion\" rd=\"3,0:4090\"/><wd nm=\"pecified\" rd=\"3,0:11503,14472|5,0:7597,8850,10784,11645,15540,27754,33387,42784|6,0:4875,13035,14581,14743,14891,15265,15359,15921,18065,28318,28383|7,0:2713,3007,5818,12981,16783,16879,17604,36991,39425,41017,41129,49972,57519|8,0:12985,14195,17689,18250,20524,21685,24526,31376,31505,40736,68618,77376,90622,90680,91873|9,0:1235,4949,16519,17208,23460|10,0:3875,4104,4319,5328,5454,11200,11243,11272,12177,12703|11,0:2569,3287,5686,5713,6051,6763,14950,16663|12,0:21719,21807,21907,21960,23248\"/><wd nm=\"pecifier\" rd=\"5,0:36056\"/><wd nm=\"pecifies\" rd=\"4,0:19980,20021,20229|5,0:4413,14718,20734,36363|6,0:17429,19663|7,0:1
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_182_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"pert\" rd=\"12,0:13930\"/><wd nm=\"perti\" rd=\"5,0:1877|12,0:23562\"/><wd nm=\"pertie\" rd=\"12,0:12221\"/><wd nm=\"perties\" rd=\"3,0:5946,6100,6163,6266,6329,7862,7919,7958,8228,9508,11782,12026,12831,12895,12984,13070,13166|4,0:2629,2662,3949,6604,14871,14938,15301,15395,17434,18192,18440|5,0:2123,2259,2321,2527,2815,2874,4592,4883,4954,11423,15530,15762,18391,18653,18891,19003,19485,19585,19690,20550,20911,21094,21283,21546,21587,21956,28869,29027,29746,29803,30266,30566,31497,31653,32077,32228,32949,33059,33145,33299,35493,35556,35629,35712,36178,36235,36273,36746,36809,39044,39124,39485,39541,39782,40174,40233,40287,40336,40382,40432,40488,41150,41225,41680,41772,41928,42692,43119,43219,43253|7,0:10348,11051,11503,11562,11578,12748,12766,12863,12883,14955,16590,16746,17808,19170,19302,19317,19436,19539,19551,20302,21446,23509,23652,24093,24714,25419,26434,30448,30503,32117,32159,32260,33428,33521,33650,37624,39316,40503,40542,42137,44449,49406,55916,69420,69451,70704,72612,72699,72749,73717,73748,75000,85680,85711,87234,88897,88928,90413|8,0:3729,3792,3901,4007,4262,4424,4473,5094,5745,6003,6317,6399,6621,6653,7060,7075,12850,14866,14968,15114,15182,15904,18609,21093,25957,26149,26219,26297,26324,26388,26483,26591,27765,27949,28324,29446,29882,29997,30095,30262,30334,31867,32080,32508,32815,33146,33181,33227,33393,35483,35606,35890,37043,37962,40163,75792,77257,91185,93252,93307|9,0:40220,40253,40572,40735,41827,42008,43416,43597|12,128:0,34,87,555,805,950,1085,1387,1592,1850,1921,2491,3369,3447,3979,4316,5326,5454,5568,5658,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_184_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"pl_mpio_collective_opt\" rd=\"7,0:8957\"/><wd nm=\"pl_mpio_f\" rd=\"5,0:13902|7,0:8560,8619\"/><wd nm=\"pl_mpiposix\" rd=\"5,0:14008,14072\"/><wd nm=\"pl_mpiposix_f\" rd=\"5,0:14029,14093\"/><wd nm=\"pl_multi\" rd=\"5,0:14143,26679,38986,39006,39158,39309,39451,39801,39821\"/><wd nm=\"pl_multi_f\" rd=\"5,0:14165\"/><wd nm=\"pl_sec2\" rd=\"5,0:14291,25443,28836,28968,29200|12,0:10209,11118\"/><wd nm=\"pl_sec2_f\" rd=\"5,0:14308\"/><wd nm=\"pl_split\" rd=\"5,0:14404,26866,40128,40264,40398,41377|12,0:10331,27368\"/><wd nm=\"pl_split_f\" rd=\"5,0:14422\"/><wd nm=\"pl_stdio\" rd=\"5,0:5539,14533,25988,32043,32169,32401\"/><wd nm=\"pl_stdio_f\" rd=\"5,0:14551\"/><wd nm=\"pl_windows\" rd=\"5,0:14609,25824,31461,31591,31826\"/><wd nm=\"pla_id\" rd=\"12,0:14220,14413,14572,14642,14711,14732,14825,15216,15396,15476,15550,15684,15775,16036,16896,17531,17978,18076\"/><wd nm=\"plab_id\" rd=\"12,0:15059,16010,16131,16886,16974,17583\"/><wd nm=\"place\" rd=\"5,0:44667|6,0:11827|7,0:67682|9,0:9250|10,0:7194|11,0:16517,18510\"/><wd nm=\"placed\" rd=\"5,0:36076|7,0:35946\"/><wd nm=\"placement\" rd=\"6,0:12533\"/><wd nm=\"places\" rd=\"6,0:13878,13965,14076,14237,14314,14653,14766,14912,15056,15280,15374,15443,15509|8,0:87523|11,0:3116,16614|12,0:24978\"/><wd nm=\"plained\" rd=\"3,0:12691\"/><wd nm=\"plains\" rd=\"3,0:620|7,0:95
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_187_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"primarily\" rd=\"8,0:15658\"/><wd nm=\"primary\" rd=\"4,0:22586|6,0:2849|10,0:123,141,418,2559,2888,3181,3388\"/><wd nm=\"prime\" rd=\"1,0:2131\"/><wd nm=\"print\" rd=\"9,0:15869|11,0:906,2618,5271,5381,5452,5464,5591,5616,6224,6382,6974,7949,8054,8091,8251,8502,8758\"/><wd nm=\"print_cb\" rd=\"11,0:10250,13396\"/><wd nm=\"print_f\" rd=\"11,0:2627\"/><wd nm=\"printed\" rd=\"11,0:4047,4515,5350,5780,6478,7889\"/><wd nm=\"printf\" rd=\"4,0:13696,13781,13839,24033,24718|5,0:36027,37465|7,0:68670,68766,68944,69306,69542,69829,69937,70151,70460,70796,70923,71167,73100,73193,73296,73375,73450,73605,73839,74123,74232,74445,74756,75097,75224,75472,85567,85801,86087,86195,86355,86649,87056,87328,87455,87701,88784,89019,89305,89413,89576,89907,90231,90509,90636,90884|8,0:15286,15348,15387,15411,15459,15498,15524,15563,15580,65918,65978,69686,78476,78519,78562,84646,84731,84754,84987,85233|9,0:38924,38971,39000,39029|11,0:8572,10691,10812,10860,10908,13837,13958,14006,14054\"/><wd nm=\"printing\" rd=\"3,0:19012|6,0:7191|11,0:3001,5495,6537,6587,6731,6951,7827,7928,8146\"/><wd nm=\"prints\" rd=\"5,0:37509|8,0:15081|11,0:2639,5667,8298\"/><wd nm=\"prior\" rd=\"1,0:1412|10,0:12581\"/><wd nm=\"priori\" rd=\"8,0:55926\"/><wd nm=\"prising\" rd=\"7,0:1053\"/><wd nm=\"private\" rd=\"3,0:10212|7,0:62664,62718,64683,67358\"/><wd nm=\"privately\" rd=\"1,0:3064\"/><wd nm=\"privileges\" rd=\"5,0:222\"/><wd nm=\"pri­ate\" rd
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_189_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ptable\" rd=\"7,0:14160\"/><wd nm=\"pted\" rd=\"4,0:25915,25993|5,0:17053,17317,23569|8,0:73742,74072\"/><wd nm=\"pter\" rd=\"3,0:613|4,0:184,6991|5,0:55,299,482,547,21683|6,0:1732,11873|8,0:472,87451|9,0:517,1036,7202,39589|10,0:1495|12,0:1550,1797,2187,2308,21310,21362,21509,25116,25156,25460,25533\"/><wd nm=\"pters\" rd=\"4,0:2084|12,0:1948,2351\"/><wd nm=\"pth\" rd=\"8,0:63285,78772\"/><wd nm=\"pti\" rd=\"12,0:26833\"/><wd nm=\"ptimal\" rd=\"6,0:11405|8,0:59705|12,0:11998,13653\"/><wd nm=\"ptimization\" rd=\"12,0:11137\"/><wd nm=\"ptimizations\" rd=\"12,0:11183\"/><wd nm=\"ptimize\" rd=\"12,0:11729\"/><wd nm=\"ptimizing\" rd=\"12,0:8084\"/><wd nm=\"ption\" rd=\"3,0:4839,4901,16335|4,0:5897,6176,25694|5,0:22898,23793,25211|6,0:2095,2252,3439,27823|7,0:132,1172,13602,13763,13909,19563,23905,27230,29643,31272,33929,36503,39098,42546,43154,43236,43774,44257,49824,70027,74322,86467,89745|8,0:240,6640,8865,10167,12457,12717,15091,17964,18059,22838,22906,24125,26631,27996,29492,29928,30377,33433,35647,37083,38002,74119,79295,80110,89245,90801,91267,91807,94217,95093,97078,97138,97240,97577,97905,98175,100589,100902|9,0:1405,1502,20051|11,0:250,5135,5256,10077|12,0:17378|13,0:1351\"/><wd nm=\"ptional\" rd=\"3,0:12506|5,0:5365|7,0:10199,12963,13546,13731,13747,13965,14129,19388,20286,20440,22543,22706,25130,29176,29262,29408,31310,32172|9,0:10386|10,0:2782,3284\"/><wd nm=\"ptionally\" rd=\"3,0:10232|4,0:20219|6,0:19653\"/><wd nm=\"ptions\" rd=\"3,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_192_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"rating\" rd=\"3,0:1795,11611|4,0:2312,9031|5,0:6195,14210|6,0:11454,20563|8,0:97038,97106|10,0:1768,10628\"/><wd nm=\"ratio\" rd=\"7,0:8864,8925|12,0:11927\"/><wd nm=\"ration\" rd=\"1,0:1987,2666|3,0:16819|4,0:2927,2967|5,0:8663,10885,12274,12417,42932|6,0:3225,4212,4308|7,0:11481,16966,17048,17129,19484,19796,27617,28398,28431,29530,35107,36542,55648,56778,60584,76505,84079|8,0:7580,7700,20259,20363,20428,20543,20651,20734,20839,20930,21031,21220,21400,21501,31395,31523,31627,41130,43021,69102,71796,71917,72029,72482,73104,73207,90812,90996,91646,93856,94356,94510,94597,94669|9,0:503,16396,16469,16712,16915,17008,22852,32016|10,0:9104,10712,10867,10927,11231,11575|11,0:13305|12,0:3001,9960,16294,16569\"/><wd nm=\"rations\" rd=\"0,128:17,372|1,128:17,4191|2,128:17,433|3,0:14983,15680|4,0:740,910,22668,26074,26146|5,0:34781,34918|6,0:2856,2937,3157,18325,22158|7,0:1417,9818,9890,10082,10182,10919,11079,11193,11255,11386,16275,16381,24938,26135,26242,26721,26856,26908,31175,33053,34154,36287,59782|8,0:2847,5337,13464,16596,24083,74493,93993|9,0:437,627,6675,6955,15947,25643,31941,31983,32460|11,0:280,514,1196,1254,3380,3960,11662,11710,11751,11881|12,0:1826,2242,12750,17621,17648,17729,20842,26173|13,0:799,968\"/><wd nm=\"ratios\" rd=\"7,0:8083,8141,8180,8238,32568,32606,32651\"/><wd nm=\"ratios_f\" rd=\"7,0:8103,8200\"/><wd nm=\"rative\" rd=\"6,0:28097,28578|10,0:11526\"/><wd nm=\"rator\" rd=\"3,0:19202,19239,19296|6,0:7383,7420,7477\"/><wd nm
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_195_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"recision\" rd=\"7,0:54533,54853,55214,56539,56633,56863,57128,57167,57492,57691,58363,58402,58875,60903,61211,63454,65964,68469,68528,68584,68599,68629,68655,68692,69084,69178,71931,72140,72175,72290,72670,73238,73255,73281,73318,82737,84054,84120|8,0:6717,6820,7313,7442,8620,18723,18770,18799,18843,27222,27254,27613,27747,32266,33838,34109,34142,34323,34547,35163,35465,37171,37214,37247,37262,38461,38701,40023,40366,40510,41315,41813,44803,44960,44987,53648,53880,54784,74901\"/><wd nm=\"recision_f\" rd=\"8,0:18740,18816\"/><wd nm=\"reci­sion\" rd=\"8,0:34868,38205,39181\"/><wd nm=\"reclaim\" rd=\"7,0:3765,8392,8525,47188,49332|8,0:64886,65358,66036,69753\"/><wd nm=\"reclaim_f\" rd=\"7,0:3781\"/><wd nm=\"reclaimed\" rd=\"3,0:18301,21133|6,0:5628\"/><wd nm=\"reclaiming\" rd=\"7,0:47100,47254\"/><wd nm=\"reclaims\" rd=\"7,0:3800\"/><wd nm=\"recognize\" rd=\"3,0:15763\"/><wd nm=\"recommended\" rd=\"7,0:41897,42871,43242,43359,43408,91808\"/><wd nm=\"recom­mendation\" rd=\"1,0:3247\"/><wd nm=\"reconciled\" rd=\"9,0:21982\"/><wd nm=\"reconstruct\" rd=\"3,0:13676\"/><wd nm=\"record\" rd=\"3,0:7637|4,0:14464|8,0:59960,79777,80672,81025,81179|11,0:342,2775,3578,3688,4283,4833,5120,12079,12622,12828,16785,16968,17587|12,0:739,8374\"/><wd nm=\"recorded\" rd=\"12,0:22479\"/><wd nm=\"recording\" rd=\"12,0:22747\"/><wd nm=\"records\" rd=\"5,0:30609,30777,30822|7,0:38140|8,0:6135,42620|9,0:12114,37618|11,0:1315,3461,3473,3885,11798,11937,12109,12891,16118,1613
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_198_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"rforming\" rd=\"7,0:53002|8,0:93035|10,0:11218\"/><wd nm=\"rforms\" rd=\"4,0:26058|5,0:30755|7,0:26713,60566,76479,83748|8,0:66248\"/><wd nm=\"rful\" rd=\"4,0:14503\"/><wd nm=\"rg\" rd=\"1,0:3729|2,0:183\"/><wd nm=\"rganization\" rd=\"3,0:782,3844|5,0:3584,24310|7,0:25438,26888|8,0:6028\"/><wd nm=\"rganize\" rd=\"4,0:17219|9,0:32086\"/><wd nm=\"rganized\" rd=\"3,0:3446,5277,5377,13760,16614|6,0:3965|7,0:13803,25292,30328,48544|8,0:3463,23663|9,0:17274\"/><wd nm=\"rganizing\" rd=\"3,0:21026|4,0:18956|6,0:31993|9,0:31685,31852\"/><wd nm=\"rge\" rd=\"3,0:1092,11409|5,0:22090,23117,35016,38606|6,0:8832,9395,9407|7,0:17376,35898,91871,92030|8,0:77948|9,0:18100,20527,33444|10,0:1406,1431,12828,12982,14151,14497,14789,14854,15773,15858,15951,16107,16255,16351,16508,16915|12,0:14873\"/><wd nm=\"rge_committed_dtype_path\" rd=\"12,0:22811\"/><wd nm=\"rge_committed_dtype_paths\" rd=\"12,0:22962\"/><wd nm=\"rger\" rd=\"5,0:13756,22474,26435,35076,38528|7,0:39907,52831,54104,61096,61150,92189|8,0:28578,36156,48232|9,0:20614,21932|10,0:14294\"/><wd nm=\"rgest\" rd=\"9,0:9642\"/><wd nm=\"rget\" rd=\"3,0:16971|5,0:8679,8740,9581,9663,44843,44909,45227,45345|6,0:4403,6066,6111,6204,6399,20345,22628,22769,22869,24941,25525,25607,26331,31509,31870|7,0:1547|9,0:34329,36842,36953,38019\"/><wd nm=\"rget_region\" rd=\"9,0:38410,38505\"/><wd nm=\"rget_select\" rd=\"9,0:3321
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_199_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ring_create\" rd=\"12,0:4689\"/><wd nm=\"ring_out\" rd=\"4,0:24705,24767\"/><wd nm=\"ringe\" rd=\"1,0:3056\"/><wd nm=\"ringent\" rd=\"5,0:32660\"/><wd nm=\"rings\" rd=\"7,0:48742|8,0:2860,2871,7644,20232,33303,37632,37697,37740,63529,63604,67205,67261,67330,67434,67547,68658,68761,69419,69440,69552,69564,74483,93527,93564|9,0:4499\"/><wd nm=\"rint\" rd=\"9,0:15869|11,0:906,2618,5271,5381,5452,5464,5591,5616,6224,6382,6974,7949,8054,8091,8251,8502,8758\"/><wd nm=\"rint_cb\" rd=\"11,0:10250,13396\"/><wd nm=\"rint_f\" rd=\"11,0:2627\"/><wd nm=\"rinted\" rd=\"11,0:4047,4515,5350,5780,6478,7889\"/><wd nm=\"rintf\" rd=\"4,0:13696,13781,13839,24033,24718|5,0:36027,37465|7,0:68670,68766,68944,69306,69542,69829,69937,70151,70460,70796,70923,71167,73100,73193,73296,73375,73450,73605,73839,74123,74232,74445,74756,75097,75224,75472,85567,85801,86087,86195,86355,86649,87056,87328,87455,87701,88784,89019,89305,89413,89576,89907,90231,90509,90636,90884|8,0:15286,15348,15387,15411,15459,15498,15524,15563,15580,65918,65978,69686,78476,78519,78562,84646,84731,84754,84987,85233|9,0:38924,38971,39000,39029|11,0:8572,10691,10812,10860,10908,13837,13958,14006,14054\"/><wd nm=\"rinting\" rd=\"3,0:19012|6,0:7191|11,0:3001,5495,6537,6587,6731,6951,7827,7928,8146\"/><wd nm=\"rints\" rd=\"5,0:37509|8,0:15081|11,0:2639,5667,8298\"/><wd nm=\"rio\" rd=\"6,0:26757,26949\"/><wd nm=\"riod\" rd=\"6,0:6912\"/><wd nm=\"rior\" rd=\"1,0:1412|10,0:12581\"/><wd nm=\"riori\" rd=\"8
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_1_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\")\" rd=\"1,0:139,197,291,526,1831,1902,1932,1966,2002,2089,2275,2532,2572,2607,2659|3,0:110,226,1190,1669,1870,2491,4224,4655,4749,5121,7153,7385,7479,7542,7745,8850,9152,10382,10606,11289,12090,12148,12591,13112,14262,14904,15506,17327,17818,17949,18874,18955|4,0:310,2751,2774,3690,3803,3847,4135,4313,4534,4553,4574,5376,6690,8893,9149,10036,10103,10164,10329,11168,11383,11458,11472,12390,12403,12440,12608,12698,12936,13067,13331,13619,13671,13695,13725,13755,13780,13806,13836,13860,13893,14033,14669,15947,16199,16542,16585,16605,16653,16673,16925,16977,17033,18020,18257,18302,18545,18894,19383,19789,19905,21014,21051,21080,21105,21208,21453,21691,22122,22244,22344,23252,23340,23413,23466,23510,23985,24030,24094,24114,24632,24657,24679,24715,24777,25317,26656,27008|5,0:1273,1551,3648,4391,4602,4858,4931,5032,5373,5530,5567,5624,5812,6768,6787,6825,6853,6923,7521,7649,7776,7861,8473,8544,8634,8731,8810,9218,9542,9631,9844,10638,10870,10982,11096,11316,11584,12017,12245,12381,12742,13105,13178,13319,13448,13852,13965,14649,14715,14830,15231,16132,17122,19086,19409,19444,19794,19842,20417,20494,23490,23606,24557,25002,27403,28029,28171,28526,28997,29615,29708,30414,31016,31623,32199,32448,33115,33181,33204,33572,33724,35646,35729,36036,36145,37621,37696,37925,38163,38172,38186,39301,39448,41846,41912,43322,43363,43599,43631,43700,43722,43976,44037,44127,44186,45853|6,0:1796,1849,2680,3380,3807,3921,6561,6918,6973,7134,9621,9761,10330,10710,11142,11404,12361,12420,12505,12518,12609,13428,13639,13755,13769,14137,14204,14460,14709,14983,15245,15339,15593,15675,16278,17551,18004,18144,18586,18913,19399,19466,19547,19623,20668,20834,21009,21052,21101,21449,21549,21588,2168
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_204_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"rs_avail\" rd=\"6,0:15634|7,0:5456\"/><wd nm=\"rs_f\" rd=\"6,0:13517,13564,13641,16009|7,0:5560|8,0:20778,21159\"/><wd nm=\"rsa\" rd=\"4,0:15942|8,0:43713|9,0:11130,30856\"/><wd nm=\"rsal\" rd=\"6,0:28710|8,0:66265|11,0:2166,7218,8215,9243,9428,9513\"/><wd nm=\"rsally\" rd=\"7,0:53507\"/><wd nm=\"rsals\" rd=\"6,0:17049,17123\"/><wd nm=\"rse\" rd=\"1,0:1350|6,0:22825|7,0:40219,60577|8,0:65393|9,0:17537,21312|10,0:9015,9206|11,0:9374|12,0:12425,13507\"/><wd nm=\"rsed\" rd=\"3,0:19783|6,0:28615,31059|8,0:64853|11,0:9063\"/><wd nm=\"rsely\" rd=\"7,0:43125\"/><wd nm=\"rsement\" rd=\"1,0:3235,3500\"/><wd nm=\"rses\" rd=\"11,0:8840\"/><wd nm=\"rship\" rd=\"3,0:6797,7028,18024|6,0:2367,5366\"/><wd nm=\"rsing\" rd=\"8,0:66370\"/><wd nm=\"rsio\" rd=\"8,0:90177\"/><wd nm=\"rsion\" rd=\"3,0:6014,14180|4,0:4006|5,0:6962,7297,7544,7606,7672,7732,11157,11199,12761,21346,21456,21485,21517,26168|6,0:10200,10229,16611,16725|7,0:6996,7739,7835,22070,27463,27492,27583,27719,27845,28504,28648,32415,56138,56274,57582,57936,58946,58990,59146,59386,71960,83768|8,0:18147,18355,18404,18469,18534,18559,23434,23530,49347,49637,67085,90469,91465,92305,94189,94276,94342,94445,96997|10,0:12922|11,0:849,5917,14424\"/><wd nm=\"rsion_f\" rd=\"5,0:6978,7314,11172\"/><wd nm=\"rsion_ge\" rd=\"5,0:7487\"/><wd nm=\"rsion_le\" rd=\"5,0:7615\"/><wd n
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_205_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"rtran_s1\" rd=\"8,0:99311\"/><wd nm=\"rts\" rd=\"3,0:1291,13776|4,0:1724,7272,7311,11783,27494|5,0:26749,26829|7,0:618,32201,40261,48794,51005,51024,51874,51893,55355,55513,57203,58572,62424,76638,78531,81281,82952|8,0:1983,2928,5892,18231,20417,40288,40977,50508,91174,97811|9,0:4188,15053,28683,28717|10,0:6586,8302\"/><wd nm=\"rtual\" rd=\"3,0:15486|4,0:25297|5,0:3503,9257,24229,24389,24497,27584,34515|7,0:25664,27906,29495,30278,30913,31824|12,0:10045\"/><wd nm=\"rtunity\" rd=\"11,0:11459\"/><wd nm=\"rty\" rd=\"3,0:5055,11658,11686,11753,11796,11859,11940,12162,12248,12295,12425,12477,12612,12675,12745,12779,16442|4,0:1807,2375,2403,6204,6227,6255,18050,20783,27620,28070|5,0:401,434,1913,1994,2444,2473,2507,3001,3028,3089,4111,4144,4231,4301,4556,4807,5111,5323,6800,8108,8195,9819,10704,11249,11291,11664,11760,11925,12057,12311,12457,14852,15554,15610,15646,15707,16261,16398,16751,18206,18309,18328,18452,18480,18505,18574,18777,18817,18904,18937,19033,19103,19193,19237,19291,19317,19453,19608,20233,20422,20648,20726,21773,28102,29053,29829,29937,30449,30592,31679,32254,33240,33325,34198,34314,36261,36314,36771,36887,39567,39770,40514,40894,41136,41211,42112,42215,43397,43754,46011|6,0:10242,10294,10433,10608,10668,12365,13112,15568,17443,17574,18084|7,0:2517,3374,3465,4362,6891,8166,8263,9128,9218,10232,10282,10377,10420,14209,14271,15259,15284,15355,15487,15692,15842,19249,20519,20919,21698,21797,21857,22327,22796,23104,23799,30708,32336,32631,32835,32875,32926,33447,33585,33620,43218,43629,43948,48289,48994,49751,49996,50431,50648,5
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_206_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"rying\" rd=\"9,0:15471\"/><wd nm=\"rypted\" rd=\"4,0:25915,25993|8,0:73742,74072\"/><wd nm=\"ryption\" rd=\"4,0:25694|8,0:74119\"/><wd nm=\"rything\" rd=\"7,0:31806\"/><wd nm=\"ry’s\" rd=\"4,0:25522,26754|5,0:15730|7,0:44469|8,0:18322|11,0:4120,4249,12065,12720\"/><wd nm=\"ry”\" rd=\"8,0:44188,44572,44767,45339,45686,46165\"/><wd nm=\"r­acter\" rd=\"13,0:1219\"/><wd nm=\"r­age\" rd=\"3,0:15380|5,0:3601,24327|7,0:27554,36495,55817\"/><wd nm=\"r­allel\" rd=\"5,0:26940\"/><wd nm=\"r­ally\" rd=\"8,0:49472\"/><wd nm=\"r­archy\" rd=\"3,0:3055\"/><wd nm=\"r­cumstances\" rd=\"12,0:10777\"/><wd nm=\"r­ence\" rd=\"8,0:25569,70064|9,0:7041|10,0:13315\"/><wd nm=\"r­ent\" rd=\"8,0:63390\"/><wd nm=\"r­flow\" rd=\"8,0:91247,94208\"/><wd nm=\"r­form\" rd=\"10,0:9089\"/><wd nm=\"r­forms\" rd=\"7,0:60089\"/><wd nm=\"r­get\" rd=\"6,0:31476,31834\"/><wd nm=\"r­ify\" rd=\"12,0:10646\"/><wd nm=\"r­ing\" rd=\"10,0:14276\"/><wd nm=\"r­ious\" rd=\"7,0:38108\"/><wd nm=\"r­its\" rd=\"12,0:5552,5646\"/><wd nm=\"r­lying\" rd=\"8,0:73320\"/><wd nm=\"r­malization\" rd=\"8,0:28670,36259\"/><wd nm=\"r­mally\" rd=\"4,0:27154|7,0:53040\"/><wd nm=\"r­mat\" rd=\"5,0:9334\"/><wd nm=\"r­mats\" rd=\"6,0:9106|8,0:5573\"/><wd nm=\"r
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_208_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"sb_t\" rd=\"8,0:52045,52069,52120,52378,52420\"/><wd nm=\"sb_tid\" rd=\"8,0:52341,52396,52667\"/><wd nm=\"sbset\" rd=\"8,0:28705,36294\"/><wd nm=\"sc\" rd=\"11,0:9878,10064,10294,10509,10570,10638,10753,10774,10794,13440,13655,13716,13784,13899,13920,13940,16934\"/><wd nm=\"sc_t\" rd=\"8,0:52090,52114,52139,52485,52527\"/><wd nm=\"sc_tid\" rd=\"8,0:52448,52503,52727\"/><wd nm=\"scalar\" rd=\"4,0:23178,23208,23242,23354,23521,23672,23836|9,0:4231,4283,4299,4336,4557,7598,7615,7720,7869,15074,15328\"/><wd nm=\"scalar_f\" rd=\"9,0:7786\"/><wd nm=\"scale\" rd=\"7,0:6233,29892,29938,30856,53344,76419,76456,76488,76620,77089,77651,77778,77893,78724,81418,82912,83019,83233,84880,84946,86434,87916,88011,88118,88209,88260,89655,89721,89879,91099,92042|9,0:8083\"/><wd nm=\"scale_factor\" rd=\"7,0:81575,81755\"/><wd nm=\"scale_fac­tor\" rd=\"7,0:82788\"/><wd nm=\"scaleoffset\" rd=\"7,0:6178,83081,83104,83211,86483,86564,86671,89761,89842,89929\"/><wd nm=\"scaleoffset_f\" rd=\"7,0:6197\"/><wd nm=\"scaleoffset_float_dscale\" rd=\"7,0:88260\"/><wd nm=\"scaleoffset_int\" rd=\"7,0:85072\"/><wd nm=\"scaleoffset_test_float_dscale\" rd=\"7,0:88209\"/><wd nm=\"scaleoffset_test_int\" rd=\"7,0:85030\"/><wd nm=\"scaling\" rd=\"7,0:77725,77939,77989,78001,78010,78083,81225,81242,81254,81291,81300,81324,81333,82079,82225,82593,82612,82806,82815,82927,82965,91274,91286,91329,92077\"/><wd nm=\"scan1\"
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_212_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"set_shared_mesg_index_f\" rd=\"5,0:10743\"/><wd nm=\"set_shared_mesg_nindexes\" rd=\"5,0:10484\"/><wd nm=\"set_shared_mesg_nindexes_f\" rd=\"5,0:10512\"/><wd nm=\"set_shared_mesg_phase_change\" rd=\"5,0:10930\"/><wd nm=\"set_shuffle\" rd=\"7,0:6253,30642\"/><wd nm=\"set_shuffle_f\" rd=\"7,0:6268\"/><wd nm=\"set_sieve_buf_size\" rd=\"5,0:23222\"/><wd nm=\"set_sign\" rd=\"8,0:19252,32299,35666\"/><wd nm=\"set_sign_f\" rd=\"8,0:19264\"/><wd nm=\"set_simple\" rd=\"9,0:2570\"/><wd nm=\"set_simple_f\" rd=\"9,0:2587\"/><wd nm=\"set_size\" rd=\"4,0:24660|7,0:73347|8,0:18659,33452,37102,69371,82312\"/><wd nm=\"set_size_f\" rd=\"8,0:18671\"/><wd nm=\"set_sizes\" rd=\"5,0:20940,43602\"/><wd nm=\"set_small_data_block_size\" rd=\"5,0:12845|7,0:9245,33065\"/><wd nm=\"set_small_data_block_size_f\" rd=\"5,0:12874|7,0:9274\"/><wd nm=\"set_strpad\" rd=\"8,0:20163,37430\"/><wd nm=\"set_strpad_f\" rd=\"8,0:20177\"/><wd nm=\"set_sym_k\" rd=\"5,0:21123\"/><wd nm=\"set_szip\" rd=\"7,0:6315\"/><wd nm=\"set_szip_f\" rd=\"7,0:6327\"/><wd nm=\"set_t\" rd=\"8,0:29505,37322\"/><wd nm=\"set_tag\" rd=\"8,0:22566,38021,74007\"/><wd nm=\"set_tag_f\" rd=\"8,0:22577\"/><wd nm=\"set_test_float_dscale\" rd=\"7,0:88209\"/><wd nm=\"set_test_int\" rd=\"7,0:85030\"/><wd nm=\"set_type_conv_cb\" rd=\"7,0:7672|8
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_213_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"sh_f\" rd=\"5,0:7997\"/><wd nm=\"shall\" rd=\"1,0:1620,3463\"/><wd nm=\"shape\" rd=\"3,0:7425|7,0:13629,35044,35255,35959|9,0:172,4135,16006,16133,16156,16256,16303,16350,16440,16514,20662,22732,27105,27189,27279,28608,29158,29442,32071,32153,32202,38591|12,0:129,13792\"/><wd nm=\"shaped\" rd=\"4,0:9279,9384,11527\"/><wd nm=\"shapes\" rd=\"9,0:26723\"/><wd nm=\"share\" rd=\"4,0:22447|8,0:87137,88563,90105\"/><wd nm=\"shareable\" rd=\"8,0:4671,88690\"/><wd nm=\"shared\" rd=\"3,0:11374,14035,18441|5,0:10555,10658,10793,10910,10989,11108|6,0:5771|8,0:3340,4594,25120,87212,87249|10,0:1197,16358,16662,16760,16834,16842\"/><wd nm=\"shared_attribute\" rd=\"10,0:16404,16423\"/><wd nm=\"shared_mesg_index\" rd=\"5,0:10718,10825\"/><wd nm=\"shared_mesg_index_f\" rd=\"5,0:10743\"/><wd nm=\"shared_mesg_nindexes\" rd=\"5,0:10484,10590\"/><wd nm=\"shared_mesg_nindexes_f\" rd=\"5,0:10512\"/><wd nm=\"shared_mesg_phase_change\" rd=\"5,0:10930,11044\"/><wd nm=\"shared_type”\" rd=\"8,0:88751\"/><wd nm=\"shed\" rd=\"4,0:27565|5,0:15961,33592|7,0:12378,47977|8,0:42607,47170|9,0:16826|11,0:3485,3586|12,0:2940,8889\"/><wd nm=\"shes\" rd=\"3,0:2727|5,0:5831,7063,8009|6,0:6552|11,0:2761,3675,5425,16953,17574\"/><wd nm=\"shifted\" rd=\"8,0:28734,28912,36323,36501\"/><wd nm=\"shing\" rd=\"7,0:63940|11,0:16046,17634\"/><wd nm=\"shion\" rd=\"11,0:11303\"/><wd nm=\"shi
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_218_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"st2\" rd=\"8,0:77593,77662,77721\"/><wd nm=\"st_class\" rd=\"12,0:17953,18014\"/><wd nm=\"st_error\" rd=\"11,0:10543,10610,10678,12366,13689,13756,13824\"/><wd nm=\"st_f\" rd=\"5,0:8067,8152|6,0:13071|7,0:3304|8,0:17417|9,0:2841,3673|10,0:4359\"/><wd nm=\"st_float\" rd=\"7,0:71642\"/><wd nm=\"st_float_dscale\" rd=\"7,0:88209\"/><wd nm=\"st_id\" rd=\"5,0:4822,4895,5011,5022,5494,5557,5614,45845,46000|7,0:24398,24643|8,0:54142,54180,55650,55718,55786,76126,76159,76217,76367,76776,76834,76973,78390,78449,92256|11,0:18198|12,0:17254\"/><wd nm=\"st_int\" rd=\"7,0:68194,85030\"/><wd nm=\"st_limits\" rd=\"5,0:7413\"/><wd nm=\"st_limits_f\" rd=\"5,0:7436\"/><wd nm=\"st_link_info\" rd=\"6,0:16765,16866\"/><wd nm=\"st_link_info_f\" rd=\"6,0:16786,16887\"/><wd nm=\"stablished\" rd=\"7,0:12378|12,0:8889\"/><wd nm=\"stack\" rd=\"11,0:181,331,573,986,1048,1676,1718,1799,1851,1945,2009,2161,2315,2383,2525,2611,2653,2790,3072,3139,3254,3424,3436,3514,3603,3701,3861,3979,4038,4110,4136,4188,4265,4299,5291,5336,5394,5477,5603,5630,5681,5697,5745,5951,5964,5984,6000,6046,6062,6120,6135,6247,6628,6758,6774,7104,7213,7572,7652,7776,8017,8163,8749,8856,8908,8970,9047,9052,9105,9389,9423,9546,11815,11956,16087,16159,16201,16317,16343,16355,16418,16470,16487,16539,16563,16589,16637,16658,16674,16709,16729,16801,16827,16986,17056,17129,17189,17257,17278,17291,17311,17350,17388,17401,17421,17477,17532,17612,17664,17784,18014,18090,18131,18254,183
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_219_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"storage_size\" rd=\"7,0:3566,24105|10,0:4896\"/><wd nm=\"storage_size_f\" rd=\"7,0:3586|10,0:4916\"/><wd nm=\"store\" rd=\"3,0:1873,2151,4634|4,0:3743,20265|5,0:20765,33102,33191,33410,33468,33546,33697,33849,33975,34276,34682|6,0:19699|7,0:3735,4485,4643,13917,14770,17229,17389,31296,31325,31356,31386,31417,31447,35500,35554,38695,55797,65417,65681,65758,65863,65927,65995,66060,66172,66275,66340,66443,66753,66862,66917,66985,77111|8,0:27419,37618,49402,63365,63581,66864,67007,67556,68293,68422,70414,73728,74432,95161|9,0:8463,11215,12367,12423,31150,32572,37366|10,0:14492,16515|11,0:7734\"/><wd nm=\"store_k\" rd=\"5,0:10175,21312,21330\"/><wd nm=\"store_k_f\" rd=\"5,0:10195\"/><wd nm=\"stored\" rd=\"3,0:483,513,1417,1514,3217,3242,3339,4275,4431,8172,8429,9749,10263,10707,13449,13574,15135,15184,18085|5,0:26520,26595,28623,35271,38552,41049|6,0:5427,8919,9293,9463,11557|7,0:231,285,600,907,12553,12728,13212,13670,16807,23823,23966,24029,25047,25371,25988,27812,30105,33745,33798,33966,34022,34072,34305,34463,34973,35619,36239,36433,36648,38253,38514,38854,39114,39266,39532,39634,39720,40632,47002,48783,49455,51031,51900,54452,54655,54903,55021,56039,56096,57771,59224,59286,62632,63412,63555,63646,63765,63984,64556,65048,65093,67555,75885,78920,79734,79865|8,0:2097,2727,4203,4528,5198,7507,13128,28540,28873,29043,29115,36118,36462,36632,36704,43336,48180,48449,48981,59624,63182,64150,67490,68004,69912,70092,71810,72620,72726,73640,73822,74466,74759,8578
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_220_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"subtract\" rd=\"7,0:81496,84607\"/><wd nm=\"subtracted\" rd=\"7,0:79322\"/><wd nm=\"subtracts\" rd=\"7,0:79507,82163\"/><wd nm=\"sub­divided\" rd=\"8,0:60763\"/><wd nm=\"sub­sequent\" rd=\"7,0:10908\"/><wd nm=\"succeed\" rd=\"6,0:23927\"/><wd nm=\"successful\" rd=\"7,0:10580,10842\"/><wd nm=\"successfully\" rd=\"5,0:15784|6,0:22288\"/><wd nm=\"successively\" rd=\"10,0:11138\"/><wd nm=\"succinctly\" rd=\"8,0:63453\"/><wd nm=\"such\" rd=\"1,0:1756|3,0:1943,3503,7968,9854,10002,14228,15393,20980|4,0:1299,2988,4190,24240|5,0:2039,2561,3497,16492,24223,32868,37490,40591|6,0:1344,5916,7735,28154,31144|7,0:11089,18423,25145,26489,26748,26918,27956,28021,35848,47880,53728,55701,76242|8,0:890,3911,5582,15736,16279,75454,79836,88383,97129|9,0:10130,12152,21416,21842|10,0:1090,1988,8770,12273,17130,17208|11,0:320,5812,6218,8396,11191,11247|12,0:3045,7826,17877,18873\" sp=\"1\"/><wd nm=\"sue\" rd=\"9,0:11165|12,0:19820\"/><wd nm=\"sues\" rd=\"5,0:638|10,0:1484,1852,12773,12791\"/><wd nm=\"sues”\" rd=\"10,0:1355\"/><wd nm=\"suffered\" rd=\"1,0:1674\"/><wd nm=\"sufficient\" rd=\"5,0:24581|7,0:17211,35467|8,0:45436|11,0:427,4360|12,0:12540\"/><wd nm=\"suffix\" rd=\"5,0:37218,37241\"/><wd nm=\"suffixed\" rd=\"5,0:37726\"/><wd nm=\"suggested\" rd=\"6,0:39\"/><wd nm=\"suggestions\" rd=\"7,0:91569,91600\"/><wd nm=\"suggests\" rd=\"3,0:2552|9,0:17395
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_225_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"taset1\" rd=\"6,0:1149,1228,7887,7952,7983,8167,8247,8306,8371,8394,21012,21452,23492,23858|7,0:11856,11982|10,0:15976,16026,16081,16491,16522,16563,16627\"/><wd nm=\"taset1”\" rd=\"8,0:64328,70901\"/><wd nm=\"taset2\" rd=\"6,0:1379,21056,21591,23545,23968\"/><wd nm=\"taset2”\" rd=\"8,0:70996\"/><wd nm=\"taset3”\" rd=\"8,0:70763\"/><wd nm=\"taset_access\" rd=\"12,0:4475\"/><wd nm=\"taset_create\" rd=\"3,0:12964|4,0:18239,21033|7,0:15746,51625,52436,69804,74098,86062,89280|8,0:76178,76795|12,0:4456,14239,14336,18044\"/><wd nm=\"taset_id\" rd=\"7,0:21023,21276,21477,21561,21884,22003,22361,22443,23191,23343,23540,23624,24362,24524,24596,24630,24672,24756,41306,41452,41617,41676|8,0:13257,14570,14714,51099,51206,52656,52716,57492,57600,57899,58009,58166,58511,58619,59184,59294,76290,77613,77689,92205\"/><wd nm=\"taset_name\" rd=\"4,0:23931,24571|7,0:68217,70378,70892,71667,74673,75193,85060,86974,87424,88248,90149,90605\"/><wd nm=\"taset_region\" rd=\"7,0:1842|9,0:35118,35539,35941,36194,38462,38528\"/><wd nm=\"taset_xfer\" rd=\"3,0:13052|7,0:22117|8,0:52600|12,0:4494\"/><wd nm=\"taset_xfer_f\" rd=\"8,0:54123\"/><wd nm=\"taseta\" rd=\"10,0:15918,16003,16468,16649\"/><wd nm=\"tasetname\" rd=\"4,0:4068,18477|8,0:62503,72397,76935,78279,82898|9,0:39748,40609\"/><wd nm=\"tasets\" rd=\"3,0:2977,14896,19952,20571,20742|4,0:1704,4767,5471,5541,5598,5639,5659,6013,6126,6907,7318,16708,17146,17185,18995,22478,22575|5,0:6373,10279,43820,44818,44884,44980,45041
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_22_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"_times\" rd=\"12,0:22378,22691\"/><wd nm=\"_times_f\" rd=\"12,0:22401,22714\"/><wd nm=\"_to_dtype\" rd=\"8,0:22772,97474,97673,98129,100468,100624,100798,100937\"/><wd nm=\"_to_target\" rd=\"6,0:25525,25607\"/><wd nm=\"_to_text\" rd=\"8,0:22851,97527,97769,98149\"/><wd nm=\"_tr\" rd=\"9,0:13536,13852,42797,44070,44097\"/><wd nm=\"_track_times\" rd=\"12,0:22378,22691\"/><wd nm=\"_track_times_f\" rd=\"12,0:22401,22714\"/><wd nm=\"_tracked\" rd=\"6,0:10617\"/><wd nm=\"_transform\" rd=\"7,0:7513,7590\"/><wd nm=\"_transform_f\" rd=\"7,0:7535,7612\"/><wd nm=\"_trunc\" rd=\"4,0:2550,2714,2902|5,0:989,1276,1801,15330,15416,42575,42619,42718,43178,43284,43661|7,0:69497,73794,85756,88974|9,0:40179,40294|10,0:15280\"/><wd nm=\"_trunc_f\" rd=\"9,0:41865,43454\"/><wd nm=\"_txt\" rd=\"0,0:81,102\"/><wd nm=\"_type\" rd=\"4,0:13600,24584|5,0:14677,14792|7,0:3203,9070,9155,23983,24618|8,0:17621,21621,25523,25536,25627,30846,32232,32283,32311,38427,38478,38506,56223,57713,57791,57997,58068,78313,84582,84812,85951,85991,86625,89027,90083,98355,98369,98386,98399,98423,99480,99639,99687,99827,99857,100299|9,0:2381,2640|10,0:4988,10032,10097,10187,11052|11,0:14637,14809,15040\"/><wd nm=\"_type_conv_cb\" rd=\"7,0:7672,7768|8,0:23367,23463,91308\"/><wd nm=\"_type_con­v_cb\" rd=\"11,0:11215\"/><wd nm=\"_type_def\" rd=\"8,0:99511,99531,100330,100350\"/><wd nm=\"_type_f\" rd=\"7,0:3215|8,0:17640,21
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_232_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"throughout\" rd=\"3,0:14327|7,0:65272|12,0:2749,25610\"/><wd nm=\"ths\" rd=\"3,0:17339,17781,17889|5,0:10030,43472|6,0:4924,5116,5229,20606,20967,21401,23332,30469,31021|8,0:9280,18570,64982|12,0:22888,22962,23036\"/><wd nm=\"thtext\" rd=\"8,0:92383,92412\"/><wd nm=\"thus\" rd=\"3,0:9673|4,0:8154|5,0:19250,22485,32765|6,0:30439,30833|8,0:5320,42422,73199,81325,90828,92975|10,0:1311\"/><wd nm=\"th­ers\" rd=\"12,0:722\"/><wd nm=\"th­erwise\" rd=\"8,0:88256\"/><wd nm=\"th”\" rd=\"8,0:3936\"/><wd nm=\"ti\" rd=\"4,0:13080|5,0:1877,14143,14755,14863,26477,26484,26679,26853,38269,38424,38868,38880,38986,39006,39158,39309,39451,39503,39586,39801,39821,40030|7,0:311,8753,9142,9232,31435,31992,33707,34390,52208|8,0:60577,61587,63049,78615|12,0:23562,26567,26833\"/><wd nm=\"ti_f\" rd=\"5,0:14165\"/><wd nm=\"ti_type\" rd=\"5,0:14677,14792|7,0:9070,9155\"/><wd nm=\"tial\" rd=\"3,0:11254|4,0:3074,6900,16801,16865,25495|5,0:10371,10451,12254,12397|7,0:18736,18777,36803,37444,37546,37757|8,0:31748|9,128:17,45,7394,18051,44496|10,0:1128,3056,6936,17623\"/><wd nm=\"tialization\" rd=\"8,0:32903|9,0:12952,40044\"/><wd nm=\"tialize\" rd=\"4,0:3285,3359|5,0:23748|7,0:16443,20222,21092,68996|8,0:50781,52162,52897,53914,65547|9,0:13332,13670,41639,41748,43224,43337\"/><wd nm=\"tialized\" rd=\"5,0:23511|7,0:11434,13873,17310,44094,71860|8,0:54035,77160|11,0:6933|12,0:8551,14441\"/><wd nm=
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_235_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"to\" rd=\"0,64:229|1,64:1098,1348,2304,3101,3851,3862,4048|2,64:72,168,290|3,64:240,271,291,362,504,1090,1333,1427,1478,1507,1591,1871,1928,1993,2149,2326,2423,2529,3052,3121,3180,3691,3902,3932,3987,4160,4328,4401,4534,4548,5817,6144,6442,6497,6628,6894,6942,7008,7260,8094,8628,8957,9421,9475,9518,9627,9950,10219,10301,10662,10791,11035,11447,11906,11964,12176,12213,12283,12330,12381,12497,13377,13422,13554,13667,14275,14544,14993,15011,15031,15056,15088,15549,15627,15761,16344,16796,16860,17215,17355,17405,17694,17894,17935,18111,18208,18228,18325,18366,18437,18474,18534,18555,18979,19629,19709,19726,20120,20911,21057,21270|4,64:230,315,384,527,584,621,628,732,864,896,1118,1125,1423,2177,2244,2421,2565,2853,2936,3190,4016,4354,5083,5155,5269,5506,5708,5820,6070,6421,6493,6570,6830,6875,7071,7090,7099,7286,7453,8346,8529,8742,8795,8822,8878,9077,9114,9142,9224,9263,9367,9523,9633,9734,9818,9949,10346,10425,10440,10521,10652,10955,11511,11613,11922,11937,12262,12977,13131,13164,13176,13210,13241,13444,14258,14319,14453,14538,14582,14621,15372,15500,15588,15670,15771,15877,15977,16260,16475,16788,16833,16946,16997,17177,17217,17258,17469,17492,17527,17576,17633,17724,18062,18202,18319,18573,19128,19459,19517,20254,20263,20388,20582,20807,20856,21285,21572,21837,22414,22551,22636,22708,22736,22811,23514,23625,23831,24118,24204,24477,24997,25266,25292,25335,25434,25580,25952,26025,26093,26414,26648,26747,26782,26835,26970,27174,27327,27437,27453,27701,27819,27983,28040,28186|5,64:64,77,113,124,810,1733,2156,3284,3555,3820,5420,5854,6007,6173,6267,6429,7077,7182,7592,7717,8020,8994,9235,9637,9723,10041,10140,10244,11951,12323,12672,13265,1
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_237_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"tran_s1\" rd=\"8,0:99311\"/><wd nm=\"trans\" rd=\"7,0:24776\"/><wd nm=\"transfe\" rd=\"4,0:25121\"/><wd nm=\"transfer\" rd=\"3,0:442,1440,12140,12572|4,0:6594,25611,26186,26253,26395,27599,27710,28062|7,0:1132,8158,8255,8588,8653,10334,13017,16267,16396,16582,18509,18521,19162,19241,19294,19428,19531,19788,19826,20049,20187,20294,21438,21645,21690,23501,26234,26399,26426,30495,32109,32151,32252,32328,32623,32827,33003,33420,33513,34146,37373,48986,70694,74990,87226,90405|8,0:1633,1823,5329,12558,13357,13671,51809,52563,53998,77402,90160,90457,95896,95923,96338|9,0:595,10071,15926,15957,17407,17616,18488,18929,20858,21519,22023,22040,22068,22206,26959,27317,27601,30167,30588,31712,32477,40727|12,0:2150,4440,8684,8789,11298,11461,25977\"/><wd nm=\"transferred\" rd=\"3,0:8181|7,0:12637,13344,16302,16533,17253,18720,18766,20153,20959,48187,53168|8,0:1579,13492,60837,62940,90210,93778,95670|9,0:17951,18015,22807,23094,30635,30667\"/><wd nm=\"transferring\" rd=\"4,0:25539|8,0:1171,4771,5008,95194|9,0:26802,36866\"/><wd nm=\"transfers\" rd=\"3,0:1401|4,0:25166|7,0:16980,19192,24813,36842|8,0:12330,13757|9,0:17857,28753,31810\"/><wd nm=\"transform\" rd=\"7,0:7513,7569,7590,7651,18149,18457,19965,77697,81376,81769|8,0:5144\"/><wd nm=\"transform_f\" rd=\"7,0:7535,7612\"/><wd nm=\"transformation\" rd=\"7,0:77847,80974,81161|8,0:91996,93046\"/><wd nm=\"transformations\" rd=\"7,0:20061,24857,26343\"/><wd nm=\"transformed\" rd=\"3,0:2497|4,0:26974
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_239_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ts_by_name\" rd=\"10,0:3975\"/><wd nm=\"ts_by_name_f\" rd=\"10,0:3993\"/><wd nm=\"ts_default\" rd=\"7,0:86613\"/><wd nm=\"ts_f\" rd=\"5,0:7436|9,0:2306,3458,3562,3769|10,0:3902\"/><wd nm=\"ts_fig1\" rd=\"7,0:553,566\"/><wd nm=\"ts_fig10\" rd=\"7,0:28085,28099\"/><wd nm=\"ts_fig12\" rd=\"7,0:34514,34528\"/><wd nm=\"ts_fig13\" rd=\"7,0:35201,35215\"/><wd nm=\"ts_fig14\" rd=\"7,0:36767,36781\"/><wd nm=\"ts_fig15\" rd=\"7,0:39559,39573\"/><wd nm=\"ts_fig16\" rd=\"7,0:40647,40661\"/><wd nm=\"ts_fig19\" rd=\"7,0:51201,51215\"/><wd nm=\"ts_fig2\" rd=\"7,0:10130,10143\"/><wd nm=\"ts_fig20\" rd=\"7,0:52088,52102\"/><wd nm=\"ts_fig5\" rd=\"7,0:17139,17152\"/><wd nm=\"ts_fig9\" rd=\"7,0:25555,25568\"/><wd nm=\"ts_nbitfloating1\" rd=\"7,0:58215,58237\"/><wd nm=\"ts_nbitfloating2\" rd=\"7,0:58727,58749\"/><wd nm=\"ts_nbitinteger1\" rd=\"7,0:56994,57015\"/><wd nm=\"ts_nbitinteger2\" rd=\"7,0:57358,57379\"/><wd nm=\"tself\" rd=\"3,0:17994,18547|6,0:1303,1583,5336,5877,27386,29770|7,0:899,61647,62160|8,0:81094|11,0:115,4342,11837\"/><wd nm=\"tset_cset\" rd=\"8,0:20031,37297\"/><wd nm=\"tset_cset_f\" rd=\"8,0:20043\"/><wd nm=\"tset_ebias\" rd=\"7,0:73420|8,0:19552,36061\"/><wd nm=\"tset_ebias_f\" rd=\"8,0:19565\"/><wd nm=\"tse
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_23_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"a1\" rd=\"8,0:52124,52202,52699\"/><wd nm=\"a2\" rd=\"6,0:21616|8,0:52143,52214,52759\"/><wd nm=\"a_block_size\" rd=\"5,0:12078,12845,12957,22513,22586|7,0:9245,9357,33065\"/><wd nm=\"a_block_size_f\" rd=\"5,0:12105,12874,12986|7,0:9274,9386\"/><wd nm=\"a_dacpl_id\" rd=\"12,0:20294\"/><wd nm=\"a_dims\" rd=\"8,0:55624,55692,55760\"/><wd nm=\"a_extension\" rd=\"5,0:40316,40686,40751\"/><wd nm=\"a_id\" rd=\"12,0:14220,14413,14572,14642,14711,14732,14825,15216,15396,15476,15550,15684,15775,16036,16831,16874,16896,17531,17978,18076,20329\"/><wd nm=\"a_link\" rd=\"6,0:23219,23352,23456,23515,23881\"/><wd nm=\"a_loc_id\" rd=\"6,0:23422,23826,24509\"/><wd nm=\"a_name”\" rd=\"8,0:48708,50929,51502,53099,54625,55222,57322,76568,81794,83162,95447,96553,96784\"/><wd nm=\"a_new\" rd=\"4,0:19533,19653,19744,19812,19860,20173\"/><wd nm=\"a_new1\" rd=\"6,0:19501\"/><wd nm=\"a_new2\" rd=\"6,0:19577\"/><wd nm=\"a_operator2_t\" rd=\"10,0:11095\"/><wd nm=\"a_operator_t\" rd=\"10,0:11600\"/><wd nm=\"a_out\" rd=\"9,0:38913,39010\"/><wd nm=\"a_properties\" rd=\"5,0:40336,41150\"/><wd nm=\"a_seta\" rd=\"5,0:17859,17915\"/><wd nm=\"a_size\" rd=\"8,0:14541,14686\"/><wd nm=\"a_transform\" rd=\"7,0:7513,7590\"/><wd nm=\"a_transform_f\" rd=\"7,0:7535,7612\"/><wd nm=\"aa\" rd=\"5,0:45022|6,0:29049,29067\"/><wd nm=\"ab\" rd=\"3,0:8967|4,0:7382,7514,7909,7920,8073,8166,82
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_246_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"upports\" rd=\"4,0:7272|7,0:55355,55513,76638,81281,82952|8,0:1983,2928,5892,50508|9,0:4188,15053\"/><wd nm=\"uppose\" rd=\"4,0:5414,5939,9620,10372,11642,11905,17456|6,0:24612|7,0:57138,58373|8,0:38653|9,0:23515\"/><wd nm=\"upposed\" rd=\"11,0:12395\"/><wd nm=\"ups\" rd=\"3,0:2970,4743,5318,14365,14887,17088,18461,19943,20007,20241,20315,20398,20562,20733|4,0:1750,4760,18923,18930,19065,20467|5,0:6383,44804,44966,44991,46060|6,128:4,15,466,650,1885,1936,4521,5791,8802,8837,8957,9229,9400,10088,11082,11108,11551,12342,12401,16643,16757,17490,17622,18212,18252,19212,19262,19367,21188,21871,22536,28200,28952,29338,29384,29415,30344,30775,30923,30978,32292|7,0:11121,47805|8,0:69825|10,0:1994,12946,13974|12,0:435,4206,9533,9799,24427,24644,27591,27599\"/><wd nm=\"ups_fig27_a\" rd=\"6,0:28855,28872\"/><wd nm=\"ups_fig27_aa\" rd=\"6,0:29049,29067\"/><wd nm=\"ups_fig27_b\" rd=\"6,0:28892,28909\"/><wd nm=\"ups_fig27_bb\" rd=\"6,0:29088,29106\"/><wd nm=\"ups_fig28_a\" rd=\"6,0:29884,29901\"/><wd nm=\"ups_fig28_b\" rd=\"6,0:29921,29938\"/><wd nm=\"ups_fig28_c\" rd=\"6,0:30072,30089\"/><wd nm=\"ups_fig28_d\" rd=\"6,0:30109,30126\"/><wd nm=\"ups_fig29_a\" rd=\"6,0:31212,31229\"/><wd nm=\"ups_fig29_b\" rd=\"6,0:31249,31266\"/><wd nm=\"ups_fig29_c\" rd=\"6,0:31368,31385\"/><wd nm=\"ups_fig29_d\" rd=\"6,0:31405,31422\"/><wd nm=
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_247_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"us_f\" rd=\"7,0:3128\"/><wd nm=\"us_n\" rd=\"4,0:10106\"/><wd nm=\"usability\" rd=\"12,0:875\"/><wd nm=\"usage\" rd=\"3,0:12772|5,0:18753,20623,34826,39901|7,0:67977,79785,84821|9,0:7568|10,0:115\"/><wd nm=\"usands\" rd=\"5,0:22317|6,0:9427,11124|12,0:839,7735\"/><wd nm=\"use\" rd=\"1,0:421,1057,1707,3045|3,0:3476,12156,17868,18989,19030|4,0:1115,2919,3006,6921,12730,14593,17111,17685,19564,20377,20809,21817,21943,23615,27136,27587|5,0:384,419,452,4206,6164,8937,9634,9720,13538,17398,22810,23433,28307,28881,29758,30463,31278,31509,32089,33254,34217,36190,36643,36790,38248,38416,39497,40444,40927,45689|6,0:4547,5208,7168,9549,11645,13194,13507,13687,16425,16504,17718,18621,20002,20303,20578,24237,26556,26861,27955,28013,31038|7,0:1427,2336,6090,6157,6225,6292,6348,6711,9033,15836,16792,18407,20012,24688,29573,32754,33571,34830,42788,53330,57646,59952,61769,63884,64430,68028,70677,71399,71492,74973,75679,75754,78448,84872,87209,87908,88003,89679,90388,91091,91963,92022,92098|8,0:9506,12452,13055,13401,13766,15667,23119,25329,31898,33628,45874,57117,57707,63557,68796,68915,68976,73476,73525,74626,74943,88614,92111,92554,94487,100463,100793|9,0:556,1084,6818,6967,15138,15383,18331,21288,26243,29020,32553,37311,41128,42698|10,0:5942,8521,8643,8783,8872,8956,9061,10300,12285,14006,14466,14892,17351|11,0:9331|12,0:381,6959,6999,8097,9467,12366,12585,12646,12842,12895,12968,13633,16126,16186,20079,20289,20363,24058,24242,24439,24681,26418,26450,27216|13,0:89,238,1202,1342\" sp=\"1\"/><wd nm=\"used\" rd=\"1,0:1344,3473|3,0:2590,8260,8953,10133,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_249_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"vanced\" rd=\"4,0:4887|5,0:34818|6,0:8852|11,0:493,537,1233,3939,11641|12,0:2257,20853,26309,26513\"/><wd nm=\"vant\" rd=\"3,0:12322,12373,12705|5,0:34296|8,0:26437|12,0:5578,5675,5785,6673,7311,27467\"/><wd nm=\"vantage\" rd=\"6,0:961|10,0:14090|12,0:594,2776\"/><wd nm=\"vantages\" rd=\"8,0:60964,60977,61037,61050,61073,61085|10,0:13898\"/><wd nm=\"variable\" rd=\"4,0:16177,23064|5,0:29146,31772,32347|7,0:3740,8347,8480,19649,24226,37799,48522,48599,48762,48812,49049,49141,49200,55589,76941,76984,82646,82973,88036,89682|8,0:6185,8012,8030,22268,22376,22470,46344,61773,62669,62695,62874,64223,67355,67871,67960,68800,69045,69150,69237,69328,69388,69404,69537,78976,93395,93549,93585,99179,100496,100551,100662\"/><wd nm=\"variable_length_type\" rd=\"8,0:98399,99639\"/><wd nm=\"variable_str\" rd=\"8,0:22401\"/><wd nm=\"variable_str_f\" rd=\"8,0:22420\"/><wd nm=\"variables\" rd=\"7,0:48341|8,0:59487,59716,59776,59850,59913,60033\"/><wd nm=\"varies\" rd=\"8,0:68768|9,0:23164\"/><wd nm=\"variety\" rd=\"5,0:3837,25069|8,0:15840\"/><wd nm=\"various\" rd=\"3,0:15914|5,0:3656,11220,21365,21793,24905|8,0:3668,8920,9063,60992|12,0:1006,3084,3898,4633,11710,16271\"/><wd nm=\"vari­able\" rd=\"5,0:41322\"/><wd nm=\"vari­ables\" rd=\"3,0:2699\"/><wd nm=\"vary\" rd=\"7,0:36616,82750\"/><wd nm=\"var­ious\" rd=\"7,0:38108\"/><wd nm=\"vate\" rd=\"3,0:10212|7,0:62664,62718,64683,67358\"/><wd nm=\"vately\
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_250_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ver_bounds\" rd=\"5,0:12571,12701|6,0:10310,10359|10,0:15192\"/><wd nm=\"ver_bounds_f\" rd=\"5,0:12592\"/><wd nm=\"ver_f\" rd=\"5,0:13212\"/><wd nm=\"ver_info\" rd=\"5,0:13280\"/><wd nm=\"ver_latest\" rd=\"6,0:10407|10,0:15218,15237\"/><wd nm=\"veral\" rd=\"3,0:1593,9133,10154,15143,18454|4,0:496,5691,7626,13375,19036|5,0:23134,30929,32464,35201|6,0:5784,28791|7,0:379,9803,9841,26014,29401,31475,33815,34587,41767,48207|8,0:2936,12147,59435,59659,67152,67443,74400,78639|9,0:14879,39559|10,0:9030,9263|12,0:3021,8727,10123,11790,22019\"/><wd nm=\"verall\" rd=\"3,0:16581|4,0:9770|7,0:26219|8,0:84354|9,0:23709\"/><wd nm=\"verbosity\" rd=\"5,0:30669\"/><wd nm=\"vered\" rd=\"7,0:2259|8,0:84398,84507|9,0:37791\"/><wd nm=\"verge\" rd=\"12,0:14873\"/><wd nm=\"verhead\" rd=\"6,0:9201|7,0:36406\"/><wd nm=\"verifies\" rd=\"5,0:6997|6,0:15678|7,0:5500|9,0:3187\"/><wd nm=\"verify\" rd=\"5,0:6175|6,0:11782|12,0:9845\"/><wd nm=\"vering\" rd=\"6,0:27666,27890,28401|8,0:1047,12344,15163,56755\"/><wd nm=\"verlap\" rd=\"7,0:51569|8,0:28480,36046,41758,79595\"/><wd nm=\"verlapping\" rd=\"4,0:14818|9,0:26988,28873\"/><wd nm=\"vermore\" rd=\"1,0:2241,2497\"/><wd nm=\"vern\" rd=\"6,0:11327\"/><wd nm=\"verned\" rd=\"5,0:22710,39747,41113,41188|6,0:26158\"/><wd nm=\"verning\" rd=\"7,0:9021\"/><wd nm=\"vernment\" rd=\"1,0:
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_251_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"w1\" rd=\"6,0:19469,19501\"/><wd nm=\"w2\" rd=\"6,0:19550,19577\"/><wd nm=\"w_data\" rd=\"7,0:68437,71153,72116,75458,85273,87687,88474,90870\"/><wd nm=\"w_extension\" rd=\"5,0:40363,40712,40783\"/><wd nm=\"w_properties\" rd=\"5,0:40382,41225\"/><wd nm=\"w_type\" rd=\"8,0:32232,32283,32311,38427,38478,38506\"/><wd nm=\"walk\" rd=\"11,0:915,3210,8730,8818,8937,8957,9617\"/><wd nm=\"walk2\" rd=\"11,0:11266\"/><wd nm=\"walk_downward\" rd=\"11,0:9334\"/><wd nm=\"walk_t\" rd=\"11,0:9006,9660\"/><wd nm=\"walk_upward\" rd=\"11,0:9223\"/><wd nm=\"walks\" rd=\"11,0:3241\"/><wd nm=\"wance\" rd=\"6,0:990\"/><wd nm=\"want\" rd=\"4,0:9629,10499,17523|5,0:32570|8,0:55119|9,0:23524,25120|10,0:10794|12,0:13525\"/><wd nm=\"wants\" rd=\"8,0:92681|9,0:8456,16791|11,0:6371\"/><wd nm=\"wap\" rd=\"7,0:18269,28667|8,0:5307\"/><wd nm=\"wapped\" rd=\"4,0:27001\"/><wd nm=\"wapping\" rd=\"7,0:26758,28748\"/><wd nm=\"ward\" rd=\"5,0:6111|7,0:76803,78023|10,0:16148|11,0:824,9223,9334|12,0:18553\"/><wd nm=\"ware\" rd=\"1,0:140,198,292,1066,1389,1510,1716,1866|3,0:1834,1935,2348,19066|6,0:7241|7,0:83809\"/><wd nm=\"warning\" rd=\"6,0:26384\"/><wd nm=\"warranty\" rd=\"1,0:1569,2868\"/><wd nm=\"was\" rd=\"1,0:967,1117,2441,2703|4,0:5218,5258,5318,8872|5,0:6552,6586,25722,27878,28141,31159|6,0:22112,22285,22850,25878,27227|7,0:59616,59685,64
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_252_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"wise\" rd=\"1,0:3187|5,0:36480|6,0:26825|7,0:59775|8,0:88256,91350|10,0:17053\"/><wd nm=\"wish\" rd=\"4,0:2849,10436,10951,11918,17465|5,0:17414,18960|8,0:73722|10,0:10840\"/><wd nm=\"wishes\" rd=\"11,0:5425\"/><wd nm=\"wit\" rd=\"4,0:18919\"/><wd nm=\"witch\" rd=\"5,0:37503|6,0:10049,11336|8,0:15194,15315,15428,74352|12,0:451\"/><wd nm=\"witching\" rd=\"6,0:9070\"/><wd nm=\"with\" rd=\"1,0:447,830,1563,2032,2192,3536|3,0:3993,4796,5019,8621,8814,10090,10713,11045,15863,15890,16013,16050,16808,17062,17195,17251,17288,17451,17613,17777,19939,19998,20237,20394,20558,20729|4,0:1393,1621,6100,6303,6484,7524,7929,8116,8514,12179,13273,14377,14638,16818,17534,17794,17949,18684,19061,19088,20463,20571,20827,21320,22359,22518,22571,22800,24415,24747,26133,26261,27773,27926,27940,27993|5,0:83,185,243,820,912,946,1245,1329,1430,1490,1590,5440,5726,14495,14998,15034,15302,15523,15976,16031,16160,16915,17163,19046,19329,20146,20246,20453,23073,24715,25355,25647,25957,26026,26061,26259,26496,28151,29172,29896,30662,31798,32373,32716,33606,33787,34289,36084,36840,37173,37734,38207,38763,39579,40527,41349,42773,43091,43378,43446,43509,43737,44200,44279,45537|6,0:279,1403,1488,1560,1881,1932,3137,3675,4114,4203,4299,4495,4634,4728,4766,5112,6281,8538,9030,9220,9391,9493,10383,10915,11088,11114,11688,12338,12397,13510,13690,18248,18730,18901,19009,19293,19318,19914,20944,21184,21378,21844,22563,22727,23121,25218,25331,25387,25717,25802,26440,26489,26521,27541,28074,29329,30638,31471|7,0:1341,1388,1610,1810,2106,2387,2488,2549,3488,4228,9837,10228,11445,12284,12326,14437,15177,15423,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_253_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ww\" rd=\"5,0:45083\"/><wd nm=\"wwithtext\" rd=\"8,0:92383,92412\"/><wd nm=\"w­ing\" rd=\"4,0:2074|7,0:54410,83313\"/><wd nm=\"x\" rd=\"3,0:4264,6444,11601,13974,17217,17414,17716,18381|4,0:1147,1404,1662,3631,7507,9641,10416,10418,10465,10816,10818,11958,12376,14271,14518,14973,14982,16270,16359,16914,16953,17004,17540,18806,24342,24357,24505,24548,24754,24898|5,0:1940,4478,10718,10818,10825,10923,14008,14072,18733,20614,24721,24966,25236,25268,25388,25760,27047,27054,28158,28513,28537,28589,28887,28940,29179,29289,30529,31197,31302,31423,31805,31946,35901,37036,37218,37241,37394,37929,38175,39296,39443,41078|6,0:368,1690,4659,4999,5050,5711,6004,8461,13223,13333,13502,14790,14907,14920,14944,15043,15064,30003,30207,30492,30561,30894,31045,31158,31166,31174|7,0:2296,14380,20600,22874,27968,31537,31594,35433,35459,35563,35576,36115,36153,37925,39201,39829,41520,41561,41654,42396,50517,50674,55363,61068,61131,63086,63157,65324,68245,68271,68425,68446,69118,69241,69675,69743,71697,71719,71991,72125,73540,73970,74038,77322,85095,85121,85261,85282,85406,85502,85933,86001,88292,88318,88460,88483,88615,88719,89151,89219|8,0:3243,20958,21013,21428,21483,28781,28860,28959,29028,30647,30683,30886,36370,36449,36548,36617,42427,44131,44325,44702,44915,46461,46482,46723,47071,47495,47592,47614,47658,47680,61455,63736,66200,78608,83885,93747,93809,93843,97194,97752,100826,100873|9,0:2981,4386,4660,6631,12299,12312,12374,12493,12599,12676,12859,12904,12980,13072,13211,1
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_254_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"xpl_mpio_chunk_opt_ratio\" rd=\"7,0:8864|12,0:11927\"/><wd nm=\"xpl_mpio_collective_opt\" rd=\"7,0:8957\"/><wd nm=\"xpl_mpio_f\" rd=\"7,0:8560,8619\"/><wd nm=\"xplained\" rd=\"3,0:12691\"/><wd nm=\"xplains\" rd=\"3,0:620|7,0:9505|9,0:524|11,0:4982\"/><wd nm=\"xplanation\" rd=\"7,0:39025,65298|8,0:43319\"/><wd nm=\"xplanations\" rd=\"9,0:1065\"/><wd nm=\"xplicit\" rd=\"11,0:5437\"/><wd nm=\"xplicitly\" rd=\"4,0:2199|5,0:160,278,17979|6,0:4317,19883|11,0:6392,7879,7939|12,0:19434\"/><wd nm=\"xplore\" rd=\"6,0:28686\"/><wd nm=\"xponent\" rd=\"7,0:58284,58463,58479,58796,59010,59026,59067,59138,59196,59265,59327,59406,59463,59489,59540,72364,72383,72405,72478,72893,72940,73472|8,0:4022,4037,6876,6913,6926,19517,19588,28276,28530,28595,28802,28980,29254,34464,36108,36173,36391,36569,36855,41070,41640\"/><wd nm=\"xports\" rd=\"3,0:1291\"/><wd nm=\"xpo­nent\" rd=\"3,0:9574|8,0:6893\"/><wd nm=\"xpress\" rd=\"1,0:2877\"/><wd nm=\"xpressed\" rd=\"1,0:1593,3355|4,0:8482|9,0:5369,5494|12,0:17180,26746\"/><wd nm=\"xpression\" rd=\"7,0:7578,7660\"/><wd nm=\"xt\" rd=\"0,0:81,102|3,0:7526|4,0:964,10336,18024,18309,20596|6,0:924|7,0:27067,53194|8,0:22728,22834,22851,22902,49947,67213,68319,68371,92383,92412,96969,97074,97134,97236,97527,97573,97769,97901,98113,98149,100585,100898|9,0:23187|10,0:7784,11437,14452|11,0:3818|12,0:1203\"/><wd nm=\"xt_to_dtype\" rd=
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_257_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"z_set_parms_nooptype\" rd=\"7,0:64864,66147\"/><wd nm=\"z_so_float_dscale\" rd=\"7,0:89879\"/><wd nm=\"z_so_int\" rd=\"7,0:86601\"/><wd nm=\"z_so_int_minimumbits_default\" rd=\"7,0:86613\"/><wd nm=\"z_­filter_nbit\" rd=\"7,0:67377\"/><wd nm=\"zation\" rd=\"3,0:782,3844|5,0:3584,24310|7,0:25438,26888|8,0:6028,6997,19667,19750,28670,32903,36259|9,0:12952,40044|12,0:11137\"/><wd nm=\"zations\" rd=\"12,0:11183\"/><wd nm=\"ze\" rd=\"3,0:2328,7460,8705,8720,12861,14546,15090,15763,18327|4,0:3285,3359,3560,3607,5058,7554,8405,8727,8810,9130,9841,10915,11488,13541,13811,13816,13846,13856,14688,15565,16851,17219,17260,18584,18831,18848,18890,20372,24660|5,0:2048,2095,2639,2743,7475,8305,8350,8774,8839,9942,10014,10120,10225,11538,11604,12078,12155,12193,12479,12548,12845,12913,12957,13051,18592,19744,19790,19838,20086,20158,20224,20490,20540,20993,21063,21179,21252,22194,22513,22549,22586,22657,22723,22865,22982,23222,23257,23288,23335,23748,29589,29606,29681,29699,29996,30026,30030,30054,30406,33084,33171,33396,34262,34486,35614,35696,35769,35782,36354,36382,36414,36499,36520,36572,36624,36901,36944,37207,37229,37601,37647,37697,37710,38011|6,0:5657,16971,17958,18024,19776,25934,26046|7,0:3566,3655,4622,4712,7864,7971,9245,9313,9357,9451,9945,9970,12057,12154,12192,12268,12439,14588,14634,16443,17493,17648,20222,21092,21739,22316,23829,24105,24174,30345,32401,33065,33111,34036,34634,34875,34987,35248,35402,35967,36038,36057,36070,36123,36716,37771,37785,37890,37926,38362,38613,38768,39179,39202,39757,39790,39830,39889,3992
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_29_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ame­ters\" rd=\"3,0:6180|7,0:7227,63926\"/><wd nm=\"ame”\" rd=\"8,0:48708,48767,48827,50929,50989,51051,51502,51526,51550,52403,52510,53099,53123,53147,54625,54734,54852,55222,55356,55486,57322,57382,57444,58465,59072,59136,76568,76628,76689,81794,81854,81915,83162,83184,83208,95447,95507,95568,96553,96613,96674,96784,96844\"/><wd nm=\"amically\" rd=\"7,0:63244|8,0:65047|13,0:677\"/><wd nm=\"amiliar\" rd=\"8,0:79788\"/><wd nm=\"amilies\" rd=\"5,0:13707,37403\"/><wd nm=\"amily\" rd=\"3,0:1656|5,0:11961,13648,26238,26246,26457,34980,35107,35373,35392,35405,35428,35450,35487,35550,35574,35655,35747,36091,36117,36147,36196,36348,36401,36545,36612,36702,36740,36796,36959,37110,37325,37357,37670,37882,38017,38087|7,0:31343|12,0:10228,10242,27313,27331\"/><wd nm=\"amily_f\" rd=\"5,0:13671\"/><wd nm=\"amily_offset\" rd=\"5,0:11870,11976\"/><wd nm=\"amily_offset_f\" rd=\"5,0:11891\"/><wd nm=\"amine\" rd=\"5,0:28341|6,0:11699,27919,27992,28037|7,0:56381\"/><wd nm=\"amined\" rd=\"8,0:97855\"/><wd nm=\"amines\" rd=\"6,0:28117\"/><wd nm=\"aming\" rd=\"4,0:1356,1648|6,0:26364\"/><wd nm=\"amm\" rd=\"8,0:23561\"/><wd nm=\"ammar\" rd=\"3,0:19097,19136|5,0:6279,6662|6,0:7275,7313,12244\"/><wd nm=\"ammer\" rd=\"12,0:4951\"/><wd nm=\"ammers\" rd=\"8,0:67583\"/><wd nm=\"ammin\" rd=\"4,0:1895|7,0:9466|9,0:6698\"/><wd nm=\"amming\" rd=\"3,0:342,844,998,1126,1265,1737|4,128:17,51,362,1943,22492,27545,28329|5,0:
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_2_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"*\" rd=\"3,0:19218,19322|4,0:2502,2524,2528,2530,2564,2609,2644,2673,2691,3505,3524,3529,3531,3578,3619,3695,3697,3736,3769,3852,3854,3901,3948,3960,4005,4042,6555,6557,6603,6615,9971,9973,10003,10039,10059,10170,10172,10201,11059,11061,11084,11174,11176,11199,12326,12374,12422,12442,12614,12616,12651,12704,12706,12723,12774,12813,12941,12943,12995,13001,13469,13471,13508,13550,13587,13622,13641,13896,13916,13921,13968,13975,16400,16409,16422,16436,16466,16491,17820,17852,17928,17930,17973,18168,18170,18219,18386,18388,18431,18451,18771,18773,18809,19294,19296,19319,19639,19641,19688,19712,19798,19800,19835,20695,20697,20749,20798,20846,20896,20917,21401,21403,21417,21458,21460,21507,21555,21595,22018,22020,22065,22179,22181,22208,22249,22251,22294,23167,23193,23199,23201,23224,23346,23348,23370,23419,23421,23446,23471,23473,23489,23822,23824,23875,23899,24468,24470,24523,24540|5,0:15185,16100,19837,29662,29680,29698,30373,33170,33190,35695,35711,39205,39226,39247,39253,39277,39356,39377,39398,39399,39423,39442,40315,40362,41892,41907,43142,43153,43158,43206,43251,43327,43340,44042,44074,44134,44167|6,0:7399,7503,22585,23912,23953,23965,24017,24059,24075|7,0:14558,14560,14606,14646,14717,14719,14754,14803,14886,14888,14932,14972,15486,15499,15665,15667,15718,15726,15820,15854,21035,21047,21091,21112,21166,21177,21196,21251,21273,21326,21458,22052,22054,22093,22169,22174,22194,22341,23243,23262,23318,23340,23392,23522,24425,24444,24499,24521,24687,24736,41352,41371,41427,41449,41501,41547,41551,41563,41640,41656,49879,50541,50552,50567,68490,68539,68547,68598,68623,68813,68834,68872,68898,68995,69044,69094,69105,69204,69230,69360,69362,69411,69462,69591,69593,69641,69686,69726,69983,69985,70039,70089,70109,70202,70204,7024
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_31_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"andard\" rd=\"3,0:9955,13499|4,0:1505|5,0:3336,3372,24066,24101,25895,26915,26980,37543,41569|7,0:13059,25177,25707,29159,29234,58116|8,0:749,3030,8334,8892,8981,16356,65131,66257,68868,74146,74276|9,0:6091|10,0:262,817|11,0:4059,4527,7022,8337|12,0:10179\"/><wd nm=\"andards\" rd=\"3,0:9640\"/><wd nm=\"andatory\" rd=\"10,0:12558\"/><wd nm=\"anded\" rd=\"5,0:18709|7,0:11651,72799|8,0:83966,99943\"/><wd nm=\"anding\" rd=\"5,0:498,24427|8,0:41769|12,0:1369,2324\"/><wd nm=\"andle\" rd=\"5,0:9180,9244|7,0:76288,78667,81030|10,0:1383,1425|11,0:578,1488,1995,16233,16439,16723,17372,17461,18419\"/><wd nm=\"andled\" rd=\"4,0:26161|7,0:53654|8,0:97412|10,0:2023,16880|12,0:11083\"/><wd nm=\"andler\" rd=\"8,0:91285|11,0:7507,7754,8460,8535,8664,8697\"/><wd nm=\"andles\" rd=\"8,0:60075|9,0:12794,14527|10,0:13549|11,0:13244\"/><wd nm=\"andlin\" rd=\"11,0:1386,1433,3372,11654\"/><wd nm=\"andling\" rd=\"7,0:81065,84351,91189|10,0:16099|11,128:9,27,272,506,789,1188,1246,1348,1553,3952,7629,7983,11702,11743,18850\"/><wd nm=\"andom\" rd=\"3,0:13461,15599,20899|7,0:44118,44366,69020\"/><wd nm=\"andoned\" rd=\"5,0:17028,26209\"/><wd nm=\"andprops\" rd=\"5,0:3103,3122\"/><wd nm=\"ands\" rd=\"5,0:22317|6,0:9427,11124|7,0:40108|8,0:80889|12,0:839,7735\"/><wd nm=\"ane\" rd=\"4,0:10561,10737|8,0:60905,61136,61154,61419,61559|9,0:21849\"/><wd nm=\"aned\" rd=\"4,0:
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_34_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"arizes\" rd=\"7,0:38272,44499,46065|8,0:33116,91402\"/><wd nm=\"ari­able\" rd=\"5,0:41322\"/><wd nm=\"ari­ables\" rd=\"3,0:2699\"/><wd nm=\"ark\" rd=\"1,0:1952,3162|10,0:17233\"/><wd nm=\"arks\" rd=\"8,0:59634\"/><wd nm=\"arlier\" rd=\"8,0:100163|10,0:14056|12,0:20190\"/><wd nm=\"arly\" rd=\"4,0:1157|6,0:9240,30495|7,0:28694,41720,42306,42559,42803,43342,43537,43566,43582,43589,44709,45261,53521|8,0:14014,81217,97165,97731|9,0:27130|12,0:781,2883,7977\"/><wd nm=\"arms\" rd=\"4,0:18131,18222,18280,18424,18527\"/><wd nm=\"arms_array\" rd=\"7,0:64843,65561,66318,66597,67135\"/><wd nm=\"arms_atomic\" rd=\"7,0:64821,65516,65735,66552,67090\"/><wd nm=\"arms_compound\" rd=\"7,0:64888,65607,66643,66728,67181\"/><wd nm=\"arms_noopdatatype\" rd=\"7,0:65653,66688,67226\"/><wd nm=\"arms_nooptype\" rd=\"7,0:64864,66147\"/><wd nm=\"arning\" rd=\"6,0:26384\"/><wd nm=\"around\" rd=\"5,0:45512|7,0:37820|11,0:8798|12,0:2638\"/><wd nm=\"arr_compound_1\" rd=\"8,0:101023\"/><wd nm=\"arr_compound_2\" rd=\"8,0:101055\"/><wd nm=\"arrange\" rd=\"9,0:32219\"/><wd nm=\"arranged\" rd=\"8,0:94\"/><wd nm=\"arrangement\" rd=\"4,0:25792|7,0:28865\"/><wd nm=\"arranging\" rd=\"8,0:13541|9,0:17597\"/><wd nm=\"arranty\" rd=\"1,0:1569,2868\"/><wd nm=\"array\" rd=\"3,0:4777,4884,7386,7435,7606,8152,8402,8577,8598,9269,9309,10832,11414,13437|4,0:3569,8097,8509,8867,10420,10595,10820,10903,11708,11859
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_35_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"as_f\" rd=\"8,0:19489,19565\"/><wd nm=\"ascii\" rd=\"3,0:18891,19388|5,0:6238|6,0:7060,7580,9579,10940,17726|7,0:6719,11726|8,0:1928,7250,23127,29578,29584,37378,37384,38094,83372,99263,100703|10,0:5950,6715,16984,17356|12,0:390\"/><wd nm=\"ase\" rd=\"0,0:55|2,0:99,146|3,0:6759,17980|4,0:8247,14456,15857,16840,20406|5,0:4195,4485,7354,11021,11133,14475,17382,19133,26661,26844,38718,39631,39684,40021,40579,42812|6,0:189,239,1275,5322,5927,8745,9034,10262,11838,21743,21865,22390,25861,29723,30597,30676,30990|7,0:9485,9704,12246,20879,34383,37194,40298,40462,41266,44089,48148,50220,53608,55480,55738,57844,61178,61818,61934,62012,63067,63799,63818,66497,78066,81270|8,0:1768,3487,7943,8092,8368,8409,8556,9207,9956,15222,15330,15369,15441,15483,17579,23687,25604,30137,30179,31225,38337,41691,43613,47344,47390,58793,61914,63996,64498,65347,73510,75368,75475,85181,87067,89446,90391,93461,93691,94497,96123,100139,100150|9,0:10135,18728,23402,40835,42232,43821|10,0:545,6289,6492,12419|11,0:759,12661|12,0:5169,5180,5529,7498,20057,22355,22668\"/><wd nm=\"ase_change\" rd=\"5,0:10930,11044|6,0:11380,16538,16651|10,0:6211,6419,13273,14579,15355|12,0:22277,22595\"/><wd nm=\"ase_change_f\" rd=\"6,0:16563,16676|10,0:6236,6444|12,0:22302,22620\"/><wd nm=\"ase_type\" rd=\"8,0:99827,99857\"/><wd nm=\"ased\" rd=\"4,0:4296,5361,27224|5,0:15103,16007,16639,26617,29040,29816,30579,31666,32241,33312,36248,39554,40501|6,0:20247,22321|7,0:47926,50669,72839,83265|8,0:10823,12094,34334,34558,34735,35185,40045,89417,95965\"/><wd
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_37_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ata1\" rd=\"8,0:52124,52202,52699\"/><wd nm=\"ata2\" rd=\"6,0:21616|8,0:52143,52214,52759\"/><wd nm=\"ata_block_size\" rd=\"5,0:12845,12957|7,0:9245,9357,33065\"/><wd nm=\"ata_block_size_f\" rd=\"5,0:12874,12986|7,0:9274,9386\"/><wd nm=\"ata_dims\" rd=\"8,0:55624,55692,55760\"/><wd nm=\"ata_link\" rd=\"6,0:23219,23352,23456,23515,23881\"/><wd nm=\"ata_loc_id\" rd=\"6,0:23422,23826,24509\"/><wd nm=\"ata_new\" rd=\"4,0:19533,19653,19744,19812,19860,20173\"/><wd nm=\"ata_new1\" rd=\"6,0:19501\"/><wd nm=\"ata_new2\" rd=\"6,0:19577\"/><wd nm=\"ata_out\" rd=\"9,0:38913,39010\"/><wd nm=\"ata_seta\" rd=\"5,0:17859,17915\"/><wd nm=\"ata_size\" rd=\"8,0:14541,14686\"/><wd nm=\"ata_transform\" rd=\"7,0:7513,7590\"/><wd nm=\"ata_transform_f\" rd=\"7,0:7535,7612\"/><wd nm=\"atabase\" rd=\"4,0:14456\"/><wd nm=\"atabases\" rd=\"4,0:14381\"/><wd nm=\"atalink_loc_id\" rd=\"6,0:23439\"/><wd nm=\"atas\" rd=\"4,0:6414\"/><wd nm=\"atase\" rd=\"7,0:9485\"/><wd nm=\"ataset\" rd=\"3,0:3330,4752,5030,7127,7333,7347,7783,7837,7847,7885,7904,8035,8055,8370,8453,8991,9024,10038,10224,10583,10794,11038,11450,12083,12549,12565,12997,15158,17458,17647,20028,20090,20186,20408,20483,20647,20826|4,0:3063,3097,3183,3229,3311,3341,3372,3463,3477,3611,3728,3865,3932,4045,4218,4443,4546,5311,5337,5386,6451,6545,6575,6634,6866,7044,7083,7113,7198,7257,7299,7433,7660
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_38_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ataspaces\" rd=\"3,0:8646,9153|4,0:1844,6765,6935|7,0:37431,47908,48275|8,0:534,59687|9,128:4,32,4013,4218,4237,4255,4271,6394,6763,7875,10712,13897,15080,15909,16654,18476,18508,22281,24231,24967,27656,30210,31748,44483|12,0:16365\"/><wd nm=\"atat\" rd=\"8,0:11815\"/><wd nm=\"ataty\" rd=\"8,0:16403,85410\"/><wd nm=\"atatyp\" rd=\"8,0:23580,31676\"/><wd nm=\"atatype\" rd=\"3,0:4891,5045,7154,7728,7762,9167,9183,9348,9436,9681,9725,10066,10114,10192,10244,10285,10345,10374,10414,10484,10598,10856,11479,11823|4,0:3107,3327,3485,3705,3772,3826,3914,3994,4080,4197,4421,4526,13255,13475,13518,13591,13623,13663,13747,13828,14086,14190,14292,14605,14630,14724,14891,14924,15169,15179,15195,15291,15334,15539,15601,15714,15741,15927,16243,16348,19094,23548,23715,24254,24407|6,0:2644,2672|7,0:3810,7731,7827,8362,8495,10403,11545,12490,12510,12571,13428,13646,14173,14249,14536,14726,14807,14861,14945,15004,15113,15454,15585,15639,15798,15886,15989,16483,16709,17469,17558,17624,17698,17728,17749,17959,18066,18300,18380,20497,20814,22697,22774,23014,24007,24887,27455,27484,27504,27575,27711,27837,28454,28484,28496,28607,28640,37162,37303,37874,38368,48471,53984,54000,54011,54061,54139,54215,54237,54268,54357,54438,54495,54550,54583,54640,54845,54893,55206,55286,55394,55430,55447,55467,55955,56014,56071,56130,56229,56258,56266,56517,56558,57120,57155,57230,57250,57484,57626,57663,57872,57957,57993,58355,58390,58599,58619,58867,58938,59085,59758,60007,60151,60191,60232,60271,60384,60890,61196,61274,61381,61400,61437,61504,61522,61584,61605,61665,61684,61822,61873,61938,61956,62016,62037,62099,62118,62820,62971,63003,63042,63101,63
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_40_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ation_order\" rd=\"6,0:10684,17136,17247|10,0:6091,6312|12,0:22157,22489\"/><wd nm=\"ation_order_f\" rd=\"6,0:17163,17274|10,0:6118,6339|12,0:22184,22516\"/><wd nm=\"ational\" rd=\"1,0:1150,1783,2066,2250,2506|7,0:53956|12,0:530\"/><wd nm=\"ations\" rd=\"0,128:17,372|1,128:17,1003,1181,1814,4191|2,128:17,433|3,0:594,671,1680,4034,10492,11061,14983,15680|4,0:740,910,9324,22668,25198,26074,26146,26487,27670|5,0:3487,3870,20035,22575,24213,24871,25102,25810,30167,31351,32471,34781,34918,35354,38386,38468,38615|6,0:2856,2937,3157,18325,22158|7,0:1417,9818,9890,10082,10182,10919,11079,11193,11255,11386,16275,16381,20061,24857,24938,26135,26242,26343,26721,26856,26908,31175,33053,34154,34594,36287,53495,55370,59782,63165,76246,77069,91156,91221|8,0:116,2016,2847,2978,5337,9476,13464,16596,19433,22182,24083,31139,42944,55895,73154,73292,74493,79043,93993,97386,97818,97992|9,0:437,627,1065,6359,6533,6675,6955,12709,15947,17497,18244,18304,25643,31622,31733,31900,31941,31983,32460|10,0:13603,14035,16133,16210|11,0:280,514,1196,1254,1285,3380,3960,6409,8169,11662,11710,11751,11881|12,0:850,1428,1826,2242,3703,4867,5139,6288,11183,12750,17621,17648,17729,20842,26173|13,0:799,968,1176,1244\"/><wd nm=\"ationships\" rd=\"3,0:561\"/><wd nm=\"ation­ship\" rd=\"6,0:6698\"/><wd nm=\"ation’s\" rd=\"5,0:3449,24175|7,0:27417|11,0:12091,12852,12918|12,0:12075\"/><wd nm=\"ation”\" rd=\"7,0:43692\"/><wd nm=\"atios\" rd=\"7,0:8083,8141,8180,8238,32568,32606,32651\"/><wd nm=\"atios_f\" rd=\"7,0:8103,8200\"/><wd 
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_41_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"atype1”\" rd=\"8,0:71183\"/><wd nm=\"atype_access\" rd=\"12,0:4609\"/><wd nm=\"atype_create\" rd=\"12,0:4589\"/><wd nm=\"atypes\" rd=\"3,0:9794,9809,9885,9931,9993,10464|4,0:1861,14067,14228,14409,14478,15443,15461,15491|7,0:17930,19974,29881,37241,47895,48265,48614,55337,55524,55536,55705,55721,58553,59892,60285,60337,60619,61318,61741,64809,76000,76051,76670|8,128:4,18,225,524,972,1836,2961,3006,3048,3075,3213,3260,3306,3326,3438,3451,4372,5529,5868,5909,5962,5991,6088,6115,6253,8250,8311,8705,8836,8989,9327,10147,10655,11025,11895,11984,12036,12276,12403,12768,12801,13406,15632,15683,15757,15855,16460,16524,18259,19879,20270,21858,22283,22517,23638,23651,23735,23945,23997,24325,25106,25559,25916,26342,26406,26609,27377,27974,29470,29906,30018,30295,30355,31736,32345,32866,33040,33099,33411,35625,37061,37980,41906,41928,41985,42008,42133,42151,42300,42448,42594,42999,43732,43771,43789,46778,49125,49457,50228,50266,50318,50390,51723,52280,53398,55824,55861,62684,62889,62954,63564,65118,67142,69276,69853,69957,71701,73218,73338,78629,78694,78798,78870,78889,79017,79057,79133,79261,79382,79868,79924,80540,80556,83455,85454,86336,86481,86514,87349,87398,87848,88119,90070,93113,93155,93193,93280,93339,93367,93465,93600,94745,94947,95956,97201,97759,98041,98082,98259,98316,100249,101337|10,0:2011,12965,13993|12,0:4654,4760|13,0:382\"/><wd nm=\"atype’s\" rd=\"7,0:63057,63428,63571\"/><wd nm=\"atype”\" rd=\"11,0:5238\"/><wd nm=\"at­egies\" rd=\"7,0:33854\"/><wd nm=\"at­forms\" rd=\"8,0:45723\"/><wd nm=\"at­ing\" rd=\"7,0:53552|8,0:1142,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_45_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"blocklist_f\" rd=\"9,0:2841\"/><wd nm=\"blocks\" rd=\"3,0:3268,3289,3369,14794,14935,15217|4,0:8297,8433,8454,9218,11968,12033,12184,12202,12378,25253,25440,26693|5,0:20185|7,0:28970,29105,30349,30965,31652,32551,33103,33291,34879,36258,38685|9,0:2724,2803,2896,17168,17314,17427,20205,21224,25079,25139,25896,39272,39312,39375\"/><wd nm=\"blocks_f\" rd=\"9,0:2752\"/><wd nm=\"block­ing\" rd=\"5,0:22283\"/><wd nm=\"blue\" rd=\"8,0:72542,72688\"/><wd nm=\"bluegreen_txt\" rd=\"0,0:81,102\"/><wd nm=\"blue”\" rd=\"8,0:72253\"/><wd nm=\"bly\" rd=\"3,0:6991|4,0:325,19153|5,0:23211,38781|6,0:2561,24930|7,0:32026|8,0:2145,13380,13533,15707,63016,64950|12,0:1350\"/><wd nm=\"bnf\" rd=\"3,0:19094,19133|5,0:6698|6,0:7272,7310,12280\"/><wd nm=\"bnl\" rd=\"1,0:2085\"/><wd nm=\"bo\" rd=\"6,0:27688\"/><wd nm=\"board\" rd=\"1,0:343\"/><wd nm=\"bol\" rd=\"5,0:10150,20968,20999|8,0:20498,31345,73176,73280,93913,99997,100022|12,0:6146\"/><wd nm=\"bolic\" rd=\"6,0:14225,22939,22981,24863,24877,24976,25021,25084,25123,25176,25247,25364|8,0:7619,8342,71959,72658\"/><wd nm=\"bool\" rd=\"8,0:11542\"/><wd nm=\"bool_t\" rd=\"5,0:33095,33183,39289,39435|8,0:11560\"/><wd nm=\"boolean\" rd=\"5,0:33423\"/><wd nm=\"boost\" rd=\"5,0:23195\"/><wd nm=\"boratory\" rd=\"1,0:2074,2258|10,0:556\"/><wd nm=\"bosity\" rd=\"5,0:30669\"/><wd nm=\"both\" rd=\"4,0:5333,6823|5,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_4_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"0\" rd=\"3,0:10945,10969,10984,13789,14098|4,0:3628,10211,10236,10543,10545,11093,11213,11233,11250,11263,11455,11457,11682,12437,12452,12455,12476,12500,12523,12823,12836,12848,12861,16951,17002,17773,18704,18804,18817,18825,18836,18844,20926,20929,20943,20953,20956,20969,22350,23134|5,0:18200,18925,19570,21533,23605,23782,30752,32140,33717,33995,36144,39968|6,0:8754,9043,10271,29857|7,0:14656,15523,21121,21138,28085,28099,36151,36154,36701,40610,41574,42504,51681,51686,51728,51730,51772,51777,52088,52102,52489,52528,52567,54723,56906,58413,58497,65698,68098,68247,68260,68276,68666,68762,68940,69114,69132,69238,69302,69538,69673,69740,69825,69933,70147,70456,70792,70919,71163,71356,72007,72054,72059,72064,72068,72099,72100,72300,72400,72527,73085,73096,73189,73248,73292,73371,73446,73537,73601,73835,74035,74119,74228,74441,74752,75093,75220,75468,75636,77280,81552,81741,82110,82202,82281,82302,82307,82387,82391,82445,82523,82587,85097,85110,85126,85402,85420,85455,85499,85563,85797,85931,85998,86083,86191,86278,86351,86645,87052,87324,87451,87697,87865,88294,88307,88323,88611,88629,88665,88672,88676,88716,88780,89015,89149,89216,89301,89409,89496,89501,89572,89903,90227,90505,90632,90880,91048,92065|8,0:5823,22947,26420,27928,39313,39357,39384,41697,44893,45227,45682,46160,46202,46230,46245,50804,51595,51600,51603,51624,51643,52185,53192,53197,53200,53215,53221,53234,53240,53510,54598,55197,55330,55461,59563,61708,64609,65506,65579,65583,65660,65706,65896,65956,67819,68104,69300,69664,70884,71576,72162,72529,72968,72983,73771,76771,76907,80492,81361,81424,82641,83071,83298,83421
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_54_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"copy_f\" rd=\"8,0:17165,50133|9,0:1258,1707|12,0:21761\"/><wd nm=\"copy_object\" rd=\"12,0:23075,23281\"/><wd nm=\"copy_object_f\" rd=\"12,0:23094,23300\"/><wd nm=\"copying\" rd=\"5,0:37299|8,0:8488,74864,85529,87017,87333,87382|12,0:7391,14013,14190,21797|13,0:366\"/><wd nm=\"copyright\" rd=\"1,0:33,75,226,320,615,727,3601\"/><wd nm=\"cord\" rd=\"3,0:7637|4,0:14464|8,0:59960,79777,80672,81025,81179|11,0:342,2775,3578,3688,4283,4833,5120,12079,12622,12828,16785,16968,17587|12,0:739,8374\"/><wd nm=\"corded\" rd=\"12,0:22479\"/><wd nm=\"cording\" rd=\"3,0:9466,9618|5,0:6258,26542|6,0:14865|7,0:19073,24873,26003,28889,55898|8,0:102,29325,36926,47943,71816,94808,95725|9,0:12647|10,0:4234|12,0:11232,22747\"/><wd nm=\"cordingly\" rd=\"8,0:28820,28998,36409,36587\"/><wd nm=\"cords\" rd=\"5,0:30609,30777,30822|7,0:38140|8,0:6135,42620|9,0:12114,37618|11,0:1315,3461,3473,3885,11798,11937,12109,12891,16118,16139,17161,17239\"/><wd nm=\"cord­ing\" rd=\"6,0:13295|7,0:47044\"/><wd nm=\"core\" rd=\"5,0:13369,26015,26220,32444,32818,32898,32917,33037,33123,33207,33794,34236|7,0:31285|12,0:27387,27403|13,0:1055\"/><wd nm=\"core_f\" rd=\"5,0:13390\"/><wd nm=\"core”\" rd=\"7,0:25768|8,0:67569\"/><wd nm=\"corner\" rd=\"9,0:19870,27790\"/><wd nm=\"corners\" rd=\"9,0:19977\"/><wd nm=\"corporation\" rd=\"1,0:1987\"/><wd nm=\"correct\" rd=\"7,0:20018,25071,42475,69036|8,0:1671,45923,77136,
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_5_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"100\" rd=\"7,0:82110,82523,92065|8,0:73771|9,0:8501,8771,8995,9521,10631,11234,11299,11440,11624,11642,11699,11876,11965,12027,12111|10,0:15145|12,0:15736,15787,15791,15795\"/><wd nm=\"1000\" rd=\"4,0:20929|7,0:51686,88672\"/><wd nm=\"10000\" rd=\"7,0:85455,86278,88665,89496\"/><wd nm=\"102\" rd=\"7,0:82198\"/><wd nm=\"1024\" rd=\"5,0:20206|7,0:22170,22175|8,0:32168,32292\"/><wd nm=\"103516\" rd=\"7,0:72012\"/><wd nm=\"104\" rd=\"7,0:82097,82510\"/><wd nm=\"105\" rd=\"7,0:82117,82530\"/><wd nm=\"10596e\" rd=\"7,0:72075\"/><wd nm=\"108\" rd=\"7,0:82309\"/><wd nm=\"109\" rd=\"7,0:82393\"/><wd nm=\"11\" rd=\"3,0:9425,12420|4,0:18108|5,0:23864,27649,28507,29226,30116,31109,31855,32428,32992,34974,37032,38263,39966,41404,41406|6,0:31193|7,0:43457,51179,71569|8,0:23285,26473,29425,39396,39438,39457,39513,46545,46598,46613,46646,68078,96967|9,0:13049,13426,13751,26800,40141,41056,41733,42599,43305,44227|11,0:17632|13,0:19,130\"/><wd nm=\"110596e\" rd=\"7,0:72075\"/><wd nm=\"1122\" rd=\"8,0:39205\"/><wd nm=\"11231\" rd=\"1,0:2154\"/><wd nm=\"11_b\" rd=\"3,0:12438,12455\"/><wd nm=\"12\" rd=\"3,0:17439|4,0:18367|5,0:20164,20202,35536,42516,42557,43368,43727|7,0:34514,34528,43743,52044,53614,54133,54166,77418,84944|8,0:26525,29861,47419,48881|9,0:13051,13428,13757,17356,25098,30417,30918,40143,41059,41735,42607,43311,44230|11,0:18110\"/><wd nm=\"1200m\" rd=\"7,0:917
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_64_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"dheres\" rd=\"9,0:10947,10987|10,0:11588\"/><wd nm=\"dia\" rd=\"3,0:15388,20975|4,0:25575|5,0:32796,38566\"/><wd nm=\"diag\" rd=\"11,0:4672,5886,12175,12450\"/><wd nm=\"diagnosed\" rd=\"11,0:11629\"/><wd nm=\"diagram\" rd=\"7,0:16951|9,0:5255,34139\"/><wd nm=\"dian\" rd=\"4,0:3754,4024,13794,25931,26042|7,0:14405,14782,28584,28630,54671,56834,58100,61040,61117,72449|8,0:2120,4213,5231,5269,5661,5677,9603,9752,9843,9911,10098,10117,10214,10271,10329,10394,13162,27120,27194,34055,34081,35019,35065,38169,38393,38677,38808,38871,39300,39320,39344,39367,39880,39926,51317,51369,52823,52991,73439,73451,90327,90370,92656,92800,93759,93818\"/><wd nm=\"dianness\" rd=\"7,0:63443,68966,83758,83897\"/><wd nm=\"diate\" rd=\"6,0:17478,17610|12,0:9521,24632,27579\"/><wd nm=\"diate_group\" rd=\"6,0:17367,17498|12,0:9595,24318,24539\"/><wd nm=\"diate_group_f\" rd=\"12,0:24351,24572\"/><wd nm=\"diate_groups\" rd=\"12,0:27599\"/><wd nm=\"diately\" rd=\"6,0:3249|7,0:42594|9,0:39648|12,0:5243,17437\"/><wd nm=\"dicate\" rd=\"6,0:8502|8,0:8594,74108|9,0:8005,10228|11,0:4238,4372,17906\"/><wd nm=\"dicated\" rd=\"5,0:6534,12292,12438,39711|6,0:6724,6791|8,0:77988|11,0:14789|12,0:8612,24845\"/><wd nm=\"dicates\" rd=\"4,0:6844|5,0:16308,33481|6,0:6672,22264,22350|11,0:4893|12,0:6152\"/><wd nm=\"dicating\" rd=\"6,0:6920,6975,8473|7,0:62870,65204|12,0:18062\"/><wd nm=\"dication\" rd=\"8,0:8641,6834
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_66_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ds_f\" rd=\"5,0:9125,12592|8,0:19330,19412|9,0:2942\"/><wd nm=\"dscale\" rd=\"7,0:88209,88260,89879\"/><wd nm=\"dscatter\" rd=\"7,0:4105\"/><wd nm=\"dscompound\" rd=\"8,0:51128,51412,53009,57519,57926,58538,59211\"/><wd nm=\"dset\" rd=\"6,0:31883,31941|7,0:14999,15881,21215,21304,21968,22031,23281,23371,24463,24552,41390,41480\"/><wd nm=\"dset1\" rd=\"3,0:17661,20522|6,0:29004,29020,29203,29439,29618,29962,29987,30007,30016,30046,30149,30176,30220,30544,30565,30716,30756,30863,31358,31688|8,0:88812,88978,89039\"/><wd nm=\"dset1”\" rd=\"7,0:14448,22909|8,0:88833,88997\"/><wd nm=\"dset2\" rd=\"3,0:20103,20691,20880|6,0:29140,29274,29485,29635,29842,30062,30190,30211,30732,30877,30898,31178,31663,31745|8,0:71530,88894\"/><wd nm=\"dset2”\" rd=\"8,0:88915\"/><wd nm=\"dset3\" rd=\"6,0:31459,31819,31955|8,0:89052\"/><wd nm=\"dset3”\" rd=\"8,0:89073\"/><wd nm=\"dset4\" rd=\"8,0:89134\"/><wd nm=\"dset4”\" rd=\"8,0:89155\"/><wd nm=\"dset_create_plists\" rd=\"7,0:74719\"/><wd nm=\"dset_create_props\" rd=\"7,0:68363,69776,69901,70128,70424,71313,71795,74070,74196,74422,75593,85199,86034,86159,86306,86583,87020,87822,88396,89252,89377,89525,89861,90195,91005\"/><wd nm=\"dset_data\" rd=\"7,0:20667,21071,21149,21355,21532,21933,22223,22414,23224,23419,23595|8,0:14531,14625,14676,14769\"/><wd nm=\"
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_68_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"e1\" rd=\"5,0:44793,45203,45268,45773,45910|8,0:24698\"/><wd nm=\"e1_dim1\" rd=\"8,0:65817,65900,69584,69668,71394\"/><wd nm=\"e1_rank\" rd=\"4,0:12676|9,0:26190\"/><wd nm=\"e1”\" rd=\"8,0:71183\"/><wd nm=\"e2\" rd=\"5,0:44953,44999,45051,45184,45254,45764,45946,45991|6,0:15527|8,0:24709|12,0:13155,13330,16840,16928\"/><wd nm=\"e32\" rd=\"8,0:92094,92332,92466\"/><wd nm=\"e9\" rd=\"7,0:72022\"/><wd nm=\"e_\" rd=\"6,0:22575\"/><wd nm=\"e__\" rd=\"11,0:17813,17827,18282,18296\"/><wd nm=\"e_access\" rd=\"3,0:12878|5,0:4916,5515,19208,19429,43961|10,0:15167|12,0:3863,4609\"/><wd nm=\"e_anon\" rd=\"6,0:12765|7,0:2787\"/><wd nm=\"e_anon_f\" rd=\"6,0:12780|7,0:2802\"/><wd nm=\"e_auto2_t\" rd=\"11,0:7517\"/><wd nm=\"e_auto_t\" rd=\"11,0:6640,7116\"/><wd nm=\"e_b16\" rd=\"8,0:11627\"/><wd nm=\"e_b32\" rd=\"8,0:11688\"/><wd nm=\"e_b64\" rd=\"8,0:11749\"/><wd nm=\"e_b8\" rd=\"8,0:11569\"/><wd nm=\"e_buf_size\" rd=\"5,0:12479,23222,23288\"/><wd nm=\"e_buf_size_f\" rd=\"5,0:12505\"/><wd nm=\"e_by_idx\" rd=\"6,0:14790,14920,15064|10,0:4167,4742\"/><wd nm=\"e_by_idx_f\" rd=\"6,0:14809|10,0:4184,4761\"/><wd nm=\"e_by_name\" rd=\"6,0:14360|10,0:3807,4257,5187,5654\"/><wd nm=\"e_by_name_f\" rd=\"6,0:14379|10,0:3825,4275,5672\"/><wd nm
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_74_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"efault”\" rd=\"7,0:43209\"/><wd nm=\"efer\" rd=\"4,0:623,1120|7,0:1754,42637,42716|8,0:17262,25844\"/><wd nm=\"efere\" rd=\"8,0:69800\"/><wd nm=\"eference\" rd=\"3,0:11364,11438|4,0:855,2104,6378|5,0:6637,18854,20685,23419,23532,23634,23761,27185,37833,39847,46132|6,0:1190,1319,1501,3853,8132,8551,12218,22964,24280,25040,26911,27647|7,0:1521,1563,1581,1655,1716,1738,1792,1827,1869,1900,1921,1961,10751,55571,67892,70073,74368,86520,89798|8,0:7783,7794,7846,8782,10585,25379,25462,25700,26768,56554,69928,69948,69973,69991,70006,70134,70319,70348,70522,70540,70608,70843,70938,71032,71115,71344,71536,98073,98495,99451|9,0:777,19263,32578,32618,32781,32857,32911,33087,33310,33871,34011,34076,34677,34904,35163,35584,35984,36919,36996,37061,37074,37185,37210,37243,37267,37591,37975,38321,38340,38367,38438|10,0:11729,16588,16714,17452|12,0:20911,25717\"/><wd nm=\"eferenced\" rd=\"7,0:10765,52960|8,0:70369|9,0:33101\"/><wd nm=\"eferences\" rd=\"4,0:1827|5,0:11777,11854,23377,23401,23804,23848|6,0:698,765,1009,3482|7,0:11139|8,0:2882,10019,25834,63711,63850,70202,70255,70419,70710|9,0:19294,32519,33343,33360,33836,34250,34552,34565,34821,34857,36236,36267,36402,36468,36649,36762,37016,37507,38151|12,0:26698\"/><wd nm=\"eferences_f\" rd=\"5,0:11802\"/><wd nm=\"eferencing\" rd=\"9,0:37697\"/><wd nm=\"eferred\" rd=\"4,0:2169,4346|5,0:3547,24273|7,0:82635|9,0:6583,14364|10,0:10486\"/><wd nm=\"efers\" rd=\"7,0:55693,56022,56079|8,0:89859|9,0:34473\"/><wd nm=\"efe
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_75_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"ehaviors\" rd=\"7,0:46087\"/><wd nm=\"ehensive\" rd=\"5,0:5929|12,0:20770\"/><wd nm=\"ei\" rd=\"8,0:54327,54461,54698,55165\"/><wd nm=\"eid\" rd=\"8,0:72390,72423\"/><wd nm=\"eight\" rd=\"6,0:11204|8,0:10196,10460,10496,10542,27480,72602,72919,74633|9,0:25131\"/><wd nm=\"eiling\" rd=\"7,0:77398,77455\"/><wd nm=\"ein\" rd=\"1,0:3095,3364|6,0:28594\"/><wd nm=\"eing\" rd=\"4,0:26156|5,0:7563,7691,17023,19115,25564,28777,29362,34457,36551|7,0:46473,46621,53078|8,0:49561,63132,64958,66275,66604,70328,70364|9,0:4437,6048,14376,24157|10,0:1237,13052|11,0:3833,5546|12,0:11260,22474|13,0:1258\"/><wd nm=\"eir\" rd=\"1,0:2845|3,0:4539,5698,12767|4,0:15083|5,0:20030,39896|6,0:6681|7,0:51374,91432|8,0:6616,12793,12845,30082|11,0:1075,1302|12,0:26413\"/><wd nm=\"either\" rd=\"1,0:1262,1587,2777|4,0:14496,20524|5,0:15682,32594,34160,38712|6,0:7636,7912,8331,11565,11722,23313,29602,30458,30528,30807,31927|7,0:1234,40456|8,0:26905,33556,70508,89565,89807,92782,94403|9,0:19058,32807|11,0:7265,14764|12,0:384,5163,5477,7158,7492,13971,19149\"/><wd nm=\"eived\" rd=\"7,0:25925\"/><wd nm=\"ejoining\" rd=\"5,0:38120\"/><wd nm=\"el\" rd=\"3,128:11,44,122,155,182,207,263,286,431,735,753,809,876,937,989,1009,1017,1137,1217,1276,1374,1563,1578,1748,1768,2940,3166,3208,3803,3923,4025,4142,4195,4215,4308,4479,4700,13252,13277,13540,13722,13784,13819,13846,13881,13896,13916,13936,13956,13981,14000,14027,14060,14093,14293,14371,14626,14721,15291,15585,15665,15976,16174,16469,21407
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_76_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"elements_f\" rd=\"9,0:3769\"/><wd nm=\"elete\" rd=\"3,0:18139|6,0:3052,5481,15398,18412,22733,23627,23796,23816,24147,24550,25394,26571|7,0:1392,2391,47294,47346|8,0:87509|10,0:4124,12017,12028,12050,12067,12105,12195|11,0:17013\"/><wd nm=\"elete_by_idx\" rd=\"10,0:4167\"/><wd nm=\"elete_by_idx_f\" rd=\"10,0:4184\"/><wd nm=\"elete_by_name\" rd=\"10,0:4257\"/><wd nm=\"elete_by_name_f\" rd=\"10,0:4275\"/><wd nm=\"elete_f\" rd=\"6,0:15408|10,0:4134\"/><wd nm=\"eleted\" rd=\"3,0:18241,21160|6,0:3130,3892,5580,23066,24067,24110,24336,29710,29786|7,0:1371,2380,47221|8,0:85911,87482|10,0:13649\"/><wd nm=\"eletes\" rd=\"6,0:16178,24655|7,0:6000|10,0:4147,4204|11,0:2562,17093\"/><wd nm=\"eleting\" rd=\"3,0:17961,18098|6,0:5303,5440,23639,24178,26506|7,0:47072|10,0:1805,11912\"/><wd nm=\"eletion\" rd=\"9,0:27557\"/><wd nm=\"elevant\" rd=\"3,0:12322,12373,12705|5,0:34296|12,0:5578,5675,5785,6673,7311,27467\"/><wd nm=\"eley\" rd=\"1,0:2058\"/><wd nm=\"ele­ment\" rd=\"3,0:9256|8,0:7670,48434,67949|9,0:5407,19637\"/><wd nm=\"ele­ments\" rd=\"3,0:9012|7,0:30357|8,0:7898,8069,66960,71936|9,0:3141\"/><wd nm=\"ele­vant\" rd=\"8,0:26437\"/><wd nm=\"elf\" rd=\"3,0:13596,17994,18547,19667|6,0:1303,1583,5336,5877,27386,28463,29770|7,0:899,61647,62160|8,0:81094|11,0:115,4342,11837\"/><wd nm=\"elies\" rd=\"5,0:16336\"/><wd nm=\"eliminate
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_78_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"en_by_idx_f\" rd=\"10,0:5388\"/><wd nm=\"en_by_name\" rd=\"4,0:23591,23907|10,0:5482,8649,8672\"/><wd nm=\"en_by_name_f\" rd=\"10,0:5498\"/><wd nm=\"en_colors\" rd=\"8,0:72063,72137,72187,72239,72290,72342,72409\"/><wd nm=\"en_create\" rd=\"8,0:22332,32761,63965,64271\"/><wd nm=\"en_create_f\" rd=\"8,0:22347\"/><wd nm=\"en_f\" rd=\"5,0:7376,9385,9429|6,0:12865|7,0:2888,3676|8,0:16698|9,0:41781,43370|10,0:5290\"/><wd nm=\"en_get_buf_size\" rd=\"7,0:3655,24174\"/><wd nm=\"en_get_max_len_f\" rd=\"7,0:3676\"/><wd nm=\"en_idx\" rd=\"7,0:2296\"/><wd nm=\"en_mem_manager\" rd=\"7,0:8277,8410,49095|8,0:65260,66631\"/><wd nm=\"en_name\" rd=\"7,0:2283\"/><wd nm=\"en_reclaim\" rd=\"7,0:3765,8392,8525,49332|8,0:64886,65358,66036,69753\"/><wd nm=\"en_reclaim_f\" rd=\"7,0:3781\"/><wd nm=\"en_re­claim\" rd=\"8,0:66224\"/><wd nm=\"en_txt\" rd=\"0,0:81,102\"/><wd nm=\"enable\" rd=\"4,0:17400,18064,18110,18204|6,0:17589|7,0:7290,33360|11,0:6563|12,0:565,729,9360,9396,10090,10447,11491\"/><wd nm=\"enabled\" rd=\"7,0:7403,27874,49726|10,0:13377\"/><wd nm=\"enables\" rd=\"3,0:15740|6,0:8159,8756,9539|8,0:14821,31700,60023|12,0:9628\"/><wd nm=\"enabling\" rd=\"5,0:14766|6,0:1310\"/><wd nm=\"ename\" rd=\"9,0:41217,41856,42788,43445|10,0:5611\"/><wd nm=\"ename_by_name\" rd=\"10,0:5654\"/><wd nm=\"
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_81_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"er1\" rd=\"7,0:56994,57015\"/><wd nm=\"er2\" rd=\"7,0:57358,57379\"/><wd nm=\"er32\" rd=\"6,0:16380,16433,16459,16512|7,0:6045,6098,30133,30145|12,0:10586,11570\"/><wd nm=\"er32_f\" rd=\"6,0:16398,16477|7,0:6063\"/><wd nm=\"er_attribute\" rd=\"4,0:22914,23693\"/><wd nm=\"er_be\" rd=\"7,0:68926|8,0:15373,27202,34088\"/><wd nm=\"er_blocklist\" rd=\"9,0:2811,39334\"/><wd nm=\"er_blocklist_f\" rd=\"9,0:2841\"/><wd nm=\"er_bounds\" rd=\"5,0:12571,12701|6,0:10310,10359|10,0:15192\"/><wd nm=\"er_bounds_f\" rd=\"5,0:12592\"/><wd nm=\"er_by_id\" rd=\"6,0:15852|7,0:5749\"/><wd nm=\"er_by_id_f\" rd=\"6,0:15872|7,0:5769\"/><wd nm=\"er_cache\" rd=\"7,0:32508\"/><wd nm=\"er_callback\" rd=\"7,0:7427\"/><wd nm=\"er_class\" rd=\"8,0:21241,30485,56369|11,0:2851,3146,14357,15252,15521,16011\"/><wd nm=\"er_class_f\" rd=\"8,0:21261\"/><wd nm=\"er_conv\" rd=\"8,0:18270\"/><wd nm=\"er_conv_f\" rd=\"8,0:18287\"/><wd nm=\"er_f\" rd=\"5,0:13212|6,0:15736,16085,16158,16331,17163,17274|7,0:5407,5633,5907,5980,6971,7042|8,0:17553,17813,17874,54123|10,0:6118,6339|12,0:22184,22516\"/><wd nm=\"er_group_f\" rd=\"6,0:17400\"/><wd nm=\"er_id\" rd=\"8,0:52582,52635,52691,52751|9,0:36483,36576\"/><wd nm=\"er_index\" rd=\"8,0:20958,21428\"/><wd nm=\"er_index_f\" rd=\"8,0:21448\"/><wd nm=\"er_info\" rd=\"5,0:1
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_82_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"erformed\" rd=\"4,0:22686,26513|7,0:9828,30895,56286|8,0:91380,92016|12,0:11265\"/><wd nm=\"erforming\" rd=\"7,0:53002|8,0:93035|10,0:11218\"/><wd nm=\"erforms\" rd=\"4,0:26058|5,0:30755|7,0:26713,60566,76479,83748|8,0:66248\"/><wd nm=\"erful\" rd=\"4,0:14503\"/><wd nm=\"erge\" rd=\"12,0:14873\"/><wd nm=\"erge_committed_dtype_path\" rd=\"12,0:22811\"/><wd nm=\"erge_committed_dtype_paths\" rd=\"12,0:22962\"/><wd nm=\"ergy\" rd=\"1,0:2120,2597\"/><wd nm=\"erhaps\" rd=\"8,0:63537\"/><wd nm=\"erhead\" rd=\"6,0:9201|7,0:36406\"/><wd nm=\"eri\" rd=\"8,0:67135\"/><wd nm=\"eria\" rd=\"6,0:11255\"/><wd nm=\"erial\" rd=\"3,0:15935|5,0:516,17499,17540|7,0:25787,31517,31574,31787,32053,40139,40529,42051,43434,43495|12,0:464,1321,11044,11100\"/><wd nm=\"erialize\" rd=\"7,0:9970\"/><wd nm=\"erialized\" rd=\"7,0:34422\"/><wd nm=\"erials\" rd=\"1,0:813,1028\"/><wd nm=\"eric\" rd=\"3,0:11679|7,0:8828,11714,59710,64957,65774,66188,66356,66769|8,0:26456,27967,33202,35618,94370,94386,94641,94708|12,0:1672,2227,20431,20489,20827,20952,21106,23763,26185,26273\"/><wd nm=\"erical\" rd=\"4,0:25735|7,0:386\"/><wd nm=\"eried\" rd=\"5,0:20269,20446,20585,20930,21113,21302|8,0:26186,89931|9,0:5091\"/><wd nm=\"eries\" rd=\"4,0:1969,11949|6,0:16704,16911,17304|7,0:54373|8,0:14993,26430|10,0:10986|12,0:23993,24387\"/><wd nm=\"erifies\" rd=\"5,0:6
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_83_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"error_test\" rd=\"11,0:12241,12345\"/><wd nm=\"errors\" rd=\"11,0:160,466,1494,4609,6597,6741,14529\"/><wd nm=\"ers\" rd=\"1,0:1687|3,0:1115,1401,1949,2460,2608,2860,3556,4525,5081,5484,6035,6180,6201,6211,7613,7622,9316,9325,9563,9969,12092,12182,12923,14018,14051,14202,14246,14267,14641,14921,15817,16070,16183,16367,18896,18964,19020,19393,20342|4,0:669,682,699,1763,1877,2084,3513,3760,4870,5344,5830,6727,8325,8465,8601,11435,13456,13495,14765,14772,14899,15030,15153,15316,15569,15891,16020,16063,16277,16366,21562,25166,25318,25659,27443|5,0:470,2112,3161,3683,7097,9084,9167,9567,10126,11519,16363,16573,16622,19333,19998,20979,21067,21165,21256,21632,21643,21755,23024,24486,24613,24800,24817,24831,24925,25034,25117,25171,27292,28697,28806,29076,30069,30958,30993,31009,31062,31243,31702,32277,34714,36965,36983,37741,38023,38093,39917,40950,41250,42467,45438,45451|6,0:447,503,1948,2891,3058,3530,7065,7143,7199,7518,7529,7585,9448,10945,11005,11096,11135,11214,13680,15701,15993,16046,16194,16598,18403,18426,18521,23697,28213,30932|7,0:742,1290,3824,4058,4139,5523,5544,5597,6016,7019,7145,7227,9857,10207,11731,12933,12971,12993,13082,13170,13202,13323,13467,13950,13973,13999,14795,16610,16623,16636,16763,16980,17067,18033,18433,19192,19212,19330,19375,19396,19410,19583,19610,19718,19735,19762,19775,19873,20001,20079,20609,21000,21036,22883,22957,24813,24977,25138,25242,26333,26478,26999,27222,27773,27949,28253,28262,29006,29136,29197,29270,29344,29416,29455,29587,29626,30094,30183,30413,30537,30882,31068,31251,32059,32180,32467,32499,32724,32738,32767,34905,36842,38574,38603,41941
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_85_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"es_f\" rd=\"5,0:9983,10512,11802|12,0:22401,22714\"/><wd nm=\"es_fig1\" rd=\"8,0:557,571\"/><wd nm=\"es_fig10\" rd=\"8,0:46230,46245\"/><wd nm=\"es_fig11\" rd=\"8,0:46598,46613\"/><wd nm=\"es_fig16a\" rd=\"8,0:67696,67712\"/><wd nm=\"es_fig16b\" rd=\"8,0:67832,67848\"/><wd nm=\"es_fig16c\" rd=\"8,0:68107,68123\"/><wd nm=\"es_fig16d\" rd=\"8,0:68142,68158\"/><wd nm=\"es_fig17a\" rd=\"8,0:72933,72949\"/><wd nm=\"es_fig2\" rd=\"8,0:5459,5473\"/><wd nm=\"es_fig20a\" rd=\"8,0:83499,83515\"/><wd nm=\"es_fig20b\" rd=\"8,0:83568,83584\"/><wd nm=\"es_fig20c\" rd=\"8,0:83653,83669\"/><wd nm=\"es_fig20d\" rd=\"8,0:83723,83739\"/><wd nm=\"es_fig23\" rd=\"8,0:48934,48949\"/><wd nm=\"es_fig26_pic1of4\" rd=\"8,0:60316,60339\"/><wd nm=\"es_fig26_pic2of4\" rd=\"8,0:60365,60388\"/><wd nm=\"es_fig26_pic3of4\" rd=\"8,0:60414,60437\"/><wd nm=\"es_fig26_pic4of4\" rd=\"8,0:60464,60487\"/><wd nm=\"es_fig28\" rd=\"8,0:62629,62644\"/><wd nm=\"es_fig3\" rd=\"5,0:45118,45131|8,0:6263,6277\"/><wd nm=\"es_fig33\" rd=\"8,0:66117,66132\"/><wd nm=\"es_fig4\" rd=\"5,0:45274,45287|8,0:6556,6570\"/><wd nm=\"es_fig40\" rd=\"8,0:72968,72983\"/><wd nm=\"es_fig45\" rd=\"8,0:79934,79949\"/><wd nm=\"es_fig47\" rd=\"8,0:83023,83038\"/><wd nm=\"es_fig5
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_8_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"5ch11231\" rd=\"1,0:2154\"/><wd nm=\"5check_version\" rd=\"5,0:6962\"/><wd nm=\"5check_version_f\" rd=\"5,0:6978\"/><wd nm=\"5close\" rd=\"4,0:5741,5762|5,0:7044|10,0:12591\"/><wd nm=\"5close_f\" rd=\"5,0:7052|9,0:42438,44027\"/><wd nm=\"5d\" rd=\"4,0:1699|7,0:1066,2501,2626,16661,20323\"/><wd nm=\"5d_chunked\" rd=\"12,0:15485,19185\"/><wd nm=\"5d_contiguous\" rd=\"7,0:49661|12,0:15528,19168\"/><wd nm=\"5d_unlimited\" rd=\"7,0:12225\"/><wd nm=\"5d_­compact\" rd=\"12,0:19155\"/><wd nm=\"5dclose\" rd=\"4,0:4537|7,0:2977,15064,15940,21552,22434,23615,24747,41667,70847,71263,75148,75544,87378,87773,90559,90956|9,0:40876|11,0:18487\"/><wd nm=\"5dclose_f\" rd=\"7,0:2986|9,0:42263,43852\"/><wd nm=\"5dcreate\" rd=\"4,0:4053,18462,21116,21577,21606|6,0:21461,21600|7,0:2670,10569,11456,14983,15380,15865,70363,74658,86959,90134|8,0:13268,51110,62488,64313,70748,72380,75807,75831,76301,76920,82883,85749,86966,88818,88900,89058,89140|9,0:36534,40594\"/><wd nm=\"5dcreate2\" rd=\"12,0:13155,13330,16840,16928\"/><wd nm=\"5dcreate_anon\" rd=\"7,0:2787\"/><wd nm=\"5dcreate_anon_f\" rd=\"7,0:2802\"/><wd nm=\"5dcreate_f\" rd=\"7,0:2680|8,0:54942|9,0:42025,43614\"/><wd nm=\"5detect\" rd=\"8,0:9416\"/><wd nm=\"5dextend\" rd=\"4,0:18607,18872\"/><wd nm=\"5dfill\" rd=\"7,0:4187\"/><wd nm=\"5dfill_f\" rd=\"7,0
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_91_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"exam­ples\" rd=\"12,0:10141\"/><wd nm=\"exceed\" rd=\"5,0:34497|7,0:36048\"/><wd nm=\"exceeded\" rd=\"10,0:13464\"/><wd nm=\"except\" rd=\"3,0:5845,18923|4,0:1134|5,0:25506,29300|6,0:3730|7,0:21606,26118,71016,75317,80483,87548,90729|8,0:68031,77098,86775,88331,98050|9,0:22129|10,0:6917,17543\"/><wd nm=\"excepti\" rd=\"12,0:26833\"/><wd nm=\"exception\" rd=\"3,0:16335|4,0:5897,6176|6,0:2252|8,0:240,90801,91267,94217|12,0:17378\"/><wd nm=\"exceptions\" rd=\"4,0:5698|8,0:91475,91510|11,0:6198|12,0:19872,26866\"/><wd nm=\"excerpt\" rd=\"4,0:20604\"/><wd nm=\"excessively\" rd=\"4,0:17246\"/><wd nm=\"excl\" rd=\"4,0:3016|5,0:975,1152,4354,4997,15439\"/><wd nm=\"execute\" rd=\"9,0:27587\"/><wd nm=\"executed\" rd=\"6,0:4240|7,0:16033|9,0:22235\"/><wd nm=\"executes\" rd=\"6,0:3210\"/><wd nm=\"execution\" rd=\"4,0:3419\"/><wd nm=\"exed\" rd=\"4,0:15064|5,0:21151,21185|6,0:8685,8881,8989,9099,9339,9486,9878,9932,10026,10072,10132,10750,10795,10992,11362,11582,11611,17350|9,0:33463,33691\"/><wd nm=\"exercise\" rd=\"6,0:26536\"/><wd nm=\"exes\" rd=\"5,0:10484,10581,10590,10683|10,0:12310\"/><wd nm=\"exes_f\" rd=\"5,0:10512\"/><wd nm=\"exibility\" rd=\"4,0:9307\"/><wd nm=\"exible\" rd=\"5,0:24363|8,0:991,3145|9,0:31665\"/><wd nm=\"exing\" rd=\"5,0:10264|6,0:8821,17221|10,0:6168,6384,13851|12,0:22234,22561\"/><wd nm=\"exist\" rd
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_97_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"flushed\" rd=\"5,0:33592\"/><wd nm=\"flushes\" rd=\"5,0:5831,7063,8009\"/><wd nm=\"fly\" rd=\"0,64:231|1,64:4050|2,64:292|3,64:21272|4,64:28188|5,64:18685,46253|6,64:32164|7,64:64922,92417|8,64:55996,101209|9,64:44355|10,64:17864|11,64:18717|12,64:446,27738|13,64:1534\"/><wd nm=\"fmount\" rd=\"5,0:9343,44370,44522,45738,45800,45817,46082|6,0:27548,27622\"/><wd nm=\"fmount_f\" rd=\"5,0:9352\"/><wd nm=\"fmpl\" rd=\"12,0:3840,6195\"/><wd nm=\"fo\" rd=\"5,0:8441,13280,41834,41842,41899,41908,42029,42040,42051,42073,42182|6,0:3408,13136,14598,14661,14677,14774,16765,16866,24243,24398,24497,24521,26867,27764,27778|8,0:66734,66782|10,0:4430,8962,10306,10360,10398,10451\"/><wd nm=\"fo_by_idx\" rd=\"6,0:13223,14944|10,0:4509\"/><wd nm=\"fo_by_idx_f\" rd=\"6,0:13242|10,0:4528\"/><wd nm=\"fo_by_name\" rd=\"6,0:13340,15087|10,0:4605\"/><wd nm=\"fo_by_name_f\" rd=\"6,0:13360,15107|10,0:4625\"/><wd nm=\"fo_f\" rd=\"6,0:13148,14610,16786,16887|10,0:4442\"/><wd nm=\"fo_idx_f\" rd=\"6,0:13430,13539,13697\"/><wd nm=\"fo_null\" rd=\"5,0:44024\"/><wd nm=\"fo_t\" rd=\"6,0:27855,27867|7,0:48669,48862|10,0:10387\"/><wd nm=\"focus\" rd=\"12,0:1804\"/><wd nm=\"folder\" rd=\"5,0:35925\"/><wd nm=\"folders\" rd=\"6,0:447,503\"/><wd nm=\"follow\" rd=\"6,0:6361|7,0:77755,84674\"/><wd nm=\"followed\" rd=\"6,0:6094|8,0:48119,77805|9,0:18365\"/><wd nm=\"following\" 
[…]

### 2016-02-04 html/UG/HDF5_Users_Guide-Responsive HTML5/whxdata/package_98_xml.js

@@ -1,1 +1,1 @@
-gXMLBuffer="<?xml version=\"1.0\" encoding=\"utf-8\" standalone=\"no\"?><pk><wd nm=\"formatted\" rd=\"5,0:6249|8,0:42275\"/><wd nm=\"forma­tion\" rd=\"10,0:9278\"/><wd nm=\"formed\" rd=\"3,0:2497|4,0:22686,26513,26974,27032|7,0:9828,12705,27045,30895,56286|8,0:1803,90417,91380,92016,92827|12,0:11265\"/><wd nm=\"former\" rd=\"8,0:95073\"/><wd nm=\"formerly\" rd=\"3,0:10354|6,0:2653|8,0:86494\"/><wd nm=\"forming\" rd=\"7,0:53002|8,0:93035|10,0:11218\"/><wd nm=\"formly\" rd=\"4,0:8925\"/><wd nm=\"forms\" rd=\"1,0:441,888|3,0:1058|4,0:279,7999,25447,26058|5,0:30755|7,0:17845,26713,28519,53695,60089,60566,76479,80062,83748|8,0:45723,48070,66248,92844,97368,97974,98202|9,0:19008\"/><wd nm=\"formula\" rd=\"7,0:59118\"/><wd nm=\"fornia\" rd=\"1,0:2222,2478,2638,2827,3317,3449\"/><wd nm=\"fort\" rd=\"4,0:20847|5,0:16954|6,0:10524\"/><wd nm=\"forth\" rd=\"9,0:23204\"/><wd nm=\"fortran\" rd=\"3,0:2040|4,0:14332|5,0:6936,7504,7632,7789,7844,8456,8527,8617,8714,8793,9201,9525,9614,9857,10621,10853,10965,11079,11329,11567,12000,12228,12364,12725,13118,13161,13302,13835,14632,14698,14813|6,0:12622,13584,13791,14120,14187,14443,14692,14966,15228,15322,15606,15658,17534,17923,17987,18127|7,0:2642,3422,3960,4038,4119,4400,4997,5480,6929,7453,7695,7791,8304,8437,8697,8803,8900,8992,9091,9176|8,0:9084,9122,16618,17297,17727,18178,18378,18439,18506,18631,20291,20981,21115,21879,22304,22538,22744,22793,22872,23003,23339,23390,23486,37706,37922,42194,42653,42699,42937,43056,43227,43249,43572,43663,44668,44722,44824,44931,49782,49831,50120,532
[…]

### 2016-02-04 RFCs/HDF5_Library/AnalysisExt/analysis_ext-body.tex
More fixes to analysis RFC
Former-commit-id: c8ef4ae1fe2c15cc648c50526e6b8da0c5e65c7a

@@
 application developer to select, read and write data but does not provide any 
-mechanism to select and retrieve pieces without prior knowledge of their
+mechanism to select and retrieve pieces without prior knowledge of its
 content, or without the developer to provide the exact data coordinates that
@@
 to issue queries by specifying a data selection criteria. These queries,
-when applied to the data, can then generate a selection, which contains the coordinates
-that satisfy the query---this may imply accessing the data and selecting it,
-depending on the query condition satisfaction. To accelerate and facilitate this
-process (i.e., so that the data no longer needs to be directly accessed), one can
-use indexing techniques, which consist of generating an index and using that index
-to answer the query selection criteria and find the matching elements.
+applied to the data, can then generate a selection, which in turn contains a
+set of coordinates
+satisfying the query. However, generating a selection may actually imply accessing the
+data. To accelerate and facilitate that
+process (i.e., so that the actual data no longer needs to be accessed), one can
+also generate indexes and use these indexes
+to directly answer the specified query, by finding the coordinates of the matching
+elements directly from the index.
 
@@
 \item New \textit{index} objects and API routines, which allows the creation of
-indices on the contents of HDF5 containers, to improve query performance.
+indexes on the contents of HDF5 containers, to improve query performance.
 \end{itemize}
@@
 calls to \texttt{H5Qcombine}, creating more complex queries.
-
 For example, a single call to \texttt{H5Qcreate} could create a query object
@@
 Applying a query to an HDF5 container creates an HDF5 \textit{view}. A view is
-an anonymous HDF5 group in a temporary memory container. A view group contains up to
+an anonymous HDF5 group created in a temporary memory container. A view group contains up to
 three 1-D dataset objects with references into the contents of the HDF5 container
@@
 group. The attributes, objects, and/or data regions referenced within a view's
-datasets can be retrieved by further HDF5 dataset (H5D*) API calls.
+datasets can be retrieved by further HDF5 dataset (\texttt{H5D*}) API calls.
 
@@
 container may have been modified in the meantime). It may be useful in
-that case to define different states to the view (\textit{dead} or
+the future to define different states to the view (\textit{dead} or
 \textit{live}) so that the user knows whether the view is current or not.
@@
 
-\begin{table}[ht]\footnotesize
-\caption{Query combinations and associated result reference type.}
-\label{tab:querycomb}
-\begin{tabular}{ll} \toprule
-Query &
-Result Type\\ \midrule
+\begin{longtable}{ll}
+\vspace{-30pt}\\
+\caption{Query combinations and associated result reference type.}\\
+\label{tab:querycomb} \vspace{-10pt} \\
+\toprule
+Query & Result Type\\ \midrule
+\endfirsthead
+\toprule
+Query & Result Type\\ \midrule
+\endhead
+\multicolumn{2}{c}{\ldots}\\
+\bottomrule
+\endfoot
+\bottomrule
+\endlastfoot
 \texttt{H5Q\_TYPE\_DATA\_ELEM} & Dataset~Region \\
@@
 Combination $\mathrm{\land}$ Combination & None \\
-\bottomrule
-\end{tabular}
-\end{table}
+\end{longtable}
 
@@
 \begin{lstlisting}
-hid_t H5Qapply_multi(size_t loc_count, hid_t *loc_ids, hid_t query_id,
+hid_t H5Qapply_multi(size_t loc_count, hid_t loc_ids[], hid_t query_id,
   unsigned *result, hid_t vcpl_id);
@@
 or individual datasets within a container. These locations may reside within the
-same container, or in multiple containers. Additionally, the \texttt{H5Qapply\_str}
-routine allows the user to provide container names instead of HDF5 locations:
-
-{\lstsetc
-\begin{lstlisting}
-hid_t H5Qapply_str(size_t cont_count, const char *cont_name[], hid_t query_id,
-  unsigned *result, hid_t vcpl_id);
-\end{lstlisting}
-}
-
-As a direct consequence, one may want to pass queries that match a particular
-container name. Therefore the \texttt{H5Q\_TYPE\_CONT\_NAME} query type can be
-used to construct a query that matches this new condition. The matching
-condition may be passed in the form of a file name or a regular
-expression.
-
-(Optional?) Apply query on all the containers of a given directory with \texttt{H5Qapply\_dir}
-{\lstsetc
-\begin{lstlisting}
-hid_t H5Qapply_dir(const char *path, hid_t query_id, unsigned *result, hid_t vcpl_id);
-\end{lstlisting}
-}
-
+same container, or in multiple containers.
 Applying cross-container queries creates a view that contains references
@@
 a reference to an object within an externally referenced container\footnote{
-As a result, the HDF5 reference API does not require any changes.}.
+Please refer to the H5R reference RFC.}.
 
-Parallel execution of the query optional? \textit{Pass hint for parallel execution
-through property list.}
+%Additionally, the \texttt{H5Qapply\_str}
+%routine allows the user to provide container names instead of HDF5 locations:
+%{\lstsetc
+%\begin{lstlisting}
+%hid_t H5Qapply_str(size_t cont_count, const char *cont_name[], hid_t query_id,
+%  unsigned *result, hid_t vcpl_id);
+%\end{lstlisting}
+%}
+%As a direct consequence, one may want to pass queries that match a particular
+%container name. Therefore the \texttt{H5Q\_TYPE\_CONT\_NAME} query type can be
+%used to construct a query that matches this new condition. The matching
+%condition may be passed in the form of a file name or a regular
+%expression.
+%(Optional?) Apply query on all the containers of a given directory with \texttt{H5Qapply\_dir}
+%{\lstsetc
+%\begin{lstlisting}
+%hid_t H5Qapply_dir(const char *path, hid_t query_id, unsigned *result, hid_t vcpl_id);
+%\end{lstlisting}
+%}
+
+%Parallel execution of the query optional? \textit{Pass hint for parallel execution
+%through property list.}
 
@@
 Index objects are designed to accelerate creation of views from query operations.
-For example, if the ``$\mathrm{(link\_name = Pressure)}$
+For example, if the previously described ``$\mathrm{(link\_name = Pressure)}$
 $\mathrm{\land}$ $\mathrm{(data\_element = 17)}$'' query
-(previously described) is going to be either frequently executed or executed
-on a container that contains significantly large datasets, indices
+is going to be either frequently executed or executed
+on a container that contains significantly large datasets, indexes
 could be created in that container, which would speed up the
 creation of views when querying for link names and for data element values.
-Indices created for accelerating the  ``$\mathrm{(link\_name = Pressure)}$'' or
+Indexes created for accelerating the  ``$\mathrm{(link\_name = Pressure)}$'' or
 ``$\mathrm{(data\_element}$ $\mathrm{= 17)}$'' queries
@@
 $\mathrm{(data\_element = 17)}$'' query.
-Although creating indices for metadata components of queries, such as link or
+Although creating indexes for metadata components of queries, such as link or
 attribute names, is possible, we first focus on index creation for dataset elements,
@@
 a dataspace selection to the library for later use.
-There are different techniques for creating data element indices, and the most
+There are different techniques for creating data element indexes, and the most
 efficient method will vary depending on the type of the data that is to be
@@
 The interface provides indexing plugins with efficient access to the contents of
-the container for both the creation and the maintenance of indices. In addition,
+the container for both the creation and the maintenance of indexes. In addition,
 the interface allows third-party plugins to create private data structures
@@
 \begin{figure}
+\vspace{-30pt}
 \input{pics/hdf5_index}
@@
 parameters. Applications can also directly use the internally called
-\texttt{H5Dquery} routine defined below
-to directly execute a query on a particular dataset (accelerated by any index defined on the dataset),
+\texttt{H5Dquery} routine defined below to directly execute a query on a
+particular dataset (accelerated by any index defined on the dataset),
 and retrieve the selection that matches the query.
@@
 Because the amount of space taken by the index cannot be directly retrieved by
-the user (since the datasets storing the indices are known only by the plugin
+the user (since the datasets storing the indexes are known only by the plugin
 itself), the \texttt{get\_size} callback can query the amount of space that
@@
 \begin{figure}
+\vspace{-10pt}
 \input{plots/indexing_perf}
@@
 
-There are some existing limitations in the use of indices in the current
+There are some existing limitations in the use of indexes in the current
 implementation: FastBit and ALACRITY do not support incremental updates,
 an index is a shared resource for a dataset. Taken together, these conspire to
-put limits on application updates to datasets with indices.
+put limits on application updates to datasets with indexes.
 Additionally, because FastBit and ALACRITY do not allow incremental updates to
@@
 \subsubsection*{Questions}
-Some questions are still open regarding the handling of indices:
+Some questions are still open regarding the handling of indexes:
 \begin{enumerate}
@@
 Consequently, creating an index from that dataset requires the user to select a
-particular field to be indexed, which may lead to having multiple indices per dataset
+particular field to be indexed, which may lead to having multiple indexes per dataset
 depending on the number of fields that it contains. This can be done by passing
@@
 Existing HDF5 tools must be compatible and take into account the existence of
-indices in the file if there are any. For reference, the following behavior for
+indexes in the file if there are any. For reference, the following behavior for
 the tools is given:

### 2016-02-04 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
More fixes to analysis RFC
Former-commit-id: c8ef4ae1fe2c15cc648c50526e6b8da0c5e65c7a

@@
 \providecommand{\kb}[1]{\SI{#1}{\kilo\byte}}
+
+% Break table
+\usepackage{longtable}
 
@@
 \author{Quincey Koziol}
-\date{Oct 15, 2015}
-\rfcversion{2014-07-17.v7}
+\date{Feb 3, 2016}
+\rfcversion{2014-07-17.v9}
 \revision{Jul. 17, 2014}{Version 1 circulated for comment within The HDF Group.}
@@
 \revision{Oct. 15, 2015}{Version 7 first draft of cross-container queries.}
+\revision{Oct. 31, 2015}{Version 8 some corrections.}
+\revision{Feb. 3, 2016}{Version 9 more text corrections.}
 
@@
 consuming process, particularly so when data is very large. To enable, ease and 
-accelerate this process, we introduce in this RFC extensions to the library
-to efficiently query, select and index data.
+accelerate this process, we introduce a set of extensions to the HDF5 library
+that enable efficient query, selection, and indexing of data. This document defines
+the \texttt{H5Q} \textit{query} and \texttt{H5X} \textit{indexing} interfaces as
+well as a \textit{view} structure that can be used to store and retrieve query results.
 \end{abstract}

### 2016-02-06 RFCs/HDF5_Library/AnalysisExt/analysis_ext-body.tex
More update to analysis document
Former-commit-id: bc183e6cb18f23e94a8800a6dbc554da7d4c95b2

@@
 $\mathrm{(data\_element = 17)}$'' query.
-Although creating indexes for metadata components of queries, such as link or
-attribute names, is possible, we first focus on index creation for dataset elements,
-as they represent the largest volume of data in typical HPC application usage of
-HDF5. Queries with metadata components execute properly,
-but are not able to be accelerated with an index currently.
+We distinguish two different types of indexes: \textit{data} indexes and
+\textit{metadata} indexes. Data indexes apply to dataset elements, which
+represent the largest volume of data in typical HPC application usage of HDF5,
+whereas metadata indexes apply to link or attribute name components of the queries.
 
-The indexing API can work in conjunction with the view creation. When an \texttt{H5Qapply}
+\subsection{Data Indexing}
+
+The data indexing API can work in conjunction with the view creation. When an \texttt{H5Qapply}
 call is made on a given location, an index attached to any dataset queried
@@
 
-\subsection{Indexing Interface and Plugins}
+\subsubsection{Indexing Interface and Plugins}
 
@@
 
-    /* Callbacks, described above */
+    /* Callbacks */
+    union {               /* Union of callback index structures */
+        H5X_data_class_t data_class;
+        H5X_metadata_class_t metadata_class;
+    } idx_class;
+} H5X_class_t;
+
+typedef struct {
     void *(*create)(hid_t dataset_id, hid_t xcpl_id, hid_t xapl_id,
@@
     herr_t (*get_size)(void *idx_handle, hsize_t *idx_size);
-} H5X_class_t;
+} H5X_data_class_t;
 \end{lstlisting}
@@
 
-\subsection{Limitations}
+\subsubsection{Limitations}
 
@@
 
-\subsubsection*{Questions}
-Some questions are still open regarding the handling of indexes:
+\paragraph{Questions}Some questions are still open regarding the handling of indexes:
 \begin{enumerate}
@@
 
-\subsection{Support for HDF5 Compound Types (TBD)}
+\subsubsection{Support for HDF5 Compound Types (TBD)}
 
@@
 
-\subsection{Support for HDF5 Chunking (TBD)}
+\subsubsection{Support for HDF5 Chunking (TBD)}
 
@@
 
-\subsection{Support for Parallel Indexing (TBD)}
+\subsubsection{Support for Parallel Indexing (TBD)}
 
@@
 interface more heavy.
+
+\subsection{Metadata Indexing}
+
+Metadata indexing accelerates HDF5 metadata query operations, improving 
+the speed of data analysis operations. Currently metadata query operations
+in HDF5 are performed by traversing the contents of the container specified
+in the query, potentially generating a large amount of I/O and taking
+significant time to create the query results. Adding a mechanism for storing
+metadata indexes to HDF5 containers can accelerate query operations by avoiding
+these expensive traversals, as is available for data element queries.
+
+A metadata index is a data structure that tracks a particular aspect of an HDF5 container 
+and can quickly answer queries about that aspect. For example, a metadata index can 
+be created that tracks all the link names for objects in a container, updating the index 
+whenever a link is added, modified or removed. This index can then be applied to 
+queries on link names, avoiding a traversal over all the links for groups in the container.
+
+\subsubsection{Indexing Interface and Plugins}
+
+The interface for metadata indexes in HDF5 containers is modeled after the interface 
+for data element indexes in HDF5, with a plugin architecture that allows new metadata 
+index packages to be developed and added at application runtime, without modifications 
+to the core HDF5 library.
+The HDF5 library can then interact with the third-party indexes created in this manner 
+through a set of callback interfaces that present query information to the
+indexing package and retrieve results from it.
+An HDF5 metadata index can be considered as a generic key-value store, in the
+sense that for each \textit{key} that represents an HDF5 object ID, is associated
+either a link/attribute name or an attribute \textit{value}.
+
+{\lstsetc
+\begin{lstlisting}
+typedef struct {
+    void *(*create)(hid_t loc_id, hid_t xcpl_id, hid_t xapl_id,
+        size_t *metadata_size, void **metadata);
+    herr_t (*remove)(hid_t loc_id, size_t metadata_size, void *metadata);
+    void *(*open)(hid_t loc_id, hid_t xapl_id, size_t metadata_size,
+        void *metadata);
+    herr_t (*close)(void *idx_handle);
+
+    herr_t (*insert_entry)(void *idx_handle, hid_t obj_id, hid_t xxpl_id);
+    herr_t (*remove_entry)(void *idx_handle, hid_t obj_id, hid_t xxpl_id);
+    herr_t (*query)(void *idx_handle, hid_t query_id, hid_t xxpl_id,
+        size_t *obj_count, hid_t *obj_ids[]);
+
+    herr_t (*get_size)(void *idx_handle, hsize_t *idx_size);
+} H5X_metadata_class_t;
+\end{lstlisting}
+}
+
+The \texttt{create}, \texttt{remove}, \texttt{open}, \texttt{close} callbacks
+are similar to the data index plugins, albeit they operate on a file location and
+not on a single object. The \texttt{insert\_entry}, \texttt{remove\_entry} callbacks
+respectively insert/remove a referenced object from the index. Values can be extracted from
+the object ID, depending on the metadata type that the plugin will index.
+When the \texttt{query} callback is invoked, a list of object IDs that matches
+the query is returned. The \texttt{get\_size} callback returns the size of the index
+and additional info callbacks may also be added depending on the needs.
+
+\subsubsection{Current and future plugins}
+
+Are considered both a MDHIM and a B-Tree plugin.
 

### 2016-02-08 RFCs/HDF5_Library/AnalysisExt/analysis_ext-body.tex
Update metadata indexing design doc
Former-commit-id: b578bfebadc799e9faf5e2b0b5429a7c93f079de

@@
 An HDF5 metadata index can be considered as a generic key-value store, in the
-sense that for each \textit{key} that represents an HDF5 object ID, is associated
-either a link/attribute name or an attribute \textit{value}.
+sense that for each \textit{key} that can for instance represent either a
+link/attribute name and/or an attribute \textit{value}, is associated an HDF5
+object ID. However, this is up to the plugin to define that mapping and its
+storage organization.
 
@@
 not on a single object. The \texttt{insert\_entry}, \texttt{remove\_entry} callbacks
-respectively insert/remove a referenced object from the index. Values can be extracted from
-the object ID, depending on the metadata type that the plugin will index.
+respectively insert/remove a referenced object from the index. Information can
+be directly extracted from the object ID, depending on the metadata type that
+the plugin will choose to index.
 When the \texttt{query} callback is invoked, a list of object IDs that matches
-the query is returned. The \texttt{get\_size} callback returns the size of the index
-and additional info callbacks may also be added depending on the needs.
+the query is returned. The \texttt{get\_size} callback\footnote{Additional info
+callbacks may also be added depending on the needs.} returns the size of the index.
 
@@
 
-Are considered both a MDHIM and a B-Tree plugin.
+Are considered both a MDHIM~\cite{Greenberg15} and a B-Tree based plugin to
+provide metadata indexing capabilities. \textit{More details will be added
+once the design for these plugins has been defined.}
 
@@
 
-\section{Usage Example}
+\section{Usage Examples}
 
-In the following example, we show how one can make use of the query and
-indexing interface to retrieve a dataspace selection within a dataset.
-For simplicity's sake, we first create a dataset within the file, then open it to
-create and attach a new index, in order to finally query data from it.
-Note that for convenience, calls to directly read data that corresponds to the
-result of the index query may be moved to the high-level API in the future.
+These basic examples aim at showing the analysis components presented so far.
+We describe in these examples the query and view creation process and how to
+efficiently retrieve data from a file by adding indexes.
+
+\subsection{Query and View}
+In this example, we show how one can create a query, apply that query to a file,
+and retrieve data from the resulting view.
+
+{\lstsetc
+\begin{lstlisting}
+#define FILENAME "test.h5"
+#define DATASETNAME "Pressure"
+
+int
+main(int argc, char *argv[])
+{
+    hid_t t file, query, subquery1, subquery2, view;
+    float subquery2_value = 3.14;
+    unsigned apply_result = 0;
+
+    /* Create file */
+    file = H5Fcreate(FILENAME, H5F_ACC_TRUNC, H5P_DEFAULT, H5P_DEFAULT);
+
+    /* Create groups / datasets / attributes / etc */
+
+    /* Close the file */
+    H5Fclose(file);
+
+    /* Create a simple query */
+    subquery1 = H5Qcreate(H5Q_TYPE_LINK_NAME, H5Q_MATCH_EQUAL, DATASETNAME);
+    subquery2 = H5Qcreate(H5Q_TYPE_DATA_ELEM, H5Q_MATCH_LESS_THAN,
+        H5T_NATIVE_FLOAT, &subquery2_value);
+    query = H5Qcombine(subquery1, H5Q_COMBINE_AND, subquery2);
+
+    /* Open file */
+    file = H5Fopen(FILENAME, H5F_ACC_RDONLY, H5P_DEFAULT);
+
+    /* Apply query to file */
+    view = H5Qapply(file, query, &apply_result, H5P_DEFAULT)
+
+    /* Result should contain region reference */
+    if (result & H5Q_REF_REG) {
+        hid_t refs, ref_type, ref_space, space;
+        size_t n_refs, ref_size;
+        void *ref_buf;
+
+        /* Read region reference from view */
+        refs = H5Dopen(view, H5Q_VIEW_REF_REG_NAME, H5P_DEFAULT);
+        ref_type = H5Dget_type(refs);
+        ref_space = H5Dget_space(refs);
+        n_refs = (size_t) H5Sget_select_npoints(ref_space);
+        ref_size = H5Tget_size(ref_type);
+        ref_buf = malloc(n_refs * ref_size)
+        H5Dread(refs, ref_type, H5S_ALL, ref_space, H5P_DEFAULT, ref_buf);
+        H5Dclose(refs);
+        H5Sclose(ref_space);
+
+        /* Get selection from region reference */
+        space = H5Rget_region(file, (href_t *) ref_buf);
+
+        /* Use selection result [...] */
+
+        /* Close selection */
+        H5Sclose(space);
+
+        /* Free reference buffer */
+        free(ref_buf);
+    }
+
+    /* Close view */
+    H5Gclose(view);
+
+    /* Close queries */
+    H5Qclose(query);
+    H5Qclose(subquery1);
+    H5Qclose(subquery2);
+
+    /* Close the file */
+    H5Fclose(file);
+}
+\end{lstlisting}
+}
+
+\subsection{Data Index and Data Query}
+In this example, we show how one can make use of the query and
+indexing APIs to efficiently retrieve a dataspace selection within a dataset.
 
@@
 #define NTUPLES 256
+#define FILENAME "test.h5"
+#define DATASETNAME "Pressure"
 
@@
 {
-    float data[NTUPLES];
+    float data[NTUPLES], *result;
     hsize_t dims[1] = {NTUPLES};
-    hid_t t file_id, dataspace_id, dataset_id;
-    hid_t query_id, result_space_id;
+    hid_t t file, dataspace, dataset, dcpl, query, result_space;
     size_t result_npoints;
-    float *result;
     int i;
 
-    /* Initialize data. */
+    /* Initialize data */
     for(i = 0; i < NTUPLES; i++) data[i] = (float) i;
 
-    /* Create file. */
-    file_id = H5Fcreate(file_name, H5F_ACC_TRUNC, H5P_DEFAULT, H5P_DEFAULT);
+    /* Create file */
+    file = H5Fcreate(FILENAME, H5F_ACC_TRUNC, H5P_DEFAULT, H5P_DEFAULT);
 
-    /* Create the data space for the dataset. */
-    dataspace_id = H5Screate_simple(rank, dims, NULL);
+    /* Create the data space for the dataset */
+    dataspace = H5Screate_simple(1, dims, NULL);
 
-    /* Create dataset. */
-    dataset_id = H5Dcreate(file_id, "Pressure", H5T_NATIVE_FLOAT, dataspace_id,
-        H5P_DEFAULT, H5P_DEFAULT, H5P_DEFAULT);
+    /* Create and set property list to use FastBit index */
+    dcpl = H5Pcreate(H5P_DATASET_CREATE);
+    H5Pset_index_plugin(dcpl, H5X_PLUGIN_FASTBIT);
 
-    /* Write dataset. */
-    H5Dwrite(dataset_id, H5T_NATIVE_FLOAT, H5S_ALL, H5S_ALL, H5P_DEFAULT, data);
+    /* Create dataset */
+    dataset = H5Dcreate(file, DATASETNAME, H5T_NATIVE_FLOAT, dataspace,
+        H5P_DEFAULT, dcpl, H5P_DEFAULT);
 
-    /* Close the dataset. */
-    H5Dclose(dataset_id);
+    /* Write dataset */
+    H5Dwrite(dataset, H5T_NATIVE_FLOAT, H5S_ALL, H5S_ALL, H5P_DEFAULT, data);
 
-    /* Close dataspace. */
-    H5Sclose(dataspace_id);
+    /* Close the dataset */
+    H5Dclose(dataset);
 
-    /* Open dataset. */
-    dataset_id = H5Dopen(file_id, "Pressure", H5P_DEFAULT);
+    /* Close dataspace */
+    H5Sclose(dataspace);
 
-    /* Create index using FastBit. */
-    H5Xcreate(file_id, H5X_PLUGIN_FASTBIT, dataset_id, H5P_DEFAULT);
+    /* Close the property */
+    H5Pclose(dcpl);
 
-    /* Close the dataset. */
-    H5Dclose(dataset_id);
+    /* Close the file */
+    H5Fclose(file);
 
     /* Create a simple query */
-    query_id = H5Qcreate(H5Q_TYPE_DATA_ELEM, H5Q_MATCH_EQUAL, H5T_NATIVE_FLOAT,
+    query = H5Qcreate(H5Q_TYPE_DATA_ELEM, H5Q_MATCH_EQUAL, H5T_NATIVE_FLOAT,
         &query_value);
 
-    /* Open dataset. */
-    dataset_id = H5Dopen(file_id, "Pressure", H5P_DEFAULT);
+    /* Open file */
+    file = H5Fopen(FILENAME, H5F_ACC_RDONLY, H5P_DEFAULT);
 
-    /* Use query to select elements in the dataset. */
-    result_space_id = H5Dquery(dataset_id, H5S_ALL, query_id, H5P_DEFAULT);
+    /* Open dataset */
+    dataset = H5Dopen(file, DATASETNAME, H5P_DEFAULT);
 
-    /* Allocate space to read data. */ 
-    result_npoints = (size_t) H5Sget_select_npoints(result_space_id);
+    /* NB. Alternatively the index can be generated on the existing dataset.
+     * This, however, requires the file to be open in H5F_ACC_RDWR so that
+     * the index can be stored within the file and attached to the dataset.
+     * H5Xcreate(dataset, H5X_PLUGIN_FASTBIT, H5P_DEFAULT); */
+
+    /* Use query to select elements in the dataset */
+    result_space = H5Dquery(dataset, H5S_ALL, query, H5P_DEFAULT);
+
+    /* Allocate space to read data */ 
+    result_npoints = (size_t) H5Sget_select_npoints(result_space);
     result = malloc(result_npoints * sizeof(float));
 
-    /* Read data using result_space_id. */
-    H5Dread(dataset_id, H5T_NATIVE_FLOAT, H5S_ALL, result_space_id,
+    /* Read data using result_space_id */
+    H5Dread(dataset, H5T_NATIVE_FLOAT, H5S_ALL, result_space,
         H5P_DEFAULT, result);
 
-    /* Use result. */
-    [...]
+    /* Use result [...] */
 
-    /* Free result. */
+    /* Free result */
     free(result);
 
-    /* Close the dataset. */
-    H5Dclose(dataset_id);
+    /* Close the dataset */
+    H5Dclose(dataset);
 
-    /* Close dataspace. */
-    H5Sclose(result_space_id);
+    /* Close dataspace */
+    H5Sclose(result_space);
 
-    /* Close query. */
-    H5Qclose(query_id);
+    /* Close query */
+    H5Qclose(query);
 
-    /* Close the file. */
-    H5Fclose(file_id);
+    /* Close the file */
+    H5Fclose(file);
+}
+\end{lstlisting}
+}
+
+\subsection{Metadata Index}
+In this example, we show how one can make use of the query and
+indexing APIs to efficiently execute a metadata query on a file.
+
+{\lstsetc
+\begin{lstlisting}
+#define FILENAME "test.h5"
+#define DATASETNAME "Pressure"
+
+int
+main(int argc, char *argv[])
+{
+    hid_t t file, fcpl, query, view;
+    unsigned apply_result = 0;
+
+    /* Create and set property list to use B-Tree index */
+    fcpl = H5Pcreate(H5P_FILE_CREATE);
+    H5Pset_index_plugin(fcpl, H5X_PLUGIN_BTREE);
+
+    /* Create file */
+    file = H5Fcreate(FILENAME, H5F_ACC_TRUNC, fcpl, H5P_DEFAULT);
+
+    /* Create groups / datasets / attributes / etc */
+
+    /* Close the property */
+    H5Pclose(fcpl);
+
+    /* Close the file */
+    H5Fclose(file);
+
+    /* Create a simple query */
+    query = H5Qcreate(H5Q_TYPE_LINK_NAME, H5Q_MATCH_EQUAL, DATASETNAME);
+
+    /* Open file */
+    file = H5Fopen(FILENAME, H5F_ACC_RDONLY, H5P_DEFAULT);
+
+    /* NB. Alternatively the index can be generated on the existing file.
+     * This, however, requires the file to be open in H5F_ACC_RDWR so that
+     * the index can be stored within the file and attached to it.
+     * H5Xcreate(file, H5X_PLUGIN_BTREE, H5P_DEFAULT); */
+
+    /* Apply query to file */
+    view = H5Qapply(file, query, &apply_result, H5P_DEFAULT)
+
+    /* Use view result [...] */
+
+    /* Close view */
+    H5Gclose(view);
+
+    /* Close query */
+    H5Qclose(query);
+
+    /* Close the file */
+    H5Fclose(file);
 }

### 2016-02-08 RFCs/HDF5_Library/AnalysisExt/analysis_ext.tex
More update to analysis document
Former-commit-id: bc183e6cb18f23e94a8800a6dbc554da7d4c95b2
Update metadata indexing design doc
Former-commit-id: b578bfebadc799e9faf5e2b0b5429a7c93f079de

@@
     H5Q_combine_op_t, H5Q_type_t, H5Q_match_op_t,
-    H5Fcreate, H5Fclose,
-    H5Dcreate, H5Dopen, H5Dclose, H5Dwrite, H5Dread, H5Dquery,
+    H5Fcreate, H5Fclose, H5Fopen,
+    H5Gcreate, H5Gopen, H5Gclose,
+    H5Dcreate, H5Dopen, H5Dclose, H5Dwrite, H5Dread, H5Dquery, H5Dget_type,
+    H5Dget_space,
+    H5Pcreate, H5Pclose, H5Pset_index_plugin,
     H5Qcreate, H5Qclose, H5Qcombine, H5Qget_type, H5Qget_match_op,
@@
     H5Qapply, H5Qapply_multi, H5Qapply_str, H5Qapply_dir,
+    H5Rget_region,
     H5Screate_simple, H5Sclose, H5Sget_select_npoints,
+    H5Tget_size,
     H5Xregister, H5Xunregister, H5Xcreate, H5Xremove, H5Xget_count, H5Xget_size,
@@
 \author{Quincey Koziol}
-\date{Feb 3, 2016}
-\rfcversion{2014-07-17.v9}
+\date{Feb 8, 2016}
+\rfcversion{2014-07-17.v10}
 \revision{Jul. 17, 2014}{Version 1 circulated for comment within The HDF Group.}
@@
 \revision{Feb. 3, 2016}{Version 9 more text corrections.}
+\revision{Feb. 8, 2016}{Version 10 add metadata indexing and usage examples.}
 

### 2018-01-09 RFCs/HDF5/VOL/RFC/RFC_VOL.tex
updates
Former-commit-id: 075132ce087eee5f33c09f6c78cb3bd1c8f6d8c8
minor edits, fixed LaTeX
Former-commit-id: f58e77a5ab8675ee8b4755efa0593ba44b783e8b

@@
 % Title, author, etc
-\title{RFC: Virtual Object Layer}
+\title{Virtual Object Layer}
 \author{Mohamad Chaarawi}
@@
 \section{Introduction}
-The HDF5 data model is composed of two basic objects, groups and datasets.
+The HDF5 data model is composed of two primary objects, groups and datasets.
 The data model in itself is very powerful and widely used by many applications, including High Performance Computing (HPC) applications.
@@
 
-The main challenge currently in HDF5 is not in the data model itself, but in the native HDF5 single file format that has performance issues that vary widely over different platforms and has some limitations where all objects actually have to be accessible locally.
-Furthermore, in parallel applications, file access by several processes has to be coordinated in order to maintain strict consistency semantics to avoid file corruption.
-In addition, the emergence of new tiered storage architectures and object storage file systems renders the current HDF5 library in need of major implementation changes to leverage such architectures.
+The primary challenge currently in HDF5 is not in the data model itself, but in the native HDF5 single file format that has performance issues that vary widely over different platforms and has some limitations where all objects have to be accessible locally.
+Furthermore, in parallel applications, file access by several processes has to be coordinated to maintain strict consistency semantics to avoid file corruption.
+Also, the emergence of new tiered storage architectures and object storage file systems renders the current HDF5 library in need of significant implementation changes to leverage such architectures.
 To address those concerns, we have been working on a new abstraction layer inside the HDF5 library called the Virtual object layer (VOL).
 The VOL intercepts all HDF5 API calls that could potentially access objects in the file and forwards those calls to a plugin ``object driver''.
-The plugins could actually store the objects in variety of ways.
+The plugins could store the objects in a variety of ways.
 A plugin could, for example, have objects be distributed remotely over different platforms, provide a raw mapping of the model to the file system, or even store the data in other file formats (like native netCDF or HDF4 format).
 The user still gets the same data model where access is done to a single HDF5 ``container''; however the plugin object driver translates from what the user sees to how the data is actually stored.
-Having this abstraction layer maintains the object model of HDF5 and would allow much better usage of new object storage file systems that are targeted for Exascale systems.
+Having this abstraction layer maintains the object model of HDF5 and would allow for much better use of new object storage file systems that are targeted for Exascale systems.
 
@@
 \item Implementing a VOL plugin should not require any change to the HDF5 library unless the plugin is an internal plugin that modifies the current native file format. 
-\item Current applications, third party libraries, or tools that use the HDF5 library with the native file format should not require any change to work properly with the VOL addition.
+\item Current applications, third-party libraries, or tools that use the HDF5 library with the native file format should not require any change to work properly with the VOL addition.
 \item Performance of applications without the VOL changes should not change.
 The VOL framework will introduce additional function calls to every HDF5 API call that maps to through the VOL interface, but that should be detrimental to performance.
-\item Applications, third party libraries, and tools that only use the HDF5 public routines and objects should work as expected with any correct and fully implemented plugin.
+\item Applications, third-party libraries, and tools that only use the HDF5 public routines and objects should work as expected with any correct and fully implemented plugin.
 Performance may and probably will vary across the different plugins.
-\item The VOL framework should allow plugins to be stackable on top of each other, and should allow implementation of plugins that use 2 or more different plugins.
-It is the plugin developer's  responsibility though to correctly implement such plugins.
+\item The VOL framework should allow plugins to be stackable on top of each other and should allow implementation of plugins that use 2 or more different plugins.
+It is the plugin developer's  responsibility though to implement such plugins correctly.
 \item Plugin developers should not be required to implement the full VOL functionality for a specific plugin if the intended use of that plugin is a subset of the HDF5 data model and features.
-For example, if a user just intends to access HDF5 datasets, it should be sufficient to develop a plugin that implement container and dataset operations in that container.
+For example, if a user just intends to access HDF5 datasets, it should be sufficient to develop a plugin that implements container and dataset operations in that container.
 Other advanced functionality of the HDF5 data model should not be required if they will not be used.
@@
 \end{enumerate}
-
 \section{Design/Architecture}
@@
 The H5Dcreate call will inform the user that a dataset with the returned ID has been created in the HDF5 container being accessed with the chosen VOL plugin.
-Depending on the plugin selected, the H5Dcreate function might have created a dataset object in an HDF5 file, a netCDF file, a file on a remote machine, or any way a plugin is designed to create a dataset.
+Depending on the plugin selected, the H5Dcreate function might have created a dataset object in an HDF5 file, a netCDF file, a file on a remote machine, or anyway a plugin is designed to create a dataset.
 
@@
 }
-The {\tt cls} parameter is a structure containing function pointers to the routines that implement all the callback routines the VOL class specifies.
+The \texttt{cls} parameter is a structure containing function pointers to the routines that implement all the callback routines the VOL class specifies.
 For more information on creating and using VOL plugins, please refer to the VOL user guide.
@@
 \subsubsection{Different File Format Plugins}
-We mentioned earlier that a developer could design a plugin such that the file that stores data on disk could be of different format than the H5 format.
+We mentioned earlier that a developer could design a plugin such that the file that stores data on disk could be of a different format than the H5 format.
 This is very important to users that would like to use the HDF5 API and data model, but also desire the portability to use their files across different libraries or would like to access data from pre-existing files that are not in the H5 format.
@@
 The plugin, which understands the HDF5 data model and how the data is stored, will do the necessary ``translation'' needed for this kind of model.
-The following figure explains more on how this is achieved:
+The following figure explains more about how this is achieved:
 
@@
 Large, remote datasets are very expensive to migrate to the local virtualization system.
-It would be faster to just enable in situ virtualization to remotely access the virtualization data using the HDF5 API.
+It would be faster to just enable in-situ virtualization to remotely access the virtualization data using the HDF5 API.
 This is however not possible at the moment with the native implementation for HDF5 as the file is required to be present locally.
@@
 
-It would be also possible to stack VOL plugins on top of each other.
+It would also be possible to stack VOL plugins on top of each other.
 This notion is similar to the idea of the split VFD, where underneath the split VFD itself, two file drivers would be used, one for the file storing the metadata and another for raw data.
@@
 For example, stacking the native HDF5 plugin on top of a non-HDF5 backend plugin does not make sense and is erroneous.
-Figure~\ref{fig:stack} showes a stacking of the remote plugin, where data is distributed remotely, on top of the native h5 plugin, where servers that store the data at remote locations use the h5 file format.
+Figure~\ref{fig:stack} shows a stacking of the remote plugin, where data is distributed remotely, on top of the native h5 plugin, where servers that store the data at remote locations use the h5 file format.
 
@@
 Another useful design option is to allow a mirroring plugin, where the HDF5 API calls are forwarded through a mirror plugin to two or more VOL plugins.
-This is an extention to the stacking feature.
+This is an extension to the stacking feature.
 Figure~\ref{fig:mirror} shows an example of a VOL mirror that maps HDF5 API calls to an h5 backend plugin and an XML backend plugin:
@@
 
-Another possible VOL plugin could be a statistics plugin that just gathers information on HDF5 API calls and records statistics associated with the number of calls to a specific API functions and corresponding parameters.
+Another possible VOL plugin could be a statistics plugin that just gathers information on HDF5 API calls and records statistics associated with the number of calls to specific API functions and corresponding parameters.
 This plugin would be very useful for profiling purposes.
@@
 The HDF5 API is too large however to have a 1 to 1 mapping from API routines to VOL callbacks, so we introduce the notion of a generic function call that developers could use to implement certain API routines that do not map to one of the VOL callbacks.
-This is similar to the UNIX {\tt ioctl()} routine.
+This is similar to the UNIX \texttt{ioctl()} routine.
 
@@
 In order to be able to support those API routines and not to double the number of VOL callback routines, we made all VOL callbacks nonblocking compatible, by adding an HDF5 request parameter to all VOL callbacks.
-If the high level operation issued by the user is nonblocking, then the request would just be forwarded to the VOL plugin and the plugin itself would be responsible to support the nonblocking behavior.
+If the high-level operation issued by the user is nonblocking, then the request would just be forwarded to the VOL plugin and the plugin itself would be responsible to support the nonblocking behavior.
 If the high level operation is a blocking operation, then a non-active request is forwarded to the plugin which detects that the request is inactive and implements the operation in a blocking behavior.
 
-One could argue that the interface can be simplified by having, for example, a common open routine for all objects (like the {\tt H5Oopen}) routine.
+One could argue that the interface can be simplified by having, for example, a common open routine for all objects (like the \texttt{H5Oopen}) routine.
 We found however that having  a common interface would be detrimental to performance in certain plugin implementations, since it would require querying the VOL plugin twice, once for looking up the object location and once for opening the object.
 Having an optional callback for every object and a generic one would solve this issue.
-The VOL layer would check if the specific object callback is implemented in the VOL plugin, and if it is not, it would fall back to the generic object callback routine.
+The VOL layer would check if the specific object callback is implemented in the VOL plugin, and if it is not, it will fall back to the generic object callback routine.
 This way we do not sacrifice performance for generality.
 
-Another design issue comes to mind when looking at the large set of functions, and that is whether to lump all the functions together into one data structure as the VOL class, or to have a more object oriented approach, where we can either have a general class that contains all common functions, and then children of that class that contain functions specific to certain HDF5 objects, or for each object have a set of callbacks that are specific to that object.
+Another design issue comes to mind when looking at the large set of functions, and that is whether to lump all the functions together into one data structure as the VOL class, or to have a more object-oriented approach, where we can either have a general class that contains all common functions, and then children of that class that contain functions specific to certain HDF5 objects, or for each object have a set of callbacks that are specific to that object.
 The current design chosen seems to be a good middle ground between generality and readability/maintainability.
@@
 They are required to ship with the HDF5 library to be used by applications.
-External plugins on the other hand are ones that are implemented outside of the HDF5 library and applications link with to use.
+External plugins, on the other hand, are ones that are implemented outside of the HDF5 library and applications link with to use.
 Those plugins do not require using private HDF5 functionality.
-They can however use public HDF5 features.
+They can, however, use public HDF5 features.
 
-External plugins can be provided by the applications themselves or as a third party library, i.e.
-not provided by the HDF5 library nor the application.
+External plugins can be provided by the applications themselves or as a third party library, i.e., not provided by the HDF5 library nor the application.
 Third party plugins should be installed on the system to be used as a shared library or a DLL.
@@
 
-\subsection{{\tt H5Ocopy and H5Ocompare}}
+\subsection{\texttt {H5Ocopy and H5Ocompare}}
 The HDF5 API has two routines that will require extra attention to be compatible with the VOL layer, and those are the object copy and compare routines:
@@
 
-If the two objects are in containers of the same type, i.e.
-created using the same VOL plugin, then the VOL layer would be able to detect that and forward those calls to the corresponding implementation using a designated VOL callback.
+If the two objects are in containers of the same type, i.e., created using the same VOL plugin, then the VOL layer would be able to detect that and forward those calls to the corresponding implementation using a designated VOL callback.
 This would allow different sorts of optimizations that a VOL plugin could choose to implement in order to copy or compare two objects.

### 2018-01-10 RFCs/HDF5/VOL/user_guide/external.tex
updated LateX and general editing of document
Former-commit-id: 2e4326ee524db559b5b9ab32ee07a03caa786f9a

@@
 shipped with the HDF5 library, but can just link to it from userspace
-just like an HDF5 application. If an external VOL plugin is installed on system as a shared library or a DLL, the library can search for it and load it dynamically to be used by an application.
+just like an HDF5 application. If an external VOL plugin is installed on the system as a shared library or a DLL, the library can search for it and load it dynamically to be used by an application.
 
@@
 Developing an external plugin is similar to developing an internal plugin.
-Refer to Section~ref{sec:vol} for details on plugin creation.
+Refer to Section~\ref{sec:vol} for details on plugin creation.
 The important thing to keep in mind is that external plugins cannot use internal HDF5 features.
@@
 
-In order for the HDF5 library to be able to load an external plugin dynamically, the plugin developer has to define two public routines with the following name and signature:
+For the HDF5 library to be able to load an external plugin dynamically, the plugin developer has to define two public routines with the following name and signature:
 \begin{lstlisting}
@@
 Unlike internal plugins, external plugins cannot create an API routine for applications to use to set the VOL plugin in the file access property list.
-External plugin developers can however provide a wrapper routine that registers the plugin with {\tt H5VLregister()} instead of having the application call that directly with the pointer to the plugin class structure.
-Both ways are possible if the external plugin used is in the application's user space.
-External plugins provided by third pary vendors that are not in the application's user space but are installed on the system with a shared library or DLL can be registered by the application using {\tt H5VLregister\_name()} provided that the application knows the plugin's name in advance.
+External plugin developers can, however, provide a wrapper routine that registers the plugin with {\tt H5VLregister()} instead of having the application call that directly with the pointer to the plugin class structure.
+Both ways are possible if the external plugin used is in the application's userspace.
+External plugins provided by third party vendors that are not in the application's userspace but are installed on the system with a shared library or DLL can be registered by the application using {\tt H5VLregister\_name()} provided that the application knows the plugin's name in advance.
 
@@
 This identifier is used to initialize the plugin if it requires an initialization phase.
-A third party library could use that ID to create a plugin that stacks or mirrors on top of an internal plugin using that identifier (refer to section~\ref{sec:stack} for more details on stacking and mirroring).
+A third party library could use that ID to create a plugin that stacks or mirrors on top of an internal plugin using that identifier (refer to Section~\ref{sec:stack} for more details on stacking and mirroring).
 
@@
 
-Finally the application is required to un-register the plugin from the library when access to the container(s) is terminated using {\tt H5VLunregister}.
+Finally, the application is required to un-register the plugin from the library when access to the container(s) is terminated using {\tt H5VLunregister}.
 

### 2018-01-10 RFCs/HDF5/VOL/user_guide/new_api.tex
updated LateX and general editing of document
Former-commit-id: 2e4326ee524db559b5b9ab32ee07a03caa786f9a

@@
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Registers a user defined VOL plugin with the HDF5 library and returns an identifier for that plugin to be used if successful, otherwise returns a negative value.
-This function is used when the application has direct access to the plugin it wants to use and is able to obtain a pointer for the plugin structure to pass to the HDF5 library.
-The plugin must be unregistered before the application exists with {\tt H5VLunregister()}.
 
@@
 \end{tabular}
+\end{mdframed}
 
+Registers a user defined VOL plugin with the HDF5 library and returns an identifier for that plugin to be used if successful, otherwise returns a negative value.
+This function is used when the application has direct access to the plugin it wants to use and is able to obtain a pointer for the plugin structure to pass to the HDF5 library.
+The plugin must be unregistered before the application exists with {\texttt H5VLunregister()}.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Registers a VOL plugin with the HDF5 library given the name of the plugin and returns an identifier for that plugin to be used if successful, otherwise returns a negative value.
-If the plugin is already registered the library will create an identifier for it and returns it to the user; otherwise the library will look for available third party plugins and dynamically load them and registers them for use, then returns an identifier for the plugin.
-Third party plugins must be installed on the system as a shared library or DLL.
-The plugin must be unregistered before the application exists with {\tt H5VLunregister()}.
-
 \textbf{Arguments:}\\
@@
 \end{tabular}
+\end{mdframed}
+Registers a VOL plugin with the HDF5 library given the name of the plugin and returns an identifier for that plugin to be used if successful, otherwise returns a negative value.
+If the plugin is already registered the library will create an identifier for it and returns it to the user; otherwise the library will look for available third party plugins and dynamically load them and registers them for use, then returns an identifier for the plugin.
+Third party plugins must be installed on the system as a shared library or DLL.
+The plugin must be unregistered before the application exists with {\tt H5VLunregister()}.\bigskip
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Unregisters a plugin from the library and return a positive value on success otherwise return a negative value.
-
 \textbf{Arguments:}\\
@@
 \end{tabular}
+\end{mdframed}
+Unregisters a plugin from the library and return a positive value on success otherwise return a negative value.\bigskip
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Checks if a VOL plugin is registered with the library given the plugin name and returns TRUE/FALSE on success, otherwise it returns a negative value.
-
 \textbf{Arguments:}\\
@@
 \end{tabular}
+\end{mdframed}
+Checks if a VOL plugin is registered with the library given the plugin name and returns TRUE/FALSE on success, otherwise it returns a negative value.\bigskip
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Retrieves the name of a VOL plugin given and object identifier that was created/opened with it. On success, the name length is returned.
 
@@
 \end{tabular}
+\end{mdframed}
+Retrieves the name of a VOL plugin given and object identifier that was created/opened with it. On success, the name length is returned.\bigskip
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Given a plugin name that is registered with the library, this function returns an identifier for the plugin.
-If the plugin is not registered with the library, a negative value is returned.
-The identifier must be released with a call to {\tt H5VLclose()}.
-
 \textbf{Arguments:}\\
@@
 \end{tabular}
+\end{mdframed}
+Given a plugin name that is registered with the library, this function returns an identifier for the plugin.
+If the plugin is not registered with the library, a negative value is returned.
+The identifier must be released with a call to {\tt H5VLclose()}.\bigskip
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Shuts down access to the plugin that the identifier points to and release resources associated with it.
 
@@
 \end{tabular}
+\end{mdframed}
+Shuts down access to the plugin that the identifier points to and release resources associated with it.\bigskip
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Creates an HDF5 identifier for an object given its type and an identifier of the plugin that was used in creating it.
-This function is typically used by external plugins wanting to wrap an {\tt hid\_t} around a plugin specific object to return to a user callback for functions like {\tt H5Literate, H5Lvisit, H5Ovisit, H5Aiterate} etc...
-A Negative value is returned on failure.
 
@@
 \end{tabular}
+\end{mdframed}
+Creates an HDF5 identifier for an object given its type and an identifier of the plugin that was used in creating it.
+This function is typically used by external plugins wanting to wrap an {\tt hid\_t} around a plugin specific object to return to a user callback for functions like {\tt H5Literate, H5Lvisit, H5Ovisit, H5Aiterate} etc...
+A Negative value is returned on failure.\bigskip
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Retrieves a pointer to the VOL object from an HDF5 file or object identifier.
 
@@
 \end{tabular}
+\end{mdframed}
+Retrieves a pointer to the VOL object from an HDF5 file or object identifier.\bigskip
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-Initializes access to the VOL plugin represented by {\tt plugin\_id} with initialization parameters set as properties in the the property list {\tt vipl\_id}.
-Some plugins may not require initialization.
-For more information about plugin initialization and what properties are required to be set in the property list refer to the actual plugin documentation.
 
@@
 \end{tabular}
+\end{mdframed}
+Initializes access to the VOL plugin represented by {\tt plugin\_id} with initialization parameters set as properties in the the property list {\tt vipl\_id}.
+Some plugins may not require initialization.
+For more information about plugin initialization and what properties are required to be set in the property list refer to the actual plugin documentation.\bigskip
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
@@
 \end{lstlisting}
-
-Terminates access to the VOL plugin represented by {\tt plugin\_id} with termination parameters set as properties in the the property list {\tt vtpl\_id}.
-Some plugins may not require termination.
-For more information about plugin termination and what properties are required to be set in the property list refer to the actual plugin documentation.
 
@@
 \end{tabular}
+\end{mdframed}
+Terminates access to the VOL plugin represented by {\tt plugin\_id} with termination parameters set as properties in the the property list {\tt vtpl\_id}.
+Some plugins may not require termination.
+For more information about plugin termination and what properties are required to be set in the property list refer to the actual plugin documentation.
 

### 2018-01-10 RFCs/HDF5/VOL/user_guide/plugin.tex
updated LateX and general editing of document
Former-commit-id: 2e4326ee524db559b5b9ab32ee07a03caa786f9a

@@
 \label{sec:vol}
-Each VOL plugin should be of type {\tt H5VL\_class\_t} that is defined
-as:
-
-\begin{lstlisting}
+Each VOL plugin should be of type \texttt{H5VL\_class\_t}, Listing \ref{lst:VOLclass}.
+
+\hfill
+
+\begin{lstlisting}[caption={VOL plugin class, H5VLpublic.h},captionpos=b, label={lst:VOLclass}]
 /* Class information for each VOL driver */
 typedef struct H5VL_class_t {
+    unsigned int version;
     H5VL_class_value_t value;
@@
 
-The {\tt value} field is a unique integer enum identifier that should be
+The \texttt{version} field is the HDF5 VOL driver version.
+
+The \texttt{value} field is a unique integer enum identifier that should be
 greater than 128 for external plugins and smaller than 128 for
@@
 
-The {\tt name} field is a string that uniquely identifies the VOL plugin
+The \texttt{name} field is a string that uniquely identifies the VOL plugin
 name. Setting it in the VOL structure is required. No two plugins with the same name can be registered with the library at the same time.
 
-The {\tt initialize} field is a function pointer to a routine that a plugin implements to set up or intialize access to the plugin.
-Implementing this function by the plugin is not required, since some plugins do not require any set up to start accessing the plugin.
+The \texttt{initialize} field is a function pointer to a routine that a plugin implements to set up or initialize access to the plugin.
+Implementing this function by the plugin is not required since some plugins do not require any set up to start accessing the plugin.
 In that case, the value of the function pointer should be set to NULL.
 Plugin specific variables that are required to be passed from users should be passed through the VOL initialize property list.
-Generic properties can be added to this property class for user-defined plugins that can not modify the HDF5 library to add internal properties.
+Generic properties can be added to this property class for user-defined plugins that cannot modify the HDF5 library to add internal properties.
 For more information consult the property list reference manual pages.
 
-The {\tt terminate} field is a function pointer to a routine that a plugin implements to terminate or finalize access to the plugin.
-Implementing this function by the plugin is not required, since some plugins do not require any termination phase to the plugin.
+The \texttt{terminate} field is a function pointer to a routine that a plugin implements to terminate or finalize access to the plugin.
+Implementing this function by the plugin is not required since some plugins do not require any termination phase to the plugin.
 In that case, the value of the function pointer should be set to NULL.
 Plugin specific variables that are required to be passed from users should be passed through the VOL terminate property list.
-Generic properties can be added to this property class for user-defined plugins that can not modify the HDF5 library to add internal properties.
+Generic properties can be added to this property class for user-defined plugins that cannot modify the HDF5 library to add internal properties.
 For more information consult the property list reference manual pages.
 
-The {\tt fapl\_size} field indicates the size required to store the
+The \texttt{fapl\_size} field indicates the size required to store the
 info data that the plugin needs. That info data is passed when the
@@
 
-The {\tt fapl\_copy} field is a function pointer that is called when
+The \texttt{fapl\_copy} field is a function pointer that is called when
 the plugin is selected with the fapl function. It allows the plugin to
-make a copy if the info data since the user might free it when closing
+make a copy of the info data since the user might free it when closing
 the fapl. It is required if there is info data needed by the plugin.
 
-The {\tt fapl\_free} field is a function pointer that is called to
+The \texttt{fapl\_free} field is a function pointer that is called to
 free the info data when the fapl close routine is called. It is
@@
 
-The rest of the fields in the {\tt H5VL\_class\_t} struct are "subclasses'' that define all the VOL function callbacks that
+The rest of the fields in the \texttt{H5VL\_class\_t} struct are "subclasses'' that define all the VOL function callbacks that
 are mapped to from the HDF5 API layer.
@@
 Asynchronous operations, for example, are a service that most plugins can implement, so we add a class for it in the VOL structure.
-If a service becomes generic enough and common between many plugins, a class for it should be added in the VOL structure.
+If a service becomes generic enough and common among many plugins, a class for it should be added to the VOL structure.
 However, many plugins can/will provide services that are not shared by other plugins.
@@
 handle all the HDF5 API operations that would access the
-file. Furthermore it has to capture future additions to the HDF5
+file. Furthermore, it has to capture future additions to the HDF5
 library with little to no changes to the callback interface. Changing
@@
   VOL callback function.
-\item A pointer to a request ({\tt void **req}) to handle asynchronous
+\item A pointer to a request (\texttt{void **req}) to handle asynchronous
   operations if the HDF5 library adds support for them in future
@@
   plugin to a request object it creates to manage progress on that
-  asynchronous operation. If the {\tt req} is {\tt NULL}, that means
+  asynchronous operation. If the \texttt{req} is \texttt{NULL}, that means
   that the API operation is blocking and so the plugin would not
@@
 In order to keep the number of the VOL object classes and callbacks
-concise and readable, it was decided to not have a one-to-one mapping
+concise and readable, it was decided not to have a one-to-one mapping
 between API operation and callbacks. Furthermore, to keep the
@@
 The HDF5 library provides several routines to access an object in the
-container. For example to open an attribute on a group object, the
-user could use {\tt H5Aopen()} and pass the group identifier directly
+container. For example, to open an attribute on a group object, the
+user could use \texttt{H5Aopen()} and pass the group identifier directly
 where the attribute needs to be opened. Alternatively, the user could
-use {\tt H5Aopen\_by\_name()} or {\tt H5Aopen\_by\_idx()} to open the
+use \texttt{H5Aopen\_by\_name()} or \texttt{H5Aopen\_by\_idx()} to open the
 attribute, which provides a more flexible way of locating the
@@
 have multiple types of accesses.  The location parameter is a
-structure defined as follows:
-
-\begin{lstlisting}
+structure defined in Listing \ref{lst:ObjLocclass}.
+
+\newpage
+
+\begin{lstlisting}[caption={Structure to hold parameters for object locations, H5VLpublic.h}, captionpos=b, label={lst:ObjLocclass}]
 /* 
@@
     const char *name; /* The path relative to the starting location */
-    hid_t plist_id; /* The link access property list */
+    hid_t lapl_id; /* The link access property list */
 };
@@
     hsize_t n; /* position in index */
-    hid_t plist_id; /* The link access property list */
+    hid_t lapl_id; /* The link access property list */
 };
@@
     const void *_ref;
-    hid_t plist_id;
+    hid_t lapl_id;
 };
 \end{lstlisting}
+
+\newpage
 
@@
 \begin{itemize} 
-\item the {\tt Get} operations that retrieve something from an object; for example a property list or a datatype of a dataset, etc... 
-\item API routines specific to each class of callbacks(attributes, files, etc...). Having a callback for each one would clutter the VOL callback structure and reduce user friendliness. 
+\item the \texttt{Get} operations that retrieve something from an object; for example a property list or a datatype of a dataset, etc.
+\item API routines are specific to each class of callbacks (attributes, files, etc...). Having a callback for each one would clutter the VOL callback structure and reduce user-friendliness. 
 \item API routines that make sense to only implement in the native HDF5 file format and would not be possible to implement in other plugins.
@@
 
-To handle that large set of API routines, each class in the Data Model category has three generic callbacks, {\tt get}, {\tt specific}, and {\tt optional} to handle the three set of API operations outline above respectively.
-The callbacks will have a {\tt va\_list} argument to handle the different set of parameters that could be passed in.
-The {\tt get} and {\tt specific} callbacks also have an {\tt op\_type} that contain an {\tt enum} of the type of operation that is requested to be performed.
-Using that type, the {\tt va\_list} argument can be parsed.
-The {\tt optional} callback is a free for all callback where anything from the API layer is passed in directly.
+To handle that large set of API routines, each class in the Data Model category has three generic callbacks, \texttt{get}, \texttt{specific}, and \texttt{optional} to handle the three set of API operations outline above respectively.
+The callbacks will have a \texttt{va\_list} argument to handle the different set of parameters that could be passed in.
+The \texttt{get} and \texttt{specific} callbacks also have an \texttt{op\_type} that contain an \texttt{enum} of the type of operation that is requested to be performed.
+Using that type, the \texttt{va\_list} argument can be parsed.
+The \texttt{optional} callback is a free for all callback where anything from the API layer is passed in directly.
 This callback is used to support plugin specific operations in the API that other plugins should or would not know about.
@@
 map to one of the file callback routines in this class that the plugin
-needs to implement:
-
-\begin{lstlisting}
+needs to implement, Listing \ref{lst:Fileclass}.
+
+\begin{lstlisting}[caption={File class for file API routines, H5VLpublic.h}, captionpos=b, label={lst:Fileclass}]
 typedef struct H5VL_file_class_t {
@@
 
-The {\tt create} callback in the file class should create a container
+The \texttt{create} callback in the file class should create a container
 and returns a pointer to the file structure created by the plugin containing information to
-access the container in future calls.
-
+access the container in future calls.\medskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt name} & (IN): The name of the container to be created.\\
-  {\tt flags} & (IN): The creation flags of the container.\\
-  {\tt fcpl\_id} & (IN): The file creation property list.\\
-  {\tt fapl\_id} & (IN): The file access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt open} callback in the file class should open a container and
+  \texttt{name} & (IN): The name of the container to be created.\\
+  \texttt{flags} & (IN): The creation flags of the container.\\
+  \texttt{fcpl\_id} & (IN): The file creation property list.\\
+  \texttt{fapl\_id} & (IN): The file access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+\hspace*{\fill}
+The \texttt{open} callback in the file class should open a container and
 returns a pointer to the file structure created by the plugin containing information to
-access the container in future calls.
-
+access the container in future calls.\bigskip
+
+\begin{mdframed}[style=bgbox] 
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt name} & (IN): The name of the container to open.\\
-  {\tt flags} & (IN): The open flags of the container.\\
-  {\tt fapl\_id} & (IN): The file access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt get} callback in the file class should retrieve
-information about the container as specified in the {\tt get\_type}
-parameter. It returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{name} & (IN): The name of the container to open.\\
+  \texttt{flags} & (IN): The open flags of the container.\\
+  \texttt{fapl\_id} & (IN): The file access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{get} callback in the file class should retrieve
+information about the container as specified in the \texttt{get\_type}
+parameter. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox] 
 \textbf{Signature:}
@@
 
-The {\tt get\_type} argument is an {\tt enum}:
+The \texttt{get\_type} argument is an \texttt{enum}:
 \begin{lstlisting}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The container or object where information needs to be
+  \texttt{obj} & (IN): The container or object where information needs to be
   retrieved from.\\
-  {\tt get\_type} & (IN): The type of the information to retrieve.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
@@
 
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt get\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_FILE\_GET\_FCPL}, to retrieve the file creation
+\item \texttt{H5VL\_FILE\_GET\_FCPL}, to retrieve the file creation
   property list:
   \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     file creation property list.
@@
 
-\item {\tt H5VL\_FILE\_GET\_FAPL}, to retrieve the file access
+\item \texttt{H5VL\_FILE\_GET\_FAPL}, to retrieve the file access
   property list:
   \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     file access property list.
@@
 
-\item {\tt H5VL\_FILE\_GET\_OBJ\_COUNT:}, to retrieve the object count
+\item \texttt{H5VL\_FILE\_GET\_OBJ\_COUNT:}, to retrieve the object count
   in the container:
   \begin{enumerate}
-  \item {\tt unsigned types} (IN): type of objects to look for.
-  \item {\tt ssize\_t *ret} (OUT): buffer for the object count.
-  \end{enumerate}
-
-\item {\tt H5VL\_FILE\_GET\_OBJ\_IDS:}, to retrieve object identifiers
+  \item \texttt{unsigned types} (IN): type of objects to look for.
+  \item \texttt{ssize\_t *ret} (OUT): buffer for the object count.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_GET\_OBJ\_IDS:}, to retrieve object identifiers
   in the container:
   \begin{enumerate}
-  \item {\tt unsigned types} (IN): type of objects to look for.
-  \item {\tt size\_t max\_objs} (IN): maximum number of objects to
+  \item \texttt{unsigned types} (IN): type of objects to look for.
+  \item \texttt{size\_t max\_objs} (IN): maximum number of objects to
     open.
-  \item {\tt hid\_t *oid\_list} (OUT): buffer for the object identifiers.
-  \item {\tt ssize\_t *ret} (OUT): buffer for the object count.
-  \end{enumerate}
-
-\item {\tt H5VL\_FILE\_GET\_INTENT}, get access intent of the
+  \item \texttt{hid\_t *oid\_list} (OUT): buffer for the object identifiers.
+  \item \texttt{ssize\_t *ret} (OUT): buffer for the object count.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_GET\_INTENT}, get access intent of the
   container:
   \begin{enumerate}
-  \item {\tt unsigned *ret} (OUT): buffer for the intent value.
-  \end{enumerate}
-
-\item {\tt H5VL\_FILE\_GET\_NAME}, get container name an object
+  \item \texttt{unsigned *ret} (OUT): buffer for the intent value.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_GET\_NAME}, get container name an object
   belongs to:
   \begin{enumerate}
-  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
-  \item {\tt size\_t size} (IN): size of the buffer for the file name.
-  \item {\tt char *name} (OUT): buffer for the file name.
-  \item {\tt ssize\_t *ret} (OUT): buffer for the entire size of the
+  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
+  \item \texttt{size\_t size} (IN): size of the buffer for the file name.
+  \item \texttt{char *name} (OUT): buffer for the file name.
+  \item \texttt{ssize\_t *ret} (OUT): buffer for the entire size of the
     file name.
@@
 
-\item {\tt H5VL\_OBJECT\_GET\_FILE}, get the container that the object
+\item \texttt{H5VL\_OBJECT\_GET\_FILE}, get the container that the object
   belongs to:
   \begin{enumerate}
-  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
-  \item {\tt void **ret} (OUT): pointer to the file structure returned
+  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
+  \item \texttt{void **ret} (OUT): pointer to the file structure returned
     by the plugin.
@@
 \end{itemize}
-
-The {\tt specific} callback in the file class implements specific operations on HDF5 files as specified in the {\tt
-  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.
-
+\end{mdframed}
+The \texttt{specific} callback in the file class implements specific operations on HDF5 files as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox] 
 \textbf{Signature:}
@@
 
-The {\tt specific\_type} argument is an {\tt enum}:
+The \texttt{specific\_type} argument is an \texttt{enum}:
 \begin{lstlisting}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The container or object where the operation needs
+  \texttt{obj} & (IN): The container or object where the operation needs
   to happen.\\
-  {\tt specific\_type} & (IN): The type of the operation.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
@@
 
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt specific\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_FILE\_FLUSH}, flushes all buffers associated with the container to disk:
-  \begin{enumerate}
-  \item {\tt H5I\_type\_t obj\_type} (IN): The object type of {\tt obj} on which the flush operation was called.
-  \item {\tt H5F\_scope\_t scope} (IN): The scope of the flushing action.
-  \end{enumerate}
-
-\item {\tt H5VL\_FILE\_IS\_ACCESSIBLE}, checks if a container is
+\item \texttt{H5VL\_FILE\_FLUSH}, flushes all buffers associated with the container to disk:
+  \begin{enumerate}
+  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
+  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_IS\_ACCESSIBLE}, checks if a container is
   accessible using a specific file access property list:
   \begin{enumerate}
-  \item {\tt hid\_t *fapl\_id} (IN): file access property list.
-  \item {\tt char *name} (IN): name of the container to check.
-  \item {\tt htri\_t *result} (OUT): buffer for the result; 0 if no, 1
+  \item \texttt{hid\_t *fapl\_id} (IN): file access property list.
+  \item \texttt{char *name} (IN): name of the container to check.
+  \item \texttt{htri\_t *result} (OUT): buffer for the result; 0 if no, 1
     if yes.
@@
 
-\item {\tt H5VL\_FILE\_MOUNT}, Mounts a file on the location object:
-  \begin{enumerate}
-  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
-  \item {\tt char *name} (IN): name of the group onto which the file
-    specified by {\tt file} is to be mounted.
-  \item {\tt void *file} (IN): child file to be mounted.
-  \item {\tt hid\_t *fmpl\_id} (IN): file mount property list.
-  \end{enumerate}
-
-\item {\tt H5VL\_FILE\_UNMOUNT}, un-mounts a file from the location object:
-  \begin{enumerate}
-  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
-  \item {\tt char *name} (IN): name of the mount point.
+\item \texttt{H5VL\_FILE\_MOUNT}, Mounts a file on the location object:
+  \begin{enumerate}
+  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
+  \item \texttt{char *name} (IN): name of the group onto which the file
+    specified by \texttt{file} is to be mounted.
+  \item \texttt{void *file} (IN): child file to be mounted.
+  \item \texttt{hid\_t *fmpl\_id} (IN): file mount property list.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_UNMOUNT}, un-mounts a file from the location object:
+  \begin{enumerate}
+  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
+  \item \texttt{char *name} (IN): name of the mount point.
   \end{enumerate}
 \end{itemize}
-
-The {\tt optional} callback in the file class implements plugin specific operations on an HDF5 container. It returns an {\tt
-  herr\_t} indicating success or failure.
-
+\end{mdframed}
+
+The \texttt{optional} callback in the file class implements plugin specific operations on an HDF5 container. It returns an 
+\texttt{herr\_t} indicating success or failure. \bigskip
+\begin{mdframed}[style=bgbox] 
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-
-Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-For example, in the native plugin, the first argument in the {\tt va\_list} is the optional argument type enum defined as follows:
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+For example, in the native plugin, the first argument in the \texttt{va\_list} is the optional argument type enum defined as follows:
 
@@
 %
-%\item {\tt H5VL\_FILE\_GET\_SIZE}, retrieve the size of the container
-%  in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_GET\_SIZE}, retrieve the size of the container
+%  in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt hsize\_t *ret} (OUT): file size.
+%  \item \texttt{hsize\_t *ret} (OUT): file size.
 %  \end{enumerate}
 %
-%\item {\tt H5VL\_FILE\_GET\_FILE\_IMAGE}, retrieve file image from the
-%  container in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_GET\_FILE\_IMAGE}, retrieve file image from the
+%  container in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt void *buf\_ptr} (OUT): buffer to return the file image.
-%  \item {\tt ssize\_t *ret} (OUT): buffer for the total size needed for
+%  \item \texttt{void *buf\_ptr} (OUT): buffer to return the file image.
+%  \item \texttt{ssize\_t *ret} (OUT): buffer for the total size needed for
 %    the file image.
-%  \item {\tt size\_t buf\_len} (IN): size of the buffer passed in.
+%  \item \texttt{size\_t buf\_len} (IN): size of the buffer passed in.
 %  \end{enumerate}
 %
-%\item {\tt H5VL\_FILE\_GET\_FREE\_SPACE}, retrieve amount of free
-%  space in the container in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_GET\_FREE\_SPACE}, retrieve amount of free
+%  space in the container in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt hssize\_t *ret} (OUT): buffer for the free space.
+%  \item \texttt{hssize\_t *ret} (OUT): buffer for the free space.
 %  \end{enumerate}
 %
-%\item {\tt H5VL\_FILE\_GET\_FREE\_SECTIONS}, retrieve free sections from the
-%  container in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_GET\_FREE\_SECTIONS}, retrieve free sections from the
+%  container in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt H5F\_sect\_info\_t *sinfo} (OUT): pointer to the section
+%  \item \texttt{H5F\_sect\_info\_t *sinfo} (OUT): pointer to the section
 %    info structure to fill.
-%  \item {\tt ssize\_t *ret} (OUT): buffer for the total number of free
+%  \item \texttt{ssize\_t *ret} (OUT): buffer for the total number of free
 %    sections.
-%  \item {\tt H5F\_mem\_t type} (IN): type of the memory space to check
+%  \item \texttt{H5F\_mem\_t type} (IN): type of the memory space to check
 %    for.
-%  \item {\tt size\_t nsects} (IN): number of section allocate in {\tt sinfo}.
+%  \item \texttt{size\_t nsects} (IN): number of section allocate in \texttt{sinfo}.
 %  \end{enumerate}
 %
-%\item {\tt H5VL\_FILE\_GET\_INFO}, retrieve file info from the
-%  object in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_GET\_INFO}, retrieve file info from the
+%  object in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
-%  \item {\tt H5F\_info2\_t *finfo} (OUT): pointer to info structure to fill.
+%  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
+%  \item \texttt{H5F\_info2\_t *finfo} (OUT): pointer to info structure to fill.
 %  \end{enumerate}
 %
-%\item {\tt H5VL\_FILE\_GET\_MDC\_CONF}, retrieve the meta data cache
-%  configuration from the container in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_GET\_MDC\_CONF}, retrieve the meta data cache
+%  configuration from the container in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt H5I\_type\_t type} (IN): the object type in {\tt obj}.
-%  \item {\tt H5AC\_cache\_config\_t *conf} (OUT): pointer to
+%  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
+%  \item \texttt{H5AC\_cache\_config\_t *conf} (OUT): pointer to
 %    configuration structure to fill.
@@
 %
-%\item {\tt H5VL\_FILE\_GET\_MDC\_HR}, retrieve the meta data cache
-%  hit rate from the container in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_GET\_MDC\_HR}, retrieve the meta data cache
+%  hit rate from the container in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt double *ret} (OUT): buffer for the hit rate.
+%  \item \texttt{double *ret} (OUT): buffer for the hit rate.
 %  \end{enumerate}
 %
-%\item {\tt H5VL\_FILE\_GET\_MDC\_SIZE}, retrieve the meta data cache
-%  size information from the container in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_GET\_MDC\_SIZE}, retrieve the meta data cache
+%  size information from the container in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt size\_t max\_size\_ptr} (OUT): buffer for maximum size.
-%  \item {\tt size\_t min\_clean\_size\_ptr} (OUT): buffer for minimum
+%  \item \texttt{size\_t max\_size\_ptr} (OUT): buffer for maximum size.
+%  \item \texttt{size\_t min\_clean\_size\_ptr} (OUT): buffer for minimum
 %    clean size.
-%  \item {\tt size\_t cur\_size\_ptr} (OUT): buffer for current size.
-%  \item {\tt int cur\_num\_entries\_ptr} (OUT): buffer for number of
+%  \item \texttt{size\_t cur\_size\_ptr} (OUT): buffer for current size.
+%  \item \texttt{int cur\_num\_entries\_ptr} (OUT): buffer for number of
 %    current cache entries.
@@
 %
-%\item {\tt H5VL\_FILE\_GET\_VFD\_HANDLE}, retrieve the virtual file
-%  driver handle from the container in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_GET\_VFD\_HANDLE}, retrieve the virtual file
+%  driver handle from the container in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt void **handle} (OUT): pointer to a buffer the plugin sets
+%  \item \texttt{void **handle} (OUT): pointer to a buffer the plugin sets
 %    to the VFD handle.
-%  \item {\tt hid\_t fapl} (IN): File access property list.
+%  \item \texttt{hid\_t fapl} (IN): File access property list.
 %  \end{enumerate}
 %
-%\item {\tt H5VL\_FILE\_CLEAR\_ELINK\_CACHE}, clears the external link
+%\item \texttt{H5VL\_FILE\_CLEAR\_ELINK\_CACHE}, clears the external link
 %  file cache. Takes no extra arguments.
 %
-%\item {\tt H5VL\_FILE\_REOPEN}, reopen the container in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_REOPEN}, reopen the container in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt void **ret} (OUT): pointer to be set to the opened file
+%  \item \texttt{void **ret} (OUT): pointer to be set to the opened file
 %    structure.
@@
 %
-%\item {\tt H5VL\_FILE\_RESET\_MDC\_HIT\_RATE}, resets the hit rate
-%  statistics for the metadata cache on the container in {\tt
+%\item \texttt{H5VL\_FILE\_RESET\_MDC\_HIT\_RATE}, resets the hit rate
+%  statistics for the metadata cache on the container in \texttt{
 %    obj}. Takes no extra arguments.
 %
-%\item {\tt H5VL\_FILE\_SET\_MDC\_CONFIG}, sets the meta data cache
-%  configuration for the container in {\tt obj}:
+%\item \texttt{H5VL\_FILE\_SET\_MDC\_CONFIG}, sets the meta data cache
+%  configuration for the container in \texttt{obj}:
 %  \begin{enumerate}
-%  \item {\tt H5AC\_cache\_config\_t *conf} (IN): pointer to
+%  \item \texttt{H5AC\_cache\_config\_t *conf} (IN): pointer to
 %    configuration structure to use.
@@
 
-The {\tt close} callback in the file class should terminate access to
+The \texttt{close} callback in the file class should terminate access to
 the file object and free all resources it was consuming, and returns
-an {\tt herr\_t} indicating success or failure.
-
+an \texttt{herr\_t} indicating success or failure.\bigskip\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt file} & (IN): Pointer to the file.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
+  \texttt{file} & (IN): Pointer to the file.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
 
@@
 map to one of the group callback routines in this class that the
-plugin needs to implement:
-
-\begin{lstlisting}
+plugin needs to implement, Listing \ref{lst:Groupclass}.
+
+\begin{lstlisting}[caption={Structure for group callback routines, H5VLpublic.h}, captionpos=b, label={lst:Groupclass}]
 typedef struct H5VL_group_class_t {
@@
 
-The {\tt create} callback in the group class should create a group
+The \texttt{create} callback in the group class creates a group
 object in the container of the location object and returns a pointer
 to the group structure containing information to access the group in
-future calls.
-
+future calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to an object where the group needs
+  \texttt{obj} & (IN): Pointer to an object where the group needs
   to be created or where the look-up of the target object needs to
   start.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_SELF} in this callback. \\
-  {\tt name} & (IN): The name of the group to be created.\\
-  {\tt dcpl\_id} & (IN): The group creation property list. It contains
+  \texttt{loc\_params} & (IN): The location parameters as explained in
+  section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  \texttt{name} & (IN): The name of the group to be created.\\
+  \texttt{dcpl\_id} & (IN): The group creation property list. It contains
   all the group creation properties in addition to the link creation
-  property list of the create operation (an {\tt hid\_t}) that can be
-  retrieved with the property {\tt H5VL\_GRP\_LCPL\_ID}.\\
-  {\tt gapl\_id} & (IN): The group access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt open} callback in the group class should open a group object
+  property list of the create operation (an \texttt{hid\_t}) that can be
+  retrieved with the property \texttt{H5VL\_GRP\_LCPL\_ID}.\\
+  \texttt{gapl\_id} & (IN): The group access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{open} callback in the group class opens a group object
 in the container of the location object and returns a pointer to the
 group structure containing information to access the group in future
-calls.
-
+calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to an object where the group needs to be
+  \texttt{obj} & (IN): Pointer to an object where the group needs to be
   opened or where the look-up of the target object needs to start.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_SELF} in this callback. \\
-  {\tt name} & (IN): The name of the group to be opened.\\
-  {\tt dapl\_id} & (IN): The group access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt get} callback in the group class should retrieve information
-about the group as specified in the {\tt get\_type} parameter. It
-returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{loc\_params} & (IN): The location parameters as explained in
+  section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  \texttt{name} & (IN): The name of the group to be opened.\\
+  \texttt{dapl\_id} & (IN): The group access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{get} callback in the group class retrieves information
+about the group as specified in the \texttt{get\_type} parameter. It
+returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The group object where information needs to be
+  \texttt{obj} & (IN): The group object where information needs to be
   retrieved from.\\
-  {\tt get\_type} & (IN): The type of the information to retrieve.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt get\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_GROUP\_GET\_GCPL}, to retrieve the group creation
-  property list of the group specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+\item \texttt{H5VL\_GROUP\_GET\_GCPL}, to retrieve the group creation
+  property list of the group specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     group creation property list.
@@
 
-\item {\tt H5VL\_GROUP\_GET\_INFO}, to retrieve the attribute info:
-  \begin{enumerate}
-  \item {\tt H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
+\item \texttt{H5VL\_GROUP\_GET\_INFO}, to retrieve the attribute info:
+  \begin{enumerate}
+  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
     explained in section~\ref{sec:map}. 
-  \item {\tt H5G\_info\_t *ginfo} (OUT): info structure to fill the
+  \item \texttt{H5G\_info\_t *ginfo} (OUT): info structure to fill the
     group info in.
@@
 
-The {\tt specific} callback in the group class currently does not require any functionality to be implemented and should be left as {\tt NULL}.
-
-The {\tt optional} callback in the group class implements plugin specific operations on an HDF5 group. It returns an {\tt
-  herr\_t} indicating success or failure.
-
+The \texttt{specific} callback in the group class currently does not require any functionality to be implemented and should be left as \texttt{NULL}.
+
+The \texttt{optional} callback in the group class implements plugin specific operations on an HDF5 group. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-
-Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
-The {\tt close} callback in the group class should terminate access to
-the group object and free all resources it was consuming, and returns
-an {\tt herr\_t} indicating success or failure.
-
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+The \texttt{close} callback in the group class terminates access to
+the group object and frees all resources it was consuming, and returns
+an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt group} & (IN): Pointer to the group object.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
+  \texttt{group} & (IN): Pointer to the group object.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
 
@@
 map to one of the dataset callback routines in this class that the
-plugin needs to implement:
-
-\begin{lstlisting}
+plugin needs to implement, Listing \ref{lst:DSclass}.
+
+\begin{lstlisting}[caption={Structure for dataset callback routines, H5VLpublic.h}, captionpos=b, label={lst:DSclass}]
 typedef struct H5VL_dataset_class_t {
@@
 
-The {\tt create} callback in the dataset class should create a dataset
+The \texttt{create} callback in the dataset class creates a dataset
 object in the container of the location object and returns a pointer
 to the dataset structure containing information to access the dataset
-in future calls.
-
+in future calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to an object where the dataset needs
+  \texttt{obj} & (IN): Pointer to an object where the dataset needs
   to be created or where the look-up of the target object needs to
   start.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_SELF} in this callback. \\
-  {\tt name} & (IN): The name of the dataset to be created.\\
-  {\tt dcpl\_id} & (IN): The dataset creation property list. It contains
+  \texttt{loc\_params} & (IN): The location parameters as explained in
+  section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  \texttt{name} & (IN): The name of the dataset to be created.\\
+  \texttt{dcpl\_id} & (IN): The dataset creation property list. It contains
   all the dataset creation properties in addition to the dataset
-  datatype (an {\tt hid\_t}), dataspace (an {\tt hid\_t}), and the
-  link creation property list of the create operation (an {\tt
-    hid\_t}) that can be retrieved with the properties, {\tt
-    H5VL\_DSET\_TYPE\_ID}, {\tt H5VL\_DSET\_SPACE\_ID},  and {\tt
-    H5VL\_DSET\_LCPL\_ID} respectively.\\
-  {\tt dapl\_id} & (IN): The dataset access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt open} callback in the dataset class should open a dataset
+  datatype (an \texttt{hid\_t}), dataspace (an \texttt{hid\_t}), and the
+  link creation property list of the create operation (an \texttt{hid\_t}) that can be retrieved with the properties, \texttt{H5VL\_DSET\_TYPE\_ID}, \texttt{H5VL\_DSET\_SPACE\_ID},  and \texttt{H5VL\_DSET\_LCPL\_ID} respectively.\\
+  \texttt{dapl\_id} & (IN): The dataset access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{open} callback in the dataset class opens a dataset
 object in the container of the location object and returns a pointer
 to the dataset structure containing information to access the dataset
-in future calls.
-
+in future calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to an object where the dataset needs to be
+  \texttt{obj} & (IN): Pointer to an object where the dataset needs to be
   opened or where the look-up of the target object needs to start.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_SELF} in this callback. \\
-  {\tt name} & (IN): The name of the dataset to be opened.\\
-  {\tt dapl\_id} & (IN): The dataset access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt read} callback in the dataset class should read data from
-the dataset object and returns an {\tt herr\_t} indicating success or
-failure.
-
+  \texttt{loc\_params} & (IN): The location parameters as explained in
+  section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  \texttt{name} & (IN): The name of the dataset to be opened.\\
+  \texttt{dapl\_id} & (IN): The dataset access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{read} callback in the dataset class  reads data from
+the dataset object and returns an \texttt{herr\_t} indicating success or
+failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt dset} & (IN): Pointer to the dataset object.\\
-  {\tt mem\_type\_id} & (IN): The memory datatype of the data.\\
-  {\tt mem\_space\_id} & (IN): The memory dataspace selection.\\
-  {\tt file\_space\_id} & (IN): The file dataspace selection.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt buf} & (OUT): Data buffer to be read into.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt write} callback in the dataset class should write data to
-the dataset object and returns an {\tt herr\_t} indicating success or
-failure.
-
+  \texttt{dset} & (IN): Pointer to the dataset object.\\
+  \texttt{mem\_type\_id} & (IN): The memory datatype of the data.\\
+  \texttt{mem\_space\_id} & (IN): The memory dataspace selection.\\
+  \texttt{file\_space\_id} & (IN): The file dataspace selection.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{buf} & (OUT): Data buffer to be read into.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{write} callback in the dataset class writes data to
+the dataset object and returns an \texttt{herr\_t} indicating success or
+failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt dset} & (IN): Pointer to the dataset object.\\
-  {\tt mem\_type\_id} & (IN): The memory datatype of the data.\\
-  {\tt mem\_space\_id} & (IN): The memory dataspace selection.\\
-  {\tt file\_space\_id} & (IN): The file dataspace selection.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt buf} & (IN): Data buffer to be written from.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt get} callback in the dataset class should retrieve
-information about the dataset as specified in the {\tt get\_type}
-parameter.It returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{dset} & (IN): Pointer to the dataset object.\\
+  \texttt{mem\_type\_id} & (IN): The memory datatype of the data.\\
+  \texttt{mem\_space\_id} & (IN): The memory dataspace selection.\\
+  \texttt{file\_space\_id} & (IN): The file dataspace selection.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{buf} & (IN): Data buffer to be written from.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{get} callback in the dataset class retrieves
+information about the dataset as specified in the \texttt{get\_type}
+parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt dset} & (IN): The dataset object where information needs to be
+  \texttt{dset} & (IN): The dataset object where information needs to be
   retrieved from.\\
-  {\tt get\_type} & (IN): The type of the information to retrieve.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt get\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_DATASET\_GET\_DAPL}, to retrieve the dataset access
-  property list of the dataset specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+\item \texttt{H5VL\_DATASET\_GET\_DAPL}, to retrieve the dataset access
+  property list of the dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     dataset access property list.
@@
 
-\item {\tt H5VL\_DATASET\_GET\_DCPL}, to retrieve the dataset creation
-  property list of the dataset specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+\item \texttt{H5VL\_DATASET\_GET\_DCPL}, to retrieve the dataset creation
+  property list of the dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     dataset creation property list.
@@
 
-\item {\tt H5VL\_DATASET\_GET\_OFFSET}, to retrieve the offset of the
-  dataset specified in {\tt obj} in the container:
-  \begin{enumerate}
-  \item {\tt haddr\_t *ret} (OUT): buffer for the offset of the
+\item \texttt{H5VL\_DATASET\_GET\_OFFSET}, to retrieve the offset of the
+  dataset specified in \texttt{obj} in the container:
+  \begin{enumerate}
+  \item \texttt{haddr\_t *ret} (OUT): buffer for the offset of the
     dataset in the container.
@@
 
-\item {\tt H5VL\_DATASET\_GET\_SPACE}, to retrieve the dataspace of the
-  dataset specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+\item \texttt{H5VL\_DATASET\_GET\_SPACE}, to retrieve the dataspace of the
+  dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     dataset dataspace.
@@
 
-\item {\tt H5VL\_DATASET\_GET\_SPACE\_STATUS}, to retrieve the
+\item \texttt{H5VL\_DATASET\_GET\_SPACE\_STATUS}, to retrieve the
   information whether space has been allocated for the dataset:
   \begin{enumerate}
-  \item {\tt H5D\_space\_status\_t *allocation} (OUT): buffer for the
+  \item \texttt{H5D\_space\_status\_t *allocation} (OUT): buffer for the
     space status.
@@
 
-\item {\tt H5VL\_DATASET\_GET\_STORAGE\_SIZE}, to retrieve the storage
-  size of the dataset specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hsize\_t *ret} (OUT): buffer for the storage size of
+\item \texttt{H5VL\_DATASET\_GET\_STORAGE\_SIZE}, to retrieve the storage
+  size of the dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hsize\_t *ret} (OUT): buffer for the storage size of
     the dataset in the container.
@@
 
-\item {\tt H5VL\_DATASET\_GET\_TYPE}, to retrieve the datatype of the
-  dataset specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+\item \texttt{H5VL\_DATASET\_GET\_TYPE}, to retrieve the datatype of the
+  dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     dataset datatype.
@@
 
-The {\tt specific} callback in the dataset class implements specific operations on HDF5 datasets as specified in the {\tt
-  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.
-
+The \texttt{specific} callback in the dataset class implements specific operations on HDF5 datasets as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The dset  where the operation needs
+  \texttt{obj} & (IN): The dset  where the operation needs
   to happen.\\
-  {\tt specific\_type} & (IN): The type of the operation.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt specific\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_DATASET\_SET\_EXTENT}, changes the extent of the dataset dimensions:
-  \begin{enumerate}
-  \item {\tt hsize\_t size} (IN): Array containing the new magnitude of each dimension of the dataset. 
+\item \texttt{H5VL\_DATASET\_SET\_EXTENT}, changes the extent of the dataset dimensions:
+  \begin{enumerate}
+  \item \texttt{hsize\_t size} (IN): Array containing the new magnitude of each dimension of the dataset. 
   \end{enumerate}
@@
 
-The {\tt optional} callback in the dataset class implements plugin specific operations on an HDF5 dataset. It returns an {\tt
-  herr\_t} indicating success or failure.
-
+The \texttt{optional} callback in the dataset class implements plugin specific operations on an HDF5 dataset. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-
-Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
-The {\tt close} callback in the dataset class should terminate access
-to the dataset object and free all resources it was consuming, and
-returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+The \texttt{close} callback in the dataset class terminates access
+to the dataset object and free all resources it was consuming and
+returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt dset} & (IN): Pointer to the dataset object.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
+  \texttt{dset} & (IN): Pointer to the dataset object.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
 
@@
 container map to one of the attribute callback routines in this
-class that the plugin needs to implement:
-
-\begin{lstlisting}
+class that the plugin needs to implement, Listing \ref{lst:ATTRclass}.
+
+\begin{lstlisting}[caption={Structure for attribute callback routines, H5VLpublic.h}, captionpos=b, label={lst:ATTRclass}]
 typedef struct H5VL_attr_class_t {
@@
 
-The {\tt create} callback in the attribute class should create an
+The \texttt{create} callback in the attribute class creates an
 attribute object in the container of the location object and
 returns a pointer to the attribute structure containing information to
-access the attribute in future calls.
-
+access the attribute in future calls. \bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to an object where the attribute needs
+  \texttt{obj} & (IN): Pointer to an object where the attribute needs
   to be created or where the look-up of the target object needs to
   start.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
+  \texttt{loc\_params} & (IN): The location parameters as explained in
   section~\ref{sec:map}.\\
-  {\tt attr\_name} & (IN): The name of the attribute to be created.\\
-  {\tt acpl\_id} & (IN): The attribute creation property list. It contains
+  \texttt{attr\_name} & (IN): The name of the attribute to be created.\\
+  \texttt{acpl\_id} & (IN): The attribute creation property list. It contains
   all the attribute creation properties in addition to the attribute
-  datatype (an {\tt hid\_t}) and dataspace (an {\tt hid\_t}) that can
-  be retrieved with the properties, {\tt H5VL\_ATTR\_TYPE\_ID} and
-  {\tt H5VL\_ATTR\_SPACE\_ID}.\\
-  {\tt aapl\_id} & (IN): The attribute access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt open} callback in the attribute class should open an
+  datatype (an \texttt{hid\_t}) and dataspace (an \texttt{hid\_t}) that can
+  be retrieved with the properties, \texttt{H5VL\_ATTR\_TYPE\_ID} and
+  \texttt{H5VL\_ATTR\_SPACE\_ID}.\\
+  \texttt{aapl\_id} & (IN): The attribute access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{open} callback in the attribute class opens an
 attribute object in the container of the location object and returns a
 pointer to the attribute structure containing information to access
-the attribute in future calls.
-
+the attribute in future calls. \bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to an object where the attribute needs to be
+  \texttt{obj} & (IN): Pointer to an object where the attribute needs to be
   opened or where the look-up of the target object needs to start.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
+  \texttt{loc\_params} & (IN): The location parameters as explained in
   section~\ref{sec:map}.\\
-  {\tt attr\_name} & (IN): The name of the attribute to be opened.\\
-  {\tt aapl\_id} & (IN): The attribute access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt read} callback in the attribute class should read data from
-the attribute object and returns an {\tt herr\_t} indicating success or
-failure.
-
+  \texttt{attr\_name} & (IN): The name of the attribute to be opened.\\
+  \texttt{aapl\_id} & (IN): The attribute access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{read} callback in the attribute class reads data from
+the attribute object and returns an \texttt{herr\_t} indicating success or
+failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt attr} & (IN): Pointer to the attribute object.\\
-  {\tt mem\_type\_id} & (IN): The memory datatype of the attribute.\\
-  {\tt buf} & (OUT): Data buffer to be read into.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt write} callback in the attribute class should write data to
-the attribute object and returns an {\tt herr\_t} indicating success or
-failure.
-
+  \texttt{attr} & (IN): Pointer to the attribute object.\\
+  \texttt{mem\_type\_id} & (IN): The memory datatype of the attribute.\\
+  \texttt{buf} & (OUT): Data buffer to be read into.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{write} callback in the attribute class writes data to
+the attribute object and returns an \texttt{herr\_t} indicating success or
+failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt attr} & (IN): Pointer to the attribute object.\\
-  {\tt mem\_type\_id} & (IN): The memory datatype of the attribute.\\
-  {\tt buf} & (IN): Data buffer to be written.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt get} callback in the attribute class should retrieve
-information about the attribute as specified in the {\tt get\_type}
-parameter.It returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{attr} & (IN): Pointer to the attribute object.\\
+  \texttt{mem\_type\_id} & (IN): The memory datatype of the attribute.\\
+  \texttt{buf} & (IN): Data buffer to be written.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{get} callback in the attribute class retrieves
+information about the attribute as specified in the \texttt{get\_type}
+parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt attr} & (IN): An attribute or location object where information
+  \texttt{attr} & (IN): An attribute or location object where information
   needs to be retrieved from.\\
-  {\tt get\_type} & (IN): The type of the information to retrieve.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt get\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
@@
 
-\item {\tt H5VL\_ATTR\_GET\_ACPL}, to retrieve the attribute creation
-  property list of the attribute specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+\item \texttt{H5VL\_ATTR\_GET\_ACPL}, to retrieve the attribute creation
+  property list of the attribute specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     attribute creation property list.
@@
 
-\item {\tt H5VL\_ATTR\_GET\_INFO}, to retrieve the attribute info:
-  \begin{enumerate}
-  \item {\tt H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
+\item \texttt{H5VL\_ATTR\_GET\_INFO}, to retrieve the attribute info:
+  \begin{enumerate}
+  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
     explained in section~\ref{sec:map}. 
-  \item {\tt H5A\_info\_t *ainfo} (OUT): info structure to fill the
+  \item \texttt{H5A\_info\_t *ainfo} (OUT): info structure to fill the
     attribute info in.
@@
 
-\item {\tt H5VL\_ATTR\_GET\_NAME}, to retrieve an attribute name on a
-  particular object specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
+\item \texttt{H5VL\_ATTR\_GET\_NAME}, to retrieve an attribute name on a
+  particular object specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
     explained in section~\ref{sec:map}. The type could be either
-    {\tt H5VL\_OBJECT\_BY\_SELF} meaning {\tt obj} is the attribute,
-    or {\tt H5VL\_OBJECT\_BY\_IDX} meaning the attribute to retrieve
+    \texttt{H5VL\_OBJECT\_BY\_SELF} meaning \texttt{obj} is the attribute,
+    or \texttt{H5VL\_OBJECT\_BY\_IDX} meaning the attribute to retrieve
     the name for should be looked up using the index information on
-    the object in {\tt obj} and the index information in {\tt loc\_params}.
-  \item {\tt size\_t buf\_size} (IN): the size of the buffer to store
+    the object in \texttt{obj} and the index information in \texttt{loc\_params}.
+  \item \texttt{size\_t buf\_size} (IN): the size of the buffer to store
     the name in.
-  \item {\tt void *buf} (OUT): Buffer to store the name in.
-  \item {\tt ssize\_t *ret\_val} (OUT): return the actual size needed
+  \item \texttt{void *buf} (OUT): Buffer to store the name in.
+  \item \texttt{ssize\_t *ret\_val} (OUT): return the actual size needed
     to store the fill attribute name.
@@
 
-\item {\tt H5VL\_ATTR\_GET\_SPACE}, to retrieve the dataspace of the
-  attribute specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+\item \texttt{H5VL\_ATTR\_GET\_SPACE}, to retrieve the dataspace of the
+  attribute specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     attribute dataspace.
@@
 
-\item {\tt H5VL\_ATTR\_GET\_STORAGE\_SIZE}, to retrieve the storage
-  size of the attribute specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hsize\_t *ret} (OUT): buffer for the storage size of
+\item \texttt{H5VL\_ATTR\_GET\_STORAGE\_SIZE}, to retrieve the storage
+  size of the attribute specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hsize\_t *ret} (OUT): buffer for the storage size of
     the attribute in the container.
@@
 
-\item {\tt H5VL\_ATTR\_GET\_TYPE}, to retrieve the datatype of the
-  attribute specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+\item \texttt{H5VL\_ATTR\_GET\_TYPE}, to retrieve the datatype of the
+  attribute specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     attribute datatype.
@@
 
-The {\tt specific} callback in the attribute class implements specific operations on HDF5 attributes as specified in the {\tt
-  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.
-
+The \texttt{specific} callback in the attribute class implements specific operations on HDF5 attributes as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The location object  where the operation needs to happen.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
-  {\tt specific\_type} & (IN): The type of the operation.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt specific\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_ATTR\_DELETE}, to delete an attribute on an object:
-  \begin{enumerate}
-  \item {\tt char *attr\_name} (IN): the name of the attribute to delete.
-  \end{enumerate}
-
-\item {\tt H5VL\_ATTR\_EXISTS}, to check if an attribute exists on a
-  particular object specified in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
+\item \texttt{H5VL\_ATTR\_DELETE}, to delete an attribute on an object:
+  \begin{enumerate}
+  \item \texttt{char *attr\_name} (IN): the name of the attribute to delete.
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_EXISTS}, to check if an attribute exists on a
+  particular object specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
     explained in section~\ref{sec:map}.
-  \item {\tt char *attr\_name} (IN): the attribute name to check.
-  \item {\tt htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
-  \end{enumerate}
-
-\item {\tt H5VL\_ATTR\_ITER}, to iterate over all attributes of an object and call a user specified callback on each one:
-  \begin{enumerate}
-  \item {\tt H5\_index\_t idx\_type} (IN): Type of index.\\
-  \item {\tt H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
-  \item {\tt hsize\_t *idx} (IN/OUT): Initial and return offset within index.\\
-  \item {\tt H5A\_operator2\_t op} (IN): User-defined function to pass each attribute to. \\
-  \item {\tt void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
-  \end{enumerate}
-
-\item {\tt H5VL\_ATTR\_RENAME}, to rename an attribute on an object:
-  \begin{enumerate}
-  \item {\tt char *old\_name} (IN): the original name of the attribute.
-  \item {\tt char *new\_name} (IN): the new name to assign for the attribute.
+  \item \texttt{char *attr\_name} (IN): the attribute name to check.
+  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_ITER}, to iterate over all attributes of an object and call a user-specified callback on each one:
+  \begin{enumerate}
+  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
+  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
+  \item \texttt{hsize\_t *idx} (IN/OUT): Initial and return offset within index.\\
+  \item \texttt{H5A\_operator2\_t op} (IN): User-defined function to pass each attribute to. \\
+  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_RENAME}, to rename an attribute on an object:
+  \begin{enumerate}
+  \item \texttt{char *old\_name} (IN): the original name of the attribute.
+  \item \texttt{char *new\_name} (IN): the new name to assign for the attribute.
   \end{enumerate}
@@
 
-The {\tt optional} callback in the attribute class implements plugin specific operations on an HDF5 attribute. It returns an {\tt
-  herr\_t} indicating success or failure.
-
+The \texttt{optional} callback in the attribute class implements plugin specific operations on an HDF5 attribute. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-
-Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
-The {\tt close} callback in the attribute class should terminate
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+The \texttt{close} callback in the attribute class terminates
 access to the attribute object and free all resources it was
-consuming, and returns an {\tt herr\_t} indicating success or failure.
-
+consuming, and returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt attr} & (IN): Pointer to the attribute object.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
+  \texttt{attr} & (IN): Pointer to the attribute object.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
 
@@
 the named datatype callback routines in this class that the plugin needs to
-implement:
-
-\begin{lstlisting}
+implement, Listing \ref{lst:H5Tclass}.
+
+\begin{lstlisting}[caption={Structure for datatype callback routines, H5VLpublic.h}, captionpos=b, label={lst:H5Tclass}]
 typedef struct H5VL_datatype_class_t {
@@
 
-The {\tt commit} callback in the named datatype class should create a datatype object in the container of the location object and
-returns a pointer to the datatype structure containing information to access the datatype in future calls.
-
+The \texttt{commit} callback in the named datatype class creates a datatype object in the container of the location object and
+returns a pointer to the datatype structure containing information to access the datatype in future calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to an object where the datatype needs
+  \texttt{obj} & (IN): Pointer to an object where the datatype needs
   to be committed or where the look-up of the target object needs to
   start.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. In this call, the location type is always {\tt
-    H5VL\_OBJECT\_BY\_SELF}. \\
-  {\tt name} & (IN): The name of the datatype to be created.\\
-  {\tt type\_id} & (IN): The transient datatype identifier to be
+  \texttt{loc\_params} & (IN): The location parameters as explained in
+  section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
+  \texttt{name} & (IN): The name of the datatype to be created.\\
+  \texttt{type\_id} & (IN): The transient datatype identifier to be
   committed. \\
-  {\tt lcpl\_id} & (IN): The link creation property list. \\
-  {\tt tcpl\_id} & (IN): The datatype creation property list.\\
-  {\tt tapl\_id} & (IN): The datatype access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt open} callback in the named datatype class should open a
+  \texttt{lcpl\_id} & (IN): The link creation property list. \\
+  \texttt{tcpl\_id} & (IN): The datatype creation property list.\\
+  \texttt{tapl\_id} & (IN): The datatype access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{open} callback in the named datatype class opens a
 previously committed datatype object in the container of the location
 object and returns a pointer to the datatype structure containing
-information to access the datatype in future calls.
-
+information to access the datatype in future calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to an object where the datatype needs
+  \texttt{obj} & (IN): Pointer to an object where the datatype needs
   to be opened or where the look-up of the target object needs to
   start.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. In this call, the location type is always {\tt
-    H5VL\_OBJECT\_BY\_SELF}. \\
-  {\tt name} & (IN): The name of the datatype to be opened.\\
-  {\tt tapl\_id} & (IN): The datatype access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt get\_binary} callback in the named datatype class should
-serialize the original transient HDF5 datatype that was committed, or
-return the size that is required for it be serialized if the passed in
-buffer is {\tt NULL}. The HDF5 library provides two functions to
-encode and decode datatypes in their transient form, {\tt H5Tencode()}
-and {\tt H5Tdecode()}. When a datatype is committed, the plugin is
+  \texttt{loc\_params} & (IN): The location parameters as explained in
+  section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
+  \texttt{name} & (IN): The name of the datatype to be opened.\\
+  \texttt{tapl\_id} & (IN): The datatype access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{get\_binary} callback in the named datatype class
+serializes the original transient HDF5 datatype that was committed, or
+returns the size that is required for it be serialized if the passed in
+buffer is \texttt{NULL}. The HDF5 library provides two functions to
+encode and decode datatypes in their transient form, \texttt{H5Tencode()}
+and \texttt{H5Tdecode()}. When a datatype is committed, the plugin is
 required to keep the serialized form of the transient datatype stored
@@
 identifier that allows all the H5T ``transient'' routines to work
-properly on the named datatype.
-
+properly on the named datatype.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to the named datatype object.\\
-  {\tt buf} & (OUT): Buffer to out the binary form of the datatype in.\\
-  {\tt size} & (IN): The size of the buffer passed in (0 if NULL).\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt get} callback in the named datatype class should retrieve
-information about the named datatype as specified in the {\tt get\_type}
-parameter.It returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{obj} & (IN): Pointer to the named datatype object.\\
+  \texttt{buf} & (OUT): Buffer to out the binary form of the datatype in.\\
+  \texttt{size} & (IN): The size of the buffer passed in (0 if NULL).\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{get} callback in the named datatype class retrieves
+information about the named datatype as specified in the \texttt{get\_type}
+parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The named datatype to retrieve information from.\\
-  {\tt get\_type} & (IN): The type of the information to retrieve.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{obj} & (IN): The named datatype to retrieve information from.\\
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt get\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_DATATYPE\_GET\_BINARY}, to retrieve the serialized original transient HDF5 datatype that was committed, or
-return the size that is required for it be serialized if the passed in buffer is {\tt NULL}. The HDF5 library provides two functions to
-encode and decode datatypes in their transient form, {\tt H5Tencode()} and {\tt H5Tdecode()}.
+\item \texttt{H5VL\_DATATYPE\_GET\_BINARY}, to retrieve the serialized original transient HDF5 datatype that was committed, or
+return the size that is required for it be serialized if the passed in buffer is \texttt{NULL}. The HDF5 library provides two functions to
+encode and decode datatypes in their transient form, \texttt{H5Tencode()} and \texttt{H5Tdecode()}.
 When a datatype is committed, the plugin is required to keep the serialized form of the transient datatype stored somewhere in the container (which is usually the case anyway when committing a named datatype), so it can be retrieved with this call.
@@
   \begin{enumerate}
-  \item {\tt ssize\_t *nalloc} (OUT): buffer to store the total size of the serialized datatype.
-  \item {\tt void *buf} (OUT): buffer to store the serialized datatype.
-  \item {\tt size\_t size} (IN): size of the passed in buffer.
-  \end{enumerate}
-
-\item {\tt H5VL\_DATATYPE\_GET\_TCPL}, to retrieve the datatype
+  \item \texttt{ssize\_t *nalloc} (OUT): buffer to store the total size of the serialized datatype.
+  \item \texttt{void *buf} (OUT): buffer to store the serialized datatype.
+  \item \texttt{size\_t size} (IN): size of the passed in buffer.
+  \end{enumerate}
+
+\item \texttt{H5VL\_DATATYPE\_GET\_TCPL}, to retrieve the datatype
   creation property list:
   \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the identifier of the
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
     type creation property list.
@@
 
-The {\tt specific} callback in the datatype class currently does not require any functionality to be implemented and should be left as {\tt NULL}.
-
-The {\tt optional} callback in the datatype class implements plugin specific operations on an HDF5 datatype. It returns an {\tt
-  herr\_t} indicating success or failure.
-
+The \texttt{specific} callback in the datatype class currently does not require any functionality to be implemented and should be left as \texttt{NULL}.
+
+The \texttt{optional} callback in the datatype class implements plugin specific operations on an HDF5 datatype. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-
-Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
-The {\tt close} callback in the named datatype class should terminate
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+The \texttt{close} callback in the named datatype class terminates
 access to the datatype object and free all resources it was
-consuming, and returns an {\tt herr\_t} indicating success or failure.
-
+consuming and returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt dt} & (IN): Pointer to the datatype object.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
+  \texttt{dt} & (IN): Pointer to the datatype object.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
 
@@
 modify the HDF5 container map to one of the object callback routines
-in this class that the plugin needs to implement:
-
-\begin{lstlisting}
+in this class that the plugin needs to implement, Listing \ref{lst:H5Oclass}.
+
+\begin{lstlisting}[caption={Structure for object callback routines, H5VLpublic.h}, captionpos=b, label={lst:H5Oclass}]
 typedef struct H5VL_object_class_t {
@@
 
-The {\tt open} callback in the object class should open the object in
+The \texttt{open} callback in the object class opens the object in
 the container of the location object and returns a pointer to the
 object structure containing information to access the object in future
-calls.
-
+calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): Pointer to a file or group where the objecy needs to be
+  \texttt{obj} & (IN): Pointer to a file or group where the objecy needs to be
   opened or where the look-up of the target object needs to start.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
+  \texttt{loc\_params} & (IN): The location parameters as explained in
   section~\ref{sec:map}.\\
-  {\tt opened\_type} & (OUT): buffer to return the type of the object
-  opened ({\tt H5I\_GROUP} or {\tt H5I\_DATASET} or {\tt H5I\_DATATYPE}).\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt copy} callback in the object class should copy the object
-from the source object to the destination object. It returns an {\tt
-  herr\_t} indicating success or failure.
-
+  \texttt{opened\_type} & (OUT): buffer to return the type of the object
+  opened (\texttt{H5I\_GROUP} or \texttt{H5I\_DATASET} or \texttt{H5I\_DATATYPE}).\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{copy} callback in the object class  copies the object
+from the source object to the destination object. It returns an \texttt{
+  herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt src\_obj} & (IN): Pointer to location of the source object to
+  \texttt{src\_obj} & (IN): Pointer to location of the source object to
   be copied.\\
-  {\tt loc\_params1} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type should only be {\tt
-    H5VL\_OBJECT\_BY\_SELF} for this callback.\\
-  {\tt src\_name} & (IN): Name of the source object to
+  \texttt{loc\_params1} & (IN): The location parameters as explained in
+  section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
+  \texttt{src\_name} & (IN): Name of the source object to
   be copied.\\
-  {\tt dst\_obj} & (IN): Pointer to location of the destination
+  \texttt{dst\_obj} & (IN): Pointer to location of the destination
   object.\\
-  {\tt loc\_params2} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type should only be {\tt
-    H5VL\_OBJECT\_BY\_SELF} for this callback.\\
-  {\tt dst\_name} & (IN): Name to be assigned to the new copy.\\
-  {\tt ocpypl\_id} & (IN): The object copy property list.\\
-  {\tt lcpl\_id} & (IN): The link creation property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt get} callback in the object class should retrieve information
-about the object as specified in the {\tt get\_type} parameter.It
-returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{loc\_params2} & (IN): The location parameters as explained in
+  section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
+  \texttt{dst\_name} & (IN): Name to be assigned to the new copy.\\
+  \texttt{ocpypl\_id} & (IN): The object copy property list.\\
+  \texttt{lcpl\_id} & (IN): The link creation property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{get} callback in the object class retrieves information
+about the object as specified in the \texttt{get\_type} parameter.It
+returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): A location object where information needs to be
+  \texttt{obj} & (IN): A location object where information needs to be
   retrieved from.\\
-  {\tt loc\_params} & (IN): The location parameters as
+  \texttt{loc\_params} & (IN): The location parameters as
   explained in section~\ref{sec:map}.\\
-  {\tt get\_type} & (IN): The type of the information to retrieve.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt get\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_REF\_GET\_NAME}, to retrieve a name for a referenced object:
-  \begin{enumerate}
-  \item {\tt ssize\_t *ret} (OUT): buffer to return the length of the
+\item \texttt{H5VL\_REF\_GET\_NAME}, to retrieve a name for a referenced object:
+  \begin{enumerate}
+  \item \texttt{ssize\_t *ret} (OUT): buffer to return the length of the
     name.
-  \item {\tt char* name} (OUT): buffer to copy the name into.
-  \item {\tt size\_t size} (IN): size of the buffer name, if 0, return
+  \item \texttt{char* name} (OUT): buffer to copy the name into.
+  \item \texttt{size\_t size} (IN): size of the buffer name, if 0, return
     only the buffer size needed.
-  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
+  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
     query.
-  \item {\tt void *ref} (IN): the region reference to query.
-  \end{enumerate}
-
-\item {\tt H5VL\_REF\_GET\_REGION}, to retrieve a region reference
-  contained in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt hid\_t *ret\_id} (OUT): buffer for the dataspace created
+  \item \texttt{void *ref} (IN): the region reference to query.
+  \end{enumerate}
+
+\item \texttt{H5VL\_REF\_GET\_REGION}, to retrieve a region reference
+  contained in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the dataspace created
     from the region reference.
-  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference
-    (should be {\tt H5R\_DATASET\_REGION}).
-  \item {\tt void *ref} (IN): the region reference to open.
-  \end{enumerate}
-
-\item {\tt H5VL\_REF\_GET\_TYPE}, to retrieve object type a reference
+  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference
+    (should be \texttt{H5R\_DATASET\_REGION}).
+  \item \texttt{void *ref} (IN): the region reference to open.
+  \end{enumerate}
+
+\item \texttt{H5VL\_REF\_GET\_TYPE}, to retrieve object type a reference
   points to:
   \begin{enumerate}
-  \item {\tt H5O\_type\_t *type} (OUT): buffer to return the object type.
-  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
+  \item \texttt{H5O\_type\_t *type} (OUT): buffer to return the object type.
+  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
     query.
-  \item {\tt void *ref} (IN): the region reference to query.
+  \item \texttt{void *ref} (IN): the region reference to query.
   \end{enumerate}
@@
 
-The {\tt specific} callback in the object class implements specific operations on HDF5 objects as specified in the {\tt
-  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.
-
+The \texttt{specific} callback in the object class implements specific operations on HDF5 objects as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The location object  where the operation needs to happen.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
-  {\tt specific\_type} & (IN): The type of the operation.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt specific\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_OBJECT\_CHANGE\_REF\_COUNT}, to update the reference
-  count for the object in {\tt obj}:
-  \begin{enumerate}
-  \item {\tt int ref\_count} (IN): reference count to set on the object.
-  \end{enumerate}
-
-\item {\tt H5VL\_OBJECT\_EXISTS}, to check if an object with name
-  specified in {\tt loc\_params} (type {\tt H5VL\_OBJECT\_BY\_NAME})
+\item \texttt{H5VL\_OBJECT\_CHANGE\_REF\_COUNT}, to update the reference
+  count for the object in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{int ref\_count} (IN): reference count to set on the object.
+  \end{enumerate}
+
+\item \texttt{H5VL\_OBJECT\_EXISTS}, to check if an object with name
+  specified in \texttt{loc\_params} (type \texttt{H5VL\_OBJECT\_BY\_NAME})
   exists:
   \begin{enumerate}
-  \item {\tt htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
-  \end{enumerate}
-
-\item {\tt H5VL\_OBJECT\_VISIT}, to iterate over all objects starting at the location provided and call a user specified callback on each one:
-  \begin{enumerate}
-  \item {\tt H5\_index\_t idx\_type} (IN): Type of index.\\
-  \item {\tt H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
-  \item {\tt H5O\_iterate\_t op} (IN): User-defined function to pass each object to. \\
-  \item {\tt void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
-  \end{enumerate}
-
-\item {\tt H5VL\_REF\_CREATE}, to create a reference of an object
-  under the location object {\tt obj}:
-  \begin{enumerate}
-  \item {\tt void *ref} (OUT): the region reference created.
-  \item {\tt char* name} (IN): Name of the object at the location {\tt
-      obj}.
-  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference to
+  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
+  \end{enumerate}
+
+\item \texttt{H5VL\_OBJECT\_VISIT}, to iterate over all objects starting at the location provided and call a user-specified callback on each one:
+  \begin{enumerate}
+  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
+  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
+  \item \texttt{H5O\_iterate\_t op} (IN): User-defined function to pass each object to. \\
+  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
+  \end{enumerate}
+
+\item \texttt{H5VL\_REF\_CREATE}, to create a reference of an object
+  under the location object \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{void *ref} (OUT): the region reference created.
+  \item \texttt{char* name} (IN): Name of the object at the location \texttt{obj}.
+  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
     create.
-  \item {\tt hid\_t* space\_id} (IN): Dataspace identifier with
+  \item \texttt{hid\_t* space\_id} (IN): Dataspace identifier with
     selection. Used only for dataset region references; passed as -1 if
-    reference is an object reference, i.e., of type {\tt H5R\_OBJECT}.
+    reference is an object reference, i.e., of type \texttt{H5R\_OBJECT}.
   \end{enumerate}
@@
 
-The {\tt optional} callback in the object class implements plugin specific operations on an HDF5 object. It returns an {\tt
-  herr\_t} indicating success or failure.
-
+The \texttt{optional} callback in the object class implements plugin specific operations on an HDF5 object. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-
-Each plugin should be able to parse the {\tt va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
 
@@
 map to one of the link callback routines in this class that the
-plugin needs to implement:
-
-\begin{lstlisting}
+plugin needs to implement, Listing \ref{lst:H5Lclass}.
+
+\begin{lstlisting}[caption={Structure for link callback routines, H5VLpublic.h}, captionpos=b, label={lst:H5Lclass}]
 typedef struct H5VL_link_class_t {
@@
 
-The {\tt create} callback in the group class should create a hard,
+The \texttt{create} callback in the group class creates a hard,
 soft, external, or user-defined links in the container. It returns an
-{\tt herr\_t} indicating success or failure.
-
+\texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 
-The {\tt create\_type} argument is an {\tt enum}:
+The \texttt{create\_type} argument is an \texttt{enum}:
 \begin{lstlisting}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt create\_type} & (IN): type of the link to be created.\\
-  {\tt obj} & (IN): Pointer to an object where the link needs to be
+  \texttt{create\_type} & (IN): type of the link to be created.\\
+  \texttt{obj} & (IN): Pointer to an object where the link needs to be
   created from.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in
+  \texttt{loc\_params} & (IN): The location parameters as explained in
   section~\ref{sec:map} for the source object. \\
-  {\tt lcpl\_id} & (IN): The link creation property list. It contains
+  \texttt{lcpl\_id} & (IN): The link creation property list. It contains
   all the link creation properties in addition to other API parameters
   depending on the creation type, which will be detailed next.\\
-  {\tt lapl\_id} & (IN): The link access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-As mentioned in the argument list, the {\tt lcpl\_id} contains the
+  \texttt{lapl\_id} & (IN): The link access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+As mentioned in the argument list, the \texttt{lcpl\_id} contains the
 parameters for the link creation operation depending on the creation
@@
 \begin{itemize}
-\item {\tt H5VL\_LINK\_CREATE\_HARD} contains two properties:
-  \begin{enumerate}
-  \item {\tt H5VL\_LINK\_TARGET} (with type {\tt void*}): The target
+\item \texttt{H5VL\_LINK\_CREATE\_HARD} contains two properties:
+  \begin{enumerate}
+  \item \texttt{H5VL\_LINK\_TARGET} (with type \texttt{void*}): The target
     object where the hard link needs to be created to.
-  \item {\tt H5VL\_LINK\_TARGET\_LOC\_PARAMS} (with type {\tt
-      H5VL\_loc\_params\_t}): The location parameters as explained in
+  \item \texttt{H5VL\_LINK\_TARGET\_LOC\_PARAMS} (with type \texttt{H5VL\_loc\_params\_t}): The location parameters as explained in
     section~\ref{sec:map} for the target object.
@@
 
-\item {\tt H5VL\_LINK\_CREATE\_SOFT} contains one property:
-  \begin{enumerate}
-  \item {\tt H5VL\_LINK\_TARGET\_NAME} (with type {\tt char*}): The target
+\item \texttt{H5VL\_LINK\_CREATE\_SOFT} contains one property:
+  \begin{enumerate}
+  \item \texttt{H5VL\_LINK\_TARGET\_NAME} (with type \texttt{char*}): The target
     link where the soft link should point to.
@@
 
-\item {\tt H5VL\_LINK\_CREATE\_UD} contains two properties:
-  \begin{enumerate}
-  \item {\tt H5VL\_LINK\_TYPE} (with type {\tt H5L\_type\_t}): The
-    user defined link class. {\tt H5L\_TYPE\_EXTERNAL} suggests an
+\item \texttt{H5VL\_LINK\_CREATE\_UD} contains two properties:
+  \begin{enumerate}
+  \item \texttt{H5VL\_LINK\_TYPE} (with type \texttt{H5L\_type\_t}): The
+    user defined link class. \texttt{H5L\_TYPE\_EXTERNAL} suggests an
     external link is to be created.
-  \item {\tt H5VL\_LINK\_UDATA} (with type {\tt void*}): User supplied
+  \item \texttt{H5VL\_LINK\_UDATA} (with type \texttt{void*}): User supplied
     link information (contains the external link buffer for external
     links). 
-  \item {\tt H5VL\_LINK\_UDATA\_SIZE} (with type {\tt size\_t}): size
-    of the {\tt udata} buffer. 
+  \item \texttt{H5VL\_LINK\_UDATA\_SIZE} (with type \texttt{size\_t}): size
+    of the \texttt{udata} buffer. 
   \end{enumerate}
@@
 
-The {\tt move} callback in the link class should move a link within the HDF5 container. It returns an {\tt herr\_t} indicating success or failure.
-
+The \texttt{move} callback in the link class moves a link within the HDF5 container. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt src\_obj} & (IN): original/source object or file. \\
-  {\tt loc\_params1} & (IN): The location parameters for the source
-  object as explained in section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
-  {\tt dst\_obj} & (IN): destination object or file. \\
-  {\tt loc\_params1} & (IN): The location parameters for the destination
-  object as explained in section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
-  {\tt lcpl\_id} & (IN): The link creation property list.\\
-  {\tt lapl\_id} & (IN): The link access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt copy} callback in the link class should copy a link within the HDF5 container. It returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{src\_obj} & (IN): original/source object or file. \\
+  \texttt{loc\_params1} & (IN): The location parameters for the source
+  object as explained in section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
+  \texttt{dst\_obj} & (IN): destination object or file. \\
+  \texttt{loc\_params1} & (IN): The location parameters for the destination
+  object as explained in section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
+  \texttt{lcpl\_id} & (IN): The link creation property list.\\
+  \texttt{lapl\_id} & (IN): The link access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{copy} callback in the link class copies a link within the HDF5 container. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt src\_obj} & (IN): original/source object or file. \\
-  {\tt loc\_params1} & (IN): The location parameters for the source
-  object as explained in section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
-  {\tt dst\_obj} & (IN): destination object or file. \\
-  {\tt loc\_params1} & (IN): The location parameters for the destination
-  object as explained in section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_NAME} in this callback. \\
-  {\tt lcpl\_id} & (IN): The link creation property list.\\
-  {\tt lapl\_id} & (IN): The link access property list.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-
-The {\tt get} callback in the link class should retrieve information
-about links as specified in the {\tt get\_type} parameter. It
-returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{src\_obj} & (IN): original/source object or file. \\
+  \texttt{loc\_params1} & (IN): The location parameters for the source
+  object as explained in section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
+  \texttt{dst\_obj} & (IN): destination object or file. \\
+  \texttt{loc\_params1} & (IN): The location parameters for the destination
+  object as explained in section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
+  \texttt{lcpl\_id} & (IN): The link creation property list.\\
+  \texttt{lapl\_id} & (IN): The link access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{get} callback in the link class retrieves information
+about links as specified in the \texttt{get\_type} parameter. It
+returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The file or group object where information needs to be
+  \texttt{obj} & (IN): The file or group object where information needs to be
   retrieved from.\\
-  {\tt loc\_params} & (IN): The location parameters for the source
-  object as explained in section~\ref{sec:map}. The type can be only {\tt
-    H5VL\_OBJECT\_BY\_NAME} or {\tt H5VL\_OBJECT\_BY\_IDX} in this
+  \texttt{loc\_params} & (IN): The location parameters for the source
+  object as explained in section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} or \texttt{H5VL\_OBJECT\_BY\_IDX} in this
   callback.\\ 
-  {\tt get\_type} & (IN): The type of the information to retrieve.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt get\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_LINK\_GET\_INFO}, to retrieve the link info from the
-  link specified in the {\tt loc\_params}:
-  \begin{enumerate}
-  \item {\tt H5L\_info\_t linfo} (OUT): pointer to info structure to
+\item \texttt{H5VL\_LINK\_GET\_INFO}, to retrieve the link info from the
+  link specified in the \texttt{loc\_params}:
+  \begin{enumerate}
+  \item \texttt{H5L\_info\_t linfo} (OUT): pointer to info structure to
     fill.
@@
 
-\item {\tt H5VL\_LINK\_GET\_NAME}, to retrieve the name of the link
-  specified by the index information in {\tt loc\_params} ({\tt
-    loc\_params} is of type {\tt H5VL\_OBJECT\_BY\_IDX} only with this
+\item \texttt{H5VL\_LINK\_GET\_NAME}, to retrieve the name of the link
+  specified by the index information in \texttt{loc\_params} (\texttt{loc\_params} is of type \texttt{H5VL\_OBJECT\_BY\_IDX} only with this
   type):
   \begin{enumerate}
-  \item {\tt char* name} (OUT): buffer to copy the name into.
-  \item {\tt size\_t size} (IN): size of the buffer name, if 0, return
+  \item \texttt{char* name} (OUT): buffer to copy the name into.
+  \item \texttt{size\_t size} (IN): size of the buffer name, if 0, return
     only the buffer size needed.
-  \item {\tt ssize\_t *ret} (OUT): buffer to return the length of the
+  \item \texttt{ssize\_t *ret} (OUT): buffer to return the length of the
     link name.
@@
 
-\item {\tt H5VL\_LINK\_GET\_VAL}, to retrieve the link value from the
-  link specified in the {\tt loc\_params}:
-  \begin{enumerate}
-  \item {\tt void *buf} (OUT): buffer to put the value into.
-  \item {\tt size\_t size} (IN): size of the passed in buffer.
+\item \texttt{H5VL\_LINK\_GET\_VAL}, to retrieve the link value from the
+  link specified in the \texttt{loc\_params}:
+  \begin{enumerate}
+  \item \texttt{void *buf} (OUT): buffer to put the value into.
+  \item \texttt{size\_t size} (IN): size of the passed in buffer.
   \end{enumerate}
@@
 
-The {\tt specific} callback in the link class implements specific operations on HDF5 links as specified in the {\tt
-  specific\_type} parameter. It returns an {\tt herr\_t} indicating success or failure.
-
+The \texttt{specific} callback in the link class implements specific operations on HDF5 links as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The location object  where the operation needs to happen.\\
-  {\tt loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
-  {\tt specific\_type} & (IN): The type of the operation.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and
+  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
   output pointers for the get operation. \\
 \end{tabular}
-
-The {\tt arguments} argument contains a variable list of arguments
-depending on the {\tt specific\_type} parameter. The following list shows
-the argument list, in-order, for each type:
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
 
 \begin{itemize}
-\item {\tt H5VL\_LINK\_DELETE}, to remove a link specified in the location parameter from an HDF5 container.
-
-\item {\tt H5VL\_LINK\_EXITS}, to determine whether the link specified
-  in the {\tt loc\_params} exits ({\tt loc\_params} is of type {\tt
-    H5VL\_OBJECT\_BY\_NAME} only with this type):
-  \begin{enumerate}
-  \item {\tt htri\_t *ret} (OUT): buffer for the existence of the link
+\item \texttt{H5VL\_LINK\_DELETE}, to remove a link specified in the location parameter from an HDF5 container.
+
+\item \texttt{H5VL\_LINK\_EXITS}, to determine whether the link specified
+  in the \texttt{loc\_params} exits (\texttt{loc\_params} is of type \texttt{H5VL\_OBJECT\_BY\_NAME} only with this type):
+  \begin{enumerate}
+  \item \texttt{htri\_t *ret} (OUT): buffer for the existence of the link
     (0 for no, 1 for yes).
@@
 
-\item {\tt H5VL\_LINK\_ITER}, to iterate over all links starting at the location provided and call a user specified callback on each one:
-  \begin{enumerate}
-  \item {\tt hbool\_t recursive} (IN): whether to recursively follow links into subgroups of the specified group.\\
-  \item {\tt H5\_index\_t idx\_type} (IN): Type of index.\\
-  \item {\tt H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
-  \item {\tt hsize\_t *idx} (IN/OUT):  iteration position where to start and return position where an interrupted iteration may restart.\\
-  \item {\tt H5L\_iterate\_t op} (IN): User-defined function to pass each link to. \\
-  \item {\tt void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
+\item \texttt{H5VL\_LINK\_ITER}, to iterate over all links starting at the location provided and call a user-specified callback on each one:
+  \begin{enumerate}
+  \item \texttt{hbool\_t recursive} (IN): whether to recursively follow links into subgroups of the specified group.\\
+  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
+  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
+  \item \texttt{hsize\_t *idx} (IN/OUT):  iteration position where to start and return position where an interrupted iteration may restart.\\
+  \item \texttt{H5L\_iterate\_t op} (IN): User-defined function to pass each link to. \\
+  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
   \end{enumerate}
@@
 
-The {\tt optional} callback in the link class implements plugin specific operations on an HDF5 link. It returns an {\tt
-  herr\_t} indicating success or failure.
-
+The \texttt{optional} callback in the link class implements plugin specific operations on an HDF5 link. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 was added nevertheless to handle an asynchronous API that might be
-added in the future:
-
-\begin{lstlisting}
+added in the future, Listing \ref{lst:Asyncclass}.
+
+\begin{lstlisting}[caption={Structure for async callback routines, H5VLpublic.h}, captionpos=b, label={lst:Asyncclass}]
 typedef struct H5VL_async_class_t {
@@
 
-The {\tt H5ES\_status\_t} argument is an {\tt enum}:
+The \texttt{H5ES\_status\_t} argument is an \texttt{enum}:
 \begin{lstlisting}
@@
 
-The {\tt cancel} callback attempts to cancel an asynchronous operation
-and returns an {\tt herr\_t} indicating success or failure.
-
+The \texttt{cancel} callback attempts to cancel an asynchronous operation
+and returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt req} & (IN): A pointer to the asynchronous request.\\
-  {\tt status} & (OUT): result of the cancel operation.\\
-\end{tabular}
-
-The {\tt test} callback tests an asynchronous operation completion
-and returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{req} & (IN): A pointer to the asynchronous request.\\
+  \texttt{status} & (OUT): result of the cancel operation.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{test} callback tests an asynchronous operation completion
+and returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt req} & (IN): A pointer to the asynchronous request.\\
-  {\tt status} & (OUT): result of the test operation.\\
-\end{tabular}
-
-The {\tt wait} callback waits for an asynchronous operation completion
-and returns an {\tt herr\_t} indicating success or failure.
-
+  \texttt{req} & (IN): A pointer to the asynchronous request.\\
+  \texttt{status} & (OUT): result of the test operation.\\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{wait} callback waits for an asynchronous operation completion
+and returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt req} & (IN): A pointer to the asynchronous request.\\
-  {\tt status} & (OUT): result of the wait operation.\\
-\end{tabular}
+  \texttt{req} & (IN): A pointer to the asynchronous request.\\
+  \texttt{status} & (OUT): result of the wait operation.\\
+\end{tabular}
+\end{mdframed}
 
@@
 
-The {\tt optional} callback has the following definition. It returns an {\tt herr\_t} indicating success or failure.
-
+The \texttt{optional} callback has the following definition. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
 \textbf{Signature:}
@@
 \begin{tabular}{l p{10cm}}
-  {\tt obj} & (IN): The container or object where the operation needs to happen.\\
-  {\tt dxpl\_id} & (IN): The data transfer property list.\\
-  {\tt req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  {\tt arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
 

### 2018-01-10 RFCs/HDF5/VOL/user_guide/stacking.tex
add example
Former-commit-id: 06d8b556668e3dd53df67be09620df7dc29f6629
updated LateX and general editing of document
Former-commit-id: 2e4326ee524db559b5b9ab32ee07a03caa786f9a

@@
 \subsection{Stacking Plugins on Top of Each Other}
-It would be also possible to stack VOL plugins on top of each
+It would also be possible to stack VOL plugins on top of each
 other. This notion is similar to the idea of the split VFD, where
@@
 \centering
-\includegraphics[width=90mm]{stacked.jpg}
+\includegraphics[scale=0.75]{stacked.jpg}
 \caption{Stacked VOL plugins.}
@@
 HDF5 API calls are forwarded through a mirror plugin to two or more
-VOL plugins. This is an extention to the stacking
+VOL plugins. This is an extension to the stacking
 feature. Figure~\ref{fig:mirror} shows an example of a VOL mirror that
@@
 \centering
-\includegraphics[width=90mm]{mirrored.jpg}
+\includegraphics[scale=0.75]{mirrored.jpg}
 \caption{Mirrored VOL plugins.}
@@
 gathers information on HDF5 API calls and records statistics
-associated with the number of calls to a specific API functions and
+associated with the number of calls to specific API functions and
 corresponding parameters. This plugin would be very useful for
@@
 
-\subsection{Implementing Stacked and Mirrored Plugins}
+\subsection{Implementing Stacked \& Mirrored Plugins}
 A new set of API calls that map directly to the VOL callbacks have
@@
 Then the mirror plugin creates a structure containing the pointers for the containers returned from both underlying plugins and returns a pointer to that structure as the output of the file create callback.
-Subsequent access to the container created would receive as input the structure with the two files and would again call the the public VOL routines twice for each plugin with its corresponding file object and combine the output as needed.
+Subsequent access to the container created would receive as input the structure with the two files and would again call the public VOL routines twice for each plugin with its corresponding file object and combine the output as needed.
 
-MSC - refer to an appendix for an example?
+Appendix~\ref{sec:A} show an example on how to stack a simple plugin that does a printf of the VOL operation on top of the native HDF5 plugin.
 

### 2018-01-11 RFCs/HDF5/VOL/user_guide/appendix.tex
updated LateX and general editing of document
Former-commit-id: 2e4326ee524db559b5b9ab32ee07a03caa786f9a
misc. doc changes
Former-commit-id: 06e7d1ed7bd432a0564b1d363fe2435226459869

@@
-\appendix
-\section{VOL Plugin Example}
+\begin{appendices}
+\section{\\VOL Plugin Example}
 \label{sec:A}
@@
 
+\section{\\Listing of Direct Mapping to VOL Callback APIs}
+\label{sec:B}
+
+\begin{lstlisting}
+/* ATTRIBUTE OBJECT ROUTINES */
+void *H5VLattr_create(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *attr_name, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
+void *H5VLattr_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t aapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLattr_read(void *attr, hid_t plugin_id, hid_t dtype_id, void *buf, hid_t dxpl_id, void **req);
+herr_t H5VLattr_write(void *attr, hid_t plugin_id, hid_t dtype_id, const void *buf, hid_t dxpl_id, void **req);
+herr_t H5VLattr_get(void *obj, hid_t plugin_id, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLattr_specific(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLattr_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLattr_close(void *attr, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* DATASET OBJECT ROUTINES */
+void *H5VLdataset_create(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
+void *H5VLdataset_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLdataset_read(void *dset, hid_t plugin_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, void *buf, void **req);
+herr_t H5VLdataset_write(void *dset, hid_t plugin_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
+herr_t H5VLdataset_get(void *dset, hid_t plugin_id, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdataset_specific(void *obj, hid_t plugin_id, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdataset_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdataset_close(void *dset, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* DATATYPE OBJECT ROUTINES */
+void *H5VLdatatype_commit(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
+void *H5VLdatatype_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLdatatype_get(void *dt, hid_t plugin_id, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdatatype_specific(void *obj, hid_t plugin_id, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdatatype_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdatatype_close(void *dt, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* FILE OBJECT ROUTINES */
+void *H5VLfile_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
+void *H5VLfile_open(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLfile_get(void *file, hid_t plugin_id, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLfile_specific(void *obj, hid_t plugin_id, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLfile_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLfile_close(void *file, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* GROUP OBJECT ROUTINES */
+void *H5VLgroup_create(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
+void *H5VLgroup_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLgroup_get(void *obj, hid_t plugin_id, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLgroup_specific(void *obj, hid_t plugin_id, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLgroup_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLgroup_close(void *grp, hid_t plugin_id, hid_t dxpl_id, void **req);
+
+/* LINK OBJECT ROUTINES */
+herr_t H5VLlink_create(H5VL_link_create_type_t create_type, void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLlink_copy(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t plugin_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLlink_move(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t plugin_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLlink_get(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLlink_specific(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLlink_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+
+/* OBJECT ROUTINES */
+void *H5VLobject_open(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
+herr_t H5VLobject_copy(void *src_obj, H5VL_loc_params_t loc_params1, hid_t plugin_id1, const char *src_name,                      void *dst_obj, H5VL_loc_params_t loc_params2, hid_t plugin_id2, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
+herr_t H5VLobject_get(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLobject_specific(void *obj, H5VL_loc_params_t loc_params, hid_t plugin_id, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLobject_optional(void *obj, hid_t plugin_id, hid_t dxpl_id, void **req, va_list arguments);
+
+/* ASYNCHRONOUS ROUTINES */
+herr_t H5VLrequest_cancel(void **req, hid_t plugin_id, H5ES_status_t *status);
+herr_t H5VLrequest_test(void **req, hid_t plugin_id, H5ES_status_t *status);
+herr_t H5VLrequest_wait(void **req, hid_t plugin_id, H5ES_status_t *status);
+\end{lstlisting}
+
+\end{appendices}
+
 %%% Local Variables: 

### 2018-01-11 RFCs/HDF5/VOL/user_guide/new_api.tex
misc. doc changes
Former-commit-id: 06e7d1ed7bd432a0564b1d363fe2435226459869

--- 2014-09-10 RFCs/HDF5/VOL/user_guide/new_api.tex
@@
 \section{New VOL API Routines}
+\label{sec:api}
 New API routines have been added to the HDF5 library to manage VOL plugins. This section details each new API call and explains their intended usage.
 
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
 \begin{lstlisting}
-  hid_t H5VLobject_register(void *obj, H5I_type_t obj_type, const H5VL_class_t *cls);
-\end{lstlisting}
-to register an {\tt hid\_t} with an object {\tt obj} associated with
-the VOL plugin of class {\tt cls}. This is needed in all iterate and
-visit callbacks where the plugins internally need to wrap an {\tt
-  hid\_t} around an object to call the user defined operation {\tt op}
-on.
-
-\begin{lstlisting}
-  herr_t H5VLget_object(hid_t obj_id, void **obj, H5VL_t **vol_plugin);
-\end{lstlisting}
-to retrieve the VOL object and plugin structure from an HDF5
-identifier ({\tt hid\_t}). The plugin structure is defined as:
-\begin{lstlisting}
-struct H5VL_t {
-    const H5VL_class_t *cls;     /* constant class info */
-    const char *container_name;  /* name of the underlying storage 
-                                    container */
-    unsigned long feature_flags; /* VOL Driver feature Flags */
-    int nrefs;                   /* number of references by objects
-                                    using this struct */
-};
+hid_t H5VLregister(const H5VL_class_t *cls);
 \end{lstlisting}
 
-% H5_DLL void *H5Pget_vol_info(hid_t plist_id);
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt cls} & (IN): A pointer to the plugin structure to register.\\
+\end{tabular}
+\end{mdframed}
+
+Registers a user defined VOL plugin with the HDF5 library and returns an identifier for that plugin to be used if successful, otherwise returns a negative value.
+This function is used when the application has direct access to the plugin it wants to use and is able to obtain a pointer for the plugin structure to pass to the HDF5 library.
+The plugin must be unregistered before the application exists with {\texttt H5VLunregister()}.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+hid_t H5VLregister_by_name(const char *plugin_name);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt name} & (IN): The plugin name to search for an register.\\
+\end{tabular}
+\end{mdframed}
+Registers a VOL plugin with the HDF5 library given the name of the plugin and returns an identifier for that plugin to be used if successful, otherwise returns a negative value.
+If the plugin is already registered the library will create an identifier for it and returns it to the user; otherwise the library will look for available third party plugins and dynamically load them and registers them for use, then returns an identifier for the plugin.
+Third party plugins must be installed on the system as a shared library or DLL.
+The plugin must be unregistered before the application exists with {\tt H5VLunregister()}.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+herr_t H5VLunregister(hid_t plugin_id);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt plugin\_id} & (IN): A valid identifier of the plugin to unregister.\\
+\end{tabular}
+\end{mdframed}
+Unregisters a plugin from the library and return a positive value on success otherwise return a negative value.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+htri_t H5VLis_registered(const char *name);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt name} & (IN): The plugin name to check for.\\
+\end{tabular}
+\end{mdframed}
+Checks if a VOL plugin is registered with the library given the plugin name and returns TRUE/FALSE on success, otherwise it returns a negative value.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+ssize_t H5VLget_plugin_name(hid_t obj_id, char *name/*out*/, size_t size);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt obj\_id} & (IN): The object identifier to check.\\
+  {\tt name} & (OUT): Buffer pointer to put the plugin name. If NULL, the library just returns the size required to store the plugin name.\\
+  {\tt size} & (IN): the size of the passed in buffer.\\
+\end{tabular}
+\end{mdframed}
+Retrieves the name of a VOL plugin given and object identifier that was created/opened with it. On success, the name length is returned.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+hid_t H5VLget_plugin_id(const char *name);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt name} & (IN): The plugin name to check for.\\
+\end{tabular}
+\end{mdframed}
+Given a plugin name that is registered with the library, this function returns an identifier for the plugin.
+If the plugin is not registered with the library, a negative value is returned.
+The identifier must be released with a call to {\tt H5VLclose()}.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+herr_t H5VLclose(hid_t plugin_id);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt plugin\_id} & (IN): A valid identifier of the plugin to close.\\
+\end{tabular}
+\end{mdframed}
+Shuts down access to the plugin that the identifier points to and release resources associated with it.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  hid_t H5VLobject_register(void *obj, H5I_type_t obj_type, hid_t plugin_id);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt obj} & (IN): pointer to the object to register.\\
+ {\tt obj\_type} & (IN): The type of the object ({\tt H5I\_FILE, H5I\_DATASET, H5I\_GROUP, H5I\_ATTRIBUTE, H5I\_DATATYPE}).\\
+ {\tt plugin\_id} & (IN): identifier of the vol plugin the object is associated with.\\
+\end{tabular}
+\end{mdframed}
+Creates an HDF5 identifier for an object given its type and an identifier of the plugin that was used in creating it.
+This function is typically used by external plugins wanting to wrap an {\tt hid\_t} around a plugin specific object to return to a user callback for functions like {\tt H5Literate, H5Lvisit, H5Ovisit, H5Aiterate} etc...
+A Negative value is returned on failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  herr_t H5VLget_object(hid_t obj_id, void **obj); 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt obj\_id} & (IN): identifier of the object to dereference.\\
+ {\tt obj} & (OUT): buffer to store the pointer of the VOL object associated with the object identifier.\\
+\end{tabular}
+\end{mdframed}
+Retrieves a pointer to the VOL object from an HDF5 file or object identifier.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+herr_t H5VLinitialize(hid_t plugin_id, hid_t vipl_id);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt plugin\_id} & (IN): identifier of VOL plugin to initialize.\\
+ {\tt vipl\_id} & (IN): VOL initialize property list containing properties required for plugin initialization.\\
+\end{tabular}
+\end{mdframed}
+Initializes access to the VOL plugin represented by {\tt plugin\_id} with initialization parameters set as properties in the the property list {\tt vipl\_id}.
+Some plugins may not require initialization.
+For more information about plugin initialization and what properties are required to be set in the property list refer to the actual plugin documentation.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+herr_t H5VLterminate(hid_t plugin_id, hid_t vtpl_id);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt plugin\_id} & (IN): identifier of VOL plugin to terminate.\\
+ {\tt vtpl\_id} & (IN): VOL terminate property list containing properties required for plugin termination.\\
+\end{tabular}
+\end{mdframed}
+Terminates access to the VOL plugin represented by {\tt plugin\_id} with termination parameters set as properties in the the property list {\tt vtpl\_id}.
+Some plugins may not require termination.
+For more information about plugin termination and what properties are required to be set in the property list refer to the actual plugin documentation.
+
+A set of API calls that map directly to the VOL callbacks themselves have been added to aid in the development of stacked or mirrored plugins.
+For more information on usage refer to Section~\ref{sec:stack}.
+The routines are listed in Appendix~\ref{sec:B}.
+
 %%% Local Variables: 

### 2018-01-11 RFCs/HDF5/VOL/user_guide/plugin.tex
misc. doc changes
Former-commit-id: 06e7d1ed7bd432a0564b1d363fe2435226459869

@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{name} & (IN): The name of the container to be created.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{name} & (IN): The name of the container to open.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): The container or object where information needs to be
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): The container or object where the operation needs
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{file} & (IN): Pointer to the file.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): Pointer to an object where the group needs
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
   \texttt{name} & (IN): The name of the group to be created.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): Pointer to an object where the group needs to be
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
   \texttt{name} & (IN): The name of the group to be opened.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): The group object where information needs to be
@@
   \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
-    explained in section~\ref{sec:map}. 
+    explained in Section~\ref{sec:map}. 
   \item \texttt{H5G\_info\_t *ginfo} (OUT): info structure to fill the
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{group} & (IN): Pointer to the group object.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): Pointer to an object where the dataset needs
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
   \texttt{name} & (IN): The name of the dataset to be created.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): Pointer to an object where the dataset needs to be
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
   \texttt{name} & (IN): The name of the dataset to be opened.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{dset} & (IN): Pointer to the dataset object.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{dset} & (IN): The dataset object where information needs to be
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): The dset  where the operation needs
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): Pointer to an object where the attribute needs
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}.\\
+  Section~\ref{sec:map}.\\
   \texttt{attr\_name} & (IN): The name of the attribute to be created.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): Pointer to an object where the attribute needs to be
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}.\\
+  Section~\ref{sec:map}.\\
   \texttt{attr\_name} & (IN): The name of the attribute to be opened.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{attr} & (IN): Pointer to the attribute object.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{attr} & (IN): An attribute or location object where information
@@
   \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
-    explained in section~\ref{sec:map}. 
+    explained in Section~\ref{sec:map}. 
   \item \texttt{H5A\_info\_t *ainfo} (OUT): info structure to fill the
@@
   \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
-    explained in section~\ref{sec:map}. The type could be either
+    explained in Section~\ref{sec:map}. The type could be either
     \texttt{H5VL\_OBJECT\_BY\_SELF} meaning \texttt{obj} is the attribute,
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in section~\ref{sec:map}.\\
+  \texttt{loc\_params} & (IN): The location parameters as explained in Section~\ref{sec:map}.\\
   \texttt{specific\_type} & (IN): The type of the operation.\\
@@
   \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
-    explained in section~\ref{sec:map}.
+    explained in Section~\ref{sec:map}.
   \item \texttt{char *attr\_name} (IN): the attribute name to check.
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): Pointer to an object where the datatype needs
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
+  Section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
   \texttt{name} & (IN): The name of the datatype to be created.\\
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
+  Section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
   \texttt{name} & (IN): The name of the datatype to be opened.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): Pointer to the named datatype object.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): The named datatype to retrieve information from.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{dt} & (IN): Pointer to the datatype object.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): Pointer to a file or group where the objecy needs to be
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map}.\\
+  Section~\ref{sec:map}.\\
   \texttt{opened\_type} & (OUT): buffer to return the type of the object
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{src\_obj} & (IN): Pointer to location of the source object to
@@
   \texttt{loc\_params1} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
+  Section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
   \texttt{src\_name} & (IN): Name of the source object to
@@
   \texttt{loc\_params2} & (IN): The location parameters as explained in
-  section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
+  Section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
   \texttt{dst\_name} & (IN): Name to be assigned to the new copy.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): A location object where information needs to be
@@
   \texttt{loc\_params} & (IN): The location parameters as
-  explained in section~\ref{sec:map}.\\
+  explained in Section~\ref{sec:map}.\\
   \texttt{get\_type} & (IN): The type of the information to retrieve.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{create\_type} & (IN): type of the link to be created.\\
@@
   \texttt{loc\_params} & (IN): The location parameters as explained in
-  section~\ref{sec:map} for the source object. \\
+  Section~\ref{sec:map} for the source object. \\
   \texttt{lcpl\_id} & (IN): The link creation property list. It contains
@@
   \item \texttt{H5VL\_LINK\_TARGET\_LOC\_PARAMS} (with type \texttt{H5VL\_loc\_params\_t}): The location parameters as explained in
-    section~\ref{sec:map} for the target object.
+    Section~\ref{sec:map} for the target object.
   \end{enumerate}
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{src\_obj} & (IN): original/source object or file. \\
   \texttt{loc\_params1} & (IN): The location parameters for the source
-  object as explained in section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
+  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
   \texttt{dst\_obj} & (IN): destination object or file. \\
   \texttt{loc\_params1} & (IN): The location parameters for the destination
-  object as explained in section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
+  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
   \texttt{lcpl\_id} & (IN): The link creation property list.\\
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{obj} & (IN): The file or group object where information needs to be
@@
   \texttt{loc\_params} & (IN): The location parameters for the source
-  object as explained in section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} or \texttt{H5VL\_OBJECT\_BY\_IDX} in this
+  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} or \texttt{H5VL\_OBJECT\_BY\_IDX} in this
   callback.\\ 
@@
 \textbf{Arguments:}\\
-\begin{tabular}{l p{10cm}}
+\begin{tabular}{l p{13.5cm}}
   \texttt{req} & (IN): A pointer to the asynchronous request.\\

### 2019-10-28 RFCs/HDF5/VOL/vol_internals/internal.tex
Moved existing documentation to new locations.
Former-commit-id: 508462df47bf2580fff47c7ce7bef7fc05c1ab6e

--- 2014-09-10 RFCs/HDF5/VOL/user_guide/internal.tex
@@
 \subsection{Implementing an Internal Plugin}
-The first step to implement an internal plugin is to implement all the callbacks defined in the VOL class as described in section~\ref{sec:vol}.
+The first step to implement an internal plugin is to implement all the callbacks defined in the VOL class as described in Section~\ref{sec:vol}.
 After implementing the VOL class, the next step would be to allow users to select

### 2019-10-28 RFCs/HDF5/VOL/vol_internals/intro.tex
Moved existing documentation to new locations.
Former-commit-id: 508462df47bf2580fff47c7ce7bef7fc05c1ab6e

--- 2014-08-28 RFCs/HDF5/VOL/user_guide/intro.tex
@@
 library that intercepts all API calls that could potentially access
-objects in an HDF5 container and forwards those calls to plugin
-''object drivers''. The plugins could store the objects in variety of
+objects in an HDF5 container and forwards those calls to the plugin
+``object drivers''. The plugins could store the objects in a variety of
 ways. A plugin could, for example, have objects be distributed
@@
 native netCDF or HDF4 format). The user still gets the same data model
-where access is done to a single HDF5 “container”; however the plugin
+where access is done to a single HDF5 “container”; however, the plugin
 object driver translates from what the user sees to how the data is
@@
 reader has good knowledge of the VOL architecture obtained by reading
-the VOL architectural design document ~\ref{HERE} MSC-ref. The
+the VOL architectural design document~\cite{vol:rfc}. The
 document will cover the steps needed to create external and internal

### 2019-10-28 RFCs/HDF5/VOL/user_guide/body.tex
Added empty container for user guide.
Former-commit-id: cc05b463de6397bf0a3063a8bd70214255de319f

--- 2014-08-28 RFCs/HDF5/VOL/user_guide/intro.tex
@@
 \section{Introduction}
-The Virtual Object Layer (VOL) is an abstraction layer in the HDF5
-library that intercepts all API calls that could potentially access
-objects in an HDF5 container and forwards those calls to plugin
-''object drivers''. The plugins could store the objects in variety of
-ways. A plugin could, for example, have objects be distributed
-remotely over different platforms, provide a raw mapping of the model
-to the file system, or even store the data in other file formats (like
-native netCDF or HDF4 format). The user still gets the same data model
-where access is done to a single HDF5 “container”; however the plugin
-object driver translates from what the user sees to how the data is
-actually stored. Having this abstraction layer maintains the object
-model of HDF5 and would allow HDF5 developers or users to write their
-own plugins for accessing HDF5 data.
-
-This user guide is for developers interested in developing a VOL
-plugin for the HDF5 library. The document is meant to be used in
-conjunction with the HDF5 reference manual. It is assumed that the
-reader has good knowledge of the VOL architecture obtained by reading
-the VOL architectural design document ~\ref{HERE} MSC-ref. The
-document will cover the steps needed to create external and internal
-VOL plugins. Both ways have a lot of common steps and rules that will
-be covered first.
+COPY TEXT HERE

### 2019-10-28 RFCs/HDF5/VOL/connector_author_guide/new_api.tex
Added sections to the user guide.
Former-commit-id: 15a1ec1be53192de85295747f08219839df562f0

--- 2018-01-11 RFCs/HDF5/VOL/user_guide/new_api.tex
@@
 \begin{lstlisting}
-ssize_t H5VLget_plugin_name(hid_t obj_id, char *name/*out*/, size_t size);
+ssize_t H5VLget_driver_name(hid_t obj_id, char *name/*out*/, size_t size);
 \end{lstlisting}
@@
 \begin{lstlisting}
-hid_t H5VLget_plugin_id(const char *name);
+hid_t H5VLget_driver_id(const char *name);
 \end{lstlisting}

### 2019-10-29 RFCs/HDF5/VOL/user_guide/body.tex
Added sections to the user guide.
Former-commit-id: 15a1ec1be53192de85295747f08219839df562f0
Added tables for native-only and VOL-independent API calls.
Former-commit-id: f9b1d3436ca1dacefc1231aa774a904185353622

@@
 \section{Introduction}
-COPY TEXT HERE
+
+\section{Quickstart}
+\subsection*{Use A VOL-Enabled HDF5 Library}
+\subsection*{Make Sure The VOL Connector Is In The Search Path}
+\subsection*{Update Your Code To Load The Connector}
+
+\section{Loading and Registering Connectors}
+\subsection{VOL Connector Search Path}
+\subsection{Connector-Specific Registration Calls}
+\subsection{\tt H5Pset\_vol()}
+\subsection{Environment Variable}
+
+\section{Adapting HDF5 Software to Use the VOL}
+
+\section{Using VOL Connectors With The HDF5 Command-Line Tools}
+\subsection{Connection Strings}
+\subsection{Connector Compatibility}
+
+\section{Compatibility}
+\subsection{Feature Flags}
+\subsection{List of HDF5 Native VOL API Calls}
+
+These API calls will probably fail when used with terminal VOL connectors other than the native HDF5 file format connector. Their use should be protected in code that uses arbitrary VOL connectors.
+\begin{longtable}{ |>{\raggedright\arraybackslash}p{\linewidth}| }
+    \hline
+    H5Aiterate1 \\
+    \hline
+    H5Ddebug \\
+    H5Dformat\_convert \\
+    H5Dget\_chunk\_index\_type \\
+    H5Dget\_chunk\_info \\
+    H5Dget\_chunk\_info\_by\_coord \\
+    H5Dget\_chunk\_storage\_size \\
+    H5Dget\_num\_chunks \\
+    H5Dread\_chunk H5Dwrite\_chunk \\
+    \hline
+    H5FD* \\
+    \hline
+    H5Fclear\_elink\_file\_cache \\
+    H5Fformat\_convert \\
+    H5Fget\_dset\_no\_attrs\_hint \\
+    H5Fget\_eoa H5Fget\_file\_image \\
+    H5Fget\_filesize \\
+    H5Fget\_free\_sections \\
+    H5Fget\_freespace \\
+    H5Fget\_info1 \\
+    H5Fget\_info2 \\
+    H5Fget\_mdc\_config \\
+    H5Fget\_mdc\_hit\_rate \\
+    H5Fget\_mdc\_image\_info \\
+    H5Fget\_mdc\_logging\_status \\
+    H5Fget\_mdc\_size \\
+    H5Fget\_metadata\_read\_retry\_info \\
+    H5Fget\_mpi\_atomicity \\
+    H5Fget\_page\_buffering\_stats \\
+    H5Fget\_vfd\_handle \\
+    H5Fincrement\_filesize \\
+    H5Fis\_hdf5 \\
+    H5Freset\_mdc\_hit\_rate\_stats \\
+    H5Freset\_page\_buffering\_stats \\
+    H5Fset\_dset\_no\_attrs\_hint \\
+    H5Fset\_latest\_format \\
+    H5Fset\_libver\_bounds \\
+    H5Fset\_mdc\_config \\
+    H5Fset\_mpi\_atomicity \\
+    H5Fstart\_mdc\_logging \\
+    H5Fstart\_swmr\_write \\
+    H5Fstop\_mdc\_logging \\
+    \hline
+    H5Gget\_comment \\
+    H5Giterate \\
+    H5Gset\_comment \\
+    H5Gget\_info \\
+    H5Gget\_info\_by\_name \\
+    H5Gget\_info\_by\_idx \\
+    H5Gget\_objinfo \\
+    H5Gget\_objname\_by\_idx \\
+    H5Gget\_objtype\_by\_idx \\
+    \hline
+    H5Oare\_mdc\_flushes\_disabled \\
+    H5Odisable\_mdc\_flushes \\
+    H5Oenable\_mdc\_flushes \\
+    H5Oget\_comment \\
+    H5Oget\_comment\_by\_name \\
+    H5Oget\_info\_by\_idx1 \\
+    H5Oget\_info\_by\_idx2 \\
+    H5Oget\_info\_by\_name1 \\
+    H5Oget\_info\_by\_name2 \\
+    H5Oget\_info1 \\
+    H5Oget\_info2 \\
+    H5Oset\_comment \\
+    H5Oset\_comment\_by\_name \\
+    \hline
+\caption{Alphabetical list of HDF5 API calls specific to the native VOL connector}
+\end{longtable}
+
+\subsection{List of HDF5 VOL-Independent API Calls}
+
+These HDF5 API calls do not depend on a particular VOL connector being loaded.
+
+\begin{longtable}{ |>{\raggedright\arraybackslash}p{\linewidth}| }
+    \hline
+    H5* \\
+    \hline
+    H5Dfill \\
+    H5Dgather \\
+    H5Diterate \\
+    H5Dscatter \\
+    H5Dvlen\_reclaim \\
+    H5Dvlen\_get\_buf\_size \\
+    \hline
+    H5E* \\
+    H5I* \\
+    \hline
+    H5Lis\_registered \\
+    H5Lregister \\
+    H5Lunpack\_elink\_val \\
+    H5Lunregister \\
+    \hline
+    H5PL* \\
+    H5P* \\
+    H5S* \\
+    H5T* (non-committed) \\
+    H5VL* \\
+    H5Z* \\
+    \hline
+\caption{Alphabetical list of VOL-independent HDF5 API calls}
+\end{longtable}

### 2019-10-31 RFCs/HDF5/VOL/user_guide/body.tex
Added a "preliminary" text box for use throughout the documentation.
Former-commit-id: 71cccf5114725b40d743a242666bbf6cf870c15b
Added preliminary breakdown of HDF5 API calls by VOL callback to the user guide. This will probably get moved to the connector author guide but it can live here for now.
Former-commit-id: 453e70206494496e620482c82b61c797c23bb69d
Corrections to some API calls in the big HDF5 API call to VOL callback table. Marked functions as deprected in all tables.
Former-commit-id: 7ab94fde980b16dc90076056810cbaa38213fa85

@@
 
+\subsection{Specific API Call Substitutions}
+${\tt H5Fis\_hdf5} \rightarrow {\tt H5Fis\_accessible}$
+
+${\tt H5Oget\_info(1|2)} \rightarrow {\tt H5Ofuture\_function\_goes\_here}$
+
 \section{Using VOL Connectors With The HDF5 Command-Line Tools}
@@
 \subsection{Feature Flags}
+\begin{tcolorbox}[colback=yellow!10!white,colframe=red!75!black,title=PRELIMINARY]
+    This feature is under active development and is either incomplete or may change in behavior before the final release.
+\end{tcolorbox}
 \subsection{List of HDF5 Native VOL API Calls}
@@
     \hline
-    H5Aiterate1 \\
+    H5Aget\_num\_attrs (deprecated) \\
+    H5Aiterate1 (deprecated) \\
     \hline
@@
     H5Fget\_freespace \\
-    H5Fget\_info1 \\
+    H5Fget\_info1 (deprecated) \\
     H5Fget\_info2 \\
@@
     H5Fincrement\_filesize \\
-    H5Fis\_hdf5 \\
+    H5Fis\_hdf5 (deprecated) \\
     H5Freset\_mdc\_hit\_rate\_stats \\
@@
     H5Fset\_dset\_no\_attrs\_hint \\
-    H5Fset\_latest\_format \\
+    H5Fset\_latest\_format (deprecated) \\
     H5Fset\_libver\_bounds \\
@@
     \hline
-    H5Gget\_comment \\
-    H5Giterate \\
-    H5Gset\_comment \\
+    H5Gget\_comment (deprecated) \\
+    H5Giterate (deprecated) \\
     H5Gget\_info \\
@@
     H5Gget\_info\_by\_idx \\
-    H5Gget\_objinfo \\
-    H5Gget\_objname\_by\_idx \\
-    H5Gget\_objtype\_by\_idx \\
+    H5Gget\_objinfo (deprecated) \\
+    H5Gget\_objname\_by\_idx (deprecated) \\
+    H5Gget\_objtype\_by\_idx (deprecated) \\
+    H5Gset\_comment (deprecated) \\
     \hline
@@
     H5Oget\_comment\_by\_name \\
-    H5Oget\_info\_by\_idx1 \\
+    H5Oget\_info\_by\_idx1 (deprecated) \\
     H5Oget\_info\_by\_idx2 \\
-    H5Oget\_info\_by\_name1 \\
+    H5Oget\_info\_by\_name1 (deprecated) \\
     H5Oget\_info\_by\_name2 \\
-    H5Oget\_info1 \\
+    H5Oget\_info1 (deprecated) \\
     H5Oget\_info2 \\
@@
     H5Dscatter \\
-    H5Dvlen\_reclaim \\
+    H5Dvlen\_reclaim (deprecated) \\
     H5Dvlen\_get\_buf\_size \\
@@
 \end{longtable}
+
+\subsection{List of HDF5 API Calls By Callback}
+
+\begin{longtable}{ |l|>{\raggedright\arraybackslash}l| }
+    \hline
+    \multicolumn{1}{|c|}{VOL Callback} & \multicolumn{1}{|c|}{HDF5 API Call} \\
+    \hline
+    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}FILE} \\
+    \hline
+    create & H5Fcreate \\
+    \hline
+    open & H5Fopen \\
+    \hline
+    get & H5Fget\_access\_plist \\
+        & H5Fget\_create\_plist \\
+        & H5Fget\_fileno \\
+        & H5Fget\_intent \\
+        & H5Fget\_name \\
+        & H5Fget\_obj\_count \\
+        & H5Fget\_obj\_ids \\
+    \hline
+    specific & H5Fdelete \\
+             & H5Fflush \\
+             & H5Fis\_accessible \\
+             & H5Fis\_hdf5 (deprecated, hard-coded to use native connector) \\
+             & H5Fmount \\
+             & H5Freopen \\
+             & H5Funmount \\
+    \hline
+    close & H5Fclose \\
+    \hline
+    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}GROUP} \\
+    \hline
+    create & H5Gcreate1 (deprecated) \\
+           & H5Gcreate2 \\
+           & H5Gcreate\_anon \\
+    \hline
+    open & H5Gopen1 (deprecated) \\
+         & H5Gopen2 \\
+    \hline
+    get & H5Gget\_create\_plist \\
+        & H5Gget\_info \\
+        & H5Gget\_info\_by\_idx \\
+        & H5Gget\_info\_by\_name \\
+        & H5Gget\_num\_objs (deprecated) \\
+    \hline
+    specific & H5Gflush \\
+             & H5Grefresh \\
+    \hline
+    close & H5Gclose \\
+    \hline
+    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}DATASET} \\
+    \hline
+    create & H5Dcreate1 (deprecated) \\
+           & H5Dcreate2 \\
+    \hline
+    open & H5Dopen1 (deprecated) \\
+         & H5Dopen2 \\
+    \hline
+    read & H5Dread \\
+    \hline
+    write & H5Dwrite \\
+    \hline
+    get & H5Dget\_access\_plist \\
+        & H5Dget\_create\_plist \\
+        & H5Dextend \\
+        & H5Dget\_offset \\
+        & H5Dget\_space \\
+        & H5Dget\_space\_status \\
+        & H5Dget\_storage\_size \\
+        & H5Dget\_type \\
+    \hline
+    specific & H5Dextend (deprecated) \\
+             & H5Dflush \\
+             & H5Drefresh \\
+             & H5Dset\_extent \\
+    \hline
+    close & H5Dclose \\
+    \hline
+    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}OBJECT} \\
+    \hline
+    open & H5Oopen \\
+         & H5Oopen\_by\_addr \\
+         & H5Oopen\_by\_idx \\
+         & H5Oopen\_by\_name \\
+    \hline
+    copy & H5Ocopy \\
+    \hline
+    get & N/A \\
+    \hline
+    specific & H5Odecr\_refcount \\
+             & H5Oexists\_by\_name \\
+             & H5Oflush \\
+             & H5O\_incr\_refcount \\
+             & H5Orefresh \\
+             & H5Ovisit\_by\_name1 (deprecated) \\
+             & H5Ovisit\_by\_name2 \\
+             & H5Ovisit1 (deprecated) \\
+             & H5Ovisit2 \\
+    \hline
+    close & H5Oclose \\
+    \hline
+    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}LINK} \\
+    \hline
+    create & H5Glink (deprecated) \\
+           & H5Glink2 (deprecated) \\
+           & H5Lcreate\_hard \\
+           & H5Lcreate\_soft \\
+           & H5Lcreate\_ud \\
+           & H5Olink \\
+    \hline
+    copy & H5Lcopy \\
+    \hline
+    move & H5Gmove (deprecated) \\
+         & H5Gmove2 (deprecated) \\
+         & H5Lmove \\
+    \hline
+    get & H5Gget\_linkval (deprecated) \\
+        & H5Lget\_info \\
+        & H5Lget\_info\_by\_idx \\
+        & H5Lget\_name\_by\_idx \\
+        & H5Lget\_val \\
+        & H5Lget\_val\_by\_idx \\
+    \hline
+    specific & H5Gunlink (deprecated) \\
+             & H5Ldelete \\
+             & H5Ldelete\_by\_idx \\
+             & H5Lexists \\
+             & H5Literate \\
+             & H5Literate\_by\_name \\
+             & H5Lvisit \\
+             & H5Lvisit\_by\_name \\
+    \hline
+    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}DATATYPE} \\
+    \hline
+    commit & H5Tcommit1 (deprecated) \\
+           & H5Tcommit2 \\
+           & H5Tcommit\_anon \\
+    \hline
+    open & H5Topen1 (deprecated) \\
+         & H5Topen2 \\
+    \hline
+    get & H5Tget\_create\_plist \\
+    \hline
+    specific & H5Tflush \\
+             & H5Trefresh \\
+    \hline
+    close & H5Tclose \\
+    \hline
+    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}ATTRIBUTE} \\
+    \hline
+    create & H5Acreate1 (deprecated) \\
+           & H5Acreate2 \\
+           & H5Acreate\_by\_name \\
+    \hline
+    open & H5Aopen \\
+         & H5Aopen\_by\_idx \\
+         & H5Aopen\_by\_name \\
+         & H5Aopen\_idx (deprecated)\\
+         & H5Aopen\_name (deprecated) \\
+    \hline
+    read & H5Aread \\
+    \hline
+    write & H5Awrite \\
+    \hline
+    get & H5Aget\_get\_create\_plist \\
+        & H5Aget\_info \\
+        & H5Aget\_info\_by\_idx \\
+        & H5Aget\_info\_by\_name \\
+        & H5Aget\_name \\
+        & H5Aget\_name\_by\_idx \\
+        & H5Aget\_space \\
+        & H5Aget\_storage\_size \\
+        & H5Aget\_type \\
+    \hline
+    specific & H5Adelete \\
+             & H5Adelete\_by\_idx \\
+             & H5Adelete\_by\_name \\
+             & H5Aexists \\
+             & H5Aexists\_by\_name \\
+             & H5Aiterate1 (deprecated) \\
+             & H5Aiterate2 \\
+             & H5Aiterate\_by\_name \\
+             & H5Arename \\
+             & H5Arename\_by\_name \\
+    \hline
+    close & H5Aclose \\
+    \hline
+\caption{Breakdown of HDF5 API calls by VOL callback}
+\end{longtable}

### 2019-11-11 RFCs/HDF5/VOL/user_guide/body.tex
Updates to quickstart
Former-commit-id: 8f697d49afbe11de5880ce9643fec3bf577b22a4

@@
 \section{Quickstart}
+
+\subsection*{Read The Documentation For The New VOL Connector}
+
+Many VOL connectors will require specific setup and configuration of both the application and the storage.
+Specific permissions may have to be set, configuration files constructed, and connector-specific setup calls may need to be invoked in the application.
+In many cases, converting software to use a new VOL connector will be more than just a straightforward drop-in replacement done by specifying a name in the VOL plugin environment variable.
+
 \subsection*{Use A VOL-Enabled HDF5 Library}
+
+The virtual object layer was introduced in HDF5 1.12.0, so you will need that version or later to use it.
+The particular configuration of the library (serial vs parallel, thread-safe, debug vs production/release) does not matter.
+The VOL is a fundamental part of the library and cannot be disabled, so any build will do.
+
+On Windows, it's probably best to use the same debug vs release configuration for the application and all libraries in order to avoid C runtime (CRT) issues.
+On pre-2015 versions of Visual Studio, you'll probably also want to stick to the same Visual Studio version (and thus same CRT version) as well.
+
+When working with a debug HDF5 library, it's probably also wise to build with the "memory sanity checking" feature disabled to avoid accidentally clobbering our memory tracking infrastructure when dealing with buffers obtained from the HDF5 library.
+
 \subsection*{Make Sure The VOL Connector Is In The Search Path}
-\subsection*{Update Your Code To Load The Connector}
+
+The default location for all HDF5 plugins is set at configure time when building the HDF5 library. This is true for both CMake and the Autotools.
+
+\textbf{Default locations:}
+
+\begin{tabular}{ l l }
+    POSIX systems: &  {\tt /usr/local/hdf5/lib/plugin} \\
+     & \\
+    Windows: & {\tt \%ALLUSERSPROFILE\%/hdf5/lib/plugin}
+\end{tabular}
+
+These default locations can be overridden by setting the {\tt HDF5\_PLUGIN\_PATH} environment variable.
+There are also public {\tt H5PL} API calls which can be used to add, modify, and remove search paths.
+The library will only look for plugins in the specified plugin paths.
+By default, it will NOT find plugins that are simply located in the same directory as the executable.
+
+\subsection*{Update Your Code To Load And Use A VOL Connector}
+
+How this is done depends on the VOL connector, which may have special API calls for setup or require appropriate configuration files, but the most generic way to modify a program to use a specific VOL connector would be to {\tt use H5Pset\_vol()} to set the VOL connector in the file access property list (fapl) that will be used to open the file.
+
+You will also need to protect any API calls which are only implemented in the native VOL connector as those calls will fail when using a non-native VOL connector.
+See the section entitled "Adapting HDF5 Software to Use the VOL", below.
+A list of native VOL API calls has been included in an appendix.
+
+\subsection*{Optional: Set The VOL Connector Via The Environment Variable}
 
@@
 \subsection{VOL Connector Search Path}
+\subsection{Connector Versioning}
 \subsection{Connector-Specific Registration Calls}
 \subsection{\tt H5Pset\_vol()}
+\subsection{Connector Compatibility}
+
+\thgfuturewarning
+
+\subsection{Connection Strings}
 \subsection{Environment Variable}
+
+The HDF5 library allows specifying a default VOL connector via an environment variable: {\tt HDF5\_VOL\_CONNECTOR}.
+The value of this environment variable should be set to "\textit{vol\_connector\_name $<$parameters$>$}".
+
+This will perform the equivalent of:
+
+\begin{enumerate}
+    \item {\tt H5VLregister\_connector\_by\_name()} using the specified connector name
+    \item {\tt H5VLconnector\_str\_to\_info()} using the specified parameters.
+This will go through the connector we got from the previous step and should return a VOL info struct from the parameter string in the environment variable.
+    \item {\tt H5Pset\_vol()} on the default fapl using the obtained ID and info.
+\end{enumerate}
+
+The environment variable is parsed once, at library startup.
+Since the environment variable scheme just changes the default connector, it can be overridden by subsequent calls to {\tt H5Pset\_vol()}.
+The \textit{$<$parameters$>$} is optional, so for connectors which do not require any special configuration parameters you can just set the environment variable to the name.
 
@@
 \subsection{Specific API Call Substitutions}
-${\tt H5Fis\_hdf5} \rightarrow {\tt H5Fis\_accessible}$
+\subsection*{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}
 
-${\tt H5Oget\_info(1|2)} \rightarrow {\tt H5Ofuture\_function\_goes\_here}$
+{\tt H5Fis\_hdf5()} does not take a file access property list (fapl).
+As this is where the VOL connector is specified, this call cannot be used with aribtrary connectors.
+As a VOL-enabled replacement, {\tt H5Fis\_accessible()} has been added to the library.
+It has the same semantics as {\tt H5Fis\_hdf5()}, but takes a fapl so it can work with any VOL connector.
+
+Note that, at this time, {\tt H5Fis\_hdf5()} \textit{always} uses the native VOL connector, regardless of the settings of environment variables, etc.
+
+\subsection*{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Ofuture\_function\_goes\_here()}$}
+
+\thgfuturewarning
+
+The {\tt H5Oget\_info1()} and {\tt H5Oget\_info2()} are often used by user code to obtain information about an object in the file, however these calls return a struct which contains native information and are thus currently handled via the native connector's \textit{object optional} callback.
+
+These calls will be separated into two functions: one for getting generic object info (which will go through the \textit{object get} callback), and another for returning native file format information (which will go through the native connector's \textit{object optional} callback).
+
+\subsection{Protect Native-Only API Calls}
 
 \section{Using VOL Connectors With The HDF5 Command-Line Tools}
-\subsection{Connection Strings}
-\subsection{Connector Compatibility}
 
@@
 \subsection{Feature Flags}
-\begin{tcolorbox}[colback=yellow!10!white,colframe=red!75!black,title=PRELIMINARY]
-    This feature is under active development and is either incomplete or may change in behavior before the final release.
-\end{tcolorbox}
+\thgfuturewarning
 \subsection{List of HDF5 Native VOL API Calls}

### 2019-11-20 RFCs/HDF5/VOL/user_guide/body.tex
Almost done with the VOL UG.
Former-commit-id: c323781cf89e12de483ff1a845ed90a3e4bf9851

@@
 \section{Introduction}
+
+The virtual object layer is an abstraction layer in the HDF5 library that intercepts all API calls that could potentially access objects in an HDF5 container and forwards those calls to a VOL connector, which implements the storage.
+The user or application gets the benefit of using the familiar and widely-used HDF5 data model and API, but can map the physical storage of the HDF5 file and objects to storage that better meets the application's data needs.
+
+\subsection*{The VOL Abstraction Layer}
+
+The VOL lies just under the public API.
+When a storage-oriented public API call is made, the library performs a few sanity checks on the input parameters and then immediately invokes a VOL callback, which resolves to an implementation in the VOL connector that was selected when opening or creating the file.
+The VOL connector then performs whatever operations are needed before control returns to the library, where any final library operations such as assigning IDs for newly created/opened datasets are performed before returning.
+This means that, for calls that utilize the VOL, all of the functionality is deferred to the VOL connector and the HDF5 library does very little work.
+An important consideration of this is that most of the HDF5 caching layers (metadata and chunk caches, page buffering, etc.) will not be available as those are implemented in the HDF5 native VOL connector and cannot be easily reused by external connectors.
+
+\begin{figure}[h]
+\caption {The VOL Architecture}
+\includegraphics[width=\textwidth]{vol_architecture.png}
+\end{figure}
+
+Not all public HDF5 API calls pass through the VOL.
+Only calls which require manipulating storage go through the VOL and require a VOL connector author to implement the appropriate callback.
+Dataspace, property list, error stack, etc.
+calls have nothing to do with storage manipulation or querying and do not use the VOL.
+This may be confusing when it comes to property list calls, since many of those calls set properties for storage.
+Property lists are just collections of key-value pairs, though, so the VOL is not involved with setting or getting any properties.
+
+Another thing to keep in mind is that not every VOL connector will implement the full HDF5 public API.
+In some cases, a particular feature like variable-length types may not have been developed yet or may not have an equivalent in the target storage system.
+Also, many HDF5 public API calls are specific to the native HDF5 file format and are unlikely to have any use in other VOL connectors.
+A feature/capabilities flag scheme is being developed to help navigate this.
+
+For more information about which calls go through the VOL and the mechanism by which this is implemented, see the connector author and library internals documentation.
+
+\subsection*{VOL Connectors}
+
+An external VOL connector is normally implemented as a dynamically loaded plugin.
+In order to be used by an application, they must be discoverable and loadable via path settings, etc.
+These plugins are loaded at runtime via the same HDF5 plugin scheme used for filters.
+A VOL connector for a file is set in the file access property list (FAPL) used to open it, either via H5Pset\_vol() or a connector-specific API call provided by the connector author.
+
+Many VOL connectors (at various stages of construction) can be found here:
+
+\quad \quad https://bitbucket.hdfgroup.org/projects/HDF5VOL
+
+Not every connector in this collection is actively maintained by The HDF Group.
+It simply serves as a single location where important VOL connectors can be found.
+See the documentation in a connector's repository to determine its development status and the parties responsible for it.
+The collection also includes a VOL template that contains build scripts (Autotools and CMake) and an empty VOL connector "shell" which can be copied and used as a starting point for building new connectors.
+See the VOL Connector Author Guide for more information on this.
+
+The native VOL connector is a special case. It is currently implemented as a built-in part of the HDF5 library and cannot be unloaded, nor can its ID be closed.
 
@@
 
+In place of modifying the source code of your application, you may be able to simply set the {\tt HDF5\_VOL\_CONNECTOR} environment variable (see below).
+This will automatically use the speicified VOL in place of the native VOL connector.
+
 \section{Loading and Registering Connectors}
-\subsection{VOL Connector Search Path}
-\subsection{Connector Versioning}
-\subsection{Connector-Specific Registration Calls}
-\subsection{\tt H5Pset\_vol()}
-\subsection{Connector Compatibility}
+
+Before a VOL connector can be used, it must be discoverable by the library and then loaded and registered.
+
+\subsection*{VOL Connector Search Path}
+
+VOL connector plugins are discovered and loaded by the library using the same mechanism as dataset/group filter plugins (REF). Essentially,
+
+\subsection*{registration}
+
+Before a connector can be used, it must be registered. This loads the connector into the library and give it an HDF5 {\tt hid\_t} ID. The {\tt H5VLregister\_connector} API calls are used for this.
+
+\quad\quad {\tt hid\_t H5VLregister\_connector(const H5VL\_class\_t *cls, hid\_t vipl\_id)}
+
+\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_name(const char *connector\_name, hid\_t vipl\_id)}
+
+\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_value(H5VL\_class\_value\_t connector\_value, hid\_t vipl\_id)}
+
+Each of these functions will check to see if an appropriate plugin with a matching name, value, etc.
+is already loaded and check the plugin path (see above) for matching plugins if this is not true.
+They return {\tt H5I\_INVALID\_HID} if they are unable to register the connector.
+Most people will use the {\tt \_by\_name()} or {\tt \_by\_value} versions of this API call.
+The call that takes an {\tt H5VL\_class\_t} struct is considered a lower-level call this is more commonly used by connector authors.
+Many VOL connectors will provide a connector-specific init call that will load and register the connector for you.
+
+Note the two ways that a VOL connector can be identified: by a name or by a connector-specific numerical value ({\tt H5VL\_class\_value\_t} is typedef'd to an integer).
+The name and value for a connector can be found in the connector's documentation or public header file.
+
+Each call also takes a VOL initialization property list (vipl).
+The library adds no properties to this list, so it is entirely for use by connector authors.
+Set this to {\tt H5P\_DEFAULT} unless instructed differently by the documentation for the VOL connector.
+
+As far as the library is concerned, connectors do not need to be explicitly unregistered as the library will unload the plugin and close the ID when the library is closed.
+If you want to close a VOL connector ID, either {\tt H5VLunregister\_connector()} or {\tt H5VLclose()} can be used (they have the same internal code path).
+The library maintains a reference count on all open IDs and will not do the actual work of closing an ID until its reference count drops to zero, so it's safe to close IDs anytime after they are used, even while an HDF5 file that was opened with that connector is still open.
+
+Note that it's considered an error to close/unload the native VOL connector.
+The library will prevent this.
+This means that, for the time being, the native VOL connector will always be available.
+This may change in the future so that the memory footprint of the native VOL connector goes away when not in use.
+
+\subsection*{Connector Versioning}
 
@@
 
-\subsection{Connection Strings}
-\subsection{Environment Variable}
+There is currently no recommended or library-inherent way to version VOL connectors.
+A {\tt version} field is included in the {\tt H5VL\_class\_t} struct which holds a connector's information and callbacks, but this has not been utilized in the plugin loading code at this time.
+
+\subsection*{Connector-Specific Registration Calls}
+
+\subsection*{\tt H5Pset\_vol()}
+
+The is the main library API call for setting the VOL connector in a file access property list. Its signature is:
+
+\quad\quad {\tt herr\_t H5Pset\_vol(hid\_t plist\_id, hid\_t vol\_id, vol\_info)}
+
+It takes the ID of the file access property list, the ID of the registered VOL connector, and a pointer to whatever connector-specific data the connector is expecting.
+This will usually be a data struct specified in the connector's header.
+
+Most connectors will provide a special API call which will make this call for you.
+For example, the DAOS VOL (https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/daos-vol) provides a {\tt H5Pset\_fapl\_daos()} API call which will take MPI parameters and make this call.
+
+\subsection*{Connector Compatibility}
+
+\thgfuturewarning
+
+\subsection*{Parameter Strings}
+
+Each VOL connector is allowed to take in a parameter string which can be parsed via {\tt H5VLconnector\_str\_to\_info()} to get an info struct which can be passed to {\tt H5Pset\_vol()}.
+
+\quad\quad {\tt herr\_t H5VLconnector\_str\_to\_info(const char *str, hid\_t connector\_id, void **info)}
+
+And the obtained info can be freed via:
+
+\quad\quad {\tt herr\_t H5VLfree\_connector\_info(hid\_t connector\_id, void *vol\_info)}
+
+Most users will not need this functionality as they will be using either connector-specific setup calls which will handle registering and configuring the connector for them or they will be using the environment variable (see below).
+
+\subsection*{Environment Variable}
 
@@
 
-\subsection{Specific API Call Substitutions}
+\subsection*{Specific API Call Substitutions}
 \subsection*{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}
@@
 
-\subsection*{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Ofuture\_function\_goes\_here()}$}
+\subsection*{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_[native|data\_model]\_info()}$}
 
@@
 
-The {\tt H5Oget\_info1()} and {\tt H5Oget\_info2()} are often used by user code to obtain information about an object in the file, however these calls return a struct which contains native information and are thus currently handled via the native connector's \textit{object optional} callback.
+The {\tt H5Oget\_info1()} and {\tt H5Oget\_info2()} API calls are often used by user code to obtain information about an object in the file, however these calls return a struct which contains native information and are thus currently handled via the native connector's \textit{object optional} callback and so are not handled by most external VOL connectors.
 
-These calls will be separated into two functions: one for getting generic object info (which will go through the \textit{object get} callback), and another for returning native file format information (which will go through the native connector's \textit{object optional} callback).
+These calls will be separated into two functions: one for getting an object's data model information ({\tt H5Oget\_data\_model\_info()}, which will go through the \textit{object get} callback), and another for returning an object's native file format information ({\tt H5Oget\_native\_info()}, which will go through the native connector's \textit{object optional} callback).
 
-\subsection{Protect Native-Only API Calls}
+\textbf{This section will be expanded when the RFC for this feature is complete.}
+
+\subsection*{Protect Native-Only API Calls}
+
+There is currently no simple way to determine if the VOL connector used for a file or object is the native VOL connector.
+You will have to track this in your application and not make native-only VOL calls with non-native VOL connectors.
+
+A list of native-only connector calls is given below.
+
+We are working on a mechanism that will allow detecting when the VOL connector is the native VOL connector, however a good mechanism for this is complicated as some VOL connectors will be passthrough VOL connectors (or even splitters) which ultimately resolve down to the native VOL connectors.
 
@@
 
+The best way to use a particular VOL connector with the HDF5 tools, both command-line and GUI tools, is to specify the VOL connector using the VOL connector environment variable (HDF5\_VOL\_CONNECTOR - see above).
+
+The HDF5 tools currently do not have an option to specify a VOL connector on the command line, though this option will be added soon.
+
 \section{Compatibility}
-\subsection{Feature Flags}
+\subsection*{Introspection / Feature Flags}
 \thgfuturewarning
-\subsection{List of HDF5 Native VOL API Calls}
 
-These API calls will probably fail when used with terminal VOL connectors other than the native HDF5 file format connector. Their use should be protected in code that uses arbitrary VOL connectors.
+Some VOL connectors will not implement all the functionality available in the HDF5 library, especially in the early stages of development.
+Unfortunately, there is currently no easy way to determine if a VOL connector implements particular API calls or groups of calls.
+
+We are working on an introspection mechanism, possibly involving a set of feature or capabilities flags and will have that available in a future release.
+
+\subsection*{List of HDF5 Native VOL API Calls}
+
+These API calls will probably fail when used with terminal VOL connectors other than the native HDF5 file format connector.
+Their use should be protected in code that uses arbitrary VOL connectors.
+Note that some connectors may, in fact, implement some of this functionality as it is possible to mimic the native HDF5 connector, however this will probably not be true for most non-native VOL connectors.
+
 \begin{longtable}{ |>{\raggedright\arraybackslash}p{\linewidth}| }
@@
 
-\subsection{List of HDF5 VOL-Independent API Calls}
+\subsection*{List of HDF5 VOL-Independent API Calls}
 
@@
 
-\subsection{List of HDF5 API Calls By Callback}
+\subsection*{List of HDF5 API Calls By Callback}
 

### 2019-11-20 RFCs/HDF5/VOL/user_guide/body.tex
Fixed a few missing things. Did some renaming.
Former-commit-id: 29616398bccaab1347956b136990c6bc077172b4

@@
 
-\subsection*{The VOL Abstraction Layer}
+\subsection{The VOL Abstraction Layer}
 
@@
 
-\subsection*{VOL Connectors}
+\subsection{VOL Connectors}
 
@@
 
-\subsection*{Read The Documentation For The New VOL Connector}
+\subsection{Read The Documentation For The New VOL Connector}
 
@@
 
-\subsection*{Use A VOL-Enabled HDF5 Library}
+\subsection{Use A VOL-Enabled HDF5 Library}
 
@@
 
-\subsection*{Make Sure The VOL Connector Is In The Search Path}
+\subsection{Make Sure The VOL Connector Is In The Search Path}
 
@@
 
-\subsection*{Update Your Code To Load And Use A VOL Connector}
+\subsection{Update Your Code To Load And Use A VOL Connector}
 
@@
 
-\subsection*{Optional: Set The VOL Connector Via The Environment Variable}
+\subsection{Optional: Set The VOL Connector Via The Environment Variable}
 
@@
 
-\subsection*{VOL Connector Search Path}
+\subsection{VOL Connector Search Path}
 
@@
 
-\subsection*{registration}
+\subsection{registration}
 
@@
 
-\subsection*{Connector Versioning}
+\subsection{Connector Versioning}
 
@@
 
-\subsection*{Connector-Specific Registration Calls}
+\subsection{Connector-Specific Registration Calls}
 
-\subsection*{\tt H5Pset\_vol()}
+Most connectors will provide a special API call which will set the connector in the fapl.
+These will often be in the form of {\tt H5Pset\_fapl\_<name>()}.
+For example, the DAOS VOL (https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/daos-vol) provides a {\tt H5Pset\_fapl\_daos()} API call which will take MPI parameters and make this call.
+See the connector's documentation or public header file(s) for more information.
+
+\subsection{\tt H5Pset\_vol()}
 
@@
 
-Most connectors will provide a special API call which will make this call for you.
-For example, the DAOS VOL (https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/daos-vol) provides a {\tt H5Pset\_fapl\_daos()} API call which will take MPI parameters and make this call.
+As mentioned above, many connectors will provide their own replacement for this call. See the connector's documentation for more information.
 
-\subsection*{Connector Compatibility}
-
-\thgfuturewarning
-
-\subsection*{Parameter Strings}
+\subsection{Parameter Strings}
 
@@
 
-\subsection*{Environment Variable}
+\subsection{Environment Variable}
 
@@
 
-\subsection*{Specific API Call Substitutions}
-\subsection*{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}
+\subsection{Specific API Call Substitutions}
+\subsection{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}
 
@@
 
-\subsection*{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_[native|data\_model]\_info()}$}
+\subsection{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_[native|data\_model]\_info()}$}
 
@@
 
-\subsection*{Protect Native-Only API Calls}
+\subsection{Protect Native-Only API Calls}
 
@@
 \section{Compatibility}
-\subsection*{Introspection / Feature Flags}
+\subsection{Introspection / Feature Flags}
 \thgfuturewarning
@@
 
-\subsection*{List of HDF5 Native VOL API Calls}
+\subsection{List of HDF5 Native VOL API Calls}
 
@@
 
-\subsection*{List of HDF5 VOL-Independent API Calls}
+\subsection{List of HDF5 VOL-Independent API Calls}
 
@@
 
-\subsection*{List of HDF5 API Calls By Callback}
+\subsection{List of HDF5 API Calls By Callback}
 

### 2019-11-25 RFCs/HDF5/VOL/connector_author_guide/appendix.tex
Most API changes in. Still need to move "helper" text over.
Former-commit-id: c236ad85c2fcb331051a2de3ffa110e6bfaeb004

\begin{appendices}

\pagebreak

\section{Mapping of VOL Callbacks to HDF5 API Calls}
\label{sec:A}

\begin{longtable}{ |l|>{\raggedright\arraybackslash}l| }
    \hline
    \multicolumn{1}{|c|}{VOL Callback} & \multicolumn{1}{|c|}{HDF5 API Call} \\
    \hline
    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}FILE} \\
    \hline
    create & H5Fcreate \\
    \hline
    open & H5Fopen \\
    \hline
    get & H5Fget\_access\_plist \\
        & H5Fget\_create\_plist \\
        & H5Fget\_fileno \\
        & H5Fget\_intent \\
        & H5Fget\_name \\
        & H5Fget\_obj\_count \\
        & H5Fget\_obj\_ids \\
    \hline
    specific & H5Fdelete \\
             & H5Fflush \\
             & H5Fis\_accessible \\
             & H5Fis\_hdf5 (deprecated, hard-coded to use native connector) \\
             & H5Fmount \\
             & H5Freopen \\
             & H5Funmount \\
    \hline
    close & H5Fclose \\
    \hline
    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}GROUP} \\
    \hline
    create & H5Gcreate1 (deprecated) \\
           & H5Gcreate2 \\
           & H5Gcreate\_anon \\
    \hline
    open & H5Gopen1 (deprecated) \\
         & H5Gopen2 \\
    \hline
    get & H5Gget\_create\_plist \\
        & H5Gget\_info \\
        & H5Gget\_info\_by\_idx \\
        & H5Gget\_info\_by\_name \\
        & H5Gget\_num\_objs (deprecated) \\
    \hline
    specific & H5Gflush \\
             & H5Grefresh \\
    \hline
    close & H5Gclose \\
    \hline
    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}DATASET} \\
    \hline
    create & H5Dcreate1 (deprecated) \\
           & H5Dcreate2 \\
    \hline
    open & H5Dopen1 (deprecated) \\
         & H5Dopen2 \\
    \hline
    read & H5Dread \\
    \hline
    write & H5Dwrite \\
    \hline
    get & H5Dget\_access\_plist \\
        & H5Dget\_create\_plist \\
        & H5Dextend \\
        & H5Dget\_offset \\
        & H5Dget\_space \\
        & H5Dget\_space\_status \\
        & H5Dget\_storage\_size \\
        & H5Dget\_type \\
    \hline
    specific & H5Dextend (deprecated) \\
             & H5Dflush \\
             & H5Drefresh \\
             & H5Dset\_extent \\
    \hline
    close & H5Dclose \\
    \hline
    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}OBJECT} \\
    \hline
    open & H5Oopen \\
         & H5Oopen\_by\_addr \\
         & H5Oopen\_by\_idx \\
         & H5Oopen\_by\_name \\
    \hline
    copy & H5Ocopy \\
    \hline
    get & N/A \\
    \hline
    specific & H5Odecr\_refcount \\
             & H5Oexists\_by\_name \\
             & H5Oflush \\
             & H5O\_incr\_refcount \\
             & H5Orefresh \\
             & H5Ovisit\_by\_name1 (deprecated) \\
             & H5Ovisit\_by\_name2 \\
             & H5Ovisit1 (deprecated) \\
             & H5Ovisit2 \\
    \hline
    close & H5Oclose \\
    \hline
    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}LINK} \\
    \hline
    create & H5Glink (deprecated) \\
           & H5Glink2 (deprecated) \\
           & H5Lcreate\_hard \\
           & H5Lcreate\_soft \\
           & H5Lcreate\_ud \\
           & H5Olink \\
    \hline
    copy & H5Lcopy \\
    \hline
    move & H5Gmove (deprecated) \\
         & H5Gmove2 (deprecated) \\
         & H5Lmove \\
    \hline
    get & H5Gget\_linkval (deprecated) \\
        & H5Lget\_info \\
        & H5Lget\_info\_by\_idx \\
        & H5Lget\_name\_by\_idx \\
        & H5Lget\_val \\
        & H5Lget\_val\_by\_idx \\
    \hline
    specific & H5Gunlink (deprecated) \\
             & H5Ldelete \\
             & H5Ldelete\_by\_idx \\
             & H5Lexists \\
             & H5Literate \\
             & H5Literate\_by\_name \\
             & H5Lvisit \\
             & H5Lvisit\_by\_name \\
    \hline
    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}DATATYPE} \\
    \hline
    commit & H5Tcommit1 (deprecated) \\
           & H5Tcommit2 \\
           & H5Tcommit\_anon \\
    \hline
    open & H5Topen1 (deprecated) \\
         & H5Topen2 \\
    \hline
    get & H5Tget\_create\_plist \\
    \hline
    specific & H5Tflush \\
             & H5Trefresh \\
    \hline
    close & H5Tclose \\
    \hline
    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}ATTRIBUTE} \\
    \hline
    create & H5Acreate1 (deprecated) \\
           & H5Acreate2 \\
           & H5Acreate\_by\_name \\
    \hline
    open & H5Aopen \\
         & H5Aopen\_by\_idx \\
         & H5Aopen\_by\_name \\
         & H5Aopen\_idx (deprecated)\\
         & H5Aopen\_name (deprecated) \\
    \hline
    read & H5Aread \\
    \hline
    write & H5Awrite \\
    \hline
    get & H5Aget\_get\_create\_plist \\
        & H5Aget\_info \\
        & H5Aget\_info\_by\_idx \\
        & H5Aget\_info\_by\_name \\
        & H5Aget\_name \\
        & H5Aget\_name\_by\_idx \\
        & H5Aget\_space \\
        & H5Aget\_storage\_size \\
        & H5Aget\_type \\
    \hline
    specific & H5Adelete \\
             & H5Adelete\_by\_idx \\
             & H5Adelete\_by\_name \\
             & H5Aexists \\
             & H5Aexists\_by\_name \\
             & H5Aiterate1 (deprecated) \\
             & H5Aiterate2 \\
             & H5Aiterate\_by\_name \\
             & H5Arename \\
             & H5Arename\_by\_name \\
    \hline
    close & H5Aclose \\
    \hline
\caption{Breakdown of HDF5 API calls by VOL callback}
\end{longtable}

\pagebreak

\section{Callback Wrapper API Calls for Passthrough Connector Authors}
\label{sec:B}

From {\tt H5VL\_connector\_passthru.h}

\begin{lstlisting}

/* Helper routines for VOL connector authors */                                  
herr_t H5VLcmp_connector_cls(int *cmp, hid_t connector_id1, hid_t connector_id2);
hid_t H5VLwrap_register(void *obj, H5I_type_t type);                      
herr_t H5VLretrieve_lib_state(void **state);                              
herr_t H5VLrestore_lib_state(const void *state);                          
herr_t H5VLreset_lib_state(void);                                         
herr_t H5VLfree_lib_state(void *state);

/* Pass-through callbacks */                                                     
void *H5VLget_object(void *obj, hid_t connector_id);                      
herr_t H5VLget_wrap_ctx(void *obj, hid_t connector_id, void **wrap_ctx);  
void *H5VLwrap_object(void *obj, H5I_type_t obj_type, hid_t connector_id, void *wrap_ctx);                                                             
void *H5VLunwrap_object(void *obj, hid_t connector_id);                   
herr_t H5VLfree_wrap_ctx(void *wrap_ctx, hid_t connector_id);

/* Public wrappers for generic callbacks */                                      
herr_t H5VLinitialize(hid_t connector_id, hid_t vipl_id);                 
herr_t H5VLterminate(hid_t connector_id);                                 
herr_t H5VLget_cap_flags(hid_t connector_id, unsigned *cap_flags);        
herr_t H5VLget_value(hid_t connector_id, H5VL_class_value_t *conn_value);

/* Public wrappers for info fields and callbacks */                              
herr_t H5VLcopy_connector_info(hid_t connector_id, void **dst_vol_info, void *src_vol_info);
herr_t H5VLcmp_connector_info(int *cmp, hid_t connector_id, const void *info1,
    const void *info2);                                                          
herr_t H5VLfree_connector_info(hid_t connector_id, void *vol_info);       
herr_t H5VLconnector_info_to_str(const void *info, hid_t connector_id, char **str);
herr_t H5VLconnector_str_to_info(const char *str, hid_t connector_id, void **info);

/* Public wrappers for attribute callbacks */                                    
void *H5VLattr_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *attr_name, hid_t type_id, hid_t space_id, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
void *H5VLattr_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t aapl_id, hid_t dxpl_id, void **req);
herr_t H5VLattr_read(void *attr, hid_t connector_id, hid_t dtype_id, void *buf, hid_t dxpl_id, void **req);
herr_t H5VLattr_write(void *attr, hid_t connector_id, hid_t dtype_id, const void *buf, hid_t dxpl_id, void **req);
herr_t H5VLattr_get(void *obj, hid_t connector_id, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLattr_close(void *attr, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for dataset callbacks */                                      
void *H5VLdataset_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t lcpl_id, hid_t type_id, hid_t space_id, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
void *H5VLdataset_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
herr_t H5VLdataset_read(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, void *buf, void **req);
herr_t H5VLdataset_write(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
herr_t H5VLdataset_get(void *dset, hid_t connector_id, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_specific(void *obj, hid_t connector_id, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdataset_close(void *dset, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for file callbacks */                                         
void *H5VLfile_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
void *H5VLfile_open(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
herr_t H5VLfile_get(void *file, hid_t connector_id, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_specific(void *obj, hid_t connector_id, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLfile_close(void *file, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for group callbacks */                                        
void *H5VLgroup_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t lcpl_id, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
void *H5VLgroup_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
herr_t H5VLgroup_get(void *obj, hid_t connector_id, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_specific(void *obj, hid_t connector_id, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLgroup_close(void *grp, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for link callbacks */
herr_t H5VLlink_create(H5VL_link_create_type_t create_type, void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
herr_t H5VLlink_move(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
herr_t H5VLlink_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLlink_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);

/* Public wrappers for object callbacks */
void *H5VLobject_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
herr_t H5VLobject_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, const char *src_name, void *dst_obj, const H5VL_loc_params_t *loc_params2, const char *dst_name, hid_t connector_id, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
herr_t H5VLobject_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLobject_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLobject_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);

/* Public wrappers for named datatype callbacks */                               
void *H5VLdatatype_commit(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
void *H5VLdatatype_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
herr_t H5VLdatatype_get(void *dt, hid_t connector_id, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_specific(void *obj, hid_t connector_id, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
herr_t H5VLdatatype_close(void *dt, hid_t connector_id, hid_t dxpl_id, void **req);

/* Public wrappers for asynchronous request callbacks */                         
herr_t H5VLrequest_wait(void *req, hid_t connector_id, uint64_t timeout, H5ES_status_t *status);
herr_t H5VLrequest_notify(void *req, hid_t connector_id, H5VL_request_notify_t cb, void *ctx);
herr_t H5VLrequest_cancel(void *req, hid_t connector_id);                 
herr_t H5VLrequest_specific(void *req, hid_t connector_id, H5VL_request_specific_t specific_type, va_list arguments);
herr_t H5VLrequest_optional(void *req, hid_t connector_id, va_list arguments);
herr_t H5VLrequest_free(void *req, hid_t connector_id);

/* Public wrappers for blob callbacks */                                         
herr_t H5VLblob_put(void *obj, hid_t connector_id, const void *buf, size_t size, void *blob_id, void *ctx);
herr_t H5VLblob_get(void *obj, hid_t connector_id, const void *blob_id, void *buf, size_t size, void *ctx);
herr_t H5VLblob_specific(void *obj, hid_t connector_id, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);

/* Public wrappers for generic 'optional' callback */                            
herr_t H5VLoptional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);

\end{lstlisting}

\end{appendices}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-11-25 RFCs/HDF5/VOL/connector_author_guide/connector_interface.tex
Most API changes in. Still need to move "helper" text over.
Former-commit-id: c236ad85c2fcb331051a2de3ffa110e6bfaeb004

--- 2018-01-11 RFCs/HDF5/VOL/user_guide/plugin.tex
@@
-\section{Creating a VOL Plugin}
+\section{VOL Connector Interface Reference}
 \label{sec:vol}
-Each VOL plugin should be of type \texttt{H5VL\_class\_t}, Listing \ref{lst:VOLclass}.
+Each VOL connector should be of type \texttt{H5VL\_class\_t}, Listing \ref{lst:VOLclass}.
 
@@
 
-\begin{lstlisting}[caption={VOL plugin class, H5VLpublic.h},captionpos=b, label={lst:VOLclass}]
+\begin{lstlisting}[caption={VOL connector class, H5VLpublic.h},captionpos=b, label={lst:VOLclass}]
 /* Class information for each VOL driver */
 typedef struct H5VL_class_t {
-    unsigned int version;
-    H5VL_class_value_t value;
-    const char *name;
-    herr_t  (*initialize)(hid_t vipl_id);
-    herr_t  (*terminate)(hid_t vtpl_id);
-    size_t  fapl_size;
-    void *  (*fapl_copy)(const void *info);
-    herr_t  (*fapl_free)(void *info);
+    /* Overall connector fields & callbacks */                                   
+    unsigned int version;                   /* VOL connector class struct version #     */
+    H5VL_class_value_t value;               /* Value to identify connector              */
+    const char *name;                       /* Connector name (MUST be unique!)         */
+    unsigned cap_flags;                     /* Capability flags for connector           */
+    herr_t (*initialize)(hid_t vipl_id);    /* Connector initialization callback        */
+    herr_t (*terminate)(void);              /* Connector termination callback           */
+
+    /* VOL framework */                                                          
+    H5VL_info_class_t       info_cls;       /* VOL info fields & callbacks  */   
+    H5VL_wrap_class_t       wrap_cls;       /* VOL object wrap / retrieval callbacks */
 
     /* Data Model */                                                             
-    H5VL_attr_class_t          attr_cls;
-    H5VL_dataset_class_t       dataset_cls;
-    H5VL_datatype_class_t      datatype_cls;
-    H5VL_file_class_t          file_cls;
-    H5VL_group_class_t         group_cls;
-    H5VL_link_class_t          link_cls;
-    H5VL_object_class_t        object_cls;
-
-    /* Services */
-    H5VL_async_class_t         async_cls;
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    H5VL_attr_class_t       attr_cls;       /* Attribute (H5A*) class callbacks */
+    H5VL_dataset_class_t    dataset_cls;    /* Dataset (H5D*) class callbacks   */
+    H5VL_datatype_class_t   datatype_cls;   /* Datatype (H5T*) class callbacks  */
+    H5VL_file_class_t       file_cls;       /* File (H5F*) class callbacks      */
+    H5VL_group_class_t      group_cls;      /* Group (H5G*) class callbacks     */
+    H5VL_link_class_t       link_cls;       /* Link (H5L*) class callbacks      */
+    H5VL_object_class_t     object_cls;     /* Object (H5O*) class callbacks    */
+
+    /* Infrastructure / Services */                                              
+    H5VL_request_class_t    request_cls;    /* Asynchronous request class callbacks */
+    H5VL_blob_class_t       blob_cls;       /* 'blob' callbacks */
+
+    /* Catch-all */                                                              
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); /* Optional callback */
 } H5VL_class_t;
@@
 
-The \texttt{version} field is the HDF5 VOL driver version.
-
-The \texttt{value} field is a unique integer enum identifier that should be
-greater than 128 for external plugins and smaller than 128 for
-internal plugins. Setting it in the VOL structure is required.
-
-The \texttt{name} field is a string that uniquely identifies the VOL plugin
-name. Setting it in the VOL structure is required. No two plugins with the same name can be registered with the library at the same time.
-
-The \texttt{initialize} field is a function pointer to a routine that a plugin implements to set up or initialize access to the plugin.
-Implementing this function by the plugin is not required since some plugins do not require any set up to start accessing the plugin.
+The \texttt{version} field is the version of the \texttt{H5VL\_class\_t} struct. This is identical to how the \texttt{version} field is used in the \texttt{H5Z\_class2\_t} struct for filters.
+
+The \texttt{value} field is a unique integer identifier that should be greater than 256 for external, non-library connectors. Setting it in the VOL structure is required.
+
+The \texttt{name} field is a string that uniquely identifies the VOL connector name. Setting it in the VOL structure is required.
+
+The \texttt{cap\_flags} field will be used to hold bitwise capability/feature flags that can be used with a future query API call to determine which operations and capabilities are supported by a the VOL connector.
+This feature is currently under development.
+
+The \texttt{initialize} field is a function pointer to a routine that a connector implements to set up or initialize access to the connector.
+Implementing this function by the connector is not required since some connectors do not require any set up to start accessing the connector.
 In that case, the value of the function pointer should be set to NULL.
-Plugin specific variables that are required to be passed from users should be passed through the VOL initialize property list.
-Generic properties can be added to this property class for user-defined plugins that cannot modify the HDF5 library to add internal properties.
+Connector specific variables that are required to be passed from users should be passed through the VOL initialize property list.
+Generic properties can be added to this property class for user-defined connectors that cannot modify the HDF5 library to add internal properties.
 For more information consult the property list reference manual pages.
 
-The \texttt{terminate} field is a function pointer to a routine that a plugin implements to terminate or finalize access to the plugin.
-Implementing this function by the plugin is not required since some plugins do not require any termination phase to the plugin.
+The \texttt{terminate} field is a function pointer to a routine that a connector implements to terminate or finalize access to the connector.
+Implementing this function by the connector is not required since some connectors do not require any termination phase to the connector.
 In that case, the value of the function pointer should be set to NULL.
-Plugin specific variables that are required to be passed from users should be passed through the VOL terminate property list.
-Generic properties can be added to this property class for user-defined plugins that cannot modify the HDF5 library to add internal properties.
+Connector specific variables that are required to be passed from users should be passed through the VOL terminate property list.
+Generic properties can be added to this property class for user-defined connectors that cannot modify the HDF5 library to add internal properties.
 For more information consult the property list reference manual pages.
-
-The \texttt{fapl\_size} field indicates the size required to store the
-info data that the plugin needs. That info data is passed when the
-plugin is selected for usage with the file access property list (fapl)
-function. It might be that the plugin defined does not require any
-information from the user, which means the size in this field will be
-zero. More information about the info data and the fapl selection
-routines follow later.
-
-The \texttt{fapl\_copy} field is a function pointer that is called when
-the plugin is selected with the fapl function. It allows the plugin to
-make a copy of the info data since the user might free it when closing
-the fapl. It is required if there is info data needed by the plugin.
-
-The \texttt{fapl\_free} field is a function pointer that is called to
-free the info data when the fapl close routine is called. It is
-required if there is info data needed by the plugin.
 
@@
 Service classes are those that provide services for users that are not related to the data model specifically.
-Asynchronous operations, for example, are a service that most plugins can implement, so we add a class for it in the VOL structure.
-If a service becomes generic enough and common among many plugins, a class for it should be added to the VOL structure.
-However, many plugins can/will provide services that are not shared by other plugins.
-A good way to support these services is through an optional callback in the VOL structure which can be a hook from the API to the plugin that provides those services, passing any necessary arguments needed without the HDF5 library having to worry about supporting that service.
+Asynchronous operations, for example, are a service that most connectors can implement, so we add a class for it in the VOL structure.
+If a service becomes generic enough and common among many connectors, a class for it should be added to the VOL structure.
+However, many connectors can/will provide services that are not shared by other connectors.
+A good way to support these services is through an optional callback in the VOL structure which can be a hook from the API to the connector that provides those services, passing any necessary arguments needed without the HDF5 library having to worry about supporting that service.
 A similar API operation to allow users to use that service will be added.
-This API call would be similar to an “ioctl” call where any kind of operation can be supported and passed down to the plugin that has enough knowledge from the user to interpret the type of the operation.
+This API call would be similar to an “ioctl” call where any kind of operation can be supported and passed down to the connector that has enough knowledge from the user to interpret the type of the operation.
 All classes and their defined callbacks will be detailed in the following sub-sections.
@@
 the interface often whenever new features are added would be
-discouraging to plugin developers since that would mean reworking
-their VOL plugin structure. To remedy this issue, every callback will
+discouraging to connector developers since that would mean reworking
+their VOL connector structure. To remedy this issue, every callback will
 contain two parameters:
@@
 \item A data transfer property list (DXPL) which allows that API to
-  put some properties on for the plugins to retrieve if they have to
+  put some properties on for the connectors to retrieve if they have to
   for particular operations, without having to add arguments to the
@@
   releases (beyond the 1.8 series). That pointer is set by the VOL
-  plugin to a request object it creates to manage progress on that
+  connector to a request object it creates to manage progress on that
   asynchronous operation. If the \texttt{req} is \texttt{NULL}, that means
-  that the API operation is blocking and so the plugin would not
-  execute the operation asynchronously. If the plugin does not support
+  that the API operation is blocking and so the connector would not
+  execute the operation asynchronously. If the connector does not support
   asynchronous operations, it needs not to worry about this field and
@@
 retrieved by calling the public routine (or its private version if
-this is an internal plugin): 
+this is an internal connector): 
 \begin{lstlisting}
@@
  * Structure to hold parameters for object locations.
- * either: BY_SELF, BY_NAME, BY_IDX, BY_ADDR, BY_REF 
+ * either: BY_SELF, BY_NAME, BY_IDX, BY_TOKEN
  */
@@
     union { /* parameters of the location */
-        struct H5VL_loc_by_name loc_by_name;
-        struct H5VL_loc_by_idx  loc_by_idx;
-        struct H5VL_loc_by_addr loc_by_addr;
-        struct H5VL_loc_by_ref  loc_by_ref;
+        H5VL_loc_by_token_t     loc_by_token;                                    
+        H5VL_loc_by_name_t      loc_by_name;                                     
+        H5VL_loc_by_idx_t       loc_by_idx;  
     }loc_data;
@@
 typedef enum H5VL_loc_type_t {
-    /* starting location is the target object*/
+    /* starting location is the target object */
     H5VL_OBJECT_BY_SELF,
 
-    /* location defined by object and path in H5VL_loc_by_name */
+    /* location defined by object and path in H5VL_loc_by_name_t */
     H5VL_OBJECT_BY_NAME,
 
-    /* location defined by object, path, and index in H5VL_loc_by_idx */
+    /* location defined by object, path, and index in H5VL_loc_by_idx_t */
     H5VL_OBJECT_BY_IDX,
 
-    /* location defined by physical address in H5VL_loc_by_addr */
-    H5VL_OBJECT_BY_ADDR,
-
-    /* NOT USED */
-    H5VL_OBJECT_BY_REF
+    /* location defined by token (e.g. physical address) in H5VL_loc_by_token_t */
+    H5VL_OBJECT_BY_TOKEN,
 } H5VL_loc_type_t;
 
-struct H5VL_loc_by_name {
+typedef struct H5VL_loc_by_name {
     const char *name; /* The path relative to the starting location */
     hid_t lapl_id; /* The link access property list */
-};
-
-struct H5VL_loc_by_idx {
+}H5VL_loc_by_name_t;
+
+typedef struct H5VL_loc_by_idx {
     const char *name; /* The path relative to the starting location */
@@
     H5_iter_order_t order; /* Index traversal order */
-    hsize_t n; /* position in index */
+    hsize_t n; /* Position in index */
     hid_t lapl_id; /* The link access property list */
-};
-
-struct H5VL_loc_by_addr {
-    haddr_t addr; /* physical address of location */
-};
-
-/* Not used for now */
-struct H5VL_loc_by_ref {
-    H5R_type_t ref_type;
-    const void *_ref;
-    hid_t lapl_id;
-};
+}H5VL_loc_by_idx_t;
+
+typedef struct H5VL_loc_by_token {
+    void *token; /* arbitrary token (physical address of location in native VOL) */
+}H5VL_loc_by_token_t;
 \end{lstlisting}
@@
 \item API routines are specific to each class of callbacks (attributes, files, etc...). Having a callback for each one would clutter the VOL callback structure and reduce user-friendliness. 
-\item API routines that make sense to only implement in the native HDF5 file format and would not be possible to implement in other plugins.
-Adding a callback for those routines would be confusing to plugin developers.
+\item API routines that make sense to only implement in the native HDF5 file format and would not be possible to implement in other connectors.
+Adding a callback for those routines would be confusing to connector developers.
 \end{itemize}
@@
 The \texttt{optional} callback is a free for all callback where anything from the API layer is passed in directly.
-This callback is used to support plugin specific operations in the API that other plugins should or would not know about.
+This callback is used to support connector specific operations in the API that other connectors should or would not know about.
 More information about types and the arguments for each type will be detailed in the corresponding class arguments.
 
-\subsection{The File Function Callbacks}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% CONNECTOR INFORMATION CALLBACKS %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Connector Information Callbacks}
+
+This section's callbacks involve the connector-specific information that will be associated with the VOL in the fapl via \texttt{H5Pset\_fapl()} et al.
+This data is copied into the fapl so the library needs these functions to manage this in a way that prevents resource leaks.
+
+The \texttt{to\_str} and \texttt{from\_str} callbacks are used to convert the connector-specific data to and from a configuration string.
+There is no official way to construct VOL configuration strings, so the format used (JSON, XML, getopt-style processing, etc.) is up to the connector author.
+These connector configuration strings can be used to set up a VOL connector via mechanisms like command-line parameters and environment variables.
+
+\begin{lstlisting}[caption={Info class for connector information routines, H5VLconnector.h}, captionpos=b, label={lst:Infoclass}]
+typedef struct H5VL_info_class_t {                                               
+    size_t size;
+    void * (*copy)(const void *info);
+    herr_t (*cmp)(int *cmp_value, const void *info1, const void *info2);
+    herr_t (*free)(void *info);
+    herr_t (*to_str)(const void *info, char **str);
+    herr_t (*from_str)(const char *str, void **info);
+} H5VL_info_class_t;
+\end{lstlisting}
+
+\subsubsection{info: size}
+The \texttt{size} field indicates the size required to store any special information that the connector needs.
+
+If the connector requires no special information, set this field to zero.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    size_t size;
+\end{lstlisting}
+\end{mdframed}
+
+\subsubsection{info: copy}
+The \texttt{copy} callback is invoked when the connector is selected for use with \texttt{H5Pset\_fapl()}, the connector-specific set call, etc.
+Where possible, the information should be deep copied in such a way that the original data can be freed.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void * (*copy)(const void *info);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{info} & (IN): The connector-specific info to copy.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{info: cmp}
+The \texttt{cmp} callback is uesd to determine if two connector-specific data structs are identical and helps the library manage connector resources.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*cmp)(int *cmp_value, const void *info1, const void *info2);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{cmp\_value} & (OUT): A strcmp-like compare value.\\
+  \texttt{info1} & (IN): The 1st connector-specific info to copy.\\
+  \texttt{info2} & (IN): The 2nd connector-specific info to copy.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{info: free}
+The \texttt{free} callback is used to clean up the connector-specific information that was copied when set in the fapl via the \texttt{copy} callback.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*free)(void *info);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{info} & (IN): The connector-specific info to free.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{info: to\_str}
+The \texttt{to\_str} callback converts a connector-specific information structure to a connector-specific configuration string. It is the opposite of the \texttt{from\_str} callback.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*to_str)(const void *info, char **str);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{info} & (IN): The connector-specific info to convert to a configuration string.\\
+  \texttt{str} & (OUT): The constructed configuration string.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{info: from\_str}
+The \texttt{to\_str} callback converts a connector-specific configuration string to a connector-specific information structure. It is the opposite of the \texttt{to\_str} callback.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*from_str)(const char *str, void **info);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{str} & (IN): The connector-specific configuration string.\\
+  \texttt{info} & (OUT): The connector-specific info generated from the configuration string.\\
+\end{tabular}
+\end{mdframed}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% OBJECT WRAP CALLBACKS %
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Object Wrap Callbacks}
+The object wrap callbacks are used by passthrough connectors to wrap/unwrap
+objects and contexts when passing them up and down the VOL chain.
+
+\begin{lstlisting}[caption={Wrap class for object wrapping routines, H5VLconnector.h}, captionpos=b, label={lst:Wrapclass}]
+typedef struct H5VL_wrap_class_t {                                               
+    void * (*get_object)(const void *obj);
+    herr_t (*get_wrap_ctx)(const void *obj, void **wrap_ctx);
+    void * (*wrap_object)(void *obj, H5I_type_t obj_type, void *wrap_ctx);
+    void * (*unwrap_object)(void *obj);
+    herr_t (*free_wrap_ctx)(void *wrap_ctx);
+} H5VL_wrap_class_t; 
+\end{lstlisting}
+
+\subsubsection{wrap: get\_object}
+Retrieves an underlying object.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void * (*get_object)(const void *obj);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Object being unwrapped.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{wrap: get\_wrap\_ctx}
+Get a VOL connector's object wrapping context.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*get_wrap_ctx)(const void *obj, void **wrap_ctx);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Object for which we need a context.\\
+  \texttt{wrap\_ctx} & (OUT): Context.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{wrap: wrap\_object}
+Asks a connector to wrap an underlying object.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void * (*wrap_object)(void *obj, H5I_type_t obj_type, void *wrap_ctx);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Object being wrapped.\\
+  \texttt{obj\_type} & (IN): Object type (see \texttt{H5Ipublic.h}).\\
+  \texttt{wrap\_ctx} & (IN): Context.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{wrap: unwrap\_object}
+Unwrap an object from connector.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void * (*unwrap_object)(void *obj);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Object being unwrapped.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{wrap: free\_wrap\_ctx}
+Release a VOL connector's object wrapping context.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*free_wrap_ctx)(void *wrap_ctx);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{wrap\_ctx} & (IN): Context to be freed.\\
+\end{tabular}
+\end{mdframed}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+% ATTRIBUTE CALLBACKS %
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{The Attribute Function Callbacks}
+The attribute API routines (H5A) allow HDF5 users to create and manage
+HDF5 attributes. All the H5A API routines that modify the HDF5
+container map to one of the attribute callback routines in this
+class that the connector needs to implement.
+
+\begin{lstlisting}[caption={Structure for attribute callback routines, H5VLconnector.h}, captionpos=b, label={lst:ATTRclass}]
+typedef struct H5VL_attr_class_t {                                               
+    void *(*create)(void *obj, const H5VL_loc_params_t *loc_params, const char *attr_name, hid_t type_id, hid_t space_id, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
+    void *(*open)(void *obj, const H5VL_loc_params_t *loc_params, const char *attr_name, hid_t aapl_id, hid_t dxpl_id, void **req);
+    herr_t (*read)(void *attr, hid_t mem_type_id, void *buf, hid_t dxpl_id, void **req);
+    herr_t (*write)(void *attr, hid_t mem_type_id, const void *buf, hid_t dxpl_id, void **req);
+    herr_t (*get)(void *obj, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); 
+    herr_t (*close) (void *attr, hid_t dxpl_id, void **req);                     
+} H5VL_attr_class_t; 
+\end{lstlisting}
+
+\subsubsection{attr: create}
+The \texttt{create} callback in the attribute class creates an
+attribute object in the container of the location object and
+returns a pointer to the attribute structure containing information to
+access the attribute in future calls. \bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void *(*create)(void *obj, H5VL_loc_params_t *loc_params, 
+        const char *attr_name, hid_t type_id, hid_t space_id,
+        hid_t acpl_id, hid_t aapl_id, 
+        hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to an object where the attribute needs
+  to be created or where the look-up of the target object needs to
+  start.\\
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
+  Section~\ref{sec:map}.\\
+  \texttt{attr\_name} & (IN): The name of the attribute to be created.\\
+  \texttt{type\_id} & (IN): The datatype of the attribute.\\
+  \texttt{space\_id} & (IN): The dataspace of the attribute.\\
+  \texttt{acpl\_id} & (IN): The attribute creation property list.\\
+  \texttt{aapl\_id} & (IN): The attribute access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{attr: open}
+The \texttt{open} callback in the attribute class opens an
+attribute object in the container of the location object and returns a
+pointer to the attribute structure containing information to access
+the attribute in future calls. \bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void *(*open)(void *obj, H5VL_loc_params_t *loc_params, 
+        const char *attr_name, hid_t aapl_id, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to an object where the attribute needs to be
+  opened or where the look-up of the target object needs to start.\\
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
+  Section~\ref{sec:map}.\\
+  \texttt{attr\_name} & (IN): The name of the attribute to be opened.\\
+  \texttt{aapl\_id} & (IN): The attribute access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{attr: read}
+The \texttt{read} callback in the attribute class reads data from
+the attribute object and returns an \texttt{herr\_t} indicating success or
+failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*read)(void *attr, hid_t mem_type_id, void *buf, 
+        hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{attr} & (IN): Pointer to the attribute object.\\
+  \texttt{mem\_type\_id} & (IN): The memory datatype of the attribute.\\
+  \texttt{buf} & (OUT): Data buffer to be read into.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{attr: write}
+The \texttt{write} callback in the attribute class writes data to
+the attribute object and returns an \texttt{herr\_t} indicating success or
+failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*write)(void *attr, hid_t mem_type_id, const void *buf, 
+        hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{attr} & (IN): Pointer to the attribute object.\\
+  \texttt{mem\_type\_id} & (IN): The memory datatype of the attribute.\\
+  \texttt{buf} & (IN): Data buffer to be written.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{attr: get}
+The \texttt{get} callback in the attribute class retrieves
+information about the attribute as specified in the \texttt{get\_type}
+parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*get)(void *obj, H5VL_attr_get_t get_type, hid_t dxpl_id, 
+        void **req, va_list arguments);
+\end{lstlisting}
+
+The \texttt{get\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* types for attribute GET callback */
+typedef enum H5VL_attr_get_t {                                                   
+    H5VL_ATTR_GET_ACPL,                     /* creation property list              */
+    H5VL_ATTR_GET_INFO,                     /* info                                */
+    H5VL_ATTR_GET_NAME,                     /* access property list                */
+    H5VL_ATTR_GET_SPACE,                    /* dataspace                           */
+    H5VL_ATTR_GET_STORAGE_SIZE,             /* storage size                        */
+    H5VL_ATTR_GET_TYPE                      /* datatype                            */
+} H5VL_attr_get_t; 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{attr} & (IN): An attribute or location object where information
+  needs to be retrieved from.\\
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
+
+\begin{itemize}
+
+\item \texttt{H5VL\_ATTR\_GET\_ACPL}, to retrieve the attribute creation
+  property list of the attribute specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
+    attribute creation property list.
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_GET\_INFO}, to retrieve the attribute info:
+  \begin{enumerate}
+  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
+    explained in Section~\ref{sec:map}. 
+  \item \texttt{H5A\_info\_t *ainfo} (OUT): info structure to fill the
+    attribute info in.
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_GET\_NAME}, to retrieve an attribute name on a
+  particular object specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
+    explained in Section~\ref{sec:map}. The type could be either
+    \texttt{H5VL\_OBJECT\_BY\_SELF} meaning \texttt{obj} is the attribute,
+    or \texttt{H5VL\_OBJECT\_BY\_IDX} meaning the attribute to retrieve
+    the name for should be looked up using the index information on
+    the object in \texttt{obj} and the index information in \texttt{loc\_params}.
+  \item \texttt{size\_t buf\_size} (IN): the size of the buffer to store
+    the name in.
+  \item \texttt{void *buf} (OUT): Buffer to store the name in.
+  \item \texttt{ssize\_t *ret\_val} (OUT): return the actual size needed
+    to store the fill attribute name.
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_GET\_SPACE}, to retrieve the dataspace of the
+  attribute specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
+    attribute dataspace.
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_GET\_STORAGE\_SIZE}, to retrieve the storage
+  size of the attribute specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hsize\_t *ret} (OUT): buffer for the storage size of
+    the attribute in the container.
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_GET\_TYPE}, to retrieve the datatype of the
+  attribute specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
+    attribute datatype.
+  \end{enumerate}
+
+\end{itemize}
+
+\subsubsection{attr: specific}
+The \texttt{specific} callback in the attribute class implements specific operations on HDF5 attributes as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+The \texttt{specific\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* types for attribute SPECFIC callback */
+typedef enum H5VL_attr_specific_t {                                              
+    H5VL_ATTR_DELETE,                       /* H5Adelete(_by_name/idx)             */
+    H5VL_ATTR_EXISTS,                       /* H5Aexists(_by_name)                 */
+    H5VL_ATTR_ITER,                         /* H5Aiterate(_by_name)                */
+    H5VL_ATTR_RENAME                        /* H5Arename(_by_name)                 */
+} H5VL_attr_specific_t; 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): A pointer to the location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
+
+\begin{itemize}
+\item \texttt{H5VL\_ATTR\_DELETE}, to delete an attribute on an object:
+  \begin{enumerate}
+  \item \texttt{char *attr\_name} (IN): the name of the attribute to delete.
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_EXISTS}, to check if an attribute exists on a
+  particular object specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
+    explained in Section~\ref{sec:map}.
+  \item \texttt{char *attr\_name} (IN): the attribute name to check.
+  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_ITER}, to iterate over all attributes of an object and call a user-specified callback on each one:
+  \begin{enumerate}
+  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
+  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
+  \item \texttt{hsize\_t *idx} (IN/OUT): Initial and return offset within index.\\
+  \item \texttt{H5A\_operator2\_t op} (IN): User-defined function to pass each attribute to. \\
+  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
+  \end{enumerate}
+
+\item \texttt{H5VL\_ATTR\_RENAME}, to rename an attribute on an object:
+  \begin{enumerate}
+  \item \texttt{char *old\_name} (IN): the original name of the attribute.
+  \item \texttt{char *new\_name} (IN): the new name to assign for the attribute.
+  \end{enumerate}
+
+\end{itemize}
+
+\subsubsection{attr: optional}
+The \texttt{optional} callback in the attribute class implements connector specific operations on an HDF5 attribute. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each connector should be able to parse the \texttt{va\_list arguments} if it has connector specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+\subsubsection{attr: close}
+The \texttt{close} callback in the attribute class terminates
+access to the attribute object and free all resources it was
+consuming, and returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*close)(void *attr, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{attr} & (IN): Pointer to the attribute object.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+%%%%%%%%%%%%%%%%%%%%%
+% DATASET CALLBACKS %
+%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Dataset Callbacks}
+The dataset API routines (H5D) allow HDF5 users to create and manage
+HDF5 datasets. All the H5D API routines that modify the HDF5 container
+map to one of the dataset callback routines in this class that the
+connector needs to implement.
+
+\begin{lstlisting}[caption={Structure for dataset callback routines, H5VLconnector.h}, captionpos=b, label={lst:DSclass}]
+typedef struct H5VL_dataset_class_t {                                            
+    void *(*create)(void *obj, const H5VL_loc_params_t *loc_params, const char *name, hid_t lcpl_id, hid_t type_id, hid_t space_id, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
+    void *(*open)(void *obj, const H5VL_loc_params_t *loc_params, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
+    herr_t (*read)(void *dset, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t dxpl_id, void * buf, void **req);
+    herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t dxpl_id, const void * buf, void **req);
+    herr_t (*get)(void *obj, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*specific)(void *obj, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*close) (void *dset, hid_t dxpl_id, void **req);
+} H5VL_dataset_class_t; 
+\end{lstlisting}
+
+\subsubsection{dataset: create}
+The \texttt{create} callback in the dataset class creates a dataset
+object in the container of the location object and returns a pointer
+to the dataset structure containing information to access the dataset
+in future calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void *(*create)(void *obj, H5VL_loc_params_t *loc_params, const char *name, hid_t lcpl_id, hid_t type_id, hid_t space_id, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to an object where the dataset needs
+  to be created or where the look-up of the target object needs to
+  start.\\
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
+  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  \texttt{name} & (IN): The name of the dataset to be created.\\
+  \texttt{lcpl\_id} & (IN): The link creation property list.\\
+  \texttt{type\_id} & (IN): The datatype of the dataset.\\
+  \texttt{space\_id} & (IN): The dataspace of the dataset.\\
+  \texttt{dcpl\_id} & (IN): The dataset creation property list.\\
+  \texttt{dapl\_id} & (IN): The dataset access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{dataset: open}
+The \texttt{open} callback in the dataset class opens a dataset
+object in the container of the location object and returns a pointer
+to the dataset structure containing information to access the dataset
+in future calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void *(*open)(void *obj, H5VL_loc_params_t *loc_params, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to an object where the dataset needs to be
+  opened or where the look-up of the target object needs to start.\\
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
+  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
+  \texttt{name} & (IN): The name of the dataset to be opened.\\
+  \texttt{dapl\_id} & (IN): The dataset access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{dataset: read}
+The \texttt{read} callback in the dataset class  reads data from
+the dataset object and returns an \texttt{herr\_t} indicating success or
+failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*read)(void *dset, hid_t mem_type_id, hid_t mem_space_id, 
+        hid_t file_space_id, hid_t dxpl_id, void *buf, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{dset} & (IN): Pointer to the dataset object.\\
+  \texttt{mem\_type\_id} & (IN): The memory datatype of the data.\\
+  \texttt{mem\_space\_id} & (IN): The memory dataspace selection.\\
+  \texttt{file\_space\_id} & (IN): The file dataspace selection.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{buf} & (OUT): Data buffer to be read into.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{dataset: write}
+The \texttt{write} callback in the dataset class writes data to
+the dataset object and returns an \texttt{herr\_t} indicating success or
+failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, 
+        hid_t file_space_id, hid_t dxpl_id, const void * buf, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{dset} & (IN): Pointer to the dataset object.\\
+  \texttt{mem\_type\_id} & (IN): The memory datatype of the data.\\
+  \texttt{mem\_space\_id} & (IN): The memory dataspace selection.\\
+  \texttt{file\_space\_id} & (IN): The file dataspace selection.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{buf} & (IN): Data buffer to be written from.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{dataset: get}
+The \texttt{get} callback in the dataset class retrieves
+information about the dataset as specified in the \texttt{get\_type}
+parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*get)(void *dset, H5VL_dataset_get_t get_type, 
+        hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+The \texttt{get\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* types for dataset GET callback */
+typedef enum H5VL_dataset_get_t {                                                
+    H5VL_DATASET_GET_DAPL,                  /* access property list                */
+    H5VL_DATASET_GET_DCPL,                  /* creation property list              */
+    H5VL_DATASET_GET_OFFSET,                /* offset                              */
+    H5VL_DATASET_GET_SPACE,                 /* dataspace                           */
+    H5VL_DATASET_GET_SPACE_STATUS,          /* space  status                       */
+    H5VL_DATASET_GET_STORAGE_SIZE,          /* storage size                        */
+    H5VL_DATASET_GET_TYPE                   /* datatype                            */
+} H5VL_dataset_get_t; 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{dset} & (IN): The dataset object where information needs to be
+  retrieved from.\\
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
+
+\begin{itemize}
+\item \texttt{H5VL\_DATASET\_GET\_DAPL}, to retrieve the dataset access
+  property list of the dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
+    dataset access property list.
+  \end{enumerate}
+
+\item \texttt{H5VL\_DATASET\_GET\_DCPL}, to retrieve the dataset creation
+  property list of the dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
+    dataset creation property list.
+  \end{enumerate}
+
+\item \texttt{H5VL\_DATASET\_GET\_OFFSET}, to retrieve the offset of the
+  dataset specified in \texttt{obj} in the container:
+  \begin{enumerate}
+  \item \texttt{haddr\_t *ret} (OUT): buffer for the offset of the
+    dataset in the container.
+  \end{enumerate}
+
+\item \texttt{H5VL\_DATASET\_GET\_SPACE}, to retrieve the dataspace of the
+  dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
+    dataset dataspace.
+  \end{enumerate}
+
+\item \texttt{H5VL\_DATASET\_GET\_SPACE\_STATUS}, to retrieve the
+  information whether space has been allocated for the dataset:
+  \begin{enumerate}
+  \item \texttt{H5D\_space\_status\_t *allocation} (OUT): buffer for the
+    space status.
+  \end{enumerate}
+
+\item \texttt{H5VL\_DATASET\_GET\_STORAGE\_SIZE}, to retrieve the storage
+  size of the dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hsize\_t *ret} (OUT): buffer for the storage size of
+    the dataset in the container.
+  \end{enumerate}
+
+\item \texttt{H5VL\_DATASET\_GET\_TYPE}, to retrieve the datatype of the
+  dataset specified in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
+    dataset datatype.
+  \end{enumerate}
+\end{itemize}
+
+\subsubsection{dataset: specific}
+The \texttt{specific} callback in the dataset class implements specific operations on HDF5 datasets as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*specific)(void *obj, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+The \texttt{specific\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* types for dataset SPECFIC callback */
+typedef enum H5VL_dataset_specific_t {                                           
+    H5VL_DATASET_SET_EXTENT,                /* H5Dset_extent                       */
+    H5VL_DATASET_FLUSH,                     /* H5Dflush                            */
+    H5VL_DATASET_REFRESH                    /* H5Drefresh                          */
+} H5VL_dataset_specific_t;
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The dset  where the operation needs
+  to happen.\\
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
+
+\begin{itemize}
+\item \texttt{H5VL\_DATASET\_SET\_EXTENT}, changes the extent of the dataset dimensions:
+  \begin{enumerate}
+  \item \texttt{hsize\_t size} (IN): Array containing the new magnitude of each dimension of the dataset. 
+  \end{enumerate}
+\item \texttt{H5VL\_DATASET\_FLUSH}, flushes a dataset:
+  \begin{enumerate}
+  \item \texttt{hid\_t dset\_id} (IN): The dataset ID. Needed so that the refreshed data can be associated with the old ID. 
+  \end{enumerate}
+\item \texttt{H5VL\_DATASET\_REFRESH}, clears a dataset's buffers and reloads from disk:
+  \begin{enumerate}
+  \item \texttt{hid\_t dset\_id} (IN): The dataset ID. Needed so that the refreshed data can be associated with the old ID. 
+  \end{enumerate}
+\end{itemize}
+
+\subsubsection{dataset: optional}
+The \texttt{optional} callback in the dataset class implements connector specific operations on an HDF5 dataset. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each connector should be able to parse the \texttt{va\_list arguments} if it has connector specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+\subsubsection{dataset: close}
+The \texttt{close} callback in the dataset class terminates access
+to the dataset object and free all resources it was consuming and
+returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*close)(void *dset, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{dset} & (IN): Pointer to the dataset object.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+%%%%%%%%%%%%%%%%%%%%%%
+% DATATYPE CALLBACKS %
+%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Datatype Callbacks}
+The HDF5 datatype routines (H5T) allow users to create and manage HDF5
+datatypes. Those routines are divided into two categories. One that
+operates on all types of datatypes but do not modify the contents of
+the container (all in memory), and others that operate on named
+datatypes by accessing the container. When a user creates an HDF5
+datatype, it is still an object in memory space (transient datatype)
+that has not been added to the HDF5 containers. Only when a user
+commits the HDF5 datatype, it becomes persistent in the
+container. Those are called named/committed datatypes. The transient
+H5T routines should work on named datatypes nevertheless.
+
+All the H5T API routines that modify the HDF5 container map to one of
+the named datatype callback routines in this class that the connector needs to
+implement.
+
+\begin{lstlisting}[caption={Structure for datatype callback routines, H5VLconnector.h}, captionpos=b, label={lst:H5Tclass}]
+typedef struct H5VL_datatype_class_t {                                           
+    void *(*commit)(void *obj, const H5VL_loc_params_t *loc_params, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
+    void *(*open)(void *obj, const H5VL_loc_params_t *loc_params, const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);
+    herr_t (*get)   (void *obj, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*specific)(void *obj, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); 
+    herr_t (*close) (void *dt, hid_t dxpl_id, void **req);                       
+} H5VL_datatype_class_t; 
+\end{lstlisting}
+
+\subsubsection{datatype: commit}
+The \texttt{commit} callback in the named datatype class creates a datatype object in the container of the location object and
+returns a pointer to the datatype structure containing information to access the datatype in future calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void *(*commit)(void *obj, H5VL_loc_params_t *loc_params, 
+        const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, 
+        hid_t tapl_id, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to an object where the datatype needs
+  to be committed or where the look-up of the target object needs to
+  start.\\
+  \texttt{loc\_params} & (IN): Pointer to location parameters as explained in
+  Section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
+  \texttt{name} & (IN): The name of the datatype to be created.\\
+  \texttt{type\_id} & (IN): The transient datatype identifier to be
+  committed. \\
+  \texttt{lcpl\_id} & (IN): The link creation property list. \\
+  \texttt{tcpl\_id} & (IN): The datatype creation property list.\\
+  \texttt{tapl\_id} & (IN): The datatype access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{datatype: open}
+The \texttt{open} callback in the named datatype class opens a
+previously committed datatype object in the container of the location
+object and returns a pointer to the datatype structure containing
+information to access the datatype in future calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void *(*open) (void *obj, H5VL_loc_params_t *loc_params, 
+        const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to an object where the datatype needs
+  to be opened or where the look-up of the target object needs to
+  start.\\
+  \texttt{loc\_params} & (IN): Pointer to location parameters as explained in
+  Section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
+  \texttt{name} & (IN): The name of the datatype to be opened.\\
+  \texttt{tapl\_id} & (IN): The datatype access property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{datatype: get}
+The \texttt{get} callback in the named datatype class retrieves
+information about the named datatype as specified in the \texttt{get\_type}
+parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*get) (void *obj, H5VL_datatype_get_t get_type, 
+        hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+The \texttt{get\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* types for datatype GET callback */
+typedef enum H5VL_datatype_get_t {                                               
+    H5VL_DATATYPE_GET_BINARY,               /* get serialized form of transient type    */
+    H5VL_DATATYPE_GET_TCPL                  /* datatype creation property list          */
+} H5VL_datatype_get_t; 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The named datatype to retrieve information from.\\
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
+
+\begin{itemize}
+\item \texttt{H5VL\_DATATYPE\_GET\_BINARY}, to retrieve the serialized original transient HDF5 datatype that was committed, or
+return the size that is required for it be serialized if the passed in buffer is \texttt{NULL}. The HDF5 library provides two functions to
+encode and decode datatypes in their transient form, \texttt{H5Tencode()} and \texttt{H5Tdecode()}.
+When a datatype is committed, the connector is required to keep the serialized form of the transient datatype stored somewhere in the container (which is usually the case anyway when committing a named datatype), so it can be retrieved with this call.
+This is needed to generate the higher level HDF5 datatype identifier that allows all the H5T ``transient'' routines to work properly on the named datatype.
+  \begin{enumerate}
+  \item \texttt{ssize\_t *nalloc} (OUT): buffer to store the total size of the serialized datatype.
+  \item \texttt{void *buf} (OUT): buffer to store the serialized datatype.
+  \item \texttt{size\_t size} (IN): size of the passed in buffer.
+  \end{enumerate}
+
+\item \texttt{H5VL\_DATATYPE\_GET\_TCPL}, to retrieve the datatype
+  creation property list:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
+    type creation property list.
+  \end{enumerate}
+\end{itemize}
+
+\subsubsection{datatype: specific}
+The \texttt{specific} callback in the datatype class implements specific operations on HDF5 named datatypes as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+The \texttt{specific\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* types for datatype SPECFIC callback */                                        
+typedef enum H5VL_datatype_specific_t {                                          
+    H5VL_DATATYPE_FLUSH,                                                         
+    H5VL_DATATYPE_REFRESH                                                        
+} H5VL_datatype_specific_t;  
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): Pointer to location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
+
+\begin{itemize}
+\item \texttt{H5VL\_DATATYPE\_FLUSH}, flushes a datatype:
+  \begin{enumerate}
+  \item \texttt{hid\_t type\_id} (IN): The datatype ID. Needed so that the refreshed data can be associated with the old ID. 
+  \end{enumerate}
+\item \texttt{H5VL\_DATATYPE\_REFRESH}, clears a datatype's buffers and reloads from disk:
+  \begin{enumerate}
+  \item \texttt{hid\_t type\_id} (IN): The datatype ID. Needed so that the refreshed data can be associated with the old ID. 
+  \end{enumerate}
+\end{itemize}
+
+\subsubsection{datatype: optional}
+The \texttt{optional} callback in the datatype class implements connector specific operations on an HDF5 datatype. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each connector should be able to parse the \texttt{va\_list arguments} if it has connector specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+\subsubsection{datatype: close}
+The \texttt{close} callback in the named datatype class terminates
+access to the datatype object and free all resources it was
+consuming and returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*close) (void *dt, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{dt} & (IN): Pointer to the datatype object.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+%%%%%%%%%%%%%%%%%%
+% FILE CALLBACKS %
+%%%%%%%%%%%%%%%%%%
+
+\subsection{File Callbacks}
 The file API routines (H5F) allow HDF5 users to create and manage HDF5
 containers. All the H5F API routines that modify the HDF5 container
-map to one of the file callback routines in this class that the plugin
-needs to implement, Listing \ref{lst:Fileclass}.
-
-\begin{lstlisting}[caption={File class for file API routines, H5VLpublic.h}, captionpos=b, label={lst:Fileclass}]
+map to one of the file callback routines in this class that the connector
+needs to implement.
+
+\begin{lstlisting}[caption={File class for file API routines, H5VLconnector.h}, captionpos=b, label={lst:Fileclass}]
 typedef struct H5VL_file_class_t {                                               
@@
 
+\subsubsection{file: create}
 The \texttt{create} callback in the file class should create a container
-and returns a pointer to the file structure created by the plugin containing information to
+and returns a pointer to the file structure created by the connector containing information to
 access the container in future calls.\medskip
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
 \hspace*{\fill}
+
+\subsubsection{file: open}
 The \texttt{open} callback in the file class should open a container and
-returns a pointer to the file structure created by the plugin containing information to
+returns a pointer to the file structure created by the connector containing information to
 access the container in future calls.\bigskip
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{file: get}
 The \texttt{get} callback in the file class should retrieve
@@
 typedef enum H5VL_file_get_t {                                                   
+    H5VL_FILE_GET_CONT_INFO,                /* file get container info              */
     H5VL_FILE_GET_FAPL,                     /* file access property list            */
     H5VL_FILE_GET_FCPL,                     /* file creation property list          */
+    H5VL_FILE_GET_FILENO,                   /* file number                          */
     H5VL_FILE_GET_INTENT,                   /* file intent                          */
@@
     H5VL_FILE_GET_OBJ_COUNT,                /* object count in file                 */
-    H5VL_FILE_GET_OBJ_IDS,   /* object ids in file          */
-    H5VL_OBJECT_GET_FILE     /* retrieve or resurrect file of object */
+    H5VL_FILE_GET_OBJ_IDS                   /* object ids in file                   */
 } H5VL_file_get_t; 
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
+  operation created by the connector.\\
   \texttt{arguments} & (IN/OUT): argument list containing parameters and
@@
 \begin{itemize}
+\item \texttt{H5VL\_OBJECT\_GET\_CONT\_INFO}, get the container that the object
+  belongs to:
+  \begin{enumerate}
+  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
+  \item \texttt{void **ret} (OUT): pointer to the file structure returned
+    by the connector.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_GET\_FAPL}, to retrieve the file access
+  property list:
+  \begin{enumerate}
+  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
+    file access property list.
+  \end{enumerate}
+
 \item \texttt{H5VL\_FILE\_GET\_FCPL}, to retrieve the file creation
@@
 
-\item \texttt{H5VL\_FILE\_GET\_FAPL}, to retrieve the file access
-  property list:
+\item \texttt{H5VL\_FILE\_GET\_FILENO}, to retrieve the file's file number:
   \begin{enumerate}
   \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    file access property list.
+    file creation property list.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_GET\_INTENT}, get access intent of the
+  container:
+  \begin{enumerate}
+  \item \texttt{unsigned *ret} (OUT): buffer for the intent value.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_GET\_NAME}, get container name an object
+  belongs to:
+  \begin{enumerate}
+  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
+  \item \texttt{size\_t size} (IN): size of the buffer for the file name.
+  \item \texttt{char *name} (OUT): buffer for the file name.
+  \item \texttt{ssize\_t *ret} (OUT): buffer for the entire size of the
+    file name.
   \end{enumerate}
@@
 
-\item \texttt{H5VL\_FILE\_GET\_INTENT}, get access intent of the
-  container:
-  \begin{enumerate}
-  \item \texttt{unsigned *ret} (OUT): buffer for the intent value.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_GET\_NAME}, get container name an object
-  belongs to:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
-  \item \texttt{size\_t size} (IN): size of the buffer for the file name.
-  \item \texttt{char *name} (OUT): buffer for the file name.
-  \item \texttt{ssize\_t *ret} (OUT): buffer for the entire size of the
-    file name.
-  \end{enumerate}
-
-\item \texttt{H5VL\_OBJECT\_GET\_FILE}, get the container that the object
-  belongs to:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
-  \item \texttt{void **ret} (OUT): pointer to the file structure returned
-    by the plugin.
-  \end{enumerate}
 \end{itemize}
 \end{mdframed}
+
+\subsubsection{file: specific}
 The \texttt{specific} callback in the file class implements specific operations on HDF5 files as specified in the \texttt{specific\_type} parameter.
@@
 typedef enum H5VL_file_specific_t {                                              
+    H5VL_FILE_POST_OPEN,                    /* Adjust file after open, with wrapping context */
     H5VL_FILE_FLUSH,                        /* Flush file                       */
+    H5VL_FILE_REOPEN,                       /* Reopen the file                  */
+    H5VL_FILE_MOUNT,                        /* Mount a file                     */
+    H5VL_FILE_UNMOUNT,                      /* Unmount a file                   */
     H5VL_FILE_IS_ACCESSIBLE,                /* Check if a file is accessible    */
-    H5VL_FILE_MOUNT,                  /* Mount a file */
-    H5VL_FILE_UNMOUNT                 /* Un-Mount a file */
+    H5VL_FILE_DELETE                        /* Delete a file                    */
 } H5VL_file_specific_t;
@@
 \begin{itemize}
-\item \texttt{H5VL\_FILE\_FLUSH}, flushes all buffers associated with the container to disk:
+\item \texttt{H5VL\_FILE\_POST\_OPEN}, adjust a file after opening it:
   \begin{enumerate}
@@
 
-\item \texttt{H5VL\_FILE\_IS\_ACCESSIBLE}, checks if a container is
-  accessible using a specific file access property list:
-  \begin{enumerate}
-  \item \texttt{hid\_t *fapl\_id} (IN): file access property list.
-  \item \texttt{char *name} (IN): name of the container to check.
-  \item \texttt{htri\_t *result} (OUT): buffer for the result; 0 if no, 1
-    if yes.
+\item \texttt{H5VL\_FILE\_FLUSH}, flushes all buffers associated with the container to disk:
+  \begin{enumerate}
+  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
+  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_REOPEN}, reopens a file:
+  \begin{enumerate}
+  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
+  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
   \end{enumerate}
@@
   \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_IS\_ACCESSIBLE}, checks if a container is
+  accessible using a specific file access property list:
+  \begin{enumerate}
+  \item \texttt{hid\_t *fapl\_id} (IN): file access property list.
+  \item \texttt{char *name} (IN): name of the container to check.
+  \item \texttt{htri\_t *result} (OUT): buffer for the result; 0 if no, 1
+    if yes.
+  \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_DELETE}, deletes a file:
+  \begin{enumerate}
+  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
+  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
+  \end{enumerate}
  \end{itemize}
@@
 
-The \texttt{optional} callback in the file class implements plugin specific operations on an HDF5 container. It returns an 
+\subsubsection{file: optional}
+The \texttt{optional} callback in the file class implements connector specific operations on an HDF5 container. It returns an 
 \texttt{herr\_t} indicating success or failure. \bigskip
@@
   \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the connector.\\
   \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
@@
 
-Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-For example, in the native plugin, the first argument in the \texttt{va\_list} is the optional argument type enum defined as follows:
-
-\begin{lstlisting}
-/* types for all file optional operations */
-typedef enum H5VL_file_optional_t {
-    H5VL_FILE_CLEAR_ELINK_CACHE,  /* Clear external link cache         */
-    H5VL_FILE_GET_FILE_IMAGE,     /* file image                        */
-    H5VL_FILE_GET_FREE_SECTIONS,  /* file free selections              */
-    H5VL_FILE_GET_FREE_SPACE,     /* file freespace                    */
-    H5VL_FILE_GET_INFO,           /* file info                         */
-    H5VL_FILE_GET_MDC_CONF,       /* file metadata cache configuration */
-    H5VL_FILE_GET_MDC_HR,         /* file metadata cache hit rate      */
-    H5VL_FILE_GET_MDC_SIZE,       /* file metadata cache size          */
-    H5VL_FILE_GET_SIZE,           /* file size                         */
-    H5VL_FILE_GET_VFD_HANDLE,     /* file VFD handle                   */
-    H5VL_FILE_REOPEN,             /* reopen the file                   */
-    H5VL_FILE_RESET_MDC_HIT_RATE, /* get metadata cache hit rate       */
-    H5VL_FILE_SET_MDC_CONFIG      /* set metadata cache configuration  */
-} H5VL_file_optional_t;
-\end{lstlisting}
-
-The remaining arguments are parsed depending on the optional operation type.
-
-%\begin{itemize}
-%
-%\item \texttt{H5VL\_FILE\_GET\_SIZE}, retrieve the size of the container
-%  in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{hsize\_t *ret} (OUT): file size.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_GET\_FILE\_IMAGE}, retrieve file image from the
-%  container in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{void *buf\_ptr} (OUT): buffer to return the file image.
-%  \item \texttt{ssize\_t *ret} (OUT): buffer for the total size needed for
-%    the file image.
-%  \item \texttt{size\_t buf\_len} (IN): size of the buffer passed in.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_GET\_FREE\_SPACE}, retrieve amount of free
-%  space in the container in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{hssize\_t *ret} (OUT): buffer for the free space.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_GET\_FREE\_SECTIONS}, retrieve free sections from the
-%  container in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{H5F\_sect\_info\_t *sinfo} (OUT): pointer to the section
-%    info structure to fill.
-%  \item \texttt{ssize\_t *ret} (OUT): buffer for the total number of free
-%    sections.
-%  \item \texttt{H5F\_mem\_t type} (IN): type of the memory space to check
-%    for.
-%  \item \texttt{size\_t nsects} (IN): number of section allocate in \texttt{sinfo}.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_GET\_INFO}, retrieve file info from the
-%  object in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
-%  \item \texttt{H5F\_info2\_t *finfo} (OUT): pointer to info structure to fill.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_GET\_MDC\_CONF}, retrieve the meta data cache
-%  configuration from the container in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
-%  \item \texttt{H5AC\_cache\_config\_t *conf} (OUT): pointer to
-%    configuration structure to fill.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_GET\_MDC\_HR}, retrieve the meta data cache
-%  hit rate from the container in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{double *ret} (OUT): buffer for the hit rate.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_GET\_MDC\_SIZE}, retrieve the meta data cache
-%  size information from the container in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{size\_t max\_size\_ptr} (OUT): buffer for maximum size.
-%  \item \texttt{size\_t min\_clean\_size\_ptr} (OUT): buffer for minimum
-%    clean size.
-%  \item \texttt{size\_t cur\_size\_ptr} (OUT): buffer for current size.
-%  \item \texttt{int cur\_num\_entries\_ptr} (OUT): buffer for number of
-%    current cache entries.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_GET\_VFD\_HANDLE}, retrieve the virtual file
-%  driver handle from the container in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{void **handle} (OUT): pointer to a buffer the plugin sets
-%    to the VFD handle.
-%  \item \texttt{hid\_t fapl} (IN): File access property list.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_CLEAR\_ELINK\_CACHE}, clears the external link
-%  file cache. Takes no extra arguments.
-%
-%\item \texttt{H5VL\_FILE\_REOPEN}, reopen the container in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{void **ret} (OUT): pointer to be set to the opened file
-%    structure.
-%  \end{enumerate}
-%
-%\item \texttt{H5VL\_FILE\_RESET\_MDC\_HIT\_RATE}, resets the hit rate
-%  statistics for the metadata cache on the container in \texttt{
-%    obj}. Takes no extra arguments.
-%
-%\item \texttt{H5VL\_FILE\_SET\_MDC\_CONFIG}, sets the meta data cache
-%  configuration for the container in \texttt{obj}:
-%  \begin{enumerate}
-%  \item \texttt{H5AC\_cache\_config\_t *conf} (IN): pointer to
-%    configuration structure to use.
-%  \end{enumerate}
-%
-%\end{itemize}
-
+Each connector should be able to parse the \texttt{va\_list arguments} if it has connector specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+\subsubsection{file: close}
 The \texttt{close} callback in the file class should terminate access to
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-\subsection{The Group Function Callbacks}
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+%%%%%%%%%%%%%%%%%%%
+% GROUP CALLBACKS %
+%%%%%%%%%%%%%%%%%%%
+
+\subsection{Group Callbacks}
 The group API routines (H5G) allow HDF5 users to create and manage
@@
 map to one of the group callback routines in this class that the
-plugin needs to implement, Listing \ref{lst:Groupclass}.
-
-\begin{lstlisting}[caption={Structure for group callback routines, H5VLpublic.h}, captionpos=b, label={lst:Groupclass}]
+connector needs to implement.
+
+\begin{lstlisting}[caption={Structure for group callback routines, H5VLconnector.h}, captionpos=b, label={lst:Groupclass}]
 typedef struct H5VL_group_class_t {                                              
-    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
+    void *(*create)(void *obj, const H5VL_loc_params_t *loc_params, const char *name, hid_t lcpl_id, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
+    void *(*open)(void *obj, const H5VL_loc_params_t *loc_params, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
     herr_t (*get)(void *obj, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
@@
 
+\subsubsection{group: create}
 The \texttt{create} callback in the group class creates a group
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{group: open}
 The \texttt{open} callback in the group class opens a group object
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{group: get}
 The \texttt{get} callback in the group class retrieves information
@@
 typedef enum H5VL_group_get_t {                                                  
-    H5VL_GROUP_GET_GCPL,      /*group creation property list */
-    H5VL_GROUP_GET_INFO       /*group info                   */
+    H5VL_GROUP_GET_GCPL,                    /* group creation property list     */
+    H5VL_GROUP_GET_INFO                     /* group info                       */
 } H5VL_group_get_t; 
@@
 
-The \texttt{specific} callback in the group class currently does not require any functionality to be implemented and should be left as \texttt{NULL}.
-
-The \texttt{optional} callback in the group class implements plugin specific operations on an HDF5 group. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
+\subsubsection{group: specific}
+The \texttt{specific} callback in the group class implements specific operations on HDF5 groups as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+The \texttt{specific\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* types for group SPECFIC callback */                                           
+typedef enum H5VL_group_specific_t {                                             
+    H5VL_GROUP_FLUSH,                                                            
+    H5VL_GROUP_REFRESH                                                           
+} H5VL_group_specific_t;
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): The location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
+
+\begin{itemize}
+\item \texttt{H5VL\_GROUP\_FLUSH}, flushes a group:
+  \begin{enumerate}
+  \item \texttt{hid\_t grp\_id} (IN): The group ID. Needed so that the refreshed data can be associated with the old ID. 
+  \end{enumerate}
+\item \texttt{H5VL\_GROUP\_REFRESH}, clears a group's buffers and reloads from disk:
+  \begin{enumerate}
+  \item \texttt{hid\_t grp\_id} (IN): The group ID. Needed so that the refreshed data can be associated with the old ID. 
+  \end{enumerate}
+\end{itemize}
+
+\subsubsection{group: optional}
+The \texttt{optional} callback in the group class implements connector specific operations on an HDF5 group. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
 
@@
 
-Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
+Each connector should be able to parse the \texttt{va\_list arguments} if it has connector specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+\subsubsection{group: close}
 The \texttt{close} callback in the group class terminates access to
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-\subsection{The Dataset Function Callbacks}
-The dataset API routines (H5D) allow HDF5 users to create and manage
-HDF5 datasets. All the H5D API routines that modify the HDF5 container
-map to one of the dataset callback routines in this class that the
-plugin needs to implement, Listing \ref{lst:DSclass}.
-
-\begin{lstlisting}[caption={Structure for dataset callback routines, H5VLpublic.h}, captionpos=b, label={lst:DSclass}]
-typedef struct H5VL_dataset_class_t {
-    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
-    herr_t (*read)(void *dset, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t xfer_plist_id, void * buf, void **req);
-    herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t xfer_plist_id, const void * buf, void **req);
-    herr_t (*get)(void *obj, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*close) (void *dset, hid_t dxpl_id, void **req);
-} H5VL_dataset_class_t;
-\end{lstlisting}
-
-The \texttt{create} callback in the dataset class creates a dataset
-object in the container of the location object and returns a pointer
-to the dataset structure containing information to access the dataset
-in future calls.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): Pointer to an object where the dataset needs
-  to be created or where the look-up of the target object needs to
-  start.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
-  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
-  \texttt{name} & (IN): The name of the dataset to be created.\\
-  \texttt{dcpl\_id} & (IN): The dataset creation property list. It contains
-  all the dataset creation properties in addition to the dataset
-  datatype (an \texttt{hid\_t}), dataspace (an \texttt{hid\_t}), and the
-  link creation property list of the create operation (an \texttt{hid\_t}) that can be retrieved with the properties, \texttt{H5VL\_DSET\_TYPE\_ID}, \texttt{H5VL\_DSET\_SPACE\_ID},  and \texttt{H5VL\_DSET\_LCPL\_ID} respectively.\\
-  \texttt{dapl\_id} & (IN): The dataset access property list.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{open} callback in the dataset class opens a dataset
-object in the container of the location object and returns a pointer
-to the dataset structure containing information to access the dataset
-in future calls.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): Pointer to an object where the dataset needs to be
-  opened or where the look-up of the target object needs to start.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
-  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
-  \texttt{name} & (IN): The name of the dataset to be opened.\\
-  \texttt{dapl\_id} & (IN): The dataset access property list.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{read} callback in the dataset class  reads data from
-the dataset object and returns an \texttt{herr\_t} indicating success or
-failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*read)(void *dset, hid_t mem_type_id, hid_t mem_space_id, 
-        hid_t file_space_id, hid_t dxpl_id, void *buf, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{dset} & (IN): Pointer to the dataset object.\\
-  \texttt{mem\_type\_id} & (IN): The memory datatype of the data.\\
-  \texttt{mem\_space\_id} & (IN): The memory dataspace selection.\\
-  \texttt{file\_space\_id} & (IN): The file dataspace selection.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{buf} & (OUT): Data buffer to be read into.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{write} callback in the dataset class writes data to
-the dataset object and returns an \texttt{herr\_t} indicating success or
-failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, 
-        hid_t file_space_id, hid_t dxpl_id, const void * buf, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{dset} & (IN): Pointer to the dataset object.\\
-  \texttt{mem\_type\_id} & (IN): The memory datatype of the data.\\
-  \texttt{mem\_space\_id} & (IN): The memory dataspace selection.\\
-  \texttt{file\_space\_id} & (IN): The file dataspace selection.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{buf} & (IN): Data buffer to be written from.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{get} callback in the dataset class retrieves
-information about the dataset as specified in the \texttt{get\_type}
-parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*get)(void *dset, H5VL_dataset_get_t get_type, 
-        hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for dataset GET callback */
-typedef enum H5VL_dataset_get_t {
-    H5VL_DATASET_GET_DAPL,                  /* access property list */
-    H5VL_DATASET_GET_DCPL,                  /* creation property list */
-    H5VL_DATASET_GET_OFFSET,                /* offset */
-    H5VL_DATASET_GET_SPACE,                 /* dataspace */
-    H5VL_DATASET_GET_SPACE_STATUS,          /* space  status */
-    H5VL_DATASET_GET_STORAGE_SIZE,          /* storage size */
-    H5VL_DATASET_GET_TYPE                   /* datatype */
-} H5VL_dataset_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{dset} & (IN): The dataset object where information needs to be
-  retrieved from.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_DATASET\_GET\_DAPL}, to retrieve the dataset access
-  property list of the dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    dataset access property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_DCPL}, to retrieve the dataset creation
-  property list of the dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    dataset creation property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_OFFSET}, to retrieve the offset of the
-  dataset specified in \texttt{obj} in the container:
-  \begin{enumerate}
-  \item \texttt{haddr\_t *ret} (OUT): buffer for the offset of the
-    dataset in the container.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_SPACE}, to retrieve the dataspace of the
-  dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    dataset dataspace.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_SPACE\_STATUS}, to retrieve the
-  information whether space has been allocated for the dataset:
-  \begin{enumerate}
-  \item \texttt{H5D\_space\_status\_t *allocation} (OUT): buffer for the
-    space status.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_STORAGE\_SIZE}, to retrieve the storage
-  size of the dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hsize\_t *ret} (OUT): buffer for the storage size of
-    the dataset in the container.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_TYPE}, to retrieve the datatype of the
-  dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    dataset datatype.
-  \end{enumerate}
-\end{itemize}
-
-The \texttt{specific} callback in the dataset class implements specific operations on HDF5 datasets as specified in the \texttt{specific\_type} parameter.
-It returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*specific)(void *obj, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for dataset SPECFIC callback */
-typedef enum H5VL_dataset_specific_t {
-    H5VL_DATASET_SET_EXTENT           /* H5Dset_extent */
-} H5VL_dataset_specific_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The dset  where the operation needs
-  to happen.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_DATASET\_SET\_EXTENT}, changes the extent of the dataset dimensions:
-  \begin{enumerate}
-  \item \texttt{hsize\_t size} (IN): Array containing the new magnitude of each dimension of the dataset. 
-  \end{enumerate}
-\end{itemize}
-
-The \texttt{optional} callback in the dataset class implements plugin specific operations on an HDF5 dataset. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
-The \texttt{close} callback in the dataset class terminates access
-to the dataset object and free all resources it was consuming and
-returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*close)(void *dset, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{dset} & (IN): Pointer to the dataset object.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-\subsection{The Attribute Function Callbacks}
-The attribute API routines (H5A) allow HDF5 users to create and manage
-HDF5 attributes. All the H5A API routines that modify the HDF5
-container map to one of the attribute callback routines in this
-class that the plugin needs to implement, Listing \ref{lst:ATTRclass}.
-
-\begin{lstlisting}[caption={Structure for attribute callback routines, H5VLpublic.h}, captionpos=b, label={lst:ATTRclass}]
-typedef struct H5VL_attr_class_t {
-    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *attr_name, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char *attr_name, hid_t aapl_id, hid_t dxpl_id, void **req);
-    herr_t (*read)(void *attr, hid_t mem_type_id, void *buf, hid_t dxpl_id, void **req);
-    herr_t (*write)(void *attr, hid_t mem_type_id, const void *buf, hid_t dxpl_id, void **req);
-    herr_t (*get)(void *obj, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*close) (void *attr, hid_t dxpl_id, void **req);
-} H5VL_attr_class_t;
-\end{lstlisting}
-
-The \texttt{create} callback in the attribute class creates an
-attribute object in the container of the location object and
-returns a pointer to the attribute structure containing information to
-access the attribute in future calls. \bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    void *(*create)(void *obj, H5VL_loc_params_t loc_params, 
-        const char *attr_name, hid_t acpl_id, hid_t aapl_id, 
-        hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): Pointer to an object where the attribute needs
-  to be created or where the look-up of the target object needs to
-  start.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
-  Section~\ref{sec:map}.\\
-  \texttt{attr\_name} & (IN): The name of the attribute to be created.\\
-  \texttt{acpl\_id} & (IN): The attribute creation property list. It contains
-  all the attribute creation properties in addition to the attribute
-  datatype (an \texttt{hid\_t}) and dataspace (an \texttt{hid\_t}) that can
-  be retrieved with the properties, \texttt{H5VL\_ATTR\_TYPE\_ID} and
-  \texttt{H5VL\_ATTR\_SPACE\_ID}.\\
-  \texttt{aapl\_id} & (IN): The attribute access property list.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{open} callback in the attribute class opens an
-attribute object in the container of the location object and returns a
-pointer to the attribute structure containing information to access
-the attribute in future calls. \bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
-        const char *attr_name, hid_t aapl_id, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): Pointer to an object where the attribute needs to be
-  opened or where the look-up of the target object needs to start.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
-  Section~\ref{sec:map}.\\
-  \texttt{attr\_name} & (IN): The name of the attribute to be opened.\\
-  \texttt{aapl\_id} & (IN): The attribute access property list.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{read} callback in the attribute class reads data from
-the attribute object and returns an \texttt{herr\_t} indicating success or
-failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*read)(void *attr, hid_t mem_type_id, void *buf, 
-        hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{attr} & (IN): Pointer to the attribute object.\\
-  \texttt{mem\_type\_id} & (IN): The memory datatype of the attribute.\\
-  \texttt{buf} & (OUT): Data buffer to be read into.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{write} callback in the attribute class writes data to
-the attribute object and returns an \texttt{herr\_t} indicating success or
-failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*write)(void *attr, hid_t mem_type_id, const void *buf, 
-        hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{attr} & (IN): Pointer to the attribute object.\\
-  \texttt{mem\_type\_id} & (IN): The memory datatype of the attribute.\\
-  \texttt{buf} & (IN): Data buffer to be written.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{get} callback in the attribute class retrieves
-information about the attribute as specified in the \texttt{get\_type}
-parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*get)(void *obj, H5VL_attr_get_t get_type, hid_t dxpl_id, 
-        void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for attribute GET callback */
-typedef enum H5VL_attr_get_t {
-    H5VL_ATTR_GET_ACPL,               /* creation property list */
-    H5VL_ATTR_GET_INFO,               /* info */
-    H5VL_ATTR_GET_NAME,               /* access property list */
-    H5VL_ATTR_GET_SPACE,              /* dataspace */
-    H5VL_ATTR_GET_STORAGE_SIZE,       /* storage size */
-    H5VL_ATTR_GET_TYPE                 /* datatype */
-} H5VL_attr_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{attr} & (IN): An attribute or location object where information
-  needs to be retrieved from.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-
-\item \texttt{H5VL\_ATTR\_GET\_ACPL}, to retrieve the attribute creation
-  property list of the attribute specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    attribute creation property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_INFO}, to retrieve the attribute info:
-  \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
-    explained in Section~\ref{sec:map}. 
-  \item \texttt{H5A\_info\_t *ainfo} (OUT): info structure to fill the
-    attribute info in.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_NAME}, to retrieve an attribute name on a
-  particular object specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
-    explained in Section~\ref{sec:map}. The type could be either
-    \texttt{H5VL\_OBJECT\_BY\_SELF} meaning \texttt{obj} is the attribute,
-    or \texttt{H5VL\_OBJECT\_BY\_IDX} meaning the attribute to retrieve
-    the name for should be looked up using the index information on
-    the object in \texttt{obj} and the index information in \texttt{loc\_params}.
-  \item \texttt{size\_t buf\_size} (IN): the size of the buffer to store
-    the name in.
-  \item \texttt{void *buf} (OUT): Buffer to store the name in.
-  \item \texttt{ssize\_t *ret\_val} (OUT): return the actual size needed
-    to store the fill attribute name.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_SPACE}, to retrieve the dataspace of the
-  attribute specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    attribute dataspace.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_STORAGE\_SIZE}, to retrieve the storage
-  size of the attribute specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hsize\_t *ret} (OUT): buffer for the storage size of
-    the attribute in the container.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_TYPE}, to retrieve the datatype of the
-  attribute specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    attribute datatype.
-  \end{enumerate}
-
-\end{itemize}
-
-The \texttt{specific} callback in the attribute class implements specific operations on HDF5 attributes as specified in the \texttt{specific\_type} parameter.
-It returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for attribute SPECFIC callback */
-typedef enum H5VL_attr_specific_t {
-    H5VL_ATTR_DELETE,                 /* H5Adelete(_by_name/idx) */
-    H5VL_ATTR_EXISTS,                 /* H5Aexists(_by_name) */
-    H5VL_ATTR_ITER,                   /* H5Aiterate(_by_name) */
-    H5VL_ATTR_RENAME                  /* H5Arename(_by_name) */
-} H5VL_attr_specific_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in Section~\ref{sec:map}.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_ATTR\_DELETE}, to delete an attribute on an object:
-  \begin{enumerate}
-  \item \texttt{char *attr\_name} (IN): the name of the attribute to delete.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_EXISTS}, to check if an attribute exists on a
-  particular object specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
-    explained in Section~\ref{sec:map}.
-  \item \texttt{char *attr\_name} (IN): the attribute name to check.
-  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_ITER}, to iterate over all attributes of an object and call a user-specified callback on each one:
-  \begin{enumerate}
-  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
-  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
-  \item \texttt{hsize\_t *idx} (IN/OUT): Initial and return offset within index.\\
-  \item \texttt{H5A\_operator2\_t op} (IN): User-defined function to pass each attribute to. \\
-  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_RENAME}, to rename an attribute on an object:
-  \begin{enumerate}
-  \item \texttt{char *old\_name} (IN): the original name of the attribute.
-  \item \texttt{char *new\_name} (IN): the new name to assign for the attribute.
-  \end{enumerate}
-
-\end{itemize}
-
-The \texttt{optional} callback in the attribute class implements plugin specific operations on an HDF5 attribute. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
-The \texttt{close} callback in the attribute class terminates
-access to the attribute object and free all resources it was
-consuming, and returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*close)(void *attr, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{attr} & (IN): Pointer to the attribute object.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-\subsection{The Named Datatype Function Callbacks}
-The HDF5 datatype routines (H5T) allow users to create and manage HDF5
-datatypes. Those routines are divided into two categories. One that
-operates on all types of datatypes but do not modify the contents of
-the container (all in memory), and others that operate on named
-datatypes by accessing the container. When a user creates an HDF5
-datatype, it is still an object in memory space (transient datatype)
-that has not been added to the HDF5 containers. Only when a user
-commits the HDF5 datatype, it becomes persistent in the
-container. Those are called named/committed datatypes. The transient
-H5T routines should work on named datatypes nevertheless.
-
-All the H5T API routines that modify the HDF5 container map to one of
-the named datatype callback routines in this class that the plugin needs to
-implement, Listing \ref{lst:H5Tclass}.
-
-\begin{lstlisting}[caption={Structure for datatype callback routines, H5VLpublic.h}, captionpos=b, label={lst:H5Tclass}]
-typedef struct H5VL_datatype_class_t {
-    void *(*commit)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);
-    herr_t (*get)   (void *obj, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*close) (void *dt, hid_t dxpl_id, void **req);
-} H5VL_datatype_class_t;
-\end{lstlisting}
-
-The \texttt{commit} callback in the named datatype class creates a datatype object in the container of the location object and
-returns a pointer to the datatype structure containing information to access the datatype in future calls.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    void *(*commit)(void *obj, H5VL_loc_params_t loc_params, 
-        const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, 
-        hid_t tapl_id, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): Pointer to an object where the datatype needs
-  to be committed or where the look-up of the target object needs to
-  start.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
-  Section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
-  \texttt{name} & (IN): The name of the datatype to be created.\\
-  \texttt{type\_id} & (IN): The transient datatype identifier to be
-  committed. \\
-  \texttt{lcpl\_id} & (IN): The link creation property list. \\
-  \texttt{tcpl\_id} & (IN): The datatype creation property list.\\
-  \texttt{tapl\_id} & (IN): The datatype access property list.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{open} callback in the named datatype class opens a
-previously committed datatype object in the container of the location
-object and returns a pointer to the datatype structure containing
-information to access the datatype in future calls.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    void *(*open) (void *obj, H5VL_loc_params_t loc_params, 
-        const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): Pointer to an object where the datatype needs
-  to be opened or where the look-up of the target object needs to
-  start.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
-  Section~\ref{sec:map}. In this call, the location type is always \texttt{H5VL\_OBJECT\_BY\_SELF}. \\
-  \texttt{name} & (IN): The name of the datatype to be opened.\\
-  \texttt{tapl\_id} & (IN): The datatype access property list.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{get\_binary} callback in the named datatype class
-serializes the original transient HDF5 datatype that was committed, or
-returns the size that is required for it be serialized if the passed in
-buffer is \texttt{NULL}. The HDF5 library provides two functions to
-encode and decode datatypes in their transient form, \texttt{H5Tencode()}
-and \texttt{H5Tdecode()}. When a datatype is committed, the plugin is
-required to keep the serialized form of the transient datatype stored
-somewhere in the container (which is usually the case anyway when
-committing a named datatype), so it can be retrieved with this
-call. This is needed to generate the higher level HDF5 datatype
-identifier that allows all the H5T ``transient'' routines to work
-properly on the named datatype.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    ssize_t (*get_binary)(void *obj, unsigned char *buf, size_t size, 
-        hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): Pointer to the named datatype object.\\
-  \texttt{buf} & (OUT): Buffer to out the binary form of the datatype in.\\
-  \texttt{size} & (IN): The size of the buffer passed in (0 if NULL).\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{get} callback in the named datatype class retrieves
-information about the named datatype as specified in the \texttt{get\_type}
-parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*get) (void *obj, H5VL_datatype_get_t get_type, 
-        hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for datatype GET callback */
-typedef enum H5VL_datatype_get_t {
-    H5VL_DATATYPE_GET_BINARY,               /* get serialized form of transient type */
-    H5VL_DATATYPE_GET_TCPL                  /* datatype creation property list     */
-} H5VL_datatype_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The named datatype to retrieve information from.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_DATATYPE\_GET\_BINARY}, to retrieve the serialized original transient HDF5 datatype that was committed, or
-return the size that is required for it be serialized if the passed in buffer is \texttt{NULL}. The HDF5 library provides two functions to
-encode and decode datatypes in their transient form, \texttt{H5Tencode()} and \texttt{H5Tdecode()}.
-When a datatype is committed, the plugin is required to keep the serialized form of the transient datatype stored somewhere in the container (which is usually the case anyway when committing a named datatype), so it can be retrieved with this call.
-This is needed to generate the higher level HDF5 datatype identifier that allows all the H5T ``transient'' routines to work properly on the named datatype.
-  \begin{enumerate}
-  \item \texttt{ssize\_t *nalloc} (OUT): buffer to store the total size of the serialized datatype.
-  \item \texttt{void *buf} (OUT): buffer to store the serialized datatype.
-  \item \texttt{size\_t size} (IN): size of the passed in buffer.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATATYPE\_GET\_TCPL}, to retrieve the datatype
-  creation property list:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    type creation property list.
-  \end{enumerate}
-\end{itemize}
-
-The \texttt{specific} callback in the datatype class currently does not require any functionality to be implemented and should be left as \texttt{NULL}.
-
-The \texttt{optional} callback in the datatype class implements plugin specific operations on an HDF5 datatype. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
-The \texttt{close} callback in the named datatype class terminates
-access to the datatype object and free all resources it was
-consuming and returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*close) (void *dt, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{dt} & (IN): Pointer to the datatype object.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-\subsection{The Object Function Callbacks}
-The object API routines (H5O) allow HDF5 users to manage HDF5 group,
-dataset, and named datatype objects. All the H5O API routines that
-modify the HDF5 container map to one of the object callback routines
-in this class that the plugin needs to implement, Listing \ref{lst:H5Oclass}.
-
-\begin{lstlisting}[caption={Structure for object callback routines, H5VLpublic.h}, captionpos=b, label={lst:H5Oclass}]
-typedef struct H5VL_object_class_t {
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
-    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, const char *src_name, void *dst_obj, H5VL_loc_params_t loc_params2, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
-    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
-} H5VL_object_class_t;
-\end{lstlisting}
-
-The \texttt{open} callback in the object class opens the object in
-the container of the location object and returns a pointer to the
-object structure containing information to access the object in future
-calls.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
-        H5I_type_t *opened_type, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): Pointer to a file or group where the objecy needs to be
-  opened or where the look-up of the target object needs to start.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
-  Section~\ref{sec:map}.\\
-  \texttt{opened\_type} & (OUT): buffer to return the type of the object
-  opened (\texttt{H5I\_GROUP} or \texttt{H5I\_DATASET} or \texttt{H5I\_DATATYPE}).\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{copy} callback in the object class  copies the object
-from the source object to the destination object. It returns an \texttt{
-  herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, 
-        const char *src_name, void *dst_obj, 
-        H5VL_loc_params_t loc_params2, const char *dst_name,
-        hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{src\_obj} & (IN): Pointer to location of the source object to
-  be copied.\\
-  \texttt{loc\_params1} & (IN): The location parameters as explained in
-  Section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
-  \texttt{src\_name} & (IN): Name of the source object to
-  be copied.\\
-  \texttt{dst\_obj} & (IN): Pointer to location of the destination
-  object.\\
-  \texttt{loc\_params2} & (IN): The location parameters as explained in
-  Section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
-  \texttt{dst\_name} & (IN): Name to be assigned to the new copy.\\
-  \texttt{ocpypl\_id} & (IN): The object copy property list.\\
-  \texttt{lcpl\_id} & (IN): The link creation property list.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{get} callback in the object class retrieves information
-about the object as specified in the \texttt{get\_type} parameter.It
-returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
-        H5VL_object_get_t get_type, hid_t dxpl_id, 
-        void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* type for object GET callback */
-typedef enum H5VL_object_get_t {
-    H5VL_REF_GET_NAME,                 /* object name                       */
-    H5VL_REF_GET_REGION,               /* dataspace of region               */
-    H5VL_REF_GET_TYPE                  /* type of object                    */
-} H5VL_object_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): A location object where information needs to be
-  retrieved from.\\
-  \texttt{loc\_params} & (IN): The location parameters as
-  explained in Section~\ref{sec:map}.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_REF\_GET\_NAME}, to retrieve a name for a referenced object:
-  \begin{enumerate}
-  \item \texttt{ssize\_t *ret} (OUT): buffer to return the length of the
-    name.
-  \item \texttt{char* name} (OUT): buffer to copy the name into.
-  \item \texttt{size\_t size} (IN): size of the buffer name, if 0, return
-    only the buffer size needed.
-  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
-    query.
-  \item \texttt{void *ref} (IN): the region reference to query.
-  \end{enumerate}
-
-\item \texttt{H5VL\_REF\_GET\_REGION}, to retrieve a region reference
-  contained in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the dataspace created
-    from the region reference.
-  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference
-    (should be \texttt{H5R\_DATASET\_REGION}).
-  \item \texttt{void *ref} (IN): the region reference to open.
-  \end{enumerate}
-
-\item \texttt{H5VL\_REF\_GET\_TYPE}, to retrieve object type a reference
-  points to:
-  \begin{enumerate}
-  \item \texttt{H5O\_type\_t *type} (OUT): buffer to return the object type.
-  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
-    query.
-  \item \texttt{void *ref} (IN): the region reference to query.
-  \end{enumerate}
-\end{itemize}
-
-The \texttt{specific} callback in the object class implements specific operations on HDF5 objects as specified in the \texttt{specific\_type} parameter.
-It returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for object SPECIFIC callback */
-typedef enum H5VL_object_specific_t {
-    H5VL_OBJECT_CHANGE_REF_COUNT,      /* H5Oincr/decr_refcount              */
-    H5VL_OBJECT_EXISTS,                /* H5Oexists_by_name                  */
-    H5VL_OBJECT_VISIT,                 /* H5Ovisit(_by_name)                 */
-    H5VL_REF_CREATE                    /* H5Rcreate                          */
-} H5VL_object_specific_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in Section~\ref{sec:map}.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_OBJECT\_CHANGE\_REF\_COUNT}, to update the reference
-  count for the object in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{int ref\_count} (IN): reference count to set on the object.
-  \end{enumerate}
-
-\item \texttt{H5VL\_OBJECT\_EXISTS}, to check if an object with name
-  specified in \texttt{loc\_params} (type \texttt{H5VL\_OBJECT\_BY\_NAME})
-  exists:
-  \begin{enumerate}
-  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
-  \end{enumerate}
-
-\item \texttt{H5VL\_OBJECT\_VISIT}, to iterate over all objects starting at the location provided and call a user-specified callback on each one:
-  \begin{enumerate}
-  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
-  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
-  \item \texttt{H5O\_iterate\_t op} (IN): User-defined function to pass each object to. \\
-  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
-  \end{enumerate}
-
-\item \texttt{H5VL\_REF\_CREATE}, to create a reference of an object
-  under the location object \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{void *ref} (OUT): the region reference created.
-  \item \texttt{char* name} (IN): Name of the object at the location \texttt{obj}.
-  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
-    create.
-  \item \texttt{hid\_t* space\_id} (IN): Dataspace identifier with
-    selection. Used only for dataset region references; passed as -1 if
-    reference is an object reference, i.e., of type \texttt{H5R\_OBJECT}.
-  \end{enumerate}
-\end{itemize}
-
-The \texttt{optional} callback in the object class implements plugin specific operations on an HDF5 object. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
-\subsection{The Link Function Callbacks}
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+%%%%%%%%%%%%%%%%%%
+% LINK CALLBACKS %
+%%%%%%%%%%%%%%%%%%
+
+\subsection{Link Callbacks}
 The link API routines (H5L) allow HDF5 users to create and manage
@@
 map to one of the link callback routines in this class that the
-plugin needs to implement, Listing \ref{lst:H5Lclass}.
-
-\begin{lstlisting}[caption={Structure for link callback routines, H5VLpublic.h}, captionpos=b, label={lst:H5Lclass}]
+connector needs to implement.
+
+\begin{lstlisting}[caption={Structure for link callback routines, H5VLconnector.h}, captionpos=b, label={lst:H5Lclass}]
 typedef struct H5VL_link_class_t {                                               
-    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj, H5VL_loc_params_t loc_params, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
-    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
-    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
-    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj, const H5VL_loc_params_t *loc_params, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*copy)(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);           
+    herr_t (*move)(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);           
+    herr_t (*get)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);                 
+    herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
     herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); 
@@
 
+\subsubsection{link: create}
 The \texttt{create} callback in the group class creates a hard,
-soft, external, or user-defined links in the container. It returns an
+soft, external, or user-defined link in the container. It returns an
 \texttt{herr\_t} indicating success or failure.\bigskip
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
+  operation created by the connector.\\
 \end{tabular}
@@
 
-The \texttt{move} callback in the link class moves a link within the HDF5 container. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
+\subsubsection{link: copy}
+The \texttt{copy} callback in the link class copies a link within the HDF5 container. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{copy} callback in the link class copies a link within the HDF5 container. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl, hid_t lapl, hid_t dxpl_id, void **req);
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{link: move}
+The \texttt{move} callback in the link class moves a link within the HDF5 container. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the plugin.\\
-\end{tabular}
-\end{mdframed}
-
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{link: get}
 The \texttt{get} callback in the link class retrieves information
@@
 
+\subsubsection{link: specific}
 The \texttt{specific} callback in the link class implements specific operations on HDF5 links as specified in the \texttt{specific\_type} parameter.
@@
 
-The \texttt{optional} callback in the link class implements plugin specific operations on an HDF5 link. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+\subsubsection{link: optional}
+The \texttt{optional} callback in the link class implements connector specific operations on an HDF5 link. It returns an \texttt{herr\_t} indicating success or failure.\bigskip
 
@@
 
-Each plugin should be able to parse the \texttt{va\_list arguments} if it has plugin specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
-
-\subsection{The Asynchronous Function Callbacks}
-As of now, the HDF5 library does not provide asynchronous API
-operations. An asynchronous class to manage asynchronous operations
-was added nevertheless to handle an asynchronous API that might be
-added in the future, Listing \ref{lst:Asyncclass}.
-
-\begin{lstlisting}[caption={Structure for async callback routines, H5VLpublic.h}, captionpos=b, label={lst:Asyncclass}]
-typedef struct H5VL_async_class_t {
-    herr_t (*cancel)(void **, H5ES_status_t *);
-    herr_t (*test)  (void **, H5ES_status_t *);
-    herr_t (*wait)  (void **, H5ES_status_t *);
-} H5VL_async_class_t;
-\end{lstlisting}
-
-The \texttt{H5ES\_status\_t} argument is an \texttt{enum}:
+Each connector should be able to parse the \texttt{va\_list arguments} if it has connector specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+%%%%%%%%%%%%%%%%%%%%
+% OBJECT CALLBACKS %
+%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Object Callbacks}
+The object API routines (H5O) allow HDF5 users to manage HDF5 group,
+dataset, and named datatype objects. All the H5O API routines that
+modify the HDF5 container map to one of the object callback routines
+in this class that the connector needs to implement.
+
+\begin{lstlisting}[caption={Structure for object callback routines, H5VLconnector.h}, captionpos=b, label={lst:H5Oclass}]
+typedef struct H5VL_object_class_t {                                             
+    void *(*open)(void *obj, const H5VL_loc_params_t *loc_params, H5I_type_t *opened_type, hid_t dxpl_id, void **req);                                    
+    herr_t (*copy)(void *src_obj, const H5VL_loc_params_t *loc_params1, const char *src_name, void *dst_obj, const H5VL_loc_params_t *loc_params2, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
+    herr_t (*get)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);                 
+    herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); 
+} H5VL_object_class_t; 
+\end{lstlisting}
+
+\subsubsection{object: open}
+The \texttt{open} callback in the object class opens the object in
+the container of the location object and returns a pointer to the
+object structure containing information to access the object in future
+calls.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    void *(*open)(void *obj, H5VL_loc_params_t *loc_params, 
+        H5I_type_t *opened_type, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to a file or group where the objecy needs to be
+  opened or where the look-up of the target object needs to start.\\
+  \texttt{loc\_params} & (IN): Pointer to location parameters as explained in
+  Section~\ref{sec:map}.\\
+  \texttt{opened\_type} & (OUT): buffer to return the type of the object
+  opened (\texttt{H5I\_GROUP} or \texttt{H5I\_DATASET} or \texttt{H5I\_DATATYPE}).\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{object: copy}
+The \texttt{copy} callback in the object class  copies the object
+from the source object to the destination object. It returns an \texttt{
+  herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*copy)(void *src_obj, H5VL_loc_params_t *loc_params1, 
+        const char *src_name, void *dst_obj, 
+        H5VL_loc_params_t *loc_params2, const char *dst_name,
+        hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{src\_obj} & (IN): Pointer to location of the source object to
+  be copied.\\
+  \texttt{loc\_params1} & (IN): Pointer to location parameters as explained in
+  Section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
+  \texttt{src\_name} & (IN): Name of the source object to
+  be copied.\\
+  \texttt{dst\_obj} & (IN): Pointer to location of the destination
+  object.\\
+  \texttt{loc\_params2} & (IN): Pointer to location parameters as explained in
+  Section~\ref{sec:map}. The type should only be \texttt{H5VL\_OBJECT\_BY\_SELF} for this callback.\\
+  \texttt{dst\_name} & (IN): Name to be assigned to the new copy.\\
+  \texttt{ocpypl\_id} & (IN): The object copy property list.\\
+  \texttt{lcpl\_id} & (IN): The link creation property list.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{object: get}
+The \texttt{get} callback in the object class retrieves information
+about the object as specified in the \texttt{get\_type} parameter.It
+returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*get)(void *obj, H5VL_loc_params_t *loc_params, 
+        H5VL_object_get_t get_type, hid_t dxpl_id, 
+        void **req, va_list arguments);
+\end{lstlisting}
+
+The \texttt{get\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* type for object GET callback */
+typedef enum H5VL_object_get_t {                                                 
+    H5VL_OBJECT_GET_NAME,              /* object name                       */   
+    H5VL_OBJECT_GET_TYPE               /* object type                       */   
+} H5VL_object_get_t; 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): A location object where information needs to be
+  retrieved from.\\
+  \texttt{loc\_params} & (IN): Pointer to location parameters as
+  explained in Section~\ref{sec:map}.\\
+  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{get\_type} parameter. The following list shows
+the argument list, in order, for each type:
+
+\begin{itemize}
+\item \texttt{H5VL\_OBJECT\_GET\_NAME}, to retrieve a name for a referenced object:
+  \begin{enumerate}
+  \item \texttt{ssize\_t *ret} (OUT): buffer to return the length of the
+    name.
+  \item \texttt{char* name} (OUT): buffer to copy the name into.
+  \item \texttt{size\_t size} (IN): size of the buffer name, if 0, return
+    only the buffer size needed.
+  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
+    query.
+  \item \texttt{void *ref} (IN): the region reference to query.
+  \end{enumerate}
+
+\item \texttt{H5VL\_OBJECT\_GET\_TYPE}, to retrieve object type a reference
+  points to:
+  \begin{enumerate}
+  \item \texttt{H5O\_type\_t *type} (OUT): buffer to return the object type.
+  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
+    query.
+  \item \texttt{void *ref} (IN): the region reference to query.
+  \end{enumerate}
+\end{itemize}
+
+\subsubsection{object: specific}
+The \texttt{specific} callback in the object class implements specific operations on HDF5 objects as specified in the \texttt{specific\_type} parameter.
+It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+The \texttt{specific\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* types for object SPECIFIC callback */
+typedef enum H5VL_object_specific_t {                                            
+    H5VL_OBJECT_CHANGE_REF_COUNT,       /* H5Oincr/decr_refcount             */  
+    H5VL_OBJECT_EXISTS,                 /* H5Oexists_by_name                 */  
+    H5VL_OBJECT_LOOKUP,                 /* Lookup object                     */  
+    H5VL_OBJECT_VISIT,                  /* H5Ovisit(_by_name)                */  
+    H5VL_OBJECT_FLUSH,                  /* H5{D|G|O|T}flush                  */  
+    H5VL_OBJECT_REFRESH                 /* H5{D|G|O|T}refresh                */  
+} H5VL_object_specific_t; 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): Pointer to location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{specific\_type} & (IN): The type of the operation.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and
+  output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+The \texttt{arguments} argument contains a variable list of arguments
+depending on the \texttt{specific\_type} parameter. The following list shows
+the argument list, in order, for each type:
+
+\begin{itemize}
+\item \texttt{H5VL\_OBJECT\_CHANGE\_REF\_COUNT}, to update the reference
+  count for the object in \texttt{obj}:
+  \begin{enumerate}
+  \item \texttt{int ref\_count} (IN): reference count to set on the object.
+  \end{enumerate}
+
+\item \texttt{H5VL\_OBJECT\_EXISTS}, to check if an object with name
+  specified in \texttt{loc\_params} (type \texttt{H5VL\_OBJECT\_BY\_NAME})
+  exists:
+  \begin{enumerate}
+  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
+  \end{enumerate}
+
+\item \texttt{H5VL\_OBJECT\_VISIT}, to iterate over all objects starting at the location provided and call a user-specified callback on each one:
+  \begin{enumerate}
+  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
+  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
+  \item \texttt{H5O\_iterate\_t op} (IN): User-defined function to pass each object to. \\
+  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
+  \end{enumerate}
+
+\item \texttt{H5VL\_OBJECT\_FLUSH}, flushes a object:
+  \begin{enumerate}
+  \item \texttt{hid\_t obj\_id} (IN): The object ID. Needed so that the refreshed data can be associated with the old ID. 
+  \end{enumerate}
+
+\item \texttt{H5VL\_OBJECT\_REFRESH}, clears an object's buffers and reloads from disk:
+  \begin{enumerate}
+  \item \texttt{hid\_t obj\_id} (IN): The object ID. Needed so that the refreshed data can be associated with the old ID. 
+  \end{enumerate}
+\end{itemize}
+
+\subsubsection{object: optional}
+The \texttt{optional} callback in the object class implements connector specific operations on an HDF5 object. It returns an \texttt{herr\_t} indicating success or failure. \bigskip
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each connector should be able to parse the \texttt{va\_list arguments} if it has connector specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+
+%%%%%%%%%%%%%%%%%%%%%
+% REQUEST CALLBACKS %
+%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Request (Async) Callbacks}
+
+\begin{lstlisting}[caption={Structure for async request callback routines, H5VLconnector.h}, captionpos=b, label={lst:Requestclass}]
+typedef struct H5VL_request_class_t {                                            
+    herr_t (*wait)(void *req, uint64_t timeout, H5ES_status_t *status);          
+    herr_t (*notify)(void *req, H5VL_request_notify_t cb, void *ctx);            
+    herr_t (*cancel)(void *req);                                                 
+    herr_t (*specific)(void *req, H5VL_request_specific_t specific_type, va_list arguments);
+    herr_t (*optional)(void *req, va_list arguments);                            
+    herr_t (*free)(void *req);                                                   
+} H5VL_request_class_t;
+\end{lstlisting}
+
+\subsubsection{request: wait}
+Wait (with a timeout) for an async operation to complete. Releases the request if the operation has completed and the connector callback succeeds.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*wait)(void *req, uint64_t timeout, H5ES_status_t *status);          
+\end{lstlisting}
+
+The \texttt{status} argument is an \texttt{enum} (from \texttt{H5ESpublic.h}):
 \begin{lstlisting}
@@
     H5ES_STATUS_FAIL,          /* Operation has completed, but failed                   */
-    H5ES_STATUS_CANCEL       /* Operation has not completed and has been cancelled */
+    H5ES_STATUS_CANCELED       /* Operation has not completed and was canceled          */
 } H5ES_status_t;
@@
 
-The \texttt{cancel} callback attempts to cancel an asynchronous operation
-and returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*cancel)(void **req, H5ES_status_t *status);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{req} & (IN): A pointer to the asynchronous request.\\
-  \texttt{status} & (OUT): result of the cancel operation.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{test} callback tests an asynchronous operation completion
-and returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*test)(void **req, H5ES_status_t *status);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{req} & (IN): A pointer to the asynchronous request.\\
-  \texttt{status} & (OUT): result of the test operation.\\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{wait} callback waits for an asynchronous operation completion
-and returns an \texttt{herr\_t} indicating success or failure.\bigskip
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*wait)(void **req, H5ES_status_t *status);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{req} & (IN): A pointer to the asynchronous request.\\
-  \texttt{status} & (OUT): result of the wait operation.\\
-\end{tabular}
-\end{mdframed}
-
-\subsection{The Optional Generic Callback}
-A generic optional callback is provided for services that are specific to a plugin.
-Asynchronous operations/services could have been implemented through this optional callback, however since we anticipate asynchronous operations to be common across many plugins, they have been promoted to a subclass by themselves as shown in the previous section.
-Other services that are not shared across different plugins might include transactional semantics for managing operations like in~/ref{fastforward}, MSC - add more use cases here.
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{req} & (IN): The async request on which to wait.\\
+  \texttt{timeout} & (IN): The timeout value.\\
+  \texttt{status} & (IN): The status.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{request: notify}
+Registers a user callback to be invoked when an asynchronous operation completes. Releases the request if connector callback succeeds.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*notify)(void *req, H5VL_request_notify_t cb, void *ctx);            
+\end{lstlisting}
+
+The \texttt{cb} argument is a function pointer:
+\begin{lstlisting}
+    typedef herr_t (*H5VL_request_notify_t)(void *ctx, H5ES_status_t status);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{req} & (IN): The async request that will receive the notify callback.\\
+  \texttt{cb} & (IN): The notify callback for the request.\\
+  \texttt{ctx} & (IN): The request's context.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{request: cancel}
+Cancels an asynchronous operation. Releases the request if connector callback succeeds.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*cancel)(void *req);                                                 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{req} & (IN): The async request to be cancelled.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{request: specific}
+Perform a specific operation on an asynchronous request.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*specific)(void *req, H5VL_request_specific_t specific_type, va_list arguments);
+\end{lstlisting}
+
+The \texttt{specific\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* types for async request SPECIFIC callback */
+typedef enum H5VL_request_specific_t {
+    H5VL_REQUEST_WAITANY,               /* Wait until any request completes */   
+    H5VL_REQUEST_WAITSOME,              /* Wait until at least one requesst completes */
+    H5VL_REQUEST_WAITALL                /* Wait until all requests complete */   
+} H5VL_request_specific_t; 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{req} & (IN): The async request on which to perform the operation.\\
+  \texttt{specific\_type} & (IN): The specific operation to perform.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{request: optional}
+Perform a connector-specific operation for a request.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*optional)(void *req, va_list arguments);                            
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{req} & (IN): The async request on which to perform the operation.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{request: free}
+Frees an asynchronous request.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*free)(void *req);                                                   
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{req} & (IN): The async request to be freed.\\
+\end{tabular}
+\end{mdframed}
+
+%%%%%%%%%%%%%%%%%%%
+% BLOB CALLBACKS %
+%%%%%%%%%%%%%%%%%%%
+
+\subsection{Blob Callbacks}
+\begin{lstlisting}[caption={Structure for blob callback routines, H5VLconnector.h}, captionpos=b, label={lst:Blobclass}]
+typedef struct H5VL_blob_class_t {                                               
+    herr_t (*put)(void *obj, const void *buf, size_t size, void *blob_id, void *ctx);
+    herr_t (*get)(void *obj, const void *blob_id, void *buf, size_t size, void *ctx);
+    herr_t (*specific)(void *obj, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);
+    herr_t (*optional)(void *obj, void *blob_id, va_list arguments);             
+} H5VL_blob_class_t; 
+\end{lstlisting}
+
+\subsubsection{blob: put}
+Put a blob through the VOL.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*put)(void *obj, const void *buf, size_t size, void *blob_id, void *ctx);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to the blob container.\\
+  \texttt{buf} & (IN): Pointer to the blob.\\
+  \texttt{size} & (IN): Size of the blob.\\
+  \texttt{blob\_id} & (OUT): Pointer to the blob's connector-specific ID.\\
+  \texttt{ctx} & (IN): Connector-specific blob context.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{blob: get}
+Get a blob through the VOL.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*get)(void *obj, const void *blob_id, void *buf, size_t size, void *ctx);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to the blob container.\\
+  \texttt{blob\_id} & (IN): Pointer to the blob's connector-specific ID.\\
+  \texttt{buf} & (IN/OUT): Pointer to the blob.\\
+  \texttt{size} & (IN): Size of the blob.\\
+  \texttt{ctx} & (IN): Connector-specific blob context.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{blob: specific}
+Perform a defined operation on a blob via the VOL.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*specific)(void *obj, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);
+\end{lstlisting}
+
+The \texttt{specific\_type} argument is an \texttt{enum}:
+\begin{lstlisting}
+typedef enum H5VL_blob_specific_t {
+    H5VL_BLOB_DELETE,                   /* Delete a blob (by ID) */
+    H5VL_BLOB_GETSIZE,                  /* Get size of blob */
+    H5VL_BLOB_ISNULL,                   /* Check if a blob ID is "null" */ 
+    H5VL_BLOB_SETNULL                   /* Set a blob ID to the connector's "null" blob ID value */
+} H5VL_blob_specific_t;
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to the blob container.\\
+  \texttt{blob\_id} & (IN): Pointer to the blob's connector-specific ID.\\
+  \texttt{specific\_type} & (IN): The operation to perform.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{blob: optional}
+Perform a connector-specific operation on a blob via the VOL.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*optional)(void *obj, void *blob_id, va_list arguments);             
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to the blob container.\\
+  \texttt{blob\_id} & (IN): Pointer to the blob's connector-specific ID.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
+\end{tabular}
+\end{mdframed}
+
+%%%%%%%%%%%%%%%%%%%%%
+% OPTIONAL CALLBACK %
+%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Optional Generic Callback}
+A generic optional callback is provided for services that are specific to a connector.
 
@@
   \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the plugin.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the connector.\\
+  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
 \end{tabular}

### 2019-11-25 RFCs/HDF5/VOL/connector_author_guide/intro.tex
Most API changes in. Still need to move "helper" text over.
Former-commit-id: c236ad85c2fcb331051a2de3ffa110e6bfaeb004

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

\section{Introduction}
The Virtual Object Layer (VOL) is an abstraction layer in the HDF5
library which intercepts all API calls that could potentially access
objects in an HDF5 container and forwards those calls to object drivers
referred to as \textit{VOL connectors}. The architecture of this feature
is described in the VOL User Guide and VOL Architecture and Internals
Documentation and will not be duplicated here.

This guide is for people who are interested in developing their own VOL
connector for the HDF5 library. It is assumed that the reader has good knowledge
of the VOL architecture obtained by reading the VOL architectural design
document~\cite{vol:rfc}.

### 2019-11-25 RFCs/HDF5/VOL/connector_author_guide/new_api_calls.tex
Most API changes in. Still need to move "helper" text over.
Former-commit-id: c236ad85c2fcb331051a2de3ffa110e6bfaeb004

\section{New VOL API Routines}
\label{sec:api}
New API routines have been added to the HDF5 library to manage VOL connectors. This section details each new API call and explains their intended usage.

Additionally, a set of API calls that map directly to the VOL callbacks themselves have been added to aid in the development of passthrough connectors which can be stacked and/or split. For more information on usage refer to Section~\ref{sec:stack}. The routines are listed in Appendix~\ref{sec:B}.

\bigskip

\subsection{H5VLpublic.h}

\subsubsection{H5VLregister\_connector}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
hid_t H5VLregister_connector(const H5VL_class_t *cls, hid_t vipl_id);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  {\tt cls} & (IN): A pointer to the connector structure to register.\\
  {\tt vipl\_id} & (IN): An ID for a VOL initialization property list (vipl).\\
\end{tabular}
\end{mdframed}

Registers a user-defined VOL connector with the HDF5 library and returns an identifier for that connector (\texttt{H5I\_INVALID\_HID} on errors). This function is used when the application has direct access to the connector it wants to use and is able to obtain a pointer for the connector structure to pass to the HDF5 library.
\bigskip

\subsubsection{H5VLregister\_connector\_by\_name}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
hid_t H5VLregister_by_name(const char *connector_name, hid_t vipl_id);
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  {\tt name} & (IN): The connector name to search for and register.\\
  {\tt vipl\_id} & (IN): An ID for a VOL initialization property list (vipl).\\
\end{tabular}
\end{mdframed}
Registers a VOL connector with the HDF5 library given the name of the connector and returns an identifier for it (\texttt{H5I\_INVALID\_HID} on errors). If the connector is already registered, the library will create a new identifier for it and returns it to the user; otherwise the library will search the plugin path for a connector of that name, loading and registering it, returning an ID for it, if found. See the VOL User Guide for more information on loading plugins and the search paths.
\bigskip

\subsubsection{H5VLregister\_connector\_by\_value}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
hid_t H5VLregister_by_value(H5VL_class_value_t connector_value, hid_t vipl_id);
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  {\tt connector\_value} & (IN): The connector value to search for and register.\\
  {\tt vipl\_id} & (IN): An ID for a VOL initialization property list (vipl).\\
\end{tabular}
\end{mdframed}
Registers a VOL connector with the HDF5 library given a value for the connector and returns an identifier for it (\texttt{H5I\_INVALID\_HID} on errors). If the connector is already registered, the library will create a new identifier for it and returns it to the user; otherwise the library will search the plugin path for a connector of that name, loading and registering it, returning an ID for it, if found. See the VOL User Guide for more information on loading plugins and the search paths.
\bigskip

\subsubsection{H5VLis\_connector\_registered}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
htri_t H5VLis_connector_registered(const char *name);
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  {\tt name} & (IN): The connector name to check for.\\
\end{tabular}
\end{mdframed}
Checks if a VOL connector is registered with the library given the connector name and returns TRUE/FALSE on success, otherwise it returns a negative value.\bigskip

\subsubsection{H5VLget\_connector\_id}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
hid_t H5VLget_connector_id(const char *name);
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  {\tt name} & (IN): The connector name to check for.\\
\end{tabular}
\end{mdframed}
Given a connector name that is registered with the library, this function returns an identifier for the connector. If the connector is not registered with the library, a negative value is returned. The identifier must be released with a call to {\tt H5VLclose()}.\bigskip

\subsubsection{H5VLget\_connector\_name}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
ssize_t H5VLget_connector_name(hid_t id, char *name/*out*/, size_t size);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  {\tt id} & (IN): The object identifier to check.\\
  {\tt name} & (OUT): Buffer pointer to put the connector name. If NULL, the library just returns the size required to store the connector name.\\
  {\tt size} & (IN): the size of the passed in buffer.\\
\end{tabular}
\end{mdframed}
Retrieves the name of a VOL connector given an object identifier that was created/opened with it. On success, the name length is returned.\bigskip

\subsubsection{H5VLclose}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
herr_t H5VLclose(hid_t connector_id);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
 {\tt connector\_id} & (IN): A valid identifier of the connector to close.\\
\end{tabular}
\end{mdframed}
Shuts down access to the connector that the identifier points to and release resources associated with it.\bigskip

\subsubsection{H5VLunregister\_connector}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
herr_t H5VLunregister(hid_t connector_id);
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  {\tt connector\_id} & (IN): A valid identifier of the connector to unregister.\\
\end{tabular}
\end{mdframed}
Unregisters a connector from the library and return a positive value on success otherwise return a negative value. That native VOL connector cannot be unregistered (this will return a negative herr\_t value).\bigskip

\subsection{H5VLconnector.h}

\subsubsection{H5VLobject\_register}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
  hid_t H5VLobject_register(void *obj, H5I_type_t obj_type, hid_t connector_id);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
 {\tt obj} & (IN): pointer to the object to register.\\
 {\tt obj\_type} & (IN): The type of the object ({\tt H5I\_FILE, H5I\_DATASET, H5I\_GROUP, H5I\_ATTRIBUTE, H5I\_DATATYPE}).\\
 {\tt connector\_id} & (IN): identifier of the vol connector the object is associated with.\\
\end{tabular}
\end{mdframed}
Creates an HDF5 identifier for an object given its type and an identifier of the connector that was used in creating it. This function is typically used by external connectors wanting to wrap an {\tt hid\_t} around a connector specific object to return to a user callback for functions like {\tt H5Literate, H5Lvisit, H5Ovisit, H5Aiterate} etc... A Negative value is returned on failure.\bigskip

\subsubsection{H5VLget\_object}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
  herr_t H5VLget_object(hid_t obj_id, void **obj); 
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
 {\tt obj\_id} & (IN): identifier of the object to dereference.\\
 {\tt obj} & (OUT): buffer to store the pointer of the VOL object associated with the object identifier.\\
\end{tabular}
\end{mdframed}
Retrieves a pointer to the VOL object from an HDF5 file or object identifier.\bigskip

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-11-25 RFCs/HDF5/VOL/connector_author_guide/stacking.tex
Most API changes in. Still need to move "helper" text over.
Former-commit-id: c236ad85c2fcb331051a2de3ffa110e6bfaeb004

--- 2018-01-10 RFCs/HDF5/VOL/user_guide/stacking.tex
@@
-\section{Interchanging and Stacking VOL Plugins}
+\section{Interchanging and Stacking VOL Connectors}
 \label{sec:stack}
@@
 
-\subsection{Stacking Plugins on Top of Each Other}
+\subsection{Stacking Connectors on Top of Each Other}
 It would also be possible to stack VOL plugins on top of each
@@
 
-\subsection{Mirroring Plugins}
+\subsection{Mirroring Connectors}
 Another useful design option is to allow a mirroring plugin, where the
@@
 
-\subsection{Implementing Stacked \& Mirrored Plugins}
+\subsection{Implementing Stacked \& Mirrored Connectors}
 A new set of API calls that map directly to the VOL callbacks have
@@
 
-Appendix~\ref{sec:A} show an example on how to stack a simple plugin that does a printf of the VOL operation on top of the native HDF5 plugin.
+Appendix~\ref{sec:A} demonstrates how to stack a simple plugin that does a printf of the VOL operation on top of the native HDF5 plugin.
 

### 2019-11-25 RFCs/HDF5/VOL/connector_author_guide/writing_new.tex
Most API changes in. Still need to move "helper" text over.
Former-commit-id: c236ad85c2fcb331051a2de3ffa110e6bfaeb004

--- 2018-01-10 RFCs/HDF5/VOL/user_guide/external.tex
@@
-\section{Creating and Using an External Plugin}
+\section{Creating a New Connector}
 External plugins are developed outside of the HDF5 library and do not
@@
 
-\subsection{Creating an External Plugin}
+\subsection{Overview}
 Developing an external plugin is similar to developing an internal plugin.
@@
 
-\subsection{Using an External Plugin}
+\subsection{Using The New Connector}
 Unlike internal plugins, external plugins cannot create an API routine for applications to use to set the VOL plugin in the file access property list.
@@
 
-% /* Function prototypes */
-% H5_DLL htri_t H5VLis_registered(hid_t id);
-% H5_DLL ssize_t H5VLget_plugin_name(hid_t id, char *name/*out*/, size_t size);
+\subsection{Testing}
 
-% H5_DLL void *H5Pget_vol_info(hid_t plist_id);
+\subsection{Internal Connectors}
+
+Internal plugins are developed internally with the HDF5 library and
+are required to ship with the entire library to be used. Typically
+those plugins need to use internal features and functions of the HDF5
+library that are not available publicly from the user application.
+
+\subsubsection{Implementing an Internal Connector}
+The first step to implement an internal plugin is to implement all the callbacks defined in the VOL class as described in Section~\ref{sec:vol}.
+After implementing the VOL class, the next step would be to allow users to select
+this plugin to be used. This is done by creating a new API routine to
+set the plugin on the file access property list. For example, if we
+create an internal plugin called ``dummy'' that needs an MPI
+communicator and info object as information from the user, that
+routine signature should look like:
+
+\begin{lstlisting}
+herr_t H5Pset_fapl_dummy(hid_t fapl_id, MPI_Comm comm, MPI_Info info);
+\end{lstlisting}
+
+The implementation for the above routine should use the internal
+function:
+\begin{lstlisting}
+herr_t H5P_set_vol(H5P_genplist_t *plist, H5VL_class_t *vol_cls, const
+void *vol_info);
+\end{lstlisting}
+that will set the file access using that {\tt fapl\_id} to go through
+the ``dummy'' plugin. It will also call the copy callback of the
+``dummy'' plugin on the info object ({\tt comm and info}).
+
+A sample implementation for the {\tt H5Pset\_fapl\_dummy()} would look like this:
+
+\begin{lstlisting}
+/* DUMMY-specific file access properties */
+typedef struct H5VL_dummy_fapl_t {
+    MPI_Comm            comm;     /* communicator       */
+    MPI_Info            info;     /* MPI information   */
+} H5VL_dummy_fapl_t;
+
+herr_t
+H5Pset_fapl_dummy(hid_t fapl_id, MPI_Comm comm, MPI_Info info)
+{
+    H5VL_dummy_fapl_t fa;
+    H5P_genplist_t  *plist;      /* Property list pointer */
+    herr_t          ret_value;
+
+    FUNC_ENTER_API(FAIL)
+
+    if(fapl_id == H5P_DEFAULT)
+        HGOTO_ERROR(H5E_PLIST, H5E_BADVALUE, FAIL, "can't set values in default property list")
+
+    if(NULL == (plist = H5P_object_verify(fapl_id, H5P_FILE_ACCESS)))
+        HGOTO_ERROR(H5E_ARGS, H5E_BADTYPE, FAIL, "not a file access property list")
+
+    if(MPI_COMM_NULL == comm)
+	HGOTO_ERROR(H5E_PLIST, H5E_BADTYPE, FAIL, "not a valid communicator")
+
+    /* Initialize driver specific properties */
+    fa.comm = comm;
+    fa.info = info;
+
+    ret_value = H5P_set_vol(plist, &H5VL_dummy_g, &fa);
+
+done:
+    FUNC_LEAVE_API(ret_value)
+} /* end H5Pset_fapl_dummy() */
+\end{lstlisting}
+
+At this point, the internal plugin is ready to be used. For more
+information on how to implement an internal plugin, the native plugin
+for the HDF5 library is a comprehensive plugin that implements all
+features of the library and can be used as a guide.
+
+\subsubsection{Using an Internal Connector}
+An internal plugin is registered automatically with the HDF5 library when the library gets initialized.
+Users should not attempt to register an internal plugin.
+The internal registration operation creates a global identifier for each internal plugin.
+Applications can query the library for that identifier using the plugin name with {\tt H5VLget\_plugin\_id()}.
+This identifier is used to initialize the plugin if it requires an initialization phase.
+A third party library could use that ID to create a plugin that stacks or mirrors on top of an internal plugin using that identifier (refer to Section~\ref{sec:stack} for more details on stacking and mirroring).
+
+Some plugins could require an initialization phase before using the plugin with some input parameters from users.
+For example, a remote plugin would need to setup a connection to a remote machine with a specific hostname that the user knows and the HDF5 library does not know about.
+This process is done by creating a VOL initialization property list and setting a public property that should be defined by the internal plugin to the hostname of the remote machine.
+The user then calls the initialize routine ({\tt H5VLintialize()}) with the plugin\_id and the property list to initialize the plugin.
+Some plugins could create a public API routine that wraps the property list creation, property settings, and plugin initialization into one routine that the user calls to simplify this process for the users.
+The native HDF5 plugin does not require an initialization phase.
+
+Now that the plugin is initialized, the application can create or open an HDF5 container using the internal plugin by creating a file access property list and calling the corresponding API routine that the internal plugin should define for setting the VOL plugin property and container parameters on the file access property list.
+That FAPL can be passed to the {\tt H5Fcreate()} or {\tt H5Fopen{}} calls to access the container through the VOL plugin.
+Subsequently, all other HDF5 calls on the container and objects created or opened in that container will automatically go to the selected VOL plugin.
+
+After closing all objects and containers on that plugin, the application should terminate access to the selected plugin if it requires a termination phase by calling {\tt H5VLterminate()} with the required termination properties (similar to the initialization phase).
+The native HDF5 plugin does not require a termination phase.
+
+The internal plugin is unregistered automatically by the HDF5 library on library termination, and users should not attempt to unregister it themselves.
+
 %%% Local Variables: 

### 2019-12-05 RFCs/HDF5/VOL/user_guide/body.tex
Updated the VOL UG based on feedback.
Former-commit-id: 449ef748a4c26dbcc78a52e5f103b2bcff65f970

@@
 This may be confusing when it comes to property list calls, since many of those calls set properties for storage.
-Property lists are just collections of key-value pairs, though, so the VOL is not involved with setting or getting any properties.
+Property lists are just collections of key-value pairs, though, so a particular VOL connector is not required to set or get properties.
 
@@
 
-An external VOL connector is normally implemented as a dynamically loaded plugin.
-In order to be used by an application, they must be discoverable and loadable via path settings, etc.
-These plugins are loaded at runtime via the same HDF5 plugin scheme used for filters.
-A VOL connector for a file is set in the file access property list (FAPL) used to open it, either via H5Pset\_vol() or a connector-specific API call provided by the connector author.
+A VOL connector can be implemented in several ways: as a shared or static library linked to an application; as a dynamically loaded plugin, implemented as a shared library; and even as an internal connector, built into the HDF5 library itself.
+This document mostly focuses on external connectors, both libraries and plugins, as those are expected to be much more common than internal implementations.
 
-Many VOL connectors (at various stages of construction) can be found here:
+Many VOL connectors (at various stages of implementation) can be found here:
 
-\quad \quad https://bitbucket.hdfgroup.org/projects/HDF5VOL
+\quad \quad \url{https://bitbucket.hdfgroup.org/projects/HDF5VOL}
 
@@
 
-The native VOL connector is a special case. It is currently implemented as a built-in part of the HDF5 library and cannot be unloaded, nor can its ID be closed.
+The only current (non-test) internal VOL connector distributed with the library is the native file format connector (the "native VOL connector") which contains the code that handles native HDF5 (*.h5/hdf5) files.
+In other words, even the canonical HDF5 file format is implemented via the VOL, making it a core part of the HDF5 library and not an optional component which could be disabled.
+It has not been completely abstracted from the HDF5 library, though, and is treated as a special case.
+For example, it cannot be unloaded and is always present.
 
 \section{Quickstart}
+
+The following steps summarize how one would go about using a VOL connector with an application. More information on particular steps can be found later on in this document.
 
@@
 
-\subsection{Make Sure The VOL Connector Is In The Search Path}
+\subsection{Determine How You Will Set The VOL Connector}
 
-The default location for all HDF5 plugins is set at configure time when building the HDF5 library. This is true for both CMake and the Autotools.
+Fundamentally, setting a VOL connector involves modifying the file access propertly list (fapl) that will be used to open or create the file.
+
+There are essentially three ways to do this:
+
+\begin{itemize}
+    \item Direct use of {\tt H5Pset\_vol()}
+    \item Library-specific API calls that call {\tt H5Pset\_vol()} for you
+    \item Use the VOL environment variable, which will also call {\tt H5Pset\_vol()} for you
+\end{itemize}
+
+Exactly how you go about setting a VOL connector in a fapl, will depend on the complexity of the VOL connector and how much control you have over the application's source code.
+
+\subsection{If Needed: Update Your Code To Load And Use A VOL Connector}
+
+There are two concerns when modifying the application:
+
+\begin{itemize}
+    \item It may be convenient to add connector-specific setup calls to the application.
+
+    \item You will also need to protect any API calls which are only implemented in the native VOL connector as those calls will fail when using a non-native VOL connector.
+See the section entitled "Adapting HDF5 Software to Use the VOL", below.
+A list of native VOL API calls has been included in an appendix.
+\end{itemize}
+
+In some cases, using the VOL environment variable will work well for setting the connector and any associated storage setup and the application will not use API calls that are not supported by the VOL connector.
+In this case, no application modification will be necessary.
+
+\subsection{If Using A Plugin: Make Sure The VOL Connector Is In The Search Path}
+
+The default location for all HDF5 plugins is set at configure time when building the HDF5 library.
+This is true for both CMake and the Autotools.
+The default locations for the plugins on both Windows and POSIX systems is listed further on in this document.
+
+\subsection{Optional: Set The VOL Connector Via The Environment Variable}
+
+In place of modifying the source code of your application, you may be able to simply set the {\tt HDF5\_VOL\_CONNECTOR} environment variable (see below).
+This will automatically use the specified VOL in place of the native VOL connector.
+
+\section{Connector Use}
+
+Before a VOL connector can be set in a fapl, it must be registered with the library ({\tt H5Pset\_vol()} requires the connector's {\tt hid\_t} ID) and, if a plugin, it must be discoverable by the library at run time.
+
+\subsection{Registration}
+
+Before a connector can be used, it must be registered. This loads the connector into the library and give it an HDF5 {\tt hid\_t} ID. The {\tt H5VLregister\_connector} API calls are used for this.
+
+\quad\quad {\tt hid\_t H5VLregister\_connector(const H5VL\_class\_t *cls, hid\_t vipl\_id)}
+
+\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_name(const char *connector\_name, hid\_t vipl\_id)}
+
+\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_value(H5VL\_class\_value\_t connector\_value, hid\_t vipl\_id)}
+
+When used with a plugin, these functions will check to see if an appropriate plugin with a matching name, value, etc.
+is already loaded and check the plugin path (see above) for matching plugins if this is not true.
+The functions return {\tt H5I\_INVALID\_HID} if they are unable to register the connector.
+Most people will use the {\tt \_by\_name()} or {\tt \_by\_value} versions of this API call.
+The call that takes an {\tt H5VL\_class\_t} struct is considered a lower-level call this is more commonly used by connector authors in connector-specific setup/registration code.
+Many VOL connectors will provide a connector-specific init call that will load and register the connector for you.
+
+Note the two ways that a VOL connector can be identified: by a name or by a connector-specific numerical value ({\tt H5VL\_class\_value\_t} is typedef'd to an integer).
+The name and value for a connector can be found in the connector's documentation or public header file.
+
+Each call also takes a VOL initialization property list (vipl).
+The library adds no properties to this list, so it is entirely for use by connector authors.
+Set this to {\tt H5P\_DEFAULT} unless instructed differently by the documentation for the VOL connector.
+
+As far as the library is concerned, connectors do not need to be explicitly unregistered as the library will unload the plugin and close the ID when the library is closed.
+If you want to close a VOL connector ID, either {\tt H5VLunregister\_connector()} or {\tt H5VLclose()} can be used (they have the same internal code path).
+The library maintains a reference count on all open IDs and will not do the actual work of closing an ID until its reference count drops to zero, so it's safe to close IDs anytime after they are used, even while an HDF5 file that was opened with that connector is still open.
+
+Note that it's considered an error to unload the native VOL connector.
+The library will prevent this.
+This means that, for the time being, the native VOL connector will always be available.
+This may change in the future so that the memory footprint of the native VOL connector goes away when not in use.
+
+\subsection{Connector Versioning}
+
+\thgfuturewarning
+
+There is currently no recommended or library-inherent way to version VOL connectors.
+A {\tt version} field is included in the {\tt H5VL\_class\_t} struct which holds a connector's information and callbacks, but this is intended for use when versioning the class struct.
+
+\subsection{Connector-Specific Registration Calls}
+
+Most connectors will provide a special API call which will set the connector in the fapl.
+These will often be in the form of {\tt H5Pset\_fapl\_<name>()}.
+For example, the DAOS VOL connector \url{https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/daos-vol} provides a {\tt H5Pset\_fapl\_daos()} API call which will take MPI parameters and make this call.
+See the connector's documentation or public header file(s) for more information.
+
+\subsection{\tt H5Pset\_vol()}
+
+The is the main library API call for setting the VOL connector in a file access property list. Its signature is:
+
+\quad\quad {\tt herr\_t H5Pset\_vol(hid\_t plist\_id, hid\_t vol\_id, vol\_info)}
+
+It takes the ID of the file access property list, the ID of the registered VOL connector, and a pointer to whatever connector-specific data the connector is expecting.
+This will usually be a data struct specified in the connector's header.
+
+As mentioned above, many connectors will provide their own replacement for this call. See the connector's documentation for more information.
+
+\subsection{VOL Connector Search Path}
+
+Dynamically loaded VOL connector plugins are discovered and loaded by the library using the same mechanism as dataset/group filter plugins. The default locations are:
 
@@
 By default, it will NOT find plugins that are simply located in the same directory as the executable.
-
-\subsection{Update Your Code To Load And Use A VOL Connector}
-
-How this is done depends on the VOL connector, which may have special API calls for setup or require appropriate configuration files, but the most generic way to modify a program to use a specific VOL connector would be to {\tt use H5Pset\_vol()} to set the VOL connector in the file access property list (fapl) that will be used to open the file.
-
-You will also need to protect any API calls which are only implemented in the native VOL connector as those calls will fail when using a non-native VOL connector.
-See the section entitled "Adapting HDF5 Software to Use the VOL", below.
-A list of native VOL API calls has been included in an appendix.
-
-\subsection{Optional: Set The VOL Connector Via The Environment Variable}
-
-In place of modifying the source code of your application, you may be able to simply set the {\tt HDF5\_VOL\_CONNECTOR} environment variable (see below).
-This will automatically use the speicified VOL in place of the native VOL connector.
-
-\section{Loading and Registering Connectors}
-
-Before a VOL connector can be used, it must be discoverable by the library and then loaded and registered.
-
-\subsection{VOL Connector Search Path}
-
-VOL connector plugins are discovered and loaded by the library using the same mechanism as dataset/group filter plugins (REF). Essentially,
-
-\subsection{registration}
-
-Before a connector can be used, it must be registered. This loads the connector into the library and give it an HDF5 {\tt hid\_t} ID. The {\tt H5VLregister\_connector} API calls are used for this.
-
-\quad\quad {\tt hid\_t H5VLregister\_connector(const H5VL\_class\_t *cls, hid\_t vipl\_id)}
-
-\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_name(const char *connector\_name, hid\_t vipl\_id)}
-
-\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_value(H5VL\_class\_value\_t connector\_value, hid\_t vipl\_id)}
-
-Each of these functions will check to see if an appropriate plugin with a matching name, value, etc.
-is already loaded and check the plugin path (see above) for matching plugins if this is not true.
-They return {\tt H5I\_INVALID\_HID} if they are unable to register the connector.
-Most people will use the {\tt \_by\_name()} or {\tt \_by\_value} versions of this API call.
-The call that takes an {\tt H5VL\_class\_t} struct is considered a lower-level call this is more commonly used by connector authors.
-Many VOL connectors will provide a connector-specific init call that will load and register the connector for you.
-
-Note the two ways that a VOL connector can be identified: by a name or by a connector-specific numerical value ({\tt H5VL\_class\_value\_t} is typedef'd to an integer).
-The name and value for a connector can be found in the connector's documentation or public header file.
-
-Each call also takes a VOL initialization property list (vipl).
-The library adds no properties to this list, so it is entirely for use by connector authors.
-Set this to {\tt H5P\_DEFAULT} unless instructed differently by the documentation for the VOL connector.
-
-As far as the library is concerned, connectors do not need to be explicitly unregistered as the library will unload the plugin and close the ID when the library is closed.
-If you want to close a VOL connector ID, either {\tt H5VLunregister\_connector()} or {\tt H5VLclose()} can be used (they have the same internal code path).
-The library maintains a reference count on all open IDs and will not do the actual work of closing an ID until its reference count drops to zero, so it's safe to close IDs anytime after they are used, even while an HDF5 file that was opened with that connector is still open.
-
-Note that it's considered an error to close/unload the native VOL connector.
-The library will prevent this.
-This means that, for the time being, the native VOL connector will always be available.
-This may change in the future so that the memory footprint of the native VOL connector goes away when not in use.
-
-\subsection{Connector Versioning}
-
-\thgfuturewarning
-
-There is currently no recommended or library-inherent way to version VOL connectors.
-A {\tt version} field is included in the {\tt H5VL\_class\_t} struct which holds a connector's information and callbacks, but this has not been utilized in the plugin loading code at this time.
-
-\subsection{Connector-Specific Registration Calls}
-
-Most connectors will provide a special API call which will set the connector in the fapl.
-These will often be in the form of {\tt H5Pset\_fapl\_<name>()}.
-For example, the DAOS VOL (https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/daos-vol) provides a {\tt H5Pset\_fapl\_daos()} API call which will take MPI parameters and make this call.
-See the connector's documentation or public header file(s) for more information.
-
-\subsection{\tt H5Pset\_vol()}
-
-The is the main library API call for setting the VOL connector in a file access property list. Its signature is:
-
-\quad\quad {\tt herr\_t H5Pset\_vol(hid\_t plist\_id, hid\_t vol\_id, vol\_info)}
-
-It takes the ID of the file access property list, the ID of the registered VOL connector, and a pointer to whatever connector-specific data the connector is expecting.
-This will usually be a data struct specified in the connector's header.
-
-As mentioned above, many connectors will provide their own replacement for this call. See the connector's documentation for more information.
 
@@
 
+The VOL was engineered to be as unobtrusive as possible and, when a connector which implements most/all of the data model functionality is in use, most applications should require little, if any, modification.
+As mentioned in the quick start section, most modifications will probably consist of connector setup code (which can usually be accomplished via the environment variable) and protecting native file format functions.
+
 \subsection{Specific API Call Substitutions}
-\subsection{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}
+\subsubsection{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}
 
@@
 
-\subsection{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_[native|data\_model]\_info()}$}
+\subsubsection{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_info3()} {\tt H5Oget\_native\_info()}$}
 
@@
 
-The {\tt H5Oget\_info1()} and {\tt H5Oget\_info2()} API calls are often used by user code to obtain information about an object in the file, however these calls return a struct which contains native information and are thus currently handled via the native connector's \textit{object optional} callback and so are not handled by most external VOL connectors.
+The {\tt H5Oget\_info1()} and {\tt H5Oget\_info2()} family of HDF5 API calls are often used by user code to obtain information about an object in the file, however these calls return a struct which contains native information and are thus currently handled via the native connector's \textit{object optional} callback and so are not handled by most external VOL connectors.
 
-These calls will be separated into two functions: one for getting an object's data model information ({\tt H5Oget\_data\_model\_info()}, which will go through the \textit{object get} callback), and another for returning an object's native file format information ({\tt H5Oget\_native\_info()}, which will go through the native connector's \textit{object optional} callback).
+These calls will be separated into two functions: one for getting an object's data model information ({\tt H5Oget\_info3()}, which will go through the \textit{object get} callback), and another for returning an object's native file format information ({\tt H5Oget\_native\_info()}, which will go through the native connector's \textit{object optional} callback).
+These API calls will use new {\tt H5O\_info2\_t} and {\tt H5O\_native\_info\_t} structs, respectively, to hold the returned data.
 
-\textbf{This section will be expanded when the RFC for this feature is complete.}
+This feature is under development and this section will be updated when the feature is complete.
+
+\subsubsection{Optional: ${\tt H5Ovisit[1|2]()} \rightarrow {\tt H5Ovisit3()}$}
+
+\thgfuturewarning
+
+The {\tt H5Ovisit()} family of API functions uses the {\tt H5O\_info\_t} struct in its callback function:
+
+\quad \quad {\tt typedef herr\_t (*H5O\_iterate\_t)(hid\_t obj, const char *name, const H5O\_info\_t *info, void *op\_data) }
+
+A new callback that takes the updated, data-model-only struct will replace the old callback in new {\tt H5Ovisit3} API calls.
+Note that replacing this function is optional as it goes through the VOL's \textit{object specific} callback.
+
+As with the {\tt H5Oget\_info()} work, this feature is under development and this section will be updated when the feature is complete.
 
@@
 \end{longtable}
-
-\subsection{List of HDF5 API Calls By Callback}
-
-\begin{longtable}{ |l|>{\raggedright\arraybackslash}l| }
-    \hline
-    \multicolumn{1}{|c|}{VOL Callback} & \multicolumn{1}{|c|}{HDF5 API Call} \\
-    \hline
-    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}FILE} \\
-    \hline
-    create & H5Fcreate \\
-    \hline
-    open & H5Fopen \\
-    \hline
-    get & H5Fget\_access\_plist \\
-        & H5Fget\_create\_plist \\
-        & H5Fget\_fileno \\
-        & H5Fget\_intent \\
-        & H5Fget\_name \\
-        & H5Fget\_obj\_count \\
-        & H5Fget\_obj\_ids \\
-    \hline
-    specific & H5Fdelete \\
-             & H5Fflush \\
-             & H5Fis\_accessible \\
-             & H5Fis\_hdf5 (deprecated, hard-coded to use native connector) \\
-             & H5Fmount \\
-             & H5Freopen \\
-             & H5Funmount \\
-    \hline
-    close & H5Fclose \\
-    \hline
-    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}GROUP} \\
-    \hline
-    create & H5Gcreate1 (deprecated) \\
-           & H5Gcreate2 \\
-           & H5Gcreate\_anon \\
-    \hline
-    open & H5Gopen1 (deprecated) \\
-         & H5Gopen2 \\
-    \hline
-    get & H5Gget\_create\_plist \\
-        & H5Gget\_info \\
-        & H5Gget\_info\_by\_idx \\
-        & H5Gget\_info\_by\_name \\
-        & H5Gget\_num\_objs (deprecated) \\
-    \hline
-    specific & H5Gflush \\
-             & H5Grefresh \\
-    \hline
-    close & H5Gclose \\
-    \hline
-    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}DATASET} \\
-    \hline
-    create & H5Dcreate1 (deprecated) \\
-           & H5Dcreate2 \\
-    \hline
-    open & H5Dopen1 (deprecated) \\
-         & H5Dopen2 \\
-    \hline
-    read & H5Dread \\
-    \hline
-    write & H5Dwrite \\
-    \hline
-    get & H5Dget\_access\_plist \\
-        & H5Dget\_create\_plist \\
-        & H5Dextend \\
-        & H5Dget\_offset \\
-        & H5Dget\_space \\
-        & H5Dget\_space\_status \\
-        & H5Dget\_storage\_size \\
-        & H5Dget\_type \\
-    \hline
-    specific & H5Dextend (deprecated) \\
-             & H5Dflush \\
-             & H5Drefresh \\
-             & H5Dset\_extent \\
-    \hline
-    close & H5Dclose \\
-    \hline
-    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}OBJECT} \\
-    \hline
-    open & H5Oopen \\
-         & H5Oopen\_by\_addr \\
-         & H5Oopen\_by\_idx \\
-         & H5Oopen\_by\_name \\
-    \hline
-    copy & H5Ocopy \\
-    \hline
-    get & N/A \\
-    \hline
-    specific & H5Odecr\_refcount \\
-             & H5Oexists\_by\_name \\
-             & H5Oflush \\
-             & H5O\_incr\_refcount \\
-             & H5Orefresh \\
-             & H5Ovisit\_by\_name1 (deprecated) \\
-             & H5Ovisit\_by\_name2 \\
-             & H5Ovisit1 (deprecated) \\
-             & H5Ovisit2 \\
-    \hline
-    close & H5Oclose \\
-    \hline
-    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}LINK} \\
-    \hline
-    create & H5Glink (deprecated) \\
-           & H5Glink2 (deprecated) \\
-           & H5Lcreate\_hard \\
-           & H5Lcreate\_soft \\
-           & H5Lcreate\_ud \\
-           & H5Olink \\
-    \hline
-    copy & H5Lcopy \\
-    \hline
-    move & H5Gmove (deprecated) \\
-         & H5Gmove2 (deprecated) \\
-         & H5Lmove \\
-    \hline
-    get & H5Gget\_linkval (deprecated) \\
-        & H5Lget\_info \\
-        & H5Lget\_info\_by\_idx \\
-        & H5Lget\_name\_by\_idx \\
-        & H5Lget\_val \\
-        & H5Lget\_val\_by\_idx \\
-    \hline
-    specific & H5Gunlink (deprecated) \\
-             & H5Ldelete \\
-             & H5Ldelete\_by\_idx \\
-             & H5Lexists \\
-             & H5Literate \\
-             & H5Literate\_by\_name \\
-             & H5Lvisit \\
-             & H5Lvisit\_by\_name \\
-    \hline
-    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}DATATYPE} \\
-    \hline
-    commit & H5Tcommit1 (deprecated) \\
-           & H5Tcommit2 \\
-           & H5Tcommit\_anon \\
-    \hline
-    open & H5Topen1 (deprecated) \\
-         & H5Topen2 \\
-    \hline
-    get & H5Tget\_create\_plist \\
-    \hline
-    specific & H5Tflush \\
-             & H5Trefresh \\
-    \hline
-    close & H5Tclose \\
-    \hline
-    \multicolumn{2}{|>{\raggedright\arraybackslash}p{\linewidth}|}{\cellcolor{gray!35}ATTRIBUTE} \\
-    \hline
-    create & H5Acreate1 (deprecated) \\
-           & H5Acreate2 \\
-           & H5Acreate\_by\_name \\
-    \hline
-    open & H5Aopen \\
-         & H5Aopen\_by\_idx \\
-         & H5Aopen\_by\_name \\
-         & H5Aopen\_idx (deprecated)\\
-         & H5Aopen\_name (deprecated) \\
-    \hline
-    read & H5Aread \\
-    \hline
-    write & H5Awrite \\
-    \hline
-    get & H5Aget\_get\_create\_plist \\
-        & H5Aget\_info \\
-        & H5Aget\_info\_by\_idx \\
-        & H5Aget\_info\_by\_name \\
-        & H5Aget\_name \\
-        & H5Aget\_name\_by\_idx \\
-        & H5Aget\_space \\
-        & H5Aget\_storage\_size \\
-        & H5Aget\_type \\
-    \hline
-    specific & H5Adelete \\
-             & H5Adelete\_by\_idx \\
-             & H5Adelete\_by\_name \\
-             & H5Aexists \\
-             & H5Aexists\_by\_name \\
-             & H5Aiterate1 (deprecated) \\
-             & H5Aiterate2 \\
-             & H5Aiterate\_by\_name \\
-             & H5Arename \\
-             & H5Arename\_by\_name \\
-    \hline
-    close & H5Aclose \\
-    \hline
-\caption{Breakdown of HDF5 API calls by VOL callback}
-\end{longtable}

### 2019-12-05 RFCs/HDF5/VOL/connector_author_guide/connector_interface.tex
Extra pass over GET/SPECIFIC callback variable args.
Former-commit-id: aa84c8f75e1afd60adf7115cbb8e8fc08ae5db08

@@
 \begin{tabular}{l p{13.5cm}}
-  \texttt{attr} & (IN): An attribute or location object where information
+  \texttt{obj} & (IN): An attribute or location object where information
   needs to be retrieved from.\\
@@
   \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
+  \item \texttt{H5VL\_loc\_params\_t *loc\_params} (IN): Pointer to the location parameters
     explained in Section~\ref{sec:map}. 
@@
   \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
+  \item \texttt{H5VL\_loc\_params\_t *loc\_params} (IN): Pointer to the location parameters
     explained in Section~\ref{sec:map}. The type could be either
@@
   \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
-    explained in Section~\ref{sec:map}.
   \item \texttt{char *attr\_name} (IN): the attribute name to check.
@@
     herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, 
-        hid_t file_space_id, hid_t dxpl_id, const void * buf, void **req);
+        hid_t file_space_id, hid_t dxpl_id, const void *buf, void **req);
 \end{lstlisting}
@@
 \begin{itemize}
-\item \texttt{H5VL\_OBJECT\_GET\_CONT\_INFO}, get the container that the object
-  belongs to:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
-  \item \texttt{void **ret} (OUT): pointer to the file structure returned
-    by the connector.
+\item \texttt{H5VL\_OBJECT\_GET\_CONT\_INFO}, get information about the container
+    that the object belongs to:
+  \begin{enumerate}
+  \item \texttt{H5VL\_file\_cont\_info\_t *info} (OUT): pointer to the file
+    container info structure returned.
   \end{enumerate}
@@
   \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    file creation property list.
+  \item \texttt{unsigned long *fileno} (OUT): buffer for the file number.
   \end{enumerate}
@@
   \begin{enumerate}
-  \item \texttt{unsigned *ret} (OUT): buffer for the intent value.
+  \item \texttt{unsigned *intent\_flags} (OUT): buffer for the intent flags value.
   \end{enumerate}
@@
     H5VL_FILE_IS_ACCESSIBLE,                /* Check if a file is accessible    */
-    H5VL_FILE_DELETE                        /* Delete a file                    */
+    H5VL_FILE_DELETE,                       /* Delete a file                    */
+    H5VL_FILE_IS_EQUAL                      /* Check if two files are the same  */
 } H5VL_file_specific_t;
@@
 \item \texttt{H5VL\_FILE\_POST\_OPEN}, adjust a file after opening it:
+
+\item \texttt{H5VL\_FILE\_FLUSH}, flushes all buffers associated with the container to disk:
   \begin{enumerate}
@@
 
-\item \texttt{H5VL\_FILE\_FLUSH}, flushes all buffers associated with the container to disk:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
-  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
-  \end{enumerate}
-
 \item \texttt{H5VL\_FILE\_REOPEN}, reopens a file:
   \begin{enumerate}
-  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
-  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
+      \item \texttt{void *file} (IN): pointer to the reopened file (same type
+          of pointer as is returned from the connector's create/open callbacks).
   \end{enumerate}
@@
     specified by \texttt{file} is to be mounted.
-  \item \texttt{void *file} (IN): child file to be mounted.
+  \item \texttt{void *child} (IN): child file to be mounted (same type
+          of pointer as is returned from the connector's create/open callbacks).
   \item \texttt{hid\_t *fmpl\_id} (IN): file mount property list.
@@
   \end{enumerate}
+
+\item \texttt{H5VL\_FILE\_IS\_EQUAL}, check if one file is equal to another:
+  \begin{enumerate}
+  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
+  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
+  \end{enumerate}
+
  \end{itemize}
@@
 \begin{lstlisting}
-    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
+    void *(*create)(void *obj, H5VL_loc_params_t *loc_params, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
   start.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
   Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
@@
 \begin{lstlisting}
-    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
+    void *(*open)(void *obj, H5VL_loc_params_t *loc_params, 
         const char*name, hid_t gapl_id, hid_t dxpl_id, void **req);
@@
   opened or where the look-up of the target object needs to start.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
   Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
@@
   \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
-    explained in Section~\ref{sec:map}. 
-  \item \texttt{H5G\_info\_t *ginfo} (OUT): info structure to fill the
+  \item \texttt{H5VL\_loc\_params\_t *loc\_params} (IN): Pointer to the location
+      parameters explained in Section~\ref{sec:map}. 
+  \item \texttt{H5G\_info\_t *group\_info} (OUT): info structure to fill the
     group info in.
@@
 \begin{lstlisting}
-	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}
@@
   \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in Section~\ref{sec:map}.\\
   \texttt{specific\_type} & (IN): The type of the operation.\\
@@
     herr_t (*create)(H5VL_link_create_type_t create_type, void *obj,
-        H5VL_loc_params_t loc_params, hid_t lcpl_id, 
+        H5VL_loc_params_t *loc_params, hid_t lcpl_id, 
         hid_t lapl_id, hid_t dxpl_id, void **req);
@@
   created from.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
   Section~\ref{sec:map} for the source object. \\
@@
 \begin{lstlisting}
-    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+    herr_t (*copy)(void *src_obj, H5VL_loc_params_t *loc_params1, void *dst_obj, H5VL_loc_params_t *loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
   \texttt{src\_obj} & (IN): original/source object or file. \\
-  \texttt{loc\_params1} & (IN): The location parameters for the source
+  \texttt{loc\_params1} & (IN): Pointer to the location parameters for the source
   object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
   \texttt{dst\_obj} & (IN): destination object or file. \\
-  \texttt{loc\_params1} & (IN): The location parameters for the destination
+  \texttt{loc\_params1} & (IN): Pointer to the location parameters for the destination
   object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
@@
 \begin{lstlisting}
-    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+    herr_t (*move)(void *src_obj, H5VL_loc_params_t *loc_params1, void *dst_obj, H5VL_loc_params_t *loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
 \begin{lstlisting}
-    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
+    herr_t (*get)(void *obj, H5VL_loc_params_t *loc_params, 
         H5VL_link_get_t get_type, hid_t dxpl_id, void **req, 
@@
   retrieved from.\\
-  \texttt{loc\_params} & (IN): The location parameters for the source
+  \texttt{loc\_params} & (IN): Pointer to the location parameters for the source
   object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} or \texttt{H5VL\_OBJECT\_BY\_IDX} in this
@@
   \begin{enumerate}
-  \item \texttt{H5L\_info\_t linfo} (OUT): pointer to info structure to
+  \item \texttt{H5L\_info\_t *linfo} (OUT): pointer to info structure to
     fill.
@@
 \begin{lstlisting}
-	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}
@@
   \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
-  \texttt{loc\_params} & (IN): The location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in Section~\ref{sec:map}.\\
   \texttt{specific\_type} & (IN): The type of the operation.\\
@@
 
-\item \texttt{H5VL\_LINK\_EXITS}, to determine whether the link specified
+\item \texttt{H5VL\_LINK\_EXISTS}, to determine whether the link specified
   in the \texttt{loc\_params} exits (\texttt{loc\_params} is of type \texttt{H5VL\_OBJECT\_BY\_NAME} only with this type):
@@
   \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
-  \item \texttt{hsize\_t *idx} (IN/OUT):  iteration position where to start and return position where an interrupted iteration may restart.\\
+  \item \texttt{hsize\_t *idx\_p} (IN/OUT):  iteration position where to start and return position where an interrupted iteration may restart.\\
   \item \texttt{H5L\_iterate\_t op} (IN): User-defined function to pass each link to. \\
@@
 typedef enum H5VL_object_get_t {                                                 
+    H5VL_OBJECT_GET_FILE,              /* object's file                     */   
     H5VL_OBJECT_GET_NAME,              /* object name                       */   
@@
 \begin{itemize}
+\item \texttt{H5VL\_OBJECT\_GET\_FILE}, to retrieve a file for a referenced object:
+  \begin{enumerate}
+  \item \texttt{void **ret} (OUT): pointer to buffer to return the file.
+  \end{enumerate}
+
  \item \texttt{H5VL\_OBJECT\_GET\_NAME}, to retrieve a name for a referenced object:
@@
     only the buffer size needed.
-  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
-    query.
-  \item \texttt{void *ref} (IN): the region reference to query.
   \end{enumerate}
@@
   \item \texttt{H5O\_type\_t *type} (OUT): buffer to return the object type.
-  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
-    query.
-  \item \texttt{void *ref} (IN): the region reference to query.
   \end{enumerate}
@@
 
+\item \texttt{H5VL\_OBJECT\_LOOKUP}, Look up an object:
+  \begin{enumerate}
+  \item \texttt{void *token} (IN): The object's token.\\
+  \end{enumerate}
+
 \item \texttt{H5VL\_OBJECT\_VISIT}, to iterate over all objects starting at the location provided and call a user-specified callback on each one:
@@
   \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
+  \item \texttt{unsigned fields} (IN): Fields in H5O\_info\_t struct to return. \\
   \end{enumerate}

### 2019-12-09 RFCs/HDF5/VOL/connector_author_guide/connector_interface.tex
The VOL connector author guide should be largely done for the time being.
Former-commit-id: 45242fb08a77b641dbe164270db51dcb6dc0d19c

@@
 All classes and their defined callbacks will be detailed in the following sub-sections.
+
+To handle that large set of API routines, each class in the Data Model category has three generic callbacks, \texttt{get}, \texttt{specific}, and \texttt{optional} to handle the three set of API operations outline above respectively.
+The callbacks will have a \texttt{va\_list} argument to handle the different set of parameters that could be passed in.
+The \texttt{get} and \texttt{specific} callbacks also have an \texttt{op\_type} that contain an \texttt{enum} of the type of operation that is requested to be performed.
+Using that type, the \texttt{va\_list} argument can be parsed.
+The \texttt{optional} callback is a free for all callback where anything from the API layer is passed in directly.
+This callback is used to support connector specific operations in the API that other connectors should or would not know about.
+More information about types and the arguments for each type will be detailed in the corresponding class arguments.
 
@@
   operations if the HDF5 library adds support for them in future
-  releases (beyond the 1.8 series). That pointer is set by the VOL
+  releases. That pointer is set by the VOL
   connector to a request object it creates to manage progress on that
@@
 concise and readable, it was decided not to have a one-to-one mapping
-between API operation and callbacks. Furthermore, to keep the
-callbacks themselves short and not cluttered with a lot of parameters,
-some of the parameters are passed in as properties in property lists
-included with the callback. The value of those properties can be
-retrieved by calling the public routine (or its private version if
-this is an internal connector): 
-\begin{lstlisting}
-herr_t H5Pget(hid_t plist_id, const char *property_name, void *value);
-\end{lstlisting}
-The property names and value types will be detailed when describing
-each callback in their respective sections.
+between API operation and callbacks. The parameter names and types will be
+detailed when describing each callback in their respective sections.
 
@@
 
-\newpage
-
-\begin{lstlisting}[caption={Structure to hold parameters for object locations, H5VLpublic.h}, captionpos=b, label={lst:ObjLocclass}]
+\begin{lstlisting}[caption={Structure to hold parameters for object locations, H5VLconnector.h}, captionpos=b, label={lst:ObjLocclass}]
 /* 
@@
 \end{lstlisting}
-
-\newpage
-
-Other API routines that would make a one-to-one mapping difficult are:
-\begin{itemize} 
-\item the \texttt{Get} operations that retrieve something from an object; for example a property list or a datatype of a dataset, etc.
-\item API routines are specific to each class of callbacks (attributes, files, etc...). Having a callback for each one would clutter the VOL callback structure and reduce user-friendliness. 
-\item API routines that make sense to only implement in the native HDF5 file format and would not be possible to implement in other connectors.
-Adding a callback for those routines would be confusing to connector developers.
-\end{itemize}
-
-To handle that large set of API routines, each class in the Data Model category has three generic callbacks, \texttt{get}, \texttt{specific}, and \texttt{optional} to handle the three set of API operations outline above respectively.
-The callbacks will have a \texttt{va\_list} argument to handle the different set of parameters that could be passed in.
-The \texttt{get} and \texttt{specific} callbacks also have an \texttt{op\_type} that contain an \texttt{enum} of the type of operation that is requested to be performed.
-Using that type, the \texttt{va\_list} argument can be parsed.
-The \texttt{optional} callback is a free for all callback where anything from the API layer is passed in directly.
-This callback is used to support connector specific operations in the API that other connectors should or would not know about.
-More information about types and the arguments for each type will be detailed in the corresponding class arguments.
 

### 2019-12-09 RFCs/HDF5/VOL/connector_author_guide/intro.tex
The VOL connector author guide should be largely done for the time being.
Former-commit-id: 45242fb08a77b641dbe164270db51dcb6dc0d19c

@@
 of the VOL architecture obtained by reading the VOL architectural design
-document~\cite{vol:rfc}.
+document.
+
+This is a preliminary version of this document. The final version will be
+released with the HDF5 1.12.0 release in late 2019.

### 2019-12-09 RFCs/HDF5/VOL/connector_author_guide/new_api_calls.tex
The VOL connector author guide should be largely done for the time being.
Former-commit-id: 45242fb08a77b641dbe164270db51dcb6dc0d19c

@@
 \label{sec:api}
-New API routines have been added to the HDF5 library to manage VOL connectors. This section details each new API call and explains their intended usage.
-
+New API routines have been added to the HDF5 library to manage VOL connectors.
+This section details each new API call and explains their intended usage.
 Additionally, a set of API calls that map directly to the VOL callbacks themselves have been added to aid in the development of passthrough connectors which can be stacked and/or split.
-For more information on usage refer to Section~\ref{sec:stack}.
-The routines are listed in Appendix~\ref{sec:B}.
+A list of these API calls is given in an appendix.
 
@@
 \subsection{H5VLpublic.h}
+
+The API calls in this header are for VOL management and general use (i.e., not
+limited to VOL connector authors).
 
@@
 Unregisters a connector from the library and return a positive value on success otherwise return a negative value.
-That native VOL connector cannot be unregistered (this will return a negative herr\_t value).\bigskip
+The native VOL connector cannot be unregistered (this will return a negative herr\_t value).\bigskip
 
@@
 
-\subsubsection{H5VLobject\_register}
+This functionality is intended for VOL connector authors and includes helper
+functions that are useful for writing connectors. Callback equivalent
+functions can be found in {\tt H5VLconnector\_passthru.h}. A list of these
+functions is included as an appendix to this document.
+
+\subsubsection{H5VLobject}
 \begin{mdframed}[style=bgbox]
@@
 \begin{lstlisting}
-  hid_t H5VLobject_register(void *obj, H5I_type_t obj_type, hid_t connector_id);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
- {\tt obj} & (IN): pointer to the object to register.\\
- {\tt obj\_type} & (IN): The type of the object ({\tt H5I\_FILE, H5I\_DATASET, H5I\_GROUP, H5I\_ATTRIBUTE, H5I\_DATATYPE}).\\
- {\tt connector\_id} & (IN): identifier of the vol connector the object is associated with.\\
-\end{tabular}
-\end{mdframed}
-Creates an HDF5 identifier for an object given its type and an identifier of the connector that was used in creating it.
-This function is typically used by external connectors wanting to wrap an {\tt hid\_t} around a connector specific object to return to a user callback for functions like {\tt H5Literate, H5Lvisit, H5Ovisit, H5Aiterate} etc...
-A Negative value is returned on failure.\bigskip
-
-\subsubsection{H5VLget\_object}
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-  herr_t H5VLget_object(hid_t obj_id, void **obj); 
+  void *H5VLget_object(hid_t obj_id); 
 \end{lstlisting}
@@
  {\tt obj\_id} & (IN): identifier of the object to dereference.\\
- {\tt obj} & (OUT): buffer to store the pointer of the VOL object associated with the object identifier.\\
 \end{tabular}
@@
 Retrieves a pointer to the VOL object from an HDF5 file or object identifier.\bigskip
+
+\subsubsection{H5VLget\_file\_type}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  hid_t H5VLget_file_type(void *file_obj, hid_t connector_id, hid_t dtype_id); 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt file\_obj} & (IN): pointer to a file or file object's connector-specific data.\\
+ {\tt connector\_id} & (IN): A valid identifier of the connector to use.\\
+ {\tt dtype\_id} & (IN): A valid identifier for the type.\\
+\end{tabular}
+\end{mdframed}
+Returns a copy of the {\tt dtype\_id} parameter but with the location set to
+be in the file. Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.\bigskip
+
+\subsubsection{H5VLpeek\_connector}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  hid_t H5VLpeek_connector_id(const char *name); 
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt name} & (IN): name of the connector to query.\\
+\end{tabular}
+\end{mdframed}
+Retrieves the ID for a registered VOL connector. This is done without duplicating
+the ID and transferring ownership to the caller (as it normally the case in the
+HDF5 library). The ID returned from this operation should not be closed.
+This is intended for use by VOL connectors to find their own ID.
+
+Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.\bigskip
 

### 2019-12-09 RFCs/HDF5/VOL/connector_author_guide/writing_new.tex
The VOL connector author guide should be largely done for the time being.
Former-commit-id: 45242fb08a77b641dbe164270db51dcb6dc0d19c

--- 2018-01-10 RFCs/HDF5/VOL/user_guide/external.tex
@@
-\section{Creating and Using an External Plugin}
-External plugins are developed outside of the HDF5 library and do not
-use any internal HDF5 private functions. They do not require to be
-shipped with the HDF5 library, but can just link to it from userspace
-just like an HDF5 application. If an external VOL plugin is installed on the system as a shared library or a DLL, the library can search for it and load it dynamically to be used by an application.
+\section{Creating a New Connector}
 
-\subsection{Creating an External Plugin}
-Developing an external plugin is similar to developing an internal plugin.
-Refer to Section~\ref{sec:vol} for details on plugin creation.
-The important thing to keep in mind is that external plugins cannot use internal HDF5 features.
-The ``value'' field for an external plugin should be a positive integer greater than 128.
-The name should be unique across all plugins registered with the library.
+\subsection{Overview}
+Creating a new VOL connector can be a complicated process. You will need to map
+your storage system to the HDF5 data model through the lens of the VOL and this
+may involve some impedence mismatch that you will have to work around. The good
+news is that the HDF5 library has been re-engineered to handle arbitrary,
+connector-specific data structures via the VOL callbacks, so no knowledge of
+the library internals is necessary to write a VOL connector.
+
+Writing a VOL connector requires these things:
+
+\begin{enumerate}
+    \item Decide on library vs plugin vs internal.
+    \item Set up your build/test files (CMake, Autotools, etc.).
+    \item Fill in some boilerplate information in your {\tt H5VL\_class\_t} struct.
+    \item Decide how you will perform any necessary initialization needed
+        by your storage system.
+    \item Map Storage to HDF5 File Objects
+    \item Create implementations for the callbacks you need to support.
+    \item Test the connector.
+\end{enumerate}
+
+Each of the steps listed above is decribed in more detail in this section of the document.
+
+The "model then implement" steps can be performed iteratively. You might begin
+by only supporting files, datasets, and groups and only allowing basic operations
+on them. In some cases, this may be all that is needed. As your needs grow, you
+can repeat those steps and increase the connector's HDF5 API coverage at a pace
+that makes sense for your users.
+
+Also, note that this document only covers writing VOL connectors using the
+C programming language. It is often possible to write connectors in other programming languages
+(e.g.; Python) via the language's C interop facilities, but that topic is out of
+scope for this document.
+
+\subsection{Sources Of Information}
+
+Use of the VOL, including topics such as registration and loading VOL plugins, is
+described in the VOL User Guide.
+
+Public header files you will need to be familiar with include:
+
+\begin{tabularx}{\linewidth}{ l X }
+  \texttt{H5VLpublic.h} & Public VOL header.\\
+  \texttt{H5VLconnector.h} & Main connector author header. Contains definitions for the main VOL struct and callbacks, enum values, etc.\\
+  \texttt{H5VLconnector\_passthru.h} & Helper routines for passthrough connector authors.\\
+    \texttt{H5VLnative.h} & Native VOL connector header. May be useful if your connector will attempt to implement native HDF5 API calls that are handled via the \textit{optional} callbacks.\\
+  \texttt{H5PLextern.h} & Needed if your connector will be built as a plugin.\\
+\end{tabularx}
+
+Many VOL connectors can be found on The HDF Group's Bitbucket server, located at
+\url{https://bitbucket.hdfgroup.org/projects/HDF5VOL}. Not all of these VOL
+connectors are supported by THe HDF Group and the level of completeness varies,
+but the connectors found there can serve as examples of working implementations.
+
+\subsection{Library vs Plugin vs Internal}
+
+When building a VOL connector, you have several options:
+
+\subsubsection*{Library}
+
+The connector can be built as a normal shared or static library. Software that
+uses your connector will have to link to it just like any other library. This
+can be convenient since you don't have to deal with plugin paths and searching
+for the connector at runtime, but it also means that software which uses
+your connector will have to be built and linked against it.
+
+\subsubsection*{Plugin}
+
+You can also build your connector as a dynamically loaded plugin. The mechanism
+for this is the same mechanism used to dynamically load HDF5 filter plugins. This can
+allow use of your connector via the VOL environment variable, without modifying
+the application, but requires your plugin to be discoverable at runtime. See
+the VOL User Guide for more information about using HDF5 plugins.
+
+To build your connector as a plugin, you will have to include {\tt H5PLextern.h}
+(a public header distributed with the library) and implement the
+{\tt H5PLget\_plugin\_type()} and {\tt H5PLget\_plugin\_info()}
+calls, both of which are trivial to code up. It also often requires your
+connector to be built with certain compile/link options. The VOL connector
+template does all of these things.
+
+To show how easy this is to accomplish, here is the complete implementation
+of those functions in the template VOL connector:
+
+\begin{lstlisting}
+H5PL_type_t H5PLget_plugin_type(void) {return H5PL_TYPE_VOL;}
+const void *H5PLget_plugin_info(void) {return &template_class_g;}
+\end{lstlisting}
+
+The HDF5 library's plugin loading code will call {\tt H5PLget\_plugin\_type()}
+to determine the type of plugin (e.g.; filter, VOL) and {\tt H5PLget\_plugin\_info()}
+to get the class struct, which allows the library to query the plugin for its
+name and value to see if it has found a requested plugin. When a match is found,
+the library will use the class struct to register the connector and map its callbacks.
 
@@
 
-Implementing iteration and visit callbacks in external plugins requires the plugin invoking the user defined callback function with an HDF5 identifier ({\tt hid\_t}) on the location object.
-The current HDF5 H5I API does not allow creating and dereferencing identifiers that point to HDF5 object types.
-Therefore, two new API routines have been added (see Section~\ref{sec:api} for more details) to get around that.
-{\tt H5VLobject\_register()} is used to create an HDF5 identifier for a VOL object handle (file, group, dataset, named datatype, or attribute).
-{\tt H5VLget\_object()} is used to derefernce the HDF5 identifier back to the VOL object handle.
+\subsubsection*{Internal}
 
-\subsection{Using an External Plugin}
-Unlike internal plugins, external plugins cannot create an API routine for applications to use to set the VOL plugin in the file access property list.
-External plugin developers can, however, provide a wrapper routine that registers the plugin with {\tt H5VLregister()} instead of having the application call that directly with the pointer to the plugin class structure.
-Both ways are possible if the external plugin used is in the application's userspace.
-External plugins provided by third party vendors that are not in the application's userspace but are installed on the system with a shared library or DLL can be registered by the application using {\tt H5VLregister\_name()} provided that the application knows the plugin's name in advance.
+Your VOL connector can also be constructed as a part of the HDF5 library. This
+works in the same way as the stdio and multi virtual file drivers (VFDs) and
+does not require knowledge of HDF5 internals or use of non-public API calls. You
+simply have to add your connector's files to the {\tt Makefile.am} and/or
+{\tt CMakeLists.txt} files in the source distribution's {\tt src} directory.
+This requires maintaining a private build of the library, though, and is not
+recommended.
 
-The registration operation will return a global identifier for the registered plugin.
-Applications can query the library for that identifier using the plugin name with {\tt H5VLget\_plugin\_id()}.
-This identifier is used to initialize the plugin if it requires an initialization phase.
-A third party library could use that ID to create a plugin that stacks or mirrors on top of an internal plugin using that identifier (refer to Section~\ref{sec:stack} for more details on stacking and mirroring).
+\subsection{Build Files / VOL Template}
 
-Some plugins could require an initialization phase before using the plugin with some input parameters from users.
-This process is done by creating a VOL initialization property list and setting a public property that should be defined by the internal plugin to the hostname of the remote machine.
-The user then calls the initialize routine ({\tt H5VLintialize()}) with the plugin\_id and the property list to initialize the plugin.
-An external plugin could abstract those operations into a wrapper routine that wraps the property list creation, property settings, and plugin initialization into one call that the user makes to simplify this process.
+We have created a template VOL connector that includes both Autotools and CMake
+build files. The constructed VOL connector includes no real functionality, but 
+can be registered and loaded as a plugin.
 
-The application then sets the plugin access property in the file access property list to the external plugin using the plugin identifier with this API routine:
-\begin{lstlisting}
-  herr_t H5Pset_vol(hid_t fapl_id, hid_t plugin_id, const void *new_vol_info);
-\end{lstlisting}
-where {\tt new\_vol\_info} is the plugin information needed from the application.
-Typically it is a plugin defined structure with some fields to setup the plugin access.
-The external plugin could also provide a wrapper function around this to make it easier for the application to use.
+The VOL template  can be found here:
 
-Now that the plugin is initialized, the application can create or open an HDF5 container using the external plugin.
-After closing all objects and containers on that plugin, the application should terminate access to the selected plugin if it requires a termination phase by calling {\tt H5VLterminate()} with the required termination properties (similar to the initialization phase).
+\quad \quad \url{https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/template}
 
-Finally, the application is required to un-register the plugin from the library when access to the container(s) is terminated using {\tt H5VLunregister}.
+The purpose of this template is to quickly get you to the point where you can
+begin filling in the callback functions and writing tests. You can copy this
+code to your own repository to serve as the basis for your new connector.
 
-% /* Function prototypes */
-% H5_DLL htri_t H5VLis_registered(hid_t id);
-% H5_DLL ssize_t H5VLget_plugin_name(hid_t id, char *name/*out*/, size_t size);
+\subsection{{\tt H5VL\_class\_t} Boilerplate}
 
-% H5_DLL void *H5Pget_vol_info(hid_t plist_id);
+Several fields in the {\tt H5VL\_class\_t} struct will need to be filled in.
+
+In HDF5 1.12.0, {\tt version} will be 1, indicating version 1 of the {\tt H5VL\_class\_t} struct.
+
+Every connector needs a {\tt name} and {\tt value}. The library will use these when
+loading and registering the connector (as described in the VOL User Guide), so
+they should be unique in your ecosystem.
+
+VOL connector values are integers, with a maximum value of 65535. Values from
+0 to 255 are reserved for internal use by The HDF Group. The native VOL connector
+has a value of 0.
+
+As is the case with HDF5 filters, The HDF Group can register the value you've
+chosen for your VOL connector so that others don't use it. Please contact
+\href{mailto:help@hdfgroup.org}{help@hdfgroup.org} for help with this. We currently
+do not register connector names.
+
+The {\tt cap\_flags} field is currently not fully utilized. In the future, this
+will be most likely be used to indicate which callbacks and capabilities are
+supported by the VOL connector, but for now this struct field contains few flags, 
+a list of which can be found in {\tt H5VLconnector.h}.
+
+\subsection{Initialization and Shutdown}
+
+You'll need to decide how to perform any initialization and shutdown tasks that
+are required by your connector. There are initialize and terminate callbacks
+in the {\tt H5VL\_class\_t} struct to handle this. They are invoked when
+the connector is registered and unregistered, respectively. If this is
+unsuitable, you may have to create custom connector-specific API calls to handle
+initialization and termination. It may also be useful to perform operations in
+a custom API call used to set the VOL connector in the fapl.
+
+\subsection{Map Storage to HDF5 File Objects}
+
+The most difficult part of designing a new VOL connector is going to determining
+how to support HDF5 file objects and operaions using your storage system.
+There isn't much specific advice to give here, as
+each connector will have unique needs, but a forthcoming "tutorial" connector
+will set up a simple connector and demonstrate this process.
+
+\subsection{Fill In VOL Callbacks}
+
+For each file object you support in your connector (including the file itself),
+you will need to create a data struct to hold whatever file object
+metadata that are needed by your connector. For example, a data structure for
+a VOL connector based on text files might have a file struct that contains a
+file pointer for the text file, buffers used for cacheing data, etc. Pointers
+to these data structures are where your connector's state is stored and are
+returned to the HDF5 library from the create/open/etc. callbacks such as
+\textit{dataset create}.
+
+Once you have your data structures, you'll need to create your own
+implementations of the callback functions and map them via your
+{\tt H5VL\_class\_t} struct. 
+\subsection{Testing Your Connector}
+
+At the time of writing, some of the HDF5 library tests have been abstracted
+out of the library with their native-file-format-only sections removed and
+added to a VOL test suite available here:
+
+\quad \quad \url{https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/vol-tests}
+
+This is an evolving set of tests, so see the documentation in that repository
+for instructions as to its use. You may want to clone and modify and/or
+extend these tests for use with your own connector.
+
+In the future, we plan to modify the HDF5 test suite that ships with the
+library to use a future VOL capabilities flags scheme to selectively run
+tests that a particular connector supports. As this is a large task, it may be
+some time before that work is complete.
+
+\subsection{Passthrough Connectors}
+
+Coming Soon
+
 %%% Local Variables: 

### 2020-02-24 RFCs/HDF5/VOL/connector_author_guide/appendix.tex
Updated VOL user guide and connector author guide to be in agreement with final 1.12.0 changes.
Former-commit-id: f656be3383755816b47e431b1dabfeb7ee3e402a

@@
     open & H5Oopen \\
-         & H5Oopen\_by\_addr \\
+         & H5Oopen\_by\_addr (deprecated) \\
          & H5Oopen\_by\_idx \\
          & H5Oopen\_by\_name \\
+         & H5Oopen\_by\_token \\
     \hline
@@
     \hline
-    get & N/A \\
+    get & H5Oget\_info1 (deprecated) \\
+        & H5Oget\_info2 (deprecated) \\
+        & H5Oget\_info3 \\
     \hline
@@
              & H5Ovisit\_by\_name1 (deprecated) \\
-             & H5Ovisit\_by\_name2 \\
+             & H5Ovisit\_by\_name2 (deprecated) \\
+             & H5Ovisit\_by\_name3 \\
              & H5Ovisit1 (deprecated) \\
-             & H5Ovisit2 \\
+             & H5Ovisit2 (deprecated) \\
+             & H5Ovisit3 \\
     \hline
@@
     get & H5Gget\_linkval (deprecated) \\
-        & H5Lget\_info \\
+        & H5Lget\_info1 (deprecated) \\
+        & H5Lget\_info2 \\
         & H5Lget\_info\_by\_idx \\
@@
              & H5Lexists \\
-             & H5Literate \\
-             & H5Literate\_by\_name \\
-             & H5Lvisit \\
-             & H5Lvisit\_by\_name \\
+             & H5Literate1 (deprecated) \\
+             & H5Literate2 \\
+             & H5Literate\_by\_name1 (deprecated) \\
+             & H5Literate\_by\_name2 \\
+             & H5Lvisit1 (deprecated) \\
+             & H5Lvisit2 \\
+             & H5Lvisit\_by\_name1 (deprecated) \\
+             & H5Lvisit\_by\_name2 \\
     \hline
@@
 herr_t H5VLattr_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLattr_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLattr_optional(void *obj, hid_t connector_id, H5VL_attribute_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 herr_t H5VLattr_close(void *attr, hid_t connector_id, hid_t dxpl_id, void **req);
@@
 herr_t H5VLdataset_specific(void *obj, hid_t connector_id, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLdataset_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdataset_optional(void *obj, hid_t connector_id, H5VL_dataset_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 herr_t H5VLdataset_close(void *dset, hid_t connector_id, hid_t dxpl_id, void **req);
@@
 herr_t H5VLfile_specific(void *obj, hid_t connector_id, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLfile_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLfile_optional(void *obj, hid_t connector_id, H5VL_file_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 herr_t H5VLfile_close(void *file, hid_t connector_id, hid_t dxpl_id, void **req);
@@
 herr_t H5VLgroup_specific(void *obj, hid_t connector_id, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLgroup_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLgroup_optional(void *obj, hid_t connector_id, H5VL_group_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 herr_t H5VLgroup_close(void *grp, hid_t connector_id, hid_t dxpl_id, void **req);
@@
 herr_t H5VLlink_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLlink_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLlink_optional(void *obj, hid_t connector_id, H5VL_link_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 
@@
 herr_t H5VLobject_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLobject_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLobject_optional(void *obj, hid_t connector_id, H5VL_object_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 
@@
 herr_t H5VLdatatype_specific(void *obj, hid_t connector_id, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLdatatype_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLdatatype_optional(void *obj, hid_t connector_id, H5VL_datatype_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 herr_t H5VLdatatype_close(void *dt, hid_t connector_id, hid_t dxpl_id, void **req);
+
+/* Public wrappers for connector/container introspection callbacks */            
+H5_DLL herr_t H5VLintrospect_get_conn_cls(void *obj, hid_t connector_id, H5VL_get_conn_lvl_t lvl, const H5VL_class_t **conn_cls);                     
+H5_DLL herr_t H5VLintrospect_opt_query(void *obj, hid_t connector_id, H5VL_subclass_t subcls, int opt_type, hbool_t *supported);
 
@@
 herr_t H5VLrequest_specific(void *req, hid_t connector_id, H5VL_request_specific_t specific_type, va_list arguments);
-herr_t H5VLrequest_optional(void *req, hid_t connector_id, va_list arguments);
+herr_t H5VLrequest_optional(void *req, hid_t connector_id, H5VL_request_optional_t opt_type, va_list arguments);
 herr_t H5VLrequest_free(void *req, hid_t connector_id);
@@
 herr_t H5VLblob_specific(void *obj, hid_t connector_id, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);
+H5_DLL herr_t H5VLblob_optional(void *obj, hid_t connector_id, void *blob_id, H5VL_blob_optional_t opt_type, va_list arguments);
+
+/* Public wrappers for token callbacks */                                        
+H5_DLL herr_t H5VLtoken_cmp(void *obj, hid_t connector_id, const H5O_token_t *token1, const H5O_token_t *token2, int *cmp_value);
+H5_DLL herr_t H5VLtoken_to_str(void *obj, H5I_type_t obj_type, hid_t connector_id, const H5O_token_t *token, char **token_str);
+H5_DLL herr_t H5VLtoken_from_str(void *obj, H5I_type_t obj_type, hid_t connector_id, const char *token_str, H5O_token_t *token);
 
 /* Public wrappers for generic 'optional' callback */                            
-herr_t H5VLoptional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLoptional(void *obj, hid_t connector_id, int op_type, hid_t dxpl_id, void **req, va_list arguments);
 

### 2020-02-24 RFCs/HDF5/VOL/connector_author_guide/connector_interface.tex
Updated VOL user guide and connector author guide to be in agreement with final 1.12.0 changes.
Former-commit-id: f656be3383755816b47e431b1dabfeb7ee3e402a

@@
     /* Infrastructure / Services */
+    H5VL_introspect_class_t introspect_cls; /* Container/connector introspection class callbacks */
     H5VL_request_class_t    request_cls;    /* Asynchronous request class callbacks */
     H5VL_blob_class_t       blob_cls;       /* 'blob' callbacks */
+    H5VL_token_class_t      token_cls;      /* VOL connector object token class callbacks */
 
     /* Catch-all */                                                              
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); /* Optional callback */
+    herr_t (*optional)(void *obj, int op_type, hid_t dxpl_id, void **req, va_list arguments); /* Optional callback */
 } H5VL_class_t;
@@
     herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); 
+    herr_t (*optional)(void *obj, H5VL_attr_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments); 
     herr_t (*close) (void *attr, hid_t dxpl_id, void **req);                     
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_attr_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}
@@
   \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
+  \texttt{opt\_type} & (IN): The type of operation.\\
   \texttt{dxpl\_id} & (IN): The data transfer property list.\\
@@
 
-Each connector should be able to parse the \texttt{va\_list arguments} if it has connector specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+Each connector that requires connector-specific operations should be able to use the \texttt{opt\_type} parameter (a connector-specific enum/integer) to determine the type of the operation and parse the \texttt{va\_list arguments} appropriately.
 
@@
     herr_t (*specific)(void *obj, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_dataset_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
     herr_t (*close) (void *dset, hid_t dxpl_id, void **req);
@@
 information about the dataset as specified in the \texttt{get\_type}
-parameter.It returns an \texttt{herr\_t} indicating success or failure.\bigskip
+parameter.It returns an \texttt{herr\_t} indicating success or failure.
+\bigskip
 
@@
 
+Note that \texttt{H5VL\_DATASET\_GET\_OFFSET} (used in \texttt{H5Dget\_offset()}) retains
+the \texttt{haddr\_t} type and was not updated to use the \texttt{H5O\_token\_t}
+type. This enum value and \texttt{H5Dget\_offset()} may be deprecated in a future
+version of the HDF5 and replaced with a token-based equivalent.
+
 \textbf{Arguments:}\\
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_dataset_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}
@@
     herr_t (*specific)(void *obj, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); 
+    herr_t (*optional)(void *obj, H5VL_datatype_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments); 
     herr_t (*close) (void *dt, hid_t dxpl_id, void **req);                       
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_datatype_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}
@@
     herr_t (*specific)(void *obj, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_file_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
     herr_t (*close) (void *file, hid_t dxpl_id, void **req);
@@
 typedef enum H5VL_file_specific_t {                                              
-    H5VL_FILE_POST_OPEN,                    /* Adjust file after open, with wrapping context */
     H5VL_FILE_FLUSH,                        /* Flush file                       */
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_file_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}
@@
     herr_t (*specific)(void *obj, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_group_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
     herr_t (*close) (void *grp, hid_t dxpl_id, void **req);
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_group_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}
@@
     herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); 
+    herr_t (*optional)(void *obj, H5VL_link_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments); 
 } H5VL_link_class_t;   
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_link_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}
@@
     H5VL_OBJECT_GET_TYPE               /* object type                       */  
+    H5VL_OBJECT_GET_INFO               /* H5Oget_info(_by_idx|name)         */
 } H5VL_object_get_t; 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_object_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}
@@
 
-Each connector should be able to parse the \texttt{va\_list arguments} if it has connector specific operations to implement and determine the type of the operation and the parameters through a predefined schema.
+Each connector that requires connector-specific operations should be able to use the \texttt{opt\_type} parameter (a connector-specific enum/integer) to determine the type of the operation and parse the \texttt{va\_list arguments} appropriately.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% INTROSPECTION CALLBACKS %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Introspection Callbacks}
+
+\begin{lstlisting}[caption={Structure for VOL connector introspection callback routines, H5VLconnector.h}, captionpos=b, label={lst:Introspectclass}]
+typedef struct H5VL_introspect_class_t {                                            
+    herr_t (*get_conn_cls)(void *obj, H5VL_get_conn_lvl_t lvl, const struct H5VL_class_t **conn_cls);
+    herr_t (*opt_query)(void *obj, H5VL_subclass_t cls, int opt_type, hbool_t *supported);
+} H5VL_introspect_class_t;
+\end{lstlisting}
+
+\subsubsection{introspect: get\_conn\_cls}
+Get a connector's H5VL\_class\_t struct.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*get_conn_cls)(void *obj, H5VL_get_conn_lvl_t lvl, const struct H5VL_class_t **conn_cls);
+\end{lstlisting}
+
+The \texttt{lvl} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* "Levels" for 'get connector class' introspection callback */                  
+typedef enum H5VL_get_conn_lvl_t {
+    H5VL_GET_CONN_LVL_CURR,         /* Get "current" connector (for this object) */
+    H5VL_GET_CONN_LVL_TERM          /* Get "terminal" connector (for this object) */
+                                    /* (Recursively called, for pass-through connectors) */
+                                    /* (Connectors that "split" must choose which connector to return) */
+} H5VL_get_conn_lvl_t;
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The VOL object.\\
+  \texttt{lvl} & (IN): Current or terminal connector.\\
+  \texttt{cls} & (OUT): A const pointer to the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{introspect: opt\_query}
+Query a class for a capability or functionality.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*opt_query)(void *obj, H5VL_subclass_t cls, int opt_type, hbool_t *supported);
+\end{lstlisting}
+
+The \texttt{lvl} argument is an \texttt{enum}:
+\begin{lstlisting}
+/* Enum type for each VOL subclass */
+/* (Used for various queries, etc) */
+typedef enum H5VL_subclass_t {
+    H5VL_SUBCLS_NONE,                   /* Operations outside of a subclass */
+    H5VL_SUBCLS_INFO,                   /* 'Info' subclass */
+    H5VL_SUBCLS_WRAP,                   /* 'Wrap' subclass */
+    H5VL_SUBCLS_ATTR,                   /* 'Attribute' subclass */
+    H5VL_SUBCLS_DATASET,                /* 'Dataset' subclass */
+    H5VL_SUBCLS_DATATYPE,               /* 'Named datatype' subclass */
+    H5VL_SUBCLS_FILE,                   /* 'File' subclass */
+    H5VL_SUBCLS_GROUP,                  /* 'Group' subclass */
+    H5VL_SUBCLS_LINK,                   /* 'Link' subclass */
+    H5VL_SUBCLS_OBJECT,                 /* 'Object' subclass */
+    H5VL_SUBCLS_REQUEST,                /* 'Request' subclass */
+    H5VL_SUBCLS_BLOB,                   /* 'Blob' subclass */
+    H5VL_SUBCLS_TOKEN                   /* 'Token' subclass */
+} H5VL_subclass_t;
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The VOL object.\\
+  \texttt{cls} & (IN): The VOL 'class' to query.\\
+  \texttt{opt\_type} & (IN): The specific option to query.\\
+  \texttt{supported} & (OUT): Whether the operation is supported or not.\\
+\end{tabular}
+\end{mdframed}
 
@@
     herr_t (*specific)(void *req, H5VL_request_specific_t specific_type, va_list arguments);
-    herr_t (*optional)(void *req, va_list arguments);                            
+    herr_t (*optional)(void *req, H5VL_request_optional_t opt_type, va_list arguments);
     herr_t (*free)(void *req);
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *req, va_list arguments);                            
+    herr_t (*optional)(void *req, H5VL_request_optional_t opt_type, va_list arguments);                            
 \end{lstlisting}
@@
   \texttt{req} & (IN): The async request on which to perform the operation.\\
+  \texttt{opt\_type} & (IN): The type of operation.\\
   \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
@@
 \end{mdframed}
+
+Each connector that requires connector-specific operations should be able to use the \texttt{opt\_type} parameter (a connector-specific enum/integer) to determine the type of the operation and parse the \texttt{va\_list arguments} appropriately.
 
@@
     herr_t (*specific)(void *obj, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);
-    herr_t (*optional)(void *obj, void *blob_id, va_list arguments);             
+    herr_t (*optional)(void *obj, void *blob_id, H5VL_blob_optional_t opt_type, va_list arguments);             
 } H5VL_blob_class_t; 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, void *blob_id, va_list arguments);             
+    herr_t (*optional)(void *obj, void *blob_id, H5VL_blob_optional_t opt_type, va_list arguments);             
 \end{lstlisting}
@@
   \texttt{blob\_id} & (IN): Pointer to the blob's connector-specific ID.\\
+  \texttt{opt\_type} & (IN): The type of operation.\\
   \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
+\end{tabular}
+\end{mdframed}
+
+Each connector that requires connector-specific operations should be able to use the \texttt{opt\_type} parameter (a connector-specific enum/integer) to determine the type of the operation and parse the \texttt{va\_list arguments} appropriately.
+
+%%%%%%%%%%%%%%%%%%%
+% TOKEN CALLBACKS %
+%%%%%%%%%%%%%%%%%%%
+
+\subsection{Token Callbacks}
+
+\begin{lstlisting}[caption={Structure for token callback routines, H5VLconnector.h}, captionpos=b, label={lst:Tokenclass}]
+typedef struct H5VL_token_class_t { 
+    herr_t (*cmp)(void *obj, const H5O_token_t *token1, const H5O_token_t *token2, int *cmp_value);
+    herr_t (*to_str)(void *obj, H5I_type_t obj_type, const H5O_token_t *token, char **token_str);
+    herr_t (*from_str)(void *obj, H5I_type_t obj_type, const char *token_str, H5O_token_t *token);
+} H5VL_token_class_t;
+\end{lstlisting}
+
+\subsubsection{token: cmp}
+Compares two tokens and outputs a value like strcmp.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*cmp)(void *obj, const H5O_token_t *token1, const H5O_token_t *token2, int *cmp_value);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The underlying VOL object.\\
+  \texttt{token1} & (IN): The first token to compare.\\
+  \texttt{token2} & (IN): The second token to compare.\\
+  \texttt{cmp\_value} & (OUT): A value like strcmp.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{token: to\_str}
+Converts a token to a string representation.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*to_str)(void *obj, H5I_type_t obj_type, const H5O_token_t *token, char **token_str);
+\end{lstlisting}
+
+The \texttt{obj\_type} argument is an \texttt{enum} (from \texttt{H5Ipublic.h}):
+\begin{lstlisting}
+typedef enum H5I_type_t {                                                        
+    H5I_UNINIT      = (-2),     /* uninitialized type                           */
+    H5I_BADID       = (-1),     /* invalid Type                                 */
+    H5I_FILE        = 1,        /* type ID for File objects                     */
+    H5I_GROUP,                  /* type ID for Group objects                    */
+    H5I_DATATYPE,               /* type ID for Datatype objects                 */
+    H5I_DATASPACE,              /* type ID for Dataspace objects                */
+    H5I_DATASET,                /* type ID for Dataset objects                  */
+    H5I_MAP,                    /* type ID for Map objects                      */
+    H5I_ATTR,                   /* type ID for Attribute objects                */
+    H5I_VFL,                    /* type ID for virtual file layer               */
+    H5I_VOL,                    /* type ID for virtual object layer             */
+    H5I_GENPROP_CLS,            /* type ID for generic property list classes    */
+    H5I_GENPROP_LST,            /* type ID for generic property lists           */
+    H5I_ERROR_CLASS,            /* type ID for error classes                    */
+    H5I_ERROR_MSG,              /* type ID for error messages                   */
+    H5I_ERROR_STACK,            /* type ID for error stacks                     */
+    H5I_SPACE_SEL_ITER,         /* type ID for dataspace selection iterator     */
+    H5I_NTYPES                  /* number of library types, MUST BE LAST!       */
+} H5I_type_t;
+\end{lstlisting}
+The only values which should be used for this call are:
+\begin{itemize}
+    \item \texttt{H5I\_GROUP}
+    \item \texttt{H5I\_DATATYPE}
+    \item \texttt{H5I\_DATASET}
+    \item \texttt{H5I\_MAP}
+\end{itemize}
+as these are the only objects for which tokens are valid.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The underlying VOL object.\\
+  \texttt{obj\_type} & (IN): The type of the object.\\
+  \texttt{token} & (IN): The token to turn into a string representation.\\
+  \texttt{token\_str} & (OUT): The string representation of the token.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{token: from\_str}
+Converts a string representation of a token to a token.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*from_str)(void *obj, H5I_type_t obj_type, const char *token_str, H5O_token_t *token);
+\end{lstlisting}
+
+The \texttt{obj\_type} argument is an \texttt{enum} (from \texttt{H5Ipublic.h}):
+\begin{lstlisting}
+typedef enum H5I_type_t {                                                        
+    H5I_UNINIT      = (-2),     /* uninitialized type                           */
+    H5I_BADID       = (-1),     /* invalid Type                                 */
+    H5I_FILE        = 1,        /* type ID for File objects                     */
+    H5I_GROUP,                  /* type ID for Group objects                    */
+    H5I_DATATYPE,               /* type ID for Datatype objects                 */
+    H5I_DATASPACE,              /* type ID for Dataspace objects                */
+    H5I_DATASET,                /* type ID for Dataset objects                  */
+    H5I_MAP,                    /* type ID for Map objects                      */
+    H5I_ATTR,                   /* type ID for Attribute objects                */
+    H5I_VFL,                    /* type ID for virtual file layer               */
+    H5I_VOL,                    /* type ID for virtual object layer             */
+    H5I_GENPROP_CLS,            /* type ID for generic property list classes    */
+    H5I_GENPROP_LST,            /* type ID for generic property lists           */
+    H5I_ERROR_CLASS,            /* type ID for error classes                    */
+    H5I_ERROR_MSG,              /* type ID for error messages                   */
+    H5I_ERROR_STACK,            /* type ID for error stacks                     */
+    H5I_SPACE_SEL_ITER,         /* type ID for dataspace selection iterator     */
+    H5I_NTYPES                  /* number of library types, MUST BE LAST!       */
+} H5I_type_t;
+\end{lstlisting}
+The only values which should be used for this call are:
+\begin{itemize}
+    \item \texttt{H5I\_GROUP}
+    \item \texttt{H5I\_DATATYPE}
+    \item \texttt{H5I\_DATASET}
+    \item \texttt{H5I\_MAP}
+\end{itemize}
+as these are the only objects for which tokens are valid.
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The underlying VOL object.\\
+  \texttt{obj\_type} & (IN): The type of the object.\\
+  \texttt{token\_str} & (IN): The string representation of the token.\\
+  \texttt{token} & (OUT): The token created from the string representation.\\
 \end{tabular}
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, int opt_type, hid_t dxpl_id, void **req, va_list arguments);
 \end{lstlisting}

### 2020-02-24 RFCs/HDF5/VOL/user_guide/body.tex
Updated VOL user guide and connector author guide to be in agreement with final 1.12.0 changes.
Former-commit-id: f656be3383755816b47e431b1dabfeb7ee3e402a

@@
 Exactly how you go about setting a VOL connector in a fapl, will depend on the complexity of the VOL connector and how much control you have over the application's source code.
+Note that the environment variable method, though convenient, has some limitations in its implementation, which are discussed below.
 
@@
 
-\quad\quad {\tt hid\_t H5VLregister\_connector(const H5VL\_class\_t *cls, hid\_t vipl\_id)}
+\begin{lstlisting}
+  hid\_t H5VLregister\_connector\_by\_name(const char *connector\_name, hid\_t vipl\_id)
 
-\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_name(const char *connector\_name, hid\_t vipl\_id)}
-
-\quad\quad {\tt hid\_t H5VLregister\_connector\_by\_value(H5VL\_class\_value\_t connector\_value, hid\_t vipl\_id)}
+  hid\_t H5VLregister\_connector\_by\_value(H5VL\_class\_value\_t connector\_value, hid\_t vipl\_id)
+\end{lstlisting}
 
@@
 The functions return {\tt H5I\_INVALID\_HID} if they are unable to register the connector.
-Most people will use the {\tt \_by\_name()} or {\tt \_by\_value} versions of this API call.
-The call that takes an {\tt H5VL\_class\_t} struct is considered a lower-level call this is more commonly used by connector authors in connector-specific setup/registration code.
 Many VOL connectors will provide a connector-specific init call that will load and register the connector for you.
@@
 
-\thgfuturewarning
-
 There is currently no recommended or library-inherent way to version VOL connectors.
@@
 
-\quad\quad {\tt herr\_t H5Pset\_vol(hid\_t plist\_id, hid\_t vol\_id, vol\_info)}
+\begin{lstlisting}
+  herr\_t H5Pset\_vol(hid\_t plist\_id, hid\_t new\_vol\_id, const void *new\_vol\_info)
+\end{lstlisting}
 
 It takes the ID of the file access property list, the ID of the registered VOL connector, and a pointer to whatever connector-specific data the connector is expecting.
-This will usually be a data struct specified in the connector's header.
+This will usually be a data struct specified in the connector's header or a NULL pointer if the connecter requires no special information (as in the native VOL connector).
 
@@
 
-\quad\quad {\tt herr\_t H5VLconnector\_str\_to\_info(const char *str, hid\_t connector\_id, void **info)}
+\begin{lstlisting}
+  herr\_t H5VLconnector\_str\_to\_info(const char *str, hid\_t connector\_id, void **info)
+\end{lstlisting}
 
@@
 
-\quad\quad {\tt herr\_t H5VLfree\_connector\_info(hid\_t connector\_id, void *vol\_info)}
+\begin{lstlisting}
+  herr\_t H5VLfree\_connector\_info(hid\_t connector\_id, void *vol\_info)
+\end{lstlisting}
 
@@
 
+NOTE: Implementing the environment variable in this way means that setting the native VOL connector becomes somewhat awkward as there is no explicit HDF5 API call to do this.
+Instead you will need to get the native VOL connector's ID via {\tt H5VLget\_connector\_id\_by\_value(H5\_VOL\_NATIVE)} and set it manually in the fapl using {\tt H5Pset\_vol()}.
+
 \section{Adapting HDF5 Software to Use the VOL}
 
-The VOL was engineered to be as unobtrusive as possible and, when a connector which implements most/all of the data model functionality is in use, most applications should require little, if any, modification.
-As mentioned in the quick start section, most modifications will probably consist of connector setup code (which can usually be accomplished via the environment variable) and protecting native file format functions.
+The VOL was engineered to be as unobtrusive as possible and, when a connector which implements most/all of the data model functionality is in use, many applications will require little, if any, modification.
+As mentioned in the quick start section, most modifications will probably consist of connector setup code (which can usually be accomplished via the environment variable), adapting code to use the new token-based API calls, and protecting native-VOL-connector-specific functions.
+
+\subsection{${\tt haddr\_t} \rightarrow {\tt H5O\_token\_t}$}
+
+Some HDF5 API calls and data structures refer to addresses in the HDF5 using the {\tt haddr\_t} type.
+Unfortunately, the concept of an "address" will make no sense for many connectors,
+though they may still have some sort of location key (e.g.: a key in a key-value
+pair store).
+
+As a part of the VOL work, the HDF5 API was updated to replace the {\tt haddr\_t}
+type with a new {\tt H5O\_token\_t} type that represents a more generic object location.
+These tokens appear as an opaque byte array of {\tt H5O\_MAX\_TOKEN\_SIZE} bytes that
+is only meaningful for a particular VOL connector. They are not intended for
+interpretation outside of a VOL connector, though a connector author may provide
+an API call to convert their tokens to something meaningful for the storage.
+
+\begin{lstlisting}
+typedef struct H5O_token_t {                                                     
+    uint8_t __data[H5O_MAX_TOKEN_SIZE];                                          
+} H5O_token_t;
+\end{lstlisting}
+
+As an example, in the native VOL connector, the token stores an {\tt haddr\_t}
+address and addresses can be converted to and from tokens using
+{\tt H5VLnative\_addr\_to\_token()} and {\tt H5VLnative\_token\_to\_addr()}.
+
+\begin{lstlisting}
+  herr_t H5VLnative_addr_to_token(hid_t loc_id, haddr_t addr, H5O_token_t *token)
+
+  herr_t H5VLnative_token_to_addr(hid_t loc_id, H5O_token_t token, haddr_t *addr)
+\end{lstlisting}
+
+Several API calls have also been added to compare tokens and convert tokens to
+and from strings.
+
+\begin{lstlisting}
+  herr_t H5Otoken_cmp(hid_t loc_id, const H5O_token_t *token1, const H5O_token_t *token2, int *cmp_value)
+
+  herr_t H5Otoken_to_str(hid_t loc_id, const H5O_token_t *token, char **token_str)
+
+  herr_t H5Otoken_from_str(hid_t loc_id, const char *token_str, H5O_token_t *token)
+\end{lstlisting}
 
 \subsection{Specific API Call Substitutions}
+
 \subsubsection{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}
@@
 
-\subsubsection{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_info3()} {\tt H5Oget\_native\_info()}$}
+\begin{lstlisting}
+  htri_t H5Fis_accessible(const char *container_name, hid_t fapl_id)
+\end{lstlisting}
 
-\thgfuturewarning
+\subsubsection{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_info3()}$ and ${\tt H5Oget\_native\_info()}$}
 
-The {\tt H5Oget\_info1()} and {\tt H5Oget\_info2()} family of HDF5 API calls are often used by user code to obtain information about an object in the file, however these calls return a struct which contains native information and are thus currently handled via the native connector's \textit{object optional} callback and so are not handled by most external VOL connectors.
+The {\tt H5Oget\_info1()} and {\tt H5Oget\_info2()} family of HDF5 API calls are often
+used by user code to obtain information about an object in the file, however these
+calls returned a struct which contained native information and are thus unsuitable
+for use with arbitrary VOL connectors.
 
-These calls will be separated into two functions: one for getting an object's data model information ({\tt H5Oget\_info3()}, which will go through the \textit{object get} callback), and another for returning an object's native file format information ({\tt H5Oget\_native\_info()}, which will go through the native connector's \textit{object optional} callback).
-These API calls will use new {\tt H5O\_info2\_t} and {\tt H5O\_native\_info\_t} structs, respectively, to hold the returned data.
+A new {\tt H5Oget\_info3()} family of API calls has been added to the library which only
+return data model information via a new {\tt H5O\_info2\_t} struct. This
+struct also returns {\tt H5O\_token\_t} tokens in place of {\tt haddr\_t}
+addresses.
 
-This feature is under development and this section will be updated when the feature is complete.
+\begin{lstlisting}
+  H5Oget_info3(hid_t loc_id, H5O_info2_t *oinfo, unsigned fields)
 
-\subsubsection{Optional: ${\tt H5Ovisit[1|2]()} \rightarrow {\tt H5Ovisit3()}$}
+  herr_t H5Oget_info_by_name3(hid_t loc_id, const char *name, H5O_info2_t *oinfo, unsigned fields, hid_t lapl_id)
 
-\thgfuturewarning
+  herr_t H5Oget_info_by_idx3(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, hsize_t n, H5O_info2_t *oinfo, unsigned fields, hid_t lapl_id)
+\end{lstlisting}
 
-The {\tt H5Ovisit()} family of API functions uses the {\tt H5O\_info\_t} struct in its callback function:
+\begin{lstlisting}
+typedef struct H5O_info2_t {
+    unsigned long   fileno;     /* File number that object is located in */
+    H5O_token_t     token;      /* Token representing the object        */
+    H5O_type_t      type;       /* Basic object type (group, dataset, etc.) */
+    unsigned        rc;         /* Reference count of object            */
+    time_t          atime;      /* Access time                          */
+    time_t          mtime;      /* Modification time                    */
+    time_t          ctime;      /* Change time                          */
+    time_t          btime;      /* Birth time                           */
+    hsize_t         num_attrs;  /* # of attributes attached to object   */
+} H5O_info2_t;
+\end{lstlisting}
 
-\quad \quad {\tt typedef herr\_t (*H5O\_iterate\_t)(hid\_t obj, const char *name, const H5O\_info\_t *info, void *op\_data) }
+To return the native file format information, {\tt H5Oget\_native\_info()} calls
+have been added which can return such data separate from the data model data.
 
-A new callback that takes the updated, data-model-only struct will replace the old callback in new {\tt H5Ovisit3} API calls.
-Note that replacing this function is optional as it goes through the VOL's \textit{object specific} callback.
+\begin{lstlisting}
+  herr_t H5Oget_native_info(hid_t loc_id, H5O_native_info_t *oinfo, unsigned fields)
 
-As with the {\tt H5Oget\_info()} work, this feature is under development and this section will be updated when the feature is complete.
+  herr_t H5Oget_native_info_by_name(hid_t loc_id, const char *name, H5O_native_info_t *oinfo, unsigned fields, hid_t lapl_id)
+
+  herr_t H5Oget_native_info_by_idx(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, hsize_t n, H5O_native_info_t *oinfo, unsigned fields, hid_t lapl_id)
+\end{lstlisting}
+
+\begin{lstlisting}
+typedef struct H5O_native_info_t {                                               
+    H5O_hdr_info_t      hdr;            /* Object header information */          
+    /* Extra metadata storage for obj & attributes */                            
+    struct {                                                                     
+        H5_ih_info_t   obj;             /* v1/v2 B-tree & local/fractal heap for groups, B-tree for chunked datasets */
+        H5_ih_info_t   attr;            /* v2 B-tree & heap for attributes */    
+    } meta_size;                                                                 
+} H5O_native_info_t;
+\end{lstlisting}
+
+\subsubsection{${\tt H5Ovisit[1|2]()} \rightarrow {\tt H5Ovisit3()}$}
+
+The callback used in the {\tt H5Ovisit()} family of API calls took an {\tt H5O\_info\_t}
+struct parameter. As in {\tt H5Oget\_info()}, this both commingled data model and
+native file format information and also used native HDF5 file addresses.
+
+New {\tt H5Ovisit3()} API calls have been created which use the token-based,
+data-model-only {\tt H5O\_info\_t} struct in the callback.
+
+\begin{lstlisting}
+  herr_t H5Ovisit3(hid_t obj_id, H5_index_t idx_type, H5_iter_order_t order, H5O_iterate2_t op, void *op_data, unsigned fields)
+
+  herr_t H5Ovisit_by_name3(hid_t loc_id, const char *obj_name, H5_index_t idx_type, H5_iter_order_t order, H5O_iterate2_t op, void *op_data, unsigned fields, hid_t lapl_id)
+\end{lstlisting}
+
+\begin{lstlisting}
+typedef herr_t (*H5O_iterate2_t)(hid_t obj, const char *name, const H5O_info2_t *info, void *op_data)
+\end{lstlisting}
+
+\subsubsection{${\tt H5Lget\_info()} \rightarrow {\tt H5Lget\_info2()}$}
+
+The {\tt H5Lget\_info()} API calls were updated to use tokens instead
+of addresses in the {\tt H5L\_info\_t} struct.
+
+\begin{lstlisting}
+  herr_t H5Lget_info2(hid_t loc_id, const char *name, H5L_info2_t *linfo /*out*/, hid_t lapl_id)
+
+  herr_t H5Lget_info_by_idx2(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, hsize_t n, H5L_info2_t *linfo /*out*/, hid_t lapl_id)
+\end{lstlisting}
+
+\begin{lstlisting}
+typedef struct {                                                                 
+    H5L_type_t          type;           /* Type of link                   */     
+    hbool_t             corder_valid;   /* Indicate if creation order is valid */
+    int64_t             corder;         /* Creation order                 */     
+    H5T_cset_t          cset;           /* Character set of link name     */     
+    union {                                                                      
+        H5O_token_t     token;          /* Token of location that hard link points to */
+        size_t          val_size;       /* Size of a soft link or UD link value */
+    } u;                                                                         
+} H5L_info2_t;
+\end{lstlisting}
+
+\subsubsection{${\tt H5Literate()}$ and ${\tt H5Lvisit()}\rightarrow {\tt H5Literte2()}$ and ${\tt H5Lvisit2()}$}
+
+The callback used in these API calls used the old {\tt H5L\_info\_t} struct, which
+used addresses instead of tokens. These callbacks were versioned in the C library
+and now take modified {\tt H5L\_iterate2\_t} callbacks which use the new token-based
+info structs.
+
+\begin{lstlisting}
+  herr_t H5Literate2(hid_t grp_id, H5_index_t idx_type, H5_iter_order_t order, hsize_t *idx, H5L_iterate2_t op, void *op_data)
+
+  herr_t H5Literate_by_name2(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, hsize_t *idx, H5L_iterate2_t op, void *op_data, hid_t lapl_id)
+
+  herr_t H5Lvisit2(hid_t grp_id, H5_index_t idx_type, H5_iter_order_t order, H5L_iterate2_t op, void *op_data)
+
+  herr_t H5Lvisit_by_name2(hid_t loc_id, const char *group_name, H5_index_t idx_type, H5_iter_order_t order, H5L_iterate2_t op, void *op_data, hid_t lapl_id)
+\end{lstlisting}
+
+\begin{lstlisting}
+typedef herr_t (*H5L_iterate2_t)(hid_t group, const char *name, const H5L_info2_t *info, void *op_data); 
+\end{lstlisting}
+
+\subsubsection{${\tt H5Oopen\_by\_addr()} \rightarrow {\tt H5Oopen\_by\_token()}$}
+
+The new {\tt H5Oopen\_by\_token()} API call can be used to open objects by the tokens that are returned by the various "get info", et al. API calls.
+
+\begin{lstlisting}
+  hid_t H5Oopen_by_token(hid_t loc_id, H5O_token_t token)
+\end{lstlisting}
 
@@
 
+\section{Language Wrappers}
+
+Due to the parameter type and callback changes that were required in the C
+library API regarding the update from {\tt haddr\_t} addresses to
+{\tt H5O\_object\_t} tokens and the difficulty in versioning the wrapper
+APIs, it was decided to update all of the wrappers to use tokens instead
+of addresses. This will allow the language wrappers to make use of the VOL,
+but at the expense of backward compatibility.
+
+Information on the C API changes can be found above.
+
+Affected API calls, by language:
+
+\subsection{C++}
+
+\begin{itemize}
+    \item The {\tt visit\_operator\_t} callback now uses a {\tt H5O\_info2\_t} parameter instead of {\tt H5O\_info(1)\_t} so the callback can be passed to {\tt H5Ovisit3()} internally.
+This affects the H5Object::visit() method.
+    \item The {\tt H5Location::getObjinfo()} methods now take {\tt H5O\_info2\_t} parameters.
+    \item The {\tt H5Location::getLinkInfo()} methods now return {\tt H5L\_info2\_t} structs.
+    \item {\tt H5File::isHdf5} uses {\tt H5Fis\_accessible()}, though it always passes H5P\_DEFAULT as the fapl.
+It will only work with arbitrary VOL connectors if the default VOL connector is changed via the environment variable.
+\end{itemize}
+
+The C++ wrappers to not allow opening HDF5 file objects by address or token.
+
+The public H5VL API calls found in {\tt H5VLpublic.h} were NOT added to
+the C++ API.
+
+\subsection{Fortran}
+
+As in the C API, these API calls had their structs updated to the token version so
+the {\tt h5o\_info\_t}, etc. structs no longer contain native file format information
+and the callbacks will need to match the non-deprecated, token-enabled versions.
+
+\begin{itemize}
+    \item h5lget\_info\_f
+    \item h5lget\_info\_by\_idx\_f
+    \item h5literate\_f
+    \item h5literate\_by\_name\_f
+    \item h5oget\_info\_f
+    \item h5oget\_info\_by\_idx\_f
+    \item h5oget\_info\_by\_name\_f
+    \item h5oopen\_by\_token\_f
+    \item h5ovisit\_f
+    \item h5ovisit\_by\_name\_f
+\end{itemize}
+
+Additionally, {\tt h5fis\_hdf5\_f} was updated to use {\tt H5Fis\_accessible}
+internally, though with the same caveat as the C++ implentation: the default
+fapl is alwys passed in so arbitrary VOL connectors will only work if the
+default VOL connector is changed via the environment variable.
+
+The public H5VL API calls found in {\tt H5VLpublic.h} were also added to
+the Fortran wrappers.
+
+\subsection{Java/JNI}
+
+\begin{itemize}
+    \item {\tt H5Fis\_hdf5} Will fail when the library is built without deprecated symbols.
+    \item {\tt H5Fis\_accessible} is available and takes a fapl, allowing it to work with arbitrary VOL connectors.
+    \item The {\tt H5(O|L)get\_info}, {\tt H5(O|L)visit}, and {\tt H5Literate} calls were updated as in the C library.
+    \item {\tt H5Oget\_native\_info\_by\_name} et al. were added and they work as in the C library (e.g.: essentially native VOL connector only).
+    \item {\tt H5Oopen\_by\_addr} was replaced with {\tt H5Oopen\_by\_token}.
+    \item The public API calls in {\tt H5VLpublic.h} were added to the JNI.
+\end{itemize}
+
 \section{Using VOL Connectors With The HDF5 Command-Line Tools}
@@
 \section{Compatibility}
-\subsection{Introspection / Feature Flags}
-\thgfuturewarning
-
-Some VOL connectors will not implement all the functionality available in the HDF5 library, especially in the early stages of development.
-Unfortunately, there is currently no easy way to determine if a VOL connector implements particular API calls or groups of calls.
-
-We are working on an introspection mechanism, possibly involving a set of feature or capabilities flags and will have that available in a future release.
 
@@
     \hline
+    H5Lget\_info1 (deprecated) \\
+    H5Lget\_info\_by\_idx1 (deprecated) \\
+    H5Literate1 (deprecated) \\
+    H5Literate\_by\_name1 (deprecated) \\
+    H5Lvisit1 (deprecated) \\
+    H5Lvisit\_by\_name1 (deprecated) \\
+    \hline
     H5Oare\_mdc\_flushes\_disabled \\
@@
     H5Oget\_info\_by\_idx1 (deprecated) \\
-    H5Oget\_info\_by\_idx2 \\
+    H5Oget\_info\_by\_idx2 (deprecated)\\
     H5Oget\_info\_by\_name1 (deprecated) \\
-    H5Oget\_info\_by\_name2 \\
+    H5Oget\_info\_by\_name2 (deprecated)\\
     H5Oget\_info1 (deprecated) \\
-    H5Oget\_info2 \\
+    H5Oget\_info2 (deprecated) \\
+    H5Oopen\_by\_addr (deprecated) \\
     H5Oset\_comment \\
     H5Oset\_comment\_by\_name \\
+    H5Ovisit1 (deprecated) \\
+    H5Ovisit\_by\_name1 (deprecated) \\
+    H5Ovisit2 (deprecated) \\
+    H5Ovisit\_by\_name2 (deprecated) \\
     \hline

### 2020-02-26 RFCs/HDF5/VOL/connector_author_guide/connector_interface.tex
Updaed the VOL docs to reflect pending H5Dget_offset() changes.
Former-commit-id: 009dfbff6fdd6976182c1f57ebadfbbe7c7e57e6

@@
     H5VL_DATASET_GET_DCPL,                  /* creation property list              */
-    H5VL_DATASET_GET_OFFSET,                /* offset                              */
     H5VL_DATASET_GET_SPACE,                 /* dataspace                           */
@@
 \end{lstlisting}
-
-Note that \texttt{H5VL\_DATASET\_GET\_OFFSET} (used in \texttt{H5Dget\_offset()}) retains
-the \texttt{haddr\_t} type and was not updated to use the \texttt{H5O\_token\_t}
-type. This enum value and \texttt{H5Dget\_offset()} may be deprecated in a future
-version of the HDF5 and replaced with a token-based equivalent.
 

### 2020-04-17 RFCs/HDF5/VOL/connector_author_guide/new_api_calls.tex

@@
 New API routines have been added to the HDF5 library to manage VOL connectors.
-This section details each new API call and explains their intended usage.
+This section details each new API call and explains its intended usage.
 Additionally, a set of API calls that map directly to the VOL callbacks themselves have been added to aid in the development of passthrough connectors which can be stacked and/or split.
@@
 limited to VOL connector authors).
-
-\subsubsection{H5VLregister\_connector}
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-hid_t H5VLregister_connector(const H5VL_class_t *cls, hid_t vipl_id);
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  {\tt cls} & (IN): A pointer to the connector structure to register.\\
-  {\tt vipl\_id} & (IN): An ID for a VOL initialization property list (vipl).\\
-\end{tabular}
-\end{mdframed}
-
-Registers a user-defined VOL connector with the HDF5 library and returns an identifier for that connector (\texttt{H5I\_INVALID\_HID} on errors).
-This function is used when the application has direct access to the connector it wants to use and is able to obtain a pointer for the connector structure to pass to the HDF5 library.
-\bigskip
 
@@
 
-\subsubsection{H5VLis\_connector\_registered}
+\subsubsection{H5VLis\_connector\_registered\_by\_name}
 \begin{mdframed}[style=bgbox]
@@
 \begin{lstlisting}
-htri_t H5VLis_connector_registered(const char *name);
+htri_t H5VLis_connector_registered_by_name(const char *name);
 \end{lstlisting}
@@
 \end{mdframed}
-Checks if a VOL connector is registered with the library given the connector name and returns TRUE/FALSE on success, otherwise it returns a negative value.\bigskip
+Checks if a VOL connector is registered with the library given the connector name and returns TRUE/FALSE on success, otherwise it returns a negative value.
+\bigskip
+
+\subsubsection{H5VLis\_connector\_registered\_by\_value}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+htri_t H5VLis_connector_registered_by_value(H5VL_class_value_t connector_value);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt value} & (IN): The connector value to check for.\\
+\end{tabular}
+\end{mdframed}
+Checks if a VOL connector is registered with the library given the connector value and returns TRUE/FALSE on success, otherwise it returns a negative value.
+\bigskip
 
@@
 \begin{lstlisting}
-hid_t H5VLget_connector_id(const char *name);
+hid_t H5VLget_connector_id(hid_t obj_id);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt id} & (IN): An ID for an HDF5 VOL object.\\
+\end{tabular}
+\end{mdframed}
+Given a VOL object such as a dataset or an attribute, this function returns an identifier for its associated connector.
+If the ID is not a VOL object (such as a dataspace or uncommitted datatype), \texttt{H5I\_INVALID\_HID} is returned.
+The identifier must be released with a call to {\tt H5VLclose()}.
+\bigskip
+
+\subsubsection{H5VLget\_connector\_id\_by\_name}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+hid_t H5VLget_connector_id_by_name(const char *name);
 \end{lstlisting}
@@
 Given a connector name that is registered with the library, this function returns an identifier for the connector.
-If the connector is not registered with the library, a negative value is returned.
-The identifier must be released with a call to {\tt H5VLclose()}.\bigskip
+If the connector is not registered with the library, \texttt{H5I\_INVALID\_HID} is returned.
+The identifier must be released with a call to {\tt H5VLclose()}.
+\bigskip
+
+\subsubsection{H5VLget\_connector\_id\_by\_value}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+hid_t H5VLget_connector_id_by_value(H5VL_class_value_t connector_value);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt value} & (IN): The connector value to check for.\\
+\end{tabular}
+\end{mdframed}
+Given a connector value that is registered with the library, this function returns an identifier for the connector.
+If the connector is not registered with the library, \texttt{H5I\_INVALID\_HID} is returned.
+The identifier must be released with a call to {\tt H5VLclose()}.
+\bigskip
 
@@
 \end{lstlisting}
-
 \textbf{Arguments:}\\
@@
 \end{mdframed}
-Retrieves the name of a VOL connector given an object identifier that was created/opened with it. On success, the name length is returned.\bigskip
+Retrieves the name of a VOL connector given an object identifier that was created/opened with it. On success, the name length is returned.
+\bigskip
 
@@
 \end{mdframed}
-Shuts down access to the connector that the identifier points to and release resources associated with it.\bigskip
+Shuts down access to the connector that the identifier points to and release resources associated with it.
+\bigskip
 
@@
 Unregisters a connector from the library and return a positive value on success otherwise return a negative value.
-The native VOL connector cannot be unregistered (this will return a negative herr\_t value).\bigskip
+The native VOL connector cannot be unregistered (this will return a negative herr\_t value).
+\bigskip
 
@@
 This functionality is intended for VOL connector authors and includes helper
-functions that are useful for writing connectors. Callback equivalent
-functions can be found in {\tt H5VLconnector\_passthru.h}. A list of these
-functions is included as an appendix to this document.
+functions that are useful for writing connectors.
+
+\subsubsection{H5VLregister\_connector}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+hid_t H5VLregister_connector(const H5VL_class_t *cls, hid_t vipl_id);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt cls} & (IN): A pointer to the connector structure to register.\\
+  {\tt vipl\_id} & (IN): An ID for a VOL initialization property list (vipl).\\
+\end{tabular}
+\end{mdframed}
+Registers a user-defined VOL connector with the HDF5 library and returns an identifier for that connector (\texttt{H5I\_INVALID\_HID} on errors).
+This function is used when the application has direct access to the connector it wants to use and is able to obtain a pointer for the connector structure to pass to the HDF5 library.
+\bigskip
 
@@
 \begin{lstlisting}
-  void *H5VLget_object(hid_t obj_id); 
+  void *H5VLobject(hid_t obj_id); 
 \end{lstlisting}
-
 \textbf{Arguments:}\\
@@
 \end{mdframed}
-Retrieves a pointer to the VOL object from an HDF5 file or object identifier.\bigskip
+Retrieves a pointer to the VOL object from an HDF5 file or object identifier.
+\bigskip
 
@@
 Returns a copy of the {\tt dtype\_id} parameter but with the location set to
-be in the file. Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.\bigskip
+be in the file. Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.
+\bigskip
 
-\subsubsection{H5VLpeek\_connector}
+\subsubsection{H5VLpeek\_connector\_by\_name}
 \begin{mdframed}[style=bgbox]
@@
 \begin{lstlisting}
-  hid_t H5VLpeek_connector_id(const char *name); 
+  hid_t H5VLpeek_connector_id_by_name(const char *name); 
 \end{lstlisting}
-
 \textbf{Arguments:}\\
@@
 \end{mdframed}
-Retrieves the ID for a registered VOL connector. This is done without duplicating
+Retrieves the ID for a registered VOL connector based on a connector name.
+This is done without duplicating
 the ID and transferring ownership to the caller (as it normally the case in the
@@
 This is intended for use by VOL connectors to find their own ID.
+Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.
+\bigskip
 
-Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.\bigskip
+\subsubsection{H5VLpeek\_connector\_by\_value}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  hid_t H5VLpeek_connector_id_by_value(H5VL_class_value_t value); 
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt value} & (IN): value of the connector to query.\\
+\end{tabular}
+\end{mdframed}
+Retrieves the ID for a registered VOL connector based on a connector value.
+This is done without duplicating
+the ID and transferring ownership to the caller (as it normally the case in the
+HDF5 library). The ID returned from this operation should not be closed.
+This is intended for use by VOL connectors to find their own ID.
+Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.
+\bigskip
+
+\subsection{H5VLconnector\_passthru.h}
+
+This functionality is intended for VOL connector authors who are writing
+pass-through connectors and includes helper functions that are useful for
+writing such connectors. Callback equivalent functions can be found in this
+header as well. A list of these functions is included as an appendix to this
+document.
+
+\subsubsection{H5VLcmp\_connector\_cls}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  herr_t H5VLcmp_connector_cls(int *cmp, hid_t connector_id1, hid_t connector_id2);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt cmp} & (OUT): a value like strcmp.\\
+ {\tt connector\_id1} & (IN): the ID of the first connector to compare.\\
+ {\tt connector\_id2} & (IN): the ID of the second connector to compare.\\
+\end{tabular}
+\end{mdframed}
+Compares two connectors (given by the connector IDs) to see if they refer to the
+same connector underneath.
+Returns a positive value on success and a negative value on errors.
+\bigskip
+
+\subsubsection{H5VLwrap\_register}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  hid_t H5VLwrap_register(void *obj, H5I_type_t type);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt cmp} & (IN): an object to wrap.\\
+ {\tt type} & (IN): the type of the object (see below).\\
+\end{tabular}
+\end{mdframed}
+Wrap an internal object with a "wrap context" and register and return an
+hid\_t for the resulting object. This routine is mainly targeted toward wrapping
+objects for iteration routine callbacks (i.e. the callbacks from H5Aiterate*,
+H5Literate* / H5Lvisit*, and H5Ovisit*). The type must be a VOL-managed object
+class (H5I\_FILE, H5I\_GROUP, H5I\_DATATYPE, H5I\_DATASET, H5I\_MAP, or H5I\_ATTR).
+Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.
+\bigskip
+
+\subsubsection{H5VLretrieve\_lib\_state}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  herr_t H5VLretrieve_lib_state(void **state);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt state} & (OUT): the library state.\\
+\end{tabular}
+\end{mdframed}
+Retrieves a copy of the internal state of the HDF5 library,
+so that it can be restored later.
+Returns a positive value on success and a negative value on errors.
+\bigskip
+
+\subsubsection{H5VLrestore\_lib\_state}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  herr_t H5VLrestore_lib_state(const void *state);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt state} & (IN): the library state.\\
+\end{tabular}
+\end{mdframed}
+Restores the internal state of the HDF5 library.
+Returns a positive value on success and a negative value on errors.
+\bigskip
+
+\subsubsection{H5VLreset\_lib\_state}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  herr_t H5VLreset_lib_state(void);
+\end{lstlisting}
+\end{mdframed}
+Resets the internal state of the HDF5 library, undoing the
+affects of H5VLrestore\_lib\_state.
+This routine must be called as a "pair" with
+{\tt H5VLrestore\_lib\_state}.  It can be called before, after, or
+independently of {\tt H5VLfree\_lib\_state}.
+Returns a positive value on success and a negative value on errors.
+\bigskip
+
+\subsubsection{H5VLfree\_lib\_state}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  herr_t H5VLfree_lib_state(const void *state);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+ {\tt state} & (IN): the library state.\\
+\end{tabular}
+\end{mdframed}
+Free a retrieved library state.
+Returns a positive value on success and a negative value on errors.
+\bigskip
 

### 2020-04-17 RFCs/HDF5/VOL/user_guide/body.tex

@@
     H5Dget\_num\_chunks \\
+    H5Dget\_offset \\
     H5Dread\_chunk H5Dwrite\_chunk \\

### 2020-04-17 RFCs/HDF5/VOL/vol_internals/body.tex

--- 2014-09-23 RFCs/HDF5/VOL/developer_guide/body.tex
@@
 library that intercepts all API calls that could potentially access
-objects in an HDF5 container and forwards those calls to plugin
-''object drivers''. The plugins could store the objects in variety of
-ways. A plugin could, for example, have objects be distributed
-remotely over different platforms, provide a raw mapping of the model
-to the file system, or even store the data in other file formats (like
+objects in an HDF5 container and forwards those calls to VOL
+''object drivers'' called connectors, which are usually implemented as
+dynamically-loaded plugins. These connectors could store the objects in variety of
+ways. A connector could, for example, add the objects
+to an object store, push the objects to a remote server via REST, or even store the data in other file formats (like
 native netCDF or HDF4 format). The user still gets the same data model
-where access is done to a single HDF5 “container”; however the plugin
-object driver translates from what the user sees to how the data is
+where access is done to a single HDF5 “container”; however the connector
+translates from what the user sees to how the data is
 actually stored. Having this abstraction layer maintains the object
 model of HDF5 and would allow HDF5 developers or users to write their
-own plugins for accessing HDF5 data.
+own connectorss for accessing HDF5 data.
 
 This guide is for HDF5 library developers responsible for maintaining the HDF5 C library.
-It details the changes made to the library to implement the VOL, and the necessary requirements for adding new features to the library to work with the Virtual object layer.
+It details the changes made to the library to implement the VOL, and the necessary requirements for adding new features to the library to work with the virtual object layer.
 Readers of this document are expected to be quite familiar with the VOL high level architecture presented in ~\cite{vol:rfc} and the VOL user's guide\cite{vol:ug}.
@@
 \section{New VOL Code}
-The VOL captures all API routines that could potentially access the HDF5 file and routes them through the VOL intermediate layer which in-turn calls the plugin callback that implements the API function.
+The VOL captures all API routines that could potentially access the HDF5 file and routes them through the VOL intermediate layer which, in turn, calls the connector callback that implements the API function.
 
-The VOL code additions have been added to the library similar to any new interface introduced.
-The library's acronym to all VOL related variables and functions is {\tt H5VL}.
+The VOL code additions have been added to the library like any newly introduced interface.
+The package prefix for all VOL-related variables and functions is {\tt H5VL}.
 The public VOL definitions including the VOL class and callbacks are in {\tt H5VLpublic.h}.
@@
 \section{The VOL Property in the File Access Property List}
-A new property is added for file access property lists (FAPL) that indicates what VOL plugin should be used when accessing a file with the given FAPL.
-The property {\tt H5F\_ACS\_VOL\_ID\_NAME} maps to the plugin identifier to use.
-If the plugin selected requires information to be passed down from the application, another property is used, {\tt H5F\_ACS\_VOL\_INFO\_NAME}, which translates to a {\tt void} pointer to the information needed by specific the VOL plugin.
+A new property is added for file access property lists (FAPL) that indicates what VOL connector should be used when accessing a file with the given FAPL.
+The property {\tt H5F\_ACS\_VOL\_ID\_NAME} maps to the connector identifier to use.
+If the connector selected requires information to be passed down from the application, another property is used, {\tt H5F\_ACS\_VOL\_INFO\_NAME}, which translates to a {\tt void} pointer to the information needed by specific the VOL connector.
 The property setting are analogous to the Virtual File Driver properties for selecting and using file drivers with the native HDF5 library.
-For more information on selecting VOL plugins refer to the VOL user guide.
+For more information on selecting VOL connectors refer to the VOL user guide.
 
-The default settings for the FAPL properties for the plugin identifier is the global identifier for the native plugin.
-Since the native plugin does not require any extra information from the application, the info property is set to {\tt NULL} by default.
-The global identifier for the native plugin is initialized when the HDF5 library is initialized by registering a global identifier with the native plugin structure.
+The default settings for the FAPL properties for the connector identifier is the global identifier for the native connector.
+Since the native connector does not require any extra information from the application, the info property is set to {\tt NULL} by default.
+The global identifier for the native connector is initialized when the HDF5 library is initialized by registering a global identifier with the native connector structure.
 
-Whenever a plugin is set to be used with a FAPL or when copying a FAPL, the library calls:
+Whenever a connector is set to be used with a FAPL or when copying a FAPL, the library calls:
 \begin{lstlisting}
@@
 \end{lstlisting}
-which increments the reference count on the plugin, calls the plugin specific {\tt info\_copy} callback if the {\tt vol\_info} parameter is not {\tt NULL}, and sets the VOL properties for the VOL identifier and info that are described above.
+which increments the reference count on the connector, calls the connector specific {\tt info\_copy} callback if the {\tt vol\_info} parameter is not {\tt NULL}, and sets the VOL properties for the VOL identifier and info that are described above.
 
@@
 \end{lstlisting}
-which calls the {\tt info\_free} callback of the VOL plugin with the info if {\tt vol\_info} is not {\tt NULL}, and decrements the reference count on the VOL identifier.
+which calls the {\tt info\_free} callback of the VOL connector with the info if {\tt vol\_info} is not {\tt NULL}, and decrements the reference count on the VOL identifier.
 
@@
 
-where {\tt H5VL\_file\_create()} is a private function defined in the intermediate VOL layer that calls the the create callback in the file class of the VOL plugin selected in the file access property list.
+where {\tt H5VL\_file\_create()} is a private function defined in the intermediate VOL layer that calls the the create callback in the file class of the VOL connector selected in the file access property list.
 
@@
 The first being that the private structures that the identifiers point to now are specific to the native HDF5 implementation.
-Other plugins will have different structures that they implement.
+Other connectors will have different structures that they implement.
 Thus at the API and VOL intermediate layer, those objects are accessible only through a {\tt void} pointer with an unknown structure type to cast it to.
-The second reason is that the internal structures ({\tt H5F\_t, H5D\_t, H5G\_t,  etc ...}) do not contain a pointer to the plugin class used to create the object.
+The second reason is that the internal structures ({\tt H5F\_t, H5D\_t, H5G\_t,  etc ...}) do not contain a pointer to the connector class used to create the object.
 This is problematic because subsequent access on those object through the identifiers would not allow us to determine the VOL class to forward the call to.
@@
 typedef struct H5VL_object_t {
-    void               *vol_obj;        /* pointer to object created by plugin */
+    void               *vol_obj;        /* pointer to object created by connector */
     H5VL_t             *vol_info;       /* pointer to VOL info struct */
@@
 
-where {\tt vol\_obj} is a pointer to the plugin created object.
-In the native plugin this would be a pointer to the private structures of that object ({\tt H5F\_t, H5D\_t, H5G\_t,  etc ...}).
-The {\tt vol\_info} contains the information about the plugin that created the object and is defined as:
+where {\tt vol\_obj} is a pointer to the connector created object.
+In the native connector this would be a pointer to the private structures of that object ({\tt H5F\_t, H5D\_t, H5G\_t,  etc ...}).
+The {\tt vol\_info} contains the information about the connector that created the object and is defined as:
 
@@
 typedef struct H5VL_t {
-    const H5VL_class_t *vol_cls;        /* constant plugin class info */
+    const H5VL_class_t *vol_cls;        /* constant connector class info */
     int                 nrefs;          /* number of references by objects using this struct */
@@
 
-{\tt vol\_cls} is a pointer to the plugin class.
+{\tt vol\_cls} is a pointer to the connector class.
 {\tt nrefs} indicates how many object currently point to the {\tt H5VL\_t} structure.
-{\tt vol\_id} is the global identifier for the VOL plugin used.
+{\tt vol\_id} is the global identifier for the VOL connector used.
 Usually this structure is created in {\tt H5Fcreate()} or {\tt H5Fopen()} with {\tt nrefs = 1}, then {\tt nrefs} is incremented by 1 on any subsequent object creation that stored a copy of that pointer and decremented when the object is closed.
@@
 
-As a convenience, a new private routines is provided to create the wrapper object for the underlying plugin specific object pointer, manage the VOL info structure, and register an identifier to be returned to the user:
+As a convenience, a new private routines is provided to create the wrapper object for the underlying connector specific object pointer, manage the VOL info structure, and register an identifier to be returned to the user:
 
 \begin{lstlisting}
-H5VL_register_id(H5I_type_t type, void *object, H5VL_t *vol_plugin, hbool_t app_ref);
+H5VL_register_id(H5I_type_t type, void *object, H5VL_t *vol_connector, hbool_t app_ref);
 \end{lstlisting}
@@
 We replaced all usage of {\tt H5I\_object() and H5I\_object\_verify()} in the library as appropriate for the above listed object types.
-Developers should use the {\tt H5VL} functions above in the native library and tests when expecting to get back the plugin specific objects.
+Developers should use the {\tt H5VL} functions above in the native library and tests when expecting to get back the connector specific objects.
 
-As for {\tt H5I\_iterate()}, we update the implementation of this function internally to unwrap the object being iterated over if it is a file, dataset, group, attribute, or named datatype, and return the plugin specific object to the iterate callback.
+As for {\tt H5I\_iterate()}, we update the implementation of this function internally to unwrap the object being iterated over if it is a file, dataset, group, attribute, or named datatype, and return the connector specific object to the iterate callback.
 We saw this as a better approach than requiring a change in all the iteration callbacks to check for the object type and unwrap it accordingly.
@@
 
-\section{Native Plugin Implementation}
-The native HDF5 plugin implements the VOL callbacks with the native HDF5 file format.
+\section{Native Connector Implementation}
+The native HDF5 connector implements the VOL callbacks with the native HDF5 file format.
 This is basically all what the library currently does when implementing HDF5 features.
-The native VOL plugin is implemented in {\tt H5VLnative.c}.
+The native VOL connector is implemented in {\tt H5VLnative.c}.
 The callbacks of the VOL class are implemented here similarly to how the API routines were mapped directly to the internal HDF5 implementation before the VOL was introduced.
@@
 There are places in the library where we need to register an identifier to pass directly to the application (for example, creating a group identifier and calling the user defined link iteration callback).
-To do that, we need to create the high level object wrapper and attach the native plugin information before registering that ID.
+To do that, we need to create the high level object wrapper and attach the native connector information before registering that ID.
 This can be done by calling this private and native specific routine:
@@
 At that point the datatype should already by open and loaded into memory space for those operations to work.
-We chose not to handle those operations through the VOL even if that datatype is committed, to relieve VOL plugin developers from implementing a large set of datatype routines that is already available in the HDF5 library and is likely to be the same across all VOL plugins.
+We chose not to handle those operations through the VOL even if that datatype is committed, to relieve VOL connector developers from implementing a large set of datatype routines that is already available in the HDF5 library and is likely to be the same across all VOL connectors.
 
@@
 The higher level datatype APIs expect that the identifier for dataypes (named and transient) to map to the private {\tt H5T\_t} structure.
-However; as we explained earlier in this document, the object that we get back from the VOL plugins when committing a datatype to the file is a {\tt void} pointer that the library just needs to keep track.
-For the native plugin we do know that the pointer is actually pointing to the internal {\tt H5T\_t} structure for the name datatype, but we can not make that assumption for other plugins that will return a pointer to their own implementation of named datatypes.
-Furthermore we need to wrap whatever object returned from the plugin when creating/committing a named datatype with the higher level object structure that contains the VOL plugin information used for creating the datatype.
+However; as we explained earlier in this document, the object that we get back from the VOL connectors when committing a datatype to the file is a {\tt void} pointer that the library just needs to keep track.
+For the native connector we do know that the pointer is actually pointing to the internal {\tt H5T\_t} structure for the name datatype, but we can not make that assumption for other connectors that will return a pointer to their own implementation of named datatypes.
+Furthermore we need to wrap whatever object returned from the connector when creating/committing a named datatype with the higher level object structure that contains the VOL connector information used for creating the datatype.
 This mismatch between what the VOL expects and what the {\tt H5T} API functions expect will require us to do some special handling for committing and opening named datatypes:
@@
 However at this point we do not have the {\tt H5T\_t} structure for that datatype.
-For this reason we require all VOL plugins that support named datatypes to store a serialized copy of the HDF5 datatype somewhere in the underlying container when committing a named datatype.
-After opening the datatype through the VOL, we ask the VOL plugin to return the serialized form of the datatype which we can call {\tt H5T\_decode()} on to create the private {H5T\_t} structure which is a transient form of the datatype.
+For this reason we require all VOL connectors that support named datatypes to store a serialized copy of the HDF5 datatype somewhere in the underlying container when committing a named datatype.
+After opening the datatype through the VOL, we ask the VOL connector to return the serialized form of the datatype which we can call {\tt H5T\_decode()} on to create the private {H5T\_t} structure which is a transient form of the datatype.
 Then we store the object created from the open operation in the new {\tt vol\_obj} field of the {\tt H5T\_t} structure we just created and atomize it to return to the user.
@@
 HDF5 datatypes proved to be quite a challenge with the VOL due to the two states that they exist in unlike any other HDF5 object.
-However we believe the design decisions we made and explained above are a compromise to ease the work for plugin developers and HDF5 library maintainers at the same time.
+However we believe the design decisions we made and explained above are a compromise to ease the work for connector developers and HDF5 library maintainers at the same time.
 
-%\section{Dynamically Loaded VOL Plugins}
+%\section{Dynamically Loaded VOL Connectors}
 %The VOL supports loading third party VOL plugins that have been installed on a system as shared libraries.
@@
 \item Adding a new VOL class for the new feature.
-This usually means that a new object type is added to the HDF5 library or a new service is introduced that is expected to be general in the sense that most plugins should be implemented.
+This usually means that a new object type is added to the HDF5 library or a new service is introduced that is expected to be general in the sense that most connectors should be implemented.
 For example, consider the case when a new HDF5 object is added to the library that allows users to create and use a KV store in the HDF5 container.
-Adding a new class means that all existing plugins have to be modified to cope with the change in the VOL public structure.
+Adding a new class means that all existing connectors have to be modified to cope with the change in the VOL public structure.
 Changing the VOL public structure should be done only in major HDF5 releases, and not in maintenance releases.
@@
 This is done when a new API function is added to a particular class of operations (Files, Datasets, Groups, etc...) and is quite important that it can't be ``hidden'' in the {\tt specific} callback of that class.
-This change in the public VOL class also requires all existing plugins to be updated and should be done in major releases only.
+This change in the public VOL class also requires all existing connectors to be updated and should be done in major releases only.
 
 \item Adding a new operation type to the {\tt get, specific} or {\tt optional} callbacks of a sub-class in the VOL public structure.
-When a new operation type to retrieve data from a particular object or to execute some new operation on that object, whether that operation is general among all plugins or plugin specific, adding a new type to the {\tt enum} of types for the three callbacks present in every sub-class should be enough to support the new operation.
+When a new operation type to retrieve data from a particular object or to execute some new operation on that object, whether that operation is general among all connectors or connector specific, adding a new type to the {\tt enum} of types for the three callbacks present in every sub-class should be enough to support the new operation.
 For more information on how this works, please consult with the VOL user guide.
@@
 \item Adding a new operation type to the {\tt optional} callback in the VOL public class for services.
-New HDF5 functionality that is added specifically for certain plugins and would not make sense to promote to an actual class since it isn't general enough to be implemented by most plugins or would not be used a lot by applications should follow this option.
+New HDF5 functionality that is added specifically for certain connectors and would not make sense to promote to an actual class since it isn't general enough to be implemented by most connectors or would not be used a lot by applications should follow this option.
 

### 2021-09-30 RFCs/HDF5/VOL/user_guide/body.tex
Updates the VOL user's guide for HDF5 1.13.0

--- 2020-02-24 RFCs/HDF5/VOL/user_guide/body.tex
@@
 
-Many VOL connectors (at various stages of implementation) can be found here:
+A list of VOL connectors can be found here:
 
-\quad \quad \url{https://bitbucket.hdfgroup.org/projects/HDF5VOL}
+\url{https://portal.hdfgroup.org/display/support/Registered+VOL+Connectors}
+
+This list is incomplete and only includes the VOL connectors that have been registered with The HDF Group.
 
@@
 See the documentation in a connector's repository to determine its development status and the parties responsible for it.
-The collection also includes a VOL template that contains build scripts (Autotools and CMake) and an empty VOL connector "shell" which can be copied and used as a starting point for building new connectors.
-See the VOL Connector Author Guide for more information on this.
+
+A VOL template that contains build scripts (Autotools and CMake) and an empty VOL connector "shell" which can be copied and used as a starting point for building new connectors is located here:
+
+\url{https://github.com/HDFGroup/vol-template}
+
+This template VOL connector is for use in constructing terminal VOL connectors that do not forward calls to an underlying connector.
+The external pass-through VOL connector listed on the registered connector page can be used as a starting point for pass-through connectors.
 
@@
 
-The virtual object layer was introduced in HDF5 1.12.0, so you will need that version or later to use it.
+The virtual object layer was introduced in HDF5 1.12.0, however that version of the VOL is deprecated.
+VOL users should target HDF5 1.13.0, which is currently under development (targeted release date: late 2021).
+This release is considered "unstable" in the sense that API calls, interfaces, and the file format may change in the 1.13 release branch and we do not guarantee binary compatibility ("unstable" does NOT mean buggy).
+The next stable version of the library will be HDF5 1.14.0 which should release in 2022.
 The particular configuration of the library (serial vs parallel, thread-safe, debug vs production/release) does not matter.
@@
 When working with a debug HDF5 library, it's probably also wise to build with the "memory sanity checking" feature disabled to avoid accidentally clobbering our memory tracking infrastructure when dealing with buffers obtained from the HDF5 library.
+This feature should be disabled by default in HDF5 1.13.0.
 
@@
 \begin{lstlisting}
-  hid\_t H5VLregister\_connector\_by\_name(const char *connector\_name, hid\_t vipl\_id)
+  hid_t H5VLregister_connector_by_name(const char *connector_name, hid_t vipl_id)
 
-  hid\_t H5VLregister\_connector\_by\_value(H5VL\_class\_value\_t connector\_value, hid\_t vipl\_id)
+  hid_t H5VLregister_connector_by_value(H5VL_class_value_t connector_value, hid_t vipl_id)
 \end{lstlisting}
@@
 
-There is currently no recommended or library-inherent way to version VOL connectors.
-A {\tt version} field is included in the {\tt H5VL\_class\_t} struct which holds a connector's information and callbacks, but this is intended for use when versioning the class struct.
+The VOL connector struct provides a {\tt conn\_version} field for versioning connectors. The library developers are working on some best practices for versioning connectors.
 
@@
 These will often be in the form of {\tt H5Pset\_fapl\_<name>()}.
-For example, the DAOS VOL connector \url{https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/daos-vol} provides a {\tt H5Pset\_fapl\_daos()} API call which will take MPI parameters and make this call.
+For example, the DAOS VOL connector \url{https://github.com/HDFGroup/vol-daos} provides a {\tt H5Pset\_fapl\_daos()} API call which will take MPI parameters and make this call.
 See the connector's documentation or public header file(s) for more information.
@@
 \begin{lstlisting}
-  herr\_t H5Pset\_vol(hid\_t plist\_id, hid\_t new\_vol\_id, const void *new\_vol\_info)
+  herr_t H5Pset_vol(hid_t plist_id, hid_t new_vol_id, const void *new_vol_info)
 \end{lstlisting}
@@
 \begin{lstlisting}
-  herr\_t H5VLconnector\_str\_to\_info(const char *str, hid\_t connector\_id, void **info)
+  herr_t H5VLconnector_str_to_info(const char *str, hid_t connector_id, void **info)
 \end{lstlisting}
@@
 \begin{lstlisting}
-  herr\_t H5VLfree\_connector\_info(hid\_t connector\_id, void *vol\_info)
+  herr_t H5VLfree_connector_info(hid_t connector_id, void *vol_info)
 \end{lstlisting}
@@
 
-There is currently no simple way to determine if the VOL connector used for a file or object is the native VOL connector.
-You will have to track this in your application and not make native-only VOL calls with non-native VOL connectors.
+In HDF5 1.13.0, a way to determine support for optional calls has been added.
 
-A list of native-only connector calls is given below.
+\begin{lstlisting}
+  herr_t H5VLquery_optional(hid_t obj_id, H5VL_subclass_t subcls, int opt_type, uint64_t *flags)
+\end{lstlisting}
 
-We are working on a mechanism that will allow detecting when the VOL connector is the native VOL connector, however a good mechanism for this is complicated as some VOL connectors will be passthrough VOL connectors (or even splitters) which ultimately resolve down to the native VOL connectors.
+The call takes an object that is VOL managed (i.e.; file, group, dataset, attribute, object, committed datatype), the VOL subclass (an enum documented in H5VLpublic.h), an operation "type" (discussed below), and an out parameter for the bitwise capabilities flags (also discussed below).
+Code that needs to protect a VOL-specific API call can call the function to see if the API call is supported, which will be reported via the flags.
+Specifically, if the {\tt H5VL\_OPT\_QUERY\_SUPPORTED} bit is set, the feature is supported.
+The other flags are more useful for VOL connector authors than end users.
+
+In the case of the native VOL connector, the {\tt opt\_type} operations are documented in H5VLnative.h.
+The current list of native operations is given at the end of this document, along with a list of native-only connector calls.
 
@@
 
-The best way to use a particular VOL connector with the HDF5 tools, both command-line and GUI tools, is to specify the VOL connector using the VOL connector environment variable (HDF5\_VOL\_CONNECTOR - see above).
+The following command-line tools are VOL-aware and can be used with arbitrary VOL connectors:
 
-The HDF5 tools currently do not have an option to specify a VOL connector on the command line, though this option will be added soon.
+\begin{itemize}
+    \item {\tt (p)h5diff}
+    \item {\tt h5dump}
+    \item {\tt h5ls}
+    \item {\tt h5mkgrp}
+    \item {\tt h5repack}
+\end{itemize}
+
+The VOL connector can be set either using the {\tt HDF5\_VOL\_CONNECTOR} environment variable (see above) or via the command line.
+Each of the above tools takes command-line options to set the VOL connector by name or value and the VOL connector string, usually in the form of {\tt --vol-(name|value|info)}.
+See the individual tool's help for the options specific to that tool.
 
@@
     \hline
+    H5Dchunk\_iter \\
     H5Ddebug \\
@@
     H5Dget\_num\_chunks \\
-    H5Dread\_chunk H5Dwrite\_chunk \\
+    H5Dget\_offset \\
+    H5Dread\_chunk \\
+    H5Dwrite\_chunk \\
     \hline
@@
     H5Fget\_dset\_no\_attrs\_hint \\
-    H5Fget\_eoa H5Fget\_file\_image \\
+    H5Fget\_eoa \\
+    H5Fget\_file\_image \\
     H5Fget\_filesize \\
@@
     H5Oget\_info2 (deprecated) \\
+    H5Oget\_native\_info \\
+    H5Oget\_native\_info\_by\_idx \\
+    H5Oget\_native\_info\_by\_name \\
     H5Oopen\_by\_addr (deprecated) \\
@@
 \end{longtable}
+
+\subsection{List of Native VOL Optional Operation Values By Subclass}
+
+These values can be passed to the {\tt opt\_type} parameter of {\tt H5VLquery\_optional()}.
+
+\begin{lstlisting}
+/* H5VL_SUBCLS_ATTR */
+/* H5Aiterate (deprecated routine) */
+#define H5VL_NATIVE_ATTR_ITERATE_OLD 0
+
+/* H5VL_SUBCLS_DATASET */
+/* H5Dformat_convert (internal) */
+#define H5VL_NATIVE_DATASET_FORMAT_CONVERT          0  
+/* H5Dget_chunk_index_type */
+#define H5VL_NATIVE_DATASET_GET_CHUNK_INDEX_TYPE    1  
+/* H5Dget_chunk_storage_size */
+#define H5VL_NATIVE_DATASET_GET_CHUNK_STORAGE_SIZE  2  
+/* H5Dget_num_chunks */
+#define H5VL_NATIVE_DATASET_GET_NUM_CHUNKS          3  
+/* H5Dget_chunk_info */
+#define H5VL_NATIVE_DATASET_GET_CHUNK_INFO_BY_IDX   4  
+/* H5Dget_chunk_info_by_coord */
+#define H5VL_NATIVE_DATASET_GET_CHUNK_INFO_BY_COORD 5  
+/* H5Dchunk_read */
+#define H5VL_NATIVE_DATASET_CHUNK_READ              6  
+/* H5Dchunk_write */
+#define H5VL_NATIVE_DATASET_CHUNK_WRITE             7  
+/* H5Dvlen_get_buf_size */
+#define H5VL_NATIVE_DATASET_GET_VLEN_BUF_SIZE       8  
+/* H5Dget_offset */
+#define H5VL_NATIVE_DATASET_GET_OFFSET              9  
+/* H5Dget_offset */
+#define H5VL_NATIVE_DATASET_CHUNK_ITER              10
+
+/* H5VL_SUBCLS_FILE */
+/* H5Fclear_elink_file_cache */
+#define H5VL_NATIVE_FILE_CLEAR_ELINK_CACHE            0  
+/* H5Fget_file_image */
+#define H5VL_NATIVE_FILE_GET_FILE_IMAGE               1  
+/* H5Fget_free_sections */
+#define H5VL_NATIVE_FILE_GET_FREE_SECTIONS            2  
+/* H5Fget_freespace */
+#define H5VL_NATIVE_FILE_GET_FREE_SPACE               3  
+/* H5Fget_info1/2 */
+#define H5VL_NATIVE_FILE_GET_INFO                     4  
+/* H5Fget_mdc_config */
+#define H5VL_NATIVE_FILE_GET_MDC_CONF                 5  
+/* H5Fget_mdc_hit_rate */
+#define H5VL_NATIVE_FILE_GET_MDC_HR                   6  
+/* H5Fget_mdc_size */
+#define H5VL_NATIVE_FILE_GET_MDC_SIZE                 7  
+/* H5Fget_filesize */
+#define H5VL_NATIVE_FILE_GET_SIZE                     8  
+/* H5Fget_vfd_handle */
+#define H5VL_NATIVE_FILE_GET_VFD_HANDLE               9  
+/* H5Freset_mdc_hit_rate_stats */
+#define H5VL_NATIVE_FILE_RESET_MDC_HIT_RATE           10 
+/* H5Fset_mdc_config */
+#define H5VL_NATIVE_FILE_SET_MDC_CONFIG               11 
+/* H5Fget_metadata_read_retry_info */
+#define H5VL_NATIVE_FILE_GET_METADATA_READ_RETRY_INFO 12 
+/* H5Fstart_swmr_write */
+#define H5VL_NATIVE_FILE_START_SWMR_WRITE             13 
+/* H5Fstart_mdc_logging */
+#define H5VL_NATIVE_FILE_START_MDC_LOGGING            14 
+/* H5Fstop_mdc_logging */
+#define H5VL_NATIVE_FILE_STOP_MDC_LOGGING             15 
+/* H5Fget_mdc_logging_status */
+#define H5VL_NATIVE_FILE_GET_MDC_LOGGING_STATUS       16 
+/* H5Fformat_convert */
+#define H5VL_NATIVE_FILE_FORMAT_CONVERT               17 
+/* H5Freset_page_buffering_stats */
+#define H5VL_NATIVE_FILE_RESET_PAGE_BUFFERING_STATS   18 
+/* H5Fget_page_buffering_stats */
+#define H5VL_NATIVE_FILE_GET_PAGE_BUFFERING_STATS     19 
+/* H5Fget_mdc_image_info */
+#define H5VL_NATIVE_FILE_GET_MDC_IMAGE_INFO           20 
+/* H5Fget_eoa */
+#define H5VL_NATIVE_FILE_GET_EOA                      21 
+/* H5Fincrement_filesize */
+#define H5VL_NATIVE_FILE_INCR_FILESIZE                22 
+/* H5Fset_latest_format/libver_bounds */
+#define H5VL_NATIVE_FILE_SET_LIBVER_BOUNDS            23 
+/* H5Fget_dset_no_attrs_hint */
+#define H5VL_NATIVE_FILE_GET_MIN_DSET_OHDR_FLAG       24 
+/* H5Fset_dset_no_attrs_hint */
+#define H5VL_NATIVE_FILE_SET_MIN_DSET_OHDR_FLAG       25 
+/* H5Fget_mpi_atomicity */
+#define H5VL_NATIVE_FILE_GET_MPI_ATOMICITY 26 
+/* H5Fset_mpi_atomicity */
+#define H5VL_NATIVE_FILE_SET_MPI_ATOMICITY 27 
+/* Adjust file after open, with wrapping context */
+#define H5VL_NATIVE_FILE_POST_OPEN 28
+
+/* H5VL_SUBCLS_GROUP */
+/* HG5Giterate (deprecated routine) */
+#define H5VL_NATIVE_GROUP_ITERATE_OLD 0 
+/* HG5Gget_objinfo (deprecated routine) */
+#define H5VL_NATIVE_GROUP_GET_OBJINFO 1
+
+/* H5VL_SUBCLS_OBJECT */
+/* H5G|H5Oget_comment, H5Oget_comment_by_name */
+#define H5VL_NATIVE_OBJECT_GET_COMMENT              0 
+/* H5G|H5Oset_comment, H5Oset_comment_by_name */
+#define H5VL_NATIVE_OBJECT_SET_COMMENT              1 
+/* H5Odisable_mdc_flushes */
+#define H5VL_NATIVE_OBJECT_DISABLE_MDC_FLUSHES      2 
+/* H5Oenable_mdc_flushes */
+#define H5VL_NATIVE_OBJECT_ENABLE_MDC_FLUSHES       3 
+/* H5Oare_mdc_flushes_disabled */
+#define H5VL_NATIVE_OBJECT_ARE_MDC_FLUSHES_DISABLED 4 
+/* H5Oget_native_info(_by_idx, _by_name) */
+#define H5VL_NATIVE_OBJECT_GET_NATIVE_INFO          5 
+\end{lstlisting}

### 2021-10-01 RFCs/HDF5/VOL/connector_author_guide/connector_interface.tex

@@
     /* Overall connector fields & callbacks */
-    unsigned int version;                   /* VOL connector class struct version #     */
-    H5VL_class_value_t value;               /* Value to identify connector              */
-    const char *name;                       /* Connector name (MUST be unique!)         */
-    unsigned cap_flags;                     /* Capability flags for connector           */
-    herr_t (*initialize)(hid_t vipl_id);    /* Connector initialization callback        */
-    herr_t (*terminate)(void);              /* Connector termination callback           */
+    unsigned           version;          /**< VOL connector class struct version #     */
+    H5VL_class_value_t value;            /**< Value to identify connector              */
+    const char *       name;             /**< Connector name (MUST be unique!)         */
+    unsigned           conn_version;     /**< Version # of connector                   */
+    unsigned           cap_flags;        /**< Capability flags for connector           */
+    herr_t (*initialize)(hid_t vipl_id); /**< Connector initialization callback        */
+    herr_t (*terminate)(void);           /**< Connector termination callback           */
 
     /* VOL framework */
-    H5VL_info_class_t       info_cls;       /* VOL info fields & callbacks  */   
-    H5VL_wrap_class_t       wrap_cls;       /* VOL object wrap / retrieval callbacks */
+    H5VL_info_class_t info_cls; /**< VOL info fields & callbacks  */
+    H5VL_wrap_class_t wrap_cls; /**< VOL object wrap / retrieval callbacks */
 
     /* Data Model */
-    H5VL_attr_class_t       attr_cls;       /* Attribute (H5A*) class callbacks */
-    H5VL_dataset_class_t    dataset_cls;    /* Dataset (H5D*) class callbacks   */
-    H5VL_datatype_class_t   datatype_cls;   /* Datatype (H5T*) class callbacks  */
-    H5VL_file_class_t       file_cls;       /* File (H5F*) class callbacks      */
-    H5VL_group_class_t      group_cls;      /* Group (H5G*) class callbacks     */
-    H5VL_link_class_t       link_cls;       /* Link (H5L*) class callbacks      */
-    H5VL_object_class_t     object_cls;     /* Object (H5O*) class callbacks    */
+    H5VL_attr_class_t     attr_cls;     /**< Attribute (H5A*) class callbacks */
+    H5VL_dataset_class_t  dataset_cls;  /**< Dataset (H5D*) class callbacks   */
+    H5VL_datatype_class_t datatype_cls; /**< Datatype (H5T*) class callbacks  */
+    H5VL_file_class_t     file_cls;     /**< File (H5F*) class callbacks      */
+    H5VL_group_class_t    group_cls;    /**< Group (H5G*) class callbacks     */
+    H5VL_link_class_t     link_cls;     /**< Link (H5L*) class callbacks      */
+    H5VL_object_class_t   object_cls;   /**< Object (H5O*) class callbacks    */
 
     /* Infrastructure / Services */
-    H5VL_introspect_class_t introspect_cls; /* Container/connector introspection class callbacks */
-    H5VL_request_class_t    request_cls;    /* Asynchronous request class callbacks */
-    H5VL_blob_class_t       blob_cls;       /* 'blob' callbacks */
-    H5VL_token_class_t      token_cls;      /* VOL connector object token class callbacks */
+    H5VL_introspect_class_t introspect_cls; /**< Container/connector introspection class callbacks */
+    H5VL_request_class_t    request_cls;    /**< Asynchronous request class callbacks */
+    H5VL_blob_class_t       blob_cls;       /**< 'Blob' class callbacks */
+    H5VL_token_class_t      token_cls;      /**< VOL connector object token class callbacks */
 
     /* Catch-all */
-    herr_t (*optional)(void *obj, int op_type, hid_t dxpl_id, void **req, va_list arguments); /* Optional callback */
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id,
+                       void **req); /**< Optional callback */
 } H5VL_class_t;
+
 \end{lstlisting}
@@
 
-The \texttt{value} field is a unique integer identifier that should be greater than 256 for external, non-library connectors. Setting it in the VOL structure is required.
-
-The \texttt{name} field is a string that uniquely identifies the VOL connector name. Setting it in the VOL structure is required.
-
-The \texttt{cap\_flags} field will be used to hold bitwise capability/feature flags that can be used with a future query API call to determine which operations and capabilities are supported by a the VOL connector.
-This feature is currently under development.
+The \texttt{value} field is a unique integer identifier that should be between 512 and 65535 for external, non-library connectors..
+
+The \texttt{name} field is a string that uniquely identifies the VOL connector name.
+
+The \texttt{conn\_version} is the connector version. This is currently not used by the library.
+
+The \texttt{cap\_flags} holds bitwise capability/feature flags that determine which operations and capabilities are supported by a the VOL connector.
+These fields were enumerated in the previous section.
 
@@
 In that case, the value of the function pointer should be set to NULL.
-Connector specific variables that are required to be passed from users should be passed through the VOL terminate property list.
-Generic properties can be added to this property class for user-defined connectors that cannot modify the HDF5 library to add internal properties.
-For more information consult the property list reference manual pages.
 
 The rest of the fields in the \texttt{H5VL\_class\_t} struct are "subclasses'' that define all the VOL function callbacks that
-are mapped to from the HDF5 API layer.
-Those subclasses are categorized into two categories, Data Model and Services.
+are mapped to from the HDF5 API layer. Those subclasses are categorized into three categories, VOL Framework, Data Model, and Infrastructure / Services.
+
+VOL Framework classes provide functionality for working with the VOL connectors themselves (e.g., working with connector strings) and with wrapping and unwrapping objects for passthrough connectors.
+
 Data Model classes are those that provide functionality for accessing an HDF5 container and objects in that container as defined by the HDF5 data model.
-Service classes are those that provide services for users that are not related to the data model specifically.
+
+Infrastructure / Service classes are those that provide services for users that are not related to the data model specifically.
 Asynchronous operations, for example, are a service that most connectors can implement, so we add a class for it in the VOL structure.
+
 If a service becomes generic enough and common among many connectors, a class for it should be added to the VOL structure.
@@
 To handle that large set of API routines, each class in the Data Model category has three generic callbacks, \texttt{get}, \texttt{specific}, and \texttt{optional} to handle the three set of API operations outline above respectively.
-The callbacks will have a \texttt{va\_list} argument to handle the different set of parameters that could be passed in.
-The \texttt{get} and \texttt{specific} callbacks also have an \texttt{op\_type} that contain an \texttt{enum} of the type of operation that is requested to be performed.
-Using that type, the \texttt{va\_list} argument can be parsed.
+To handle the varying parameters that can be passed to the callback, each callback will take a struct parameter that includes an enum {\tt get/specific} or integer {\tt optional} field indicating the operation and a union of the possible parameters {\tt get/specific} or void pointer to the parameters {\tt optional}.
+
+The optional args struct used for all optional operations:
+\begin{lstlisting}
+/* Struct for all 'optional' callbacks */
+typedef struct H5VL_optional_args_t {
+    int   op_type; /* Operation to perform */
+    void *args;    /* Pointer to operation's argument struct */
+} H5VL_optional_args_t;
+\end{lstlisting}
+
+The {\tt opt\_type} member is the value assigned by the library when the optional operation was registered (or {\tt \#define}d in the case of the native VOL connector) and the {\tt args} member is a pointer to the optional operation's parameters (usually passed in as a struct).
+
+Note that this differs from the HDF5 1.12.x scheme, which used {\tt va\_list}s.
+
 The \texttt{optional} callback is a free for all callback where anything from the API layer is passed in directly.
@@
     herr_t (*write)(void *attr, hid_t mem_type_id, const void *buf, hid_t dxpl_id, void **req);
-    herr_t (*get)(void *obj, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
-    herr_t (*optional)(void *obj, H5VL_attr_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments); 
+    herr_t (*get)(void *obj, H5VL_attr_get_args_t *args, hid_t dxpl_id, void **req);
+    herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_attr_specific_args_t *args, hid_t dxpl_id, void **req);            
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req); 
     herr_t (*close) (void *attr, hid_t dxpl_id, void **req);                     
@@
 \begin{lstlisting}
-    herr_t (*get)(void *obj, H5VL_attr_get_t get_type, hid_t dxpl_id, 
-        void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for attribute GET callback */
+    herr_t (*get)(void *obj, H5VL_attr_get_args_t *args, hid_t dxpl_id, 
+        void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): An attribute or location object where information
+  needs to be retrieved from.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for attribute 'get' operations */
 typedef enum H5VL_attr_get_t {
@@
 } H5VL_attr_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): An attribute or location object where information
-  needs to be retrieved from.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-
-\item \texttt{H5VL\_ATTR\_GET\_ACPL}, to retrieve the attribute creation
-  property list of the attribute specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    attribute creation property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_INFO}, to retrieve the attribute info:
-  \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t *loc\_params} (IN): Pointer to the location parameters
-    explained in Section~\ref{sec:map}. 
-  \item \texttt{H5A\_info\_t *ainfo} (OUT): info structure to fill the
-    attribute info in.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_NAME}, to retrieve an attribute name on a
-  particular object specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t *loc\_params} (IN): Pointer to the location parameters
-    explained in Section~\ref{sec:map}. The type could be either
-    \texttt{H5VL\_OBJECT\_BY\_SELF} meaning \texttt{obj} is the attribute,
-    or \texttt{H5VL\_OBJECT\_BY\_IDX} meaning the attribute to retrieve
-    the name for should be looked up using the index information on
-    the object in \texttt{obj} and the index information in \texttt{loc\_params}.
-  \item \texttt{size\_t buf\_size} (IN): the size of the buffer to store
-    the name in.
-  \item \texttt{void *buf} (OUT): Buffer to store the name in.
-  \item \texttt{ssize\_t *ret\_val} (OUT): return the actual size needed
-    to store the fill attribute name.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_SPACE}, to retrieve the dataspace of the
-  attribute specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    attribute dataspace.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_STORAGE\_SIZE}, to retrieve the storage
-  size of the attribute specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hsize\_t *ret} (OUT): buffer for the storage size of
-    the attribute in the container.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_GET\_TYPE}, to retrieve the datatype of the
-  attribute specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    attribute datatype.
-  \end{enumerate}
-
-\end{itemize}
+
+/* Parameters for attribute 'get_name' operation */
+typedef struct H5VL_attr_get_name_args_t {
+    H5VL_loc_params_t loc_params;    /* Location parameters for object access */
+    size_t            buf_size;      /* Size of attribute name buffer */
+    char *            buf;           /* Buffer for attribute name (OUT) */
+    size_t *          attr_name_len; /* Actual length of attribute name (OUT) */
+} H5VL_attr_get_name_args_t;
+
+/* Parameters for attribute 'get_info' operation */
+typedef struct H5VL_attr_get_info_args_t {
+    H5VL_loc_params_t loc_params; /* Location parameters for object access */
+    const char *      attr_name;  /* Attribute name (for get_info_by_name) */
+    H5A_info_t *      ainfo;      /* Attribute info (OUT) */
+} H5VL_attr_get_info_args_t;
+
+/* Parameters for attribute 'get' operations */
+typedef struct H5VL_attr_get_args_t {
+    H5VL_attr_get_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_ATTR_GET_ACPL */
+        struct {
+            hid_t acpl_id; /* Attribute creation property list ID (OUT) */
+        } get_acpl;
+
+        /* H5VL_ATTR_GET_INFO */
+        H5VL_attr_get_info_args_t get_info; /* Attribute info */
+
+        /* H5VL_ATTR_GET_NAME */
+        H5VL_attr_get_name_args_t get_name; /* Attribute name */
+
+        /* H5VL_ATTR_GET_SPACE */
+        struct {
+            hid_t space_id; /* Dataspace ID (OUT) */
+        } get_space;
+
+        /* H5VL_ATTR_GET_STORAGE_SIZE */
+        struct {
+            hsize_t *data_size; /* Size of attribute in file (OUT) */
+        } get_storage_size;
+
+        /* H5VL_ATTR_GET_TYPE */
+        struct {
+            hid_t type_id; /* Datatype ID (OUT) */
+        } get_type;
+    } args;
+} H5VL_attr_get_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for attribute SPECFIC callback */
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_attr_specific_args_t *args, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): A pointer to the location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for attribute 'specific' operation */
 typedef enum H5VL_attr_specific_t {
-    H5VL_ATTR_DELETE,                       /* H5Adelete(_by_name/idx)             */
+    H5VL_ATTR_DELETE,        /* H5Adelete(_by_name)  */
+    H5VL_ATTR_DELETE_BY_IDX, /* H5Adelete_by_idx     */
     H5VL_ATTR_EXISTS,        /* H5Aexists(_by_name)  */
@@
 } H5VL_attr_specific_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
-  \texttt{loc\_params} & (IN): A pointer to the location parameters as explained in Section~\ref{sec:map}.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_ATTR\_DELETE}, to delete an attribute on an object:
-  \begin{enumerate}
-  \item \texttt{char *attr\_name} (IN): the name of the attribute to delete.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_EXISTS}, to check if an attribute exists on a
-  particular object specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{char *attr\_name} (IN): the attribute name to check.
-  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_ITER}, to iterate over all attributes of an object and call a user-specified callback on each one:
-  \begin{enumerate}
-  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
-  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
-  \item \texttt{hsize\_t *idx} (IN/OUT): Initial and return offset within index.\\
-  \item \texttt{H5A\_operator2\_t op} (IN): User-defined function to pass each attribute to. \\
-  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
-  \end{enumerate}
-
-\item \texttt{H5VL\_ATTR\_RENAME}, to rename an attribute on an object:
-  \begin{enumerate}
-  \item \texttt{char *old\_name} (IN): the original name of the attribute.
-  \item \texttt{char *new\_name} (IN): the new name to assign for the attribute.
-  \end{enumerate}
-
-\end{itemize}
+
+/* Parameters for attribute 'iterate' operation */
+typedef struct H5VL_attr_iterate_args_t {
+    H5_index_t      idx_type; /* Type of index to iterate over */
+    H5_iter_order_t order;    /* Order of index iteration */
+    hsize_t *       idx;      /* Start/stop iteration index (IN/OUT) */
+    H5A_operator2_t op;       /* Iteration callback function */
+    void *          op_data;  /* Iteration callback context */
+} H5VL_attr_iterate_args_t;
+
+/* Parameters for attribute 'delete_by_idx' operation */
+typedef struct H5VL_attr_delete_by_idx_args_t {
+    H5_index_t      idx_type; /* Type of index to iterate over */
+    H5_iter_order_t order;    /* Order of index iteration */
+    hsize_t         n;        /* Iteration index */
+} H5VL_attr_delete_by_idx_args_t;
+
+/* Parameters for attribute 'specific' operations */
+typedef struct H5VL_attr_specific_args_t {
+    H5VL_attr_specific_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_ATTR_DELETE */
+        struct {
+            const char *name; /* Name of attribute to delete */
+        } del;
+
+        /* H5VL_ATTR_DELETE_BY_IDX */
+        H5VL_attr_delete_by_idx_args_t delete_by_idx;
+
+        /* H5VL_ATTR_EXISTS */
+        struct {
+            const char *name;   /* Name of attribute to check */
+            hbool_t *   exists; /* Whether attribute exists (OUT) */
+        } exists;
+
+        /* H5VL_ATTR_ITER */
+        H5VL_attr_iterate_args_t iterate;
+
+        /* H5VL_ATTR_RENAME */
+        struct {
+            const char *old_name; /* Name of attribute to rename */
+            const char *new_name; /* New attribute name */
+        } rename;
+    } args;
+} H5VL_attr_specific_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, H5VL_attr_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
   \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
-  \texttt{opt\_type} & (IN): The type of operation.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
   \texttt{dxpl\_id} & (IN): The data transfer property list.\\
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-Each connector that requires connector-specific operations should be able to use the \texttt{opt\_type} parameter (a connector-specific enum/integer) to determine the type of the operation and parse the \texttt{va\_list arguments} appropriately.
+\end{tabular}
+\end{mdframed}
+
+Each connector that requires connector-specific operations should compare the
+value of the {\tt op\_type} field of the {\tt H5VL\_optional\_args\_t} struct
+with the values returned from calling {\tt H5VLregister\_opt\_operation} to
+determine how to handle the optional call and interpret the arguments passed
+in the struct.
 
@@
     herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t dxpl_id, const void * buf, void **req);
-    herr_t (*get)(void *obj, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*optional)(void *obj, H5VL_dataset_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*get)(void *obj, H5VL_dataset_get_args_t *args, hid_t dxpl_id, void **req);
+    herr_t (*specific)(void *obj, H5VL_dataset_specific_args_t *args, hid_t dxpl_id, void **req);
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
     herr_t (*close) (void *dset, hid_t dxpl_id, void **req);
@@
 \begin{lstlisting}
-    herr_t (*get)(void *dset, H5VL_dataset_get_t get_type, 
-        hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for dataset GET callback */
+    herr_t (*get)(void *dset, H5VL_dataset_get_args_t *args, 
+        hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{dset} & (IN): The dataset object where information needs to be
+  retrieved from.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for dataset 'get' operation */
 typedef enum H5VL_dataset_get_t {
@@
 } H5VL_dataset_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{dset} & (IN): The dataset object where information needs to be
-  retrieved from.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_DATASET\_GET\_DAPL}, to retrieve the dataset access
-  property list of the dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    dataset access property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_DCPL}, to retrieve the dataset creation
-  property list of the dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    dataset creation property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_OFFSET}, to retrieve the offset of the
-  dataset specified in \texttt{obj} in the container:
-  \begin{enumerate}
-  \item \texttt{haddr\_t *ret} (OUT): buffer for the offset of the
-    dataset in the container.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_SPACE}, to retrieve the dataspace of the
-  dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    dataset dataspace.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_SPACE\_STATUS}, to retrieve the
-  information whether space has been allocated for the dataset:
-  \begin{enumerate}
-  \item \texttt{H5D\_space\_status\_t *allocation} (OUT): buffer for the
-    space status.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_STORAGE\_SIZE}, to retrieve the storage
-  size of the dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hsize\_t *ret} (OUT): buffer for the storage size of
-    the dataset in the container.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATASET\_GET\_TYPE}, to retrieve the datatype of the
-  dataset specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    dataset datatype.
-  \end{enumerate}
-\end{itemize}
+
+/* Parameters for dataset 'get' operations */
+typedef struct H5VL_dataset_get_args_t {
+    H5VL_dataset_get_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_DATASET_GET_DAPL */
+        struct {
+            hid_t dapl_id; /* Dataset access property list ID (OUT) */
+        } get_dapl;
+
+        /* H5VL_DATASET_GET_DCPL */
+        struct {
+            hid_t dcpl_id; /* Dataset creation property list ID (OUT) */
+        } get_dcpl;
+
+        /* H5VL_DATASET_GET_SPACE */
+        struct {
+            hid_t space_id; /* Dataspace ID (OUT) */
+        } get_space;
+
+        /* H5VL_DATASET_GET_SPACE_STATUS */
+        struct {
+            H5D_space_status_t *status; /* Storage space allocation status (OUT) */
+        } get_space_status;
+
+        /* H5VL_DATASET_GET_STORAGE_SIZE */
+        struct {
+            hsize_t *storage_size; /* Size of dataset's storage (OUT) */
+        } get_storage_size;
+
+        /* H5VL_DATASET_GET_TYPE */
+        struct {
+            hid_t type_id; /* Datatype ID (OUT) */
+        } get_type;
+    } args;
+} H5VL_dataset_get_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*specific)(void *obj, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for dataset SPECFIC callback */
+    herr_t (*specific)(void *obj, H5VL_file_specific_args_t *args, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The dset  where the operation needs
+  to happen.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for dataset 'specific' operation */
 typedef enum H5VL_dataset_specific_t {
@@
 } H5VL_dataset_specific_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The dset  where the operation needs
-  to happen.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_DATASET\_SET\_EXTENT}, changes the extent of the dataset dimensions:
-  \begin{enumerate}
-  \item \texttt{hsize\_t size} (IN): Array containing the new magnitude of each dimension of the dataset. 
-  \end{enumerate}
-\item \texttt{H5VL\_DATASET\_FLUSH}, flushes a dataset:
-  \begin{enumerate}
-  \item \texttt{hid\_t dset\_id} (IN): The dataset ID. Needed so that the refreshed data can be associated with the old ID. 
-  \end{enumerate}
-\item \texttt{H5VL\_DATASET\_REFRESH}, clears a dataset's buffers and reloads from disk:
-  \begin{enumerate}
-  \item \texttt{hid\_t dset\_id} (IN): The dataset ID. Needed so that the refreshed data can be associated with the old ID. 
-  \end{enumerate}
-\end{itemize}
+
+/* Parameters for dataset 'specific' operations */
+typedef struct H5VL_dataset_specific_args_t {
+    H5VL_dataset_specific_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_DATASET_SET_EXTENT */
+        struct {
+            const hsize_t *size; /* New dataspace extent */
+        } set_extent;
+
+        /* H5VL_DATASET_FLUSH */
+        struct {
+            hid_t dset_id; /* Dataset ID (IN) */
+        } flush;
+
+        /* H5VL_DATASET_REFRESH */
+        struct {
+            hid_t dset_id; /* Dataset ID (IN) */
+        } refresh;
+    } args;
+} H5VL_dataset_specific_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, H5VL_dataset_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
     void *(*open)(void *obj, const H5VL_loc_params_t *loc_params, const char * name, hid_t tapl_id, hid_t dxpl_id, void **req);
-    herr_t (*get)   (void *obj, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
-    herr_t (*optional)(void *obj, H5VL_datatype_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments); 
+    herr_t (*get)   (void *obj, H5VL_datatype_get_args_t *args, hid_t dxpl_id, void **req);
+    herr_t (*specific)(void *obj, H5VL_datatype_specific_args_t *args, hid_t dxpl_id, void **req);            
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req); 
     herr_t (*close) (void *dt, hid_t dxpl_id, void **req);                       
@@
 \begin{lstlisting}
-    herr_t (*get) (void *obj, H5VL_datatype_get_t get_type, 
-        hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for datatype GET callback */
+    herr_t (*get) (void *obj, H5VL_datatype_get_args_t *args, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The named datatype to retrieve information from.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for datatype 'get' operation */
 typedef enum H5VL_datatype_get_t {
-    H5VL_DATATYPE_GET_BINARY,               /* get serialized form of transient type    */
-    H5VL_DATATYPE_GET_TCPL                  /* datatype creation property list          */
+    H5VL_DATATYPE_GET_BINARY_SIZE, /* Get size of serialized form of transient type */
+    H5VL_DATATYPE_GET_BINARY,      /* Get serialized form of transient type         */
+    H5VL_DATATYPE_GET_TCPL         /* Datatype creation property list               */
 } H5VL_datatype_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The named datatype to retrieve information from.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_DATATYPE\_GET\_BINARY}, to retrieve the serialized original transient HDF5 datatype that was committed, or
-return the size that is required for it be serialized if the passed in buffer is \texttt{NULL}. The HDF5 library provides two functions to
-encode and decode datatypes in their transient form, \texttt{H5Tencode()} and \texttt{H5Tdecode()}.
-When a datatype is committed, the connector is required to keep the serialized form of the transient datatype stored somewhere in the container (which is usually the case anyway when committing a named datatype), so it can be retrieved with this call.
-This is needed to generate the higher level HDF5 datatype identifier that allows all the H5T ``transient'' routines to work properly on the named datatype.
-  \begin{enumerate}
-  \item \texttt{ssize\_t *nalloc} (OUT): buffer to store the total size of the serialized datatype.
-  \item \texttt{void *buf} (OUT): buffer to store the serialized datatype.
-  \item \texttt{size\_t size} (IN): size of the passed in buffer.
-  \end{enumerate}
-
-\item \texttt{H5VL\_DATATYPE\_GET\_TCPL}, to retrieve the datatype
-  creation property list:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    type creation property list.
-  \end{enumerate}
-\end{itemize}
+
+/* Parameters for datatype 'get' operations */
+typedef struct H5VL_datatype_get_args_t {
+    H5VL_datatype_get_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_DATATYPE_GET_BINARY_SIZE */
+        struct {
+            size_t *size; /* Size of serialized form of datatype (OUT) */
+        } get_binary_size;
+
+        /* H5VL_DATATYPE_GET_BINARY */
+        struct {
+            void * buf;      /* Buffer to store serialized form of datatype (OUT) */
+            size_t buf_size; /* Size of serialized datatype buffer */
+        } get_binary;
+
+        /* H5VL_DATATYPE_GET_TCPL */
+        struct {
+            hid_t tcpl_id; /* Named datatype creation property list ID (OUT) */
+        } get_tcpl;
+    } args;
+} H5VL_datatype_get_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for datatype SPECFIC callback */                                        
-typedef enum H5VL_datatype_specific_t {                                          
-    H5VL_DATATYPE_FLUSH,                                                         
-    H5VL_DATATYPE_REFRESH                                                        
-} H5VL_datatype_specific_t;  
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_object_specific_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
   \texttt{loc\_params} & (IN): Pointer to location parameters as explained in Section~\ref{sec:map}.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_DATATYPE\_FLUSH}, flushes a datatype:
-  \begin{enumerate}
-  \item \texttt{hid\_t type\_id} (IN): The datatype ID. Needed so that the refreshed data can be associated with the old ID. 
-  \end{enumerate}
-\item \texttt{H5VL\_DATATYPE\_REFRESH}, clears a datatype's buffers and reloads from disk:
-  \begin{enumerate}
-  \item \texttt{hid\_t type\_id} (IN): The datatype ID. Needed so that the refreshed data can be associated with the old ID. 
-  \end{enumerate}
-\end{itemize}
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for datatype 'specific' operation */
+typedef enum H5VL_datatype_specific_t {
+    H5VL_DATATYPE_FLUSH,  /* H5Tflush */
+    H5VL_DATATYPE_REFRESH /* H5Trefresh */
+} H5VL_datatype_specific_t;
+
+/* Parameters for datatype 'specific' operations */
+typedef struct H5VL_datatype_specific_args_t {
+    H5VL_datatype_specific_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_DATATYPE_FLUSH */
+        struct {
+            hid_t type_id; /* Named datatype ID (IN) */
+        } flush;
+
+        /* H5VL_DATATYPE_REFRESH */
+        struct {
+            hid_t type_id; /* Named datatype ID (IN) */
+        } refresh;
+    } args;
+} H5VL_datatype_specific_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, H5VL_datatype_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
     void *(*open)(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
-    herr_t (*get)(void *obj, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
-    herr_t (*optional)(void *obj, H5VL_file_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*get)(void *obj, H5VL_file_get_args_t *args, hid_t dxpl_id, void **req);
+    herr_t (*specific)(void *obj, H5VL_file_specific_args_t *args, hid_t dxpl_id, void **req);            
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
     herr_t (*close) (void *file, hid_t dxpl_id, void **req);
@@
 \begin{lstlisting}
-    herr_t (*get)(void *obj, H5VL_file_get_t get_type, hid_t dxpl_id, 
-        void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for all file get API routines */
+    herr_t (*get)(void *obj, H5VL_file_get_args_t *args, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The container or object where information needs to be
+  retrieved from.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Info for H5VL_FILE_GET_CONT_INFO */
+typedef struct H5VL_file_cont_info_t {
+    unsigned version;       /* version information (keep first) */
+    uint64_t feature_flags; /* Container feature flags          */
+                            /* (none currently defined)         */
+    size_t token_size;      /* Size of tokens                   */
+    size_t blob_id_size;    /* Size of blob IDs                 */
+} H5VL_file_cont_info_t;
+
+/* Values for file 'get' operation */
 typedef enum H5VL_file_get_t {
@@
 } H5VL_file_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The container or object where information needs to be
-  retrieved from.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_OBJECT\_GET\_CONT\_INFO}, get information about the container
-    that the object belongs to:
-  \begin{enumerate}
-  \item \texttt{H5VL\_file\_cont\_info\_t *info} (OUT): pointer to the file
-    container info structure returned.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_GET\_FAPL}, to retrieve the file access
-  property list:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    file access property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_GET\_FCPL}, to retrieve the file creation
-  property list:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    file creation property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_GET\_FILENO}, to retrieve the file's file number:
-  \begin{enumerate}
-  \item \texttt{unsigned long *fileno} (OUT): buffer for the file number.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_GET\_INTENT}, get access intent of the
-  container:
-  \begin{enumerate}
-  \item \texttt{unsigned *intent\_flags} (OUT): buffer for the intent flags value.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_GET\_NAME}, get container name an object
-  belongs to:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
-  \item \texttt{size\_t size} (IN): size of the buffer for the file name.
-  \item \texttt{char *name} (OUT): buffer for the file name.
-  \item \texttt{ssize\_t *ret} (OUT): buffer for the entire size of the
-    file name.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_GET\_OBJ\_COUNT:}, to retrieve the object count
-  in the container:
-  \begin{enumerate}
-  \item \texttt{unsigned types} (IN): type of objects to look for.
-  \item \texttt{ssize\_t *ret} (OUT): buffer for the object count.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_GET\_OBJ\_IDS:}, to retrieve object identifiers
-  in the container:
-  \begin{enumerate}
-  \item \texttt{unsigned types} (IN): type of objects to look for.
-  \item \texttt{size\_t max\_objs} (IN): maximum number of objects to
-    open.
-  \item \texttt{hid\_t *oid\_list} (OUT): buffer for the object identifiers.
-  \item \texttt{ssize\_t *ret} (OUT): buffer for the object count.
-  \end{enumerate}
-
-\end{itemize}
-\end{mdframed}
+
+/* Parameters for file 'get_name' operation */
+typedef struct H5VL_file_get_name_args_t {
+    H5I_type_t type;          /* ID type of object pointer */
+    size_t     buf_size;      /* Size of file name buffer (IN) */
+    char *     buf;           /* Buffer for file name (OUT) */
+    size_t *   file_name_len; /* Actual length of file name (OUT) */
+} H5VL_file_get_name_args_t;
+
+/* Parameters for file 'get_obj_ids' operation */
+typedef struct H5VL_file_get_obj_ids_args_t {
+    unsigned types;    /* Type of objects to count */
+    size_t   max_objs; /* Size of array of object IDs */
+    hid_t *  oid_list; /* Array of object IDs (OUT) */
+    size_t * count;    /* # of objects (OUT) */
+} H5VL_file_get_obj_ids_args_t;
+
+/* Parameters for file 'get' operations */
+typedef struct H5VL_file_get_args_t {
+    H5VL_file_get_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_FILE_GET_CONT_INFO */
+        struct {
+            H5VL_file_cont_info_t *info; /* Container info (OUT) */
+        } get_cont_info;
+
+        /* H5VL_FILE_GET_FAPL */
+        struct {
+            hid_t fapl_id; /* File access property list (OUT) */
+        } get_fapl;
+
+        /* H5VL_FILE_GET_FCPL */
+        struct {
+            hid_t fcpl_id; /* File creation property list (OUT) */
+        } get_fcpl;
+
+        /* H5VL_FILE_GET_FILENO */
+        struct {
+            unsigned long *fileno; /* File "number" (OUT) */
+        } get_fileno;
+
+        /* H5VL_FILE_GET_INTENT */
+        struct {
+            unsigned *flags; /* File open/create intent flags (OUT) */
+        } get_intent;
+
+        /* H5VL_FILE_GET_NAME */
+        H5VL_file_get_name_args_t get_name;
+
+        /* H5VL_FILE_GET_OBJ_COUNT */
+        struct {
+            unsigned types; /* Type of objects to count */
+            size_t * count; /* # of objects (OUT) */
+        } get_obj_count;
+
+        /* H5VL_FILE_GET_OBJ_IDS */
+        H5VL_file_get_obj_ids_args_t get_obj_ids;
+    } args;
+} H5VL_file_get_args_t;
+
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*specific)(void *obj, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for file SPECIFIC callback */
+    herr_t (*specific)(void *obj, H5VL_file_specific_args_t *args, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The container or object where the operation needs
+  to happen.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for file 'specific' operation */
 typedef enum H5VL_file_specific_t {
@@
     H5VL_FILE_REOPEN,        /* Reopen the file                  */
-    H5VL_FILE_MOUNT,                        /* Mount a file                     */
-    H5VL_FILE_UNMOUNT,                      /* Unmount a file                   */
     H5VL_FILE_IS_ACCESSIBLE, /* Check if a file is accessible    */
@@
 } H5VL_file_specific_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The container or object where the operation needs
-  to happen.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_FILE\_POST\_OPEN}, adjust a file after opening it:
-
-\item \texttt{H5VL\_FILE\_FLUSH}, flushes all buffers associated with the container to disk:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
-  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_REOPEN}, reopens a file:
-  \begin{enumerate}
-      \item \texttt{void *file} (IN): pointer to the reopened file (same type
-          of pointer as is returned from the connector's create/open callbacks).
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_MOUNT}, Mounts a file on the location object:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
-  \item \texttt{char *name} (IN): name of the group onto which the file
-    specified by \texttt{file} is to be mounted.
-  \item \texttt{void *child} (IN): child file to be mounted (same type
-          of pointer as is returned from the connector's create/open callbacks).
-  \item \texttt{hid\_t *fmpl\_id} (IN): file mount property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_UNMOUNT}, un-mounts a file from the location object:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
-  \item \texttt{char *name} (IN): name of the mount point.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_IS\_ACCESSIBLE}, checks if a container is
-  accessible using a specific file access property list:
-  \begin{enumerate}
-  \item \texttt{hid\_t *fapl\_id} (IN): file access property list.
-  \item \texttt{char *name} (IN): name of the container to check.
-  \item \texttt{htri\_t *result} (OUT): buffer for the result; 0 if no, 1
-    if yes.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_DELETE}, deletes a file:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
-  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
-  \end{enumerate}
-
-\item \texttt{H5VL\_FILE\_IS\_EQUAL}, check if one file is equal to another:
-  \begin{enumerate}
-  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
-  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
-  \end{enumerate}
-
- \end{itemize}
-\end{mdframed}
+
+/* Parameters for file 'specific' operations */
+typedef struct H5VL_file_specific_args_t {
+    H5VL_file_specific_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_FILE_FLUSH */
+        struct {
+            H5I_type_t  obj_type; /* Type of object to use */
+            H5F_scope_t scope;    /* Scope of flush operation */
+        } flush;
+
+        /* H5VL_FILE_REOPEN */
+        struct {
+            void **file; /* File object for new file (OUT) */
+        } reopen;
+
+        /* H5VL_FILE_IS_ACCESSIBLE */
+        struct {
+            const char *filename;   /* Name of file to check */
+            hid_t       fapl_id;    /* File access property list to use */
+            hbool_t *   accessible; /* Whether file is accessible with FAPL settings (OUT) */
+        } is_accessible;
+
+        /* H5VL_FILE_DELETE */
+        struct {
+            const char *filename; /* Name of file to delete */
+            hid_t       fapl_id;  /* File access property list to use */
+        } del;
+
+        /* H5VL_FILE_IS_EQUAL */
+        struct {
+            void *   obj2;      /* Second file object to compare against */
+            hbool_t *same_file; /* Whether files are the same (OUT) */
+        } is_equal;
+    } args;
+} H5VL_file_specific_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, H5VL_file_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
     void *(*open)(void *obj, const H5VL_loc_params_t *loc_params, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
-    herr_t (*get)(void *obj, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*specific)(void *obj, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-    herr_t (*optional)(void *obj, H5VL_group_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*get)(void *obj, H5VL_group_get_args_t *args, hid_t dxpl_id, void **req);
+    herr_t (*specific)(void *obj, H5VL_group_specific_args_t *args, hid_t dxpl_id, void **req);
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
     herr_t (*close) (void *grp, hid_t dxpl_id, void **req);
@@
 \begin{lstlisting}
-    herr_t (*get)(void *obj, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for all group get API routines */
+    herr_t (*get)(void *obj, H5VL_group_get_args_t *args, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The group object where information needs to be
+  retrieved from.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for group 'get' operation */
 typedef enum H5VL_group_get_t {
@@
 } H5VL_group_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The group object where information needs to be
-  retrieved from.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_GROUP\_GET\_GCPL}, to retrieve the group creation
-  property list of the group specified in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
-    group creation property list.
-  \end{enumerate}
-
-\item \texttt{H5VL\_GROUP\_GET\_INFO}, to retrieve the attribute info:
-  \begin{enumerate}
-  \item \texttt{H5VL\_loc\_params\_t *loc\_params} (IN): Pointer to the location
-      parameters explained in Section~\ref{sec:map}. 
-  \item \texttt{H5G\_info\_t *group\_info} (OUT): info structure to fill the
-    group info in.
-  \end{enumerate}
-\end{itemize}
+
+/* Parameters for group 'get_info' operation */
+typedef struct H5VL_group_get_info_args_t {
+    H5VL_loc_params_t loc_params; /* Location parameters for object access */
+    H5G_info_t *      ginfo;      /* Group info (OUT) */
+} H5VL_group_get_info_args_t;
+
+/* Parameters for group 'get' operations */
+typedef struct H5VL_group_get_args_t {
+    H5VL_group_get_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_GROUP_GET_GCPL */
+        struct {
+            hid_t gcpl_id; /* Group creation property list (OUT) */
+        } get_gcpl;
+
+        /* H5VL_GROUP_GET_INFO */
+        H5VL_group_get_info_args_t get_info; /* Group info */
+    } args;
+} H5VL_group_get_args_t;
+
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for group SPECFIC callback */                                           
-typedef enum H5VL_group_specific_t {                                             
-    H5VL_GROUP_FLUSH,                                                            
-    H5VL_GROUP_REFRESH                                                           
-} H5VL_group_specific_t;
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_object_specific_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
   \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in Section~\ref{sec:map}.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_GROUP\_FLUSH}, flushes a group:
-  \begin{enumerate}
-  \item \texttt{hid\_t grp\_id} (IN): The group ID. Needed so that the refreshed data can be associated with the old ID. 
-  \end{enumerate}
-\item \texttt{H5VL\_GROUP\_REFRESH}, clears a group's buffers and reloads from disk:
-  \begin{enumerate}
-  \item \texttt{hid\_t grp\_id} (IN): The group ID. Needed so that the refreshed data can be associated with the old ID. 
-  \end{enumerate}
-\end{itemize}
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for group 'specific' operation */
+typedef enum H5VL_group_specific_t {
+    H5VL_GROUP_MOUNT,   /* Mount a file on a group          */
+    H5VL_GROUP_UNMOUNT, /* Unmount a file on a group        */
+    H5VL_GROUP_FLUSH,   /* H5Gflush                         */
+    H5VL_GROUP_REFRESH  /* H5Grefresh                       */
+} H5VL_group_specific_t;
+
+/* Parameters for group 'mount' operation */
+typedef struct H5VL_group_spec_mount_args_t {
+    const char *name;       /* Name of location to mount child file */
+    void *      child_file; /* Pointer to child file object */
+    hid_t       fmpl_id;    /* File mount property list to use */
+} H5VL_group_spec_mount_args_t;
+
+/* Parameters for group 'specific' operations */
+typedef struct H5VL_group_specific_args_t {
+    H5VL_group_specific_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_GROUP_MOUNT */
+        H5VL_group_spec_mount_args_t mount;
+
+        /* H5VL_GROUP_UNMOUNT */
+        struct {
+            const char *name; /* Name of location to unmount child file */
+        } unmount;
+
+        /* H5VL_GROUP_FLUSH */
+        struct {
+            hid_t grp_id; /* Group ID (IN) */
+        } flush;
+
+        /* H5VL_GROUP_REFRESH */
+        struct {
+            hid_t grp_id; /* Group ID (IN) */
+        } refresh;
+    } args;
+} H5VL_group_specific_args_t;
+
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, H5VL_group_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
 typedef struct H5VL_link_class_t {                                               
-    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj, const H5VL_loc_params_t *loc_params, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*create)(H5VL_link_create_args_t *args, void *obj, const H5VL_loc_params_t *loc_params, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
     herr_t (*copy)(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);           
     herr_t (*move)(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);           
-    herr_t (*get)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);                 
-    herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
-    herr_t (*optional)(void *obj, H5VL_link_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments); 
+    herr_t (*get)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_link_get_args_t *args, hid_t dxpl_id, void **req);                 
+    herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_link_specific_args_t *args, hid_t dxpl_id, void **req);            
+    herr_t (*optional)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_optional_args_t *args, hid_t dxpl_id, void **req); 
 } H5VL_link_class_t;   
@@
 \begin{lstlisting}
-    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj,
+    herr_t (*create)(H5VL_link_create_args_t *args, void *obj,
         H5VL_loc_params_t *loc_params, hid_t lcpl_id, 
@@
 
-The \texttt{create\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* link create types for VOL */
-typedef enum H5VL_link_create_type_t {
-    H5VL_LINK_CREATE_HARD,  /* Hard Link          */
-    H5VL_LINK_CREATE_SOFT,  /* Soft Link          */
-    H5VL_LINK_CREATE_UD      /* External / UD Link */
-} H5VL_link_create_type_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{create\_type} & (IN): type of the link to be created.\\
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
   \texttt{obj} & (IN): Pointer to an object where the link needs to be
@@
 
-As mentioned in the argument list, the \texttt{lcpl\_id} contains the
-parameters for the link creation operation depending on the creation
-type:
-\begin{itemize}
-\item \texttt{H5VL\_LINK\_CREATE\_HARD} contains two properties:
-  \begin{enumerate}
-  \item \texttt{H5VL\_LINK\_TARGET} (with type \texttt{void*}): The target
-    object where the hard link needs to be created to.
-  \item \texttt{H5VL\_LINK\_TARGET\_LOC\_PARAMS} (with type \texttt{H5VL\_loc\_params\_t}): The location parameters as explained in
-    Section~\ref{sec:map} for the target object.
-  \end{enumerate}
-
-\item \texttt{H5VL\_LINK\_CREATE\_SOFT} contains one property:
-  \begin{enumerate}
-  \item \texttt{H5VL\_LINK\_TARGET\_NAME} (with type \texttt{char*}): The target
-    link where the soft link should point to.
-  \end{enumerate}
-
-\item \texttt{H5VL\_LINK\_CREATE\_UD} contains two properties:
-  \begin{enumerate}
-  \item \texttt{H5VL\_LINK\_TYPE} (with type \texttt{H5L\_type\_t}): The
-    user defined link class. \texttt{H5L\_TYPE\_EXTERNAL} suggests an
-    external link is to be created.
-  \item \texttt{H5VL\_LINK\_UDATA} (with type \texttt{void*}): User supplied
-    link information (contains the external link buffer for external
-    links). 
-  \item \texttt{H5VL\_LINK\_UDATA\_SIZE} (with type \texttt{size\_t}): size
-    of the \texttt{udata} buffer. 
-  \end{enumerate}
-\end{itemize}
+\begin{lstlisting}
+/* Link create types for VOL */
+typedef enum H5VL_link_create_t {
+    H5VL_LINK_CREATE_HARD,
+    H5VL_LINK_CREATE_SOFT,
+    H5VL_LINK_CREATE_UD
+} H5VL_link_create_t;
+
+/* Parameters for link 'create' operations */
+typedef struct H5VL_link_create_args_t {
+    H5VL_link_create_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_LINK_CREATE_HARD */
+        struct {
+            void *            curr_obj;        /* Current object */
+            H5VL_loc_params_t curr_loc_params; /* Location parameters for current object */
+        } hard;
+
+        /* H5VL_LINK_CREATE_SOFT */
+        struct {
+            const char *target; /* Target of soft link */
+        } soft;
+
+        /* H5VL_LINK_CREATE_UD */
+        struct {
+            H5L_type_t  type;     /* Type of link to create */
+            const void *buf;      /* Buffer that contains link info */
+            size_t      buf_size; /* Size of link info buffer */
+        } ud;
+    } args;
+} H5VL_link_create_args_t;
+
+\end{lstlisting}
 
@@
     herr_t (*get)(void *obj, H5VL_loc_params_t *loc_params, 
-        H5VL_link_get_t get_type, hid_t dxpl_id, void **req, 
-        va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for all link get API routines */
+        H5VL_link_get_args_t *args, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The file or group object where information needs to be
+  retrieved from.\\
+  \texttt{loc\_params} & (IN): Pointer to the location parameters for the source
+  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} or \texttt{H5VL\_OBJECT\_BY\_IDX} in this
+  callback.\\ 
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for link 'get' operation */
 typedef enum H5VL_link_get_t {
@@
 } H5VL_link_get_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The file or group object where information needs to be
-  retrieved from.\\
-  \texttt{loc\_params} & (IN): Pointer to the location parameters for the source
-  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} or \texttt{H5VL\_OBJECT\_BY\_IDX} in this
-  callback.\\ 
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_LINK\_GET\_INFO}, to retrieve the link info from the
-  link specified in the \texttt{loc\_params}:
-  \begin{enumerate}
-  \item \texttt{H5L\_info\_t *linfo} (OUT): pointer to info structure to
-    fill.
-  \end{enumerate}
-
-\item \texttt{H5VL\_LINK\_GET\_NAME}, to retrieve the name of the link
-  specified by the index information in \texttt{loc\_params} (\texttt{loc\_params} is of type \texttt{H5VL\_OBJECT\_BY\_IDX} only with this
-  type):
-  \begin{enumerate}
-  \item \texttt{char* name} (OUT): buffer to copy the name into.
-  \item \texttt{size\_t size} (IN): size of the buffer name, if 0, return
-    only the buffer size needed.
-  \item \texttt{ssize\_t *ret} (OUT): buffer to return the length of the
-    link name.
-  \end{enumerate}
-
-\item \texttt{H5VL\_LINK\_GET\_VAL}, to retrieve the link value from the
-  link specified in the \texttt{loc\_params}:
-  \begin{enumerate}
-  \item \texttt{void *buf} (OUT): buffer to put the value into.
-  \item \texttt{size\_t size} (IN): size of the passed in buffer.
-  \end{enumerate}
-\end{itemize}
+
+/* Parameters for link 'get' operations */
+typedef struct H5VL_link_get_args_t {
+    H5VL_link_get_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_LINK_GET_INFO */
+        struct {
+            H5L_info2_t *linfo; /* Pointer to link's info (OUT) */
+        } get_info;
+
+        /* H5VL_LINK_GET_NAME */
+        struct {
+            size_t  name_size; /* Size of link name buffer (IN) */
+            char *  name;      /* Buffer for link name (OUT) */
+            size_t *name_len;  /* Actual length of link name (OUT) */
+        } get_name;
+
+        /* H5VL_LINK_GET_VAL */
+        struct {
+            size_t buf_size; /* Size of link value buffer (IN) */
+            void * buf;      /* Buffer for link value (OUT) */
+        } get_val;
+    } args;
+} H5VL_link_get_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for link SPECIFIC callback */
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_link_specific_args_t *args, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for link 'specific' operation */
 typedef enum H5VL_link_specific_t {
@@
 } H5VL_link_specific_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
-  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in Section~\ref{sec:map}.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_LINK\_DELETE}, to remove a link specified in the location parameter from an HDF5 container.
-
-\item \texttt{H5VL\_LINK\_EXISTS}, to determine whether the link specified
-  in the \texttt{loc\_params} exits (\texttt{loc\_params} is of type \texttt{H5VL\_OBJECT\_BY\_NAME} only with this type):
-  \begin{enumerate}
-  \item \texttt{htri\_t *ret} (OUT): buffer for the existence of the link
-    (0 for no, 1 for yes).
-  \end{enumerate}
-
-\item \texttt{H5VL\_LINK\_ITER}, to iterate over all links starting at the location provided and call a user-specified callback on each one:
-  \begin{enumerate}
-  \item \texttt{hbool\_t recursive} (IN): whether to recursively follow links into subgroups of the specified group.\\
-  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
-  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
-  \item \texttt{hsize\_t *idx\_p} (IN/OUT):  iteration position where to start and return position where an interrupted iteration may restart.\\
-  \item \texttt{H5L\_iterate\_t op} (IN): User-defined function to pass each link to. \\
-  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
-  \end{enumerate}
-\end{itemize}
+
+/* Parameters for link 'iterate' operation */
+typedef struct H5VL_link_iterate_args_t {
+    hbool_t         recursive; /* Whether iteration is recursive */
+    H5_index_t      idx_type;  /* Type of index to iterate over */
+    H5_iter_order_t order;     /* Order of index iteration */
+    hsize_t *       idx_p;     /* Start/stop iteration index (OUT) */
+    H5L_iterate2_t  op;        /* Iteration callback function */
+    void *          op_data;   /* Iteration callback context */
+} H5VL_link_iterate_args_t;
+
+/* Parameters for link 'specific' operations */
+typedef struct H5VL_link_specific_args_t {
+    H5VL_link_specific_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_LINK_DELETE */
+        /* No args */
+
+        /* H5VL_LINK_EXISTS */
+        struct {
+            hbool_t *exists; /* Whether link exists (OUT) */
+        } exists;
+
+        /* H5VL_LINK_ITER */
+        H5VL_link_iterate_args_t iterate;
+    } args;
+} H5VL_link_specific_args_t;
+
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, H5VL_link_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
     herr_t (*copy)(void *src_obj, const H5VL_loc_params_t *loc_params1, const char *src_name, void *dst_obj, const H5VL_loc_params_t *loc_params2, const char *dst_name, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
-    herr_t (*get)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);                 
-    herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);            
-    herr_t (*optional)(void *obj, hid_t dxpl_id, void **req, va_list arguments); 
+    herr_t (*get)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_object_get_args_t *args, hid_t dxpl_id, void **req);                 
+    herr_t (*specific)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_object_specific_args_t *args, hid_t dxpl_id, void **req);            
+    herr_t (*optional)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_optional_args_t *args, hid_t dxpl_id, void **req); 
 } H5VL_object_class_t; 
@@
     herr_t (*get)(void *obj, H5VL_loc_params_t *loc_params, 
-        H5VL_object_get_t get_type, hid_t dxpl_id, 
-        void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{get\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* type for object GET callback */
-typedef enum H5VL_object_get_t {                                                 
-    H5VL_OBJECT_GET_FILE,              /* object's file                     */  
-    H5VL_OBJECT_GET_NAME,              /* object name                       */  
-    H5VL_OBJECT_GET_TYPE               /* object type                       */  
-    H5VL_OBJECT_GET_INFO               /* H5Oget_info(_by_idx|name)         */
-} H5VL_object_get_t; 
+        H5VL_object_get_args_t *args, hid_t dxpl_id, 
+        void **req);
 \end{lstlisting}
@@
   explained in Section~\ref{sec:map}.\\
-  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{get\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_OBJECT\_GET\_FILE}, to retrieve a file for a referenced object:
-  \begin{enumerate}
-  \item \texttt{void **ret} (OUT): pointer to buffer to return the file.
-  \end{enumerate}
-
- \item \texttt{H5VL\_OBJECT\_GET\_NAME}, to retrieve a name for a referenced object:
-  \begin{enumerate}
-  \item \texttt{ssize\_t *ret} (OUT): buffer to return the length of the
-    name.
-  \item \texttt{char* name} (OUT): buffer to copy the name into.
-  \item \texttt{size\_t size} (IN): size of the buffer name, if 0, return
-    only the buffer size needed.
-  \end{enumerate}
-
-\item \texttt{H5VL\_OBJECT\_GET\_TYPE}, to retrieve object type a reference
-  points to:
-  \begin{enumerate}
-  \item \texttt{H5O\_type\_t *type} (OUT): buffer to return the object type.
-  \end{enumerate}
-\end{itemize}
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for object 'get' operation */
+typedef enum H5VL_object_get_t {
+    H5VL_OBJECT_GET_FILE, /* object file                       */
+    H5VL_OBJECT_GET_NAME, /* object name                       */
+    H5VL_OBJECT_GET_TYPE, /* object type                       */
+    H5VL_OBJECT_GET_INFO  /* H5Oget_info(_by_idx|name)         */
+} H5VL_object_get_t;
+
+/* Parameters for object 'get' operations */
+typedef struct H5VL_object_get_args_t {
+    H5VL_object_get_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_OBJECT_GET_FILE */
+        struct {
+            void **file; /* File object (OUT) */
+        } get_file;
+
+        /* H5VL_OBJECT_GET_NAME */
+        struct {
+            size_t  buf_size; /* Size of name buffer (IN) */
+            char *  buf;      /* Buffer for name (OUT) */
+            size_t *name_len; /* Actual length of name (OUT) */
+        } get_name;
+
+        /* H5VL_OBJECT_GET_TYPE */
+        struct {
+            H5O_type_t *obj_type; /* Type of object (OUT) */
+        } get_type;
+
+        /* H5VL_OBJECT_GET_INFO */
+        struct {
+            unsigned     fields; /* Flags for fields to retrieve */
+            H5O_info2_t *oinfo;  /* Pointer to object info (OUT) */
+        } get_info;
+    } args;
+} H5VL_object_get_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for object SPECIFIC callback */
+	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_object_specific_args_t *args, hid_t dxpl_id, void **req);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
+  \texttt{loc\_params} & (IN): Pointer to location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
+  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
+  operation created by the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for object 'specific' operation */
 typedef enum H5VL_object_specific_t {
@@
 } H5VL_object_specific_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
-  \texttt{loc\_params} & (IN): Pointer to location parameters as explained in Section~\ref{sec:map}.\\
-  \texttt{specific\_type} & (IN): The type of the operation.\\
-  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
-  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
-  operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and
-  output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-The \texttt{arguments} argument contains a variable list of arguments
-depending on the \texttt{specific\_type} parameter. The following list shows
-the argument list, in order, for each type:
-
-\begin{itemize}
-\item \texttt{H5VL\_OBJECT\_CHANGE\_REF\_COUNT}, to update the reference
-  count for the object in \texttt{obj}:
-  \begin{enumerate}
-  \item \texttt{int ref\_count} (IN): reference count to set on the object.
-  \end{enumerate}
-
-\item \texttt{H5VL\_OBJECT\_EXISTS}, to check if an object with name
-  specified in \texttt{loc\_params} (type \texttt{H5VL\_OBJECT\_BY\_NAME})
-  exists:
-  \begin{enumerate}
-  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
-  \end{enumerate}
-
-\item \texttt{H5VL\_OBJECT\_LOOKUP}, Look up an object:
-  \begin{enumerate}
-  \item \texttt{void *token} (IN): The object's token.\\
-  \end{enumerate}
-
-\item \texttt{H5VL\_OBJECT\_VISIT}, to iterate over all objects starting at the location provided and call a user-specified callback on each one:
-  \begin{enumerate}
-  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
-  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
-  \item \texttt{H5O\_iterate\_t op} (IN): User-defined function to pass each object to. \\
-  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
-  \item \texttt{unsigned fields} (IN): Fields in H5O\_info\_t struct to return. \\
-  \end{enumerate}
-
-\item \texttt{H5VL\_OBJECT\_FLUSH}, flushes a object:
-  \begin{enumerate}
-  \item \texttt{hid\_t obj\_id} (IN): The object ID. Needed so that the refreshed data can be associated with the old ID. 
-  \end{enumerate}
-
-\item \texttt{H5VL\_OBJECT\_REFRESH}, clears an object's buffers and reloads from disk:
-  \begin{enumerate}
-  \item \texttt{hid\_t obj\_id} (IN): The object ID. Needed so that the refreshed data can be associated with the old ID. 
-  \end{enumerate}
-\end{itemize}
+
+/* Parameters for object 'visit' operation */
+typedef struct H5VL_object_visit_args_t {
+    H5_index_t      idx_type; /* Type of index to iterate over */
+    H5_iter_order_t order;    /* Order of index iteration */
+    unsigned        fields;   /* Flags for fields to provide in 'info' object for 'op' callback */
+    H5O_iterate2_t  op;       /* Iteration callback function */
+    void *          op_data;  /* Iteration callback context */
+} H5VL_object_visit_args_t;
+
+/* Parameters for object 'specific' operations */
+typedef struct H5VL_object_specific_args_t {
+    H5VL_object_specific_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_OBJECT_CHANGE_REF_COUNT */
+        struct {
+            int delta; /* Amount to modify object's refcount */
+        } change_rc;
+
+        /* H5VL_OBJECT_EXISTS */
+        struct {
+            hbool_t *exists; /* Whether object exists (OUT) */
+        } exists;
+
+        /* H5VL_OBJECT_LOOKUP */
+        struct {
+            H5O_token_t *token_ptr; /* Pointer to token for lookup (OUT) */
+        } lookup;
+
+        /* H5VL_OBJECT_VISIT */
+        H5VL_object_visit_args_t visit;
+
+        /* H5VL_OBJECT_FLUSH */
+        struct {
+            hid_t obj_id; /* Object ID (IN) */
+        } flush;
+
+        /* H5VL_OBJECT_REFRESH */
+        struct {
+            hid_t obj_id; /* Object ID (IN) */
+        } refresh;
+    } args;
+} H5VL_object_specific_args_t;
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, H5VL_object_optional_t opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, const H5VL_loc_params_t *loc_params, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
   \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
-  \texttt{opt\_type} & (IN): The type of operation.\\
+  \texttt{loc\_params} & (IN): Pointer to location parameters as explained in Section~\ref{sec:map}.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
   \texttt{dxpl\_id} & (IN): The data transfer property list.\\
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the get operation. \\
-\end{tabular}
-\end{mdframed}
-
-Each connector that requires connector-specific operations should be able to use the \texttt{opt\_type} parameter (a connector-specific enum/integer) to determine the type of the operation and parse the \texttt{va\_list arguments} appropriately.
+\end{tabular}
+\end{mdframed}
+
+Each connector that requires connector-specific operations should compare the
+value of the {\tt op\_type} field of the {\tt H5VL\_optional\_args\_t} struct
+with the values returned from calling {\tt H5VLregister\_opt\_operation} to
+determine how to handle the optional call and interpret the arguments passed
+in the struct.
 
@@
     herr_t (*get_conn_cls)(void *obj, H5VL_get_conn_lvl_t lvl, const struct H5VL_class_t **conn_cls);
+    herr_t (*get_cap_flags)(const void *info, unsigned *cap_flags);
     herr_t (*opt_query)(void *obj, H5VL_subclass_t cls, int opt_type, hbool_t *supported);
@@
   \texttt{cls} & (OUT): A const pointer to the connector.\\
+\end{tabular}
+\end{mdframed}
+
+\subsubsection{introspect: get\_cap\_flags}
+Get a connector's capability flags.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*get_cap_flags)(const void *info, unsigned *cap_flags);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{info} & (IN): A const pointer to pertinent VOL info.\\
+  \texttt{cap\_flags} & (OUT): A pointer to capability flags.\\
 \end{tabular}
@@
 typedef struct H5VL_request_class_t {
-    herr_t (*wait)(void *req, uint64_t timeout, H5ES_status_t *status);
+    herr_t (*wait)(void *req, uint64_t timeout, H5VL_request_status_t *status);
     herr_t (*notify)(void *req, H5VL_request_notify_t cb, void *ctx);
-    herr_t (*cancel)(void *req);
-    herr_t (*specific)(void *req, H5VL_request_specific_t specific_type, va_list arguments);
-    herr_t (*optional)(void *req, H5VL_request_optional_t opt_type, va_list arguments);
+    herr_t (*cancel)(void *req, H5VL_request_status_t *status);
+    herr_t (*specific)(void *req, H5VL_request_specific_args_t *args);
+    herr_t (*optional)(void *req, H5VL_optional_args_t *args);
     herr_t (*free)(void *req);
@@
 \begin{lstlisting}
-    herr_t (*specific)(void *req, H5VL_request_specific_t specific_type, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
-/* types for async request SPECIFIC callback */
+    herr_t (*specific)(void *req, H5VL_request_specific_args_t *args);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{req} & (IN): The async request on which to perform the operation.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for async request 'specific' operation */
 typedef enum H5VL_request_specific_t {
-    H5VL_REQUEST_WAITANY,               /* Wait until any request completes */   
-    H5VL_REQUEST_WAITSOME,              /* Wait until at least one requesst completes */
-    H5VL_REQUEST_WAITALL                /* Wait until all requests complete */   
+    H5VL_REQUEST_GET_ERR_STACK, /* Retrieve error stack for failed operation */
+    H5VL_REQUEST_GET_EXEC_TIME  /* Retrieve execution time for operation */
 } H5VL_request_specific_t;
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{req} & (IN): The async request on which to perform the operation.\\
-  \texttt{specific\_type} & (IN): The specific operation to perform.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
-\end{tabular}
-\end{mdframed}
+
+/* Parameters for request 'specific' operations */
+typedef struct H5VL_request_specific_args_t {
+    H5VL_request_specific_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_REQUEST_GET_ERR_STACK */
+        struct {
+            hid_t err_stack_id; /* Error stack ID for operation (OUT) */
+        } get_err_stack;
+
+        /* H5VL_REQUEST_GET_EXEC_TIME */
+        struct {
+            uint64_t *exec_ts;   /* Timestamp for start of task execution (OUT) */
+            uint64_t *exec_time; /* Duration of task execution (in ns) (OUT) */
+        } get_exec_time;
+    } args;
+} H5VL_request_specific_args_t;
+
+\end{lstlisting}
 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *req, H5VL_request_optional_t opt_type, va_list arguments);                            
+    herr_t (*optional)(void *req, H5VL_optional_args_t *args);                            
 \end{lstlisting}
@@
   \texttt{req} & (IN): The async request on which to perform the operation.\\
-  \texttt{opt\_type} & (IN): The type of operation.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
-\end{tabular}
-\end{mdframed}
-
-Each connector that requires connector-specific operations should be able to use the \texttt{opt\_type} parameter (a connector-specific enum/integer) to determine the type of the operation and parse the \texttt{va\_list arguments} appropriately.
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+\end{tabular}
+\end{mdframed}
+
+Each connector that requires connector-specific operations should compare the
+value of the {\tt op\_type} field of the {\tt H5VL\_optional\_args\_t} struct
+with the values returned from calling {\tt H5VLregister\_opt\_operation} to
+determine how to handle the optional call and interpret the arguments passed
+in the struct.
 
@@
     herr_t (*get)(void *obj, const void *blob_id, void *buf, size_t size, void *ctx);
-    herr_t (*specific)(void *obj, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);
-    herr_t (*optional)(void *obj, void *blob_id, H5VL_blob_optional_t opt_type, va_list arguments);             
+    herr_t (*specific)(void *obj, void *blob_id, H5VL_blob_specific_args_t *args);
+    herr_t (*optional)(void *obj, void *blob_id, H5VL_optional_args_t *args);
 } H5VL_blob_class_t; 
@@
 \begin{lstlisting}
-    herr_t (*specific)(void *obj, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);
-\end{lstlisting}
-
-The \texttt{specific\_type} argument is an \texttt{enum}:
-\begin{lstlisting}
+    herr_t (*specific)(void *obj, void *blob_id, H5VL_blob_specific_args_t *args);
+\end{lstlisting}
+
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  \texttt{obj} & (IN): Pointer to the blob container.\\
+  \texttt{blob\_id} & (IN): Pointer to the blob's connector-specific ID.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+\end{tabular}
+\end{mdframed}
+
+\begin{lstlisting}
+/* Values for 'blob' 'specific' operation */
 typedef enum H5VL_blob_specific_t {
     H5VL_BLOB_DELETE, /* Delete a blob (by ID) */
-    H5VL_BLOB_GETSIZE,                  /* Get size of blob */
     H5VL_BLOB_ISNULL, /* Check if a blob ID is "null" */
@@
 } H5VL_blob_specific_t;
+
+/* Parameters for blob 'specific' operations */
+typedef struct H5VL_blob_specific_args_t {
+    H5VL_blob_specific_t op_type; /* Operation to perform */
+
+    /* Parameters for each operation */
+    union {
+        /* H5VL_BLOB_DELETE */
+        /* No args */
+
+        /* H5VL_BLOB_ISNULL */
+        struct {
+            hbool_t *isnull; /* Whether blob ID is "null" (OUT) */
+        } is_null;
+
+        /* H5VL_BLOB_SETNULL */
+        /* No args */
+    } args;
+} H5VL_blob_specific_args_t;
+\end{lstlisting}
+
+\subsubsection{blob: optional}
+Perform a connector-specific operation on a blob via the VOL.
+
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+    herr_t (*optional)(void *obj, void *blob_id, H5VL_optional_args_t *args);             
 \end{lstlisting}
@@
   \texttt{blob\_id} & (IN): Pointer to the blob's connector-specific ID.\\
-  \texttt{specific\_type} & (IN): The operation to perform.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
-\end{tabular}
-\end{mdframed}
-
-\subsubsection{blob: optional}
-Perform a connector-specific operation on a blob via the VOL.
-
-\begin{mdframed}[style=bgbox]
-\textbf{Signature:}
-\begin{lstlisting}
-    herr_t (*optional)(void *obj, void *blob_id, H5VL_blob_optional_t opt_type, va_list arguments);             
-\end{lstlisting}
-
-\textbf{Arguments:}\\
-\begin{tabular}{l p{13.5cm}}
-  \texttt{obj} & (IN): Pointer to the blob container.\\
-  \texttt{blob\_id} & (IN): Pointer to the blob's connector-specific ID.\\
-  \texttt{opt\_type} & (IN): The type of operation.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
-\end{tabular}
-\end{mdframed}
-
-Each connector that requires connector-specific operations should be able to use the \texttt{opt\_type} parameter (a connector-specific enum/integer) to determine the type of the operation and parse the \texttt{va\_list arguments} appropriately.
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
+\end{tabular}
+\end{mdframed}
+
+Each connector that requires connector-specific operations should compare the
+value of the {\tt op\_type} field of the {\tt H5VL\_optional\_args\_t} struct
+with the values returned from calling {\tt H5VLregister\_opt\_operation} to
+determine how to handle the optional call and interpret the arguments passed
+in the struct.
 
@@
 \begin{lstlisting}
-    herr_t (*optional)(void *obj, int opt_type, hid_t dxpl_id, void **req, va_list arguments);
+    herr_t (*optional)(void *obj, H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 \end{lstlisting}
@@
   \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
-  \texttt{opt\_type} & (IN): The type of operation.\\
+  \texttt{args} & (IN/OUT): A pointer to the arguments struct.\\
   \texttt{dxpl\_id} & (IN): The data transfer property list.\\
   \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the operation created by the connector.\\
-  \texttt{arguments} & (IN/OUT): argument list containing parameters and output pointers for the operation. \\
 \end{tabular}

### 2021-10-01 RFCs/HDF5/VOL/connector_author_guide/new_api_calls.tex

@@
 \label{sec:api}
-New API routines have been added to the HDF5 library to manage VOL connectors.
+API routines have been added to the HDF5 library to manage VOL connectors.
 This section details each new API call and explains its intended usage.
@@
 
+\subsubsection{H5VLquery\_optional}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+herr_t H5VLquery_optional(hid_t obj_id, H5VL_subclass_t subcls, int opt_type, uint64_t *flags);
+\end{lstlisting}
+\textbf{Arguments:}\\
+\begin{tabular}{l p{13.5cm}}
+  {\tt obj\_id} & (IN): A valid identifier of a VOL-managed object.\\
+  {\tt subcls} & (IN): The subclass of the optional operation.\\
+  {\tt opt\_type} & (IN): The optional operation. The native VOL connector uses hard-coded values. Other VOL connectors get this value when the optional operations are registered.\\
+  {\tt flags} & (OUT): Bitwise flags indicating support and behavior.\\
+\end{tabular}
+\end{mdframed}
+Determines if a connector or connector stack (determined from the passed-in object) supports an optional operation.
+The returned flags (listed below) not only indicate whether the operation is supported or not, but also give a sense of the option's behavior (useful for pass-through connectors).
+
+Bitwise query flag values:
+\begin{lstlisting}
+#define H5VL_OPT_QUERY_SUPPORTED       0x0001 /* VOL connector supports this operation */
+#define H5VL_OPT_QUERY_READ_DATA       0x0002 /* Operation reads data for object */
+#define H5VL_OPT_QUERY_WRITE_DATA      0x0004 /* Operation writes data for object */
+#define H5VL_OPT_QUERY_QUERY_METADATA  0x0008 /* Operation reads metadata for object */
+#define H5VL_OPT_QUERY_MODIFY_METADATA 0x0010 /* Operation modifies metadata for object */
+#define H5VL_OPT_QUERY_COLLECTIVE                                                                            \
+    0x0020 /* Operation is collective (operations without this flag are assumed to be independent) */
+#define H5VL_OPT_QUERY_NO_ASYNC  0x0040 /* Operation may NOT be executed asynchronously */
+#define H5VL_OPT_QUERY_MULTI_OBJ 0x0080 /* Operation involves multiple objects */
+
+\end{lstlisting}
+\bigskip
+
 \subsection{H5VLconnector.h}
@@
 functions that are useful for writing connectors.
+
+API calls to manage optional operations are also found in this header file.
+These are discussed in the section on optional operations, above.
 
@@
 
-\subsubsection{H5VLpeek\_connector\_by\_name}
+\subsubsection{H5VLpeek\_connector\_id\_by\_name}
 \begin{mdframed}[style=bgbox]
@@
 
-\subsubsection{H5VLpeek\_connector\_by\_value}
+\subsubsection{H5VLpeek\_connector\_id\_by\_value}
 \begin{mdframed}[style=bgbox]
@@
 
+\subsubsection{H5VLstart\_lib\_state}
+\begin{mdframed}[style=bgbox]
+\textbf{Signature:}
+\begin{lstlisting}
+  herr_t H5VLstart_lib_state(void);
+\end{lstlisting}
+\end{mdframed}
+Opens a new internal state for the HDF5 library.
+Returns a positive value on success and a negative value on errors.
+\bigskip
+
 \subsubsection{H5VLrestore\_lib\_state}
@@
 
-\subsubsection{H5VLreset\_lib\_state}
+\subsubsection{H5VLfinish\_lib\_state}
 \begin{mdframed}[style=bgbox]
@@
 \begin{lstlisting}
-  herr_t H5VLreset_lib_state(void);
+  herr_t H5VLfinish_lib_state(void);
 \end{lstlisting}
 \end{mdframed}
-Resets the internal state of the HDF5 library, undoing the
-affects of H5VLrestore\_lib\_state.
-This routine must be called as a "pair" with
-{\tt H5VLrestore\_lib\_state}.  It can be called before, after, or
-independently of {\tt H5VLfree\_lib\_state}.
+Closes the state of the library, undoing the effects of {\tt H5VLstart\_lib\_state}.
 Returns a positive value on success and a negative value on errors.

### 2022-05-27 RFCs/HDF5/VOL/connector_author_guide/appendix.tex

--- 2019-11-25 RFCs/HDF5/VOL/connector_author_guide/appendix.tex
@@
              & H5Fis\_hdf5 (deprecated, hard-coded to use native connector) \\
-             & H5Fmount \\
              & H5Freopen \\
-             & H5Funmount \\
     \hline
@@
     \hline
-    specific & H5Gflush \\
+    specific & H5Fmount \\
+             & H5Funmount \\
+             & H5Gflush \\
              & H5Grefresh \\
@@
         & H5Dextend \\
-        & H5Dget\_offset \\
         & H5Dget\_space \\
@@
 
-/* Helper routines for VOL connector authors */                                  
-herr_t H5VLcmp_connector_cls(int *cmp, hid_t connector_id1, hid_t connector_id2);
-hid_t H5VLwrap_register(void *obj, H5I_type_t type);                      
-herr_t H5VLretrieve_lib_state(void **state);                              
-herr_t H5VLrestore_lib_state(const void *state);                          
-herr_t H5VLreset_lib_state(void);                                         
-herr_t H5VLfree_lib_state(void *state);
-
 /* Pass-through callbacks */
-void *H5VLget_object(void *obj, hid_t connector_id);                      
+void * H5VLget_object(void *obj, hid_t connector_id);
 herr_t H5VLget_wrap_ctx(void *obj, hid_t connector_id, void **wrap_ctx);
-void *H5VLwrap_object(void *obj, H5I_type_t obj_type, hid_t connector_id, void *wrap_ctx);                                                             
-void *H5VLunwrap_object(void *obj, hid_t connector_id);                   
+void * H5VLwrap_object(void *obj, H5I_type_t obj_type, hid_t connector_id, void *wrap_ctx);
+void * H5VLunwrap_object(void *obj, hid_t connector_id);
 herr_t H5VLfree_wrap_ctx(void *wrap_ctx, hid_t connector_id);
@@
 herr_t H5VLcopy_connector_info(hid_t connector_id, void **dst_vol_info, void *src_vol_info);
-herr_t H5VLcmp_connector_info(int *cmp, hid_t connector_id, const void *info1,
-    const void *info2);                                                          
+herr_t H5VLcmp_connector_info(int *cmp, hid_t connector_id, const void *info1, const void *info2);
 herr_t H5VLfree_connector_info(hid_t connector_id, void *vol_info);
@@
 /* Public wrappers for attribute callbacks */
-void *H5VLattr_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *attr_name, hid_t type_id, hid_t space_id, hid_t acpl_id, hid_t aapl_id, hid_t dxpl_id, void **req);
-void *H5VLattr_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t aapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLattr_read(void *attr, hid_t connector_id, hid_t dtype_id, void *buf, hid_t dxpl_id, void **req);
-herr_t H5VLattr_write(void *attr, hid_t connector_id, hid_t dtype_id, const void *buf, hid_t dxpl_id, void **req);
-herr_t H5VLattr_get(void *obj, hid_t connector_id, H5VL_attr_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLattr_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_attr_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLattr_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+void * H5VLattr_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                              const char *attr_name, hid_t type_id, hid_t space_id, hid_t acpl_id,
+                              hid_t aapl_id, hid_t dxpl_id, void **req);
+void * H5VLattr_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                            const char *name, hid_t aapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLattr_read(void *attr, hid_t connector_id, hid_t dtype_id, void *buf, hid_t dxpl_id,
+                            void **req);
+herr_t H5VLattr_write(void *attr, hid_t connector_id, hid_t dtype_id, const void *buf, hid_t dxpl_id,
+                             void **req);
+herr_t H5VLattr_get(void *obj, hid_t connector_id, H5VL_attr_get_args_t *args, hid_t dxpl_id,
+                           void **req);
+herr_t H5VLattr_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                                H5VL_attr_specific_args_t *args, hid_t dxpl_id, void **req);
+herr_t H5VLattr_optional(void *obj, hid_t connector_id, H5VL_optional_args_t *args, hid_t dxpl_id,
+                                void **req);
 herr_t H5VLattr_close(void *attr, hid_t connector_id, hid_t dxpl_id, void **req);
@@
 /* Public wrappers for dataset callbacks */
-void *H5VLdataset_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t lcpl_id, hid_t type_id, hid_t space_id, hid_t dcpl_id, hid_t dapl_id, hid_t dxpl_id, void **req);
-void *H5VLdataset_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLdataset_read(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, void *buf, void **req);
-herr_t H5VLdataset_write(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id, hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
-herr_t H5VLdataset_get(void *dset, hid_t connector_id, H5VL_dataset_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLdataset_specific(void *obj, hid_t connector_id, H5VL_dataset_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLdataset_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+void * H5VLdataset_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                                 const char *name, hid_t lcpl_id, hid_t type_id, hid_t space_id, hid_t dcpl_id,
+                                 hid_t dapl_id, hid_t dxpl_id, void **req);
+void * H5VLdataset_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                               const char *name, hid_t dapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLdataset_read(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id,
+                               hid_t file_space_id, hid_t plist_id, void *buf, void **req);
+herr_t H5VLdataset_write(void *dset, hid_t connector_id, hid_t mem_type_id, hid_t mem_space_id,
+                                hid_t file_space_id, hid_t plist_id, const void *buf, void **req);
+herr_t H5VLdataset_get(void *dset, hid_t connector_id, H5VL_dataset_get_args_t *args, hid_t dxpl_id,
+                              void **req);
+herr_t H5VLdataset_specific(void *obj, hid_t connector_id, H5VL_dataset_specific_args_t *args,
+                                   hid_t dxpl_id, void **req);
+herr_t H5VLdataset_optional(void *obj, hid_t connector_id, H5VL_optional_args_t *args, hid_t dxpl_id,
+                                   void **req);
 herr_t H5VLdataset_close(void *dset, hid_t connector_id, hid_t dxpl_id, void **req);
 
+/* Public wrappers for named datatype callbacks */
+void * H5VLdatatype_commit(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                                  const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id,
+                                  hid_t dxpl_id, void **req);
+void * H5VLdatatype_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                                const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLdatatype_get(void *dt, hid_t connector_id, H5VL_datatype_get_args_t *args, hid_t dxpl_id,
+                               void **req);
+herr_t H5VLdatatype_specific(void *obj, hid_t connector_id, H5VL_datatype_specific_args_t *args,
+                                    hid_t dxpl_id, void **req);
+herr_t H5VLdatatype_optional(void *obj, hid_t connector_id, H5VL_optional_args_t *args, hid_t dxpl_id,
+                                    void **req);
+herr_t H5VLdatatype_close(void *dt, hid_t connector_id, hid_t dxpl_id, void **req);
+
 /* Public wrappers for file callbacks */
-void *H5VLfile_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id, void **req);
-void *H5VLfile_open(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLfile_get(void *file, hid_t connector_id, H5VL_file_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLfile_specific(void *obj, hid_t connector_id, H5VL_file_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLfile_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+void * H5VLfile_create(const char *name, unsigned flags, hid_t fcpl_id, hid_t fapl_id, hid_t dxpl_id,
+                              void **req);
+void * H5VLfile_open(const char *name, unsigned flags, hid_t fapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLfile_get(void *file, hid_t connector_id, H5VL_file_get_args_t *args, hid_t dxpl_id,
+                           void **req);
+herr_t H5VLfile_specific(void *obj, hid_t connector_id, H5VL_file_specific_args_t *args, hid_t dxpl_id,
+                                void **req);
+herr_t H5VLfile_optional(void *obj, hid_t connector_id, H5VL_optional_args_t *args, hid_t dxpl_id,
+                                void **req);
 herr_t H5VLfile_close(void *file, hid_t connector_id, hid_t dxpl_id, void **req);
@@
 /* Public wrappers for group callbacks */
-void *H5VLgroup_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t lcpl_id, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
-void *H5VLgroup_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLgroup_get(void *obj, hid_t connector_id, H5VL_group_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLgroup_specific(void *obj, hid_t connector_id, H5VL_group_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLgroup_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+void * H5VLgroup_create(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                               const char *name, hid_t lcpl_id, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id,
+                               void **req);
+void * H5VLgroup_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                             const char *name, hid_t gapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLgroup_get(void *obj, hid_t connector_id, H5VL_group_get_args_t *args, hid_t dxpl_id,
+                            void **req);
+herr_t H5VLgroup_specific(void *obj, hid_t connector_id, H5VL_group_specific_args_t *args,
+                                 hid_t dxpl_id, void **req);
+herr_t H5VLgroup_optional(void *obj, hid_t connector_id, H5VL_optional_args_t *args, hid_t dxpl_id,
+                                 void **req);
 herr_t H5VLgroup_close(void *grp, hid_t connector_id, hid_t dxpl_id, void **req);
@@
 /* Public wrappers for link callbacks */
-herr_t H5VLlink_create(H5VL_link_create_type_t create_type, void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLlink_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLlink_move(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj, const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLlink_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_link_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLlink_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLlink_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLlink_create(H5VL_link_create_args_t *args, void *obj, const H5VL_loc_params_t *loc_params,
+                              hid_t connector_id, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLlink_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj,
+                            const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id,
+                            hid_t lapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLlink_move(void *src_obj, const H5VL_loc_params_t *loc_params1, void *dst_obj,
+                            const H5VL_loc_params_t *loc_params2, hid_t connector_id, hid_t lcpl_id,
+                            hid_t lapl_id, hid_t dxpl_id, void **req);
+herr_t H5VLlink_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                           H5VL_link_get_args_t *args, hid_t dxpl_id, void **req);
+herr_t H5VLlink_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                                H5VL_link_specific_args_t *args, hid_t dxpl_id, void **req);
+herr_t H5VLlink_optional(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                                H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 
 /* Public wrappers for object callbacks */
-void *H5VLobject_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5I_type_t *opened_type, hid_t dxpl_id, void **req);
-herr_t H5VLobject_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, const char *src_name, void *dst_obj, const H5VL_loc_params_t *loc_params2, const char *dst_name, hid_t connector_id, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
-herr_t H5VLobject_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_object_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLobject_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLobject_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+void * H5VLobject_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                              H5I_type_t *opened_type, hid_t dxpl_id, void **req);
+herr_t H5VLobject_copy(void *src_obj, const H5VL_loc_params_t *loc_params1, const char *src_name,
+                              void *dst_obj, const H5VL_loc_params_t *loc_params2, const char *dst_name,
+                              hid_t connector_id, hid_t ocpypl_id, hid_t lcpl_id, hid_t dxpl_id, void **req);
+herr_t H5VLobject_get(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                             H5VL_object_get_args_t *args, hid_t dxpl_id, void **req);
+herr_t H5VLobject_specific(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                                  H5VL_object_specific_args_t *args, hid_t dxpl_id, void **req);
+herr_t H5VLobject_optional(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id,
+                                  H5VL_optional_args_t *args, hid_t dxpl_id, void **req);
 
-/* Public wrappers for named datatype callbacks */                               
-void *H5VLdatatype_commit(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t type_id, hid_t lcpl_id, hid_t tcpl_id, hid_t tapl_id, hid_t dxpl_id, void **req);
-void *H5VLdatatype_open(void *obj, const H5VL_loc_params_t *loc_params, hid_t connector_id, const char *name, hid_t tapl_id, hid_t dxpl_id, void **req);
-herr_t H5VLdatatype_get(void *dt, hid_t connector_id, H5VL_datatype_get_t get_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLdatatype_specific(void *obj, hid_t connector_id, H5VL_datatype_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLdatatype_optional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
-herr_t H5VLdatatype_close(void *dt, hid_t connector_id, hid_t dxpl_id, void **req);
+/* Public wrappers for connector/container introspection callbacks */
+herr_t H5VLintrospect_get_conn_cls(void *obj, hid_t connector_id, H5VL_get_conn_lvl_t lvl,
+                                          const H5VL_class_t **conn_cls);
+herr_t H5VLintrospect_get_cap_flags(const void *info, hid_t connector_id, unsigned *cap_flags);
+herr_t H5VLintrospect_opt_query(void *obj, hid_t connector_id, H5VL_subclass_t subcls, int opt_type,
+                                       uint64_t *flags);
 
 /* Public wrappers for asynchronous request callbacks */
-herr_t H5VLrequest_wait(void *req, hid_t connector_id, uint64_t timeout, H5ES_status_t *status);
+herr_t H5VLrequest_wait(void *req, hid_t connector_id, uint64_t timeout,
+                               H5VL_request_status_t *status);
 herr_t H5VLrequest_notify(void *req, hid_t connector_id, H5VL_request_notify_t cb, void *ctx);
-herr_t H5VLrequest_cancel(void *req, hid_t connector_id);                 
-herr_t H5VLrequest_specific(void *req, hid_t connector_id, H5VL_request_specific_t specific_type, va_list arguments);
-herr_t H5VLrequest_optional(void *req, hid_t connector_id, va_list arguments);
+herr_t H5VLrequest_cancel(void *req, hid_t connector_id, H5VL_request_status_t *status);
+herr_t H5VLrequest_specific(void *req, hid_t connector_id, H5VL_request_specific_args_t *args);
+herr_t H5VLrequest_optional(void *req, hid_t connector_id, H5VL_optional_args_t *args);
 herr_t H5VLrequest_free(void *req, hid_t connector_id);
@@
 /* Public wrappers for blob callbacks */
-herr_t H5VLblob_put(void *obj, hid_t connector_id, const void *buf, size_t size, void *blob_id, void *ctx);
-herr_t H5VLblob_get(void *obj, hid_t connector_id, const void *blob_id, void *buf, size_t size, void *ctx);
-herr_t H5VLblob_specific(void *obj, hid_t connector_id, void *blob_id, H5VL_blob_specific_t specific_type, va_list arguments);
+herr_t H5VLblob_put(void *obj, hid_t connector_id, const void *buf, size_t size, void *blob_id,
+                           void *ctx);
+herr_t H5VLblob_get(void *obj, hid_t connector_id, const void *blob_id, void *buf, size_t size,
+                           void *ctx);
+herr_t H5VLblob_specific(void *obj, hid_t connector_id, void *blob_id,
+                                H5VL_blob_specific_args_t *args);
+herr_t H5VLblob_optional(void *obj, hid_t connector_id, void *blob_id, H5VL_optional_args_t *args);
+
+/* Public wrappers for token callbacks */
+herr_t H5VLtoken_cmp(void *obj, hid_t connector_id, const H5O_token_t *token1,
+                            const H5O_token_t *token2, int *cmp_value);
+herr_t H5VLtoken_to_str(void *obj, H5I_type_t obj_type, hid_t connector_id, const H5O_token_t *token,
+                               char **token_str);
+herr_t H5VLtoken_from_str(void *obj, H5I_type_t obj_type, hid_t connector_id, const char *token_str,
+                                 H5O_token_t *token);
 
 /* Public wrappers for generic 'optional' callback */
-herr_t H5VLoptional(void *obj, hid_t connector_id, hid_t dxpl_id, void **req, va_list arguments);
+herr_t H5VLoptional(void *obj, hid_t connector_id, H5VL_optional_args_t *args, hid_t dxpl_id,
+                           void **req);
+\end{lstlisting}
 
+\pagebreak
+
+\section{Native VOL Connector Optional Values By Subclass}
+\label{sec:C}
+
+\begin{lstlisting}
+/* H5VL_SUBCLS_ATTR */
+/* H5Aiterate (deprecated routine) */
+#define H5VL_NATIVE_ATTR_ITERATE_OLD 0
+
+/* H5VL_SUBCLS_DATASET */
+/* H5Dformat_convert (internal) */
+#define H5VL_NATIVE_DATASET_FORMAT_CONVERT          0  
+/* H5Dget_chunk_index_type */
+#define H5VL_NATIVE_DATASET_GET_CHUNK_INDEX_TYPE    1  
+/* H5Dget_chunk_storage_size */
+#define H5VL_NATIVE_DATASET_GET_CHUNK_STORAGE_SIZE  2  
+/* H5Dget_num_chunks */
+#define H5VL_NATIVE_DATASET_GET_NUM_CHUNKS          3  
+/* H5Dget_chunk_info */
+#define H5VL_NATIVE_DATASET_GET_CHUNK_INFO_BY_IDX   4  
+/* H5Dget_chunk_info_by_coord */
+#define H5VL_NATIVE_DATASET_GET_CHUNK_INFO_BY_COORD 5  
+/* H5Dchunk_read */
+#define H5VL_NATIVE_DATASET_CHUNK_READ              6  
+/* H5Dchunk_write */
+#define H5VL_NATIVE_DATASET_CHUNK_WRITE             7  
+/* H5Dvlen_get_buf_size */
+#define H5VL_NATIVE_DATASET_GET_VLEN_BUF_SIZE       8  
+/* H5Dget_offset */
+#define H5VL_NATIVE_DATASET_GET_OFFSET              9  
+/* H5Dget_offset */
+#define H5VL_NATIVE_DATASET_CHUNK_ITER              10
+
+/* H5VL_SUBCLS_FILE */
+/* H5Fclear_elink_file_cache */
+#define H5VL_NATIVE_FILE_CLEAR_ELINK_CACHE            0  
+/* H5Fget_file_image */
+#define H5VL_NATIVE_FILE_GET_FILE_IMAGE               1  
+/* H5Fget_free_sections */
+#define H5VL_NATIVE_FILE_GET_FREE_SECTIONS            2  
+/* H5Fget_freespace */
+#define H5VL_NATIVE_FILE_GET_FREE_SPACE               3  
+/* H5Fget_info1/2 */
+#define H5VL_NATIVE_FILE_GET_INFO                     4  
+/* H5Fget_mdc_config */
+#define H5VL_NATIVE_FILE_GET_MDC_CONF                 5  
+/* H5Fget_mdc_hit_rate */
+#define H5VL_NATIVE_FILE_GET_MDC_HR                   6  
+/* H5Fget_mdc_size */
+#define H5VL_NATIVE_FILE_GET_MDC_SIZE                 7  
+/* H5Fget_filesize */
+#define H5VL_NATIVE_FILE_GET_SIZE                     8  
+/* H5Fget_vfd_handle */
+#define H5VL_NATIVE_FILE_GET_VFD_HANDLE               9  
+/* H5Freset_mdc_hit_rate_stats */
+#define H5VL_NATIVE_FILE_RESET_MDC_HIT_RATE           10 
+/* H5Fset_mdc_config */
+#define H5VL_NATIVE_FILE_SET_MDC_CONFIG               11 
+/* H5Fget_metadata_read_retry_info */
+#define H5VL_NATIVE_FILE_GET_METADATA_READ_RETRY_INFO 12 
+/* H5Fstart_swmr_write */
+#define H5VL_NATIVE_FILE_START_SWMR_WRITE             13 
+/* H5Fstart_mdc_logging */
+#define H5VL_NATIVE_FILE_START_MDC_LOGGING            14 
+/* H5Fstop_mdc_logging */
+#define H5VL_NATIVE_FILE_STOP_MDC_LOGGING             15 
+/* H5Fget_mdc_logging_status */
+#define H5VL_NATIVE_FILE_GET_MDC_LOGGING_STATUS       16 
+/* H5Fformat_convert */
+#define H5VL_NATIVE_FILE_FORMAT_CONVERT               17 
+/* H5Freset_page_buffering_stats */
+#define H5VL_NATIVE_FILE_RESET_PAGE_BUFFERING_STATS   18 
+/* H5Fget_page_buffering_stats */
+#define H5VL_NATIVE_FILE_GET_PAGE_BUFFERING_STATS     19 
+/* H5Fget_mdc_image_info */
+#define H5VL_NATIVE_FILE_GET_MDC_IMAGE_INFO           20 
+/* H5Fget_eoa */
+#define H5VL_NATIVE_FILE_GET_EOA                      21 
+/* H5Fincrement_filesize */
+#define H5VL_NATIVE_FILE_INCR_FILESIZE                22 
+/* H5Fset_latest_format/libver_bounds */
+#define H5VL_NATIVE_FILE_SET_LIBVER_BOUNDS            23 
+/* H5Fget_dset_no_attrs_hint */
+#define H5VL_NATIVE_FILE_GET_MIN_DSET_OHDR_FLAG       24 
+/* H5Fset_dset_no_attrs_hint */
+#define H5VL_NATIVE_FILE_SET_MIN_DSET_OHDR_FLAG       25 
+/* H5Fget_mpi_atomicity */
+#define H5VL_NATIVE_FILE_GET_MPI_ATOMICITY 26 
+/* H5Fset_mpi_atomicity */
+#define H5VL_NATIVE_FILE_SET_MPI_ATOMICITY 27 
+/* Adjust file after open, with wrapping context */
+#define H5VL_NATIVE_FILE_POST_OPEN 28
+
+/* H5VL_SUBCLS_GROUP */
+/* HG5Giterate (deprecated routine) */
+#define H5VL_NATIVE_GROUP_ITERATE_OLD 0 
+/* HG5Gget_objinfo (deprecated routine) */
+#define H5VL_NATIVE_GROUP_GET_OBJINFO 1
+
+/* H5VL_SUBCLS_OBJECT */
+/* H5G|H5Oget_comment, H5Oget_comment_by_name */
+#define H5VL_NATIVE_OBJECT_GET_COMMENT              0 
+/* H5G|H5Oset_comment, H5Oset_comment_by_name */
+#define H5VL_NATIVE_OBJECT_SET_COMMENT              1 
+/* H5Odisable_mdc_flushes */
+#define H5VL_NATIVE_OBJECT_DISABLE_MDC_FLUSHES      2 
+/* H5Oenable_mdc_flushes */
+#define H5VL_NATIVE_OBJECT_ENABLE_MDC_FLUSHES       3 
+/* H5Oare_mdc_flushes_disabled */
+#define H5VL_NATIVE_OBJECT_ARE_MDC_FLUSHES_DISABLED 4 
+/* H5Oget_native_info(_by_idx, _by_name) */
+#define H5VL_NATIVE_OBJECT_GET_NATIVE_INFO          5 
 \end{lstlisting}

### 2022-05-27 RFCs/HDF5/VOL/connector_author_guide/writing_new.tex

@@
 
-\subsection{Sources Of Information}
+\subsection{The HDF5 1.12.x VOL Interface Is DEPRECATED}
+
+Important changes were made to the VOL interface for HDF5 1.13.0 and, due to
+binary compatibility issues, these cannot be merged to HDF5 1.12.x. For this
+reason, VOL connector development should be shifted to target 1.13.0 as no
+further development of the VOL interface will take place on the 1.12.x branch.
+Unlike the other development branches of the library, there is no
+{\tt hdf5\_1\_13} branch - all HDF5 1.13.0 development is taking place in
+the {\tt develop} branch of the HDF5 repository and 1.13.x branches will split
+off from that.
+
+Note also that HDF5 1.13.0 is considered an unstable branch, and the API and
+file format are subject to change ("unstable" means "not yet finalized", not "buggy").
+The VOL feature is under active development and, although it is nearing its final form,
+may change further before the stable HDF5 1.14.0 release targeted for 2022.
+
+\subsection{VOL-Related HDF5 Header Files}
 
@@
   \texttt{H5VLpublic.h} & Public VOL header.\\
-  \texttt{H5VLconnector.h} & Main connector author header. Contains definitions for the main VOL struct and callbacks, enum values, etc.\\
+  \texttt{H5VLconnector.h} & Main header for connector authors. Contains definitions for the main VOL struct and callbacks, enum values, etc.\\
   \texttt{H5VLconnector\_passthru.h} & Helper routines for passthrough connector authors.\\
@@
 
-Many VOL connectors can be found on The HDF Group's Bitbucket server, located at
-\url{https://bitbucket.hdfgroup.org/projects/HDF5VOL}. Not all of these VOL
-connectors are supported by THe HDF Group and the level of completeness varies,
-but the connectors found there can serve as examples of working implementations.
+Many VOL connectors are listed on The HDF Group's VOL plugin registration page,
+located at \url{https://portal.hdfgroup.org/display/support/Registered+VOL+Connectors}.
+Not all of these VOL connectors are supported by The HDF Group and the level
+of completeness varies, but the connectors found there can serve as examples
+of working implementations.
 
@@
 
-To show how easy this is to accomplish, here is the complete implementation
-of those functions in the template VOL connector:
-
-\begin{lstlisting}
-H5PL_type_t H5PLget_plugin_type(void) {return H5PL_TYPE_VOL;}
-const void *H5PLget_plugin_info(void) {return &template_class_g;}
-\end{lstlisting}
-
 The HDF5 library's plugin loading code will call {\tt H5PLget\_plugin\_type()}
@@
 \end{lstlisting}
+
+To show how easy this is to accomplish, here is the complete implementation
+of those functions in the template VOL connector:
+
+\begin{lstlisting}
+H5PL_type_t H5PLget_plugin_type(void) {return H5PL_TYPE_VOL;}
+const void *H5PLget_plugin_info(void) {return &template_class_g;}
+\end{lstlisting}
+
 {\tt H5PLget\_plugin\_type} should return the library type which should always be {\tt H5PL\_TYPE\_VOL}.
@@
 For example, consider an external plugin defined as:
+
 \begin{lstlisting}
-static const H5VL_class_t H5VL_log_g = {
-    1,	/* version */
-    502,	/* value */
-    "log",	/* name */
+static const H5VL_class_t H5VL_foo_g = {
+    2,      /* version */
+    12345,  /* value */
+    "foo",  /* name */
     ...
@@
 \end{lstlisting}
+
 The plugin would implement the two routines as:
@@
 H5PL_type_t H5PLget_plugin_type(void) {return H5PL_TYPE_VOL;}
-const void *H5PLget_plugin_info(void) {return &H5VL_log_g;}
+const void *H5PLget_plugin_info(void) {return &H5VL_foo_g;}
 \end{lstlisting}
@@
 
-We have created a template VOL connector that includes both Autotools and CMake
+We have created a template terminal VOL connector that includes both Autotools and CMake
 build files. The constructed VOL connector includes no real functionality, but 
@@
 
-\quad \quad \url{https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/template}
+\quad \quad \url{https://github.com/HDFGroup/vol-template}
 
@@
 
+A template passthrough VOL is also available. This will be discussed in the
+section on passthrough connectors.
+
 \subsection{{\tt H5VL\_class\_t} Boilerplate}
@@
 
-In HDF5 1.12.0, {\tt version} will be 1, indicating version 1 of the {\tt H5VL\_class\_t} struct.
+In HDF5 1.13.0, the {\tt version} field will be 2, indicating the connector
+targets version 2 of the {\tt H5VL\_class\_t} struct. Version 1 of the struct
+was never formally released and only available in the {\tt develop} branch of
+the HDF5 git repository. Version 0 is used in the deprecated HDF5 1.12.x branch.
 
@@
 0 to 255 are reserved for internal use by The HDF Group. The native VOL connector
-has a value of 0.
+has a value of 0. Values of 256 to 511 are for connector testing and should
+not be found in the wild. Values of 512 to 65535 are for external connectors.
 
-As is the case with HDF5 filters, The HDF Group can register the value you've
-chosen for your VOL connector so that others don't use it. Please contact
+As is the case with HDF5 filters, The HDF Group can assign you an official
+VOL connector value. Please contact
 \href{mailto:help@hdfgroup.org}{help@hdfgroup.org} for help with this. We currently
-do not register connector names.
+do not register connector names, though the name you've chosen will appear on
+the registered VOL connectors page.
 
-The {\tt cap\_flags} field is currently not fully utilized. In the future, this
-will be most likely be used to indicate which callbacks and capabilities are
-supported by the VOL connector, but for now this struct field contains few flags, 
-a list of which can be found in {\tt H5VLconnector.h}.
+As noted above, registered VOL connectors will be listed at:
+
+\url{https://portal.hdfgroup.org/display/support/Registered+VOL+Connectors}
+
+A new {\tt conn\_version} field has been added to the class struct for 1.13.
+This field is currently not used by the library so its use is determined by
+the connector author. Best practices for this field will be determined in
+the near future and this part of the guide will be updated.
+
+The {\tt cap\_flags} field is used to determine the capabilities of the VOL
+connector. At this time, the use of this field is limited to indicating
+thread-safety, asynchronous capabilities, and ability to produce native
+HDF5 files. Supported flags can be found in {\tt H5VLconnector.h}.
+
+\begin{lstlisting}
+/* Capability flags for connector */
+#define H5VL_CAP_FLAG_NONE         0    /* No special connector capabilities */
+#define H5VL_CAP_FLAG_THREADSAFE   0x01 /* Connector is threadsafe */
+#define H5VL_CAP_FLAG_ASYNC        0x02 /* Connector performs operations asynchronously*/
+#define H5VL_CAP_FLAG_NATIVE_FILES 0x04 /* Connector produces native file format */
+\end{lstlisting}
 
@@
 in the {\tt H5VL\_class\_t} struct to handle this. They are invoked when
-the connector is registered and unregistered, respectively. If this is
-unsuitable, you may have to create custom connector-specific API calls to handle
+the connector is registered and unregistered, respectively. The inialize
+callback can take a VOL initialization property list, so any properties you
+need for initialization can be applied to it. The HDF5 library currently makes
+no use of the vipl so there are no default vipl properties.
+
+If this is unsuitable, you may have to create custom connector-specific API calls to handle
 initialization and termination. It may also be useful to perform operations in
 a custom API call used to set the VOL connector in the fapl.
+
+The initialization and terminate callbacks:
+\begin{lstlisting}
+herr_t (*initialize)(hid_t vipl_id); /**< Connector initialization callback */
+
+herr_t (*terminate)(void);           /**< Connector termination callback */
+\end{lstlisting}
 
@@
 {\tt H5VL\_class\_t} struct.
+
+\subsection{Handling Optional Operations}
+
+Handling optional operations has changed significantly in HDF5 1.13.0. In the
+past, optional operations were specified using an integer {\tt opt\_type}
+parameter. This proved to be a problem with pass-through connectors, though,
+as it was possible to have {\tt opt\_type} clash if two connectors used
+the same {\tt opt\_type} values.
+
+The new scheme allows a connector to register an optional operation with
+the library and receive a dynamically-allocated {\tt opt\_type} value
+for the operation.
+
+The following API calls can be used to manage the optional operations:
+\begin{lstlisting}
+herr_t H5VLregister_opt_operation(H5VL_subclass_t subcls, const char *op_name, int *op_val);
+herr_t H5VLfind_opt_operation(H5VL_subclass_t subcls, const char *op_name, int *op_val);
+herr_t H5VLunregister_opt_operation(H5VL_subclass_t subcls, const char *op_name);
+\end{lstlisting}
+
+The {\tt register} call is used to register an operation for a subclass (file, etc.)
+and the {\tt opt\_type} parameter that the library assigned to the operation will be
+returned via the {\tt opt\_val} parameter. This value can then be passed to one
+of the subclass-specific API calls (listed below). If you need to find an existing
+optional call's assigned {\tt opt\_type} value by name, you can use the {\tt find}
+call.
+
+One recommended way to handle optional calls is to register all the optional calls
+at startup, saving the values in connector state, then use these cached values
+in your optional calls. The assigned values should be unregistered using the
+{\tt unregister} call when the connector shuts down.
+
+Subclass-specific optional calls:
+\begin{lstlisting}
+herr_t H5VLattr_optional_op(const char *app_file, const char *app_func, unsigned app_line,
+                            hid_t attr_id, H5VL_optional_args_t *args, hid_t dxpl_id, hid_t es_id);
+herr_t H5VLdataset_optional_op(const char *app_file, const char *app_func, unsigned app_line,
+                               hid_t dset_id, H5VL_optional_args_t *args, hid_t dxpl_id, hid_t es_id);
+herr_t H5VLdatatype_optional_op(const char *app_file, const char *app_func, unsigned app_line,
+                                hid_t type_id, H5VL_optional_args_t *args, hid_t dxpl_id, hid_t es_id);
+herr_t H5VLfile_optional_op(const char *app_file, const char *app_func, unsigned app_line,
+                            hid_t file_id, H5VL_optional_args_t *args, hid_t dxpl_id, hid_t es_id);
+herr_t H5VLgroup_optional_op(const char *app_file, const char *app_func, unsigned app_line,
+                             hid_t group_id, H5VL_optional_args_t *args, hid_t dxpl_id, hid_t es_id);
+herr_t H5VLlink_optional_op(const char *app_file, const char *app_func, unsigned app_line,
+                            hid_t loc_id, const char *name, hid_t lapl_id, H5VL_optional_args_t *args,
+                            hid_t dxpl_id, hid_t es_id);
+herr_t H5VLobject_optional_op(const char *app_file, const char *app_func, unsigned app_line,
+                              hid_t loc_id, const char *name, hid_t lapl_id,
+                              H5VL_optional_args_t *args, hid_t dxpl_id, hid_t es_id);
+herr_t H5VLrequest_optional_op(void *req, hid_t connector_id, H5VL_optional_args_t *args);
+\end{lstlisting}
+
 \subsection{Testing Your Connector}
@@
 
-\quad \quad \url{https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/vol-tests}
+\quad \quad \url{https://github.com/HDFGroup/vol-tests}
 
@@
 
+\subsection{Asynchronous Operations}
+
+Coming Soon
+
 %%% Local Variables: 

### 2023-01-27 RFCs/HDF5_Library/VFD_Subfiling/user_guide/appendices/ref_manual.tex
Add Subfiling VFD user guide

\documentclass[../main.tex]{subfiles}

\begin{document}

\section{Reference Manual}

The section contains a list of the C APIs related to the Subfiling feature. The Fortran APIs have similar signatures and can be found online in the HDF5 Reference Manual.

\label{apdx:ref_manual}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Function Name
\subsection{H5Pset\_fapl\_subfiling}
\label{ref:h5p_set_fapl_subfiling}

% Function
\paragraph{Synopsis:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
herr_t H5Pset_fapl_subfiling(hid_t fapl_id,
                             const H5FD_subfiling_config_t * vfd_config);
\end{minted}
\end{flushleft}%

% Purpose
\paragraph{Purpose:}
\begin{flushleft}%
Sets the Subfiling \Gls{VFD} on a \Gls{FAPL}.
\end{flushleft}%

% Description
\paragraph{Description:}
\begin{flushleft}%
\texttt{H5Pset\_fapl\_subfiling} modifies the given \Gls{FAPL} to use the
Subfiling \Gls{VFD}. Configuration for the File Driver is provided by a
pointer to a \texttt{H5FD\_subfiling\_config\_t} structure (\ref{ref:h5fd_subfiling_config_t}).
MPI must have been initialized within the HDF5 application using \texttt{MPI\_Init\_thread}
with the \texttt{MPI\_THREAD\_MULTIPLE} flag prior to calling this routine. Any
special MPI Communicator and MPI Info parameters must also have been set on
the given FAPL using the \texttt{H5P\_set\_mpi\_params} routine prior to calling
this routine.
\end{flushleft}%

% Parameters
\paragraph{Parameters:}
\begin{flushleft}%
 \begin{tabular}{lp{0.4\textwidth}}%
   \texttt{hid\_t fapl\_id} & IN: \Gls{FAPL} ID \\
   \texttt{const H5FD\_subfiling\_config\_t * vfd\_config} & IN: Pointer to Subfiling VFD configuration structure. May be NULL. \\
 \end{tabular}%
\end{flushleft}%

% Return
\paragraph{Returns:}
\begin{flushleft}%
Returns a non-negative value if successful; otherwise returns a negative value.
\end{flushleft}%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Function Name
\subsection{H5Pget\_fapl\_subfiling}
\label{ref:h5p_get_fapl_subfiling}

% Function
\paragraph{Synopsis:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
herr_t H5Pget_fapl_subfiling(hid_t fapl_id,
                             H5FD_subfiling_config_t * config_out);
\end{minted}
\end{flushleft}%

% Purpose
\paragraph{Purpose:}
\begin{flushleft}%
Retrieves the Subfiling \Gls{VFD} configuration set on the given \Gls{FAPL}.
\end{flushleft}%

% Description
\paragraph{Description:}
\begin{flushleft}%
\texttt{H5Pget\_fapl\_subfiling} returns the Subfiling configuration set on
the given \Gls{FAPL} through the provided \texttt{H5FD\_subfiling\_config\_t}
structure pointer. If no such configuration has been set on the given FAPL,
a default Subfiling configuration is returned. An HDF5 application may use
this functionality to configure the Subfiling VFD by obtaining a default
configuration through calling \texttt{H5Pget\_fapl\_subfiling} on a newly-created
\Gls{FAPL}, adjusting the default values and then calling \texttt{H5Pset\_fapl\_subfiling}
with the configured \texttt{H5FD\_subfiling\_config\_t} structure.

\textbf{NOTE:} \texttt{H5Pget\_fapl\_subfiling} only returns the Subfiling
configuration parameters as set by calling \texttt{H5Pset\_fapl\_subfiling}.
Any configuration parameters set through the use of environment variables
will not be reflected in the configuration returned by this routine, so an
application may need to check those environment variables to get accurate
values for the Subfiling VFD configuration.
\end{flushleft}%

% Parameters
\paragraph{Parameters:}
\begin{flushleft}%
 \begin{tabular}{lp{0.4\textwidth}}%
   \texttt{hid\_t fapl\_id} & IN: \Gls{FAPL} ID \\
   \texttt{H5FD\_subfiling\_config\_t * config\_out} & OUT: Pointer to
   Subfiling VFD configuration structure \ through which the Subfiling VFD configuration
   information will be returned. \\
 \end{tabular}%
\end{flushleft}%

% Return
\paragraph{Returns:}
\begin{flushleft}%
Returns a non-negative value if successful; otherwise returns a negative value.
\end{flushleft}%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Function Name
\subsection{H5Pset\_fapl\_ioc}
\label{ref:h5p_set_fapl_ioc}

% Function
\paragraph{Synopsis:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
herr_t H5Pset_fapl_ioc(hid_t fapl_id,
                       H5FD_ioc_config_t * vfd_config);
\end{minted}
\end{flushleft}%

% Purpose
\paragraph{Purpose:}
\begin{flushleft}%
Sets the "IOC" I/O Concentrator \Gls{VFD} on a \Gls{FAPL}.
\end{flushleft}%

% Description
\paragraph{Description:}
\begin{flushleft}%
\texttt{H5Pset\_fapl\_ioc} modifies the given \Gls{FAPL} to use the
"IOC" I/O Concentrator \Gls{VFD}. Configuration for the File Driver
is provided by a pointer to a \texttt{H5FD\_ioc\_config\_t} structure
(\ref{ref:h5fd_ioc_config_t}).
\end{flushleft}%

% Parameters
\paragraph{Parameters:}
\begin{flushleft}%
 \begin{tabular}{lp{0.5\textwidth}}%
   \texttt{hid\_t fapl\_id} & IN: \Gls{FAPL} ID \\
   \texttt{H5FD\_ioc\_config\_t * vfd\_config} & IN: Pointer to
   "IOC" I/O Concentrator VFD configuration structure. May be NULL. \\
 \end{tabular}%
\end{flushleft}%

% Return
\paragraph{Returns:}
\begin{flushleft}%
Returns a non-negative value if successful; otherwise returns a negative value.
\end{flushleft}%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Function Name
\subsection{H5Pget\_fapl\_ioc}
\label{ref:h5p_get_fapl_ioc}

% Function
\paragraph{Synopsis:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
herr_t H5Pget_fapl_ioc(hid_t fapl_id,
                       H5FD_ioc_config_t * config_out);
\end{minted}
\end{flushleft}%

% Purpose
\paragraph{Purpose:}
\begin{flushleft}%
Retrieves the "IOC" I/O Concentrator \Gls{VFD} configuration set on the given \Gls{FAPL}.
\end{flushleft}%

% Description
\paragraph{Description:}
\begin{flushleft}%
\texttt{H5Pget\_fapl\_ioc} returns the "IOC" I/O Concentrator configuration set
on the given \Gls{FAPL} through the provided \texttt{H5FD\_ioc\_config\_t}
structure pointer. If no such configuration has been set on the given FAPL,
a default "IOC" I/O Concentrator configuration is returned. An HDF5 application
may use this functionality to configure the "IOC" I/O Concentrator VFD by obtaining
a default configuration through calling \texttt{H5Pget\_fapl\_ioc} on a newly-created
\Gls{FAPL}, adjusting the default values and then calling \texttt{H5Pset\_fapl\_ioc}
with the configured \texttt{H5FD\_ioc\_config\_t} structure.

\textbf{NOTE:} \texttt{H5Pget\_fapl\_ioc} only returns the "IOC" I/O Concentrator
configuration parameters as set by calling \texttt{H5Pset\_fapl\_ioc}. Any
configuration parameters set through the use of environment variables will not
be reflected in the configuration returned by this routine, so an application may
need to check those environment variables to get accurate values for the "IOC" I/O
Concentrator VFD configuration.
\end{flushleft}%

% Parameters
\paragraph{Parameters:}
\begin{flushleft}%
 \begin{tabular}{lp{0.5\textwidth}}%
   \texttt{hid\_t fapl\_id} & IN: \Gls{FAPL} ID \\
   \texttt{H5FD\_ioc\_config\_t * config\_out} & OUT: Pointer to
   "IOC" I/O Concentrator VFD configuration structure through which the "IOC" I/O Concentrator
   VFD configuration information will be returned. \\
 \end{tabular}%
\end{flushleft}%

% Return
\paragraph{Returns:}
\begin{flushleft}%
Returns a non-negative value if successful; otherwise returns a negative value.
\end{flushleft}%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{H5FD\_subfiling\_config\_t}
\label{ref:h5fd_subfiling_config_t}

\paragraph{Type declaration:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
typedef struct H5FD_subfiling_config_t {
    uint32_t magic;
    uint32_t version;
    hid_t    ioc_fapl_id;
    hbool_t  require_ioc;
    H5FD_subfiling_params_t shared_cfg;
} H5FD_subfiling_config_t;
\end{minted}
\end{flushleft}%

\paragraph{Purpose:}
\begin{flushleft}%
Subfiling configuration structure provided to the \texttt{H5Pset\_fapl\_subfiling} API routine
\end{flushleft}%

\paragraph{Description of fields:}
\begin{flushleft}%
\texttt{uint32\_t magic} - This field is a "magic" number used for Subfiling configuration
verification and must currently always be set to the value represented by the
\texttt{H5FD\_SUBFILING\_FAPL\_MAGIC} macro.

\texttt{uint32\_t version} - This field is the version number of the Subfiling configuration
structure and should currently always be set to the value represented by the
\texttt{H5FD\_SUBFILING\_CURR\_FAPL\_VERSION} macro.

\texttt{hid\_t ioc\_fapl\_id} - This field is the ID of the \Gls{FAPL} that the Subfiling VFD
will use for accessing subfiles and must be setup with an I/O Concentrator VFD in order for
the Subfiling VFD to operate properly. Currently, this FAPL will be setup with the "IOC" VFD
by default and shouldn't be modified, but future work may allow other I/O Concentrator VFDs to
be set on this FAPL instead of the default reference implementation VFD.

\texttt{hbool\_t require\_ioc} - This field determines whether the Subfiling VFD should require
an underlying I/O Concentrator VFD and should currently always be set to \texttt{true}.

\texttt{H5FD\_subfiling\_params\_t shared\_cfg} - This field is a structure that contains the
various parameters for the Subfiling VFD, such as the data stripe size, number of subfiles to
be used, etc. Refer to \ref{ref:h5fd_subfiling_params_t} for information about its fields.
\end{flushleft}%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{H5FD\_subfiling\_params\_t}
\label{ref:h5fd_subfiling_params_t}

\paragraph{Type declaration:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
typedef struct H5FD_subfiling_params_t {
    H5FD_subfiling_ioc_select_t ioc_selection;
    int64_t                     stripe_size;
    int32_t                     stripe_count;
} H5FD_subfiling_params_t;
\end{minted}
\end{flushleft}%

\paragraph{Purpose:}
\begin{flushleft}%
Structure containing various parameters for the Subfiling VFD
\end{flushleft}%

\paragraph{Description of fields:}
\begin{flushleft}%
\texttt{H5FD\_subfiling\_ioc\_select\_t ioc\_selection} - This field is an enumeration that
determines how the Subfiling VFD chooses MPI ranks, threads, etc. as I/O Concentrators. Refer
to \ref{ref:h5fd_subfiling_ioc_select_t} for information about its defined values.

\texttt{int64\_t stripe\_size} - This field contains the size (in bytes) of data stripes
written to subfiles. The default setting for this parameter is a 32MiB stripe size. The value
must be $> 0$.

\texttt{int32\_t stripe\_count} - This field contains the target number of subfiles to use.
The default setting for this parameter is set such that one subfile is used per machine node.
The value must be $> 0$.
\end{flushleft}%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{H5FD\_subfiling\_ioc\_select\_t}
\label{ref:h5fd_subfiling_ioc_select_t}

\paragraph{Type declaration:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
typedef enum {
    SELECT_IOC_ONE_PER_NODE = 0,
    SELECT_IOC_EVERY_NTH_RANK,
    SELECT_IOC_WITH_CONFIG,
    SELECT_IOC_TOTAL,
    ioc_selection_options
} H5FD_subfiling_ioc_select_t;
\end{minted}
\end{flushleft}%

\paragraph{Purpose:}
\begin{flushleft}%
Enumeration containing the values for different methods of selection I/O Concentrators
\end{flushleft}%

\paragraph{Description of values:}
\begin{flushleft}%
\texttt{SELECT\_IOC\_ONE\_PER\_NODE} - The default I/O Concentrator selection method. I/O
Concentrators will be selected such that only one is assigned per machine node. If this
selection method is specified, the \texttt{H5FD\_SUBFILING\_IOC\_PER\_NODE} environment
variable can be used to adjust the number of I/O Concentrators assigned per machine node.

\texttt{SELECT\_IOC\_EVERY\_NTH\_RANK} - I/O Concentrators will be selected such that an
initial I/O Concentrator is selected from the available candidates and then each following
I/O Concentrator is selected by applying a stride value \texttt{N}. For example, if I/O
Concentrators are MPI ranks, MPI rank 0 will be the first I/O Concentrator and then the
next I/O Concentrator will be MPI rank \texttt{N} and so on. The default value for
\texttt{N} is 1 and can be adjusted with the \texttt{H5FD\_SUBFILING\_IOC\_SELECTION\_CRITERIA}
environment variable.

\texttt{SELECT\_IOC\_WITH\_CONFIG} - This method of I/O Concentrator selection is currently
unsupported.

\texttt{SELECT\_IOC\_TOTAL} - I/O Concentrators will be selected such that a total number
\texttt{N} of I/O Concentrators are assigned. A fixed stride value is applied when selecting
I/O Concentrators so that they are evenly spaced across the set of available candidates. The
default value for \texttt{N} is one and can be adjusted with the
\texttt{H5FD\_SUBFILING\_IOC\_SELECTION\_CRITERIA} environment variable.

\texttt{ioc\_selection\_options} - This is a sentinel value and should not be used.
\end{flushleft}%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{H5FD\_ioc\_config\_t}
\label{ref:h5fd_ioc_config_t}

\paragraph{Type declaration:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
typedef struct H5FD_ioc_config_t {
    uint32_t magic;
    uint32_t version;
    int32_t  thread_pool_size;
} H5FD_ioc_config_t;
\end{minted}
\end{flushleft}%

\paragraph{Purpose:}
\begin{flushleft}%
"IOC" I/O Concentrator VFD configuration structure provided to the \texttt{H5Pset\_fapl\_ioc}
API routine
\end{flushleft}%

\paragraph{Description of fields:}
\begin{flushleft}%
\texttt{uint32\_t magic} - This field is a "magic" number used for "IOC" I/O Concentrator VFD
configuration verification and must currently always be set to the value represented by the
\texttt{H5FD\_IOC\_FAPL\_MAGIC} macro.

\texttt{uint32\_t version} - This field is the version number of the "IOC" I/O Concentrator VFD
configuration structure and should currently always be set to the value represented by the
\texttt{H5FD\_IOC\_CURR\_FAPL\_VERSION} macro.

\texttt{int32\_t thread\_pool\_size} - This field contains the number of worker threads to
use per I/O Concentrator. The default setting for this parameter is 4 worker threads per I/O
Concentrator. The value must be $> 0$.
\end{flushleft}%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{H5FD\_SUBFILING\_FILENAME\_TEMPLATE}
\label{ref:h5fd_subfiling_filename_template}

\paragraph{Macro declaration:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
#define H5FD_SUBFILING_FILENAME_TEMPLATE "%s.subfile_%" PRIu64 "_%0*d_of_%d"
\end{minted}
\end{flushleft}%

\paragraph{Description:}
\begin{flushleft}%
This is a convenience macro for external tooling that defines the printf-style
format template used to generate the filenames for subfiles. Its format specifiers
are as follows:

\begin{verbatim}
%s      -> base filename, e.g. "file.h5"
%PRIu64 -> file inode, e.g. 11273556
%0*d    -> number (starting at 1) signifying the Nth (out of total
           number of subfiles) subfile. Zero-padded according
           to the number of digits in the number of subfiles
           (calculated by log10(num_subfiles) + 1)
%d      -> number of subfiles
\end{verbatim}

yielding filenames such as:

\begin{verbatim}
file.h5.subfile_11273556_01_of_10
file.h5.subfile_11273556_02_of_10
file.h5.subfile_11273556_10_of_10
\end{verbatim}
\end{flushleft}%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{H5FD\_SUBFILING\_CONFIG\_FILENAME\_TEMPLATE}
\label{ref:h5fd_subfiling_config_filename_template}

\paragraph{Macro declaration:}
\begin{flushleft}%
\begin{minted}[breaklines=true,fontsize=\small]{hdf5-c-lexer.py:HDF5CLexer -x}
#define H5FD_SUBFILING_CONFIG_FILENAME_TEMPLATE "%s.subfile_%" PRIu64 ".config"
\end{minted}
\end{flushleft}%

\paragraph{Description:}
\begin{flushleft}%
This is a convenience macro for external tooling that defines the printf-style
format template used to generate a Subfiling configuration file. Its format specifiers
are as follows:

\begin{verbatim}
%s      -> base filename, e.g. "file.h5"
%PRIu64 -> file inode, e.g. 11273556
\end{verbatim}

yielding a filename such as:

\begin{verbatim}
file.h5.subfile_11273556.config
\end{verbatim}
\end{flushleft}%

\newpage

\end{document}

### 2023-01-27 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/usage.tex
Add Subfiling VFD user guide

\documentclass[../main.tex]{subfiles}

\begin{document}

\newpage

\section{Usage}

\subsection{Building}

Before enabling the Subfiling VFD, it has a few requirements that have to be
satisfied:

\begin{itemize}
\item The VFD requires that HDF5 is built with parallel support using an MPI
implementation that supports at least the MPI-3 standard,

\item The VFD requires a C11-compliant compiler since it currently makes use
of the C11 atomic type primitives from \texttt{stdatomic.h},

\item The VFD is officially only supported on Linux systems due to
the direct use of pthreads for threading. While the VFD may work under
MinGW or similar, this is not tested.
\end{itemize}

If these requirements are satisfied, the Subfiling VFD can be enabled by building using either CMake, Section \ref{subsubsec:cmake}, or Autotools, Section  \ref{subsubsec:autotools}. HDF5
will check for these requirements and then build the VFD into the library.

\subsubsection{\label{subsubsec:cmake}CMake}

\begin{minted}{bash}
cmake -DHDF5_ENABLE_PARALLEL=ON -DHDF5_ENABLE_SUBFILING_VFD=ON ..
\end{minted}

\subsubsection{\label{subsubsec:autotools}Autotools}

\begin{minted}{bash}
./configure --enable-parallel --enable-subfiling-vfd=yes
\end{minted}

\subsection{Loading}

To load and use the Subfiling VFD within an HDF5 application, a few steps must
first be taken to ensure proper operation.

\subsubsection{Initialize MPI with MPI\_THREAD\_MULTIPLE threading support}
\label{sec:req1}

The Subfiling VFD uses a combination of MPI and threading internally to achieve
its purpose. This means that a parallel HDF5 application wishing to use the
Subfiling VFD should call \texttt{MPI\_Init\_thread} (rather than \texttt{MPI\_Init})
at the beginning of the application. Further, any particular thread created by the
VFD may make MPI calls at any time, so the VFD requires that MPI is initialized
with support for this behavior by passing the \texttt{MPI\_THREAD\_MULTIPLE}
flag to \texttt{MPI\_Init\_thread}. See \ref{ex:ex1} for a minimal example of
using the Subfiling VFD which does this. After calling \texttt{MPI\_Init\_thread},
the application should always check that the level of threading support provided
by the MPI implementation is at least \texttt{MPI\_THREAD\_MULTIPLE} before
attempting to use the VFD. For example:

\begin{minted}{hdf5-c-lexer.py:HDF5CLexer -x}
int
main(int argc, char **argv)
{
    int mpi_thread_required = MPI_THREAD_MULTIPLE;
    int mpi_thread_provided = 0;

    if (MPI_SUCCESS != MPI_Init_thread(&argc, &argv,
                                       mpi_thread_required,
                                       &mpi_thread_provided))
        return -1;

    if (mpi_thread_provided < mpi_thread_required)
        return -1;

    ...

    MPI_Finalize();

    return 0;
}
\end{minted}

Failing to perform this check may result in odd and difficult to diagnose errors
when the MPI implementation doesn't provide the \texttt{MPI\_THREAD\_MULTIPLE}
level of threading support.

\textbf{NOTE:} If using MPICH for an MPI implementation, it may be necessary on
some systems to set the \texttt{MPICH\_MAX\_THREAD\_SAFETY} environment variable
to "multiple", as in:

\begin{minted}{bash}
export MPICH_MAX_THREAD_SAFETY=multiple
\end{minted}

in order to have access to the required \texttt{MPI\_THREAD\_MULTIPLE} level of
threading support when calling \texttt{MPI\_Init\_thread}.

\subsubsection{Set any MPI parameters}
\label{sec:req2}

The Subfiling VFD checks for any specially set MPI parameters during initialization,
so if the HDF5 application needs to use a special MPI Communicator and/or MPI Info
object, it should make use of the \texttt{H5Pset\_mpi\_params} API routine to set
those MPI parameters on a \Gls{FAPL} to be used for file access before making calls
to any Subfiling VFD-related API routines. In the absence of any specially set MPI
parameters, the Subfiling VFD will default to using \texttt{MPI\_COMM\_WORLD} for the
MPI Communicator and \texttt{MPI\_INFO\_NULL} for the MPI Info object.

\begin{minted}{hdf5-c-lexer.py:HDF5CLexer -x}
hid_t fapl_id = H5Pcreate(H5P_FILE_ACCESS);
/* Set any special MPI parameters */
H5Pset_mpi_params(fapl_id, MPI_COMM_WORLD, MPI_INFO_NULL);
\end{minted}

\subsubsection{Set Subfiling VFD on a FAPL}

Once these initial steps have been performed within an HDF5 application, using
the Subfiling VFD simply entails setting up a \Gls{FAPL} with Subfiling VFD access,
as in:

\begin{minted}{hdf5-c-lexer.py:HDF5CLexer -x}
hid_t fapl_id = H5Pcreate(H5P_FILE_ACCESS);
/* Set any special MPI parameters */
H5Pset_mpi_params(fapl_id, MPI_COMM_WORLD, MPI_INFO_NULL);
/* Optional Subfiling configuration can be provided rather than NULL */
H5Pset_fapl_subfiling(fapl_id, NULL);
hid_t file_id = H5Fcreate("file.h5", H5F_ACC_TRUNC, H5P_DEFAULT, fapl_id);
\end{minted}

See sections \ref{ex:ex1} and \ref{ex:ex2} for minimal examples of using the Subfiling VFD with
default and custom configurations.

\subsubsection{Load by environment variable}

Though mostly for testing purposes, the Subfiling VFD can also be loaded by setting
the \texttt{HDF5\_DRIVER} environment variable, as in:

\begin{minted}{bash}
export HDF5_DRIVER=subfiling
\end{minted}

When the Subfiling VFD is loaded this way, the only way to configure the VFD in a non-default
manner is through the use of environment variables, as described in section \ref{sec:envvars}.

\textbf{NOTE:} The HDF5 application must still fulfill the requirements in the previous
sections (\ref{sec:req1} and \ref{sec:req2}) to load the Subfiling VFD in this manner.

\subsection{Configuring}

There are two main ways to configure the Subfiling VFD: providing a Subfiling configuration
structure to the \texttt{H5Pset\_fapl\_subfiling} API routine or setting environment variables.

\subsubsection{By File Access Property List}

The \texttt{H5Pset\_fapl\_subfiling} API routine accepts a pointer to a \texttt{H5FD\_subfiling\_config\_t}
structure for configuration (defined in \ref{ref:h5fd_subfiling_config_t}). If this parameter
is \texttt{NULL}, the Subfiling VFD will use the default settings of:

\begin{itemize}
\item Default "IOC" VFD used for the I/O Concentrator VFD
\item 32MiB data stripe size
\item 1 I/O Concentrator per machine node
\item 4 worker threads per I/O Concentrator
\end{itemize}

\subsubsection{By environment variables}
\label{sec:envvars}

The Subfiling VFD can also be configured with a few different environment variables that
generally take precedence over any Subfiling configuration parameters set on a FAPL:

\begin{itemize}
\item \texttt{H5FD\_SUBFILING\_STRIPE\_SIZE} - This environment variable controls the size of
the data stripes written to subfiles. It is interpreted as a \texttt{long long} value and must
be $> 0$.

\item \texttt{H5FD\_SUBFILING\_IOC\_PER\_NODE} - This environment variable controls the number
of I/O Concentrators that will be assigned to each machine node. It is interpreted as a \texttt{long}
value and must be $> 0$.

\item \texttt{H5FD\_SUBFILING\_IOC\_SELECTION\_CRITERIA} - This environment variable is intended
to be used in conjunction with the I/O Concentrator selection method specified in a Subfiling
configuration structure set on a \Gls{FAPL}. It enables the user to specify extra criteria for
how the Subfiling VFD should operate when selection I/O Concentrators. Refer to
\href{https://github.com/HDFGroup/hdf5/blob/develop/src/H5FDsubfiling/H5FDsubfiling.h}{the Subfiling VFD header}
for more information on allowed values for this environment variable.

\item \texttt{H5FD\_SUBFILING\_SUBFILE\_PREFIX} - This environment variable allows setting of a
prefix that is prepended to the filenames generated for subfiles. It is interpreted as a string
value.

\item \texttt{H5FD\_IOC\_THREAD\_POOL\_SIZE} - This environment variable controls the number of
worker threads per I/O Concentrator. It is interpreted as an \texttt{int} value and must be $> 0$.
\end{itemize}

\subsection{Minimal example}

The following is a minimal example of creating a Subfiling-based HDF5 file
with the default Subfiling configuration of a 32MiB stripe size, 1 I/O Concentrator
per machine node and 4 worker threads per I/O Concentrator.

\label{ex:ex1}
\begin{minted}{hdf5-c-lexer.py:HDF5CLexer -x}
#include "hdf5.h"

int
main(int argc, char **argv)
{
    MPI_Comm comm = MPI_COMM_WORLD;
    MPI_Info info = MPI_INFO_NULL;
    hid_t    file_id = H5I_INVALID_HID;
    hid_t    fapl_id = H5I_INVALID_HID;
    int      mpi_thread_required = MPI_THREAD_MULTIPLE;
    int      mpi_thread_provided = 0;

    /* Initialize MPI with threading support */
    MPI_Init_thread(&argc, &argv, mpi_thread_required, &mpi_thread_provided);
    if (mpi_thread_provided != mpi_thread_required)
        MPI_Abort(comm, -1);

    /*
     * Set up File Access Property List with MPI
     * parameters for the Subfiling VFD to use
     */
    fapl_id = H5Pcreate(H5P_FILE_ACCESS);
    H5Pset_mpi_params(fapl_id, comm, info);

    /*
     * Set Subfiling VFD on FAPL using default settings
     * (use IOC VFD, 1 IOC per node, 32MiB stripe size)
     */
    H5Pset_fapl_subfiling(fapl_id, NULL);

    /*
     * Create a new Subfiling-based HDF5 file
     */
    file_id = H5Fcreate("my_h5_file.h5", H5F_ACC_TRUNC, H5P_DEFAULT, fapl_id);

    /* Close/free resources */
    H5Pclose(fapl_id);
    H5Fclose(file_id);

    MPI_Finalize();

    return 0;
}
\end{minted}

\subsection{Minimal example with custom Subfiling configuration}

The following is a minimal example of creating a Subfiling-based HDF5 file
with a custom Subfiling configuration of a 1MiB stripe size and 2 worker
threads per I/O Concentrator.

\label{ex:ex2}
\begin{minted}{hdf5-c-lexer.py:HDF5CLexer -x}
#include "hdf5.h"

int
main(int argc, char **argv)
{
    H5FD_subfiling_config_t subf_config;
    H5FD_ioc_config_t ioc_config;
    MPI_Comm comm = MPI_COMM_WORLD;
    MPI_Info info = MPI_INFO_NULL;
    hid_t    file_id = H5I_INVALID_HID;
    hid_t    fapl_id = H5I_INVALID_HID;
    int      mpi_thread_required = MPI_THREAD_MULTIPLE;
    int      mpi_thread_provided = 0;

    /* Initialize MPI with threading support */
    MPI_Init_thread(&argc, &argv, mpi_thread_required, &mpi_thread_provided);
    if (mpi_thread_provided != mpi_thread_required)
        MPI_Abort(comm, -1);

    /*
     * Set up File Access Property List with MPI
     * parameters for the Subfiling VFD to use
     */
    fapl_id = H5Pcreate(H5P_FILE_ACCESS);
    H5Pset_mpi_params(fapl_id, comm, info);

    /*
     * Get a default Subfiling and IOC configuration
     */
    H5Pget_fapl_subfiling(fapl_id, &subf_config);
    H5Pget_fapl_ioc(fapl_id, &ioc_config);

    /*
     * Set Subfiling configuration to use a 1MiB
     * stripe size.
     */
    subf_config.shared_cfg.stripe_size = 1048576;

    /*
     * Set IOC configuration to use 2 worker threads
     * per IOC instead of the default setting.
     */
    ioc_config.thread_pool_size = 2;

    /*
     * Set our new configuration on the IOC
     * FAPL used for Subfiling
     */
    H5Pset_fapl_ioc(subf_config.ioc_fapl_id, &ioc_config);

    /*
     * Finally, set our new Subfiling configuration
     * on the original FAPL
     */
    H5Pset_fapl_subfiling(fapl_id, &subf_config);

    /*
     * Create a new Subfiling-based HDF5 file
     */
    file_id = H5Fcreate("my_h5_file.h5", H5F_ACC_TRUNC, H5P_DEFAULT, fapl_id);

    /* Close/free resources */
    H5Pclose(fapl_id);
    H5Fclose(file_id);

    MPI_Finalize();

    return 0;
}
\end{minted}

\subsection{H5fuse script}

Included with the Subfiling feature is a new HDF5 tool, called \textit{H5fuse}, which
comes in the form of a Bash script ("h5fuse.sh"). This script reads a Subfiling
configuration file and then uses \href{https://man7.org/linux/man-pages/man1/dd.1.html}{dd(1)}
to combine the various subfiles back into a single, regular HDF5 file. By default,
the H5fuse tool looks for a Subfiling configuration file in the directory that it
is run from. Still, it can also be pointed to a particular configuration file with a
command-line option.

During operation, the H5fuse tool will print out the \texttt{dd} operations that it
is performing to stitch each of the subfiles together and will print out the total
time elapsed once it has finished, Figure \ref{fig:h5fuse_output}. The newly-created file can then be accessed by
HDF5 or HDF5-related tools as though it had been written without the Subfiling
VFD.

\begin{figure}
\centering
\scalebox{1}[1.4]{\includegraphics[width=\textwidth]{images/H5fuse_edited.png}}
\caption{Output from H5fuse script}
\label{fig:h5fuse_output}
\end{figure}

\subsection{HDF5 tools support}

There are a few different ways that HDF5's tools can be used with a Subfiling VFD-based
HDF5 file. The most obvious way would be to use the H5fuse tool to convert the Subfiling
VFD-based file into a regular HDF5 file and then utilize HDF5's tools normally.

Alternatively, HDF5's tools can also load and use the Subfiling VFD directly to access one of these files. For example,

\begin{minted}{bash}
# Load the Subfiling VFD by environment variable and
# dump "my_subfiling_file.h5"
HDF5_DRIVER=subfiling h5dump my_subfiling_file.h5
\end{minted}

OR

\begin{minted}{bash}
# Load the Subfiling VFD by FAPL and dump 
# "my_subfiling_file.h5"
h5dump --filedriver=subfiling my_subfiling_file.h5
\end{minted}

The former method should work for most use cases, but the latter approach may be needed
when an HDF5 tool works with more than one file simultaneously and only one of the
files is a Subfiling VFD-based HDF5 file. For example, this method would be needed if
using \texttt{h5repack} to convert a Subfiling file into a different format through
the use of another VFD.

\end{document}

### 2023-01-27 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/acknowledgements.tex

\documentclass[../main.tex]{subfiles}

\begin{document}

\newpage

\section*{Acknowledgments}
\label{acknowledgements}

% Include this section in the table of contents
\addcontentsline{toc}{section}{Acknowledgements}
This work was supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of the U.S. Department of Energy Office of Science and the National Nuclear Security Administration.

\end{document}

### 2023-01-27 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/intro.tex

\documentclass[../main.tex]{subfiles}

\begin{document}

\newpage

\section{Introduction and overview}
\label{intro}

The HDF5 Subfiling \Gls{VFD} is an MPI-based File Driver that was introduced in the HDF5 1.14.0 release.
This File Driver allows an HDF5 application to create HDF5 files which are distributed across a collection
of "\textit{subfiles}" in equal-sized data segment "\textit{stripes}." I/O to the logical HDF5 file is directed to the
appropriate "\textit{subfile}" according to the Subfiling VFD configuration and a system of "\textit{I/O Concentrators}."
For more information on the general design of this VFD, refer to the \href{https://github.com/HDFGroup/hdf5doc/blob/master/RFCs/HDF5_Library/VFD_Subfiling/RFC_VFD_subfiling_200424.docx}{Subfiling RFC}.

By allowing a user to configure its various parameters, such as the data stripe size, number of subfiles,
etc., the Subfiling VFD aims to enable an HDF5 application to achieve a middle ground between the single
shared file and file-per-process approaches to parallel file I/O for a particular machine that the application
is running on. In general, the goal is to enable these applications to avoid some of the complexity of the
file-per-process approach while also minimizing locking issues that can occur on a parallel file system
with the single shared file approach at large scales.

The Subfiling feature consists of two major components: the Subfiling VFD and an underlying I/O
Concentrator VFD. The Subfiling VFD is responsible for managing Subfiling metadata and configuration
information, as well as breaking down I/O requests into the appropriate offset/length pairs based on
the Subfiling configuration and forwarding those requests to an I/O Concentrator VFD that is stacked
under the Subfiling VFD. The I/O Concentrator VFD is responsible for receiving I/O offset/length
pairs from the Subfiling VFD and forwarding each of these I/O requests to the I/O Concentrator
(typically, an MPI rank/dedicated thread/etc.) that is controlling the relevant portion of the logical
HDF5 file.

The Subfiling feature was designed to allow different types of I/O Concentrator VFDs in the future,
but currently includes a reference implementation of an I/O Concentrator VFD (called the
"IOC VFD"), which controls a dedicated set of MPI ranks acting as I/O Concentrators. Each of those MPI
ranks hosts an I/O thread pool and uses POSIX I/O calls (e.g., pread/pwrite) within those I/O threads.
Figure \ref{fig:architecture} graphically presents the current architecture of the Subfiling feature.

\begin{figure}
\centering
\scalebox{.9}{\includegraphics[width=\textwidth]{images/Subfiling Architecture.png}}
\caption{Subfiling feature architecture overview}
\label{fig:architecture}
\end{figure}

When an HDF5 file is written with the Subfiling VFD, several different files are created: The HDF5
stub file, a Subfiling configuration file and the various subfiles. For example, an HDF5 file called
"outFile.h5" is created with the Subfiling VFD, along with four subfiles, Figure \ref{fig:outputs}.

\begin{figure}
\centering
\scalebox{.8}{\includegraphics[width=\textwidth]{images/Subfiling components.png}}
\caption{Subfiling feature output files}
\label{fig:outputs}
\end{figure}

The first of these files, the HDF5 stub file, looks like a standard HDF5 file but only contains a small
portion of the file's metadata and is primarily used for HDF5 to determine when a file was written with
the Subfiling VFD.

The next file created is a Subfiling configuration file. The Subfiling VFD keeps track of its configuration
by writing it into the previously mentioned HDF5 stub file as metadata. However, this configuration information
also gets written out to a Subfiling configuration file so external tools can obtain that information
and access Subfiling VFD-based HDF5 files without needing to involve HDF5. An example of the Subfiling
configuration file is presented in Figure \ref{fig:config_file}.

\begin{figure}
\centering
\scalebox{.8}{\includegraphics[width=\textwidth]{images/Subfiling Config File.png}}
\caption{Subfiling configuration file}
\label{fig:config_file}
\end{figure}

Finally, the created subfiles (\texttt{outFile.h5.subfile\_12190989\_X\_of\_4}) simply contain
the raw file data, distributed in a round-robin fashion across the subfiles according to the Subfiling
stripe size.

\end{document}

### 2023-01-27 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/limitations.tex

\documentclass[../main.tex]{subfiles}

\begin{document}

\newpage

\section{Known problems and limitations}

\begin{itemize}
  \item Collective I/O is currently not supported, except for collective metadata
        reads/writes, as enabled by \texttt{H5Pset\_all\_coll\_metadata\_ops} and
        \texttt{H5Pset\_coll\_metadata\_write}

  \item The VFD should currently not be used with an HDF5 library that has been
        built with thread-safety enabled. This can cause deadlocks when failures
        occur due to interactions between the VFD's internal threads and HDF5's
        global lock.

  \item The internal I/O task queue doesn't currently have any sophisticated error handling
        method, so errors are only reported at a course-grained level if an I/O request
        fails at the lowest level (pread/pwrite/etc.)
\end{itemize}

\end{document}

### 2023-01-27 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/tips.tex

\documentclass[../main.tex]{subfiles}

\begin{document}

\newpage

\section{Tips and best practices}

\begin{itemize}
\item While the default configuration for the Subfiling VFD has been found
to be generally performant across different machines, it is still a good
idea to initially test a range of Subfiling configurations to see if there
is a particular one that generally performs best on the machine of interest.

\item When using a parallel file system that stripes data across different
storage targets (e.g., Lustre, GPFS, etc.), it is generally a good idea to
choose a Subfiling stripe size that is a multiple of the size of the data
stripes. For the best performance, it is also generally recommended that
the HDF5 application use the \texttt{H5Pset\_alignment} API routine to set
the alignment of objects in the file to match the Subfiling stripe size or
to at least be a multiple of the size of the file system's data stripes.
However, setting the alignment of objects in the file can potentially waste
space and vastly increase the size of the resulting file, so caution may be
needed when trying to find a good balance with this suggestion.

\item While not always leading to an improvement in performance, it can
sometimes be useful to enable collective metadata writes and, if the application's
access pattern allows for it, collective metadata reads in a parallel HDF5
application through use of the \texttt{H5Pset\_coll\_metadata\_write} and
\texttt{H5Pset\_all\_coll\_metadata\_ops} API routines.

\item When measuring the performance of the Subfiling feature, be aware that
results may sometimes be artificially high due to file system caching.
Since all I/O to a particular subfile is directed to a single I/O Concentrator
on a machine node, there are many opportunities for data from subfiles to
be served from or written to file system caching layers.
\end{itemize}

\end{document}

### 2023-01-27 RFCs/HDF5_Library/VFD_Subfiling/user_guide/support/glossary.tex

\makeglossaries

% Glossary terms 
\newglossaryentry{hid}
{
        name=HDF5 Identifier (HID),
        description={An integer which the library (H5I in HDF5) associates with an
                     "object" in memory, such as a file, FAPL, dataset, etc.}
}

\newglossaryentry{FAPL}
{
        name=File Access Property List (FAPL),
        description={An HDF5 \href{https://docs.hdfgroup.org/hdf5/develop/group___h5_p.html}{Property List}
                     object that is used to control how a file is accessed.}
}

\newglossaryentry{VFL}
{
        name=Virtual File Layer (VFL),
        description={A logical layer in the HDF5 library responsible for isolating the
                     library's operations from the underlying storage mechanism
                     (filesystem, e.g.).}
}

\newglossaryentry{VFD}
{
        name=Virtual File Driver (VFD),
        description={An implementation of a Virtual File Driver "class" – a structure
                     containing function pointers and other data required for Virtual File
                     operations.}
}

\newglossaryentry{tVFD}
{
        name=Terminal VFD,
        description={VFD which performs operations on storage and does not support
                     any child VFD as part of its own operation.}
}

\newglossaryentry{pVFD}
{
        name=Passthrough VFD,
        description={VFD which redirects operations to other “child” VFDs.}
}

\newglossaryentry{cVFD}
{
        name=Child VFD,
        description={VFD which receives direction from a “passthrough” VFD, rather
                     than from the HDF5 library directly.}
}

\newglossaryentry{hdf5_plugin}
{
        name=Plugin,
        description={Binary code which can be loaded and utilized at runtime. Extant
                     HDF5 examples include filter and VOL connector plugins.}
}

% Glossary acronyms 
\newacronym{hdf5}{HDF5}{Hierarchical Data Format, v5}

\newacronym{rfc}{RFC}{Request for Comments}

### 2023-06-20 RFCs/HDF5_Library/VFD_Subfiling/user_guide/appendices/ref_manual.tex
Update Subfiling User's Guide with notes about stripe count

@@
 written to subfiles. The default setting for this parameter is a 32MiB stripe size. The value
-must be $> 0$.
+set must either be the value defined by the \texttt{H5FD\_SUBFILING\_DEFAULT\_STRIPE\_SIZE}
+macro, or an integer value $> 0$.
 
 \texttt{int32\_t stripe\_count} - This field contains the target number of subfiles to use.
-The default setting for this parameter is set such that one subfile is used per machine node.
-The value must be $> 0$.
+It is mostly useful when pre-creating an HDF5 file in a parallel application within some
+subset of \texttt{MPI\_COMM\_WORLD} (see section \ref{sec:tips}). The default setting for
+this parameter is set such that one subfile is used per machine node. The value set must
+either be the value defined by the \texttt{H5FD\_SUBFILING\_DEFAULT\_STRIPE\_COUNT} macro,
+or an integer value $> 0$.
 \end{flushleft}%
@@
 use per I/O Concentrator. The default setting for this parameter is 4 worker threads per I/O
-Concentrator. The value must be $> 0$.
+Concentrator. The value set must either be the value defined by the \texttt{H5FD\_IOC\_DEFAULT\_THREAD\_POOL\_SIZE}
+macro, or an integer value $> 0$.
 \end{flushleft}%

### 2023-06-20 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/acknowledgements.tex
Update Subfiling User's Guide with notes about stripe count

@@
 \addcontentsline{toc}{section}{Acknowledgements}
-This work was supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of the U.S. Department of Energy Office of Science and the National Nuclear Security Administration.
+This work was supported by the Exascale Computing Project (17-SC-20-SC), a joint project of the U.S.
+Department of Energy’s Office of Science and National Nuclear Security Administration, responsible for delivering a capable exascale ecosystem, including software, applications, and hardware technology, to support the nation’s exascale computing imperative.
 

### 2023-06-20 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/tips.tex
Update Subfiling User's Guide with notes about stripe count

@@
 \section{Tips and best practices}
+\label{sec:tips}
 
@@
 
+\item If using the Subfiling VFD with a parallel HDF5 application that
+pre-creates an HDF5 file on a single MPI rank or some other subset of
+\texttt{MPI\_COMM\_WORLD}, it is necessary to adjust the "stripe count" (or
+number of subfiles) value that the Subfiling VFD uses internally in order to
+ensure that the proper number of subfiles gets generated when the logical HDF5
+file is created. Without setting this value, the VFD will default to creating
+one subfile per machine node, which will cause it to create only one subfile
+in the case of pre-creating an HDF5 file on a single MPI rank. Note that as
+pre-creating an HDF5 file on a subset of \texttt{MPI\_COMM\_WORLD} is expected
+to be a less common operation when using the Subfiling VFD, an environment
+variable for modifying this value has not been provided at this time and the
+VFD will need to be configured on a File Access Property List for this use case.
+Using the example in section \ref{ex:ex2} as a guide, one can configure the
+stripe count value by setting the \texttt{stripe\_count} field in the
+\texttt{H5FD\_subfiling\_params\_t} structure, which is part of the
+\texttt{H5FD\_subfiling\_config\_t} structure that is passed to 
+\texttt{H5Pset\_fapl\_subfiling}. For that particular example, one would
+set the \texttt{subf\_config.shared\_cfg.stripe\_count} field to the desired
+total number of subfiles.
+
 \item While not always leading to an improvement in performance, it can

### 2023-06-20 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/usage.tex
Update Subfiling User's Guide with notes about stripe count

@@
 
+Note that modifying the stripe count from its default setting is expected to be a less common operation
+with the Subfiling VFD. Therefore, an environment variable for changing the value has not currently
+been provided at this time. If an HDF5 application needs to modify the stripe count value (refer to
+section \ref{sec:tips} for information on when modifying the stripe count value is necessary), the
+Subfiling VFD will need to be configured by a File Access Property List. However, note that any
+settings in environment variables will still take precedence, even when the VFD is configured by
+a File Access Property List.
+
 \subsection{Minimal example}

### 2024-04-11 RFCs/HDF5_Library/Float16/appendices/appendix_examples.tex
Add RFC for adding _Float16 and Complex number support

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

% Start each appendix on a new page
\newpage

\section{Appendix: Examples}
\label{apdx:examples}

The following are examples of what using these new datatypes should look like once
support has been implemented in HDF5. Note that these examples are subject to change,
depending on the final decisions made when implementing support for these new datatypes.
Once support is implemented, relevant examples will be added to HDF5 to serve as a
better guide.

\textbf{Create a dataset with a binary16 little-endian 16-bit floating-point datatype}

\begin{minted}[custom lexer]{hdf5-c-lexer.py:HDF5CLexer}
#include "hdf5.h"

int
main(int argc, char **argv)
{
    hsize_t dims[2] = { 10, 10 };
    hid_t file_id   = H5I_INVALID_HID;
    hid_t dset_id   = H5I_INVALID_HID;
    hid_t space_id  = H5I_INVALID_HID;

    file_id = H5Fcreate("file.h5", H5F_ACC_TRUNC,
                        H5P_DEFAULT, H5P_DEFAULT);

    space_id = H5Screate_simple(2, dims, NULL);

    dset_id = H5Dcreate2(file_id, "dset", H5T_IEEE_F16LE,
                         space_id, H5P_DEFAULT,
                         H5P_DEFAULT, H5P_DEFAULT);

    ...

    H5Sclose(space_id);
    H5Dclose(dset_id);
    H5Fclose(file_id);

    return 0;
}
\end{minted}

\newpage

\textbf{Write to a binary16 little-endian 16-bit floating-point dataset using native \texttt{\_Float16} type}

\begin{minted}[custom lexer]{hdf5-c-lexer.py:HDF5CLexer}
#include "hdf5.h"

int
main(int argc, char **argv)
{
    _Float16 data[100];
    hsize_t dims[2] = { 10, 10 };
    hid_t file_id   = H5I_INVALID_HID;
    hid_t dset_id   = H5I_INVALID_HID;
    hid_t space_id  = H5I_INVALID_HID;

    file_id = H5Fcreate("file.h5", H5F_ACC_TRUNC,
                        H5P_DEFAULT, H5P_DEFAULT);

    space_id = H5Screate_simple(2, dims, NULL);

    dset_id = H5Dcreate2(file_id, "dset", H5T_IEEE_F16LE,
                         space_id, H5P_DEFAULT,
                         H5P_DEFAULT, H5P_DEFAULT);

    for (size_t i = 0; i < 100; i++)
        data[i] = 1.1f16;

    H5Dwrite(dset_id, H5T_NATIVE_FLOAT16, H5S_ALL,
             H5S_ALL, H5P_DEFAULT, data);

    H5Sclose(space_id);
    H5Dclose(dset_id);
    H5Fclose(file_id);

    return 0;
}
\end{minted}

\newpage

\textbf{Write to and read from a binary16 little-endian 16-bit floating-point dataset using native \texttt{\_Float16} type}

\begin{minted}[custom lexer]{hdf5-c-lexer.py:HDF5CLexer}
#include "hdf5.h"

int
main(int argc, char **argv)
{
    _Float16 data[100];
    _Float16 read_buf[100];
    hsize_t dims[2] = { 10, 10 };
    hid_t file_id   = H5I_INVALID_HID;
    hid_t dset_id   = H5I_INVALID_HID;
    hid_t space_id  = H5I_INVALID_HID;

    file_id = H5Fcreate("file.h5", H5F_ACC_TRUNC,
                        H5P_DEFAULT, H5P_DEFAULT);

    space_id = H5Screate_simple(2, dims, NULL);

    dset_id = H5Dcreate2(file_id, "dset", H5T_IEEE_F16LE,
                         space_id, H5P_DEFAULT,
                         H5P_DEFAULT, H5P_DEFAULT);

    for (size_t i = 0; i < 100; i++)
        data[i] = 1.1f16;

    H5Dwrite(dset_id, H5T_NATIVE_FLOAT16, H5S_ALL,
             H5S_ALL, H5P_DEFAULT, data);

    H5Dread(dset_id, H5T_NATIVE_FLOAT16, H5S_ALL,
            H5S_ALL, H5P_DEFAULT, read_buf);

    for (size_t i = 0; i < 100; i++)
        printf("%f\n", (double)read_buf[i]);

    H5Sclose(space_id);
    H5Dclose(dset_id);
    H5Fclose(file_id);

    return 0;
}
\end{minted}

\newpage

\textbf{Write to and read from a little-endian 128-bit (2 64-bit doubles) complex number dataset using native \texttt{double \_Complex} type}

\begin{minted}[custom lexer]{hdf5-c-lexer.py:HDF5CLexer}
#include <complex.h>

#include "hdf5.h"

int
main(int argc, char **argv)
{
    double _Complex data[100];
    double _Complex read_buf[100];
    hsize_t dims[2] = { 10, 10 };
    hid_t file_id   = H5I_INVALID_HID;
    hid_t dset_id   = H5I_INVALID_HID;
    hid_t space_id  = H5I_INVALID_HID;

    file_id = H5Fcreate("file.h5", H5F_ACC_TRUNC,
                        H5P_DEFAULT, H5P_DEFAULT);

    space_id = H5Screate_simple(2, dims, NULL);

    dset_id = H5Dcreate2(file_id, "dset", H5T_STD_DOUBLE_COMPLEX_LE,
                         space_id, H5P_DEFAULT,
                         H5P_DEFAULT, H5P_DEFAULT);

    for (size_t i = 0; i < 100; i++)
        data[i] = 1.0 + 2.0*I;

    H5Dwrite(dset_id, H5T_NATIVE_DOUBLE_COMPLEX,
             H5S_ALL, H5S_ALL, H5P_DEFAULT, data);

    H5Dread(dset_id, H5T_NATIVE_DOUBLE_COMPLEX,
            H5S_ALL, H5S_ALL, H5P_DEFAULT, read_buf);

    for (size_t i = 0; i < 100; i++)
        printf("%f%+fi\n", creal(read_buf[i]), cimag(read_buf[i]));

    H5Sclose(space_id);
    H5Dclose(dset_id);
    H5Fclose(file_id);

    return 0;
}
\end{minted}

\newpage

\textbf{Write to a little-endian 128-bit (2 64-bit doubles) complex number dataset when platform doesn't support \texttt{double \_Complex} type}

\begin{minted}[custom lexer]{hdf5-c-lexer.py:HDF5CLexer}
#include "hdf5.h"

int
main(int argc, char **argv)
{
    /* Note that data has twice the number of elements as the dataset */
    double data[200];
    hsize_t dims[2] = { 10, 10 };
    hid_t file_id   = H5I_INVALID_HID;
    hid_t dset_id   = H5I_INVALID_HID;
    hid_t space_id  = H5I_INVALID_HID;

    file_id = H5Fcreate("file.h5", H5F_ACC_TRUNC,
                        H5P_DEFAULT, H5P_DEFAULT);

    space_id = H5Screate_simple(2, dims, NULL);

    dset_id = H5Dcreate2(file_id, "dset", H5T_STD_DOUBLE_COMPLEX_LE,
                         space_id, H5P_DEFAULT,
                         H5P_DEFAULT, H5P_DEFAULT);

    for (size_t i = 0; i < 200; ) {
        data[i]     = 1.0; /* real part */
        data[i + 1] = 2.0; /* imaginary part */
        i += 2;
    }

    H5Dwrite(dset_id, H5T_STD_DOUBLE_COMPLEX_LE,
             H5S_ALL, H5S_ALL, H5P_DEFAULT, data);

    H5Sclose(space_id);
    H5Dclose(dset_id);
    H5Fclose(file_id);

    return 0;
}
\end{minted}

\end{document}

### 2024-04-11 RFCs/HDF5_Library/Float16/appendices/appendix_portability.tex
Add RFC for adding _Float16 and Complex number support

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

% Start each appendix on a new page
\newpage

\section{Appendix: Portability}
\label{apdx:portability}

The following items must be taken into account for supporting these new datatypes across different
platforms and compilers.

\subsection{\texttt{\_Float16}}

\subsubsection{GCC}

This type is supported by GCC on:

\begin{itemize}
    \item x86 systems where SSE2 support is available
    \item ARM systems when the \texttt{-mfp16-format=ieee} flag is used to specify that the IEEE
          half-precision floating-point format should be used
    \item AArch64 systems by default
\end{itemize}

\subsubsection{Clang}

Based on \href{https://clang.llvm.org/docs/LanguageExtensions.html#half-precision-floating-point}{Clang Language Extensions},
this type is supported by Clang on:

\begin{itemize}
    \item x86 systems (natively if AVX512-FP16 is available; emulated otherwise)
    \item 32-bit ARM systems (emulated on some architectures; natively on some architectures)
    \item AArch64 systems (natively on ARMv8.2a and later)
    \item AMDGPU (natively)
    \item RISC-V (natively if Zfh or Zhinx support is available)
\end{itemize}

where "natively" means the processor can directly perform arithmetic on the type using
dedicated instructions and "emulated" means the compiler will promote to \texttt{float}
before performing arithmetic.

\subsubsection{MSVC}

As of the time of writing, Visual Studio 2022 does not appear to have support for any half-precision floating-point types.

\subsubsection{NVHPC}

NVHPC appears to support this type when compiling code used for CUDA compute (e.g., with \texttt{nvcc}), but
does not appear to support this type when compiling regular C code with \texttt{nvc}.

\subsubsection{OneAPI}

Based on \href{https://www.intel.com/content/www/us/en/docs/dpcpp-cpp-compiler/developer-guide-reference/2024-0/math-function-list.html}{Intel oneAPI Math Function List}, this type appears to be supported as of oneAPI version 2021.4 or higher with a "next-generation Intel® Xeon® Scalable processor".
The \href{https://www.intel.com/content/www/us/en/developer/tools/oneapi/onednn.html#gs.3ikawv}{Intel oneAPI Deep Neural Network Library} also appears
to have support for a 16-bit floating-point type through the \href{https://www.intel.com/content/www/us/en/docs/onednn/developer-guide-reference/2024-0/data-types-001.html}{f16} type specifier, but it's not clear whether that type is more or less appropriate as an interchange format.

\subsection{\texttt{\_\_bf16}}

\subsubsection{GCC}

This type is supported as of GCC 13 on:

\begin{itemize}
    \item x86 systems where SSE2 support is available
\end{itemize}

\subsubsection{Clang}

Based on \href{https://clang.llvm.org/docs/LanguageExtensions.html#half-precision-floating-point}{Clang Language Extensions},
this type is supported by Clang on:

\begin{itemize}
    \item x86 systems where SSE2 support is available
    \item 32-bit ARM systems
    \item AArch64 systems
    \item RISC-V systems
\end{itemize}

Note that support for the \texttt{\_\_bf16} type is currently always emulated and not
supported natively on any of the platforms above.

\subsubsection{MSVC}

As of the time of writing, Visual Studio 2022 does not appear to have support for any half-precision floating-point types.

\subsubsection{NVHPC}

This type appears to be supported by NVHPC as of version 23.9.

\subsubsection{OneAPI}

The \href{https://www.intel.com/content/www/us/en/developer/tools/oneapi/onednn.html#gs.3ikawv}{Intel oneAPI Deep Neural Network Library}
(oneDNN) appears to have support for this type through the \texttt{bf16} type specifier. A whitepaper on the topic can be found at
\href{https://www.intel.com/content/dam/develop/external/us/en/documents/bf16-hardware-numerics-definition-white-paper.pdf}{here}.

\subsection{\texttt{\_Bool}}

This type is supported on any C99-compliant compiler, which includes all the compilers mentioned for other types here.

\subsection{\texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex}}

These types will generally be supported on any platform and compiler combination that
implements the ISO C99 standard. However, it should be noted that support for complex
numbers became optional in the C11 standard, meaning that C99 compliance is not enough
of an indicator of support for these types. As of the C11 standard, there is a feature
test macro, \texttt{\_\_STDC\_NO\_COMPLEX\_\_}, to determine this support, but as it only
exists in the C11 standard and HDF5 only requires C99 compliance, additional configure
time checks will likely be needed to check for complex number support. As of the C99
standard, there is also the feature test macro, \texttt{\_\_STDC\_IEC\_559\_COMPLEX\_\_},
which determines whether the available complex number support conforms to IEC 60559.
Notably, this involves supporting some additional macros and types for imaginary numbers.
While in theory this macro could be used to check for complex number support, it is only
a recommendation in the C99 standard that a compiler which defines this macro should support
imaginary numbers. As of the C11 standard, it became mandatory for a compiler to support
imaginary numbers if it defines this macro, but as of the C23 standard this macro has
changed to \texttt{\_\_STDC\_IEC\_60559\_COMPLEX\_\_}. Therefore, a configure time check
for complex number support should likely rely on trying to compile a program that uses
the complex number types rather than relying on these macros (though \texttt{\_\_STDC\_NO\_COMPLEX\_\_}
can be checked if C11 support or later is available).

\subsubsection{GCC}

These types are fully supported, as long as the value of \texttt{\_\_STDC\_NO\_COMPLEX\_\_},
if available, is not $1$.

\subsubsection{Clang}

These types are fully supported, as long as the value of \texttt{\_\_STDC\_NO\_COMPLEX\_\_},
if available, is not $1$.

\subsubsection{MSVC}

\href{https://learn.microsoft.com/en-us/cpp/c-runtime-library/complex-math-support?view=msvc-170}{Support for complex numbers is available},
but MSVC does not expose the \texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex} types and instead uses
the \texttt{\_Fcomplex}, \texttt{\_Dcomplex}, \texttt{\_Lcomplex} types, respectively.

\subsubsection{NVHPC}

These types are fully supported, as long as the value of \texttt{\_\_STDC\_NO\_COMPLEX\_\_},
if available, is not $1$.

\subsubsection{OneAPI}

As oneAPI is C99 compliant, these types should be fully supported, as long as the value of
\texttt{\_\_STDC\_NO\_COMPLEX\_\_}, if available, is not $1$.

\end{document}

### 2024-04-11 RFCs/HDF5_Library/Float16/sections/acknowledgements.tex
Add RFC for adding _Float16 and Complex number support

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

\section*{Acknowledgments}
\label{acknowledgements}

% Include this section in the table of contents
\addcontentsline{toc}{section}{Acknowledgements}

This material is based upon work supported by the U.S. Department of Energy, Office of Science, Office of
Fusion Energy Sciences, under Award Number DE-SC0024442.

\textbf{Disclaimer:} This report was prepared as an account of work sponsored by an agency of the United
States Government. Neither the United States Government nor any agency therefore, nor any of their employees,
makes any warranty, expressed or implied, or assumes any legal liability or responsibility for the accuracy,
completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that
this use would not infringe privately owned rights. Reference herein to any specific commercial product,
process, or service by trade name, trademark, manufacturer, or otherwise does not necessarily constitute or
imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof.
The views and opinions of authors expressed herein do not necessarily state or reflect those of the United
States Government or any agency thereof.

\end{document}

### 2024-04-11 RFCs/HDF5_Library/Float16/sections/approach.tex
Add RFC for adding _Float16 and Complex number support

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

\section{Approach}
\label{approach}

\subsection{Configure time checks}

For each new datatype added, configure-time checks will be added to both CMake and the Autotools to
detect the size of the native form of each datatype. New macros in the form of \texttt{H5\_SIZEOF\_type}
will be added to the files that generate the \texttt{H5pubconf.h} header file. If a compiler doesn't
support a particular type, the macro for that type will have a value of $0$.

\subsection{New datatype IDs and macros}

For each new datatype added, variables will be added to \texttt{H5T.c} for the IDs of library-internal
datatypes which will represent the platform-native form of each datatype, as well as the "standard" file
format storage form of each datatype. Then, the following new macros will be added for the new datatypes:

\subsubsection{\_Float16}

\texttt{H5T\_NATIVE\_FLOAT16}

Maps to the ID of the library-internal datatype representing the platform's native representation
of an IEEE binary16-format 16-bit floating point number.

\textbf{NOTE: If the platform doesn't support the \texttt{\_Float16} type, this macro will map to
\texttt{H5I\_INVALID\_HID} and will cause an "invalid datatype" error if used for any HDF5 operation
which is passed a datatype identifier. In this case, one should use the \texttt{H5T\_IEEE\_F16LE} or
\texttt{H5T\_IEEE\_F16BE} macro when writing from or reading into buffers of binary16-format data.}

\texttt{H5T\_IEEE\_F16LE}

Maps to the ID of the library-internal datatype representing a binary16-format 16-bit
little-endian IEEE floating-point number.

\texttt{H5T\_IEEE\_F16BE}

Maps to the ID of the library-internal datatype representing a binary16-format 16-bit
big-endian IEEE floating-point number.

\subsubsection{\_\_bf16}

\texttt{H5T\_NATIVE\_BFLOAT16}

Maps to the ID of the library-internal datatype representing the platform's native representation
of a bfloat16-format 16-bit floating point number.

\textbf{NOTE: If the platform doesn't support the \texttt{\_\_bf16} type, this macro will map to
\texttt{H5I\_INVALID\_HID} and will cause an "invalid datatype" error if used for any HDF5 operation
which is passed a datatype identifier. In this case, one should use the \texttt{H5T\_BRAIN\_F16LE} or
\texttt{H5T\_BRAIN\_F16BE} macro when writing from or reading into buffers of bfloat16-format data.}

\texttt{H5T\_BRAIN\_F16LE}

Maps to the ID of the library-internal datatype representing a bfloat16-format 16-bit
little-endian floating-point number.

\texttt{H5T\_BRAIN\_F16BE}

Maps to the ID of the library-internal datatype representing a bfloat16-format 16-bit
big-endian floating-point number.

\subsubsection{\texttt{\_Bool}}

\texttt{H5T\_NATIVE\_BOOL}

Maps to the ID of the library-internal datatype representing the platform's native representation
of a \texttt{\_Bool} boolean type.

\texttt{H5T\_STD\_BOOL}

Maps to the ID of the library-internal datatype representing a 1-bit boolean value.

\subsubsection{\texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex}}

\texttt{H5T\_NATIVE\_FLOAT\_COMPLEX}

Maps to the ID of the library-internal datatype representing the platform's native representation
of a complex number consisting of \texttt{float} values.

\textbf{NOTE: If the platform doesn't support the \texttt{float \_Complex} type, this macro will map to
\texttt{H5I\_INVALID\_HID} and will cause an "invalid datatype" error if used for any HDF5 operation
which is passed a datatype identifier. In this case, one should use the \texttt{H5T\_STD\_FLOAT\_COMPLEX\_LE}
or \texttt{H5T\_STD\_FLOAT\_COMPLEX\_BE} macro when writing from or reading into buffers of complex numbers
consisting of 32-bit-precision floating-point values.}

\texttt{H5T\_STD\_FLOAT\_COMPLEX\_LE}

Maps to the ID of the library-internal datatype representing a complex number consisting of 2
32-bit-precision little-endian floating-point values.

\texttt{H5T\_STD\_FLOAT\_COMPLEX\_BE}

Maps to the ID of the library-internal datatype representing a complex number consisting of 2
32-bit-precision big-endian floating-point values.

\texttt{H5T\_NATIVE\_DOUBLE\_COMPLEX}

Maps to the ID of the library-internal datatype representing the platform's native representation
of a complex number consisting of \texttt{double} values.

\textbf{NOTE: If the platform doesn't support the \texttt{double \_Complex} type, this macro will map to
\texttt{H5I\_INVALID\_HID} and will cause an "invalid datatype" error if used for any HDF5 operation
which is passed a datatype identifier. In this case, one should use the \texttt{H5T\_STD\_DOUBLE\_COMPLEX\_LE}
or \texttt{H5T\_STD\_DOUBLE\_COMPLEX\_BE} macro when writing from or reading into buffers of complex numbers
consisting of 64-bit-precision floating-point values.}

\texttt{H5T\_STD\_DOUBLE\_COMPLEX\_LE}

Maps to the ID of the library-internal datatype representing a complex number consisting of 2
64-bit-precision little-endian floating-point values.

\texttt{H5T\_STD\_DOUBLE\_COMPLEX\_BE}

Maps to the ID of the library-internal datatype representing a complex number consisting of 2
64-bit-precision big-endian floating-point values.

\texttt{H5T\_NATIVE\_LDOUBLE\_COMPLEX}

Maps to the ID of the library-internal datatype representing the platform's native representation
of a complex number consisting of \texttt{long double} values.

\textbf{NOTE: If the platform doesn't support the \texttt{long double \_Complex} type, this macro will
map to \texttt{H5I\_INVALID\_HID} and will cause an "invalid datatype" error if used for any HDF5
operation which is passed a datatype identifier. In this case, one should use the \texttt{H5T\_STD\_LDOUBLE\_COMPLEX\_LE}
or \texttt{H5T\_STD\_LDOUBLE\_COMPLEX\_BE} macro when writing from or reading into buffers of complex numbers
consisting of 128-bit-precision floating-point values.}

\texttt{H5T\_STD\_LDOUBLE\_COMPLEX\_LE}

Maps to the ID of the library-internal datatype representing a complex number consisting of 2
128-bit-precision little-endian floating-point values.

\texttt{H5T\_STD\_LDOUBLE\_COMPLEX\_BE}

Maps to the ID of the library-internal datatype representing a complex number consisting of 2
128-bit-precision big-endian floating-point values.

\subsection{On-disk format for new datatypes}

\subsubsection{\texttt{\_Float16}}

Data of this type will be stored as 16-bit values on disk, according to the endian-ness of the specified
datatype (e.g. \texttt{H5T\_IEEE\_F16LE} vs. \texttt{H5T\_IEEE\_F16BE}), in a similar format to how other
floating-point values are stored in HDF5.

\subsubsection{\texttt{\_\_bf16}}

Data of this type will be stored as 16-bit values on disk, according to the endian-ness of the specified
datatype (e.g. \texttt{H5T\_BRAIN\_F16LE} vs. \texttt{H5T\_BRAIN\_F16BE}), in a similar format to how other
floating-point values are stored in HDF5.

\subsubsection{\texttt{\_Bool}}

Data of this type will be stored as a 1-bit value on disk.

\subsubsection{\texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex}}

Data of these types will be stored as atomic 64-bit, 128-bit, or 256-bit values on disk, respectively,
according to the endian-ness of the specified datatype. The benefit to choosing this format is that
these values should be able to be converted directly from disk format to a platform's in-memory
representation with zero or near-zero overhead during conversion (depending on the endian-ness of the disk
format and the in-memory representation). However, this means that there will likely be some overhead during
conversion from disk format to in-memory representation for applications that use their own convention, such
as a compound datatype with two members, for representing complex numbers.

\textbf{NOTE: These on-disk formats have been chosen as they map to common sizes (multiplied by 2) of \texttt{float},
\texttt{double} and \texttt{long double} across platforms. Care should be taken when interacting with these
datatypes on a platform where the size of the C types don't match these sizes.}

\subsection{Conversions}

For each new datatype added, hard and soft conversion routines will be added to \texttt{H5Tconv.c} to
convert between the new type and each existing native integer and floating-point type. In particular,
the conversions for complex number types will follow the rules laid out in
\href{https://github.com/HDFGroup/hdf5doc/blob/master/RFCs/HDF5_Library/New_Datatypes/new_datatypes.pdf}{RFC: New Datatypes}.
Additionally, some conversions between complex number types and existing user-defined representations
(e.g., a compound type with two members, an array type with two elements, etc.) will be added to help
maintain compatibility with those representations.

\subsection{\texttt{H5trace}}

For each new datatype added, a printout for the new datatype will be added to the \texttt{H5\_trace\_args}
function in \texttt{H5trace.c}.

\subsection{Testing}

For each new datatype added, tests will be added to the library to exercise both using the new datatype
to create objects, as well as converting between the new datatype and existing HDF5 datatypes
(see \texttt{test/dt\_arith.c}).

\end{document}

### 2024-04-11 RFCs/HDF5_Library/Float16/sections/considerations.tex
Add RFC for adding _Float16 and Complex number support

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

\section{Further considerations}
\label{considerations}

The following items are miscellaneous considerations to take into account when interacting with these
new datatypes:

\begin{itemize}
\item As there is no \texttt{printf} format specifier for the \texttt{\_Float16} C type, and since
a variable of type \texttt{\_Float16} will not be promoted to a larger type when passed to \texttt{printf},
one should cast a variable of this type to \texttt{double} and use the \texttt{\%f} specifier to print
the value of such a variable.

\end{itemize}

\end{document}

### 2024-04-11 RFCs/HDF5_Library/Float16/sections/intro.tex
Add RFC for adding _Float16 and Complex number support

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

\section{Introduction}
\label{intro}

HDF5 has a rich set of predefined datatypes to cover some of the most common use cases when
storing data in HDF5 files. However, there are several types of data in wide use today that
HDF5 does not handle in a convenient or efficient manner, causing users to have to workaround
this lack of support in ways that are often cumbersome.

One of the goals that this RFC intends to accomplish is enabling convenient and efficient
storage and retrieval of half-precision floating-point data in HDF5 files. An HDF5 user can
store their data in a dataset using one of the existing (at least 32-bit) floating-point
types and later convert the data to half-precision floating-point in memory for calculations,
but as the reduced storage requirements for 16-bit floating-point values is one of the main
benefits of the datatype, this isn't an ideal scenario. While one can already create an HDF5
datatype that will allow storing of floating-point data as 16-bit values on disk, the process
of doing so with HDF5's \texttt{H5T} API routines may not be obvious to users, meaning that
applications could potentially benefit from having a convenient predefined datatype to use.
Further, datatype conversions on datatypes like this which HDF5 doesn't have native support
for can have very poor performance, as demonstrated in issue \href{https://github.com/HDFGroup/hdf5/issues/2154}{\#2154}
in HDF5's GitHub repository. This is due to HDF5 performing conversions on these datatypes
in software rather than allowing the compiler to potentially perform these conversions in
hardware through dedicated instructions. Once again, an HDF5 user could work around this issue
by defining their own datatype conversion routine, but it would be better and more convenient
for HDF5 to be able to perform fast conversions by default where possible.

Another problematic topic in the world of HDF5 data involves the storage of complex numbers.
Complex numbers are used throughout the scientific and other communities, but HDF5 does not
currently have native support for them. This has led HDF5 users to invent their own conventions
for storing this type of data, which can be inconvenient and can result in HDF5 files that have
poor interoperability. A \href{https://github.com/HDFGroup/hdf5/discussions/3339}{feature request}
for native complex number support in HDF5 was made fairly recently and contains a good discussion
on the issues surrounding this problem.

To address these issues and work toward more portable HDF5 files, this RFC proposes adding native
support in HDF5 for several datatypes that have been requested in the past, as well as datatypes
that will be useful in future workflows which use HDF5.

\end{document}

### 2024-04-11 RFCs/HDF5_Library/Float16/sections/new_datatypes.tex

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

\section{New datatypes}
\label{new_datatypes}

Support for the following C datatypes is being considered for addition to the HDF5 library:
\texttt{\_Float16}, \texttt{\_\_bf16}, \texttt{\_Bool}, \texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex}.

\subsection{\texttt{\_Float16}}

This is a half-precision floating-point binary interchange format type specified in \textbf{ISO/IEC TS 18661-3:2015}.
It represents a \href{https://en.wikipedia.org/wiki/Half-precision_floating-point_format}{binary16-format} floating-point
type consisting of:

\begin{itemize}
    \item 16 bits of storage
    \item 1 bit for the sign
    \item 5 bits for the exponent
    \item 10 bits for the fraction
\end{itemize}

An alternative to this type is the \texttt{\_\_fp16} type, but arithmetic operations on this type promote to \texttt{float}
or higher, while arithmetic can often be performed directly on values of the \texttt{\_Float16} type. It is also generally
recommended that portable code use the \texttt{\_Float16} type, as it is standardized by the C standards committee. Due to
this, only support for the \texttt{\_Float16} type is being considered here; support for the \texttt{\_\_fp16} type may be
considered in the future.

\subsection{\texttt{\_\_bf16}}

This is a half-precision floating-point type developed by \href{https://en.wikipedia.org/wiki/Google_Brain}{Google Brain}
which is useful for machine learning applications and other workflows where the reduced storage requirements and potentially
faster calculation speeds of the format are important. It represents a \href{https://en.wikipedia.org/wiki/Bfloat16_floating-point_format}{bfloat16-format}
floating-point type consisting of:

\begin{itemize}
    \item 16 bits of storage
    \item 1 bit for the sign
    \item 8 bits for the exponent
    \item 7 bits for the fraction
\end{itemize}

This format has not been formally standardized by the C standards committee and support varies across platforms, so it
may be tricky to support this format.

\subsection{\texttt{\_Bool}}

This is the boolean datatype introduced in the C99 standard. The main reason for including native support for this type
in HDF5 is to be able to reduce its storage requirements by not having to rely on integer types for storing boolean
values.

\subsection{\texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex}}

These are types representing complex numbers consisting of a real and imaginary part, each of which is a floating-point
value of the specified type (\texttt{float}, \texttt{double} or \texttt{long double}). These types have been discussed
more extensively in \href{https://github.com/HDFGroup/hdf5doc/blob/master/RFCs/HDF5_Library/New_Datatypes/new_datatypes.pdf}{RFC: New Datatypes}
and are simply brought up once again for discussion around inclusion into HDF5.

\subsection{Other lesser-precision floating-point datatypes}

Consideration has also been given towards supporting lesser-precision floating-point datatypes, such as 8-bit floating-point
datatypes. However, current compiler support for this type seems to be minimal or nonexistent across a variety of platform/compiler
combinations. Therefore, support for these types would not be implemented at this time, but may be considered in the future
if they are found to be useful.

\end{document}

### 2024-04-11 RFCs/HDF5_Library/Float16/sections/tools.tex

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

\section{HDF5 tools support}
\label{tools}

After adding these new datatypes, HDF5's tools library and tool applications will need to be
updated to understand these new types. At minimum, this will involve updating the tools library's
object dumping routines in \texttt{h5tools\_dump.c}, the \texttt{print\_type} routine in
\texttt{h5diff\_util.c} and the \texttt{print\_native\_type} routine in \texttt{h5ls.c}.
Additionally, tools tests which exercise using the tool applications on these new types should be
added to the library's existing tests.

As part of implementing support for these datatypes, it must be decided how the tool applications
should print out a visual representation for complex datatypes when encountered. This RFC proposes
the following as a starting point for discussion:

\begin{verbatim}
COMPLEX { real: VALUE, imag: VALUE }    
\end{verbatim}

\end{document}

### 2024-04-11 RFCs/HDF5_Library/Float16/sections/wrappers.tex

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

\section{HDF5 language wrappers support}
\label{wrappers}

The following sections briefly detail implementing support for these new datatypes in the HDF5
language wrappers both internal and external to HDF5.

\subsection{Fortran}

\subsubsection{\texttt{\_Float16}}

Fortran support for this type appears to rely on compiler support; adding support in HDF5's Fortran
wrappers may be straightforward or may take a bit of work, depending on compiler support across platforms.

\subsubsection{\texttt{\_\_bf16}}

Fortran support for this type appears to rely on compiler support; adding support in HDF5's Fortran
wrappers may be straightforward or may take a bit of work, depending on compiler support across platforms.

\subsubsection{\texttt{\_Bool}}

Fortran has the \texttt{C\_BOOL} type to support this datatype.

\subsubsection{\texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex}}

Fortran has native support for this datatype; adding support in HDF5's Fortran wrappers should be straightforward.

\subsection{Python}

\subsubsection{\texttt{\_Float16}}

\texttt{h5py} supports this datatype through NumPY.

\subsubsection{\texttt{\_\_bf16}}

NumPY does not currently appear to support this type, but there has been some discussion around
supporting it, at which point \texttt{h5py} could support it as well.

\subsubsection{\texttt{\_Bool}}

\texttt{h5py} supports this datatype through NumPY.

\subsubsection{\texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex}}

\texttt{h5py} supports this datatype through NumPY.

\subsection{C++}

\subsubsection{\texttt{\_Float16}}

C++ has support for this type as an optional feature; adding support in HDF5's C++ wrappers may be
straightforward or may take a bit of work, depending on compiler support across platforms.

\subsubsection{\texttt{\_\_bf16}}

C++ has support for this type as an optional feature; adding support in HDF5's C++ wrappers may be
straightforward or may take a bit of work, depending on compiler support across platforms.

\subsubsection{\texttt{\_Bool}}

C++ has native support for this datatype; adding support in HDF5's C++ wrappers should be straightforward.

\subsubsection{\texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex}}

C++ has native support for these datatypes; adding support in HDF5's C++ wrappers should be straightforward.

\subsection{Java}

\subsubsection{\texttt{\_Float16}}

Java JDK 20 appears to introduce support for half-precision floating-point types, though they
seem to represent these values in the \texttt{short} datatype. For a Java JDK before this version,
support for this type could be implemented in HDF5's Java wrappers using one of several different
approaches.

\subsubsection{\texttt{\_\_bf16}}

Java doesn't support this datatype, but it could be implemented manually in HDF5's Java wrappers.

\subsubsection{\texttt{\_Bool}}

Java has native support for this datatype; adding support in HDF5's Java wrappers should be straightforward.

\subsubsection{\texttt{float \_Complex}, \texttt{double \_Complex}, \texttt{long double \_Complex}}

Support for complex numbers in HDF5's Java wrappers could be implemented through a Class.

\end{document}

### 2024-04-26 RFCs/HDF5_Library/WriteAheadLog/sections/abstract.tex
Add Write-Ahead Log RFC (version 1)

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

\begin{abstract}
This RFC describes a new module that implements a Write-Ahead Log (WAL) for metadata within the HDF5 library. In the event of a crash during the lifetime of an application using HDF5, this WAL can be used by the library or an external tool to restore the metadata within an HDF5 file to a self-consistent state, preventing file corruption and limiting the loss of application data with minimal I/O and memory overhead.
\end{abstract}

\end{document}

### 2024-04-26 RFCs/HDF5_Library/WriteAheadLog/sections/architecture.tex
Add Write-Ahead Log RFC (version 1)

\section{Architecture}
\label{sec:architecture}
% The architecture diagram: https://thehdfgroup-my.sharepoint.com/:u:/g/personal/mlarson_hdfgroup_org/EWdh_K7tOc5JhB0mJPSAJuYBzKx2uFQ5RvwqQQLdOyKxew?e=7T9Ngr

\subsection{Metadata Cache vs. Page Buffer}

As the WAL requires a client module that is responsible for handling metadata I/O to the file, it could be feasibly achieved with either the metadata cache or the page buffer as its primary client. For several reasons, we chose to pursue implementation via the metadata cache:

\begin{itemize}
    \item An implementation through the page buffer would necessitate either tracking which page sections are updated by writes, or writing exclusively entire metadata pages to the WAL. Tracking page sections would increase complexity greatly, and writing entire pages may negatively impact performance and increase the size of the WAL.

    \item The page buffer is often bypassed - for example, when an I/O operation is larger than one page. Implementing the WAL through the page buffer would require forcing all metadata to always pass through the page buffer.

    \item An implementation through the page buffer would still need to notify the metadata cache at the time of a log flush or log checkpoint (see \hyperref[sec:Flush-Types]{Flush Types}) in order to accurately satisfy later metadata reads. Implementing the WAL through the metadata cache means that this introduces no additional coupling.

\end{itemize}

\subsection{Flush Types}
\label{sec:Flush-Types}

There are two types of metadata flush that the library may perform:

\begin{enumerate}
    \item A "log flush" - Flushes metadata from the cache to the WAL file to create a self-consistent location to play forward to in the event of a crash.

    \item A "log checkpoint" - Replays metadata writes from the WAL to the HDF5 file to bring the file up-to-date with metadata operations until a specific point. This requires reading a WAL entry from the WAL file for each metadata write performed. This is the type of flush invoked by \texttt{H5Fflush()}.
\end{enumerate}

Each type of flush operation leaves a 'marker' in the WAL after the last WAL entry upon which it acts.

All WAL entries before a log checkpoint marker have already been written to the HDF5 file and may be safely trimmed from the WAL. A WAL trim operation involves truncating the WAL file so it only contains the WAL superblock, effectively deleting all WAL entries.

A complete implementation of the WAL without log checkpoint markers is possible, if the WAL is always trimmed immediately after each log checkpoint. In this case, all entries which would be placed before a log checkpoint marker are instead removed from the WAL entirely, and so the marker is not necessary to indicate that these entries should be skipped during subsequent WAL operations.

A log flush marker indicates that all WAL entries since the last log checkpoint should be 'played forward' to the HDF5 file during a log checkpoint or crash recovery. Log flush markers prevent re-execution of torn metadata writes, since if a torn write occurs during a log flush and leaves a malformed WAL entry, no log flush marker will be present and no modification of the HDF5 file will be attempted.

\subsection{Metadata Cache + WAL Lifecycle}
\label{sec:Metadata-Cache-WAL-Lifecycle}
In order to avoid high overhead from constant small batches of I/O, log checkpoints are performed at intermittent intervals based on either the passage of real time via a 'tick' system similar to the one proposed in the VFD SWMR RFC~\cite{rfc20180610}, or based on the quantity of metadata written to the file. The specific criteria for and frequency of log checkpoints during library operation is configurable by the application via property lists. Due to the partition of information between different layers of the library, specific user-provided values for intervals at which these operations act as heuristics rather than exact thresholds.

I/O to the WAL file uses the active VFD for the file, unless a different VFD is provided at the time the WAL is enabled by \texttt{H5P\_set\_wal()}.

\subsubsection{Metadata Writes}

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{images/wal_design.png}
    \caption{Overview of different types of metadata writes}
    \label{fig:wal-diagram}
\end{figure}

Figure~\ref{fig:wal-diagram} illustrates how the WAL alters the existing flow of metadata writes through the library.  Writes which do not prompt a flush of the metadata cache have no special handling with the WAL enabled. Once a metadata write prompts a cache flush, it will be performed as a log flush which writes metadata to the WAL file and leaves stub entries in the metadata cache. The metadata in WAL entries is not written to the HDF5 file until a log checkpoint, which is either directly invoked by \texttt{H5Fflush()} or invoked each time a user-defined threshold is reached.

\subsubsection{Metadata Reads}
The MDC must be able to read back WAL entries in order to correctly service read operations when the WAL contains a more recent version of a metadata object than the file (e.g. after a log flush but before a log checkpoint). When a dirty object is evicted from the cache, a 'stub' entry is left in the cache. This stub entry records the address of the WAL entry within the WAL file so that it may be quickly read at a later time.

The full process for a metadata read is as follows:
\begin{itemize}
    \item If the requested metadata object is not in the metadata cache, fulfill the read from the file.

    \item If the requested metadata object has a non-stub entry in the metadata cache, fulfill the read from the metadata cache.

    \item If the requested metadata object has a stub entry in the metadata cache, fulfill the read from the WAL entry. 
\end{itemize}

\subsection{Metadata Deletion and Raw Data Integrity}
\label{sec:Metadata-Deletion}

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{images/wal_md_delete_diagram.png}
    \caption{A series of WAL operations that would result in raw data being overwritten during recovery}
    \label{fig:wal-md-delete-diagram}
\end{figure}

Consider the following series of events on a file with the WAL enabled, as illustrated in Figure~\ref{fig:wal-md-delete-diagram}:

\begin{enumerate}
    \item A user operation results in a metadata write to offset \texttt{A} of length \texttt{N} within the file. This write is logged to the WAL.

    \item A user operation results in the deletion of a section of metadata, \texttt{A*} to \texttt{A* + N*}, that resides entirely or partially within the address region \texttt{A} to \texttt{A + N}.

    \item Due to free space recycling being enabled on the file, the region \texttt{A*} to \texttt{A* + N*} is marked as free for other usage within the library.

    \item A user operation results in raw data being written to the file in the (now free) region \texttt{A*} to \texttt{A* + N*}. Because this is a raw data operation, it bypasses the WAL.

    \item Before the next log checkpoint, a crash occurs.

    \item Crash recovery begins, and eventually executes the metadata write from event \#1. This results in the overwriting of whatever portion of the user's raw data was in the filespace range marked as free by event \#3, from \texttt{A*} to address \texttt{A* + N*}.
\end{enumerate}

    Strictly speaking, raw data integrity is outside the scope of the Write-Ahead Log, but it is still preferable to preserve the integrity of application data as much as possible in the event of a crash.

    To prevent this potential loss of raw data, the preferred option is to defer recycling free space for metadata until the next log checkpoint. Metadata generally takes up a relatively small amount of space in the file compared to raw data, so the potential gains from optimizing space usage in this case are limited, especially given the algorithmic overhead required to enable it.

    If there exists a use case for which non-deferred metadata free space recycling is critical, the following is an outline of the changes necessary to support simultaneous raw data integrity and non-deferred metadata free space recycling:

    The WAL entry file format would need to be expanded to support dividing a metadata block into isolated sections. This is necessary because repeated metadata deletions could divide a previously contiguous block of metadata into an arbitrary number of distinct sections. Tracked information would need to include the quantity of sections, their lengths, and their offsets. In order to keep each WAL entry header a fixed size (to avoid fracturing writes), there would need to be a fixed upper bound on the potential number of sections within a single entry.

    A rough sketch of an algorithm to track these metadata sections within WAL entries is as follows:

    \begin{enumerate}
        \item At the time of a metadata deletion, search the metadata cache for any metadata writes which overlap the deleted region and have not been written to the file. The metadata cache contains stub entries with the length and offset of the metadata, which allow this search to be done without a disk read.

        \item If any of the WAL entries with overlapping writes already have more than the maximum number of distinct sections, then trigger a log checkpoint of the WAL. After this, no previous metadata writes will need to be re-executed, so this process ends.

        \item For each WAL entry with a metadata block that overlaps the deleted metadata block, add one or more additional sections:

        \begin{enumerate}
            \item Determine which of its existing sections overlap the deleted region.

            \item For each section that overlaps the deletion, decrease its length so that no valid sections of the metadata section overlap the deleted region.

            \item If the deletion results in the creation of a new section within the block (e.g. if the deletion overlaps with a section, but not the end of that section), compute the length and start address of the new section.

            \item If this process would result in the creation of enough new sections in the metadata block to push the WAL entry over the maximum number of entries, then perform a log checkpoint instead.
        \end{enumerate}
    \end{enumerate}

\subsubsection{WAL Lifecycle}

The WAL file will be created and its superblock initialized at file open time if the WAL is enabled on the file access property list (FAPL) for the file open/create operation. The WAL will be deleted when the file is closed normally, or after recovery if the file was reopened with the WAL disabled.

\subsection{Compatibility with Other Library Features}

\subsubsection{Parallel HDF5}

WAL compatibility with Parallel HDF5 could be achieved by designating a single process as the WAL writer, and having all I/O to the WAL be performed through that process.

Due to how parallel HDF5 handles each rank's metadata cache, additional synchronization points between the ranks will not be necessary for WAL compatibility. Because metadata writes must be done collectively, each rank will have the same dirty metadata cache entries to be flushed at the same time. Each rank will create a stub entry containing the target address in the WAL file, but only the designated writer will actually perform the write to the WAL file. Each rank will have up-to-date read access to the WAL file without additional work or I/O.

Because each process needs to be able to read directly from the WAL, the WAL file must be exposed to all processes in a similar manner to the HDF5 file itself. In order to maintain consistency, there will be an additional requirement that all ranks use the same log flush and log checkpoint intervals, and these intervals must be based on bytes written. In this way every process will have the same understanding of when log flushes and log checkpoints occur, and thereby will know when to eliminate stub entries.

\subsubsection{SWMR (Single Writer/Multiple Reader)}

There are multiple ways to enable SWMR access with crashproofing enabled. Perhaps the simplest method would be for the SWMR readers to ignore the WAL file and only look at the HDF5 file. This would of course prevent them from seeing any updates until a log checkpoint. Correct ordering of writes when replaying the WAL during the log checkpoint should happen naturally since the existing SWMR mechanism will have correctly ordered the writes in the WAL file, and they are replayed in that order.

Alternatively, we may wish for the readers to be aware of the WAL file and scan it for updates to metadata. They could either only look at WAL entries up to the latest log flush marker, or look at all entries. In either case we would want to be careful to handle the case where a log checkpoint occurs during a SWMR read operation. The need to avoid caching information about the location of metadata in the WAL would necessitate scanning the WAL frequently, which may make the first approach more feasible.

\subsubsection{Page Buffer}

Because the WAL largely replaces metadata writes to the HDF5 file with writes to the WAL file, the page buffer is less relevant than when not using the WAL. That said, we may be able to achieve a similar effect on writes by, when flushing multiple entries to the WAL (at log flush time or otherwise), assembling WAL entries into a single buffer before writing them to the WAL in a single operation. It should also be possible to use the page buffer only at log checkpoint time to perform metadata writes in larger blocks, though this will only benefit the log checkpoint and file close operations.

In the future it will be possible to implement a page buffer like scheme for the WAL itself, which will aid in prefetching entries that exist only in the WAL, but this will not be in the initial implementation.

The standard HDF5 page buffer will still be available for use with raw data when the WAL is active, since the WAL does not modify the I/O pattern for raw data.

\subsubsection{Metadata Accumulators}

Metadata accumulators sit below the metadata cache and group small metadata I/O requests into larger batches to improve performance. Simultaneous use of the metadata accumulators and the WAL is not possible with the current design.

If an accumulator worked simultaneously with the WAL, then what the metadata cache considers distinct writes to the WAL file from distinct cache entries could be grouped into a single I/O request at the VFD layer. This would write a single WAL entry with a metadata block that contains metadata blocks from distinct metadata cache entries. At metadata read time, if a stub entry in the cache is used to read metadata from the WAL file, the metadata block retrieved would be larger than expected. While it would contain the requested metadata block, the metadata cache lacks the capabilities to perform introspection on the accumulated metadata block to determine which region has the requested data.

As log checkpoints involve no writes to the WAL file, metadata accumulators may be used during log checkpoint operations, with the constraint that the accumulator be flushed afterwards. Since this would provide little to no opportunity for the accumulator to bundle I/O requests, the potential usefulness of enabling the accumulators for this case is debatable.

\subsubsection{Variable-Length and Reference Datatypes}

Variable-length and reference datatypes require special consideration, since the 'raw data' for these types has a metadata component. Data with a variable-length or reference datatype is written to file as global heap IDs which point to the location of the actual data within the file's global heap (i.e. within the metadata portion of the file).

As the metadata cache does not draw a distinction between metadata for these types and 'regular' metadata, the most straightforward solution is to treat these metadata operations in the same manner as other metadata writes.

Because the amount of data in variable-length and reference datasets is likely to be much higher than other kinds of metadata, using these datatypes extensively will likely increase the I/O and storage overhead of the WAL. Therefore, we may decide to add an option to exclude these types of objects from the WAL and remove consistency guarantees for variable length and reference data.

\subsubsection{Compact Datasets}

Compact datasets store the dataset's raw data within the object header. Just like variable-length and reference datatypes, this results in what the application views as raw data being stored and retrieved as metadata. As in that case, because the semantic meaning of the metadata block is not known to the metadata cache, the WAL will treat metadata describing a compact dataset in the same manner as all other metadata.

Unlike for variable-length and reference datatypes, the size of compact datasets is strictly bounded, so it is unlikely that any option to disable the WAL for compact datasets will be added.

\subsection{WAL File Format}

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{images/wal_layout.png}
    \caption{The on-disk layout of a WAL file}
    \label{fig:wal-layout}
\end{figure}

The WAL file is composed of the WAL superblock and a contiguous series of WAL entries. A WAL entry consists of a WAL entry info block and a metadata block.

Reading an arbitrary WAL entry requires iterating through all prior WAL entries, but this is only done at log checkpoint and recovery time. Reads during log flushes are expedited by using stub entries in the metadata cache to jump directly to the address of the desired WAL entry. The speed of recovery is not a critical concern, as recovery is expected to be infrequent.

The WAL superblock consists of the following elements:

\begin{itemize}
    \item \texttt{version} - The version of the WAL file format in use.

    \item \texttt{filepath} - Filepath indicating the HDF5 file that this WAL corresponds to.

\end{itemize}

\subsubsection{WAL Entries}

Each WAL entry consists of a WAL entry info block, followed by the block of metadata for the logged metadata write. The fields in the WAL entry info block are as follows:

\begin{itemize}

\item \texttt{target\_offset} - The target offset in the HDF5 file for the metadata write operation. This field has two 'magic values' which indicate this this WAL entry is a marker. A log flush marker indicates that all previous entries are safe to be replayed in the event of a crash. A log checkpoint marker indicates that all previous entries have already been flushed to the file and do not need to be replayed. As mentioned earlier, we may eliminate log checkpoint markers in favor of always trimming the WAL on a log checkpoint, in which case the start of the WAL functions as an implicit log checkpoint marker. Markers do not contain any of the other fields listed below. Markers are stored in this fashion to avoid allocating space in each entry for a field that the majority of WAL entries will not use.

\item \texttt{length} - The size in bytes of this entry's metadata block.

\end{itemize}

We may also decide to add a checksum for the WAL entry info, or the metadata block, or both, though the metadata block may already be checksummed using existing HDF5 facilities so that may not be necessary.

WAL entries do not need start or end tags to avoid executing WAL entries that result from torn writes, because interrupted WAL entries are already handled by log flush markers. During recovery, the WAL is only played back until the most recent log flush marker. If the library terminates unexpectedly, any torn writes to the WAL will be after the most recent log flush marker, and thus will not be re-executed.

Most database implementations of a Write-Ahead-Log uniquely assign each log entry a monotonically increasing log sequence number. At the present stage, the HDF5 WAL would have no use for such a feature beyond potential consistency checks. The HDF5 WAL is not currently planned to support multiple simultaneous writers, removing a large motivation for the log sequence number. Finally, because the WAL file format is not intended to be future-proof in the same manner as the HDF5 file format, adding a log sequence number in a subsequent version if the need arises will be relatively painless.

This design places the marker for log flushes/log checkpoints within individual WAL entries via a magic value in the 'offset' field. Another potential option is to store the marker in the WAL superblock as the offset of the latest WAL entry that has been log flushed/log checkpointed. This would have the advantage of improving recovery time, because storing markers in individual entries requires a preliminary scan of the entire WAL to determine which entries to replay. However, this would incur a performance penalty  by adding a  WAL header write to log flushes and log checkpoints.

\subsection{Additions to the API}

\begin{itemize}
    \item \texttt{herr\_t H5Pset\_wal(hid\_t fapl\_id,} \\
    \texttt{ const char *wal\_path,} \\
    \texttt{ H5WLinterval\_type\_t log\_flush\_interval\_type,} \\
    \texttt{ size\_t log\_flush\_interval,} \\
    \texttt{ H5WLinterval\_type\_t log\_checkpoint\_interval\_type,} \\
    \texttt{ size\_t log\_checkpoint\_interval,} \\
    \texttt{ hid\_t wal\_fapl\_id)} \\
    Modifies the file access property list \texttt{fapl\_id} to log metadata writes to a WAL file at \texttt{wal\_path}. \texttt{log\_flush\_interval\_type} determines which metric is used to initiate periodic log flush execution (bytes written, time, or none) and the value for that threshold is \texttt{log\_flush\_interval}. \texttt{log\_checkpoint\_interval\_type} determines which metric is used to initiate periodic log checkpoint execution (bytes written, time, or none) and the value for that threshold is \texttt{log\_checkpoint\_interval}. \texttt{wal\_fapl\_id} is a file access property list which is used to determine which VFD is used to perform I/O to the WAL file. If this parameter is \texttt{H5I\_INVALID\_HID}, the active VFD from \texttt{fapl\_id} is used for WAL file I/O.

    \item \texttt{herr\_t H5Pget\_wal(hid\_t fapl\_id,} \\
    \texttt{ const char **wal\_path,} \\
    \texttt{ H5WLinterval\_type\_t *log\_flush\_interval\_type,} \\
    \texttt{ size\_t *log\_flush\_interval,} \\
    \texttt{ H5WLinterval\_type\_t *log\_checkpoint\_interval\_type,} \\
    \texttt{ size\_t *log\_checkpoint\_interval,} \\
    \texttt{ hid\_t *wal\_fapl\_id)} \\
    Retrieves whether a given file access property list has the WAL enabled, the path to the WAL file if so, and the thresholds types and values for when log checkpoints are performed. If \texttt{*wal\_path} is returned as NULL then the WAL is disabled for the file.

    \item \texttt{herr\_t H5Pset\_wal\_auto\_recovery((hid\_t fapl\_id,} \\
    \texttt{bool enable\_auto\_recovery)} \\
    Determines whether, if a valid WAL path is detected at file open time (indicating a library crash) the metadata recovery process will automatically begin.

    \item \texttt{herr\_t H5Pget\_wal\_auto\_recovery((hid\_t fapl\_id,} \\
    \texttt{bool *enable\_auto\_recovery)} \\
    Retrieves whether automatic metadata recovery on file open is enabled.

    \item \texttt{herr\_t H5Fwal\_flush(hid\_t file\_id)} \\
    Performs a log flush to the WAL. A counterpart to \texttt{H5Fflush()}, which performs a log checkpoint.
\end{itemize}

\subsection{The Recovery Process}

If WAL usage is enabled for a file, then recovery takes place at file open time if the file did not close properly. Whether the file was closed properly is tracked in the HDF5 superblock, similar to the "journal open" flag from the Metadata Journaling RFC. It is tracked via a superblock message containing the filepath of the WAL file.

At file open, this message is written, and it is deleted only at the end of the file closing process. Any premature termination of the library or an application using the library will leave the message in the superblock, which can be detected at file open time.

The process to restore a file's metadata to a self-consistent state is as follows:

\begin{itemize}
    \item Scan the WAL from the beginning to the end to find both the most recent log checkpoint marker and the most recent log flush marker.
    \item Starting from the most recent log checkpoint marker  in the WAL (or from the beginning if there are none), read each WAL entry. Copy each entry's block of metadata to the specified offset in the file.
    \item When the recovery algorithm reaches the most recent log flush marker, stop processing any further WAL entries.
    \item Trim the WAL if the file was opened with WAL enabled. If the file was opened with the WAL not enabled, delete the WAL file and remove the HDF5 superblock message.
\end{itemize}

If a file was not closed cleanly and is reopened with read only access, the recovery process is different:

\begin{itemize}
    \item Scan the WAL from the beginning to the end to find both the most recent log checkpoint marker and the most recent log flush marker.
    \item Starting from the most recent log checkpoint marker in the WAL (or from the beginning if there are none), read each WAL entry. Create a stub entry in the cache for each WAL entry.
    \item When the recovery algorithm reaches the most recent log flush marker, stop reading any further WAL entries.
\end{itemize}

Depending on available resources, we may delay implementation of the read only reopen case.

### 2024-04-26 RFCs/HDF5_Library/WriteAheadLog/sections/implementation.tex
Add Write-Ahead Log RFC (version 1)

\section{Implementation}
\label{sec:implementation}

\subsection{Changes above the Metadata Cache}

While most of the changes to the library to support the WAL will be in the metadata cache and the new WAL package, some supporting code must be added to the upper layers. Here are some of the changes that will need to be implemented:

\begin{itemize}
    \item The superblock code needs to handle the additional WAL filepath field that indicates if the file was closed normally.
    \item Properties will need to be set up and passed down as appropriate.
    \item The file code will need to handle opening and closing the WAL file itself, checking for incorrect shutdown, and initiating a recovery if appropriate.
    \item The file code will also need to pass down explicit log flush requests, and will need to make sure to issue VFD layer \texttt{flush} operations after log checkpoint operations.
\end{itemize}

\subsection{Changes to the Metadata Cache}

\subsubsection{Stub Entries}

There are a few different ways to implement the metadata stub entries that instruct the metadata cache to look at the WAL to find the actual metadata. Since the entry is stored in serialized, on disk format, it behaves differently from other cached metadata entries. We can either add the stub entries in the same tables as the standard entries, or we can create an entirely separate table of stub entries, which use an entirely different structure. Using the same table prevents the need for multiple table lookups when loading an entry. However, in the case where an entry is flushed to the WAL but not evicted until a later operation, while still clean, the MDC needs to know the address in the WAL that the new stub entry should point to. While this could be handled by adding a WAL address field to the normal entry struct, using a separate table may be simpler and clearer. In general, attempting to use the same cache entry struct for two very different things can cause maintainability issues. It may be possible to use an intermediate struct or "common prefix" style nested struct to eliminate the extra lookup while keeping the structs for normal entries and WAL stubs mostly separate.

\subsubsection{Entry Flushes}

When the WAL is enabled, all flushes of entries from the metadata cache will by default go to the WAL. This operation will be similar to the existing code for flushing a single entry, except it will forward the write call to the WAL module, and create a stub entry which stores the address returned from the WAL module (and the length already known to the MDC).

On a log flush operation, the MDC will iterate over all dirty entries in the cache (these must all be non-stub entries because stub entries cannot be dirty), flushing each to the WAL (and logging the address or creating a stub entry as discussed above). After finishing this, the MDC writes a log flush marker to the WAL, then initiates a VFD layer \texttt{flush} operation on the WAL, then returns.

On a log checkpoint operation, the MDC will first perform a log flush, including the VFD \texttt{flush} operation. This ensures that the file will be recoverable if the program stops before the log checkpoint completes. Next, the MDC will iterate over all entries in the cache, flushing all entries with an associated stub entry to the HDF5 file, and deleting the associated stub entries. It will then iterate over all remaining stub entries, reading each corresponding entry from the WAL file and writing them to the appropriate place in the HDF5 file. The order does not matter, since the MDC only keeps (or keeps a stub entry to) the most recent version of each piece of metadata. Next, the MDC initiates a VFD \texttt{flush} on the HDF5 file, writes a log checkpoint marker to the WAL (or trims the WAL), then initiates a VFD \texttt{flush} on the WAL, and returns. This way we ensure that the WAL recovery start point is only advanced once we're sure the HDF5 file has all metadata written to it.

The Metadata cache will also be responsible for determining when to perform scheduled log flushes and checkpoints, whether based on time or data written.

% \subsection{Changes below the Metadata Cache}

\subsection{The WAL Module}

The operations that the WAL must expose are as follows:

\begin{itemize}
    \item Create a WAL entry for a metadata write, and append it to the end of the WAL file.

    \item Read the superblock of a WAL file to retrieve information about its version and parent HDF5 file.

    \item Read a single WAL entry from a specific address in the WAL file.

    \item Trim all WAL entries, removing everything from the WAL file except its superblock. Care should be taken that only log checkpointed entries are trimmed in order to avoid file corruption via loss of metadata writes.

    \item Create a log flush or log checkpoint marker, and append it to the end of the WAL file. A log flush marker that indicates which entries are safe to replay in the event of a crash. A log checkpoint marker indicates which entries have been written to the file and may be safely trimmed.

    \item Read all entries from the latest log checkpoint marker until the latest log flush marker, to implement recovery. This can be implemented using an iterator, returning the addresses of the first and last entries to read, or returning all the entries in a single call.

\end{itemize}

In addition, to improve performance of log flushes and checkpoints, we may wish to add:

\begin{itemize}
    \item Create a series of WAL entries for a metadata write, and append them to the end of the WAL file, optionally adding a log flush or checkpoint marker after the entries.

    \item Read a series WAL entries from a list of specific addresses in the WAL file.

\end{itemize}

### 2024-04-26 RFCs/HDF5_Library/WriteAheadLog/sections/introduction.tex
Add Write-Ahead Log RFC (version 1)

\documentclass[../HDF5_RFC.tex]{subfiles}

\begin{document}

\section*{Introduction}
\label{sec:intro}

At present, the burden for crash prevention and recovery when using HDF5 lies entirely on application developers. The library itself has no provisions for crash recovery or backup creation. Considering the potential scale of data loss, the materials or machinery that may be required to replicate physical experiments, and the cost of compute time, the development of a native mechanism for crash recovery would be highly valuable. To limit complexity of design and I/O overhead, and because the semantics of when raw data is written to the file are already well defined, this proposal's goal is limited to restoring metadata and preventing overall file corruption.

The WAL enables crash recovery through a page-oriented replay log. This log will store enough information about metadata operations that, in the event of a crash, these operations may be replayed to restore the file's metadata to a confirmed self-consistent state. The log is page-oriented in the sense that it describes the metadata operations in terms of blocks of metadata at offsets within the file, rather than in terms of HDF5 file objects. During operation, the library will set markers in the WAL to indicate points at which the file is known to have self-consistent metadata. The WAL is an external file that may be trimmed at regular intervals to keep its size reasonable.

Previous efforts to address metadata crash-recovery through Metadata Journaling ~\cite{rfc20070801} had significant performance issues, leading to the decision to discontinue pursuit of that approach. There have also been efforts to implement full SWMR (Single Writer/Multiple Reader) support which could be extended to support crashproofing, but we feel that users that do not need SWMR access will appreciate a more lightweight and maintainable solution.

\vspace{-10pt}

\end{document}

### 2024-04-26 RFCs/HDF5_Library/WriteAheadLog/sections/testing.tex
Add Write-Ahead Log RFC (version 1)

\section{Testing}
\label{sec:testing}

In order to get some preliminary results to verify whether or not this is a good approach for crashproofing HDF5, we identified two metadata-intensive benchmarks (A and B) and one non-metadata-heavy benchmark (C): 
\begin{itemize}
    \item Benchmark A: generates an HDF5 file of size 135 MB and a total of 77,111 metadata writes.
    \item Benchmark B: generates an HDF5 file of size 23 GB and a total of 1,821,278 metadata writes.
    \item Benchmark C: generates an HDF5 file of size 41 MB and a total of 66 metadata writes.
 \end{itemize}

\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
   benchmark & file size & metadata writes \\
   \hline
   A  & 135 MB & 77,111 \\
   \hline
   B & 23 GB & 1,821,278\\
   \hline
   C & 41 MB & 66\\
   \hline
\end{tabular}
\end{center}

We then modified the library's MPIO driver to write the address and size of all the metadata writes to a log file $M$.

A dummy WAL writer was created to read the log file $M$, and for each piece of metadata read, write the metadata address, size, and bytes equal to the size of the metadata of random data to a dummy WAL file. This is meant to simulate the writing of actual metadata into a WAL file down the line.

To determine the overhead from occasional HDF5 file syncs, which are necessary for a \textit{Log Checkpoint}, we modified the library's MPIO driver to flush the HDF5 file intermittently based on the amount of metadata written. The time needed for the HDF5 file syncs was also recorded to see if it would be problematic to keep the WAL file small for metadata heavy applications.

The same thing was done for the dummy WAL writer. Since the dummy WAL writer would need to handle both \textit{Log Flush }and \textit{Log Checkpoint}, we added the ability to flush every $x$ bytes to simulate a \textit{Log Flush} to help sync the playback location and the ability to trim and flush the file every $y$ bytes to simulate a \textit{Log Checkpoint} to help reduce the size of the WAL.

For runs with no \textit{Log Checkpoint}, the flush interval has no effect on the modified MPIO file driver, and hence we used the results from a single set of averaged runs for all flush interval cases. For Benchmark C, the dummy WAL writer does not contribute a significant amount of time to the result, hence the results for Benchmark C with only \textit{Log Flush} show the same result for all flush intervals.

Specifically, we tested:
\begin{itemize}
    \item A \textit{Log Flush} every 64 KB and a \textit{Log Checkpoint} every 1 MB
    \item A \textit{Log Flush} every 256 KB and a \textit{Log Checkpoint} every 4 MB
    \item A \textit{Log Flush} every 1 MB and a\textit{Log Checkpoint} every 16 MB
    \item A \textit{Log Flush} every 4 MB and a \textit{Log Checkpoint} every 64 MB
    \item A \textit{Log Flush} every 16 MB and a \textit{Log Checkpoint} every 256 MB
    \item A \textit{Log Flush} every 64 KB
    \item A \textit{Log Flush} every 256 KB
    \item A \textit{Log Flush} every 1 MB
    \item A \textit{Log Flush} every 4 MB
    \item A \textit{Log Flush} every 16 MB
\end{itemize}

The preliminary results for benchmark A \& B indicated that:
\begin{itemize}
    \item The overhead for \textit{Log Flush} + \textit{Log Checkpoint} both decrease as we increase the interval at which we perform HDF5 file syncs.
    \item The overhead for \textit{Log Flush} is minimal, and mostly comes from adding an HDF5 file sync before file close.
\end{itemize}
See the graphs below for more information.

Note the X-axis for the graphs list the \textit{Log Checkpoint} interval, even for runs with only \textit{Log Flush}. The \textit{Log Flush} interval is always as listed above for the corresponding specified \textit{Log Checkpoint} interval.

% testing - matt
\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (CPU time) for \textit{Log Flush} + \textit{Log Checkpoint}: benchmark A \& B,
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=-10,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south west,
      column sep=1ex
}
]
\addplot[style={orange,fill=orange}]
         coordinates{(1MB,12.657)(4MB,2.721)(16MB,-5.380)(64MB,-6.267)(256MB,-3.587)};
\addplot[style={blue,fill=blue}]
         coordinates{(1MB,8.155)(4MB,-1.679)(16MB,-4.474)(64MB,-5.907)(256MB,-6.893)};    
\addlegendentry[mark color=orange]{Benchmark A}
\addlegendentry[mark color=blue]{Benchmark B}
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (CPU time) for \textit{Log Flush}: benchmark A \& B,
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=-12,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={orange,fill=orange}]
        coordinates{(1MB,-6.576)(4MB,-6.576)(16MB,-6.597)
        (64MB,-6.597)(256MB,-6.617)};
\addplot[style={blue,fill=blue}]
        coordinates{(1MB,-9.779)(4MB,-9.785)(16MB,-9.799)
        (64MB,-9.779)(256MB,-9.838)};      
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (WALL time) for \textit{Log Flush} + \textit{Log Checkpoint}: benchmark A \& B,
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=-15,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south west,
      column sep=1ex
}
]
\addplot[style={orange,fill=orange}]
        coordinates{(1MB,45.129)(4MB,11.076)(16MB,-9.029)
        (64MB,-6.702)(256MB,3.210)};
\addplot[style={blue,fill=blue}]
        coordinates{(1MB,26.691)(4MB,66.066)(16MB,107.205)(64MB,29.342)(256MB,-5.604)};   
\addlegendentry[mark color=orange]{Benchmark A}
\addlegendentry[mark color=blue]{Benchmark B}
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (WALL time) for \textit{Log Flush}: benchmark A \& B,
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=-12,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={orange,fill=orange}]
        coordinates{(1MB,-2.121)(4MB,-2.140)(16MB,-2.121)
        (64MB,-2.140)(256MB,-2.159)};
\addplot[style={blue,fill=blue}]
        coordinates{(1MB,-4.657)(4MB,-4.659)(16MB,-4.095)
        (64MB,-4.697)(256MB,-4.789)};   
\end{axis}
\end{tikzpicture}
\end{center}

As for benchmark C, the four graphs below indicated that the overhead for \textit{Log Flush} as well as \textit{Log Flush} + \textit{Log Checkpoint} is minimal.

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (CPU time) for \textit{Log Flush} + \textit{Log Checkpoint}: Benchmark C,
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=0,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={brown,fill=brown}]
        coordinates{(1MB,0.998)(4MB,5.869)(16MB,4.771)
        (64MB,8.421)(256MB,7.230)};
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (CPU time) for \textit{Log Flush}: Benchmark C,
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=0,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={brown,fill=brown}]
         coordinates{(1MB,1.107)(4MB,1.113)(16MB,1.105)
         (64MB,1.112)(256MB,1.108)}; 
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (WALL time) for \textit{Log Flush} + \textit{Log Checkpoint}: Benchmark C,
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=-5,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={brown,fill=brown}]
         coordinates{(1MB,2.591)(4MB,4.714)(16MB,15.948)
         (64MB,4.111)(256MB,-0.235)};       
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (WALL time) for \textit{Log Flush}: Benchmark C,
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=0,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={brown,fill=brown}]
         coordinates{(1MB,2.487)(4MB,2.487)(16MB,2.487)
         (64MB,2.487)(256MB,2.487)}; 
\end{axis}
\end{tikzpicture}
\end{center}

The following four graphs (CPU and WALL time) report the overhead for \textit{Log Flush} as well as \textit{Log Flush} + \textit{Log Checkpoint} when running benchmark C with a larger file size (167MB) and 4 ranks.

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (CPU time) for \textit{Log Flush} + \textit{Log Checkpoint}: Benchmark C (larger file size),
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=-15,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={brown,fill=brown}]
        coordinates{(1MB,-3.538)(4MB,-1.517)(16MB,-8.139)
        (64MB,-10.438)(256MB,4.290)};
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (CPU time) for \textit{Log Flush}: Benchmark C (larger file size),
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=0,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={brown,fill=brown}]
         coordinates{(1MB,11.712)(4MB,11.714)(16MB,11.711)
         (64MB,11.713)(256MB,11.712)}; 
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (WALL time) for \textit{Log Flush} + \textit{Log Checkpoint}: Benchmark C (larger file size),
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=-5,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={brown,fill=brown}]
        coordinates{(1MB,-1.537)(4MB,-3.737)(16MB,-1.908)
        (64MB,0.573)(256MB,-0.483)};
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}
[
title=\% Overhead (WALL time) for \textit{Log Flush}: Benchmark C (larger file size),
ybar=8pt,
nodes near coords,
bar width=0.2cm,
ymin=-2,
symbolic x coords={1MB,4MB,16MB,64MB,256MB},
xtick=data,
enlarge x limits=.2,
   legend style={
      at={(.6,.8)}, 
      anchor=south,
      column sep=1ex
}
]
\addplot[style={brown,fill=brown}]
         coordinates{(1MB,-1.180)(4MB,-1.181)(16MB,-1.180)
         (64MB,-1.181)(256MB,-1.180)}; 
\end{axis}
\end{tikzpicture}
\end{center}
